### 2023-06-21 rapport/convexemple.tex
debutrapport

\begin{remarque}
	L'ensemble $S_n^+\left( \Qp \right) $ n'est pas convexe en général.

	Par exemple pour $p = 5$, si on considère les matrices $M_1 = \begin{pmatrix} 5 + \frac{3}{5} & \frac{4}{5} \\ \frac{4}{5} & -\frac{3}{5} \end{pmatrix} $ et $M_2 = \begin{pmatrix} 25+\frac{7}{25} & \frac{24}{25} \\ \frac{24}{25}&-\frac{7}{25} \end{pmatrix} $, on a $\chi_{M_1} = X^2 -5 X -4  $ et $\chi_{M_2} = X^2 - 25 X -8$ donc en plongeant ces matrices dans $\mathbb{Q}_5$ il vient que $\chi_{M_1}, \chi_{M_2} \in \mathbf{Z}_5[X]$ i.e. $M_1,M_2 \in S_2^+\left( \Q_5 \right) $. Or $\chi_{M_1 + M_2}  = X^{2} - 150 X - \frac{3784}{5}$ qui une fois plongé dans $\mathbb{Q}_5$ n'est pas à coefficient dans $\mathbb{Z}_5$, donc $ S_2^+\left( \Q_5 \right) $ n'est pas convexe. Ce résultat se généralise pour tout $n$ en considérant les matrice par blocs $M'_i = \text{diag}\left( M_{i},0,\ldots,0 \right) $.

\end{remarque}

### 2023-06-21 rapport/polyhedra.tex
debutrapport

\partie{1}{vendredi 16 juin 15:00}{Polyèdres convexes $p$-adiques }
\begin{notation}
	Pour tout élément $x$ de $ \Qp$ on note $x\ge 0$ et on dit que $x$ est \textit{positif} si $\val(x) \ge 0$ c'est à dire si $x \in \Zp$. On induit à partir de cette notation les définitons de $x\le 0$, $x>0$ et $x<0$.

	Similairement, pour toute matrice $M$ à coefficient dans $\Qp$ on note $M\ge 0$ et on dit que $M$ est \textit{positive} si tous les coefficients de $M$  sont positifs, c'est à dire si $M \in M_n\left( \Zp \right) $ . On infère également les notation $M\le 0$, $M>0$ et $M<0$.     
\end{notation}

\begin{remarque}
	On évitera la notation $x\ge y$ qui pourrait laisser penser de manière trompeuse que $x\ge y \Rightarrow x-y\ge 0$\footnote{Par exemple, $\ldots11,11 \ge \ldots00,01 $ mais $\ldots11,11 - \ldots00,01 = \ldots 11,1 < 0$}.
\end{remarque}
\section{Polyèdres convexes \texorpdfstring{$p$}{p}-adiques}
\subsection{Matrices symétriques positive}

\begin{definition}
	On note $\P_n\left( \Qp \right) $ l'ensemble des matrices symétriques dont tous les mineurs principaux ont une valuation positive.
\end{definition}

\begin{rappel}

Un élément de $ \Qp$ a une valuation positive si et seulement si il est élément de $\Zp$. 
\end{rappel}

\begin{propriete}

	$\P_n\left( \Qp \right) = \{ M \in S_n\left( \Qp \right)$ | les\- min\-eurs\- prin\-ci\-paux\- de\- $M$ \-sont \-à \-va\-leur \-dans\- $\Zp \} $.
\end{propriete}

	\textit{Preuve :} découle directement du rappel précédent. 
	\medskip

\begin{prop}
	 \[
		 \Pn = S_n\left( \Zp \right) 
	.\]  
\end{prop}

\begin{remarque}
	On remarque alors que l'ensemble $\P_n$ correspond aux matrices symétriques à coefficients positifs.   
\end{remarque}
	\textit{Preuve :}

 Le déterminant étant une fonction polynomiale en les coefficients de la matrice, toute matrice de à coefficient dans $\Zp$ a un déterminant à valeur dans $\Zp$. D'où, par la propriété 2, $S_n\left( \Zp \right) \subset \Pn $.

 L'inclusion réciproque se montre par récurrence. On note pour tout $n \in \mathbf{N}$ $\mathcal{H}_n :  \Pn \subset  S_n(\Zp )$.

 On notera $ \Delta_{i_1,\ldots,i_n}\left( M \right) $ le mineur principal de $M$ composé des lignes et des colonnes d'indices $i_1,\ldots,i_n \in \left\{ 1,\ldots,n \right\} $ pour tout matrice $M$. On notera d'ailleurs simplement  $ \Delta_{i_1,\ldots,i_n}$ lorsque le contexte est explicite.

 Les cas $n=0$ et $n=1$ se démontrent sans difficultés aucunes. Montrons le cas $n=2$ qui servira par la suite.

 Soit $M \in \P_2\left( \Qp \right) $, $M$ s'écrit $M = \begin{pmatrix} \alpha & \gamma \\ \gamma & \beta \end{pmatrix}$, avec $\alpha, \beta, \gamma \in \Qp^3$.

 On sait alors que $ \alpha = \Delta_1$ et $ \beta = \Delta_j$ sont des entiers $p$-adiques, il suffit de montrer que $\gamma$ en est également un. Pour ce faire supposons que $ \val (\gamma) < 0$, on a alors $\val ( \gamma^2) = 2 \val\left( \gamma \right) < \val\left( \alpha \beta \right) $ et on en déduit $ \val \left( \Delta_{1,2} \right)= \min\left( \val\left( \alpha \beta \right),2~ \val \left( \gamma \right) \right) = 2 \val\left( \gamma \right) <0 $ ce qui contredit la positivité de $\Delta_{1,2}$ et est donc absurde. On conclut alors que $ \gamma \in \Zp$ et $M \in  S_n\left( \Zp \right) $. On a montré $\mathcal{H}_2$.

 Soit $n \in \mathbf{N}$ tel que la propriété $\mathcal{H}_n $ soit vérifiée et $M$ une matrice de $\Pn$.

 $M$ s'écrit 
 \[
 M= \left(\begin{array}{ccc|c}
  &      &     &   \beta_1  \\
  &  M'  &     &\vdots\\
  &      &     &   \beta_n  \\
\hline
\beta_1 &\cdots&  \alpha_n  & \alpha_{n+1}
\end{array} \right)
\]
avec $M' \in S_n\left( \Qp \right) $ et $\beta_1,\ldots, \beta_n, \alpha_{n+1} \in \Qp$.

On note $ \alpha_1,\ldots, \alpha_n$ les coefficients diagonaux de $M'$ qui sont des entiers $p$-adique par hypothèse de récurrence.

 Par définition $ \alpha_{n+1} = \Delta_{n+1}$ est un entier $p$-adique. Puis on se ramène au cas $n=2$ en utilisant le fait que pour i=1,\ldots, n, $\Delta_{i,n+1} = \begin{vmatrix} \alpha_{i} & \beta_{i}\\ \beta_{i} & \alpha_{n+1} \end{vmatrix} $ et on en déduit que $\beta_{i} \in \Zp$ pour $i=1,\ldots,n$. On conclut en appliquant l'hypothèse de récurrence à $M'$.

\hfill \ensuremath{\Box}

\begin{remarque}

	La preuve de la proposition précédente montre qu'il suffit en réalité que les mineurs principaux de taille au plus $2$ aient une valuation positive (ou soient éléments de $\Zp$) ce qui correspond à la définition de matrice semi-définie positive sur le semi-corps tropical développée par . Ce n'est toutefois pas la définition qui sera choisie ici, pour des raisons développées en partie \hyperlink{subsection.1.2}{1.2}.
\end{remarque}

\begin{propriete}
	$\Pn$ est un anneau.
\end{propriete}

\textit{Preuve :} Par la propriété précédente $\Pn = S_n \left( \Zp \right)$ comme intersection des anneaux $M_n \left( \Qp \right)$ et $S_n\left( \Qp \right) $.
\begin{propriete}
	L'ensemble $\Pn$ est :
	\begin{enumerate}[label=\roman*.]
	\item ouvert
	\item fermé
	\item borné
	\item compact
	\item convexe au sens de Monna[nsvqkbdbvujezvbqevb]

\end{enumerate}
\end{propriete}
\textit{Preuve :}
$i.$ et $ii.$ se déduisent du fait que $\Zp$ soit ouvert et fermé dans $\Qp$, $ii.$ découle directement du fait que $\|M\|_\infty = \sup |M_{i,j}|_p \le 1$ et $iv.$ se déduit de $ii.$ et $iii.$.
Quand à $v.$ c'est une conséquence directe de la convexité de $\Zp$ et $S_n\left( \Qp \right) $.
\subsection{Polyèdres convexes \texorpdfstring{$p$}{p}-adiques}

\begin{definition}

On définit un polyèdre convexe $P$ comme l'intersection de $\Pn$ avec un hyperplan affine $\mathcal{L} $ de $S_n\left( \Qp \right) $. 
\end{definition}

Soit $P$ un polyèdre convexe et $\mathcal{L} $ un plan affine tel que $P = \Pn \cap \mathcal{L}$, et dont on note $s$ la dimension de l'espace vectoriel associé. On dispose de donc de $s +1 $ matrices $M^0,M^1,\ldots, M^s$ telles que $\mathcal{L} = M^0 + \text{Vect}\left( M^1,\ldots,M^s \right)$. Le polyèdre $P$ s'écrit alors $P = \left\{ M^0 + x_1 M^1 + \ldots + x_s M^s \ge 0 \right\}$. On identifie alors souvent $P$ avec $\left\{ \left( x_1,\ldots,x_s \right) \in \Qp^s |M^0 + x_1 M^1 + \ldots + x_s M^s \ge 0 \right\}$ ce qui permet d'écrire qu'un vecteur $x_1,\ldots,x_s$ de $\Qp^s$ est élément de $P$ si et seulement si il vérifie :

	\begin{equation}
	\label{eq:1} 
\forall i,j ~  M^0_{i,j} + x_1 M^1_{i,j} + \ldots + M^s_{i,j} \ge 0
	\end{equation}

On peut alors réécrire l'inégalité matricielle en  $P = \left\{ x \in \Qp^s \-| Ax + b \ge 0 \right\} $ avec 
\[A = \begin{pmatrix} M^1_{1,1} & \ldots & M^s_{1,1} \\
\vdots & & \vdots \\
M^1_{n,n} & \ldots & M^s_{1,1}\\ \end{pmatrix} \in M_{n^2,s}\left( \Qp \right) \text{ et } 
b = \begin{pmatrix} M^0_{1,1} \\
\vdots\\
M^0_{n,n} \end{pmatrix} \in M_{n^2, 1}\left( \Qp \right) 
.\]  
\begin{remarque}
	On peut réduire de moitié la tailles des matrices $A$ et $b$ en considérant que les coefficients diagonaux et supradigonaux des $M^i$ pour $i = 0,1,\ldots,n$. Ce qui permet de se ramener à des matrices équivalente\footnote{puisque les inéquations de \ref{eq:1} impliquant le couple $(i,j)$ $i>j$ sont redondantes avec les équations impliquant $(j,i)$}  avec $\frac{n(n+1)}{2}$ lignes.  
\end{remarque}

En mettant sous cette forme le polyèdre on reconnait alors aisément que le problème de minimiser une application linéaire sur un polyèdre correspond exactement à résoudre le problème de la \textit{Programmation linéaire}.

\begin{remarque}
	On se ramène au cas quelconque du problème de la \textit{Programmation linéaire} (taille quelconque et non seulement avec un nombre de ligne en $\frac{n(n+1)}{2}$ ou $n^2$) en annulant des coefficients $M^k_{i,j}$ pour tout $i=1,\ldots,n$.   
\end{remarque}

\begin{propriete}
	Un polyèdre $p$-adique convexe est convexe au sens de Monna $[la so\bigcup_{\bigcup_{u\bigcup_{uu\bigcup_{uu\bigcup_{uu\bigcup_{uuu\bigcup_{uuuu\bigcup_{uuuuu\bigcup_{uurce} } } } } } } } }]$ 
\end{propriete}

\textit{Preuve :} Provient immédiatement du fait qu'un polyèdre s'écrit comme intersection d'ensemble convexe.

### 2023-06-21 rapport/spectrahedra.tex
debutrapport

\partie{2}{mardi 20 juin 11:00}{Spectraèdres $p$-adiques }
\newcommand\mat{matrice symétrique semie-définie positive } 
\newcommand\Mat{Matrice symétrique semie-définie positive }
\newcommand\mats{matrices symétriques semie-définies positives }
\newcommand\Mats{Matrices symétriques semie-définies positives }

\section{Spectraèdre \texorpdfstring{$p$}{p}-adiques } 
Ce paragraphe tend à fournir un définition de la notion de \mat sur les corps $p-$adiques pour en déduire une définition de spectraèdre qui serait pertinente sur un corps non-archimédien. 
\subsection{\Mats}

\begin{definition}
	On appelle \mat toute matrice $M \in S_n\left( \Qp \right) $ dont toutes les valeurs propres sont de valuation positive ou nulle[lien du pragarâgre avec les extesnions de corps lolololololololol].

	On note $S_n^+\left( \mathbb{Q}_p \right)$ l'ensemble des \mats.
\end{definition}
\begin{propriete}
	\label{caracsnp}
	Caractérisation des \mats

	Une matrice est symétrique définie positive si et seulement si son polynôme caractéristique est à coefficient dans $\Zp$ .

\end{propriete}
	\textit{Preuve :} Voir le LIEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEN0

\begin{consequence}
	$\Pn \subset S_n^+\left( \mathbb{Q}_p \right)$ 
\end{consequence}

\textit{Preuve : }  Le polynôme caractéristique d'une matrice à coefficients dans $\Zp$ étant à coefficient dans $\Zp$ on obtient le résultat par la propriété \ref{caracsnp} .

\begin{remarque}
	En général l'inclusion réciproque est fausse. Ainsi pour $M = \begin{pmatrix} 5 + \frac{3}{5} & \frac{4}{5} \\ \frac{4}{5} & -\frac{3}{5} \end{pmatrix} $, on a $\chi_M = X^2  - 5 X - 4$. Or une fois $M$ plongé dans $\mathbb{Q}_5$ on a $\chi_M \in \mathbb{Z}_5[X]$ donc $M \in S_2^+\left( \mathbb{Q}_5 \right)$ or aucun des coefficients de $M$ n'est dans $S_2^+\left( \mathbb{Q}_5 \right)$

\end{remarque}

\note{vérifier si le fait qu'une matrice snp soit soit positive ou non est lié à la présence ou non de racine uniquement dans $\mathbb{Z}_p$ }.

### 2023-07-12 rapport/padic.tex
Second commit

\section{Introduction aux nombres \texorpdfstring{p}{$p$}-adiques}

On se contentera dans cette section d'une description très élémentaire des différentes définitions et propriétés des nombres $p$-adiques. La plupart des preuves relative à cette section ainsi que de plus amples informations sont disponibles en annexe \todo{l'annexe}. Cette section est très largement inspiré du cours de Xavier Caruso \parencite{caruso_computations_2017} que l'on invite d'ailleurs à aller consulter pour une vision plus complète mais très largement compréhensible.

\begin{notation}
	On considère pour tout ce rapport $p$ un nombre premier.
\end{notation}

\subsection{Entiers \texorpdfstring{p}{$p$}-adique} 
\begin{definition}{Entier $p$-adique }

On appelle entier $p$-adique la somme formelle :
\[
	z  = a_0 + a_1 p + \ldots+a_{n}p^n+\ldots
\]
ou les $a_i$ sont des entiers compris entre $0$ et $p-1$.

\end{definition}

\begin{remarques}
	\begin{itemize}
		\item[$\circ$]  On note $\Zp$ l'ensemble des entier $p-$adiques.
		\item[$\circ$] Par commodité on notera $\ldots a_n\ldots a_1 a_0$ l'entier $p$-adique $\sum a_{i}p^i$ 
\end{itemize}
\end{remarques}

\begin{ex}

	Ainsi les sommes $\sum\limits_{i=0}^{ \infty} p^i = \ldots1111111$ ou $\sum\limits_{i=0}^{ \infty} (i\ \text{mod}\ p) p^i = \ldots210(p-1)\ldots21 $ sont des entiers $p$-adiques parfaitement définis bien que ne convergeant pas dans le cas réel. 
\end{ex}

\begin{propriete}
	$\mathbb{Z}_p$ peut être muni d'une structure d'anneau commutatif intègre en lui adjoignant l'addition terme à terme avec retenue et la multiplication.
\end{propriete}

Par exemple dans $\mathbb{Z}_5$

\begin{tabular}{lS}
     & \ldots34202243\\
  $+$& \ldots01423401\\
  \hline
  & \ldots 41131144 \\

\end{tabular}

\begin{tabular}{lS}
     & \ldots02243\\
  $\times $& \ldots23401\\
  \hline
  & \ldots 02243\\
  & \ldots 0000 \\
  & \ldots 132\\
  & \ldots 34\\
  $+$ & \ldots 1\\
\hline
& \ldots14443	
\end{tabular}

\begin{propriete}
	 $\mathbb{Z}$ est un sous-anneau de $\mathbb{Z}_p$. 	
\end{propriete}
\textit{Preuve :} Tout entier naturel $a$ admet une décomposition en base $p$ (qui est unique) i.e. s'écrit $a = \sum\limits_{i=0}^{n} a_{i}p^i$ avec $n = \left\lfloor \log_p a\right\rfloor$ et s'associe naturellement à l'élément $\ldots0000a_n\ldots a_0$ de $\mathbb{Z}_p$. Puis à tout entier négatif $b$ on associe l'opposé dans $\mathbb{Z}_p$ de $|b|$. Il n'est alors pas compliqué de vérifier que les opérations de $\mathbb{Z}_p$ restreintes à la projection de $\mathbb{Z}$ coïncident avec les opération dans $\mathbb{Z}$. \hfill \qedsymbol

\begin{remarque}
	Si l'on a vu que les entiers au sens réel était des entiers $p$-adiques, certains entiers $p$-adique ont du sens en tant que nombre rationnels sans être des entiers relatifs, ainsi on a par exemple $\frac{1}{2} = \ldots 2223 \in \mathbb{Z}_5$. Cependant tous les rationnels ne sont pas éléments de $\mathbb{Z}_p$, $\frac{1}{p}$ n'étant par exemple jamais inclus dans $\mathbb{Z}_p$.
\end{remarque}

\subsection{Nombres \texorpdfstring{p}{$p$}-adiques}

\begin{definition} Nombres $p$-adiques

	On définit l'ensemble $\Qp$ des nombres $p$-adiques comme $\mathbb{Z}_p \left[ \frac{1}{p} \right] $.   
\end{definition}

Un nombre $p$-adique $x$ s'écrit alors comme une somme de la forme $x = \sum \limits_{i=k}^{\infty} x_{i} p^i$ avec $k \in \mathbb{Z}$ et les $x_{i}$ compris entre $0$ et $p-1$. Si $k<0$ on écrira plus couramment $x = \ldots x_i \ldots x_1 x_0 , x_{-1}\ldots x_{k}$.

\begin{propriete}
	$\mathbb{Q}_{p}$ est un corps qui étend les opérations de $\mathbb{Z}_p$.
\end{propriete}
\textit{Preuve :} Voir \todo{l'annexe}

\todo{exemple d'opérations dans $\mathbb{Q}_{p} $ } 
\begin{corollaire}
	Le corps $\mathbb{Q}$ des rationnels est un sous-corps de $\mathbb{Q}_{p} $.
\end{corollaire}

Ce dernier résultat permet de construire de manière assez élémentaire des éléments de $\mathbb{Q}_{p}$ qui ne sont pas des entiers $p$-adique.

\subsection{Valuation et norme}

	\todo{Petit paragraphe introducif} 
On définit la valuation $p$-adique dans $\mathbb{Z}$ $\val^{\mathbb{Z}}:\mathbb{Z}\to \mathbb{N}\cup \{+\infty\}  $ comme l'application qui à 0 associe $+\infty$ et à un entier $a$ non nul associe le plus grand entier naturel $k$ tel que $p^k | a$% ou de façon équivalente en considérant $\sum \limits_{i=1}^{n} a_{i} p^i$ la décomposition de $a$ en base $p$, la valuation $p$-adique de $a$ est le plus petit $a_{i}$ non nul.

La valuation $p$-adique s'étend ensuite aux nombres rationnels en une application $\val^{\mathbb{Q}} : \mathbb{Q} \to \mathbb{Z}\cup \{+\infty\}   $ en définissant pour tout $r \in \mathbb{Q}$  $\val^{\mathbb{Q}} \left( r \right) = \val^\mathbb{Z}(a)- \val^\mathbb{Z}\left( b \right) $ avec $a,b \in \mathbb{Z} \times \mathbb{N}^*$ tels que $r=\frac{a}{b}.$

La valuation $p$-adique s'étend alors également à $\mathbb{Q}_p$ depuis $\mathbb{Q}$ comme suit :
\begin{definition} Valuation $p$-adique

	On appelle valuation $p$-adique l'application $\val: \mathbb{Q}_p \to \mathbb{Z}\cup \{+\infty\}  $ qui à un nombre $p$-adique $x$ associe $\max \{k \in \mathbb{Z}\cup \{+\infty\}| x\in p^k \mathbb{Z}_p\}$. 
\end{definition}
Une manière simple de visualiser la valuation d'un nombre $p$-adique est de compter la "distance à la virgule".

En effet, la valuation d'un entier $p$-adique correspond au nombres de $0$ à la fin de son écriture décimale \todo{p-imale ?} et pour un nombre $p$-adique non entier il s'agit de l'opposé nombre de décimales \todo{p-imales ?} après la virgule. Par exemple, $\val\left( \ldots 2413000 \right) = 3$ et $\val\left( \ldots 251,24 \right) = -2$.

Le principal intérêt qu'offre la notion de valuation pour le sujet développé ici est qu'elle permet de définir une notion de positivité dans un corps qui n'est pas totalement ordonnable \todo{définition peut-être en footnote ?}. À cet effet on introduira la notation suivante :
\begin{notation}
	Pour tout élément $x \in \mathbb{Q}_{p} $, on dit que $x$ est \textit{positif} et on note $x\ge 0$ si $\val\left(x\right)\ge 0$. On en induit alors les notations $x> 0$, $x\le 0$ et $x<0$.  
\end{notation}

        On évitera la notation $x\ge y$ qui pourrait laisser penser de manière trompeuse que $x\ge y \Rightarrow x-y\ge 0$\footnote{Par exemple, $\val(\ldots11,11) \ge \val(\ldots00,01) $ mais $\val(\ldots11,11 - \ldots00,01) = \val( \ldots 11,1) < 0$}.

\begin{propriete}
	La valuation $p$-adique possède les propriétés suivantes, pour tous $x$ et $y$ appartenant à $\mathbb{Q}_{p} $ :   
	\begin{enumerate}
		\item $\val(x+y) \ge \min\left( \val\left( x \right), \val\left( y \right)  \right) $ 
		\item $\val\left( xy \right) = \val (x) + \val( y)$ 
	\end{enumerate}
\end{propriete}
\textit{Preuve :} \todo{annex ?}  
\todo{Demander si mettre des exercices dans un rapport de stage c'est bien vu}

Ces propriétés permettent alors de munir $\mathbb{Q}_{p} $ d'une valeur absolue \footnote{c'est-à-dire une norme sur $\mathbb{Q}_{p} $ vu comme $\mathbb{Q}_{p} $-espace vectoriel} que l'on définira comme suit:

\begin{definition} Valeur absolue $p$-adique

	On appelle valeur absolue $p$-adique l'application 
\begin{align*}
|\cdot|_p : \mathbb{Q}_{p} & \longrightarrow \mathbb{R}^*_+\\
x & \longmapsto p^{-\val\left(x\right)} 
\end{align*}
\end{definition}

\begin{propriete}
	$\left| \cdot  \right|_p$ est une valeur absolue sur $\mathbb{Q}_{p}$ 
\end{propriete}
\textit{Preuve :} \todo{l'annexe pour changer}

On remarque en particulier d'après \todo{lien vers la prop} que pour tous $x,y \in \mathbb{Q}_{p}, \left|x+y\right|_p \le \max\left( x,y \right)$. Ce qui en fait un espace non archimédien \footnote{c'est-à-dire que $\mathbb{N}$ est borné dans $\left( \mathbb{Q}_{p}, \left| \cdot \right|_p \right) $} et rend la géométrie $p$-adique très différente du cas réel peu intuitive. Ce qui explique le manque de figure et d'explications par le dessin dans la suite de ce rapport.

On terminera cette section en discutant la proposition suivante, qui est d'une importance cruciale puisqu'elle offre une caractérisation simple de la positivité.

\begin{proposition}
	Soit $x \in \mathbb{Q}_{p} $. Les trois propriétés suivantes sont équivalentes 
	\begin{enumerate}[label= \textit{\roman*}.]
		\item $x \in \mathbb{Z}_p$
		\item $\val\left(x\right)\ge 0$
		\item $\left| x \right|_p\le 1$
	\end{enumerate}
\end{proposition}

\textcolor{red}{ On dira alors indistinctement qu'un nombre $x$ est un entier, est un élément de la boule unité ou est positif (conformément à \todo{lien vers la notation}).}

\textit{ Preuve de la propriété : } L'équivalence entre $ii$. et $iii$. découle directement de la définition de $\left| \cdot  \right|_p$. Puis on conclut en remarquant que $x \in \mathbb{Z}_p = p^0 \mathbb{Z}_p$ si et seulement si $\val\left(x\right)\ge 0$ c'est-à-dire $i. \iff ii.$.

### 2023-07-12 rapport/polyhedra.tex
Second commit

@@
-\partie{1}{vendredi 16 juin 15:00}{Polyèdres convexes $p$-adiques }
+\section{Polyèdres convexes \texorpdfstring{$p$}{p}-adiques}
 \begin{notation}
-	Pour tout élément $x$ de $ \Qp$ on note $x\ge 0$ et on dit que $x$ est \textit{positif} si $\val(x) \ge 0$ c'est à dire si $x \in \Zp$.
-On induit à partir de cette notation les définitons de $x\le 0$, $x>0$ et $x<0$.
 
-	Similairement, pour toute matrice $M$ à coefficient dans $\Qp$ on note $M\ge 0$ et on dit que $M$ est \textit{positive} si tous les coefficients de $M$  sont positifs, c'est à dire si $M \in M_n\left( \Zp \right) $ .
+	Similairement à, pour toute matrice $M$ à coefficient dans $\Qp$ on note $M\ge 0$ et on dit que $M$ est \textit{positive} si tous les coefficients de $M$  sont positifs, c'est à dire si $M \in M_n\left( \Zp \right) $ .
 On infère également les notation $M\le 0$, $M>0$ et $M<0$.
@@
 
-\begin{remarque}
-	On évitera la notation $x\ge y$ qui pourrait laisser penser de manière trompeuse que $x\ge y \Rightarrow x-y\ge 0$\footnote{Par exemple, $\ldots11,11 \ge \ldots00,01 $ mais $\ldots11,11 - \ldots00,01 = \ldots 11,1 < 0$}.
-\end{remarque}
-\section{Polyèdres convexes \texorpdfstring{$p$}{p}-adiques}
 \subsection{Matrices symétriques positive}
@@
 
-\hfill \ensuremath{\Box}
-
+\hfill \qedsymbol
 \begin{remarque}
 
-	La preuve de la proposition précédente montre qu'il suffit en réalité que les mineurs principaux de taille au plus $2$ aient une valuation positive (ou soient éléments de $\Zp$) ce qui correspond à la définition de matrice semi-définie positive sur le semi-corps tropical développée par .
+	La preuve de la proposition précédente montre qu'il suffit en réalité que les mineurs principaux de taille au plus $2$ aient une valuation positive (ou soient éléments de $\Zp$) ce qui correspond à la définition de matrice semi-définie positive sur le semi-corps tropical développée par Allamigeon, Gaubert et Skorma dans \cite{allamigeon_tropical_2020} .
 Ce n'est toutefois pas la définition qui sera choisie ici, pour des raisons développées en partie \hyperlink{subsection.1.2}{1.2}.
@@
 	\item compact
-	\item convexe au sens de Monna[nsvqkbdbvujezvbqevb]
-
+	\item convexe au sens de \parencite{monna_mo58_1958}  
 \end{enumerate}
@@
 Quand à $v.$ c'est une conséquence directe de la convexité de $\Zp$ et $S_n\left( \Qp \right) $.
+
+\todo{$\Pn$ est un cône $p$-adique pour la définition :Soit $\mathbb{E} $ un $\mathbb{Q}_{ p } $ espace vectoriel $C \subset \mathbb{E} $ est un cône si pour tout $x \in C$ et $\lambda \ge 0 $ $\lambda x \in C$.
+La preuve pour $ \Pn$ est assez triviale et pour $S_n^+\left( \mathbb{Q}_p \right)$ elle est laissée en exercice au lecteur}
 \subsection{Polyèdres convexes \texorpdfstring{$p$}{p}-adiques}
@@
 \begin{propriete}
-	Un polyèdre $p$-adique convexe est convexe au sens de Monna $[la so\bigcup_{\bigcup_{u\bigcup_{uu\bigcup_{uu\bigcup_{uu\bigcup_{uuu\bigcup_{uuuu\bigcup_{uuuuu\bigcup_{uurce} } } } } } } } }]$ 
+	Un polyèdre $p$-adique convexe est convexe au sens de \cite{monna_mo58_1958}.  
 \end{propriete}
@@
 \textit{Preuve :} Provient immédiatement du fait qu'un polyèdre s'écrit comme intersection d'ensemble convexe.
+
+\begin{ex}
+	La boule unité pour la norme infinie est un polyèdre.
+En effet, considérons le polyèdre défini par l'intersection de $S_n\left( \mathbb{Q}_{ p }  \right) $ avec le plan linéaire induit par les matrices $E_k$, k=1\ldots n, de $S_n\left( \Zp \right) $ telles que le seul coefficient non nul de $E_k$ soit le k-ième coefficient diagonal lequel est égal à $1$ .
+On observe que pour tout $x_1,\ldots,x_n \in \mathbb{Q}_{ p } ^n$, $\sum x_k E_k \ge 0$ si et seulement si $x_1,\ldots,x_s \in \mathbb{Z}_{ p }^n $ i.e.
+si et seulement si $\|(x_1,\ldots,x_n)\|_\infty \le 1$.
+
+\end{ex}
+
+\subsection{Résolution \texorpdfstring{p}{$p$}-adique de la programmation linéaire}
+
+Dans ce paragraphe, il sera étudié une forme équivalente du problème de programmation linéaire, appelée \textit{programmation linéaire $p$-adique}.
+Lequel consiste simplement à minimiser la norme $p$-adique d'une application linéaire sur un polyèdre $p$-adique.
+
+	Du fait des natures profondément différentes des polyèdres $p$-adiques et du cas réel, les techniques classiques de résolution sont mises à mal.
+Il est effet complexe d'appliquer la méthode du simplexe à un ensemble sans frontière ou des techniques d'analyse convexe dans un espace sans notion de convexité.
+Il convient donc alors de développer de nouvelles techniques pour résoudre ces problèmes.
+C'est ce qui est proposé dans cette section, qui présente un algorithme en $O(n^3)$ \todo{vérifier que c'est améliorable} pour résoudre le problème de la programmation linéaire en $p$-adique.
+
+	Cet algorithme est centré sur l'utilisation de la forme normale de Smith d'une matrice, dont seul la définition et quelques remarques sont présenté dans cette section, les preuves des résultats présentés ici ainsi que d'autres résultats sont disponible en annexe.
+\todo{faire le lien (et l'annexe)}
+i
+
+On appelle programmation linéaire $p$-adique le problème :
+\begin{equation}
+	  \tag{PLp}
+\begin{matrix}
+	\text{Minimiser } |c.x|_p \text{ tel que }\\
+	Ax + b \ge 0
+ \end{matrix}
+	    \label{eqn:Proglinp}
+\end{equation}
+
+avec $x$ le vecteur de taille $n$ que l'on fait varier, $c$ un vecteur de taille $n$ représentant le coût, $A$ une matrice de taille $m \times n $ et $b$ un vecteur de taille $m$.
+
+\todo{la transition}
+
+\begin{definition}
+	Forme Normale de Smith
+
+	Pour toute matrice $M \in \mathcal{M}_{m,n}\left( \mathbb{Q}_{ p }  \right) $ il existe une unique matrice $S$ de $\mathcal{M}_{m,n}\left( \mathbb{Q}_{ p }  \right) $ diagonale, dont les coefficients sont triés par valuation croissante et telle que
+	\[
+		M = P^{-1} S Q
+	\]
+ avec $P \in \mathcal{G}L_m\left( \mathbb{Z}_p \right)$ et $ Q \in \mathcal{G}L_n\left( \mathbb{Z}_p \right)$. La matrice $S$ est appelée forme normale de Smith de $M$.
+\end{definition}
+
+\todo{donner un exemple} 
+\begin{remarques}
+~
+
+	\begin{enumerate}[label=\roman*.]
+		\item Les coefficients de la forme normale de Smith sont uniques à chaque matrice et sont appelés \textit{facteurs invariants de Smith} ou, plus simplement, \textit{invariants de Smith}.
+		\item La valuation $p$-adique du premier coefficient de la forme normale de Smith d'une matrice $M \in \mathcal{M}_n \left( \Qp \right) $ est égale au minimum des valuation des termes de $M$.
+		\item En particulier, la forme normale de Smith d'une matrice de $\mathcal{M}_n \left( \mathbb{Z}_p \right) $ est à coefficients dans $\mathbb{Z}_p$ .
+		\item Seuls les $r = \text{rang} M$ premiers coefficients diagonaux de $S$ sont non nuls.  
+	\end{enumerate}
+
+\end{remarques}
+
+Avant de pouvoir utiliser la forme de normale de Smith pour résoudre \ref{eqn:Proglinp}, il nous faut démontrer le lemme suivant:
+
+\begin{lemme}
+	Pour tous $z \in \mathbb{Q}_{ p } ^n$ et $M \in \mathcal{M}_{m,n}\left( \mathbb{Q}_{ p }  \right)  $ si $z\ge 0$ et $M\ge 0$ alors $Mz\ge 0$.  
+\end{lemme}
+\textit{Preuve :} Pour tous $z \in \mathbb{Q}_{ p } ^n$ et $M \in \mathcal{M}_{m,n}\left( \mathbb{Q}_{ p }  \right)  $,  $z\ge 0$ et $M\ge 0$ si et seulement si  $M$ et $z$ sont à coefficients dans $\mathbb{Z}_p$, or les coefficients de $Mz$ s'écrivant comme sommes et produits de coefficients de $M$ et $z$, on a $Mz \in \mathbb{Z}_p^m$ i.e.
+$Mz\ge 0$.
+\hfill\qedsymbol
+
+En mettant alors la matrice $A$ de \ref{eqn:Proglinp} sous sa forme normale normale de Smith il vient que résoudre \ref{eqn:Proglinp} revient à résoudre :
+
+\begin{equation}
+	  \tag{PLp'}
+\begin{matrix}
+	\text{Minimiser } |c'.y|p \text{ tel que }\\
+	Sy + b' \ge 0
+ \end{matrix}
+	    \label{eqn:Proglinp2}
+\end{equation}
+où $b' = Pb$, $c' = cQ$, $S$ est la forme normale de Smith de $A$ et $A = P S Q$ avec $P \in \mathcal{G}L_m\left( \mathbb{Z}_p \right)$ et $ Q \in \mathcal{G}L_n\left( \mathbb{Z}_p \right)$.
+
+Il en vient immédiatement plusieurs résultats:
+\begin{enumerate}
+	\item $x^*$ est une solution admissible de \ref{eqn:Proglinp} si et seulement si $y^* := Q^{-1} x$ est une solution admissible de \ref{eqn:Proglinp2}
+	\item \ref{eqn:Proglinp2} possède des solutions admissible si et seulement si les $m-r$ coefficients de $Pb$ sont non nuls, où $r$ le rang de $S$.     
+	\item Si les $m-r$ derniers coefficients de $cQ$ sont non nuls \ref{eqn:Proglinp2} n'est pas borné et n'admet donc pas de solution.   
+\end{enumerate}
+
+Il sort de ces remarques que si les $m-r$ derniers coefficients de $b'$ et de $c'$ ne sont pas tous nuls, le problème n'admet pas de solution.
+Sinon on peut réduire la problème en ne considérant que les $r$ premiers coefficients de $y, b', c'$ et la sous matrice de $S$ composée des $r$ premières lignes et colonnes et dont les coefficients sont alors les exactement les facteurs invariants de Smith non nuls.
+L'ensemble $Adm$ des solutions admissible s'écrit alors comme l'ensemble des vecteurs $y \in \mathbb{Q}_{ p } ^n$ vérifiant $
+\forall 1 \le i\le r \ s_i y_i + b'_i \in \mathbb{Z}_p$ c'est-à-dire vérifiant :
+
+\[ \boxed{ 
+\forall 1 \le i\le r \ y_i \in -\frac{b'_i}{s_i} + \frac{1}{s_i} \mathbb{Z}_p
+}.\]
+
+Résoudre \ref{eqn:Proglinp2} revient donc à minimiser $|c'.y|_p$ sur $Adm$.
+Or l'image de $Adm$ par $y \mapsto c'y$ est $\sum_{i=1}^r -c'_i.\frac{b'_i}{s_i} + \sum_{i=1}^r\left( \frac{c_i}{s_{i}} \mathbb{Z}_p \right)$ qui se réécrit :
+$$c'Adm = \lambda_0 + p^{v_0} \mathbb{Z}_p$$
+où $\lambda_0 = \sum\limits_{i=1}^r -c'_i.\frac{b'_i}{s_i}$ et $v_{0} = \min\limits_{1\le i\le r} \val \frac{c'_{i}}{s_{i}} $.
+
+Ainsi, deux cas apparaissent.
+Soit $\val( \lambda_0) < v_0$ auquel cas le minimum de $y\mapsto |c'.y|_p$ sur $Adm$ est atteint en n'importe quel point de $Adm$ et vaut $| \lambda_0|_p$.
+Soit $\val\left( \lambda_0 \right) \ge v_0$, auquel cas $\lambda_0 \in p^{v_0} \mathbb{Z}_p$ et le minimum vaut $p^{-v_0} $ et est atteint en tous les points $y$ de $Adm$ tels que $\left|\sum \limits_{1\le i\le r} y_{i}\right|_p = 1$.

### 2023-07-12 rapport/proglin.tex
Second commit

\section{Résolution de la programmation linéaire \texorpdfstring{p}{$p$}-adique}

\begin{algorithm}
\caption{Un joli algorithme}
\begin{algorithmic}
\REQUIRE{habiter près des montagnes}
\REPEAT
 \IF{il fait beau}
  \STATE faire une randonnée
 \ELSE[il fait moche]
  \STATE résoudre P $\neq$ NP
 \ENDIF
\UNTIL{foulure de cheville}
\ENSURE{bobo}
\end{algorithmic}
\end{algorithm}

### 2023-07-12 rapport/spectrahedra.tex
Second commit

@@
-\partie{2}{mardi 20 juin 11:00}{Spectraèdres $p$-adiques }
-\newcommand\mat{matrice symétrique semie-définie positive } 
-\newcommand\Mat{Matrice symétrique semie-définie positive }
-\newcommand\mats{matrices symétriques semie-définies positives }
-\newcommand\Mats{Matrices symétriques semie-définies positives }
+\newcommand\mat{matrice semi-définie positive } 
+\newcommand\Mat{Matrice semi-définie positive }
+\newcommand\mats{matrices semi-définies positives }
+\newcommand\Mats{Matrices semi-définies positives }
 
@@
 Ce paragraphe tend à fournir un définition de la notion de \mat sur les corps $p-$adiques pour en déduire une définition de spectraèdre qui serait pertinente sur un corps non-archimédien. 
+La première étape pour définir un spectraèdre est de définir un équivalent des matrices symétriques définies positives.
+Sans théorème spectrale et le produit scalaire n'étant qu'une forme bilinéaire "banale" (ni positive ni définie), la symétrie est en $p$-adique parfaitement inutile et ne sera pas exigé.
+De plus, se par le manque cruel du théorème spectral la plupart des caractérisations des matrices symétriques semi-définies positives peinent à faire sens en $p$-adique.
+Il a donc été choisi de définir les \mats \footnote{notez l'absence du mot symétrique}comme les matrices à valeurs propres positives.
+Or là un second problème se pose : $\mathbb{Q}_{p} $ n'est pas algébriquement clos et les matrices $\mathcal{M}_n\left( \mathbb{Q}_{p}  \right) $ peuvent donc avoir des valeurs propres hors de $\mathbb{Q}_{p}$.
+Ce problème sera réglé en étendant la valuation $p$-adique aux extensions de $\mathbb{Q}_{p} $.
+
+\subsection{Clôture algébrique $p$-adique \texorpdfstring{p}{$p$}-adique }
+
+\begin{definition}
+	On appelle \textit{extension de corps} d'un corps $\mathbb{K}$ tout corps $\mathbb{L}$ muni d'un morphisme de corps injectif de $\mathbb{K}$ dans $\mathbb{L}$.
+On note $\mathbb{L}/\mathbb{K}$ le fait que $\mathbb{L}$ soit une extension de $\mathbb{K}.$
+\end{definition}
+
+\begin{definition}
+	Un corps $\mathbb{K}$ est dit algébriquement clos si tout polynôme $P\in \mathbb{K}[X]$ de degré au moins $1$ possède une racine dans $\mathbb{K}$.
+\end{definition}
+
+\begin{proposition}
+	$\mathbb{Q}_{p} $ n'est pas algébriquement clos.
+\end{proposition}
+\textit{Preuve :} Le polynôme $X^2 - p$ n'a pas de racine dans $\mathbb{Q}_{p}$ \hfill \qedsymbol.
+
+\begin{definition}
+	On appelle clôture algébrique l'unique (à isomorphisme près) corps $\mathbb{L}$ tel que tout élément de $\mathbb{L}$ est racine d'un polynôme de $\mathbb{K}[X]$ et $\mathbb{L}$ est algébriquement clos.
+\end{definition}
+
+On notera $\overline{\mathbb{Q}_{p} }$ la clôture algébrique de $\mathbb{Q}_{p}$, il est alors possible d'y étendre la valuation $p$-adique comme suit :
+
+\begin{definition}
+	On définit la valuation $p$-adique sur $\overline{\mathbb{Q}_{p} }$ comme 
+\begin{align*}
+	\val : \overline{\mathbb{Q}_{p}} & \longrightarrow \mathbb{Q}\cup \{+\infty\} \\
+x & \longmapsto \val^{\mathbb{Q}_{p} } \left(a\right)/d
+\end{align*}
+	où $d$ et $a$ sont respectivement le degré et le terme constant du polynôme minimal de $x$.
+\end{definition}
+
+On retrouve alors une notion de positivité dans l'extension de corps et étendra à $\overline{\mathbb{Q}_{p}} $ la notation $x\ge 0$ si et seulement si $\val\left(x\right)\ge 0$.
+Il n'est cependant informatiquement pas très pratique de travailler dans $\overline{\mathbb{Q}_{p} }$ qui est n'est pas une extension finie de $\mathbb{Q}_{p} $ %\footnote{c'est-à-dire $\overline{\mathbb{Q}_{p} }$ est un $\mathbb{Q}_{p}$-espace vectoriel de dimension infinie }.
+On essayera donc de trouver des caractérisations permettant de savoir plus simplement si un polynôme est à racines positives, ce qui sera fait dans la prochaine section.
+
 \subsection{\Mats}
@@
 \begin{definition}
-	On appelle \mat toute matrice $M \in S_n\left( \Qp \right) $ dont toutes les valeurs propres sont de valuation positive ou nulle[lien du pragarâgre avec les extesnions de corps lolololololololol].
+	On appelle \mat toute matrice $M \in \mathcal{M}_n\left( \Qp \right) $ dont toutes les valeurs propres sont de valuation positive ou nulle.
 
-	On note $S_n^+\left( \mathbb{Q}_p \right)$ l'ensemble des \mats.
+	On note $ \mathcal{M}_n^+\left( \mathbb{Q}_p \right)$ l'ensemble des \mats.
 \end{definition}
@@
 \begin{consequence}
-	$\Pn \subset S_n^+\left( \mathbb{Q}_p \right)$ 
+	$\Pn \subset \mathcal{M}_n^+\left( \mathbb{Q}_p \right)$ 
 \end{consequence}
@@
 Ainsi pour $M = \begin{pmatrix} 5 + \frac{3}{5} & \frac{4}{5} \\ \frac{4}{5} & -\frac{3}{5} \end{pmatrix} $, on a $\chi_M = X^2  - 5 X - 4$.
-Or une fois $M$ plongé dans $\mathbb{Q}_5$ on a $\chi_M \in \mathbb{Z}_5[X]$ donc $M \in S_2^+\left( \mathbb{Q}_5 \right)$ or aucun des coefficients de $M$ n'est dans $S_2^+\left( \mathbb{Q}_5 \right)$
-
+Or une fois $M$ plongé dans $\mathbb{Q}_5$ on a $\chi_M \in \mathbb{Z}_5[X]$ donc $M \in S_2^+\left( \mathbb{Q}_5 \right)$ or aucun des coefficients de $M$ n'est dans $\mathbb{Z}_5 $
 \end{remarque}
 
-\note{vérifier si le fait qu'une matrice snp soit soit positive ou non est lié à la présence ou non de racine uniquement dans $\mathbb{Z}_p$ }.
+	\todo{probablement pas nécessaire ira peut-être en annexe} 
+\begin{propriete}
+	L'ensemble $S_n^+\left( \mathbb{Q}_p \right)$  est :
+	\begin{enumerate}[label = \textit{\roman*}.]
+		\item ouvert
+		\item fermé
+		\item un cône
+	\end{enumerate}
+\end{propriete}
+
+\textit{Preuve :}  
+Montrons tout d'abord que $\Zp[X]$ est fermé et ouvert dans $\mathbb{Q}_{ p }[X] $ muni de la norme infinie $\|.\|_\infty : P = \sum_{k=1}^{n} a_k X^k \to \sup |a_k|_p$.
+
+Soit $P \in \Zp[X]$.
+On peut alors montrer que la boule ouverte de centre $P$ et de rayon $1$ est incluse dans $\Zp[X]$.
+Pour ce faire on considère $Q \in B_{o}\left( P,1 \right)_\infty $ et on remarque que cela signifie que $\|Q-P\|_\infty \le 1$ c'est-à-dire $Q-P \in \Zp[X]$.
+On a donc $Q = P + P-Q \in \Zp[X]$.
+$\Zp[X]$ est donc ouvert.
+
+Maintenant soit $P \in \mathbb{Q}_{ p } [X]^c$ et $Q \in B_o\left( P, 1 \right) $.
+On note $P = \sum_{k=1}^{n} a_k X^k$ et $Q = \sum_{k=1}^{n} a_k X^k$.
+On dispose alors de $i in \left\{  1,\ldots,n \right\} $ tel que $|a_{i}|_p >1$ et $a_i + b_{i} \in \Zp$ (car $P-Q \in \Zp$).
+Donc on a nécessairement $|b_i|_p = |a_i|_p > 1$ et $Q \in Z_p[X]^c$.
+Donc $\Zp[X]^c$ est ouvert et $\Zp[X]$ est fermé.
+
+On montre alors $i.$ et $ii.$ grâce à $\Pn = \chi^{-1}( \Zp[X]) $ ou $\chi$ est l'application qui a une matrice associe son polynôme caractéristique qui est continue car polynomiale en les coefficients de la matrice.
+
+Le $iii$. est laissé en exercice au lecteur. 
+\input{convexemple.tex}
+
+\subsection{Zoologie Spectraèdrique}
+p

### 2023-07-20 rapport/complpadic.tex
3rd commit I think ?

\section{Complément sur les corps \texorpdfstring{$p$}{p}-adique}
\label{cpadic}

Cette section de l'appendice présente la plupart des preuves qui n'ont pas été traitées en section \ref{padic} ainsi que quelques compléments sur les nombres $p$-adique pour en avoir une meilleur appréhension.

\begin{proof} \hypertarget{qpcorpspreuve}{Proposition \ref{qpcorps}} 
\end{proof}

\begin{proof} \hypertarget{propvalpreuve}{Propriété \ref{propval} }

\end{proof}

### 2023-07-20 rapport/padic.tex
3rd commit I think ?

@@
-\section{Introduction aux nombres \texorpdfstring{p}{$p$}-adiques}
+\section{Introduction aux nombres \texorpdfstring{$p$}{p}-adiques}
+\label{padic}
 
 On se contentera dans cette section d'une description très élémentaire des différentes définitions et propriétés des nombres $p$-adiques.
-La plupart des preuves relative à cette section ainsi que de plus amples informations sont disponibles en annexe \todo{l'annexe}.
+La plupart des preuves relatives à cette section ainsi que de plus amples informations sont disponibles en \ref{cpadic}.
 Cette section est très largement inspiré du cours de Xavier Caruso \parencite{caruso_computations_2017} que l'on invite d'ailleurs à aller consulter pour une vision plus complète mais très largement compréhensible.
@@
 
-\subsection{Entiers \texorpdfstring{p}{$p$}-adique} 
+\subsection{Entiers \texorpdfstring{$p$}{p}-adique} 
 \begin{definition}{Entier $p$-adique }
@@
 \]
-ou les $a_i$ sont des entiers compris entre $0$ et $p-1$.
+où les $a_i$ sont des entiers compris entre $0$ et $p-1$.
 
@@
 		\item[$\circ$]  On note $\Zp$ l'ensemble des entier $p-$adiques.
-		\item[$\circ$] Par commodité on notera $\ldots a_n\ldots a_1 a_0$ l'entier $p$-adique $\sum a_{i}p^i$ 
+		\item[$\circ$] Par commodité on notera $\overline{\ldots a_n\ldots a_1 a_0}^p$ ou plus simplement $\ldots a_n \ldots a_1a_0$ l'entier $p$-adique $\sum a_{i}p^i$ 
 \end{itemize}
@@
 
-\begin{ex}
+\begin{ex} \
 
-	Ainsi les sommes $\sum\limits_{i=0}^{ \infty} p^i = \ldots1111111$ ou $\sum\limits_{i=0}^{ \infty} (i\ \text{mod}\ p) p^i = \ldots210(p-1)\ldots21 $ sont des entiers $p$-adiques parfaitement définis bien que ne convergeant pas dans le cas réel.
+	Ainsi les sommes $\sum\limits_{i=0}^{ \infty} p^i = \overline{\ldots1111111}^p$ ou $\sum\limits_{i=0}^{ \infty} (i\ \text{mod}\ p) p^i =\overline{ \ldots210(p-1)\ldots21}^p $ sont des entiers $p$-adiques parfaitement définis bien que ne convergeant pas dans le cas réel.
 \end{ex}
@@
 
-\begin{tabular}{lS}
+\begin{definition}
+	L'anneau $\mathbb{Z}$ des entiers relatifs s'identifie naturellement à un sous-anneau de $\mathbb{Z}_p$.
+\end{definition}
+\begin{table}[htpb]
+	\centering
+	\caption{Exemples d'opérations dans $\mathbb{Z}_p$}
+	\label{tab:op}
+	\begin{tabular}{cc }
+		\begin{tabular}[t]{lS}
      & \ldots34202243\\
@@
 \end{tabular}
-
-\begin{tabular}{lS}
+&  
+\begin{tabular}[t]{lS}
      & \ldots02243\\
@@
 \end{tabular}  
-
-\begin{propriete}
-	 $\mathbb{Z}$ est un sous-anneau de $\mathbb{Z}_p$. 	
-\end{propriete}
-\textit{Preuve :} Tout entier naturel $a$ admet une décomposition en base $p$ (qui est unique) i.e.
-s'écrit $a = \sum\limits_{i=0}^{n} a_{i}p^i$ avec $n = \left\lfloor \log_p a\right\rfloor$ et s'associe naturellement à l'élément $\ldots0000a_n\ldots a_0$ de $\mathbb{Z}_p$.
-Puis à tout entier négatif $b$ on associe l'opposé dans $\mathbb{Z}_p$ de $|b|$.
-Il n'est alors pas compliqué de vérifier que les opérations de $\mathbb{Z}_p$ restreintes à la projection de $\mathbb{Z}$ coïncident avec les opération dans $\mathbb{Z}$.
-\hfill \qedsymbol
-
+	\end{tabular}
+\end{table}
 \begin{remarque}
-	Si l'on a vu que les entiers au sens réel était des entiers $p$-adiques, certains entiers $p$-adique ont du sens en tant que nombre rationnels sans être des entiers relatifs, ainsi on a par exemple $\frac{1}{2} = \ldots 2223 \in \mathbb{Z}_5$.
+	Si l'on a vu que les entiers relatifs étaient des entiers $p$-adiques, certains entiers $p$-adique ont du sens en tant que nombre rationnels sans être des entiers relatifs, ainsi on a par exemple $\frac{1}{2} = \ldots 2223 \in \mathbb{Z}_5$.
 Cependant tous les rationnels ne sont pas éléments de $\mathbb{Z}_p$, $\frac{1}{p}$ n'étant par exemple jamais inclus dans $\mathbb{Z}_p$.
@@
 
-\subsection{Nombres \texorpdfstring{p}{$p$}-adiques}
+\subsection{Nombres \texorpdfstring{$p$}{p}-adiques}
 
@@
 
-	On définit l'ensemble $\Qp$ des nombres $p$-adiques comme $\mathbb{Z}_p \left[ \frac{1}{p} \right] $.   
+	On définit l'ensemble $\Qp$ des nombres $p$-adiques comme $\mathbb{Z}_p \left[ \frac{1}{p} \right] \footnote{Le lecteur habitué à travailler dans $R[[X]]$ y verra dans la construction de $\mathbb{Q}_{p} $ à partir de $\mathbb{Z}_p$ une ressemblance avec celle de $R(X)$ à partir de $R[[X]]$.
+De nombreux autres similitudes entres ces ensemble peuvent être trouvées mais nos éviterons de les faire apparaître afin de rester à un niveau élémentaire (à reformuler bien).}  $.
 \end{definition}
@@
 Un nombre $p$-adique $x$ s'écrit alors comme une somme de la forme $x = \sum \limits_{i=k}^{\infty} x_{i} p^i$ avec $k \in \mathbb{Z}$ et les $x_{i}$ compris entre $0$ et $p-1$.
-Si $k<0$ on écrira plus couramment $x = \ldots x_i \ldots x_1 x_0 , x_{-1}\ldots x_{k}$.
+Si $k<0$ on écrira plus couramment $x = \overline{\ldots x_i \ldots x_1 x_0 , x_{-1}\ldots x_{k}}^p$.
 
 \begin{propriete}
+\label{qpcorps} 
 	$\mathbb{Q}_{p}$ est un corps qui étend les opérations de $\mathbb{Z}_p$.
 \end{propriete}
-\textit{Preuve :} Voir \todo{l'annexe}
+\textit{Preuve :} Voir \hyperlink{qpcorpspreuve}{annexe}.
 
@@
 \end{corollaire}
-
+\todo{les personne habitués pourrait y voir une analogie avec la contruction de R[[X]} 
 Ce dernier résultat permet de construire de manière assez élémentaire des éléments de $\mathbb{Q}_{p}$ qui ne sont pas des entiers $p$-adique.
@@
 	\todo{Petit paragraphe introducif} 
-On définit la valuation $p$-adique dans $\mathbb{Z}$ $\val^{\mathbb{Z}}:\mathbb{Z}\to \mathbb{N}\cup \{+\infty\}  $ comme l'application qui à 0 associe $+\infty$ et à un entier $a$ non nul associe le plus grand entier naturel $k$ tel que $p^k | a$% ou de façon équivalente en considérant $\sum \limits_{i=1}^{n} a_{i} p^i$ la décomposition de $a$ en base $p$, la valuation $p$-adique de $a$ est le plus petit $a_{i}$ non nul.
+On définit la valuation $p$-adique dans $\mathbb{Z}$ $\val^{\mathbb{Z}}:\mathbb{Z}\to \mathbb{N}\cup \{+\infty\}  $ comme l'application qui à 0 associe $+\infty$ et à un entier $a$ non nul associe le plus grand entier naturel $k$ tel que $p^k | a$.% ou de façon équivalente en considérant $\sum \limits_{i=1}^{n} a_{i} p^i$ la décomposition de $a$ en base $p$, la valuation $p$-adique de $a$ est le plus petit $a_{i}$ non nul.
 
@@
 
-En effet, la valuation d'un entier $p$-adique correspond au nombres de $0$ à la fin de son écriture décimale \todo{p-imale ?} et pour un nombre $p$-adique non entier il s'agit de l'opposé nombre de décimales \todo{p-imales ?} après la virgule.
+En effet, la valuation d'un entier $p$-adique correspond au nombres de $0$ à la fin de son écriture décimale et pour un nombre $p$-adique non entier il s'agit de l'opposé nombre de chiffres $p$-adiques après la virgule.
 Par exemple, $\val\left( \ldots 2413000 \right) = 3$ et $\val\left( \ldots 251,24 \right) = -2$.
 
-Le principal intérêt qu'offre la notion de valuation pour le sujet développé ici est qu'elle permet de définir une notion de positivité dans un corps qui n'est pas totalement ordonnable \todo{définition peut-être en footnote ?}.
+Le principal intérêt qu'offre la notion de valuation pour le sujet développé ici est qu'elle permet de définir une notion de positivité dans un corps qui n'est pas totalement ordonnable \todo{i.e.}.
 À cet effet on introduira la notation suivante :
 \begin{notation}
-	Pour tout élément $x \in \mathbb{Q}_{p} $, on dit que $x$ est \textit{positif} et on note $x\ge 0$ si $\val\left(x\right)\ge 0$. On en induit alors les notations $x> 0$, $x\le 0$ et $x<0$.  
+
+	Pour tout élément $x \in \mathbb{Q}_{p} $, on dit que $x$ est \hypertarget{positif}{\textit{positif}} et on note $x\ge 0$ si $\val\left(x\right)\ge 0$.
+On en induit alors les notations $x> 0$, $x\le 0$ et $x<0$.
 \end{notation}
@@
 	\begin{enumerate}
+		\label{propval} 
 		\item $\val(x+y) \ge \min\left( \val\left( x \right), \val\left( y \right)  \right) $ 
@@
 \end{propriete}
-\textit{Preuve :} \todo{annex ?}  
-\todo{Demander si mettre des exercices dans un rapport de stage c'est bien vu}
+\textit{Preuve :} Voir \hyperlink{propvalpreuve}{annexe}.
 
-Ces propriétés permettent alors de munir $\mathbb{Q}_{p} $ d'une valeur absolue \footnote{c'est-à-dire une norme sur $\mathbb{Q}_{p} $ vu comme $\mathbb{Q}_{p} $-espace vectoriel} que l'on définira comme suit:
+Ces propriétés permettent alors de munir $\mathbb{Q}_{p} $ d'une valeur absolue que l'on définira comme suit:
 
 \begin{definition} Valeur absolue $p$-adique
+\label{vabs}
 
@@
 \end{align*}
+qui est une valeur absolue, c'est-à-dire, une norme compatible avec le produit.
 \end{definition}
 
-\begin{propriete}
-	$\left| \cdot  \right|_p$ est une valeur absolue sur $\mathbb{Q}_{p}$ 
-\end{propriete}
-\textit{Preuve :} \todo{l'annexe pour changer}
+\textit{Preuve :} Découle directement de \ref{propval}.
 
-On remarque en particulier d'après \todo{lien vers la prop} que pour tous $x,y \in \mathbb{Q}_{p}, \left|x+y\right|_p \le \max\left( x,y \right)$.
-Ce qui en fait un espace non archimédien \footnote{c'est-à-dire que $\mathbb{N}$ est borné dans $\left( \mathbb{Q}_{p}, \left| \cdot \right|_p \right) $} et rend la géométrie $p$-adique très différente du cas réel peu intuitive.
+On observera en particulier que, d'après \ref{propval}, pour tous $x,y$ éléments de $\mathbb{Q}_{p}$ on a l'inégalité $\left|x+y\right|_p \le \max\left( \left| x \right|_p,\left| y \right|_p \right)$.
+Ce qui en fait un corps non archimédien \footnote{c'est-à-dire tel que $\mathbb{N}$ est borné dans $\left( \mathbb{Q}_{p}, \left| \cdot \right|_p \right) $} et rend la géométrie $p$-adique très différente du cas réel peu et intuitive si l'on y est pas habituée.
 Ce qui explique le manque de figure et d'explications par le dessin dans la suite de ce rapport.
 
-On terminera cette section en discutant la proposition suivante, qui est d'une importance cruciale puisqu'elle offre une caractérisation simple de la positivité.
+On terminera cette section en discutant la proposition suivante, qui est d'une importance cruciale puisqu'elle offre une caractérisation simple de la positivité dans $\mathbb{Q}_{p}$.
 
@@
 
-\textcolor{red}{ On dira alors indistinctement qu'un nombre $x$ est un entier, est un élément de la boule unité ou est positif (conformément à \todo{lien vers la notation}).}
+\textcolor{red}{ On dira alors indistinctement qu'un nombre $x$ est un entier, est un élément de la boule unité ou est positif (conformément à \hyperlink{positif}{la notation définie précédemment}).}
 

### 2023-07-20 rapport/polyhedra.tex
3rd commit I think ?

@@
 
-	Similairement à, pour toute matrice $M$ à coefficient dans $\Qp$ on note $M\ge 0$ et on dit que $M$ est \textit{positive} si tous les coefficients de $M$  sont positifs, c'est à dire si $M \in M_n\left( \Zp \right) $ .
+	Pour toute matrice $M$ à coefficient dans $\Qp$ on note $M\ge 0$ et on dit que $M$ est \textit{positive} si tous les coefficients de $M$  sont positifs, c'est à dire si $M \in M_n\left( \Zp \right) $ .
 On infère également les notation $M\le 0$, $M>0$ et $M<0$.
@@
 	\item compact
-	\item convexe au sens de \parencite{monna_mo58_1958}  
+	\item convexe au sens de \parencite{monna_ensembles_1958}
 \end{enumerate}
@@
 \begin{propriete}
-	Un polyèdre $p$-adique convexe est convexe au sens de \cite{monna_mo58_1958}.  
+Un polyèdre $p$-adique convexe est convexe au sens de \cite{monna_ensembles_1958}.  
 \end{propriete}
@@
 
-\subsection{Résolution \texorpdfstring{p}{$p$}-adique de la programmation linéaire}
-
-Dans ce paragraphe, il sera étudié une forme équivalente du problème de programmation linéaire, appelée \textit{programmation linéaire $p$-adique}.
+\subsection{Résolution \texorpdfstring{$p$}{p}-adique de la programmation linéaire}
+\label{sectionalgo} 
+Dans ce paragraphe, il sera étudié une forme équivalente du problème de programmation linéaire, appelée \textit{programmation linéaire $p$-adique} (\ref{eqn:Proglinp}) .
 Lequel consiste simplement à minimiser la norme $p$-adique d'une application linéaire sur un polyèdre $p$-adique.
@@
 Il convient donc alors de développer de nouvelles techniques pour résoudre ces problèmes.
-C'est ce qui est proposé dans cette section, qui présente un algorithme en $O(n^3)$ \todo{vérifier que c'est améliorable} pour résoudre le problème de la programmation linéaire en $p$-adique.
+C'est ce qui est proposé dans cette section, qui présente un algorithme en $O(n^3)$ \todo{vérifier que c'est améliorable} pour résoudre le problème de la programmation linéaire en $p$-adique, dont une écriture en pseudo-code ainsi qu'une implémentation en \sage sont disponible en \ref{appendixalgo}.
 
-	Cet algorithme est centré sur l'utilisation de la forme normale de Smith d'une matrice, dont seul la définition et quelques remarques sont présenté dans cette section, les preuves des résultats présentés ici ainsi que d'autres résultats sont disponible en annexe.
-\todo{faire le lien (et l'annexe)}
-i
+	Cet algorithme est centré sur l'utilisation de la forme normale de Smith d'une matrice, dont seul la définition et quelques remarques sont présenté dans cette section, les preuves des résultats présentés ici ainsi que d'autres résultats sont disponible en \ref{smith}.
 
-On appelle programmation linéaire $p$-adique le problème :
+	On appelle \textit{programmation linéaire $p$-adique} le problème :
 \begin{equation}
@@
 
-avec $x$ le vecteur de taille $n$ que l'on fait varier, $c$ un vecteur de taille $n$ représentant le coût, $A$ une matrice de taille $m \times n $ et $b$ un vecteur de taille $m$.
+avec $x$ un vecteur de taille $n$ que l'on fait varier, $c$ un vecteur de taille $n$ représentant le coût, $A$ une matrice de taille $m \times n $ et $b$ un vecteur de taille $m$.
 
-\todo{la transition}
+La méthode choisie ici consiste à mettre la matrice $A$ sous forme normale de Smith, un factorisation classique en $p$-adique et qui permet de grandement simplifier le problème posé.
 
@@
 \begin{remarques}
-~
 
@@
 		\item En particulier, la forme normale de Smith d'une matrice de $\mathcal{M}_n \left( \mathbb{Z}_p \right) $ est à coefficients dans $\mathbb{Z}_p$ .
-		\item Seuls les $r = \text{rang} M$ premiers coefficients diagonaux de $S$ sont non nuls.  
+		\item Les $r = \text{rang} M$ premiers coefficients diagonaux de $S$ sont exactement ses coefficients non nuls.  
 	\end{enumerate}
@@
 \end{lemme}
-\textit{Preuve :} Pour tous $z \in \mathbb{Q}_{ p } ^n$ et $M \in \mathcal{M}_{m,n}\left( \mathbb{Q}_{ p }  \right)  $,  $z\ge 0$ et $M\ge 0$ si et seulement si  $M$ et $z$ sont à coefficients dans $\mathbb{Z}_p$, or les coefficients de $Mz$ s'écrivant comme sommes et produits de coefficients de $M$ et $z$, on a $Mz \in \mathbb{Z}_p^m$ i.e.
-$Mz\ge 0$.
-\hfill\qedsymbol
+\textit{Preuve :} $\mathbb{Z}_p$ est un anneau. \hfill\qedsymbol
 
@@
 
+\begin{remarques}
+
 Il en vient immédiatement plusieurs résultats:
@@
 	\item \ref{eqn:Proglinp2} possède des solutions admissible si et seulement si les $m-r$ coefficients de $Pb$ sont non nuls, où $r$ le rang de $S$.     
-	\item Si les $m-r$ derniers coefficients de $cQ$ sont non nuls \ref{eqn:Proglinp2} n'est pas borné et n'admet donc pas de solution.   
+	\item Si les $n-r$ tous derniers coefficients de $c'$ sont non nuls \ref{eqn:Proglinp2} n'est pas borné et n'admet donc pas de solution.   
 \end{enumerate}
 
-Il sort de ces remarques que si les $m-r$ derniers coefficients de $b'$ et de $c'$ ne sont pas tous nuls, le problème n'admet pas de solution.
-Sinon on peut réduire la problème en ne considérant que les $r$ premiers coefficients de $y, b', c'$ et la sous matrice de $S$ composée des $r$ premières lignes et colonnes et dont les coefficients sont alors les exactement les facteurs invariants de Smith non nuls.
+\end{remarques}
+
+\begin{propriete}
+	\begin{itemize}~
+
+		\item[$\circ$] Si les $m-r$ coefficients de $b'$ ne sont pas tous nuls alors il n'existe pas de $y \in \mathbb{Q}_{p} ^n$ tel que $A'y+b' \ge  0$.
+	\item[$\circ$] Si les $n-r$ coefficients de $c'$ ne sont pas tous nuls alors le problème n'est pas borné et n'admet donc pas de solution. \end{itemize} 
+\end{propriete}
+En ne considérant alors que les itérations du problème admettant des solutions on peut réduire le problème en ne considérant que les $r$ premiers coefficients de $y, b', c'$ et la sous matrice de $S$ composée des $r$ premières lignes et colonnes et dont les coefficients sont alors les exactement les facteurs invariants de Smith non nuls.
 L'ensemble $Adm$ des solutions admissible s'écrit alors comme l'ensemble des vecteurs $y \in \mathbb{Q}_{ p } ^n$ vérifiant $
@@
 
-\[ \boxed{ 
-\forall 1 \le i\le r \ y_i \in -\frac{b'_i}{s_i} + \frac{1}{s_i} \mathbb{Z}_p
-}.\]
+\begin{equation}
+	\forall 1 \le i\le r  y_i \in -\frac{b’_i}{s_i} + \frac{1}{s_i} \mathbb{Z}_p
+\end{equation}
 
 Résoudre \ref{eqn:Proglinp2} revient donc à minimiser $|c'.y|_p$ sur $Adm$.
-Or l'image de $Adm$ par $y \mapsto c'y$ est $\sum_{i=1}^r -c'_i.\frac{b'_i}{s_i} + \sum_{i=1}^r\left( \frac{c_i}{s_{i}} \mathbb{Z}_p \right)$ qui se réécrit :
+L'image de $Adm$ par $y \mapsto c'y$ est $\sum_{i=1}^r -c'_i.\frac{b'_i}{s_i} + \sum_{i=1}^r\left( \frac{c_i}{s_{i}} \mathbb{Z}_p \right)$ qui se réécrit :
 $$c'Adm = \lambda_0 + p^{v_0} \mathbb{Z}_p$$
@@
 Soit $\val( \lambda_0) < v_0$ auquel cas le minimum de $y\mapsto |c'.y|_p$ sur $Adm$ est atteint en n'importe quel point de $Adm$ et vaut $| \lambda_0|_p$.
-Soit $\val\left( \lambda_0 \right) \ge v_0$, auquel cas $\lambda_0 \in p^{v_0} \mathbb{Z}_p$ et le minimum vaut $p^{-v_0} $ et est atteint en tous les points $y$ de $Adm$ tels que $\left|\sum \limits_{1\le i\le r} y_{i}\right|_p = 1$.
+Soit $\val\left( \lambda_0 \right) \ge v_0$, auquel cas $\lambda_0 \in p^{v_0} \mathbb{Z}_p$ et le minimum vaut $p^{-v_0} $ et est atteint en tous les points $y$ de $Adm$ tels que $\val\left(\sum \limits_{1\le i\le r} y_{i}\right) = v_0$.

### 2023-07-20 rapport/proglin.tex
3rd commit I think ?

@@
-\section{Résolution de la programmation linéaire \texorpdfstring{p}{$p$}-adique}
+\section{Résolution de la programmation linéaire \texorpdfstring{$p$}{p}-adique} 
+\label{appendixalgo} 
+Cette section présente le pseudo-code ainsi qu'une implémentation en \sage de l'algorithme de la section \ref{sectionalgo}.
+\input{algo.tex}
 
 \begin{algorithm}
-\caption{Un joli algorithme}
-\begin{algorithmic}
-\REQUIRE{habiter près des montagnes}
-\REPEAT
- \IF{il fait beau}
-  \STATE faire une randonnée
- \ELSE[il fait moche]
-  \STATE résoudre P $\neq$ NP
- \ENDIF
-\UNTIL{foulure de cheville}
-\ENSURE{bobo}
+\caption{Résolution de la programmation $p$-adique}
+%\Entry Une matrice $A$ de taille $m \times n$, un vecteur $b$ de taille $m$ et un vecteur $c$ de taille $n$.
+\begin{algorithmic}[0]
+\State $S,P,Q$ = FormeNormaleDeSmith($A$)
+\State $r$ = rang($S$)
+\State $b' = P \times b$
+\State $c'$ = $c \times Q$
+\For{$i$ allant de $r+1$ à $m$}
+\If{$\val\left(b'[i] \right) < 0$}
+\State Pas de solution
+\EndIf
+\EndFor
+\For{$i$ allant de $r+1$ à $n$} 
+\If{$c'[i]\neq 0$}
+\State Le problème n'est pas borné
+\EndIf
+\EndFor
+\State $\tilde{c} =$Projection$\left( c', 1, r \right) $ \Comment On réduit le problème à un problème de taille $r$ 
+\State $\tilde{b} =$ Projection$\left(b', 1, r \right) $ 
+\State $\tilde{S} = $SousMatrice$\left( S, (1,r),(1,r) \right) $
+\State $\lambda_0 = \tilde{c}. S^{-1}. \tilde{b} $
+\State $v_0 = \min \left\{\val\left(z_{i}\right)| \left( z_1,\ldots,z_r \right) = \tilde{c}.S^{-1}  \right\}$
+
+\If{$\val\left( \lambda_0\right) < v_0$}
+\Return $\val\left( \lambda_0 \right)$
+\Else \Return $v_0$ \Comment Si l'on cherche à calculer la valuation maximale à la place il suffit de soulever une erreur au lieu de renvoyer $v_0$.
+\EndIf
 \end{algorithmic}
 \end{algorithm}
+
+Ou FormeNormaleDeSmith renvoie la forme normale de Smith de la matrice $A$ ainsi que les matrices $P$ et $Q$ telles que \todo{stick to a convention}.
+
+L'algorithme s'exécute en $O\left( n^3 \right) $

### 2023-07-20 rapport/realspectrahedra.tex
3rd commit I think ?

\section{Spectraèdres réels}

\newcommand\ssp{symétrique semi-définie positive}
\newcommand\ssps{symétriques semi-définies positives}
\newcommand\Ssp{Symétrique semi-définie positive}
\newcommand\Ssps{Symétriques semi-définies positives}

\subsection{définiion?}
\todo{trouver un nom}

\begin{definition}
	On appelle \emph{matrice symétrique semi-définie positive} toute matrice réelle symétriques et à valeurs propres positives ou nulles.
	On notera $\mathcal{S}_n^+\left(\mathbb{R}\right) $ l'ensemble de telles matrices et $M \succeq 0$ le fait que $M \in \mathcal{S}_n^+\left(\mathbb{R}\right)$.
\end{definition}

\begin{remarque}
	On remarquera que demander la symétrie, n'est, dans le cas réel, qu'un moyen de s'assurer d'obtenir des valeurs propres réelles grâce au théorème spectral.
\end{remarque}
\begin{propriete}
	L'ensemble $\mathcal{S}_n^+\left( \mathbb{R} \right) $ est un cône convexe fermé.
\end{propriete}

\begin{definition}
	On appelle \emph{spectraèdre} l'intersection de $\mathcal{S}_n^+\left(\mathbb{R}\right)$ avec un plan affine $\mathcal{L}$ de $\mathcal{S}_n\left(\mathbb{R}\right)$.
\end{definition}

En écrivant l'hyperplan $\mathcal{L}$ de $\mathcal{S}_n^+\left(\mathbb{R}\right)$ sous sa forme paramétrique \textit{i.e.} comme l'ensemble des matrices de la forme $A_0 + x_1 A_1 + \ldots x_s A_s$ pour $A_0,\ldots, A_s$ des matrices symétriques fixées on peut définir le spéctraèdre $\mathcal{S} = \mathcal{L} \cap \mathcal{S}_n^+\left(\mathbb{R}\right)$ comme $\mathcal{S} = \{A_0 + x_1A_1 + \ldots + x_s A_s \succeq 0| (x_1,\ldots,x_s) \in \mathbb{R}^s\} $. On identifie alors souvent ce dernier à sa préimage dans $\mathbb{R}^s$ $S = \{(x_1,\ldots,x_s) | A_0+ x_1A_1 + \ldots+ x_s A_s \succeq 0 \}. $
\todo{image + exemple}

\subsection{Programmation semi-définie positive}

On appelle alors programmation semi-définie le problème d'optimisation consistant à minimiser une application linéaire sur un spéctraèdre que l'on formulera comme :
\begin{equation}
	\tag{PSD}
	\begin{matrix}
		\text{Minimiser } c.x \text{ tel que}\\
		A_0 + \sum \limits_{i=1}^s x_{i}A_{i} \succeq 0
	\end{matrix}
	\label{Psd} 
\end{equation}

pour $A_0,\ldots, A_s$ des matrices symétriques fixées et $c$ un vecteur représentant le coût.

Ce problème se résout en temps polynomial en la taille des matrices grâce à des techniques d'optimisation convexe. \todo{exemples}

Si à première vue ce problème peut sembler très spécifique il n'en est rien et de nombreux autres problèmes se rapportent à celui-ci.

Le premier exemple étant que

### 2023-07-20 rapport/smith.tex
3rd commit I think ?

\section{Forme normale de Smith}
\label{smith} 
On revient dans cette partie sur la construction de la forme normale de Smith d'une matrice ainsi que sur les principaux résultats sur cette dernière. Ces résultats sont utilisé dans l'algorithme présenté en section \ref{sectionalgo}

\begin{propriete}
	Il existe une unique matrice $0$

\end{propriete}

\begin{proof}
i
\end{proof}

### 2023-07-20 rapport/spectrahedra.tex
3rd commit I think ?

@@
 
-\section{Spectraèdre \texorpdfstring{$p$}{p}-adiques } 
+\section{Spectraèdres \texorpdfstring{$p$}{p}-adiques } 
 Ce paragraphe tend à fournir un définition de la notion de \mat sur les corps $p-$adiques pour en déduire une définition de spectraèdre qui serait pertinente sur un corps non-archimédien. 
@@
 
-\subsection{Clôture algébrique $p$-adique \texorpdfstring{p}{$p$}-adique }
+\subsection{Clôture algébrique \texorpdfstring{$p$}{p}-adique } 
+Cette section présente quelques résultats élémentaires sur les extensions de corps $p$-adiques.
+La plupart des résultats présentés dans cette section étant soit classique et trouvable dans n'importe quel cours d'algèbre de niveau master soit élémentaires, peu de preuves y seront importés.
+On recommandera toutefois la lecture de la section 5 de \parencite{gouvea_p-adic_2003} pour plus d'information sur les extensions de corps $p$-adiques.
 
@@
 \end{definition}
+Une extension d'un corps $\mathbb{K}$ est grossièrement un corps contenant une copie du corps $\mathbb{K}$.
 
@@
 On retrouve alors une notion de positivité dans l'extension de corps et étendra à $\overline{\mathbb{Q}_{p}} $ la notation $x\ge 0$ si et seulement si $\val\left(x\right)\ge 0$.
-Il n'est cependant informatiquement pas très pratique de travailler dans $\overline{\mathbb{Q}_{p} }$ qui est n'est pas une extension finie de $\mathbb{Q}_{p} $ %\footnote{c'est-à-dire $\overline{\mathbb{Q}_{p} }$ est un $\mathbb{Q}_{p}$-espace vectoriel de dimension infinie }.
-On essayera donc de trouver des caractérisations permettant de savoir plus simplement si un polynôme est à racines positives, ce qui sera fait dans la prochaine section.
+Il n'est cependant informatiquement pas très pratique de travailler dans $\overline{\mathbb{Q}_{p} }$ qui est n'est pas une extension finie de $\mathbb{Q}_{p} $ \footnote{c'est-à-dire $\overline{\mathbb{Q}_{p} }$ est un $\mathbb{Q}_{p}$-espace vectoriel de dimension infinie }.
+On cherchera donc des caractérisations plus simples pour savoir si un polynôme est à racines positives, ce qui sera fait dans la prochaine section.
 
@@
 \subsection{Zoologie Spectraèdrique}
-p
+Dans le cas réel de nombreux ensembles convexes peuvent être représentés comme des spectraèdres ou des projections de spectraèdres, il a même été conjecturé que tous les ensembles semialgébriques \footnote{$i.e.$ les ensembles définis par des inégalités polynomiales} convexes soient des ombres de spéctraèdres \todo{lien machin}.
+Bien que cette conjecture ait ensuite été prouvée fausse \todo{le lien}, il n'en reste pas loin qu'un nombre important d'ensemble admettant une telle représentation garantisse sa flexibilité
+
+\begin{definition}
+	Couronnes
+
+	On appelle couronne tout ensemble $C$ défini par $C = \{x \in \mathbb{Q}_{p}  | a\le \val\left(x\right) \le b\} $ pour $a < b$ deux réels positifs fixés.
+\end{definition}
+
+Les couronnes sont un objet fondamentale de l'étude des espaces $p$-adique. \todo{expliquer pourquoi}. 
+\begin{proposition}
+	Les couronnes sont des projections de spectraèdres.
+\end{proposition}
+
+\textit{Preuve :}
+Soit $C$ la couronne de paramètres $a<b \in R^*_+$.
+
+On considère pourtout $x,y \in \mathbb{Q}_{p} $ la matrice  $M(x,y) :=
+\begin{pmatrix} 
+p^ax & 0 & 0 & 0 \\
+0 & p^{-b}y & 0 & 0 \\
+0 & 0 & p^{-1} & p^{-1}x \\
+0 & 0 & p^{-1}y & - p^{-1}  \\
+\end{pmatrix} $ et le spectraèdre $\mathcal{S}= \{(x,y) \in \mathbb{Q}_{p}  : M(x,y) \succeq 0\} $
+
+Soient $x,y \in \mathbb{Q}_{p} $. Montrons que $x \in C$ si et seulement si  $\exists y \in \mathbb{Q}_{p} \left( x,y \right) \in \mathcal{S}$.
+
+Soient $x,y \in \mathbb{Q}_{p} $.
+En décomposant $M(x,y)$ en trois blocs : $p^ax$, $p^{-b}y $ et $M'(x,y) = \begin{pmatrix} p^{-1} & p^{-1}x \\ p^{-1} y & p^{-1}\end{pmatrix} $ et en utilisant \ref{caracsnp} on a que $M(x,y)$ est semi-définie positive si et seulement si
+$
+\begin{cases}
+p^ax \ge 0 \\
+p^{-b}y \ge 0\\
+\text{Tr}M'\left( x,y \right) = 0 \ge 0\\
+\text{det} M'(x,y ) = p^{-2}\left( xy-1 \right)  \ge 0 
+\end{cases}
+$ 
+c'est à dire si et seulement si $beg \begin{cases}
+\label{caracsdp} 
+	\val\left(x\right)\ge a\\
+\val\left(y\right)\ge -b\\
+p^{-2} \left( xy-1 \right) \ge 0
+
+\end{cases}$
+Or $x \in C$ si et seulement si il existe $y \in \mathbb{Q}_{p} $ tel que $(x, y)$ vérifient \ref{caracsdp}.
+En effet, si $x, y$ vérifient \ref{caracsdp}alors $\val\left(x\right)\ge a$, $\val\left(y\right)\ge -b$ et $p^{-2} \left( xy-1 \right) \ge 0$ implique que $\val\left(x\right)+\val\left(y\right)=\val\left(xy\right) = \val\left(-1\right) =0$ et donc que $\val\left(x\right)=-\val\left(y\right)\le -(-b)  =b$, donc $x \in $.
+Puis réciproquement si $x \in C$ alors $(x,x^{-1}) $ vérifient \ref{caracsdp}  .

### 2023-07-25 rapport/realspectrahedra.tex
exemple cayley

@@
 \begin{definition}
-	On appelle \emph{spectraèdre} l'intersection de $\mathcal{S}_n^+\left(\mathbb{R}\right)$ avec un plan affine $\mathcal{L}$ de $\mathcal{S}_n\left(\mathbb{R}\right)$.
+	On appelle \emph{spectraèdre} l'intersection de $\mathcal{S}_n^+\left(\mathbb{R}\right)$ avec un \simone{espace} affine $\mathcal{L}$ de $\mathcal{S}_n\left(\mathbb{R}\right)$.
 \end{definition}
 
-En écrivant l'hyperplan $\mathcal{L}$ de $\mathcal{S}_n^+\left(\mathbb{R}\right)$ sous sa forme paramétrique \textit{i.e.} comme l'ensemble des matrices de la forme $A_0 + x_1 A_1 + \ldots x_s A_s$ pour $A_0,\ldots, A_s$ des matrices symétriques fixées on peut définir le spéctraèdre $\mathcal{S} = \mathcal{L} \cap \mathcal{S}_n^+\left(\mathbb{R}\right)$ comme $\mathcal{S} = \{A_0 + x_1A_1 + \ldots + x_s A_s \succeq 0| (x_1,\ldots,x_s) \in \mathbb{R}^s\} $.
-On identifie alors souvent ce dernier à sa préimage dans $\mathbb{R}^s$ $S = \{(x_1,\ldots,x_s) | A_0+ x_1A_1 + \ldots+ x_s A_s \succeq 0 \}.
-$
+En écrivant l'hyperplan $\mathcal{L}$ de $\mathcal{S}_n^+\left(\mathbb{R}\right)$ sous sa forme paramétrique \textit{i.e.} comme l'ensemble des matrices de la forme $A_0 + x_1 A_1 + \ldots x_s A_s$ pour $A_0,\ldots, A_s$ des matrices symétriques fixées on peut définir le spéctraèdre $\mathcal{S} = \mathcal{L} \cap \mathcal{S}_n^+\left(\mathbb{R}\right)$ comme
+\simone{$\mathcal{S} = \{A := A_0 + x_1A_1 + \ldots + x_s A_s | A \succeq 0, (x_1,\ldots,x_s) \in \mathbb{R}^s\}$}. On identifie alors souvent ce dernier à sa préimage dans $\mathbb{R}^s$
+$S = \{(x_1,\ldots,x_s) \simone{\in \mathbb{R}^s} | A_0+ x_1A_1 + \ldots+ x_s A_s \succeq 0 \}. $
 \todo{image + exemple}
+
+\simone{
+  \begin{ex} Un exemple celèbre de spectraèdre est l'ensemble des matrices symétrique semi-définie positives
+    avec diagonale $(1,1,1)$:
+    $$
+    S = \left\{
+    \begin{pmatrix} x_1 \\ x_2 \\ x_3 \end{pmatrix} \in \mathbb{R}^3 |
+    A:=\begin{pmatrix} 1 & x_1 & x_2 \\ x_1 & 1 & x_3 \\ x_2 & x_3 & 1 \end{pmatrix} \succeq 0
+    \right\}.
+    $$
+    La surface algébrique définie par $\det A(x_1,x_2,x_3) = 0$ est dite {\it cubique de Cayley}.
+  \end{ex}
+}
 

### 2023-07-25 rapport/realspectrahedra.tex
cleveref
modifs/suggestions section 1

@@
     $$
-    La surface algébrique définie par $\det A(x_1,x_2,x_3) = 0$ est dite {\it cubique de Cayley}.
+    La surface algébrique définie par $\det A(x_1,x_2,x_3) = 0$ est dite {\it cubique de Cayley} (\Cref{cayley}).
+    Le spectraèdre $S$ est souvent appélé {\it samosa} et peut être obtenu comme {\it dérivée au sens de Renegar}
+    du tetraèdre régulier \cite{sanyal}.
+    Les quatres points singuliers correspondent à quatre matrices semi-définies positives de rang un ; les autres
+    points de la surface, correspondent à des matrices de rang deux (semi-définies si sur la frontière du spectraèdre,
+    avec au moins une valeure propre négative autrement) ; enfin, les matrices à l'intérieur du spectraèdre sont
+    définies positives (toutes valeurs singulières strictement positives).
+    \begin{figure}[!ht]
+      \centering
+      \includegraphics[scale=0.3]{figures/cayley.pdf}
+      \caption{Cubique de Cayley}
+      \label{cayley}
+    \end{figure}
   \end{ex}
@@
 
-\subsection{Programmation semi-définie positive}
+\subsection{Programmation semi-définie}
 
-On appelle alors programmation semi-définie le problème d'optimisation consistant à minimiser une application linéaire sur un spéctraèdre que l'on formulera comme :
+On appelle alors {\it programmation semi-définie} le problème d'optimisation
+consistant à minimiser une application linéaire sur un spéctraèdre que l'on formulera comme :
 \begin{equation}
   \tag{PSD}
-	\begin{matrix}
-		\text{Minimiser } c.x \text{ tel que}\\
-		A_0 + \sum \limits_{i=1}^s x_{i}A_{i} \succeq 0
-	\end{matrix}
+\begin{aligned}
+  \text{Minimiser } & \simone{\left\langle c,x \right\rangle} \\
+  \text{tel que }   & A_0 + \sum \limits_{i=1}^s x_{i}A_{i} \succeq 0
+%	\begin{matrix}
+%		\text{Minimiser } \simone{\left\langle c,x \right\rangle} \text{ tel que}\\
+%		A_0 + \sum \limits_{i=1}^s x_{i}A_{i} \succeq 0
+%	\end{matrix}
+\end{aligned}
 	\label{Psd} 
 \end{equation}
+pour $A_0,\ldots, A_s$ des matrices symétriques fixées, $c=(c_1,\ldots,c_s)$ un vecteur représentant le coût
+\simone{et $x \mapsto \left\langle c,x \right\rangle := c_1x_1+\cdots+c_sx_s$ le produit scalaire
+  Euclidien. Le problème d'admissibilité associé au problème d'optimisation \eqref{Psd}, c'est-à-dire, la question
+  si le spectraèdre $S = \{(x_1,\ldots,x_s) \in \mathbb{R}^s | A_0+ x_1A_1 + \ldots+ x_s A_s \succeq 0 \}$ est
+vide, est appélé {\it inégalité matricielle linéaire (LMI)}}.
 
-pour $A_0,\ldots, A_s$ des matrices symétriques fixées et $c$ un vecteur représentant le coût.
-
-Ce problème se résout en temps polynomial en la taille des matrices grâce à des techniques d'optimisation convexe. \todo{exemples}
+\simone{En précision finie $\epsilon$,} ce problème se résout en temps polynomial en \simone{la dimension de l'entrée (taille des matrices, nombre de variables, taille binaire des coéfficients), en $\log(1/\epsilon)$ et $\log(R)$, où $R$ est une borne {\it a priori} sur la norme d'une solution.
+En arithmétique exacte, la complexité de la programmation semi-définie est un problème essentiellement ouvert, cf \cite[Sec.1.9]{deKlerk}, \cite{ramana1997exact,porkolab1997complexity} et \cite{henrion2016exact}.}
 
 Si à première vue ce problème peut sembler très spécifique il n'en est rien et de nombreux autres problèmes se rapportent à celui-ci.
+\simone{Par exemple, tout problème d'\simone{optimisation linéaire} est en particulier un problème SDP:
 
-Le premier exemple étant que
+\begin{remarque} Un polyèdre est un spectraèdre; en particulier, l'optimisation linéaire est une sous-classe de l'optimisation semi-définie.
+En effet, soit $P = \{x \in \mathbb{R}^s | \ell_1(x) \geq 0, \ldots, \ell_d(x) \geq 0\}$ le polyèdre défini par les inégalités linéaires $\ell_1,\ldots,\ell_d$, et soit $D$ la matrice linéaire diagonale avec entrées $\ell_1,\ldots,\ell_d$.
+Alors $P$ est le spectraèdre défini par $D \succeq 0$.
+\end{remarque}
+}
+
+%\todo{exemples: par }
+
+%Le premier exemple étant que

### 2023-07-26 rapport/polyhedra.tex
Smith + prise en compte modification Simone

@@
 \section{Polyèdres convexes \texorpdfstring{$p$}{p}-adiques}
-\begin{notation}
-
-	Pour toute matrice $M$ à coefficient dans $\Qp$ on note $M\ge 0$ et on dit que $M$ est \textit{positive} si tous les coefficients de $M$  sont positifs, c'est à dire si $M \in M_n\left( \Zp \right) $ .
-On infère également les notation $M\le 0$, $M>0$ et $M<0$.
-\end{notation}
-
+\label{sec:polyedre} 
+\iffalse
 \subsection{Matrices symétriques positive}
@@
 
-\begin{propriete}
-	$\Pn$ est un anneau.
-\end{propriete}
+\fi
 
-\textit{Preuve :} Par la propriété précédente $\Pn = S_n \left( \Zp \right)$ comme intersection des anneaux $M_n \left( \Qp \right)$ et $S_n\left( \Qp \right) $.
+\subsection{Polyèdres convexes \texorpdfstring{$p$}{p}-adiques}
+
+\begin{definition}
+	(Matrice positive)
+
+	Une matrice $M$ de $\mathcal{M}_n(\Qp)$ est dite \emph{positive} si tous ses coefficients sont positifs ou nuls, c'est-à-dire, par définition si elle est à coefficient dans $\mathbb{Z}_p$.
+	On notera alors $M\ge 0$ le fait que $M \in \mathcal{M}_{n}\left(\mathbb{Z}_p\right) $
+
+\end{definition}
+
+%Tout ce beau monde ira peut-être en annexe si 
 \begin{propriete}
@@
 $i.$ et $ii.$ se déduisent du fait que $\Zp$ soit ouvert et fermé dans $\Qp$, $ii.$ découle directement du fait que $\|M\|_\infty = \sup |M_{i,j}|_p \le 1$ et $iv.$ se déduit de $ii.$ et $iii.$.
-Quand à $v.$ c'est une conséquence directe de la convexité de $\Zp$ et $S_n\left( \Qp \right) $.
+Quand à $v.$ c'est une conséquence directe de la convexité de $\Zp$.
 
@@
 La preuve pour $ \Pn$ est assez triviale et pour $S_n^+\left( \mathbb{Q}_p \right)$ elle est laissée en exercice au lecteur}
-\subsection{Polyèdres convexes \texorpdfstring{$p$}{p}-adiques}
-
 \begin{definition}
 
-On définit un polyèdre convexe $P$ comme l'intersection de $\Pn$ avec un hyperplan affine $\mathcal{L} $ de $S_n\left( \Qp \right) $. 
+On définit un polyèdre convexe $P$ comme l'intersection de $\Pn$ avec un espace affine $\mathcal{L} $ de $\mathcal{M}_n\left( \Qp \right) $. 
 \end{definition}
+Comme en \ref{sec:casreel} dans le cas réel on identifiera un polyèdre à sa préimage. Ce qui permet le résultat suivant :
 
+\iffalse
 Soit $P$ un polyèdre convexe et $\mathcal{L} $ un plan affine tel que $P = \Pn \cap \mathcal{L}$, et dont on note $s$ la dimension de l'espace vectoriel associé.
@@
 \textit{Preuve :} Provient immédiatement du fait qu'un polyèdre s'écrit comme intersection d'ensemble convexe.
-
+\fi
 \begin{ex}
-	La boule unité pour la norme infinie est un polyèdre.
-En effet, considérons le polyèdre défini par l'intersection de $S_n\left( \mathbb{Q}_{ p }  \right) $ avec le plan linéaire induit par les matrices $E_k$, k=1\ldots n, de $S_n\left( \Zp \right) $ telles que le seul coefficient non nul de $E_k$ soit le k-ième coefficient diagonal lequel est égal à $1$ .
+	La boule unité de $\mathbb{Q}_{p}^n$ pour la norme infinie est un polyèdre. En effet, la boule infinie s'écrit comme l'ensemble des points $\left( x_1,\ldots,x_n \right)$ tels que $
+	\begin{pmatrix} x_1 &  & & \\
+		  & x_2 &0 &  \\
+		&  0& \ddots & \\
+		&  & & x_n
+	\end{pmatrix} \ge 0$.
+En effet, la boule unité de $\mathbb{Q}_{p} ^n$ est $\mathbb{Z}_p^n$.
+%En effet, considérons le polyèdre défini par l'intersection de $S_n\left( \mathbb{Q}_{ p }  \right) $ avec le plan linéaire induit par les matrices $E_k$, k=1\ldots n, de $S_n\left( \Zp \right) $ telles que le seul coefficient non nul de $E_k$ soit le k-ième coefficient diagonal lequel est égal à $1$ .
 On observe que pour tout $x_1,\ldots,x_n \in \mathbb{Q}_{ p } ^n$, $\sum x_k E_k \ge 0$ si et seulement si $x_1,\ldots,x_s \in \mathbb{Z}_{ p }^n $ i.e.
@@
 
-\subsection{Résolution \texorpdfstring{$p$}{p}-adique de la programmation linéaire}
+\subsection{Programmation linéaire \texorpdfstring{$p$-adique}{p-adique} } 
 \label{sectionalgo} 
@@
 Il convient donc alors de développer de nouvelles techniques pour résoudre ces problèmes.
-C'est ce qui est proposé dans cette section, qui présente un algorithme en $O(n^3)$ \todo{vérifier que c'est améliorable} pour résoudre le problème de la programmation linéaire en $p$-adique, dont une écriture en pseudo-code ainsi qu'une implémentation en \sage sont disponible en \ref{appendixalgo}.
+C'est ce qui est proposé dans cette section, qui présente un algorithme en $O( \max\left( m,n \right)^2 )$, avec $m,n$ les dimensions de la matrice de contrainte, pour résoudre le problème de la programmation linéaire en $p$-adique, dont une écriture en pseudo-code ainsi qu'une implémentation en \sage sont disponible en \ref{appendixalgo}.
 
@@
 \begin{matrix}
-	\text{Minimiser } |c.x|_p \text{ tel que }\\
+	\text{Minimiser } \val\left(\left<c,x \right>\right) \text{ tel que }\\
 	Ax + b \ge 0
@@
 
-	Pour toute matrice $M \in \mathcal{M}_{m,n}\left( \mathbb{Q}_{ p }  \right) $ il existe une unique matrice $S$ de $\mathcal{M}_{m,n}\left( \mathbb{Q}_{ p }  \right) $ diagonale, dont les coefficients sont triés par valuation croissante et telle que
-	\[
-		M = P^{-1} S Q
-	\]
- avec $P \in \mathcal{G}L_m\left( \mathbb{Z}_p \right)$ et $ Q \in \mathcal{G}L_n\left( \mathbb{Z}_p \right)$. La matrice $S$ est appelée forme normale de Smith de $M$.
+		On appelle forme normale de Smith d'une matrice $M \in \mathcal{M}_{m,n}\left(\mathbb{Q}_{p} \right) $ de rang $r$ l'unique matrice $S$ de la forme $$S =  
+	\begin{pmatrix} p^{a_1} & \\
+		 & \ddots \\
+		 & & p^{ar}\\
+		 & & & 0\\
+		 & & & & \ddots \end{pmatrix} $$
+		 telle que $a_1\le  \ldots\le a_r$ et $M =  Q^{-1} S P$ avec $P \in \mathcal{G}L_n\left( \mathbb{Z}_p \right) $ et $Q \in \mathcal{G}L_m\left( \mathbb{Z}_p \right) $.
 \end{definition}
@@
 \begin{matrix}
-	\text{Minimiser } |c'.y|p \text{ tel que }\\
+	\text{Minimiser } \val\left(\left<c',x \right>\right) \text{ tel que }\\
 	Sy + b' \ge 0
@@
 \end{equation}
-où $b' = Pb$, $c' = cQ$, $S$ est la forme normale de Smith de $A$ et $A = P S Q$ avec $P \in \mathcal{G}L_m\left( \mathbb{Z}_p \right)$ et $ Q \in \mathcal{G}L_n\left( \mathbb{Z}_p \right)$.
+où $b' = Qb$, $c' = P^Tc$, $S$ est la forme normale de Smith de $A$ et $A = Q^{-1} S P$ avec $P \in \mathcal{G}L_m\left( \mathbb{Z}_p \right)$ et $ Q \in \mathcal{G}L_n\left( \mathbb{Z}_p \right)$.
 
@@
 \begin{enumerate}
-	\item $x^*$ est une solution admissible de \ref{eqn:Proglinp} si et seulement si $y^* := Q^{-1} x$ est une solution admissible de \ref{eqn:Proglinp2}
-	\item \ref{eqn:Proglinp2} possède des solutions admissible si et seulement si les $m-r$ coefficients de $Pb$ sont non nuls, où $r$ le rang de $S$.     
+	\item $x^*$ est une solution admissible de \ref{eqn:Proglinp} si et seulement si $y^* := P x^*$ est une solution admissible de \ref{eqn:Proglinp2}
+	\item \ref{eqn:Proglinp2} possède des solutions admissible si et seulement si les $m-r$ coefficients de $b'$ sont non nuls, où $r$ le rang de $S$.     
 	\item Si les $n-r$ tous derniers coefficients de $c'$ sont non nuls \ref{eqn:Proglinp2} n'est pas borné et n'admet donc pas de solution.   
@@
 
-Résoudre \ref{eqn:Proglinp2} revient donc à minimiser $|c'.y|_p$ sur $Adm$.
-L'image de $Adm$ par $y \mapsto c'y$ est $\sum_{i=1}^r -c'_i.\frac{b'_i}{s_i} + \sum_{i=1}^r\left( \frac{c_i}{s_{i}} \mathbb{Z}_p \right)$ qui se réécrit :
-$$c'Adm = \lambda_0 + p^{v_0} \mathbb{Z}_p$$
-où $\lambda_0 = \sum\limits_{i=1}^r -c'_i.\frac{b'_i}{s_i}$ et $v_{0} = \min\limits_{1\le i\le r} \val \frac{c'_{i}}{s_{i}} $.
+Résoudre \ref{eqn:Proglinp2} revient donc à minimiser $\val\left(\left<c',y \right>\right)$ sur $Adm$.
+L'image de $Adm$ par $y \mapsto \left<c',y \right>$ est $\sum_{i=1}^r -c'_i.\frac{b'_i}{s_i} + \sum_{i=1}^r\left( \frac{c'_i}{s_{i}} \mathbb{Z}_p \right)$ qui se réécrit :
+$$c'Adm = \lambda + p^{v} \mathbb{Z}_p$$
+où $\lambda = \sum\limits_{i=1}^r -c'_i.\frac{b'_i}{s_i}$ et $v = \min\limits_{1\le i\le r} \val \frac{c'_{i}}{s_{i}} $.
+Ainsi, deux cas apparaissent.
+\begin{itemize}
+	\item Soit $\val( \lambda) < v$ auquel cas le minimum de $y\mapsto \val\left(\left<c',y \right>\right)$ sur $Adm$ est atteint en n'importe quel point de $Adm$ et vaut $\val\left( \lambda\right)$.
+	\item Soit $\val\left( \lambda \right) \ge v$, auquel cas $\lambda \in p^{v} \mathbb{Z}_p$ et le minimum vaut $v $ et est atteint en tous les points $y$ de $Adm$ vérifiant
+	$$\val\sum \limits_{\begin{array}{c} 1\le i\le r\\ \val\left(c'_{i}/{s_{i}} \right) = v  \end{array}   } y_{i} = 0.$$
 
-Ainsi, deux cas apparaissent.
-Soit $\val( \lambda_0) < v_0$ auquel cas le minimum de $y\mapsto |c'.y|_p$ sur $Adm$ est atteint en n'importe quel point de $Adm$ et vaut $| \lambda_0|_p$.
-Soit $\val\left( \lambda_0 \right) \ge v_0$, auquel cas $\lambda_0 \in p^{v_0} \mathbb{Z}_p$ et le minimum vaut $p^{-v_0} $ et est atteint en tous les points $y$ de $Adm$ tels que $\val\left(\sum \limits_{1\le i\le r} y_{i}\right) = v_0$.
+\end{itemize}
+\begin{remarque}
+	Si l'on souhaite maximiser la valuation d'un application linéaire su un polyèdre $p$-adique au lieu de la minimiser (ce qui revient à maximiser la valeur absolue) on pourra utiliser un raisonnement similaire à celui présenté dans cette partie.
+La seule différence est que si $\val\left( \lambda\right) < v$ le problème n'est pas borné et n'admet donc pas de solution.
+\end{remarque}

### 2023-07-26 rapport/complpadic.tex
Smith + Prise en compte Simone

@@
 
+\subsection*{Représentation sous forme d'arbre}
+Un façon intuitive de se représenter les nombres $p$-adiques est de les écrire comme les feuilles d'un arbre infini.
+
+On considère l'arbre $\mathcal{T}(\mathbb{Z}_p)$ dont les nœuds sont les suites finies à coefficients dans $\{1,\ldots,p\} $ et tels que deux sommets sont reliés entre eux si et seulement si
+
 \begin{proof} \hypertarget{qpcorpspreuve}{Proposition \ref{qpcorps}} 
+En réalité on dispose même d'un résultat plus précis : $\mathbb{Q}_{p}$ est le corps des fractions de $\mathbb{Z}_p$. Pour prouver ce résultat on utilisera le lemme suivant :
+\begin{lemme}
+	\label{lemmeinversible} 
+	Les inversibles de $\mathbb{Z}_p$ sont exactement les entiers $p$-adique $\overline{\ldots x_n\ldots x_1x_0}$ tels que $x_0$ est non nul.
+\end{lemme}
+\textit{Preuve du lemme :} 
+Un entier $p$-adique $x = \overline{\ldots x_n \ldots x_1 x_0}$ est inversible si et seulement si il est inversible dans $\mathbb{Z}{/p^n\mathbb{Z}}$ pour tout $n \in \mathbb{N}$, c'est-à-dire si et seulement si $ \sum \limits_{i=0}^{n}p^i x_{i}$ est premier avec $p^n$ pour tout $n \in \mathbb{N}$ ce qui est équivalent à $x_0$ premier avec $p$ et donc $x_0 \neq 0$.
+
+Ensuite il suffit de remarquer que tout entier $p$-adique non nul $x = \overline{\ldots x_n \ldots x_1 x_0}$ s'écrit $p^n \tilde{x}$ avec $\tilde{x} \in \mathbb{Z}_p^\times $ et $n$ un entier naturel.
+On a de plus unicité par \ref{lemmeinversible}.
+
+En effet, si on pose $n$ le plus petit entier naturel tel que $x_n \neq 0$\footnote{c'est-à-dire la valuation de $x$} et $\tilde{x} := \overline{\ldots x_n }$ on a immédiatement $ x = p^n \tilde{x}$ et $\tilde{x} \in \mathbb{Z}_p^\times $.
+Il est alors immédiat que $\mathbb{Q}_{p} = \mathbb{Z}_p[\frac{1}{p}]$ est le plus petit corps contenant $\mathbb{Z}_p$
+
 \end{proof}
@@
 \begin{proof} \hypertarget{propvalpreuve}{Propriété \ref{propval} }  
+	Soient $x,y$ deux entiers naturels de valuation $n := \val\left(x\right)$ et $m := \val\left(y\right)$.
+	On peut alors écrire $x = p^n \tilde{x}$ et $y = p^m \tilde{y}$ avec $\tilde{x}, \tilde{y} \in \mathbb{Z}_p^\times $, comme vu \hyperref{qpcorpspreuve}{plus haut}.
+	On a alors tout d'abord $xy = (\tilde{x}\tilde{y}) p^{n+m}$ et donc par unicité de la décomposition $\val\left(xy\right) = \val\left(x\right)+\val\left(y\right) $.
+
+Ensuite, on trouve que $x+y \in p^n \mathbb{Z}_p+ p^m \mathbb{Z}_p = p ^{\min\left( m,n \right) }\mathbb{Z}_p $ ce qui signifie que $\val\left(x+y\right)\ge \min\left( \val\left(x\right), \val\left(y\right) \right) $.
+Puis si $m\neq n$ on peut supposer sans perte de généralité que $m>n$ et $x+y$ s'écrit alors $p^n(p^{m-n} \tilde{x} + \tilde{y})$ et par \ref{lemmeinversible}, $p^{m-n}\tilde{x}+\tilde{y} \in \mathbb{Z}_p^\times$.
+\end{proof}
+
+\begin{proof} \hypertarget{caracsdppreuve}{Théorème \ref{caracsdp} }
 

### 2023-07-26 rapport/realspectrahedra.tex
Smith + Prise en compte Simone

@@
 \begin{definition}
-	On appelle \emph{spectraèdre} l'intersection de $\mathcal{S}_n^+\left(\mathbb{R}\right)$ avec un \simone{espace} affine $\mathcal{L}$ de $\mathcal{S}_n\left(\mathbb{R}\right)$.
+	On appelle \emph{spectraèdre} l'intersection de $\mathcal{S}_n^+\left(\mathbb{R}\right)$ avec un espace affine $\mathcal{L}$ de $\mathcal{S}_n\left(\mathbb{R}\right)$.
 \end{definition}
@@
 En écrivant l'hyperplan $\mathcal{L}$ de $\mathcal{S}_n^+\left(\mathbb{R}\right)$ sous sa forme paramétrique \textit{i.e.} comme l'ensemble des matrices de la forme $A_0 + x_1 A_1 + \ldots x_s A_s$ pour $A_0,\ldots, A_s$ des matrices symétriques fixées on peut définir le spéctraèdre $\mathcal{S} = \mathcal{L} \cap \mathcal{S}_n^+\left(\mathbb{R}\right)$ comme
-\simone{$\mathcal{S} = \{A := A_0 + x_1A_1 + \ldots + x_s A_s | A \succeq 0, (x_1,\ldots,x_s) \in \mathbb{R}^s\}$}. On identifie alors souvent ce dernier à sa préimage dans $\mathbb{R}^s$
-$S = \{(x_1,\ldots,x_s) \simone{\in \mathbb{R}^s} | A_0+ x_1A_1 + \ldots+ x_s A_s \succeq 0 \}. $
-\todo{image + exemple}
+$\mathcal{S} = \{A := A_0 + x_1A_1 + \ldots + x_s A_s | A \succeq 0, (x_1,\ldots,x_s) \in \mathbb{R}^s\}$. On identifie alors souvent ce dernier à sa préimage dans $\mathbb{R}^s$
+$S = \{(x_1,\ldots,x_s) \in \mathbb{R}^s | A_0+ x_1A_1 + \ldots+ x_s A_s \succeq 0 \}. $
 
@@
     $$
-    La surface algébrique définie par $\det A(x_1,x_2,x_3) = 0$ est dite {\it cubique de Cayley} (\Cref{cayley}).
-    Le spectraèdre $S$ est souvent appélé {\it samosa} et peut être obtenu comme {\it dérivée au sens de Renegar}
-    du tetraèdre régulier \cite{sanyal}.
-    Les quatres points singuliers correspondent à quatre matrices semi-définies positives de rang un ; les autres
-    points de la surface, correspondent à des matrices de rang deux (semi-définies si sur la frontière du spectraèdre,
-    avec au moins une valeure propre négative autrement) ; enfin, les matrices à l'intérieur du spectraèdre sont
-    définies positives (toutes valeurs singulières strictement positives).
+    La surface algébrique définie par $\det A(x_1,x_2,x_3) = 0$ est dite {\it cubique de Cayley} (\ref{cayley}).
+    %Le spectraèdre $S$ est souvent appélé {\it samosa} et peut être obtenu comme {\it dérivée au sens de Renegar} du tetraèdre régulier \cite{sanyal}.
+    Les quatres points singuliers correspondent à quatre matrices semi-définies positives de rang un ; les autres points de la surface, correspondent à des matrices de rang deux (semi-définies si sur la frontière du spectraèdre, avec au moins une valeure propre négative autrement) ; enfin, les matrices à l'intérieur du spectraèdre sont définies positives (toutes valeurs singulières strictement positives).
     \begin{figure}[!ht]
@@
 
-On appelle alors {\it programmation semi-définie} le problème d'optimisation
+On appelle alors \emp{programmation semi-définie} le problème d'optimisation
 consistant à minimiser une application linéaire sur un spéctraèdre que l'on formulera comme :
@@
 \end{equation}
-pour $A_0,\ldots, A_s$ des matrices symétriques fixées, $c=(c_1,\ldots,c_s)$ un vecteur représentant le coût
-\simone{et $x \mapsto \left\langle c,x \right\rangle := c_1x_1+\cdots+c_sx_s$ le produit scalaire
-  Euclidien. Le problème d'admissibilité associé au problème d'optimisation \eqref{Psd}, c'est-à-dire, la question
-  si le spectraèdre $S = \{(x_1,\ldots,x_s) \in \mathbb{R}^s | A_0+ x_1A_1 + \ldots+ x_s A_s \succeq 0 \}$ est
-vide, est appélé {\it inégalité matricielle linéaire (LMI)}}.
+pour $A_0,\ldots, A_s$ des matrices symétriques fixées, $c=(c_1,\ldots,c_s)$ un vecteur représentant le coût et $x \mapsto \left\langle c,x \right\rangle := c_1x_1+\cdots+c_sx_s$ le produit scalaire Euclidien.
+Le problème d'admissibilité associé au problème d'optimisation \eqref{Psd}, c'est-à-dire, la question si le spectraèdre $S = \{(x_1,\ldots,x_s) \in \mathbb{R}^s | A_0+ x_1A_1 + \ldots+ x_s A_s \succeq 0 \}$ est vide, est appelée \emp{inégalité matricielle linéaire (LMI)}.
 
-\simone{En précision finie $\epsilon$,} ce problème se résout en temps polynomial en \simone{la dimension de l'entrée (taille des matrices, nombre de variables, taille binaire des coéfficients), en $\log(1/\epsilon)$ et $\log(R)$, où $R$ est une borne {\it a priori} sur la norme d'une solution.
-En arithmétique exacte, la complexité de la programmation semi-définie est un problème essentiellement ouvert, cf \cite[Sec.1.9]{deKlerk}, \cite{ramana1997exact,porkolab1997complexity} et \cite{henrion2016exact}.}
+En précision finie $\epsilon$, ce problème se résout en temps polynomial en la dimension de l'entrée (taille des matrices, nombre de variables, taille binaire des coefficients), en $\log(1/\epsilon)$ et $\log(R)$, où $R$ est une borne {\it a priori} sur la norme d'une solution.
+En arithmétique exacte, la complexité de la programmation semi-définie est un problème essentiellement ouvert, cf \cite[Sec.1.9]{deKlerk}, \cite{ramana1997exact,porkolab1997complexity} et \cite{henrion2016exact}.
 

### 2023-07-26 rapport/smith.tex
Smith + Prise en compte Simone

@@
 On revient dans cette partie sur la construction de la forme normale de Smith d'une matrice ainsi que sur les principaux résultats sur cette dernière.
-Ces résultats sont utilisé dans l'algorithme présenté en section \ref{sectionalgo}
+Ces résultats sont utilisé dans l'algorithme présenté en section \ref{sectionalgo}.
+Les preuves de cette section ont étés tirées de \todo{le lien} puis rapportées au cas $p$-adique, là ou le cours original se place dans le cadre plus général des anneaux euclidiens.
 
-\begin{propriete}
-	Il existe une unique matrice $0$
+\begin{rappel}
+	On appelle forme normale de Smith d'une matrice $M \in \mathcal{M}_{m,n}\left(\mathbb{Q}_{p} \right) $ de rang $r$ l'unique matrice $S$ de la forme $$S =  
+	\begin{pmatrix} p^{a_1} & \\
+		 & \ddots \\
+		 & & p^{ar}\\
+		 & & & 0\\
+		 & & & & \ddots \end{pmatrix} $$
+		 telle que $a_1\le  \ldots\le a_r$ et $M =  Q^{-1} S P$ avec $P \in \mathcal{G}L_n\left( \mathbb{Z}_p \right) $ et $Q \in \mathcal{G}L_m\left( \mathbb{Z}_p \right) $.
+\end{rappel}
+\textbf{Remarque préliminaire} 
+Soit $M$ une matrice de $\mathcal{M}_{m,n}\left(\mathbb{Q}_{p} \right) $.
+Pour $k \in \mathbb{N}$ suffisamment grand $M_k := p^k M$ est à coefficient dans$\mathcal{M}_{n}\left(\mathbb{Z}_p\right)$.
+Il suffit donc de montrer l'existence et l'unicité de la forme normale de Smith sur les matrices de $\mathcal{M}_{n}\left(\mathbb{Z}_p\right) $ pour l'avoir sur toutes les matrices à coefficients dans $\mathbb{Q}_{p}$.
 
-\end{propriete}
+\begin{proof} Existence de la forme normale de Smith.
 
-\begin{proof}
-i
+On démontrera le résultat par récurrence sur $m+n$.
+
+Les résultats dans les cas $n+m= 0,1$ et $2$ étant immédiats, on a l'initialisation.
+
+Soit $k \in \mathbb{N}$ tel que tout matrice $M \in M_{m,n}\left( \mathbb{Z}_{p}  \right) $ avec $m+n \le  k$ admettent une forme normale de Smith.
+
+	Soient $m,n \in \mathbb{N}$ tels que $m+n = k+1$ et $M \in \mathcal{M}_{m,n}\left(\mathbb{Z}_p\right) $.
+
+	Si $M$ est nulle le résultat est immédiat. On supposera donc $M \neq 0$. 
+	On peut alors trouver un coefficient $\alpha$ de $M$ de valuation minimale $a_1$.
+En multipliant $M$ à droite et à gauche par des matrices de permutation on peut faire remonter ce coefficient en position $(1,1)$.
+$M$ est alors équivalente à une matrice $N$ de la forme :
+
+	\[
+N = 		\begin{pmatrix} \alpha & N_{1,2} & \ldots & N_{1,n} \\
+			N_{2,1} & * & \ldots & *\\
+			\vdots & \vdots & \ddots & \vdots \\
+			N_{m,1} &* & \ldots & *\\
+		\end{pmatrix} 
+	.\] 
+	On considère alors $\tilde{\alpha} := \alpha^{-1} p^{a_1}$ ainsi $\alpha\tilde{\alpha} = p^{a_1} $ et $\tilde{\alpha} \in \mathbb{Z}_p^\times $ conformément à \ref{lemmeinversible}.
+Multiplier à gauche $N$ par la matrice $\text{diag}( \tilde{\alpha}, 0, \ldots,0)$ conserve l'équivalence dans $\mathbb{Z}_p$ \footnote{car on multiplie par une matrice de déterminant inversible dans $\mathbb{Z}_p$ et donc elle même inversible.} et permet d'obtenir une matrice $\tilde{N}$ :
+	\[
+\tilde{N} = 		\begin{pmatrix} p^{a_1} & \tilde{N}_{1,2} & \ldots & \tilde{N}_{1,n} \\
+			N_{2,1} & * & \ldots & *\\
+			\vdots & \vdots & \ddots & \vdots \\
+			N_{m,1} &* & \ldots & *\\
+		\end{pmatrix} 
+	.\]
+
+On remarque en particulier que le passage de $N$ à $\tilde{N}$ ne modifie pas la valuation de ses éléments.
+Or $N$ s'écrivant comme permutation des coefficients de $M$ $p^{a_1} $ reste un coefficient de $\tilde{N}$ de valuation minimale.
+À ce titre pour tout $2\le i\le m$ il existe $q_{i} \in \mathbb{Z}_p$ tel que $\tilde{N}_{i,1} = p^{a_1}q_{i}$ et de même pour tout $2\le j\le n$ on dispose de $p_{j} \in \mathbb{Z}_p$ vérifiant $N_{1,j} = p^{a_1} p_{j}$.
+On fixe de tels $q_{i}$ et $p_{j}$.
+En ajoutant à la $i$-ième ligne de $\tilde{N}$ $q_{i}$ fois la première pour $2\le i\le m$ on annule alors tous les coefficients de la première ligne sauf $p^{a_1}$ en conservant l'équivalence.
+
+	\[
+ 		\begin{pmatrix} p^{a_1}  & \tilde{N}_{1,2}- p^{a_1}  q_{i} & \ldots & \tilde{N}_{1,n}- p^{a_1}  q_{i} \\
+			N_{2,1} & * & \ldots & *\\
+			\vdots & \vdots & \ddots & \vdots \\
+			N_{m,1} &* & \ldots & *\\
+		\end{pmatrix} 
+ = 		\begin{pmatrix} p^{a_1}& 0 & \ldots & 0 \\
+			N_{2,1} & * & \ldots & *\\
+			\vdots & \vdots & \ddots & \vdots \\
+			N_{m,1} &* & \ldots & *\\
+		\end{pmatrix} 
+	.\]
+
+On procède alors pareillement pour les colonnes en ajoutant à la $j$-ième colonne de la matrice nouvellement obtenue $p_{j}$ fois la première pour obtenir une matrice dont le seul coefficient non nul de la première ligne et colonne est $p^{a_1}$.
+
+	\[ 		\begin{pmatrix}  p^{a_1}& 0 & \ldots & 0 \\
+			0 & * & \ldots & *\\
+			\vdots & \vdots & \ddots & \vdots \\
+			0 &* & \ldots & *\\
+		\end{pmatrix} 
+	.\]
+
+Dans les cas particuliers ou $m = 1$ ou $n=1$ la preuve s'arrête ici, la matrice étant de la forme demandée. 
+Sinon les coefficients de la matrice nouvellement obtenue s'écrive comme sommes et produits de coefficients de $M$ et sont de valuation supérieure à $a_1$.
+On applique alors l'hypothèse de récurrence et obtient le résultat.
 	\end{proof}
+
+	\begin{remarques}
+		On observe que la preuve ci-dessus décrit en fait une procédure permettant de canuler la forme normale de Smith d'une matrice ainsi que des matrices de passages associées en $O\left( \max\left( m,n \right) ^3 \right) $ opérations.
+Il est cependant possible d'obtenir ce même résultats en $O(n^{ \omega}) $ \todo{comment je dis que Tristan a pas encore publié l'article} .
+	\end{remarques}
+
+	\begin{proof} Unicité de la forme normale de Smith
+		Soit $M \in \mathcal{M}_{m,n}\left(\mathbb{Z}_p\right) $ et $S = \begin{pmatrix} p^{a_1} & \\
+		 & \ddots \\
+		 & & p^{ar}\\
+		 & & & 0\\
+		 & & & & \ddots \end{pmatrix} $ sa forme normale de Smith.
+
+		La preuve de l'unicité repose sur le fait que la valuation minimale pour les sous-déterminants de taille $k\times k$ de $M$ soit $a_1 + a_2 + \ldots + a_r$ si $k\le r$ et $0$ sinon pour $k=1,\ldots, \min(m,n)$.
+Ce qui permet de conclure immédiatement à l'unicité de $S$.
+
+		On note pour toute matrice $A \in \mathcal{M}_{m,n}\left(\mathbb{Z}_{p} \right) $, $v_k(A)$ la valuation minimale des déterminants de taille $k\times k$ de A, pour $k=1\ldots \min\left( m,n \right) $.
+
+		Remarquons tout d'abord la propriété suivante : pour tous $A \in \mathcal{M}_{m,n}\left(\mathbb{Z}_p\right) $ et $Q \in \mathcal{M}_{n}\left(\mathbb{Z}_p\right), v_k(AQ) \le v_k(A)$
+
+	Le résultat est une conséquence immédiate de \ref{propval}.
+
+	On en déduit alors ce résultat plus fort :
+	Pour toutes matrice $A \in \mathcal{M}_{m,n}\left(\mathbb{Z}_p\right) $, $P \in \mathcal{G}L_n\left( \mathbb{Z}_p \right) $ et $Q \in \mathcal{G}L_m\left( \mathbb{Z}_p \right) $ on a $v_k(A) = v_k(PAQ)$.
+
+	En effet, soient $A\in \mathcal{M}_{m,n}\left(\mathbb{Z}_p\right) $, $P \in \mathcal{M}_{n}\left(\mathbb{Z}_p\right) $ et $Q \in \mathcal{M}_{m}\left(\mathbb{Z}_p\right) $.
+	On a l'inégalité suivante par invariance de $v_k$ par transposition :
+	$$v_k(PAQ) \le v_k(PA) = v_k\left( (PA)^T \right) = v_k(A^T P^T) \le v_k(A).$$
+	Puis de même $v_k(A) = v_k(P^{-1}(PAQ)Q^{-1}) \le v_k(PAQ)$.
+
+En appliquant ce résultat à $M$ et $S$ on a que pour tout $1\le k\le \max(m,n) $ $v_k(M)  = v_k(S)$, or par définition de $S$, $v_k(S) = a_1 + a_2 + \ldots + a_r$ si $k\le r$ et $0$ sinon.
+D'où le résultat.
+
+	\end{proof}

### 2023-07-26 rapport/padic.tex

@@
 
-\todo{exemple d'opérations dans $\mathbb{Q}_{p} $ } 
+%\todo{exemple d'opérations dans $\mathbb{Q}_{p} $ } 
 \begin{corollaire}
@@
 \end{corollaire}
-\todo{les personne habitués pourrait y voir une analogie avec la contruction de R[[X]} 
+%\todo{les personne habitués pourrait y voir une analogie avec la contruction de R[[X]} 
 Ce dernier résultat permet de construire de manière assez élémentaire des éléments de $\mathbb{Q}_{p}$ qui ne sont pas des entiers $p$-adique.
@@
 
-	\todo{Petit paragraphe introducif} 
+%	\todo{Petit paragraphe introducif} 
 On définit la valuation $p$-adique dans $\mathbb{Z}$ $\val^{\mathbb{Z}}:\mathbb{Z}\to \mathbb{N}\cup \{+\infty\}  $ comme l'application qui à 0 associe $+\infty$ et à un entier $a$ non nul associe le plus grand entier naturel $k$ tel que $p^k | a$.% ou de façon équivalente en considérant $\sum \limits_{i=1}^{n} a_{i} p^i$ la décomposition de $a$ en base $p$, la valuation $p$-adique de $a$ est le plus petit $a_{i}$ non nul.
@@
 
-Le principal intérêt qu'offre la notion de valuation pour le sujet développé ici est qu'elle permet de définir une notion de positivité dans un corps qui n'est pas totalement ordonnable \todo{i.e.}.
+Le principal intérêt qu'offre la notion de valuation pour le sujet développé ici est qu'elle permet de définir une notion de positivité dans un corps qui n'est pas totalement ordonnable \footnote{i.e.
+il n'y a pas relation d'ordre $\ge $ sur $\mathbb{Q}_{p}$ compatible avec l'addition et telle que $\forall s\ge 0$ $x\ge y \Rightarrow sx\ge sy$.}.
 À cet effet on introduira la notation suivante :
 \begin{notation}
-
 	Pour tout élément $x \in \mathbb{Q}_{p} $, on dit que $x$ est \hypertarget{positif}{\textit{positif}} et on note $x\ge 0$ si $\val\left(x\right)\ge 0$.
@@
 		\label{propval} 
-		\item $\val(x+y) \ge \min\left( \val\left( x \right), \val\left( y \right)  \right) $ 
+		\item $\val(x+y) \ge \min\left( \val\left( x \right), \val\left( y \right)  \right) $ avec égalité si $\val\left(x\right) \neq \val\left(y\right)$
 		\item $\val\left( xy \right) = \val (x) + \val( y)$ 

### 2023-07-26 rapport/proglin.tex

@@
 \caption{Résolution de la programmation $p$-adique}
-%\Entry Une matrice $A$ de taille $m \times n$, un vecteur $b$ de taille $m$ et un vecteur $c$ de taille $n$.
 \begin{algorithmic}[0]
+\Require Une matrice $A$ de taille $m \times n$, un vecteur $b$ de taille $m$ et un vecteur $c$ de taille $n$.
+\Ensure Le maximum des $\val\left(\left<c,x \right>\right)$ tels que $Ax+b\ge 0$. 
 \State $S,P,Q$ = FormeNormaleDeSmith($A$)
 \State $r$ = rang($S$)
-\State $b' = P \times b$
-\State $c'$ = $c \times Q$
+\State $b' =Q \times b$
+\State $c'$ = $P^T \times c$
 \For{$i$ allant de $r+1$ à $m$}
 \If{$\val\left(b'[i] \right) < 0$}
-\State Pas de solution
+\State \Failwith Pas de solution
 \EndIf
@@
 \If{$c'[i]\neq 0$}
-\State Le problème n'est pas borné
+\State \Failwith Le problème n'est pas borné
 \EndIf
@@
 \State $\tilde{S} = $SousMatrice$\left( S, (1,r),(1,r) \right) $
-\State $\lambda_0 = \tilde{c}. S^{-1}. \tilde{b} $
-\State $v_0 = \min \left\{\val\left(z_{i}\right)| \left( z_1,\ldots,z_r \right) = \tilde{c}.S^{-1}  \right\}$
+\State $\lambda = \tilde{c}. S^{-1}. \tilde{b} $
+\State $v = \min \left\{\val\left(z_{i}\right)| \left( z_1,\ldots,z_r \right) = \tilde{c}.S^{-1}  \right\}$
 
-\If{$\val\left( \lambda_0\right) < v_0$}
-\Return $\val\left( \lambda_0 \right)$
-\Else \Return $v_0$ \Comment Si l'on cherche à calculer la valuation maximale à la place il suffit de soulever une erreur au lieu de renvoyer $v_0$.
+\If{$\val\left( \lambda\right) < v$}
+\Return $\val\left( \lambda \right)$
+\Else \Return $v$ \Comment Si l'on cherche à calculer la valuation maximale à la place il suffit d'échouer au lieu de renvoyer $v$.
 \EndIf

### 2023-07-26 rapport/spectrahedra.tex

@@
 \section{Spectraèdres \texorpdfstring{$p$}{p}-adiques } 
+\label{sec:spectraedre} 
 Ce paragraphe tend à fournir un définition de la notion de \mat sur les corps $p-$adiques pour en déduire une définition de spectraèdre qui serait pertinente sur un corps non-archimédien. 
 La première étape pour définir un spectraèdre est de définir un équivalent des matrices symétriques définies positives.
-Sans théorème spectrale et le produit scalaire n'étant qu'une forme bilinéaire "banale" (ni positive ni définie), la symétrie est en $p$-adique parfaitement inutile et ne sera pas exigé.
-De plus, se par le manque cruel du théorème spectral la plupart des caractérisations des matrices symétriques semi-définies positives peinent à faire sens en $p$-adique.
+Sans théorème spectral et le produit scalaire n'étant qu'une forme bilinéaire "banale" (ni positive ni définie), la symétrie est en $p$-adique parfaitement inutile et ne sera pas exigé.
+De plus, du fait du manque cruel du théorème spectral la plupart des caractérisations des matrices symétriques semi-définies positives peinent à faire sens en $p$-adique.
 Il a donc été choisi de définir les \mats \footnote{notez l'absence du mot symétrique}comme les matrices à valeurs propres positives.
@@
 \end{definition}
-\begin{propriete}
-	\label{caracsnp}
+\begin{theoreme}
+	\label{caracsdp}
 	Caractérisation des \mats
@@
 
-\end{propriete}
-	\textit{Preuve :} Voir le LIEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEN0
+\end{theoreme}
+	\textit{Preuve :} Voir \hyperlink{caracsdppreuve}{annexe}.
 
@@
 
-\textit{Preuve : }  Le polynôme caractéristique d'une matrice à coefficients dans $\Zp$ étant à coefficient dans $\Zp$ on obtient le résultat par la propriété \ref{caracsnp} .
+\textit{Preuve : }  $\mathbb{Z}_p$ étant un anneau, le polynôme caractéristique d'une matrice à coefficients dans $\Zp$ est à coefficient dans $\Zp$. Onconclut par \ref{caracsdp} .
 
@@
 \begin{propriete}
-	L'ensemble $S_n^+\left( \mathbb{Q}_p \right)$  est :
+	L'ensemble $\mathcal{M}_n^+\left( \mathbb{Q}_p \right)$  est :
 	\begin{enumerate}[label = \textit{\roman*}.]
@@
 Montrons tout d'abord que $\Zp[X]$ est fermé et ouvert dans $\mathbb{Q}_{ p }[X] $ muni de la norme infinie $\|.\|_\infty : P = \sum_{k=1}^{n} a_k X^k \to \sup |a_k|_p$.
-
+Il suffit pour cela de remarquer que $\|\cdot \|_\infty$  définit une distance discrète pour laquelle les boules fermées sont également ouvertes.
+Or, $\mathbb{Z}_p$ est la boule ouverte de centre $0$ et de rayon $1$ donc est fermée et ouverte.
+\iffalse
 Soit $P \in \Zp[X]$.
@@
 
-On montre alors $i.$ et $ii.$ grâce à $\Pn = \chi^{-1}( \Zp[X]) $ ou $\chi$ est l'application qui a une matrice associe son polynôme caractéristique qui est continue car polynomiale en les coefficients de la matrice.
+\fi
+On montre alors $i.$ et $ii.$ par $\mathcal{M}^+_{n}\left(\mathbb{Q}_{p} \right)  = \chi^{-1}( \Zp[X]) $ ou $\chi$ est l'application qui a une matrice associe son polynôme caractéristique qui est continue car polynomiale en les coefficients de la matrice.
 
@@
 Soient $x,y \in \mathbb{Q}_{p} $.
-En décomposant $M(x,y)$ en trois blocs : $p^ax$, $p^{-b}y $ et $M'(x,y) = \begin{pmatrix} p^{-1} & p^{-1}x \\ p^{-1} y & p^{-1}\end{pmatrix} $ et en utilisant \ref{caracsnp} on a que $M(x,y)$ est semi-définie positive si et seulement si
+En décomposant $M(x,y)$ en trois blocs : $p^ax$, $p^{-b}y $ et $M'(x,y) = \begin{pmatrix} p^{-1} & p^{-1}x \\ p^{-1} y & p^{-1}\end{pmatrix} $ et en utilisant \ref{caracsdp} on a que $M(x,y)$ est semi-définie positive si et seulement si
 $
@@
 $ 
-c'est à dire si et seulement si $beg \begin{cases}
-\label{caracsdp} 
+c'est à dire si et seulement si 
+\begin{equation}
+\label{eq:caracsdp} 
+\begin{cases} 
 	\val\left(x\right)\ge a\\
@@
 p^{-2} \left( xy-1 \right) \ge 0
+\end{cases}
+\end{equation}
 
-\end{cases}$
-Or $x \in C$ si et seulement si il existe $y \in \mathbb{Q}_{p} $ tel que $(x, y)$ vérifient \ref{caracsdp}.
+Or $x \in C$ si et seulement si il existe $y \in \mathbb{Q}_{p} $ tel que $(x, y)$ vérifient \ref{eq:caracsdp}.
 En effet, si $x, y$ vérifient \ref{caracsdp}alors $\val\left(x\right)\ge a$, $\val\left(y\right)\ge -b$ et $p^{-2} \left( xy-1 \right) \ge 0$ implique que $\val\left(x\right)+\val\left(y\right)=\val\left(xy\right) = \val\left(-1\right) =0$ et donc que $\val\left(x\right)=-\val\left(y\right)\le -(-b)  =b$, donc $x \in $.
-Puis réciproquement si $x \in C$ alors $(x,x^{-1}) $ vérifient \ref{caracsdp}  .
+Puis réciproquement si $x \in C$ alors $(x,x^{-1}) $ vérifient \ref{eq:caracsdp}  .

### 2023-09-04 rapport/complpadic.tex
Version finale cette fois

@@
 
-On considère l'arbre $\mathcal{T}(\mathbb{Z}_p)$ dont les nœuds sont les suites finies à coefficients dans $\{1,\ldots,p\} $ et tels que deux sommets sont reliés entre eux si et seulement si
+On considère l'arbre $\mathcal{T}(\mathbb{Z}_p)$ dont les nœuds sont les suites finies à coefficients dans $\{1,\ldots,p\} $ et tels que deux sommets $N_1 \to N_2$ sont reliés entre eux si et seulement si $N_1 \subset N_2$ et $|N_2| = |N_1| + 1$.
+
+On encode alors les $p$-adique comme une suite de sommets reliés entre eux.
+
+\begin{figure}[htpb]
+	\centering
+	\input{figures/tree.tex} 
+	\caption{$\mathcal{T}\left( \mathbb{Z}_p \right) $}
+	\label{fig:TZp} 
+\end{figure}
+
+Cette interprétation en arbre de $\mathbb{Z}_p$ est utile car permet de se figurer certaine propriétés géométriques des $p$-adiques, puisqu'en effet chaque sommet représente exactement une boule
 
@@
 
-\begin{proof} \hypertarget{caracsdppreuve}{Théorème \ref{caracsdp} }
+\begin{proof} \hypertarget{caractères}{Théorème \ref{caracsdp} }
+
+Afin de prouver le théorème \ref{caracsdp} nous allons reformuler ce dernier sous la forme équivalente suivante :
+
+	\begin{propriete}
+		Un polynôme de $\mathbb{Q}_{p} [X] $\emp{unitaire et de terme constant entier}est a uniquement des racines de valuation positive ou nulle dans $\overline{\mathbb{Q}_{p} }$ si et seulement si il est à coefficients dans $\mathbb{Z}_p$.
+	\end{propriete}
+Si prouver le sens réciproque de cette équivalence se fait sans difficulté, le sens direct est, lui plus complexe à démontrer.
+Pour ce faire, nous utiliserons un outil particulièrement utile pour l'étude des polynômes à coefficients $p$-adique : les polygones de Newton.
+
+\textit{Preuve du sens réciproque :} 
+	Soit $P = X^n + \sum \limits_{i=0}^{n-1} a_{i} X^i $ un polynôme à coefficients dans $\mathbb{Z}_{p}$. 
+	Montrons par l'absurde que toute racine de $P$ est de valuation positive.
+Soit $\rho \in \overline{\mathbb{Q}_{p} }$ une racine de $P$, supposons $\val\left( \rho\right)<0$.
+D'après la propriété \ref{propval}, $\val\left(P( \rho)\right) = \min \left( \val\left( \rho^n \right), \val(a_{n-1} \rho^{n-1}),\ldots, \val(a_0) \right)$.
+Or on a l'inégalité $\val\left( \rho^n\right) = n \val\left( \rho\right)\le \val\left(a_{i} p^{i} \right) = i\val\left( \rho \right) + \val\left(a_{i}\right)$ pour $i=1,\ldots,n$, car $a_i \in \mathbb{Z}_p$.
+Ainsi $\val\left(P( \rho)\right) = n \val\left( \rho\right) <0$, or $\rho$ est une racine de $P$ et donc $\val\left( P( \rho) \right) = \val\left(0\right) = +\infty$.
+Ce qui est absurde, donc $\val\left( \rho\right) \ge 0$.
+
+	\textit{Preuve du sens direct :}
+
+	Pour la preuve du sens direct on utilisera les polygones de Newton, un outil permettant de relier très facilement les coefficient d'un polynôme à la valuation de ses racines.
+On ne prouvera pas le principal résultat sur les polygones de Newton dont la preuve peut se retrouver en section 6.4 de \cite{gouvea_p-adic_2003} .
+
+\begin{definition}
+	Polygone de Newton
+
+Soit $P = \sum 	\limits_{i=0}^{n} a_i X^i$ un polynôme à coefficients dans $\mathbb{Q}_{p}$.
+On appelle \emp{polygone de Newton} l'ensemble des points enveloppe convexe inférieure de l'ensemble  $\mathcal{P} = \{\left( i, \val\left(a_{i}\right) \right)| 1\le i\le n \}$.
+\end{definition}
+
+On entend par enveloppe convexe inférieure le graphe de la plus grande fonction convexe $f$ de $[0,n]$ étant "sous" les points de  $\mathcal{P}$, i.e. telle que $f(i) > a_i$ pour $i=1\ldots n$.
+ \begin{ex}
+	 Par exemple au polynôme $P = 3 + \frac{5}{2} X+ 32 X^2+ \frac{9}{4} X^4+ 44 X^5 + 2 X^6$ on associe 
+\begin{figure}[!ht]
+      \centering
+      \includegraphics[scale=0.25]{figures/polygone_newton.pdf}
+      \caption{Polygone de Newton $\mathcal{P}$ associé à $P$}
+      \label{poly_newton}
+    \end{figure}
+  \end{ex}
+
+On pourra alors prouver que l'enveloppe convexe inférieure ainsi définie est une ligne brisée constitués de segments de pentes deux à deux différentes.
+On appelle pentes du polygones les pentes des segments de la ligne brisée et longueur d'un segment de la ligne brisé la longueur du projeté du segment sur l'axe des abscisses.
+
+\begin{theoreme}
+Les pentes du polygone de Newton $\mathcal{P}$ sont exactement les opposés des valuations des racines de $P$ (dans $\overline{\mathbb{Q}_{p}}$).
+De plus, le nombre de racines de valuation $v$ est égal à la longueur du segment de pente $-v$.
+\end{theoreme}
+
+On considère alors un polynôme $P =X^n \sum_{i=1}^{n-1} a_{i}X^i$ à coefficient dans $\mathbb{Q}_p$ unitaire.
+On remarque immédiatement que le point d'abscisse $n$ du polygone de Newton $\mathcal{P}$ associé à $P$ est d'ordonnée nulle.
+On en déduit alors que si un des coefficients $(a_{i})_{0\le i\le n-1}$ est de valuation strictement négative, $\mathcal{P}$ admet une pente strictement positive et donc $P$ admet une racine de valuation strictement négative.
+
+Par contraposée, on en déduit que si polynôme unitaire à coefficient dans $\mathbb{Q}_{p} $ est à racine positive alors il est élément de $\mathbb{Z}_p[X]$.
 

### 2023-09-04 rapport/intro.tex
Version finale cette fois

\section{Introduction} 
Les spectraèdres se présentent comme une généralisation des polyèdres, définis comme les points $x = (x_1,\ldots,x_s)$pour lesquels une matrice linéaire $A(x) = A_0 + x_1A_1+\ldots+x_s A_s$ est symétrique semi-définie positives, avec $A_0,\ldots,A_s$ des matrice symétriques. Ils sont d'une grand utilité en optimisation car ils permettent de résoudre non seulement des problèmes d'optimisation linéaire mais également d'autres plus spécifiques. En effet, une sur-classe des problèmes de programmation linéaire, les problèmes de programmation semi-définie consiste à maximiser une application linéaire sur un spectraèdre.

Si ces objets ont été largement étudiés dans le cadre réel, une voie vers leur étude dans des corps non archimédiens s'est récemment ouverte dans \cite{allamigeon_tropical_2020}. C'est ce que ce rapport étudie dans le cadre des corps $p$-adiques, corps non-archimédiens qui peuvent être vus comme des extensions du coprs $\mathbb{Q}$ des rationnels autres que le corps des réels et dans lesquels les techniques traditionnelles ne marchent pas. Ainsi, le produit scalaire n'est en $p$-adique pas une forme bilinéaire particulièrement distinguée, ce qui annule tout bénéfice de la symétrie et le corps $p$-adique $\mathbb{Q}_{p}$ n'est de plus pas algébriquement clos. Il a donc fallu trouver une nouvelle définition de matrice semi-définie positive. Celle choisie ici est celle des matrices dont la valuation $p$-adique des valeurs propres est positive dans la clôture de $\mathbb{Q}_{p}$. On en déduit alors aisément une définition de spectraèdre $p$-adique et prouve qu'avec cette dernière les couronnes $p$-adiques sont des projetés de spectraèdre.

Ce rapport commence par décrire le déroulement du stage. Suite à quoi, les spectraèdres sont définis et quelques unes de leur propriétés décrites. Puis, suit une présentation élémentaire des corps $p$-adiques. Ensuite, les polyèdres seront définis dans le cas $p$-adique, et un algorithme résolvant le problème de la programmation linéaire sera décrit. Enfin, on y construira une définition des spectraèdre $p$-adiques, basé sur la nouvelle définition de matrice semi-définie positive après avoir brièvement discuté des clôtures algébriques des corps $p$-adiques. Ultimement, on prouvera que les couronnes $p$-adiques s'écrivent comme ombre de spectraèdre et y adjoindra d'éventuelle piste pour l'étude des propriétés algorithmiques des spectraèdre nouvellement définis.

### 2023-09-04 rapport/jeracontemavie.tex
Version finale cette fois

\section{Méta-informations}

Cette courte section dévoile quelques informations non-scientifique sur le déroulement du stage.

Pour les activités non liées aux stage de façon immédiate, j'ai pu lors de mon séjour participer à 2 repas organisés respectivement par le laboratoire et par le département dans lequel je me trouvais et j'ai également assisté à deux conférences données sur place, une par mon encadrant Tristan Vaccon et une seconde par un intervenant extérieur. De plus, je mangeais régulièrement avec les chercheurs.

Je disposais d'un bureau dans une salle que je partageais avec 3 autres stagiaires \footnote{tous fort sympathiques}. Il était convenu d'un rendez-vous hebdomadaire afin de discuter des mes avancées ou de mes doutes et interrogations. Cependant, en cas de questionnement je pouvais contacter directement mes encadrants qui étaient présents une majeure partie de la journée.

Le stage a approximativement suivie le déroulement suivant :

La première semaine a été passée à se documenter sur les corps $p$-adiques. La deuxième et la troisième ont été consacrées alternativement à essayer de trouver une définition pertinente de spectraèdre $p$-adique. La quatrième a principalement servie à commencer l'écriture du rapport ainsi qu'à se documenter sur les spectraèdres et l'optimisation convexe afin de dresser des similarités entre spectraèdres réels et $p$-adiques. La cinquième et la sixième ont été utilisées afin de continuer ce rapport démontrer que les couronnes $p$-adiques étaient des spectraèdres et concevoir l'algorithme présenté en \ref{sectionalgo}. L'ultime semaine semaine a permis de peaufiner quelques détails (preuves plus formelles, légères erreurs corrigées, etc.) et de continuer mon rapport de stage. Cependant cette dernière a été peu productive car je devais préparer mon départ et je suis tombé malade (de manière totalement indépendante).

Enfin, je tiens à remercier chaleureusement mes encadrants Tristan Vaccon et Simone Naldi pour, entre autres, leur disponibilité, leurs conseils et leur patience. Mes camarades de bureaux Léo et Lucile qui ont su égayer le bureau ainsi que Abdu Razik pour sa participation à \cite{rozik_borgir_2021}.

### 2023-09-04 rapport/padic.tex
Version finale cette fois

@@
 
-On se contentera dans cette section d'une description très élémentaire des différentes définitions et propriétés des nombres $p$-adiques.
+On se contentera dans cette section d'une description très élémentaire de différentes définitions et propriétés des nombres $p$-adiques.
 La plupart des preuves relatives à cette section ainsi que de plus amples informations sont disponibles en \ref{cpadic}.
-Cette section est très largement inspiré du cours de Xavier Caruso \parencite{caruso_computations_2017} que l'on invite d'ailleurs à aller consulter pour une vision plus complète mais très largement compréhensible.
+Cette section est très largement inspirée du cours de Xavier Caruso \parencite{caruso_computations_2017} que l'on invite d'ailleurs à aller consulter pour une vision plus complète mais très largement compréhensible des corps $p$-adiques.
 
@@
 \subsection{Entiers \texorpdfstring{$p$}{p}-adique}
+
 \begin{definition}{Entier $p$-adique }
 
-On appelle entier $p$-adique la somme formelle :
+	On appelle \emp{entier $p$-adique} la somme formelle :
 \[
-	z  = a_0 + a_1 p + \ldots+a_{n}p^n+\ldots
+	a  = a_0 + a_1 p + \ldots+a_{n}p^n+\ldots
 \]
@@
 \end{definition}
+\begin{remarques}
+	\begin{itemize} \
 
-\begin{remarques}
-	\begin{itemize}
-		\item[$\circ$]  On note $\Zp$ l'ensemble des entier $p-$adiques.
+		\item[$\circ$]  L'ensemble des entiers $p$-adiques est noté $\Zp$.
 		\item[$\circ$] Par commodité on notera $\overline{\ldots a_n\ldots a_1 a_0}^p$ ou plus simplement $\ldots a_n \ldots a_1a_0$ l'entier $p$-adique $\sum a_{i}p^i$ 
@@
 
-	Ainsi les sommes $\sum\limits_{i=0}^{ \infty} p^i = \overline{\ldots1111111}^p$ ou $\sum\limits_{i=0}^{ \infty} (i\ \text{mod}\ p) p^i =\overline{ \ldots210(p-1)\ldots21}^p $ sont des entiers $p$-adiques parfaitement définis bien que ne convergeant pas dans le cas réel.
+	Ainsi les sommes $\sum\limits_{i=0}^{ \infty} p^i = \overline{\ldots1111111}^p$ ou $\sum\limits_{i=0}^{ \infty} (i\ \text{mod}\ p) p^i =\overline{ \ldots210(p-1)\ldots210}^p $ sont des entiers $p$-adiques parfaitement définis bien que ne convergeant pas dans le cas réel.
 \end{ex}
@@
 \begin{propriete}
-	$\mathbb{Z}_p$ peut être muni d'une structure d'anneau commutatif intègre en lui adjoignant l'addition terme à terme avec retenue et la multiplication.
+	$\mathbb{Z}_p$ peut être muni d'une structure d'anneau commutatif intègre en lui adjoignant l'addition terme à terme avec retenue et la multiplication avec retenue.
 \end{propriete}
+
+\begin{ex}
 
@@
 
-\begin{definition}
-	L'anneau $\mathbb{Z}$ des entiers relatifs s'identifie naturellement à un sous-anneau de $\mathbb{Z}_p$.
-\end{definition}
-\begin{table}[htpb]
+\begin{figure}[htpb]
 	\centering
-	\caption{Exemples d'opérations dans $\mathbb{Z}_p$}
 	\label{tab:op}
@@
 	\end{tabular}
-\end{table}
+	\caption{Exemples d'opérations dans $\mathbb{Z}_5$}
+\end{figure}
+
+\end{ex}
+
+\begin{proposition}
+	L'anneau $\mathbb{Z}$ des entiers relatifs s'identifie naturellement à un sous-anneau de $\mathbb{Z}_p$.
+\end{proposition}
+
 \begin{remarque}
-	Si l'on a vu que les entiers relatifs étaient des entiers $p$-adiques, certains entiers $p$-adique ont du sens en tant que nombre rationnels sans être des entiers relatifs, ainsi on a par exemple $\frac{1}{2} = \ldots 2223 \in \mathbb{Z}_5$.
+	Si l'on a vu les entiers relatifs sont des entiers $p$-adiques, certains entiers $p$-adiques ont du sens en tant que nombre rationnels sans être des entiers relatifs, ainsi on a par exemple $\frac{1}{2} = \ldots 2223 \in \mathbb{Z}_5$.
 Cependant tous les rationnels ne sont pas éléments de $\mathbb{Z}_p$, $\frac{1}{p}$ n'étant par exemple jamais inclus dans $\mathbb{Z}_p$.
@@
 
-	On définit l'ensemble $\Qp$ des nombres $p$-adiques comme $\mathbb{Z}_p \left[ \frac{1}{p} \right] \footnote{Le lecteur habitué à travailler dans $R[[X]]$ y verra dans la construction de $\mathbb{Q}_{p} $ à partir de $\mathbb{Z}_p$ une ressemblance avec celle de $R(X)$ à partir de $R[[X]]$.
-De nombreux autres similitudes entres ces ensemble peuvent être trouvées mais nos éviterons de les faire apparaître afin de rester à un niveau élémentaire (à reformuler bien).}  $.
+	On définit l'ensemble $\Qp$ des \emp{nombres $p$-adiques} comme $\mathbb{Z}_p \left[ \frac{1}{p} \right] $.
 \end{definition}
@@
 
+\begin{remarque}
+Le lecteur habitué à travailler dans $R[[X]]$ verra dans la construction de $\mathbb{Q}_{p} $ à partir de $\mathbb{Z}_p$ une ressemblance avec le passage de $R[[X]]$ à $\mathbb{R}\left( X \right) $.
+De nombreuses autres similitudes entres ces ensembles peuvent être trouvées mais nous éviterons de les évoquer afin de rester à un niveau élémentaire.
+
+\end{remarque}
 \begin{propriete}
@@
 
-%\todo{exemple d'opérations dans $\mathbb{Q}_{p} $ } 
+\begin{remarque}
+	$\mathbb{Q}_{p}$ est même le corps des fractions de $\mathbb{Z}_p$.
+Ce qui établit une analogie claire avec la construction de $\mathbb{Q}$ à partir de $\mathbb{Z}$ et explique en partie les notations $\mathbb{Z}_p$ et $\mathbb{Q}_{p} $.
+\end{remarque}
 \begin{corollaire}
@@
 \end{corollaire}
-%\todo{les personne habitués pourrait y voir une analogie avec la contruction de R[[X]} 
 Ce dernier résultat permet de construire de manière assez élémentaire des éléments de $\mathbb{Q}_{p}$ qui ne sont pas des entiers $p$-adique.
@@
 
-%	\todo{Petit paragraphe introducif} 
-On définit la valuation $p$-adique dans $\mathbb{Z}$ $\val^{\mathbb{Z}}:\mathbb{Z}\to \mathbb{N}\cup \{+\infty\}  $ comme l'application qui à 0 associe $+\infty$ et à un entier $a$ non nul associe le plus grand entier naturel $k$ tel que $p^k | a$.% ou de façon équivalente en considérant $\sum \limits_{i=1}^{n} a_{i} p^i$ la décomposition de $a$ en base $p$, la valuation $p$-adique de $a$ est le plus petit $a_{i}$ non nul.
-
+On définit la valuation $p$-adique dans $\mathbb{Z}$ $\val^{\mathbb{Z}}:\mathbb{Z}\to \mathbb{N}\cup \{+\infty\}  $ comme l'application qui à 0 associe $+\infty$ et à un entier $a$ non nul associe le plus grand entier naturel $k$ tel que $p^k | a$.
 La valuation $p$-adique s'étend ensuite aux nombres rationnels en une application $\val^{\mathbb{Q}} : \mathbb{Q} \to \mathbb{Z}\cup \{+\infty\}   $ en définissant pour tout $r \in \mathbb{Q}$  $\val^{\mathbb{Q}} \left( r \right) = \val^\mathbb{Z}(a)- \val^\mathbb{Z}\left( b \right) $ avec $a,b \in \mathbb{Z} \times \mathbb{N}^*$ tels que $r=\frac{a}{b}.$
@@
 
-	On appelle valuation $p$-adique l'application $\val: \mathbb{Q}_p \to \mathbb{Z}\cup \{+\infty\}  $ qui à un nombre $p$-adique $x$ associe $\max \{k \in \mathbb{Z}\cup \{+\infty\}| x\in p^k \mathbb{Z}_p\}$.
+	On appelle \emp{valuation $p$-adique} l'application $\val: \mathbb{Q}_p \to \mathbb{Z}\cup \{+\infty\}  $ qui à un nombre $p$-adique $x$ associe $\max \{k \in \mathbb{Z}\cup \{+\infty\}| x\in p^k \mathbb{Z}_p\}$.
 \end{definition}
@@
 
-Le principal intérêt qu'offre la notion de valuation pour le sujet développé ici est qu'elle permet de définir une notion de positivité dans un corps qui n'est pas totalement ordonnable \footnote{i.e.
+Le principal intérêt qu'offre la notion de valuation pour le sujet développé ici est qu'elle permet de définir la positivité dans un corps qui n'est pas totalement ordonnable \footnote{i.e.
 il n'y a pas relation d'ordre $\ge $ sur $\mathbb{Q}_{p}$ compatible avec l'addition et telle que $\forall s\ge 0$ $x\ge y \Rightarrow sx\ge sy$.}.
@@
 	Pour tout élément $x \in \mathbb{Q}_{p} $, on dit que $x$ est \hypertarget{positif}{\textit{positif}} et on note $x\ge 0$ si $\val\left(x\right)\ge 0$.
-On en induit alors les notations $x> 0$, $x\le 0$ et $x<0$.
+On en infère alors les notations $x> 0$, $x\le 0$ et $x<0$.
 \end{notation}
@@
 \begin{propriete}
-	La valuation $p$-adique possède les propriétés suivantes, pour tous $x$ et $y$ appartenant à $\mathbb{Q}_{p} $ :   
+	La valuation $p$-adique possède les propriétés suivantes pour tous $x$ et $y$ appartenant à $\mathbb{Q}_{p} $ :
 	\begin{enumerate}
@@
 
-	On appelle valeur absolue $p$-adique l'application 
+On appelle \emp{valeur absolue $p$-adique} l'application 
 \begin{align*}
@@
 On observera en particulier que, d'après \ref{propval}, pour tous $x,y$ éléments de $\mathbb{Q}_{p}$ on a l'inégalité $\left|x+y\right|_p \le \max\left( \left| x \right|_p,\left| y \right|_p \right)$.
-Ce qui en fait un corps non archimédien \footnote{c'est-à-dire tel que $\mathbb{N}$ est borné dans $\left( \mathbb{Q}_{p}, \left| \cdot \right|_p \right) $} et rend la géométrie $p$-adique très différente du cas réel peu et intuitive si l'on y est pas habituée.
+Ce qui fait de $\mathbb{Q}_{p} $ un corps non archimédien \footnote{c'est-à-dire tel que $\mathbb{N}$ est borné dans $\left( \mathbb{Q}_{p}, \left| \cdot \right|_p \right) $} et rend la géométrie $p$-adique très différente du cas réel et peu intuitive si l'on y est pas habitué.
 Ce qui explique le manque de figure et d'explications par le dessin dans la suite de ce rapport.

### 2023-09-04 rapport/polyhedra.tex
Version finale cette fois

@@
 \label{sec:polyedre} 
+Cette partie contient les premières contributions apportées lors de ce stage, c'est-à-dire la définition des polyèdres $p$-adiques et un algorithme qui résout le problème de la programmation linéaire en $p$-adique.
+\subsection{Définition}
+
+\begin{definition}
+	On appelle \emp{polyèdre convexe $p$-adique} toute partie de $\mathbb{Q}_{p}^s$ définie par des inégalités linéaire $\val\left( \ell_1(x)\right)\ge 0$,\ldots, $ \val\left( \ell_n\left( x \right) \right)\ge 0$ pour $ \ell_1,\ldots, \ell_n $ des formes linéaires et $x$ parcourant $\mathbb{Q}_{p} ^s$.
+
+\end{definition}
+
+\begin{ex}
+	La boule unité de $\mathbb{Q}_{p}^s$ pour la norme infinie est un polyèdre. En effet, la boule infinie s'écrit comme l'ensemble des points $\left( x_1,\ldots,x_s \right)$ tels que $$
+	\begin{pmatrix} x_1 &  & & \\
+		  & x_2 &0 &  \\
+		&  0& \ddots & \\
+		&  & & x_s/
+	\end{pmatrix} \ge 0.$$ En effet, la boule unité de $\mathbb{Q}_{p} ^s$ est $\mathbb{Z}_p^s$.
+%En effet, considérons le polyèdre défini par l'intersection de $S_n\left( \mathbb{Q}_{ p }  \right) $ avec le plan linéaire induit par les matrices $E_k$, k=1\ldots n, de $S_n\left( \Zp \right) $ telles que le seul coefficient non nul de $E_k$ soit le k-ième coefficient diagonal lequel est égal à $1$ .
+On observe que pour tout $x_1,\ldots,x_n \in \mathbb{Q}_{ p } ^n$, $\sum x_k E_k \ge 0$ si et seulement si $x_1,\ldots,x_s \in \mathbb{Z}_{ p }^n $ i.e.
+si et seulement si $\|(x_1,\ldots,x_n)\|_\infty \le 1$.
+
+\end{ex}
+
+\subsection{Programmation linéaire \texorpdfstring{$p$-adique}{p-adique} } 
+\label{sectionalgo} 
+Dans ce paragraphe, il sera étudié une forme équivalente du problème de programmation linéaire, appelée \textit{programmation linéaire $p$-adique} (\ref{eqn:Proglinp}) .
+Lequel consiste simplement à minimiser la norme $p$-adique d'une application linéaire sur un polyèdre $p$-adique.
+
+	Du fait des natures profondément différentes des polyèdres $p$-adiques et réels, les techniques classiques de résolution de la programmation linéaire sont mises à mal.
+Il est en effet complexe d'appliquer la méthode du simplexe à un ensemble sans frontière ou des techniques d'analyse convexe dans un espace sans notion de convexité.
+Il convient donc alors de développer de nouvelles techniques pour résoudre ces problèmes.
+C'est ce qui est proposé dans cette section, qui présente un algorithme en $O( \complalgo )$, avec $m,n$ les dimensions de la matrice de contrainte, pour résoudre le problème de la programmation linéaire en $p$-adique, dont une écriture en pseudo-code \iffalse ainsi qu'une implémentation en \sage  sont \fi est disponible en \ref{appendixalgo}.
+
+Cet algorithme est centré sur l'utilisation de la forme normale de Smith d'une matrice, dont seul la définition et quelques remarques sont présentées dans cette section, les preuves des résultats sont disponible en \ref{smith}.
+
+	On appelle \emp{programmation linéaire $p$-adique} le problème :
+\begin{equation}
+	  \tag{PLp}
+\begin{matrix}
+	\text{Minimiser } \val\left(\left<c,x \right>\right) \text{ tel que }\\
+	Ax + b \ge 0
+ \end{matrix}
+	    \label{eqn:Proglinp}
+\end{equation}
+
+avec $x$ un vecteur de taille $n$ parcourrant $\mathbb{Q}_{p} ^n$, $c$ un vecteur de taille $n$ représentant le coût, $A$ une matrice de taille $m \times n $ et $b$ un vecteur de taille $m$.
+
+La méthode choisie ici consiste à mettre la matrice $A$ sous forme normale de Smith, un factorisation classique en $p$-adique et qui permet de grandement simplifier le problème posé.
+
+\begin{definition}
+	Forme Normale de Smith
+
+	On appelle \emp{forme normale de Smith} d'une matrice $M \in \mathcal{M}_{m,n}\left(\mathbb{Q}_{p} \right) $ de rang $r$ l'unique matrice $S$ de la forme $$S =  
+	\begin{pmatrix} p^{a_1} & \\
+		 & \ddots \\
+		 & & p^{ar}\\
+		 & & & 0\\
+		 & & & & \ddots \end{pmatrix} $$
+		 telle que $a_1\le  \ldots\le a_r$ et $M =  Q^{-1} S P$ avec $P \in \mathcal{G}L_n\left( \mathbb{Z}_p \right) $ et $Q \in \mathcal{G}L_m\left( \mathbb{Z}_p \right) $.
+\end{definition}
+
+\begin{remarques}
+
+	\begin{enumerate}[label=\roman*.]
+		\item Les coefficients de la forme normale de Smith sont uniques et sont appelés \textit{facteurs invariants de Smith} ou, plus simplement, \textit{invariants de Smith}.
+		\item La valuation $p$-adique du premier coefficient de la forme normale de Smith d'une matrice $M \in \mathcal{M}_n \left( \Qp \right) $ est égale au minimum des valuations des termes de $M$.
+		\item En particulier, la forme normale de Smith d'une matrice de $\mathcal{M}_n \left( \mathbb{Z}_p \right) $ est à coefficients dans $\mathbb{Z}_p$ .
+		\item Les $r = \text{rang} M$ premiers coefficients diagonaux de $S$ sont exactement ses coefficients non nuls.
+	\end{enumerate}
+
+\end{remarques}
+
+Avant de pouvoir utiliser la forme de normale de Smith pour résoudre \ref{eqn:Proglinp}, il nous faut démontrer le lemme suivant:
+
+\begin{lemme}
+Pour tous $z \in \mathbb{Q}_{ p } ^n$ et $M \in \mathcal{M}_{m,n}\left( \mathbb{Q}_{ p }  \right)  $ si $z\ge 0$ et $M\ge 0$ alors $Mz\ge 0$.  
+\end{lemme}
+\textit{Preuve :} $\mathbb{Z}_p$ est un anneau. \hfill\qedsymbol
+
+En mettant alors la matrice $A$ de \ref{eqn:Proglinp} sous sa forme normale de Smith il vient que résoudre \ref{eqn:Proglinp} équivaut à résoudre :
+
+\begin{equation}
+	  \tag{PLp'}
+\begin{matrix}
+	\text{Minimiser } \val\left(\left<c',x \right>\right) \text{ tel que }\\
+	Sy + b' \ge 0
+ \end{matrix}
+	    \label{eqn:Proglinp2}
+\end{equation}
+où $b' = Qb$, $c' = P^Tc$, $S$ est la forme normale de Smith de $A$ et $A = Q^{-1} S P$ avec $P \in \mathcal{G}L_m\left( \mathbb{Z}_p \right)$ et $ Q \in \mathcal{G}L_n\left( \mathbb{Z}_p \right)$.
+
+\begin{remarques}
+
+Il en vient immédiatement plusieurs résultats:
+\begin{enumerate}
+	\item $x^*$ est une solution admissible de \ref{eqn:Proglinp} si et seulement si $y^* = P x^*$ est une solution admissible de \ref{eqn:Proglinp2}
+	\item \ref{eqn:Proglinp2} possède des solutions admissibles si et seulement si les $m-r$ coefficients de $b'$ sont non nuls, où $r$ le rang de $S$.
+	\item Si au moins un des $n-r$ derniers coefficients de $c'$ est non nul \ref{eqn:Proglinp2} n'est pas borné et n'admet donc pas de solution.   
+\end{enumerate}
+
+\end{remarques}
+
+\begin{propriete}
+	\begin{itemize}~
+
+		\item[$\circ$] Si les $m-r$ coefficients de $b'$ ne sont pas tous nuls alors il n'existe pas de $y \in \mathbb{Q}_{p} ^n$ tel que $A'y+b' \ge  0$.
+	\item[$\circ$] Si les $n-r$ coefficients de $c'$ ne sont pas tous nuls alors le problème n'est pas borné et n'admet donc pas de solution. \end{itemize} 
+\end{propriete}
+En ne considérant alors que les itérations du problème admettant des solutions on peut réduire le problème en ne considérant que les $r$ premiers coefficients de $y, b', c'$ et la sous matrice de $S$ composée des $r$ premières lignes et colonnes et dont les coefficients sont alors exactement les facteurs invariants de Smith non nuls.
+L'ensemble $Adm$ des solutions admissibles s'écrit alors comme l'ensemble des vecteurs $y \in \mathbb{Q}_{ p } ^n$ vérifiant $
+\forall 1 \le i\le r \ s_i y_i + b'_i \in \mathbb{Z}_p$ c'est-à-dire vérifiant :
+
+\begin{equation}
+	\forall 1 \le i\le r  \ y_i \in -\frac{b’_i}{s_i} + \frac{1}{s_i} \mathbb{Z}_p
+\end{equation}
+
+Résoudre \ref{eqn:Proglinp2} revient donc à minimiser $\val\left(\left<c',y \right>\right)$ sur $Adm$.
+L'image de $Adm$ par $y \mapsto \left<c',y \right>$ est $\sum_{i=1}^r -c'_i.\frac{b'_i}{s_i} + \sum_{i=1}^r\left( \frac{c'_i}{s_{i}} \mathbb{Z}_p \right)$ qui se réécrit :
+$$\left<c',Adm \right> = \lambda + p^{v} \mathbb{Z}_p$$
+où $\lambda = \sum\limits_{i=1}^r -c'_i.\frac{b'_i}{s_i}$ et $v = \min\limits_{1\le i\le r} \val \frac{c'_{i}}{s_{i}} $.
+
+Ainsi, deux cas apparaissent.
+\begin{itemize}
+	\item Soit $\val( \lambda) < v$ auquel cas le minimum de $y\mapsto \val\left(\left<c',y \right>\right)$ sur $Adm$ est atteint en n'importe quel point de $Adm$ et vaut $\val\left( \lambda\right)$.
+	\item Soit $\val\left( \lambda \right) \ge v$, auquel cas $\lambda \in p^{v} \mathbb{Z}_p$ et le minimum vaut $v $ et est atteint en tous les points $y$ de $Adm$ vérifiant
+	$$\val\sum \limits_{\begin{array}{c} 1\le i\le r\\ \val\left(c'_{i}/{s_{i}} \right) = v  \end{array}   } y_{i} = 0.$$
+
+\end{itemize}
+\begin{remarque}
+	Si l'on souhaite maximiser la valuation d'un application linéaire sur un polyèdre $p$-adique au lieu de la minimiser (ce qui revient à maximiser la valeur absolue) on pourra appliquer le même raisonnement.
+La seule différence est que si $\val\left( \lambda\right) < v$ le problème n'est pas borné et n'admet donc pas de solution.
+\end{remarque}
+
 \iffalse
@@
 
-\fi
-
 \subsection{Polyèdres convexes \texorpdfstring{$p$}{p}-adiques}
@@
 
-	Une matrice $M$ de $\mathcal{M}_n(\Qp)$ est dite \emph{positive} si tous ses coefficients sont positifs ou nuls, c'est-à-dire, par définition si elle est à coefficient dans $\mathbb{Z}_p$.
+	Une matrice $M$ de $\mathcal{M}_n(\Qp)$ est dite \emp{positive} si tous ses coefficients sont positifs ou nuls, c'est-à-dire, par définition si elle est à coefficient dans $\mathbb{Z}_p$.
 	On notera alors $M\ge 0$ le fait que $M \in \mathcal{M}_{n}\left(\mathbb{Z}_p\right) $
@@
 
-\todo{$\Pn$ est un cône $p$-adique pour la définition :Soit $\mathbb{E} $ un $\mathbb{Q}_{ p } $ espace vectoriel $C \subset \mathbb{E} $ est un cône si pour tout $x \in C$ et $\lambda \ge 0 $ $\lambda x \in C$.
+%{$\Pn$ est un cône $p$-adique pour la définition :Soit $\mathbb{E} $ un $\mathbb{Q}_{ p } $ espace vectoriel $C \subset \mathbb{E} $ est un cône si pour tout $x \in C$ et $\lambda \ge 0 $ $\lambda x \in C$.
 La preuve pour $ \Pn$ est assez triviale et pour $S_n^+\left( \mathbb{Q}_p \right)$ elle est laissée en exercice au lecteur}
@@
 
-\iffalse
 Soit $P$ un polyèdre convexe et $\mathcal{L} $ un plan affine tel que $P = \Pn \cap \mathcal{L}$, et dont on note $s$ la dimension de l'espace vectoriel associé.
@@
 
-\textit{Preuve :} Provient immédiatement du fait qu'un polyèdre s'écrit comme intersection d'ensemble convexe.
 \fi
-\begin{ex}
-	La boule unité de $\mathbb{Q}_{p}^n$ pour la norme infinie est un polyèdre. En effet, la boule infinie s'écrit comme l'ensemble des points $\left( x_1,\ldots,x_n \right)$ tels que $
-	\begin{pmatrix} x_1 &  & & \\
-		  & x_2 &0 &  \\
-		&  0& \ddots & \\
-		&  & & x_n
-	\end{pmatrix} \ge 0$.
-En effet, la boule unité de $\mathbb{Q}_{p} ^n$ est $\mathbb{Z}_p^n$.
-%En effet, considérons le polyèdre défini par l'intersection de $S_n\left( \mathbb{Q}_{ p }  \right) $ avec le plan linéaire induit par les matrices $E_k$, k=1\ldots n, de $S_n\left( \Zp \right) $ telles que le seul coefficient non nul de $E_k$ soit le k-ième coefficient diagonal lequel est égal à $1$ .
-On observe que pour tout $x_1,\ldots,x_n \in \mathbb{Q}_{ p } ^n$, $\sum x_k E_k \ge 0$ si et seulement si $x_1,\ldots,x_s \in \mathbb{Z}_{ p }^n $ i.e.
-si et seulement si $\|(x_1,\ldots,x_n)\|_\infty \le 1$.
-
-\end{ex}
-
-\subsection{Programmation linéaire \texorpdfstring{$p$-adique}{p-adique} } 
-\label{sectionalgo} 
-Dans ce paragraphe, il sera étudié une forme équivalente du problème de programmation linéaire, appelée \textit{programmation linéaire $p$-adique} (\ref{eqn:Proglinp}) .
-Lequel consiste simplement à minimiser la norme $p$-adique d'une application linéaire sur un polyèdre $p$-adique.
-
-	Du fait des natures profondément différentes des polyèdres $p$-adiques et du cas réel, les techniques classiques de résolution sont mises à mal.
-Il est effet complexe d'appliquer la méthode du simplexe à un ensemble sans frontière ou des techniques d'analyse convexe dans un espace sans notion de convexité.
-Il convient donc alors de développer de nouvelles techniques pour résoudre ces problèmes.
-C'est ce qui est proposé dans cette section, qui présente un algorithme en $O( \max\left( m,n \right)^2 )$, avec $m,n$ les dimensions de la matrice de contrainte, pour résoudre le problème de la programmation linéaire en $p$-adique, dont une écriture en pseudo-code ainsi qu'une implémentation en \sage sont disponible en \ref{appendixalgo}.
-
-	Cet algorithme est centré sur l'utilisation de la forme normale de Smith d'une matrice, dont seul la définition et quelques remarques sont présenté dans cette section, les preuves des résultats présentés ici ainsi que d'autres résultats sont disponible en \ref{smith}.
-
-	On appelle \textit{programmation linéaire $p$-adique} le problème :
-\begin{equation}
-	  \tag{PLp}
-\begin{matrix}
-	\text{Minimiser } \val\left(\left<c,x \right>\right) \text{ tel que }\\
-	Ax + b \ge 0
- \end{matrix}
-	    \label{eqn:Proglinp}
-\end{equation}
-
-avec $x$ un vecteur de taille $n$ que l'on fait varier, $c$ un vecteur de taille $n$ représentant le coût, $A$ une matrice de taille $m \times n $ et $b$ un vecteur de taille $m$.
-
-La méthode choisie ici consiste à mettre la matrice $A$ sous forme normale de Smith, un factorisation classique en $p$-adique et qui permet de grandement simplifier le problème posé.
-
-\begin{definition}
-	Forme Normale de Smith
-
-		On appelle forme normale de Smith d'une matrice $M \in \mathcal{M}_{m,n}\left(\mathbb{Q}_{p} \right) $ de rang $r$ l'unique matrice $S$ de la forme $$S =  
-	\begin{pmatrix} p^{a_1} & \\
-		 & \ddots \\
-		 & & p^{ar}\\
-		 & & & 0\\
-		 & & & & \ddots \end{pmatrix} $$
-		 telle que $a_1\le  \ldots\le a_r$ et $M =  Q^{-1} S P$ avec $P \in \mathcal{G}L_n\left( \mathbb{Z}_p \right) $ et $Q \in \mathcal{G}L_m\left( \mathbb{Z}_p \right) $.
-\end{definition}
-
-\todo{donner un exemple} 
-\begin{remarques}
-
-	\begin{enumerate}[label=\roman*.]
-		\item Les coefficients de la forme normale de Smith sont uniques à chaque matrice et sont appelés \textit{facteurs invariants de Smith} ou, plus simplement, \textit{invariants de Smith}.
-		\item La valuation $p$-adique du premier coefficient de la forme normale de Smith d'une matrice $M \in \mathcal{M}_n \left( \Qp \right) $ est égale au minimum des valuation des termes de $M$.
-		\item En particulier, la forme normale de Smith d'une matrice de $\mathcal{M}_n \left( \mathbb{Z}_p \right) $ est à coefficients dans $\mathbb{Z}_p$ .
-		\item Les $r = \text{rang} M$ premiers coefficients diagonaux de $S$ sont exactement ses coefficients non nuls.  
-	\end{enumerate}
-
-\end{remarques}
-
-Avant de pouvoir utiliser la forme de normale de Smith pour résoudre \ref{eqn:Proglinp}, il nous faut démontrer le lemme suivant:
-
-\begin{lemme}
-Pour tous $z \in \mathbb{Q}_{ p } ^n$ et $M \in \mathcal{M}_{m,n}\left( \mathbb{Q}_{ p }  \right)  $ si $z\ge 0$ et $M\ge 0$ alors $Mz\ge 0$.  
-\end{lemme}
-\textit{Preuve :} $\mathbb{Z}_p$ est un anneau. \hfill\qedsymbol
-
-En mettant alors la matrice $A$ de \ref{eqn:Proglinp} sous sa forme normale normale de Smith il vient que résoudre \ref{eqn:Proglinp} revient à résoudre :
-
-\begin{equation}
-	  \tag{PLp'}
-\begin{matrix}
-	\text{Minimiser } \val\left(\left<c',x \right>\right) \text{ tel que }\\
-	Sy + b' \ge 0
- \end{matrix}
-	    \label{eqn:Proglinp2}
-\end{equation}
-où $b' = Qb$, $c' = P^Tc$, $S$ est la forme normale de Smith de $A$ et $A = Q^{-1} S P$ avec $P \in \mathcal{G}L_m\left( \mathbb{Z}_p \right)$ et $ Q \in \mathcal{G}L_n\left( \mathbb{Z}_p \right)$.
-
-\begin{remarques}
-
-Il en vient immédiatement plusieurs résultats:
-\begin{enumerate}
-	\item $x^*$ est une solution admissible de \ref{eqn:Proglinp} si et seulement si $y^* := P x^*$ est une solution admissible de \ref{eqn:Proglinp2}
-	\item \ref{eqn:Proglinp2} possède des solutions admissible si et seulement si les $m-r$ coefficients de $b'$ sont non nuls, où $r$ le rang de $S$.     
-	\item Si les $n-r$ tous derniers coefficients de $c'$ sont non nuls \ref{eqn:Proglinp2} n'est pas borné et n'admet donc pas de solution.   
-\end{enumerate}
-
-\end{remarques}
-
-\begin{propriete}
-	\begin{itemize}~
-
-		\item[$\circ$] Si les $m-r$ coefficients de $b'$ ne sont pas tous nuls alors il n'existe pas de $y \in \mathbb{Q}_{p} ^n$ tel que $A'y+b' \ge  0$.
-	\item[$\circ$] Si les $n-r$ coefficients de $c'$ ne sont pas tous nuls alors le problème n'est pas borné et n'admet donc pas de solution. \end{itemize} 
-\end{propriete}
-En ne considérant alors que les itérations du problème admettant des solutions on peut réduire le problème en ne considérant que les $r$ premiers coefficients de $y, b', c'$ et la sous matrice de $S$ composée des $r$ premières lignes et colonnes et dont les coefficients sont alors les exactement les facteurs invariants de Smith non nuls.
-L'ensemble $Adm$ des solutions admissible s'écrit alors comme l'ensemble des vecteurs $y \in \mathbb{Q}_{ p } ^n$ vérifiant $
-\forall 1 \le i\le r \ s_i y_i + b'_i \in \mathbb{Z}_p$ c'est-à-dire vérifiant :
-
-\begin{equation}
-	\forall 1 \le i\le r  y_i \in -\frac{b’_i}{s_i} + \frac{1}{s_i} \mathbb{Z}_p
-\end{equation}
-
-Résoudre \ref{eqn:Proglinp2} revient donc à minimiser $\val\left(\left<c',y \right>\right)$ sur $Adm$.
-L'image de $Adm$ par $y \mapsto \left<c',y \right>$ est $\sum_{i=1}^r -c'_i.\frac{b'_i}{s_i} + \sum_{i=1}^r\left( \frac{c'_i}{s_{i}} \mathbb{Z}_p \right)$ qui se réécrit :
-$$c'Adm = \lambda + p^{v} \mathbb{Z}_p$$
-où $\lambda = \sum\limits_{i=1}^r -c'_i.\frac{b'_i}{s_i}$ et $v = \min\limits_{1\le i\le r} \val \frac{c'_{i}}{s_{i}} $.
-Ainsi, deux cas apparaissent.
-\begin{itemize}
-	\item Soit $\val( \lambda) < v$ auquel cas le minimum de $y\mapsto \val\left(\left<c',y \right>\right)$ sur $Adm$ est atteint en n'importe quel point de $Adm$ et vaut $\val\left( \lambda\right)$.
-	\item Soit $\val\left( \lambda \right) \ge v$, auquel cas $\lambda \in p^{v} \mathbb{Z}_p$ et le minimum vaut $v $ et est atteint en tous les points $y$ de $Adm$ vérifiant
-	$$\val\sum \limits_{\begin{array}{c} 1\le i\le r\\ \val\left(c'_{i}/{s_{i}} \right) = v  \end{array}   } y_{i} = 0.$$
-
-\end{itemize}
-\begin{remarque}
-	Si l'on souhaite maximiser la valuation d'un application linéaire su un polyèdre $p$-adique au lieu de la minimiser (ce qui revient à maximiser la valeur absolue) on pourra utiliser un raisonnement similaire à celui présenté dans cette partie.
-La seule différence est que si $\val\left( \lambda\right) < v$ le problème n'est pas borné et n'admet donc pas de solution.
-\end{remarque}

### 2023-09-04 rapport/proglin.tex
Version finale cette fois

@@
 \label{appendixalgo} 
-Cette section présente le pseudo-code ainsi qu'une implémentation en \sage de l'algorithme de la section \ref{sectionalgo}.
+Cette section présente le pseudo-code \iffalse ainsi qu'une implémentation en \sage \fi de l'algorithme de la section \ref{sectionalgo}.
+
+%\subsection*{Pseudo-code} 
 \input{algo.tex}
@@
 
-Ou FormeNormaleDeSmith renvoie la forme normale de Smith de la matrice $A$ ainsi que les matrices $P$ et $Q$ telles que \todo{stick to a convention}.
+Ou FormeNormaleDeSmith renvoie la forme normale de Smith $S$ de la matrice $A$ ainsi que les matrices $P$ et $Q$ telles que $A = Q^{-1}SP$.
 
 L'algorithme s'exécute en $O\left( n^3 \right) $
+
+%\subsection*{Code \sage}
+
+%\lstinputlisting[language=Python]{../sage/polyhedra.sage}

### 2023-09-04 rapport/realspectrahedra.tex
Version finale cette fois

@@
 \section{Spectraèdres réels}
-
-\newcommand\ssp{symétrique semi-définie positive}
-\newcommand\ssps{symétriques semi-définies positives}
-\newcommand\Ssp{Symétrique semi-définie positive}
-\newcommand\Ssps{Symétriques semi-définies positives}
-
-\subsection{définiion?}
-\todo{trouver un nom}
+\label{sec:casreel} 
+Cette section consiste en une introduction très brève à la notion de spectraèdre réel.
+Elle n'offre au lecteur que l'outillage nécessaire à la bonne compréhension de l'objet en vue de son adaptation aux corps $p$-adiques, en insistant toutefois sur son usage en optimisation.
+On ne pourra que conseiller la lecture de \cite{grigoriy_semidefinite_2012} pour des approfondissements.
+\subsection{Définition et premières propriétés}
 
 \begin{definition}
-	On appelle \emph{matrice symétrique semi-définie positive} toute matrice réelle symétriques et à valeurs propres positives ou nulles.
+	On appelle \emp{matrice symétrique semi-définie positive} toute matrice réelle symétrique et à valeurs propres positives ou nulles.
 	On notera $\mathcal{S}_n^+\left(\mathbb{R}\right) $ l'ensemble de telles matrices et $M \succeq 0$ le fait que $M \in \mathcal{S}_n^+\left(\mathbb{R}\right)$.
@@
 \begin{remarque}
-	On remarquera que demander la symétrie, n'est, dans le cas réel, qu'un moyen de s'assurer d'obtenir des valeurs propres réelles grâce au théorème spectral.
+	On remarquera que demander la symétrie permet de s'assurer d'obtenir des valeurs propres réelles grâce au théorème spectral, demander leur positivité fait alors sens.
 \end{remarque}
@@
 \begin{definition}
-	On appelle \emph{spectraèdre} l'intersection de $\mathcal{S}_n^+\left(\mathbb{R}\right)$ avec un espace affine $\mathcal{L}$ de $\mathcal{S}_n\left(\mathbb{R}\right)$.
+	On appelle \emp{spectraèdre} l'intersection de $\mathcal{S}_n^+\left(\mathbb{R}\right)$ avec un espace affine $\mathcal{L}$ de $\mathcal{S}_n\left(\mathbb{R}\right)$, l'ensemble des matrices symétriques de taille $n$ sur $\mathbb{R}$.
 \end{definition}
@@
 
-\simone{
-  \begin{ex} Un exemple celèbre de spectraèdre est l'ensemble des matrices symétrique semi-définie positives
-    avec diagonale $(1,1,1)$:
+  \begin{ex} Un exemple célèbre de spectraèdre est l'ensemble des matrices symétriques semi-définies positives avec diagonale $(1,1,1)$:
     $$
@@
     $$
-    La surface algébrique définie par $\det A(x_1,x_2,x_3) = 0$ est dite {\it cubique de Cayley} (\ref{cayley}).
-    %Le spectraèdre $S$ est souvent appélé {\it samosa} et peut être obtenu comme {\it dérivée au sens de Renegar} du tetraèdre régulier \cite{sanyal}.
-    Les quatres points singuliers correspondent à quatre matrices semi-définies positives de rang un ; les autres points de la surface, correspondent à des matrices de rang deux (semi-définies si sur la frontière du spectraèdre, avec au moins une valeure propre négative autrement) ; enfin, les matrices à l'intérieur du spectraèdre sont définies positives (toutes valeurs singulières strictement positives).
+    La surface algébrique définie par $\det A(x_1,x_2,x_3) = 0$ est appelée {\it cubique de Cayley} (\ref{cayley}).
+    %Le spectraèdre $S$ est souvent appelé {\it samosa} et peut être obtenu comme {\it dérivée au sens de Renegar} du tetraèdre régulier \cite{sanyal}.
+    Les quatre points singuliers correspondent à quatre matrices semi-définies positives de rang un ; les autres points de la surface, correspondent à des matrices de rang deux (semi-définies sur la frontière du spectraèdre, avec au moins une valeur propre négative autrement) ; enfin, les matrices à l'intérieur du spectraèdre sont définies positives (toutes valeurs singulières strictement positives).
     \begin{figure}[!ht]
@@
   \end{ex}
-}
 
 \subsection{Programmation semi-définie}
-
+\label{subsec:psdreele} 
 On appelle alors \emp{programmation semi-définie} le problème d'optimisation
@@
 \begin{aligned}
-  \text{Minimiser } & \simone{\left\langle c,x \right\rangle} \\
+  \text{Minimiser } & \left\langle c,x \right\rangle \\
   \text{tel que }   & A_0 + \sum \limits_{i=1}^s x_{i}A_{i} \succeq 0
@@
 Si à première vue ce problème peut sembler très spécifique il n'en est rien et de nombreux autres problèmes se rapportent à celui-ci.
-\simone{Par exemple, tout problème d'\simone{optimisation linéaire} est en particulier un problème SDP:
+Par exemple, tout problème d'optimisation linéaire est en particulier un problème SDP:
 
@@
 \end{remarque}
-}
-
-%\todo{exemples: par }
-
-%Le premier exemple étant que

### 2023-09-04 rapport/smith.tex
Version finale cette fois

@@
 Ces résultats sont utilisé dans l'algorithme présenté en section \ref{sectionalgo}.
-Les preuves de cette section ont étés tirées de \todo{le lien} puis rapportées au cas $p$-adique, là ou le cours original se place dans le cadre plus général des anneaux euclidiens.
+Les preuves de cette section ont étés tirées de \cite{howard_rings_nodate}  puis rapportées au cas $p$-adique, là ou le cours original se place dans le cadre plus général des anneaux euclidiens.
 
@@
 		On observe que la preuve ci-dessus décrit en fait une procédure permettant de canuler la forme normale de Smith d'une matrice ainsi que des matrices de passages associées en $O\left( \max\left( m,n \right) ^3 \right) $ opérations.
-Il est cependant possible d'obtenir ce même résultats en $O(n^{ \omega}) $ \todo{comment je dis que Tristan a pas encore publié l'article} .
+Il est cependant possible d'obtenir ce même résultats en $\Omega( \max(m,n)) $, résultat prouvé par Tristan Vaccon et son stagiaire dans un article encore non publié.
 	\end{remarques}

### 2023-09-04 rapport/spectrahedra.tex
Version finale cette fois

@@
 Ce paragraphe tend à fournir un définition de la notion de \mat sur les corps $p-$adiques pour en déduire une définition de spectraèdre qui serait pertinente sur un corps non-archimédien.
+Il contient la majeur partie de la contribution apportée lors de ce stage : les notions de matrice semi-définie positive et les propriétés et définitions concernant les spectraèdres $p$-adiques étant nouveaux.
 La première étape pour définir un spectraèdre est de définir un équivalent des matrices symétriques définies positives.
-Sans théorème spectral et le produit scalaire n'étant qu'une forme bilinéaire "banale" (ni positive ni définie), la symétrie est en $p$-adique parfaitement inutile et ne sera pas exigé.
+Sans théorème spectral et le produit scalaire n'étant qu'une forme bilinéaire "banale" (ni positive ni définie), la symétrie est en $p$-adique parfaitement inutile et ne sera pas exigée.
 De plus, du fait du manque cruel du théorème spectral la plupart des caractérisations des matrices symétriques semi-définies positives peinent à faire sens en $p$-adique.
-Il a donc été choisi de définir les \mats \footnote{notez l'absence du mot symétrique}comme les matrices à valeurs propres positives.
+Il a donc été choisi de définir les \mats \footnote{On notera l'absence du mot symétrique}comme les matrices à valeurs propres positives.
 Or là un second problème se pose : $\mathbb{Q}_{p} $ n'est pas algébriquement clos et les matrices $\mathcal{M}_n\left( \mathbb{Q}_{p}  \right) $ peuvent donc avoir des valeurs propres hors de $\mathbb{Q}_{p}$.
@@
 Cette section présente quelques résultats élémentaires sur les extensions de corps $p$-adiques.
-La plupart des résultats présentés dans cette section étant soit classique et trouvable dans n'importe quel cours d'algèbre de niveau master soit élémentaires, peu de preuves y seront importés.
-On recommandera toutefois la lecture de la section 5 de \parencite{gouvea_p-adic_2003} pour plus d'information sur les extensions de corps $p$-adiques.
+La plupart des résultats présentés dans cette section étant soit classique et trouvable dans n'importe quel cours d'algèbre de niveau master soit élémentaires, peu de preuves y seront aporté.
+On recommandera toutefois la lecture de la section 5 de \parencite{gouvea_p-adic_2003} pour plus d'informations sur les extensions de corps $p$-adiques.
 
 \begin{definition}
-	On appelle \textit{extension de corps} d'un corps $\mathbb{K}$ tout corps $\mathbb{L}$ muni d'un morphisme de corps injectif de $\mathbb{K}$ dans $\mathbb{L}$.
+	On appelle \emp{extension de corps} d'un corps $\mathbb{K}$ tout corps $\mathbb{L}$ muni d'un morphisme de corps injectif de $\mathbb{K}$ dans $\mathbb{L}$.
 On note $\mathbb{L}/\mathbb{K}$ le fait que $\mathbb{L}$ soit une extension de $\mathbb{K}.$
@@
 Une extension d'un corps $\mathbb{K}$ est grossièrement un corps contenant une copie du corps $\mathbb{K}$.
+Par exemple le corps des nombres complexes $\mathbb{C}$ est une extension du corps des nombres réels $\mathbb{R}$ qui est lui même une extension du corps $\mathbb{Q}$ des rationnels.
 
 \begin{definition}
-	Un corps $\mathbb{K}$ est dit algébriquement clos si tout polynôme $P\in \mathbb{K}[X]$ de degré au moins $1$ possède une racine dans $\mathbb{K}$.
+	Un corps $\mathbb{K}$ est dit \emp{algébriquement clos} si tout polynôme $P\in \mathbb{K}[X]$ de degré au moins $1$ possède une racine dans $\mathbb{K}$.
 \end{definition}
-
+\begin{ex}
+	Le corps $\mathbb{C}$ est algébriquement clos.
+\end{ex}
 \begin{proposition}
@@
 \begin{definition}
-	On appelle clôture algébrique l'unique (à isomorphisme près) corps $\mathbb{L}$ tel que tout élément de $\mathbb{L}$ est racine d'un polynôme de $\mathbb{K}[X]$ et $\mathbb{L}$ est algébriquement clos.
+	On appelle \emp{clôture algébrique} l'unique (à isomorphisme près) corps $\mathbb{L}$ tel que tout élément de $\mathbb{L}$ est racine d'un polynôme de $\mathbb{K}[X]$ et $\mathbb{L}$ est algébriquement clos.
 \end{definition}
-
+\begin{ex}
+	$\mathbb{C}$ est la clôture algébrique de $\mathbb{R}$.
+\end{ex}
 On notera $\overline{\mathbb{Q}_{p} }$ la clôture algébrique de $\mathbb{Q}_{p}$, il est alors possible d'y étendre la valuation $p$-adique comme suit :
@@
 On retrouve alors une notion de positivité dans l'extension de corps et étendra à $\overline{\mathbb{Q}_{p}} $ la notation $x\ge 0$ si et seulement si $\val\left(x\right)\ge 0$.
-Il n'est cependant informatiquement pas très pratique de travailler dans $\overline{\mathbb{Q}_{p} }$ qui est n'est pas une extension finie de $\mathbb{Q}_{p} $ \footnote{c'est-à-dire $\overline{\mathbb{Q}_{p} }$ est un $\mathbb{Q}_{p}$-espace vectoriel de dimension infinie }.
+Il est cependant pour des usage pratique complexe de travailler dans $\overline{\mathbb{Q}_{p} }$ qui est n'est pas une extension finie de $\mathbb{Q}_{p} $ \footnote{c'est-à-dire $\overline{\mathbb{Q}_{p} }$ est un $\mathbb{Q}_{p}$-espace vectoriel de dimension infinie }.
 On cherchera donc des caractérisations plus simples pour savoir si un polynôme est à racines positives, ce qui sera fait dans la prochaine section.
@@
 \begin{definition}
-	On appelle \mat toute matrice $M \in \mathcal{M}_n\left( \Qp \right) $ dont toutes les valeurs propres sont de valuation positive ou nulle.
+	On appelle \emp{\mat} toute matrice $M \in \mathcal{M}_n\left( \Qp \right) $ dont toutes les valeurs propres sont de valuation positive ou nulle (dans $\overline{\mathbb{Q}_{p}}$) .
 
-	On note $ \mathcal{M}_n^+\left( \mathbb{Q}_p \right)$ l'ensemble des \mats.
+	On note $ \mathcal{M}_n^+\left( \mathbb{Q}_p \right)$ l'ensemble des \mats et $M \succeq 0$ le fait que $M \in \mathcal{M}_n^+\left( \mathbb{Q}_{p}\right) $.
 \end{definition}
@@
 
-	Une matrice est symétrique définie positive si et seulement si son polynôme caractéristique est à coefficient dans $\Zp$ .
+	Une matrice est semi-définie positive si et seulement si son polynôme caractéristique est à coefficient dans $\Zp$ .
 
@@
 
-\textit{Preuve : }  $\mathbb{Z}_p$ étant un anneau, le polynôme caractéristique d'une matrice à coefficients dans $\Zp$ est à coefficient dans $\Zp$. Onconclut par \ref{caracsdp} .
+\textit{Preuve : }  $\mathbb{Z}_p$ étant un anneau, le polynôme caractéristique d'une matrice à coefficients dans $\Zp$ est à coefficient dans $\Zp$. On conclut par \ref{caracsdp} .
 
@@
 Ainsi pour $M = \begin{pmatrix} 5 + \frac{3}{5} & \frac{4}{5} \\ \frac{4}{5} & -\frac{3}{5} \end{pmatrix} $, on a $\chi_M = X^2  - 5 X - 4$.
-Or une fois $M$ plongé dans $\mathbb{Q}_5$ on a $\chi_M \in \mathbb{Z}_5[X]$ donc $M \in S_2^+\left( \mathbb{Q}_5 \right)$ or aucun des coefficients de $M$ n'est dans $\mathbb{Z}_5 $
+Or une fois $M$ plongé dans $\mathbb{Q}_5$ on a $\chi_M \in \mathbb{Z}_5[X]$ donc $M \in \mathcal{M}_2^+\left( \mathbb{Q}_5 \right)$ or aucun des coefficients de $M$ n'est dans $\mathbb{Z}_5 $
 \end{remarque}
 
-	\todo{probablement pas nécessaire ira peut-être en annexe} 
 \begin{propriete}
@@
 		\item fermé
-		\item un cône
+	%	\item un cône
 	\end{enumerate}
@@
 
-Le $iii$. est laissé en exercice au lecteur. 
-\input{convexemple.tex}
+%Le $iii$. est laissé en exercice au lecteur. 
+% Je ne parle plus de convexité dans le rapport mais on ne sait jamais
+%\input{convexemple.tex}
 
-\subsection{Zoologie Spectraèdrique}
-Dans le cas réel de nombreux ensembles convexes peuvent être représentés comme des spectraèdres ou des projections de spectraèdres, il a même été conjecturé que tous les ensembles semialgébriques \footnote{$i.e.$ les ensembles définis par des inégalités polynomiales} convexes soient des ombres de spéctraèdres \todo{lien machin}.
-Bien que cette conjecture ait ensuite été prouvée fausse \todo{le lien}, il n'en reste pas loin qu'un nombre important d'ensemble admettant une telle représentation garantisse sa flexibilité
+\subsection{Spectraèdres \texorpdfstring{$p$}{p}-adiques} 
+\begin{definition}
+	On appelle \emp{spectraèdre $p$-adique} l'intersection de $\mathcal{M}_n^+\left( \mathbb{Q}_{p} \right) $ avec un hyperplan affine $\mathcal{L}$ de $\mathcal{M}_n\left( \mathbb{Q}_{p} \right) $.
+\end{definition}
 
+\begin{remarque}
+	De même que dans le cas réel on identifiera communément le spectraèdre engendré par l'hyperplan $\mathcal{L}$ avec sa préimage dans $\mathbb{Q}_{p}^s$ (i.e.
+l'ensemble des vecteurs $x \in \mathbb{Q}_{p} ^s$ tels que la matrice linéaire $A(x) = A_0 + x_1A_1 + \ldots + x_sA_s$ soit semi-définie positive avec $A_0,A_1,\ldots,A_s$ lui engendrent $\mathcal{L}$).
+\end{remarque}
+On peut alors en déduire la propriété suivante :
+\begin{propriete}
+	Les polyèdres $p$-adique sont des spectraèdres $p$-adiques.
+\end{propriete}
+\textit{Preuve :}
+La preuve est identique à celle du cas réel présentée en \ref{subsec:psdreele}.
+
+\subsection{Couronnes \texorpdfstring{$p$}{p}-adiques}
+Dans le cas réel de nombreux ensembles convexes peuvent être représentés comme des spectraèdres ou des projections de spectraèdres, il a même été conjecturé que tous les ensembles semi-algébriques \footnote{$i.e.$ les ensembles définis par des inégalités polynomiales} convexes soient des ombres de spéctraèdres \cite{helton_sufficient_2008}.
+Bien que cette conjecture ait ensuite été réfutée par Schreider dans \cite{scheiderer_spectrahedral_2017} dans le cas réel elle a été prouvée vraie pour les spectraèdres tropicaux \cite{allamigeon_tropical_2019}, il n'en reste pas loin qu'un nombre important d'ensemble admettant une telle représentation garantisse sa flexibilité.
+	Le cas $p$-adique est lui assez différent du cas réel puisque, sans notion de convexité la conjecture d'Helton-Nie n'a pas vraiment de sens.
+On trouve au contraire des résultats très différents du cas réel.
+L'exemple développé ici est celui des couronnes $p$-adique qui peuvent s'écrire comme projections de spectraèdres bien que les couronnes réelles soient des objets non convexes.
 \begin{definition}
@@
 
-	On appelle couronne tout ensemble $C$ défini par $C = \{x \in \mathbb{Q}_{p}  | a\le \val\left(x\right) \le b\} $ pour $a < b$ deux réels positifs fixés.
+	On appelle \emp{couronne} tout ensemble $C$ défini par $C = \{x \in \mathbb{Q}_{p}  | a\le \val\left(x\right) \le b\} $ pour $a < b$ deux réels positifs fixés.
 \end{definition}
 
-Les couronnes sont un objet fondamentale de l'étude des espaces $p$-adique. \todo{expliquer pourquoi}. 
-\begin{proposition}
+Les couronnes sont un objet fondamental de l'étude des espaces $p$-adique.
+En effet, ces dernières sont à l'origine de la géométrie rigide qui sert de base une partie non négligeable de l'analyse $p$-adique.
+\begin{theoreme}
 	Les couronnes sont des projections de spectraèdres.
-\end{proposition}
+\end{theoreme}
 
@@
 
-On considère pourtout $x,y \in \mathbb{Q}_{p} $ la matrice  $M(x,y) :=
+On considère pour tous $x,y \in \mathbb{Q}_{p} $ la matrice  $$M(x,y) :=
 \begin{pmatrix} 
@@
 0 & 0 & p^{-1}y & - p^{-1}  \\
-\end{pmatrix} $ et le spectraèdre $\mathcal{S}= \{(x,y) \in \mathbb{Q}_{p}  : M(x,y) \succeq 0\} $
+\end{pmatrix} $$ et le spectraèdre associé $\mathcal{S}= \{(x,y) \in \mathbb{Q}_{p}  : M(x,y) \succeq 0\} $
 
@@
 Puis réciproquement si $x \in C$ alors $(x,x^{-1}) $ vérifient \ref{eq:caracsdp}  .
+
+\subsection{Vers la résolution du problème \texorpdfstring{ \textit{(LMI)} }{LMI}} 
+\label{piste} 
+Cette dernière section présente des résultats qui bien qu'ils n'ont pas permis d'aboutir à une résolution concrète peuvent servir de bases a de futures réflexion.
+
+On rappelle que le problème \textit{(LMI)} consiste à déterminer si un spectraèdre est vide. On y développe ici quelques pistes.
+
+Comme vu précédemment, d'après \ref{caracsdp} le fait qu'une matrice soit semi-définie positive est caractérisé par le fait que son polynôme soit à coefficient dans $\mathbb{Z}_p$.
+Pour obtenir une représentation claire des spectraèdres, qui permettrait de résoude $(LMI)$ on est en droit de se demander : à quelles conditions le polynôme caractéristique d'une matrice linéaire $A(x) := A_0 + x_1 A_1 + \ldots + x_s A_s$ est-il à coefficient dans $\mathbb{Z}_p$ ?
+Les coefficients du polynôme caractéristique de la matrice linéaire $A(x)$ étant polynomiaux en $x$ se poser la question précédente revient alors à se demander pour quelles valeurs de $x = (x_1,\ldots x_s)$ un polynôme $P \in \mathbb{Q}_{p} [x_1,\ldots,x_s]$ est-il à valeur dans $\mathbb{Z}_p$ ?
+
+Si je n'ai pu y répondre, on peut toutefois remarquer que dans le cas où le polynôme est univarié on retrouve le concept de discoïde développé par Rüth dans \cite{ruth_models_2015}.
+Ce qui signifie que pour un polynôme univarié $P$ à coefficients dans $\mathbb{Q}_{p}$ fixé, l'ensemble des points $x$ de $ \overline{\mathbb{Q}_{p} }$ tels que $P(x)\ge 0$ correspond à une union disjointes de boules de $\overline{\mathbb{Q}_{p} }$ centrées en les racines de $P$ et dont le rayon se déduit des coefficients de Taylor du polynôme en ses racines.
+Si trouver l'intersection d'un boule de $\overline{\mathbb{Q}_{p} }$ avec $\mathbb{Q}_{p}$ est aisé si cette dernière est centrée en un élément de $\mathbb{Q}_{p}$ (c'est alors le boule de même centre et de même rayon mais cette fois dans $\mathbb{Q}_{p}$) le cas où le centre donné n'est pas un nombre $p$-adique est lui plus délicat et je n'ai pas de résolution à y apporter dans ce rapport.

### 2023-09-23 rapport/abstract.tex

\section*{Abstract}

	Les spectraèdres sont une des généralisations les plus communes et utilisées des polyèdres. Ce sont des ensembles réels convexes définis comme les ensembles de matrices linéaires $A(x) = A_0 + x_1 A_1 + \ldots + x_s A_s$ qui sont symétriques définies positives, avec $x = \left( x_1,\ldots,x_s \right)$ parcourant $\in \mathbb{R}^s $ et $A_0,A_1,\ldots,A_s$ des matrices symétriques réelles fixées.
Ils sont d'une grande importance en optimisation car au cœur de la programmation semi-définie, une généralisation de la programmation linéaire visant à minimiser une forme linéaire sur un spectraèdre au lieu et en place d'un polyèdre convexe. Ainsi, une large variété de problèmes peuvent se réduire à la programmation semi-définie. En effet, aux nombreuses applications de la programmation linéaire (problème de la coupe maximale, nombreuses applications en finance, médecine, dans l'industrie\ldots) s'ajoutent des problèmes plus spécifiques dont un certain nombre est par exemple présentés dans \cite{vandenberghe_applications_1999}. Si les spectraèdres ont été largement étudiés dans le cas réel, en 2016  Allamigeon, Gaubert et Skomra ont ouvert la voie à l'étude des spéctraèdres sur les corps non-archimédien dans \cite{allamigeon_tropical_2020} en définissant les spectraèdres tropicaux.

L'objectif de ce stage était alors d'essayer de trouver une définition de spectraèdre générale sur les corps non-archimédien. (Rappelons qu'un corps (valué) non-archimédien est un corps muni d'une valeur absolue\footnote{une valeur absolue sur un corps est une norme sur ce même corps compatible avec le produit.} $\left| \cdot  \right|$ vérifiant l'inégalité non-archimédienne : pour tous $ x,y \in \mathbb{K}  \left| x+y \right|\le \max\left( \left| x \right|, \left| y \right|\right)$ ). En s'appuyant, pour ce faire, sur les corps $p$-adiques. Un corps $p$-adique $\mathbb{Q}_{p}$ étant un ensemble de nombres définis par les sommes formelles $x = \ldots + x_k p^k + \ldots + x_1 p + x_0 +x_{-1} p^{-1} + \ldots x_{n}p^n$ avec $n \in \mathbb{Z}$ et où les $(x_k)_{k\ge m}$ sont éléments de $\{0,\ldots,p-1\} $, pour $p$ un nombre premier fixé. On peut munir ces corps de la valuation $p$-adique $\val\left(x\right) = \sup \{i \ge m | x_{i}\neq 0\} $ qui définit une valeur absolue non-archimédienne $\left| \cdot  \right|_p : x\mapsto p^{-\val\left(x\right)} $.

Ce rapport propose une définition de spectraèdre sur les corps $p$-adiques. Pour ce faire, on introduira une nouvelle notion, celle de matrice semi-définie positive. Une matrice à coefficients $p$-adiques étant semi-définie positive si et seulement si les racines de son polynôme caractéristiques sont de valuation positive. Ce qui permet de définir les spéctraèdres comme les matrices linéaires $A(x) = A_0 + x_1 A_1 + \ldots x_s A_s$ semi-définies positives avec $x = \left( x_1,\ldots,x_s \right)$ parcourant $\mathbb{Q}_{p} ^s$ et $A_0,\ldots,A_s$ quelconques fixées. On peut alors en déduire le principal résultat découvert lors de ce stage : les couronnes $p$-adiques sont des projections de spectraèdres. De plus, ce rapport définit les polyèdres $p$-adiques comme les ensembles de points $x \in \mathbb{Q}_{p} ^s$ définis par inégalités de la forme $\val\left( \ell_1(x)\right)\ge 0,\ldots, \val\left( \ell_n\left( x \right) \right)\ge 0$ pour $\ell_1,\ldots, \ell_n$ des formes linéaires $p$-adiques.
Ainsi, si le temps a manqué pour proposer des résultats sur la résolution de la programmation semi-définie positive $p$-adique, il sera toute fois présenté un algorithme résolvant la programmation linéaire en $O\left( \complalgo \right) $, où $m$ et $n$ sont les dimension de la matrice de contraintes. De plus, des pistes pour la résolution du problème $LMI$ ( \textit{Linear Matrix Inequality}) $p$-adique visant à déterminer la vacuité ou non d'un spectraèdre sont également évoquées.

### 2023-09-23 rapport/conclusion.tex

\section{Conclusion}
Il a été décrit au cours de ce rapport de nouvelles définitions pour les polyèdres et les spectraèdres sur les corps $p$-adiques. Les polyèdres sont définis par des inégalités de valuation linéaire. On leur a de plus adjoint un algorithme permettant de résoudre la programmation linéaire en $O( \complalgo)$. Afin de définir les spectraèdres sur les corps $p$-adiques il a été nécessaire de trouver une nouvelle définition de matrice semi-définie positive. Pour ce faire l'on s'est débarrassé de la symétrie, obligatoire dans le cas réel, en demandant à ce que les valeurs propres de la matrice soit de valuation positive dans la clôture de $\mathbb{Q}_{p}$. La définition de spectraèdre était alors immédiate et nous a permis de trouver que les couronnes $p$-adiques sont des ombres de spectraèdre, dressant un portrait bien différent du cas réel.

Ces résultats gagneraient toutefois à être d'avantage étudiés, en effet, si la définition des polyèdres dans le cadre choisi semble difficilement pouvoir varier, celle des spectraèdre peut toutefois être discutée. En effet, l'on peut par exemple se demander si l'on obtient de résultats similaires en demandant la symétrie aux matrices semi définies positives, comme dans le cas réel en demandant des condition particulières sur les matrices de sortes à ce que leurs valeurs propres soit dans $\mathbb{Q}_{p} $. De plus, les problèmes informatiques comme la programmation semi-définie ou le problème $\left( LMI \right) $ n'ont pas été résolus (loin s'en faut). Mais il peut toutefois être interessant d'explorer les pistes laissées en \ref{piste} dans d'éventuels travaux futurs.

### 2023-10-03 article/paper_padic_spec.tex
draft

\documentclass[a4paper,12pt]{article}

%\usepackage{amsthm}
\newenvironment{proof}{\hbox{}\vspace{-0.5cm} {\bf Proof:}}{\hfill $\Box$ \\}

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{proposition}{Proposition}
\newtheorem{corollary}{Corollary}
\newtheorem{algorithm}{Algorithm}
\newtheorem{conjecture}{Conjecture}
\newtheorem{condition}{Condition}
\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}
\newtheorem{remark}{Remark}
\newtheorem{problem}{Problem}
\newtheorem{example}{Example}
\usepackage{booktabs}

\textheight235mm
\textwidth165mm
\voffset-10mm
\hoffset-12.5mm
\parindent0cm
\parskip2mm

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{mathrsfs} 
\usepackage{graphicx}
\usepackage{color}
\usepackage{ulem}
\usepackage{bm}

\usepackage{cleveref}

% updates

\newcommand{\R}{\mathbb{R}} % real numbers
\newcommand{\C}{\mathbb{C}} % complex numbers
\newcommand{\N}{\mathbb{N}} % integers

\newcommand{\simone}[1]{{\color{blue} #1}} % simone's comments
\newcommand{\corentin}[1]{{\color{red} #1}} % simone's comments
\newcommand{\tristan}[1]{{\color{olive} #1}} % simone's comments

\title{\bf Title}

\begin{document}

\author{$^{1,2}$,  $^3$}

\footnotetext[1]{CNRS; LAAS; Universit\'e de Toulouse, 7 avenue du colonel Roche, F-31400 Toulouse, France. }

\date{Draft of \today}

\maketitle

\begin{abstract}
\end{abstract}

\section{Introduction}

\end{document}

### 2023-10-03 article/paper_padic_spec.tex
added ref in bib

@@
 
-%\usepackage{amsthm}
 \newenvironment{proof}{\hbox{}\vspace{-0.5cm} {\bf Proof:}}{\hfill $\Box$ \\}
@@
 \newcommand{\simone}[1]{{\color{blue} #1}} % simone's comments
-\newcommand{\corentin}[1]{{\color{red} #1}} % simone's comments
-\newcommand{\tristan}[1]{{\color{olive} #1}} % simone's comments
+\newcommand{\corentin}[1]{{\color{red} #1}} % corentin's comments
+\newcommand{\tristan}[1]{{\color{olive} #1}} % tristan's comments
+
+\usepackage{biblatex}
+\addbibresource{../rapport/bibstage.bib}
 
@@
 
-\author{$^{1,2}$,  $^3$}
+\author{Corentin Cornou$^{1}$, Simone Naldi$^2$ and Tristan Vaccon$^2$}
 
-\footnotetext[1]{CNRS; LAAS; Universit\'e de Toulouse, 7 avenue du colonel Roche, F-31400 Toulouse, France. }
+\footnotetext[1]{ENS Paris-Saclay, Université Paris-Saclay.}
+\footnotetext[2]{Université de Limoges, CNRS, XLIM, Limoges, France.}
 
@@
 \section{Introduction}
+\subsection{Motivations and main results}
+\subsection{Real spectrahedra}
 
+\section{Notation}
+
+\section{Polyhedra and linear programming}
+
+\subsection{Polyhedra}
+\subsection{Linear programmming}
+
+\section{Spectrahedra}
+
+\subsection{Definition}
+\subsection{Annuli (couronnes)}
+\subsection{Polyhedrality}
+Cf. \cite{bhardwaj2015deciding}
+
+\printbibliography
 \end{document}

### 2023-10-05 article/paper_padic_spec.tex
commit by Simone
first par

@@
 \newcommand{\N}{\mathbb{N}} % integers
+\newcommand{\sym}{\mathbb{S}} % matrices symétriques
 
@@
 
-\footnotetext[1]{ENS Paris-Saclay, Université Paris-Saclay.}
+\footnotetext[1]{ENS Paris-Saclay, Université Paris-Saclay, France.}
 \footnotetext[2]{Université de Limoges, CNRS, XLIM, Limoges, France.}
@@
 \subsection{Motivations and main results}
+
+il faudra mentionner (et peut être motiver l'approche p-adique) :
+\begin{itemize}
+\item les questions ouvertes de complexité concernant la programmation semidefinie (pas clair si NP $\cap$ co-NP
+  dans le modele de Turing)
+\item les questions ouvertes géométriques (Conjecture de Lax)
+\end{itemize}
+
 \subsection{Real spectrahedra}
+
+Let $\sym_m(\R)$ be the vector space of $m \times m$ real symmetric matrices. We recall that
+a matrix $M \in \sym_m(\R)$ is called positive semidefinite ($M \succeq 0$) whenever the quadratic
+form $x \mapsto x^TMx$ is globally nonnegative. Recall that by the Spectral Theorem, $M \succeq 0$
+if and only if the eigenvalues of $M$ are nonnegative, if and only if all the principal minors of
+$M$ are nonnegative. The set of positive semidefinite matrices, denoted $\sym_m^+(\R) \subset \sym_m(\R)$,
+is a closed convex cone with non-empty interior in $\sym_m(\R)$.
+
+A {\it (real) spectrahedron} is an affine slice of the
 
@@
 
+\section{Linear matrix inequalities}
+
 \printbibliography

### 2023-10-05 article/paper_padic_spec.tex
realspec

@@
 \newcommand{\sym}{\mathbb{S}} % matrices symétriques
+\renewcommand{\span}[1]{{\text{span}(#1)}} % simone's comments
+\newcommand{\calL}{\mathcal{L}} % simone's comments
 
@@
 
-A {\it (real) spectrahedron} is an affine slice of the
+Let $A_0,A_1,\ldots,A_n \in \sym_m(\R)$, and let $\calL = A_0+\span{A_1,\ldots,A_n}$ be the affine space
+containing $A_0$ and with direction the vector space generated by $A_1,\ldots,A_n$. The intersection
+$\calL \cap \sym_m^+(\R) = \left\{A(x) := A_0+\sum_i x_i A_i \in \sym_m(\R) : A(x) \succeq 0\right\}$, or
+equivalently, its pre-image $S = \{x \in \R^n : A(x) \succeq 0\}$ under the map $x \mapsto A(x)$, is called
+a {\it real spectrahedron}.
 

### 2023-10-05 article/paper_padic_spec.tex
2 par + example elliptope

@@
 Let $A_0,A_1,\ldots,A_n \in \sym_m(\R)$, and let $\calL = A_0+\span{A_1,\ldots,A_n}$ be the affine space
-containing $A_0$ and with direction the vector space generated by $A_1,\ldots,A_n$. The intersection
+containing $A_0$ and with direction the vector space generated by $A_1,\ldots,A_n$ (which we assume linearly
+independent). The intersection
 $\calL \cap \sym_m^+(\R) = \left\{A(x) := A_0+\sum_i x_i A_i \in \sym_m(\R) : A(x) \succeq 0\right\}$, or
 equivalently, its pre-image $S = \{x \in \R^n : A(x) \succeq 0\}$ under the map $x \mapsto A(x)$, is called
-a {\it real spectrahedron}.
+a {\it real spectrahedron}. As affine sections of $\sym_m^+(\R)$, real spectrahedra are closed convex cones,
+but might have empty interior in $\calL$ (resp. in $\R^n$). Moreover, they are basic semialgebraic sets
+defined by sign conditions on the principal minors of the defining matrix as well as sign conditions on the
+coefficients of its characteristic polynomial (cf. \Cref{ell3}).
+
+\begin{example}\label{ell3}
+  The $3$-elliptope is the three-dimensional spectrahedron given by
+  $$
+  \mathcal{E}_3 :=
+  \left\{
+  x
+%  =
+%  \begin{bmatrix}
+%    x_1 \\
+%    x_2 \\
+%    x_3
+%  \end{bmatrix}
+  \in \R^3 :
+  \begin{bmatrix}
+    1 & x_1 & x_2 \\
+    x_1 & 1 & x_3 \\
+    x_2 & x_3 & 1
+  \end{bmatrix}
+  \succeq 0
+  \right\}
+  =
+  \left\{
+  x
+  \in \R^3 :
+  \begin{array}{r}
+    3-x_1^2-x_2^2-x_3^2 \geq 0 \\
+    1+2x_1x_2x_3-x_1^2-x_2^2-x_3^2 \geq 0
+  \end{array}
+  \right\}.
+  $$
+  The polynomials on the right are the coefficients of the univariate polynomial $p(t) = \det(A(x)+t I)$,
+  whose roots are the opposites of the eigenvalues of the defining matrix. Equivalently $\mathcal{E}_3$
+  is defined by positivity of the principal minors of the defining matrix:
+  $$
+  1-x_1^2 \geq 0, 1-x_2^2 \geq 0, 1-x_3^2 \geq 0 \,\,\, \text{ and } \,\,\, 1+2x_1x_2x_3-x_1^2-x_2^2-x_3^2 \geq 0
+  $$
+\end{example}
 

### 2023-10-05 article/paper_padic_spec.tex
encore example elliptope

@@
   $$
-  The polynomials on the right are the coefficients of the univariate polynomial $p(t) = \det(A(x)+t I)$,
+  The polynomials on the right are the (non-constant) coefficients of the univariate polynomial
+  $p(t) = \det(A(x)+t I)$,
   whose roots are the opposites of the eigenvalues of the defining matrix. Equivalently $\mathcal{E}_3$

### 2023-10-09 article/paper_padic_spec.tex
real spectrahedra

--- 2023-10-05 article/paper_padic_spec.tex
@@
 
+\tableofcontents
+
 \section{Introduction}
-\subsection{Motivations and main results}
 
-il faudra mentionner (et peut être motiver l'approche p-adique) :
+\subsection{Context and motivations}
+
+Il faudra entre autre mentionner (et peut être motiver l'approche p-adique) :
 \begin{itemize}
@@
 
+\subsection{Main results}
+
+\section{Preliminaries}
+
+\subsection{Notation}
+
 \subsection{Real spectrahedra}
 
-Let $\sym_m(\R)$ be the vector space of $m \times m$ real symmetric matrices. We recall that
-a matrix $M \in \sym_m(\R)$ is called positive semidefinite ($M \succeq 0$) whenever the quadratic
-form $x \mapsto x^TMx$ is globally nonnegative. Recall that by the Spectral Theorem, $M \succeq 0$
-if and only if the eigenvalues of $M$ are nonnegative, if and only if all the principal minors of
-$M$ are nonnegative. The set of positive semidefinite matrices, denoted $\sym_m^+(\R) \subset \sym_m(\R)$,
+Let $\sym_m(\R)$ be the vector space of $m \times m$ real symmetric matrices. A matrix $M \in \sym_m(\R)$
+is called {\it positive semidefinite} ($M \succeq 0$) whenever the quadratic
+form $x \mapsto x^TMx$ is nonnegative for all $x\in \R^n$. By the Spectral Theorem, $M \succeq 0$
+if and only if the eigenvalues of $M$ are nonnegative, and this is equivalent to all the principal minors
+of $M$ being nonnegative. The set of positive semidefinite matrices, denoted $\sym_m^+(\R) \subset \sym_m(\R)$,
 is a closed convex cone with non-empty interior in $\sym_m(\R)$.
@@
 Let $A_0,A_1,\ldots,A_n \in \sym_m(\R)$, and let $\calL = A_0+\span{A_1,\ldots,A_n}$ be the affine space
-containing $A_0$ and with direction the vector space generated by $A_1,\ldots,A_n$. The intersection
+containing $A_0$ and with direction the vector space spanned by $A_1,\ldots,A_n$ (which we assume linearly
+independent). The intersection
 $\calL \cap \sym_m^+(\R) = \left\{A(x) := A_0+\sum_i x_i A_i \in \sym_m(\R) : A(x) \succeq 0\right\}$, or
 equivalently, its pre-image $S = \{x \in \R^n : A(x) \succeq 0\}$ under the map $x \mapsto A(x)$, is called
-a {\it real spectrahedron}.
+a {\it real spectrahedron}. As affine sections of $\sym_m^+(\R)$, real spectrahedra are closed convex sets,
+but might have empty interior in $\calL$ (resp. in $\R^n$). Moreover, they are basic semialgebraic sets,
+defined by sign conditions on the principal minors of the defining matrix as well as sign conditions on the
+coefficients of its characteristic polynomial (cf. \Cref{ell3}).
 
-\section{Notation}
+\begin{example}\label{ell3}
+  The $3$-elliptope is the three-dimensional spectrahedron given by
+  $$
+  \mathcal{E}_3 :=
+  \left\{
+  x
+  \in \R^3 :
+  \begin{bmatrix}
+    1 & x_1 & x_2 \\
+    x_1 & 1 & x_3 \\
+    x_2 & x_3 & 1
+  \end{bmatrix}
+  \succeq 0
+  \right\}
+  =
+  \left\{
+  x
+  \in \R^3 :
+  \begin{array}{r}
+    3-x_1^2-x_2^2-x_3^2 \geq 0 \\
+    1+2x_1x_2x_3-x_1^2-x_2^2-x_3^2 \geq 0
+  \end{array}
+  \right\}.
+  $$
+  The polynomials on the right are the (non-constant) coefficients of the univariate polynomial
+  $p(t) = \det(A(x)+t I)$,
+  whose roots are the opposites of the eigenvalues of the defining matrix. Equivalently $\mathcal{E}_3$
+  is defined by positivity of the principal minors of the defining matrix:
+  $$
+  1-x_1^2 \geq 0, \,\,\, 1-x_2^2 \geq 0, \,\,\, 1-x_3^2 \geq 0 \,\,\, \text{ and } \,\,\, 1+2x_1x_2x_3-x_1^2-x_2^2-x_3^2 \geq 0
+  $$
+\end{example}
+
+The optimization problem of miminizing a linear function over a real spectrahedron is called {\it semidefinite programming} (SDP).
+Given $C,A_0,A_1,\ldots,A_n \in \sym_m(\R)$, the corresponding semidefinite program is defined as
+\begin{equation}
+  \label{SDP}
+\begin{array}{rcll}
+  p^* & := & \inf_{x \in \R^n} & \left\langle c, x \right\rangle \\
+  &    & \text{s.t.}         & A_0+\sum_{i=1}^n x_i A_i \succeq 0.
+\end{array}
+\end{equation}
+Since real polyhedra are special cases of real spectrahedra, SDP is a generalization of linear programming (LP).
+In a fixed-precision model of computation, SDP is solvable in polynomial time in the input size (matrix size,
+number of variables, bit size of the coefficients), in $\log(\frac{1}{\varepsilon})$ (where $\varepsilon$ is the
+precision) and $\log(\frac{1}{R})$, where $R$ is an {\it a priori} upper bound on the norm of the solution,
+cf. \cite[Sec.1.9]{deKlerk}. In exact arithmetic, the complexity status of SDP is essentially open but complexity
+bounds are known based either on general quantifier elimination \cite{ramana1997exact,porkolab1997complexity}
+or on the determinantal structure of the constraints \cite{henrion2016exact}.
+
+A more general class of convex semialgebraic sets are obtained by linear projections of real spectrahedra
+called {\it semidefinite representable sets} (or spectrahedral shadows): these are sets of the form
+$$
+P = \left\{x = \left[\begin{smallmatrix} x_1 \\ \vdots \\ x_n \end{smallmatrix}\right] \in \R^n : \exists\,y\in\R^m, \, A_0 + \sum_{i=1}^n x_i A_i + \sum_{j=1}^m y_j B_j \succeq 0\right\}
+$$
+
+\begin{example}
+\label{fermat_quartic}
+The basic closed semialgebraic set $P = \{(x_1,x_2) \in \R^2 : 1-x_1^4-x_2^4 \geq 0\}$ is not a spectrahedron
+but it is semidefinite representable:
+$$
+P = \left\{x = \begin{bmatrix} x_1 \\ x_2 \end{bmatrix} \in \R^2 :
+\exists\, (y_1,y_2) \in \R^2, \,
+\begin{bmatrix}
+  1+y_1 & y_2 \\
+  y_2 & 1-y_1
+\end{bmatrix}
+\bigoplus
+\begin{bmatrix}
+  1 & x_1 \\
+  x_1 & y_1
+\end{bmatrix}
+\bigoplus
+\begin{bmatrix}
+  1 & x_2 \\
+  x_2 & y_2
+\end{bmatrix}
+\succeq 0
+\right\}
+$$
+\end{example}
 

### 2023-10-10 article/paper_padic_spec.tex
Ajout notations + Serre dans la biblio.

@@
 
+\usepackage{stmaryrd} %for double brackets
+
 % updates
@@
 \newcommand{\tristan}[1]{{\color{olive} #1}} % tristan's comments
+
+%p-adic commands
+\DeclareMathOperator{\val}{val}
+\def\QQ{\ensuremath{\mathbb{Q}}}
+\def\ZZ{\ensuremath{\mathbb{Z}}}
+\newcommand{\OK}{\mathcal{O}_K}
 
@@
 \subsection{Notation}
+
+Throughout the paper, $K$ refers to a complete,
+discrete valuation field, $\val : K \twoheadrightarrow \ZZ \cup \{+\infty\}$ to its valuation,
+$\OK$ its ring of integers and $\pi$ a uniformizer.
+For $k \in \N$, we write $O(\pi^k)$ for $\pi^k \OK.$
+A typical example of $K$ as above is the field of $p$-adic numbers 
+$\QQ_p$ (equipped with the $p$-adic valuation). For this example, we 
+have $\OK = \ZZ_p$.
+Another example is the field of Laurent series
+$K=\QQ ((T))$ equiped with $T$-adic valuation.
+In this case,  $\OK = \QQ \llbracket T \rrbracket$.
+We refer to Serre's Local Fields \cite{Serre} for a
+general introduction to such fields
+and to Caruso's course on $p$-adic computations \cite{caruso_computations_2017}
+for an introduction to effective computations
+over them
 

### 2023-10-25 article/paper_padic_spec.tex
spectrahedron and polyhedron

@@
 \newtheorem{proposition}{Proposition}
-\newtheorem{corollary}{Corollary}
+\newtheorem{corollary}{corollary}
 \newtheorem{algorithm}{Algorithm}
@@
 \section{Polyhedra and linear programming}
+\subsection{Polyhedra}
 
-\subsection{Polyhedra}
-\subsection{Linear programmming}
+\begin{definition}
+	We call {\it convex $p$-adic polyhedra} subsets of $K^s$ defined by linear inequalities $\val\left( \ell_1(x)\right)\ge 0$,\ldots, $ \val\left( \ell_n\left( x \right) \right)\ge 0$ for $ \ell_1,\ldots, \ell_n $ fixed linear forms and for all $x \in K ^s$.
+
+\end{definition}
+
+\begin{example}
+	The closed unit ball of $K^s$ for the infinity norm [not sure if it is really used ] is convex polyhedron.It is the set of $\left( x_1,\ldots,x_s \right) \in  ^s$ so that $$
+	\begin{pmatrix} x_1 &  & & \\
+		& x_2 &0 &  \\
+		&  0& \ddots & \\
+		&  & & x_s/
+	\end{pmatrix} \ge 0.$$ which is in fact $\OK^s$.
+
+\end{example}
+
+\subsection{linear programming}
+	We call { \it $p$-adic programming} the problem :
+\begin{equation}
+	\tag{PLp}
+	\begin{matrix}
+		\text{Minimize } \val\left(\left<c,x \right>\right) \text{ subject to }\\
+		Ax + b \ge 0
+	\end{matrix}
+	\label{eqn:Proglinp}
+\end{equation}
+
+with $x$ a vector of $K ^n$, and $c$ a fixed vector of size $n$ that represents the cost, $A$ a fixed $m \times n $ matrix and $b$ fiexed a vector of size $m$.
+
+The method used in this article consists in reducing the Smith normal form of the matrix $A$.
+
+\begin{definition} Smith normal form
+
+	We call {\it Smith normal form} of a matrix $M \in \mathcal{M}_{m,n}\left(K \right) $ of rank $r$ the only matrix $S$ of the form $$S =  
+	\begin{pmatrix} p^{a_1} & \\
+		& \ddots \\
+		& & p^{ar}\\
+		& & & 0\\
+		& & & & \ddots \end{pmatrix} $$
+	so that $(a_1)_{1\le i\le r}$ is a increasing sequence of integers and $M$ can be written $M =  Q^{-1} S P$ for $P \in \mathcal{G}L_n\left( \OK \right) $, $Q \in \mathcal{G}L_m\left( \OK \right) $.
+\end{definition}
+
+\begin{remark}
+	\begin{enumerate}%[label=\roman*.]
+		\item The coefficient of the Smith normal Form are unique and called \textit{invariant factors}.
+		\item The $p$-adic valuation of the first coefficient of the Smith normal form of a matrix $M \in \mathcal{M}_n \left( K \right) $ is the minimum of the valuations of the matrix $M$'s terms.
+		\item In particular, the the normal Smith form of matrix of $\mathcal{M}_n \left( \OK \right) $ have coefficients in $\OK$ .
+		\item The $r = \text{rank} M$ first diagonals coefficients of $S$ are exactly its non-zero coefficient.
+	\end{enumerate}
+
+\end{remark}
+
+In order to be able to use the Smith normal form to resolve \ref{eqn:Proglinp} we need the following lemma :
+
+\begin{lemma}
+	Forall $p$-adic numbers $z \in K ^n$ and matrix $M \in \mathcal{M}_{m,n}\left( K  \right)  $ if $z\ge 0$ and $M\ge 0$ then $Mz\ge 0$.  
+\end{lemma}
+\begin{proof}
+	$\OK$ is a ring.
+\end{proof}
+
+If we put the matrix $A$ of \ref{eqn:Proglinp} in its normal Smith form, it comes that resolving \ref{eqn:Proglinp} is equivalent to resolve :
+
+\begin{equation}
+	\tag{PLp'}
+	\begin{matrix}
+		\text{Minimize } \val\left(\left<c',x \right>\right) \text{ subject to }\\
+		Sy + b' \ge 0
+	\end{matrix}
+	\label{eqn:Proglinp2}
+\end{equation}
+where $b' = Qb$, $c' = P^Tc$, $S$ is the Smith normal form of $A$ and $A = Q^{-1} S P$ for some $P \in \mathcal{G}L_m\left( \OK \right)$ and $ Q \in \mathcal{G}L_n\left( \OK \right)$.
+
+\begin{remark}
+
+	We have then the following results
+	\begin{enumerate}
+		\item $x^*$ is a feasible solution of \ref{eqn:Proglinp} if and only if $y^* = P x^*$ is a feasible solution of \ref{eqn:Proglinp2}
+		\item \ref{eqn:Proglinp2} have feasible solutions if and only if the $m-r$ coefficients of $b'$ are non-zero, with $r$ the rank of $S$.
+		\item If at least one of the $n-r$ last coefficients of $c'$ is non-zero \ref{eqn:Proglinp2} is unbounded and does not have a soution.
+	\end{enumerate}
+
+\end{remark}
+
+\begin{proposition}
+	\begin{itemize}~
+
+		\item[$\circ$] If not all the $m-r$ coefficients of $b'$ are zeros then there is no $y \in K ^n$ so that $A'y+b' \ge  0$.
+		\item[$\circ$] If not all the $n-r$ coefficients of $c'$ are zero then the problem is unbounded and does not have solution. \end{itemize} 
+\end{proposition}
+If one considers only the itération of the problem which have des solution one can reduce the problem by only taking acount the $r$ first coefficients of $y, b', c'$ and the submatrix of $S$ made with only $r$ first lines et columns of and which coefficients are exactly the nonzero invariants factors.
+The set $Adm$ of the feasible solutions can then be written as the set of vectors $y \in \mathbb{Q}_{ p } ^n$ that verifies $\forall 1 \le i\le r \ s_i y_i + b'_i \in \OK$ i.e.
+that verifies :
+
+\begin{equation}
+	\forall 1 \le i\le r  \ y_i \in -\frac{b’_i}{s_i} + \frac{1}{s_i} \OK
+\end{equation}
+
+Resolving \ref{eqn:Proglinp2} consists in minimizing $\val\left(\left<c',y \right>\right)$ over $Adm$.
+The image of $Adm$ by $y \mapsto \left<c',y \right>$ is $\sum_{i=1}^r -c'_i.\frac{b'_i}{s_i} + \sum_{i=1}^r\left( \frac{c'_i}{s_{i}} \OK \right)$ which can be rewritten in
+$$\left<c',Adm \right> = \lambda + p^{v} \OK$$
+with $\lambda = \sum\limits_{i=1}^r -c'_i.\frac{b'_i}{s_i}$ et $v = \min\limits_{1\le i\le r} \val \frac{c'_{i}}{s_{i}} $.
+
+The result can be split depending on the valuation of $\lambda$.
+\begin{itemize}
+	\item If $\val( \lambda) < v$ the minimum of $y\mapsto \val\left(\left<c',y \right>\right)$ over $Adm$ is reached in any point of $Adm$ and is equal to $\val\left( \lambda\right)$.
+	\item If $\val\left( \lambda \right) \ge v$ then $\lambda \in p^{v} \OK$ and the minimum is $v $ and is reached in any points $y$ of $Adm$ that verifies 
+	$$\val\sum \limits_{\begin{array}{c} 1\le i\le r\\ \val\left(c'_{i}/{s_{i}} \right) = v  \end{array}   } y_{i} = 0.$$
+
+\end{itemize}
+\begin{remark}
+	To maximize the valuation of a linear map over a convex $p$-adic polyhedron instead of minimizing it (which is equuivalent to minimize the absolute value) the same reasoning can be apllied.
+The only differnece being that if $\val\left( \lambda\right) < v$ the problem is unbounded and then does not have any solution.
+\end{remark}
 
@@
 \subsection{Definition}
+\newcommand\mat{postive semidefinite matrix } 
+\newcommand\Mat{Positive semidefinite matrix }
+\newcommand\mats{positive semidefinite matrices }
+\newcommand\Mats{positive semidefinite matrices }
+\begin{definition}
+	We call {\it \mat} any matrix $M \in \mathcal{M}_n\left( K \right) $ whose eigenvalues have nonegative valuation (in $\overline{K}$) .
+
+	We will denote as $ \mathcal{M}_n^+\left( K \right)$ the set of \mats and we will write $M \succeq 0$ if $M \in \mathcal{M}_n^+\left( K\right) $.
+\end{definition}
+\begin{theorem}
+	\label{caracsdp}
+	Characterization of the \mats
+
+	A matrixe is positive semidefinite if and only if its characteristic polynomial have coefficients in $\OK$ .
+
+\end{theorem}
+
+\begin{corollary}
+	$\mathcal{M}_n(\OK) \subset \mathcal{M}_n^+\left( K \right)$ 
+\end{corollary}
+
+\textit{Preuve : }  $\OK$ is a ring therefore the characteristic polynomial of matrix whose coefficients are $p$-adic integers have coefficients ins $Pp$. We conclude by \ref{caracsdp} .
+
+\begin{remark}
+	In general, the reciprocal inclusion is false [not sure about this one].
+For instance the characteristic polynomial of $M = \begin{pmatrix} 5 + \frac{3}{5} & \frac{4}{5} \\ \frac{4}{5} & -\frac{3}{5} \end{pmatrix} $ is $\chi_M = X^2  - 5 X - 4$.
+However when seen as an element of $\mathbb{Q}_5$, $\chi_M \in \mathbb{Z}_5[X]$ then $M \in \mathcal{M}_2^+\left( \mathbb{Q}_5 \right)$ but no coefficient of $M$ is in $\mathbb{Z}_5 $
+\end{remark}
+
+\begin{proposition}
+	The set $\mathcal{M}_n^+\left( K \right)$ is :
+	\begin{enumerate}%[label = \textit{\roman*}.]
+		\item open
+		\item closed
+		%\item a convex cone
+	\end{enumerate}
+\end{proposition}
+
+\textit{Preuve :}  
+Firstly, $\OK[X]$ is closed and open in $\mathbb{Q}_{ p }[X] $ equiped with the infinitiy norm $\|.\|_\infty : P = \sum_{k=1}^{n} a_k X^k \to \sup |a_k|_p$.
+$\OK$ is indeed the open unit ball for $\|\cdot \|_\infty$ which defines a discrete distance for which open balls are also closed.
+Furthermore, $\mathcal{M}^+_{n}\left(K \right)  = \chi^{-1}( \OK[X]) $ where $\chi$ is the function that maps its characteristic polynomial to a matrix which is continuous.
+
+%Le $iii$. est laissé en exercice au lecteur. 
+% Je ne parle plus de convexité dans le rapport mais on ne sait jamais
+%\input{convexemple.tex}
+
+\begin{definition}
+	We call {\it $p$-adic spectrahedron} the intersection of $\mathcal{M}_n^+\left( K \right) $ with an affine plan $\mathcal{L}$ of $\mathcal{M}_n\left( K \right) $.
+\end{definition}
+
+\begin{remark}
+	As in the real case, the spectrahedron associated with the affine plan $\mathcal{L}$ will often be identified with its preimage in $K^s$ (i.e.
+the set of vectors $x \in K ^s$ so that the linear matrix $A(x) = A_0 + x_1A_1 + \ldots + x_sA_s$ is positive semidefinite with $A_0,A_1,\ldots,A_s$ spanning $\mathcal{L}$).
+\end{remark}
+
+The latter allows gives us the following property :
+\begin{proposition}
+	A convex $p$-adic polyhedron is $p$-adic spectrahedron.
+\end{proposition}
+\begin{proof}
+	Same as in the real case (maybe modify it or add the link to real proof).
+\end{proof}
+
 \subsection{Annuli (couronnes)}
+\begin{definition}
+	Annulus
+
+	We call {\it annulus} a set $A$ defined as $C = \{x \in K  | a\le \val\left(x\right) \le b\} $ for $a < b$ two nonnegative real numbers.
+\end{definition}
+
+\begin{theorem}
+	Annuli are spectrahedral shadows.
+\end{theorem}
+
+\textit{Preuve :}
+Let $A$ be the annuli defined by $a<b \in R^*_+$.
+
+We consider for all $x,y \in K $ the matrix  $$M(x,y) :=
+\begin{pmatrix} 
+	p^ax & 0 & 0 & 0 \\
+	0 & p^{-b}y & 0 & 0 \\
+	0 & 0 & p^{-1} & p^{-1}x \\
+	0 & 0 & p^{-1}y & - p^{-1}  \\
+\end{pmatrix} $$ and the associated spectrahedron $\mathcal{S}= \{(x,y) \in K  : M(x,y) \succeq 0\} $
+
+Let us show that $x \in C$ if and only if  $\exists y \in K \left( x,y \right) \in \mathcal{S}$.
+
+Let $x,y$ be two $p$-adic numbers.
+$M(x,y)$ can be decomposed in three blocks : $p^ax$, $p^{-b}y $ and $M'(x,y) = \begin{pmatrix} p^{-1} & p^{-1}x \\ p^{-1} y & p^{-1}\end{pmatrix} $.
+Using \ref{caracsdp} we know that $M(x,y)$ is positive semidefinfite if and only if
+$
+\begin{cases}
+	p^ax \ge 0 \\
+	p^{-b}y \ge 0\\
+	\text{Tr}M'\left( x,y \right) = 0 \ge 0\\
+	\text{det} M'(x,y ) = p^{-2}\left( xy-1 \right)  \ge 0 
+\end{cases}
+$ 
+that is if and only if 
+\begin{equation}
+	\label{eq:caracsdp} 
+	\begin{cases} 
+		\val\left(x\right)\ge a\\
+		\val\left(y\right)\ge -b\\
+		p^{-2} \left( xy-1 \right) \ge 0
+	\end{cases}
+\end{equation}
+
+Therefore $x \in C$ if and only if there exists $y \in K $ so that $(x, y)$ verifies \ref{eq:caracsdp}.
+Si $x, y$ verifies indeed \ref{caracsdp} then $\val\left(x\right)\ge a$, $\val\left(y\right)\ge -b$ and $p^{-2} \left( xy-1 \right) \ge 0$ implies that $\val\left(x\right)+\val\left(y\right)=\val\left(xy\right) = \val\left(-1\right) =0$ and therefore that $\val\left(x\right)=-\val\left(y\right)\le -(-b)  =b$, so $x \in $.
+Reciprocally if $x \in C$ then $(x,x^{-1}) $ verifies \ref{eq:caracsdp}  .
+
 \subsection{Polyhedrality}

### 2023-10-25 article/paper_padic_spec.tex
corrected p-adic linear programming

@@
 \begin{definition}
-	We call {\it convex $p$-adic polyhedra} subsets of $K^s$ defined by linear inequalities $\val\left( \ell_1(x)\right)\ge 0$,\ldots, $ \val\left( \ell_n\left( x \right) \right)\ge 0$ for $ \ell_1,\ldots, \ell_n $ fixed linear forms and for all $x \in K ^s$.
+	We call {\it polyhedra} subsets of $K^s$ defined by linear inequalities $\val\left( \ell_1(x)\right)\ge 0$,\ldots, $ \val\left( \ell_n\left( x \right) \right)\ge 0$ for $ \ell_1,\ldots, \ell_n $ fixed linear forms and for all $x \in K ^s$.
 
@@
 \subsection{linear programming}
-	We call { \it $p$-adic programming} the problem :
+	We call { \it $p$-adic linear programming} the problem :
 \begin{equation}
@@
 
-with $x$ a vector of $K ^n$, and $c$ a fixed vector of size $n$ that represents the cost, $A$ a fixed $m \times n $ matrix and $b$ fiexed a vector of size $m$.
+with $x$ a vector of $K ^n$, and $c$ a fixed vector of size $n$ that represents the cost, $A$ a fixed $m \times n $ matrix and $b$ fixed a vector of size $m$.
 
@@
 		& \ddots \\
-		& & p^{ar}\\
+		& & p^{a_r}\\
 		& & & 0\\
 		& & & & \ddots \end{pmatrix} $$
-	so that $(a_1)_{1\le i\le r}$ is a increasing sequence of integers and $M$ can be written $M =  Q^{-1} S P$ for $P \in \mathcal{G}L_n\left( \OK \right) $, $Q \in \mathcal{G}L_m\left( \OK \right) $.
+	so that $(a_1)_{1\le i\le r}$ is a increasing sequence of integers and $M$ can be written $M =  Q^{-1} S P$ for $P \in \mathcal{G}L_n\left( \ZZ_p \right) $, $Q \in \mathcal{G}L_m\left( \ZZ_p \right) $.
 \end{definition}
@@
 	\begin{enumerate}%[label=\roman*.]
-		\item The coefficient of the Smith normal Form are unique and called \textit{invariant factors}.
-		\item The $p$-adic valuation of the first coefficient of the Smith normal form of a matrix $M \in \mathcal{M}_n \left( K \right) $ is the minimum of the valuations of the matrix $M$'s terms.
-		\item In particular, the the normal Smith form of matrix of $\mathcal{M}_n \left( \OK \right) $ have coefficients in $\OK$ .
+		\item The coefficient of the Smith normal form are unique and called \textit{invariant factors}.
+		\item The valuation of the first coefficient of the Smith normal form of a matrix $M \in \mathcal{M}_n \left( \QQ_p \right) $ is the minimum of the valuations of the matrix $M$'s terms.
+		\item In particular, the the normal Smith form of matrix of $\mathcal{M}_n \left( \OK \right) $ have coefficients in $\ZZ_p$ .
 		\item The $r = \text{rank} M$ first diagonals coefficients of $S$ are exactly its non-zero coefficient.
@@
 \begin{lemma}
-	Forall $p$-adic numbers $z \in K ^n$ and matrix $M \in \mathcal{M}_{m,n}\left( K  \right)  $ if $z\ge 0$ and $M\ge 0$ then $Mz\ge 0$.  
+	Forall $p$-adic numbers $z \in \QQ_p ^n$ and matrix $M \in \mathcal{M}_{m,n}\left( \QQ_p  \right)  $ if $z\ge 0$ and $M\ge 0$ then $Mz\ge 0$.  
 \end{lemma}
 \begin{proof}
-	$\OK$ is a ring.
+	$\ZZ_p$ is a ring.
 \end{proof}
@@
 \end{equation}
-where $b' = Qb$, $c' = P^Tc$, $S$ is the Smith normal form of $A$ and $A = Q^{-1} S P$ for some $P \in \mathcal{G}L_m\left( \OK \right)$ and $ Q \in \mathcal{G}L_n\left( \OK \right)$.
+where $b' = Qb$, $c' = P^Tc$, $S$ is the Smith normal form of $A$ and $A = Q^{-1} S P$ for some $P \in \mathcal{G}L_m\left( \ZZ_p \right)$ and $ Q \in \mathcal{G}L_n\left( \ZZ_p \right)$.
 
@@
 \begin{remark}
-	To maximize the valuation of a linear map over a convex $p$-adic polyhedron instead of minimizing it (which is equuivalent to minimize the absolute value) the same reasoning can be apllied.
+	To maximize the valuation of a linear map over a convex $p$-adic polyhedron instead of minimizing it (which is equuivalent to minimize the absolute value) the same reasoning can be aplied.
 The only differnece being that if $\val\left( \lambda\right) < v$ the problem is unbounded and then does not have any solution.
@@
 
-	A matrixe is positive semidefinite if and only if its characteristic polynomial have coefficients in $\OK$ .
+	A matrix is positive semidefinite if and only if its characteristic polynomial have coefficients in $\OK$ .
 
@@
 
-\textit{Preuve : }  $\OK$ is a ring therefore the characteristic polynomial of matrix whose coefficients are $p$-adic integers have coefficients ins $Pp$. We conclude by \ref{caracsdp} .
+\begin{proof}
+$\OK$ is a ring therefore the characteristic polynomial of matrix whose coefficients are $p$-adic integers have coefficients ins $Pp$. We conclude by \ref{caracsdp} .
+\end{proof}
 
 \begin{remark}
-	In general, the reciprocal inclusion is false [not sure about this one].
+	In general, the reverse inclusion is false.
 For instance the characteristic polynomial of $M = \begin{pmatrix} 5 + \frac{3}{5} & \frac{4}{5} \\ \frac{4}{5} & -\frac{3}{5} \end{pmatrix} $ is $\chi_M = X^2  - 5 X - 4$.
@@
 \begin{definition}
-	We call {\it $p$-adic spectrahedron} the intersection of $\mathcal{M}_n^+\left( K \right) $ with an affine plan $\mathcal{L}$ of $\mathcal{M}_n\left( K \right) $.
+	We call {\it spectrahedron} the intersection of $\mathcal{M}_n^+\left( K \right) $ with an affine plan $\mathcal{L}$ of $\mathcal{M}_n\left( K \right) $.
 \end{definition}
@@
 \begin{proposition}
-	A convex $p$-adic polyhedron is $p$-adic spectrahedron.
+	A polyhedron is a spectrahedron.
 \end{proposition}

### 2023-10-25 article/paper_padic_spec.tex
serre reference

@@
 In this case,  $\OK = \QQ \llbracket T \rrbracket$.
-We refer to Serre's Local Fields \cite{Serre} for a
+We refer to \cite{Serre:1979} for a
 general introduction to such fields

### 2023-10-26 article/paper_padic_spec.tex
modifs sec 2.2

@@
 
+%\usepackage{mathptmx}
+
 % updates
@@
 \newcommand{\OK}{\mathcal{O}_K}
+
+\newcommand{\exend}{\hfill $\blacksquare$}
 
@@
 Another example is the field of Laurent series
-$K=\QQ ((T))$ equiped with $T$-adic valuation.
+$K=\QQ(\!(T)\!)$ equiped with $T$-adic valuation.
 In this case,  $\OK = \QQ \llbracket T \rrbracket$.
@@
 general introduction to such fields
-and to Caruso's course on $p$-adic computations \cite{caruso_computations_2017}
-for an introduction to effective computations
-over them
+and to X.~Caruso's course on $p$-adic computations \cite{caruso_computations_2017}
+for an introduction to effective computations over $p$-adic numbers.
 
@@
 
-Let $\sym_m(\R)$ be the vector space of $m \times m$ real symmetric matrices. A matrix $M \in \sym_m(\R)$
+Let $\sym_d(\R)$ be the vector space of $d \times d$ real symmetric matrices. A matrix $M \in \sym_d(\R)$
 is called {\it positive semidefinite} ($M \succeq 0$) whenever the quadratic
@@
 if and only if the eigenvalues of $M$ are nonnegative, and this is equivalent to all the principal minors
-of $M$ being nonnegative. The set of positive semidefinite matrices, denoted $\sym_m^+(\R) \subset \sym_m(\R)$,
+of $M$ being nonnegative. The set of positive semidefinite matrices, denoted $\sym_d^+(\R) \subset \sym_d(\R)$,
 is a closed convex cone with non-empty interior in $\sym_m(\R)$.
 
-Let $A_0,A_1,\ldots,A_n \in \sym_m(\R)$, and let $\calL = A_0+\span{A_1,\ldots,A_n}$ be the affine space
+Let $A_0,A_1,\ldots,A_n \in \sym_d(\R)$, and let $\calL = A_0+\span{A_1,\ldots,A_n}$ be the affine space
 containing $A_0$ and with direction the vector space spanned by $A_1,\ldots,A_n$ (which we assume linearly
 independent). The intersection
-$\calL \cap \sym_m^+(\R) = \left\{A(x) := A_0+\sum_i x_i A_i \in \sym_m(\R) : A(x) \succeq 0\right\}$, or
+$\calL \cap \sym_d^+(\R) = \left\{A(x) := A_0+\sum_i x_i A_i \in \sym_d(\R) : A(x) \succeq 0\right\}$, or
 equivalently, its pre-image $S = \{x \in \R^n : A(x) \succeq 0\}$ under the map $x \mapsto A(x)$, is called
-a {\it real spectrahedron}. As affine sections of $\sym_m^+(\R)$, real spectrahedra are closed convex sets,
+a {\it real spectrahedron}. As affine sections of $\sym_d^+(\R)$, real spectrahedra are closed convex sets,
 but might have empty interior in $\calL$ (resp. in $\R^n$). Moreover, they are basic semialgebraic sets,
@@
 \begin{example}\label{ell3}
-  The $3$-elliptope is the three-dimensional spectrahedron given by
+  Let $d=n=3$. The $3$-elliptope is the three-dimensional spectrahedron given by
   $$
@@
   $$
+  \exend
 \end{example}
@@
 \end{equation}
-Since real polyhedra are special cases of real spectrahedra, SDP is a generalization of linear programming (LP).
-In a fixed-precision model of computation, SDP is solvable in polynomial time in the input size (matrix size,
+Real polyhedra (subsets of $\R^n$ defined by finitely many affine inequalities) are special cases of real
+spectrahedra, where the defining matrices $A_0, \ldots, A_n$ can be chosen diagonal. Thus SDP is a generalization
+of linear programming (LP). In a fixed-precision model of computation, SDP is solvable in polynomial time in the
+input size (matrix size,
 number of variables, bit size of the coefficients), in $\log(\frac{1}{\varepsilon})$ (where $\varepsilon$ is the
@@
 bounds are known based either on general quantifier elimination \cite{ramana1997exact,porkolab1997complexity}
-or on the determinantal structure of the constraints \cite{henrion2016exact}.
+or by exploiting the determinantal structure of the constraints \cite{henrion2016exact}.
 
@@
 \section{Polyhedra and linear programming}
-\subsection{Polyhedra}
+
+%\subsection{Polyhedra}
+
+In this section, we define polyhedra over a complete discrete valuation field $K$ with valuation $\val$,
+and we discuss the associated linear optimization problem.
 
 \begin{definition}
-	We call {\it polyhedra} subsets of $K^s$ defined by linear inequalities $\val\left( \ell_1(x)\right)\ge 0$,\ldots, $ \val\left( \ell_n\left( x \right) \right)\ge 0$ for $ \ell_1,\ldots, \ell_n $ fixed linear forms and for all $x \in K ^s$.
-
+  Let $\ell_1,\ldots,\ell_d \in K[X]_1$ be linear inequalities on $X = (X_1, \ldots, X_n)$.
+  A {\it polyhedron} is a subset $P \subset K^s$ defined by linear inequalities:
+  $P = \val\left( \ell_1(x)\right)\ge 0$,\ldots, $ \val\left( \ell_n\left( x \right) \right)\ge 0$ for $ \ell_1,\ldots, \ell_n $ fixed linear forms and for all $x \in K ^s$.
 \end{definition}
@@
 
-\subsection{linear programming}
+%\subsection{linear programming}
 	We call { \it $p$-adic linear programming} the problem :

### 2023-10-26 article/paper_padic_spec.tex
variables en maj

@@
 \newcommand{\N}{\mathbb{N}} % integers
+\newcommand{\allmat}{\mathbb{M}} % matrices
 \newcommand{\sym}{\mathbb{S}} % matrices symétriques
@@
 
+The $K$-vector space of polynomials of degree $\leq d$ on $X=(X_1,\ldots,X_n)$
+with coefficients in $K$ is denoted by $K[X]_{d}$. The vector space of matrices of
+size $p \times q$ with entries in $K$ is denoted by $\allmat_{p,q}(K)$. For the sake
+of ease of writing, diagonal matrices with entries $a_1,\ldots,a_d$ are denoted by
+$a_1 \oplus \cdots \oplus a_n$.
+
 \subsection{Real spectrahedra}
 
-Let $\sym_d(\R)$ be the vector space of $d \times d$ real symmetric matrices. A matrix $M \in \sym_d(\R)$
+Let $\sym_d(\R) \subset \allmat_{d,d}(\R)$ be the vector space of $d \times d$ real symmetric
+matrices. A matrix $M \in \sym_d(\R)$
 is called {\it positive semidefinite} ($M \succeq 0$) whenever the quadratic
@@
 of $M$ being nonnegative. The set of positive semidefinite matrices, denoted $\sym_d^+(\R) \subset \sym_d(\R)$,
-is a closed convex cone with non-empty interior in $\sym_m(\R)$.
+is a closed convex cone with non-empty interior in $\sym_d(\R)$.
 
@@
 independent). The intersection
-$\calL \cap \sym_d^+(\R) = \left\{A(x) := A_0+\sum_i x_i A_i \in \sym_d(\R) : A(x) \succeq 0\right\}$, or
-equivalently, its pre-image $S = \{x \in \R^n : A(x) \succeq 0\}$ under the map $x \mapsto A(x)$, is called
+$\calL \cap \sym_d^+(\R) = \left\{A(X) := A_0+\sum_i X_i A_i \in \sym_d(\R) : A(X) \succeq 0\right\}$, or
+equivalently, its pre-image $S = \{X \in \R^n : A(X) \succeq 0\}$ under the map $X \mapsto A(X)$, is called
 a {\it real spectrahedron}. As affine sections of $\sym_d^+(\R)$, real spectrahedra are closed convex sets,
@@
   \left\{
-  x
+  X
   \in \R^3 :
   \begin{bmatrix}
-    1 & x_1 & x_2 \\
-    x_1 & 1 & x_3 \\
-    x_2 & x_3 & 1
+    1 & X_1 & X_2 \\
+    X_1 & 1 & X_3 \\
+    X_2 & X_3 & 1
   \end{bmatrix}
@@
   \left\{
-  x
+  X
   \in \R^3 :
   \begin{array}{r}
-    3-x_1^2-x_2^2-x_3^2 \geq 0 \\
-    1+2x_1x_2x_3-x_1^2-x_2^2-x_3^2 \geq 0
+    3-X_1^2-X_2^2-X_3^2 \geq 0 \\
+    1+2X_1X_2X_3-X_1^2-X_2^2-X_3^2 \geq 0
   \end{array}
@@
   The polynomials on the right are the (non-constant) coefficients of the univariate polynomial
-  $p(t) = \det(A(x)+t I)$,
+  $p(T) = \det(A(X)+T I_3)$,
   whose roots are the opposites of the eigenvalues of the defining matrix. Equivalently $\mathcal{E}_3$
@@
   $$
-  1-x_1^2 \geq 0, \,\,\, 1-x_2^2 \geq 0, \,\,\, 1-x_3^2 \geq 0 \,\,\, \text{ and } \,\,\, 1+2x_1x_2x_3-x_1^2-x_2^2-x_3^2 \geq 0
+  1-X_1^2 \geq 0, \,\,\, 1-X_2^2 \geq 0, \,\,\, 1-X_3^2 \geq 0 \,\,\, \text{ and } \,\,\, 1+2X_1X_2X_3-X_1^2-X_2^2-X_3^2 \geq 0
   $$
@@
 The optimization problem of miminizing a linear function over a real spectrahedron is called {\it semidefinite programming} (SDP).
-Given $C,A_0,A_1,\ldots,A_n \in \sym_m(\R)$, the corresponding semidefinite program is defined as
+Given $c \in \R^n$ and $A_0,A_1,\ldots,A_n \in \sym_d(\R)$, the corresponding semidefinite program is defined (in standard dual form) as
 \begin{equation}
@@
 \begin{array}{rcll}
-  p^* & := & \inf_{x \in \R^n} & \left\langle c, x \right\rangle \\
-  &    & \text{s.t.}         & A_0+\sum_{i=1}^n x_i A_i \succeq 0.
+  p^* & := & \inf_{X \in \R^n} & \left\langle c, X \right\rangle \\
+  &    & \text{s.t.}         & A_0+\sum_{i=1}^n X_i A_i \succeq 0.
 \end{array}
@@
 Real polyhedra (subsets of $\R^n$ defined by finitely many affine inequalities) are special cases of real
-spectrahedra, where the defining matrices $A_0, \ldots, A_n$ can be chosen diagonal. Thus SDP is a generalization
-of linear programming (LP). In a fixed-precision model of computation, SDP is solvable in polynomial time in the
+spectrahedra, where the defining matrices $A_0, \ldots, A_n$ can be chosen diagonal, so that $A(X) =
+\ell_1(X) \oplus \cdots \oplus \ell_d(X)$.
+
+In other words, SDP is a generalization
+of Linear Programming (LP). In a fixed-precision model of computation, SDP is solvable in polynomial time in the
 input size (matrix size,
@@
 $$
-P = \left\{x = \left[\begin{smallmatrix} x_1 \\ \vdots \\ x_n \end{smallmatrix}\right] \in \R^n : \exists\,y\in\R^m, \, A_0 + \sum_{i=1}^n x_i A_i + \sum_{j=1}^m y_j B_j \succeq 0\right\}
+P = \left\{X = \left[\begin{smallmatrix} X_1 \\ \vdots \\ X_n \end{smallmatrix}\right] \in \R^n : \exists\,Y\in\R^p, \, A_0 + \sum_{i=1}^n X_i A_i + \sum_{j=1}^p Y_j B_j \succeq 0\right\}
 $$
@@
 \label{fermat_quartic}
-The basic closed semialgebraic set $P = \{(x_1,x_2) \in \R^2 : 1-x_1^4-x_2^4 \geq 0\}$ is not a spectrahedron
+The basic closed semialgebraic set $P = \{(X_1,X_2) \in \R^2 : 1-X_1^4-X_2^4 \geq 0\}$ is not a spectrahedron
 but it is semidefinite representable:
 $$
-P = \left\{x = \begin{bmatrix} x_1 \\ x_2 \end{bmatrix} \in \R^2 :
-\exists\, (y_1,y_2) \in \R^2, \,
+P = \left\{X = \begin{bmatrix} X_1 \\ X_2 \end{bmatrix} \in \R^2 :
+\exists\, (Y_1,Y_2) \in \R^2, \,
 \begin{bmatrix}
-  1+y_1 & y_2 \\
-  y_2 & 1-y_1
+  1+Y_1 & Y_2 \\
+  Y_2 & 1-Y_1
 \end{bmatrix}
@@
 \begin{bmatrix}
-  1 & x_1 \\
-  x_1 & y_1
+  1 & X_1 \\
+  X_1 & Y_1
 \end{bmatrix}
@@
 \begin{bmatrix}
-  1 & x_2 \\
-  x_2 & y_2
+  1 & X_2 \\
+  X_2 & Y_2
 \end{bmatrix}
@@
 \begin{definition}
-  Let $\ell_1,\ldots,\ell_d \in K[X]_1$ be linear inequalities on $X = (X_1, \ldots, X_n)$.
-  A {\it polyhedron} is a subset $P \subset K^s$ defined by linear inequalities:
-  $P = \val\left( \ell_1(x)\right)\ge 0$,\ldots, $ \val\left( \ell_n\left( x \right) \right)\ge 0$ for $ \ell_1,\ldots, \ell_n $ fixed linear forms and for all $x \in K ^s$.
+  A {\it polyhedron} is a subset $P \subset K^n$ of the form
+  $P = \{X \in K^n : \val(\ell_1(X))\geq0,\ldots,\val(\ell_n(X))\geq 0\}$,
+  where $\ell_1,\ldots,\ell_d \in K[X]_1$ are affine polynomials on $X = (X_1, \ldots, X_n)$.
 \end{definition}
@@
 \begin{example}
-	The closed unit ball of $K^s$ for the infinity norm [not sure if it is really used ] is convex polyhedron.It is the set of $\left( x_1,\ldots,x_s \right) \in  ^s$ so that $$
+  The closed unit ball in $K^n$ for the supremum norm $||\cdot||_{\infty}$ is the polyhedron defined as
+  the set of $(X_1,\ldots,X_n) \in K^n$ such that
+  $$
   \begin{pmatrix} x_1 &  & & \\
@@
   \end{pmatrix} \ge 0.$$ which is in fact $\OK^s$.
-
 \end{example}
@@
 %\subsection{linear programming}
-	We call { \it $p$-adic linear programming} the problem :
+
+A {\it linear programming problem} (or simply {\it linear program}) is
 \begin{equation}
-	\tag{PLp}
+  \tag{LP}
   \begin{matrix}
@@
 \subsection{Definition}
-\newcommand\mat{postive semidefinite matrix } 
+%\newcommand\mat{postive semidefinite matrix } 
 \newcommand\Mat{Positive semidefinite matrix }
@@
 \begin{definition}
-	We call {\it \mat} any matrix $M \in \mathcal{M}_n\left( K \right) $ whose eigenvalues have nonegative valuation (in $\overline{K}$) .
+	We call ... any matrix $M \in \mathcal{M}_n\left( K \right) $ whose eigenvalues have nonegative valuation (in $\overline{K}$) .
 

### 2023-10-26 article/paper_padic_spec.tex
debut sec poly LP

@@
   $P = \{X \in K^n : \val(\ell_1(X))\geq0,\ldots,\val(\ell_n(X))\geq 0\}$,
-  where $\ell_1,\ldots,\ell_d \in K[X]_1$ are affine polynomials on $X = (X_1, \ldots, X_n)$.
+  for some $\ell_1,\ldots,\ell_d \in K[X]_1$. This will often be denoted with
+  the compact notation $\val(\ell_1 \oplus \cdots \oplus \ell_d) \geq 0$, where $\val$
+  and $\geq$ are applied entrywise.
 \end{definition}
@@
 \begin{example}
-  The closed unit ball in $K^n$ for the supremum norm $||\cdot||_{\infty}$ is the polyhedron defined as
-  the set of $(X_1,\ldots,X_n) \in K^n$ such that
-  $$
-  \begin{pmatrix} x_1 &  & & \\
-    & x_2 &0 &  \\
-    &  0& \ddots & \\
-    &  & & x_s/
-  \end{pmatrix} \ge 0.$$ which is in fact $\OK^s$.
+  The closed unit ball $B_\infty(K^n)$ in $K^n$ for the supremum norm $||\cdot||_{\infty}$ is the
+  polyhedron defined as the set of $X=(X_1,\ldots,X_n) \in K^n$ such that $||X||_{\infty} =
+  \max_i\{X_i\}\leq 1$, other words, such that $\val(X_i) \geq 0$, for all $i=1, \ldots, n$.
+  In other words, $\OK^n = B_\infty(K^n)$ is the polyhedron in $K^n$ defined by the affine polynomials
+  $\ell_i(X)=X_i$, $i=1,\ldots, n$.
+%  $$
+%  \begin{pmatrix} x_1 &  & & \\
+%    & x_2 &0 &  \\
+%    &  0& \ddots & \\
+%    &  & & x_s/
+  %  \end{pmatrix} \ge 0.$$
 \end{example}
@@
 
-A {\it linear programming problem} (or simply {\it linear program}) is
+A {\it linear programming problem} (or simply {\it linear program}) is given by the following
+optimization problem:
 \begin{equation}
   \tag{LP}
-  \begin{matrix}
-    \text{Minimize } \val\left(\left<c,x \right>\right) \text{ subject to }\\
-    Ax + b \ge 0
-  \end{matrix}
-  \label{eqn:Proglinp}
+\begin{array}{rcll}
+  p^* & := & \inf_{X \in \R^n} & \val(\left\langle c, X \right\rangle) \\
+  &    & \text{s.t.}         & A X + b \geq 0
+\end{array}
 \end{equation}
-
-with $x$ a vector of $K ^n$, and $c$ a fixed vector of size $n$ that represents the cost, $A$ a fixed $m \times n $ matrix and $b$ fixed a vector of size $m$.
+with $c \in K^n$ a fixed vector of size $n$ that represents the cost, $A \in \allmat_{m,n}(K)$ and $b \in K^m$.
 

### 2023-10-30 article/paper_padic_spec.tex
variables

--- 2023-10-26 article/paper_padic_spec.tex
@@
 Another example is the field of Laurent series
-$K=\QQ(\!(T)\!)$ equiped with $T$-adic valuation.
-In this case,  $\OK = \QQ \llbracket T \rrbracket$.
+$K=\QQ(\!(t)\!)$ equiped with $t$-adic valuation.
+In this case, $\OK = \QQ \llbracket t \rrbracket$.
 We refer to \cite{Serre:1979} for a
@@
 
+The $K$-vector space of polynomials of degree $\leq d$ on $x=(x_1,\ldots,x_n)$
+with coefficients in $K$ is denoted by $K[x]_{d}$. The vector space of matrices of
+size $p \times q$ with entries in $K$ is denoted by $\allmat_{p,q}(K)$. For the sake
+of ease of writing, block-diagonal matrices with blocks $B_1,\ldots,B_d$ are denoted by
+$B_1 \oplus \cdots \oplus B_d$.
+
 \subsection{Real spectrahedra}
 
-Let $\sym_d(\R)$ be the vector space of $d \times d$ real symmetric matrices. A matrix $M \in \sym_d(\R)$
+Let $\sym_d(\R) \subset \allmat_{d,d}(\R)$ be the vector space of $d \times d$ real symmetric
+matrices. A matrix $M \in \sym_d(\R)$
 is called {\it positive semidefinite} ($M \succeq 0$) whenever the quadratic
@@
 containing $A_0$ and with direction the vector space spanned by $A_1,\ldots,A_n$ (which we assume linearly
-independent). The intersection
-$\calL \cap \sym_d^+(\R) = \left\{A(x) := A_0+\sum_i x_i A_i \in \sym_d(\R) : A(x) \succeq 0\right\}$, or
+independent). The intersection $\calL \cap \sym_d^+(\R) = \left\{A(x) := A_0+\sum_i x_i A_i \in \sym_d(\R) :
+A(x) \succeq 0\right\}$, or
 equivalently, its pre-image $S = \{x \in \R^n : A(x) \succeq 0\}$ under the map $x \mapsto A(x)$, is called
@@
   The polynomials on the right are the (non-constant) coefficients of the univariate polynomial
-  $p(t) = \det(A(x)+t I)$,
+  $p(t) = \det(A(x)+t I_3)$,
   whose roots are the opposites of the eigenvalues of the defining matrix. Equivalently $\mathcal{E}_3$
@@
 Real polyhedra (subsets of $\R^n$ defined by finitely many affine inequalities) are special cases of real
-spectrahedra, where the defining matrices $A_0, \ldots, A_n$ can be chosen diagonal. Thus SDP is a generalization
-of linear programming (LP). In a fixed-precision model of computation, SDP is solvable in polynomial time in the
-input size (matrix size,
+spectrahedra, where the defining matrices $A_0, \ldots, A_n$ can be chosen diagonal, so that $A(x) =
+\ell_1(x) \oplus \cdots \oplus \ell_d(x)$. In other words, SDP is a generalization of Linear Programming (LP).
+
+In a fixed-precision model of computation, SDP is solvable in polynomial time in the input size (matrix size,
 number of variables, bit size of the coefficients), in $\log(\frac{1}{\varepsilon})$ (where $\varepsilon$ is the
@@
 $$
-P = \left\{x = \left[\begin{smallmatrix} x_1 \\ \vdots \\ x_n \end{smallmatrix}\right] \in \R^n : \exists\,y\in\R^m, \, A_0 + \sum_{i=1}^n x_i A_i + \sum_{j=1}^m y_j B_j \succeq 0\right\}
+P = \left\{x = \left[\begin{smallmatrix} x_1 \\ \vdots \\ x_n \end{smallmatrix}\right] \in \R^n : \exists\,y\in\R^p, \, A_0 + \sum_{i=1}^n x_i A_i + \sum_{j=1}^p y_j B_j \succeq 0\right\}
 $$
@@
 $$
-P = \left\{x = \begin{bmatrix} x_1 \\ x_2 \end{bmatrix} \in \R^2 :
-\exists\, (y_1,y_2) \in \R^2, \,
+P = \left\{\begin{bmatrix} x_1 \\ x_2 \end{bmatrix} \in \R^2 :
+\exists\,
+\begin{bmatrix} y_1 \\ y_2 \end{bmatrix} \in \R^2, \,
 \begin{bmatrix}
@@
 
-In this section, we define polyhedra over a complete discrete valuation field $K$ with valuation $\val$,
+In this section, we define polyhedra over a (complete) discrete valuation field $K$ with valuation $\val$,
 and we discuss the associated linear optimization problem.
@@
 \begin{definition}
-  Let $\ell_1,\ldots,\ell_d \in K[X]_1$ be linear inequalities on $X = (X_1, \ldots, X_n)$.
-  A {\it polyhedron} is a subset $P \subset K^s$ defined by linear inequalities:
-  $P = \val\left( \ell_1(x)\right)\ge 0$,\ldots, $ \val\left( \ell_n\left( x \right) \right)\ge 0$ for $ \ell_1,\ldots, \ell_n $ fixed linear forms and for all $x \in K ^s$.
+  A {\it polyhedron} is a subset $P \subset K^n$ of the form
+  $P = \{x \in K^n : \val(\ell_1(x))\geq0,\ldots,\val(\ell_n(x))\geq 0\}$,
+  for some $\ell_1,\ldots,\ell_d \in K[x]_1$. This will often be denoted with
+  the compact notation $\val(\ell_1 \oplus \cdots \oplus \ell_d) \geq 0$, where $\val$
+  and $\geq$ are applied entrywise.
 \end{definition}
@@
 \begin{example}
-	The closed unit ball of $K^s$ for the infinity norm [not sure if it is really used ] is convex polyhedron.It is the set of $\left( x_1,\ldots,x_s \right) \in  ^s$ so that $$
-	\begin{pmatrix} x_1 &  & & \\
-		& x_2 &0 &  \\
-		&  0& \ddots & \\
-		&  & & x_s/
-	\end{pmatrix} \ge 0.$$ which is in fact $\OK^s$.
-
+  The closed unit ball $B_\infty(K^n)$ in $K^n$ for the supremum norm $||\cdot||_{\infty}$ is the
+  polyhedron defined as the set of $x=(x_1,\ldots,x_n) \in K^n$ such that $||x||_{\infty} =
+  \max_i\{x_i\} \leq 1$, in other words, such that $\val(x_i) \geq 0$, for all $i=1, \ldots, n$.
+  In other words, $\OK^n = B_\infty(K^n)$ is the polyhedron in $K^n$ defined by the affine polynomials
+  $\ell_i(x)=x_i$, $i=1,\ldots, n$.
+%  $$
+%  \begin{pmatrix} x_1 &  & & \\
+%    & x_2 &0 &  \\
+%    &  0& \ddots & \\
+%    &  & & x_s/
+  %  \end{pmatrix} \ge 0.$$
 \end{example}
@@
 %\subsection{linear programming}
-	We call { \it $p$-adic linear programming} the problem :
+
+A {\it linear programming problem} (or simply {\it linear program}) is given by the following
+optimization problem:
 \begin{equation}
-	\tag{PLp}
-	\begin{matrix}
-		\text{Minimize } \val\left(\left<c,x \right>\right) \text{ subject to }\\
-		Ax + b \ge 0
-	\end{matrix}
-	\label{eqn:Proglinp}
+  \tag{LP}\label{LP}
+\begin{array}{rcll}
+  p^* & := & \inf_{x \in \R^n} & \val(\left\langle c, x \right\rangle) \\
+  &    & \text{s.t.}         & A x + b \geq 0
+\end{array}
 \end{equation}
+with $c \in K^n$ a fixed vector of size $n$ that represents the cost, $A \in \allmat_{m,n}(K)$, $b \in K^m$,
+and $\left\langle c, x \right\rangle := c_1x_1+\cdots +c_nx_n$.
+We present an algorithm for solving \eqref{LP} which consists in reducing the matrix $A$ in Smith normal form.
+We recall its definition below, in our context.
 
-with $x$ a vector of $K ^n$, and $c$ a fixed vector of size $n$ that represents the cost, $A$ a fixed $m \times n $ matrix and $b$ fixed a vector of size $m$.
-
-The method used in this article consists in reducing the Smith normal form of the matrix $A$.
-
-\begin{definition} Smith normal form
-
-	We call {\it Smith normal form} of a matrix $M \in \mathcal{M}_{m,n}\left(K \right) $ of rank $r$ the only matrix $S$ of the form $$S =  
-	\begin{pmatrix} p^{a_1} & \\
-		& \ddots \\
-		& & p^{a_r}\\
-		& & & 0\\
-		& & & & \ddots \end{pmatrix} $$
-	so that $(a_1)_{1\le i\le r}$ is a increasing sequence of integers and $M$ can be written $M =  Q^{-1} S P$ for $P \in \mathcal{G}L_n\left( \ZZ_p \right) $, $Q \in \mathcal{G}L_m\left( \ZZ_p \right) $.
+\begin{definition}[Smith normal form] \label{smith_nf}
+  Let $M \in \allmat_{m,n}(K)$ be of rank $r$. There exist unique integers $a_1 \leq \cdots \leq a_r$, and
+  unique matrices $P \in GL_n(\OK)$ and $Q \in GL_m(\OK)$, such that
+  $$
+  S := QMP^{-1} = p^{a_1} \oplus p^{a_2} \oplus \cdots \oplus p^{a_r} \oplus {\bf 0}_{m-r}
+  $$
+  where ${\bf 0}_{m-r}$ is a null square matrix of size $m-r$.
+  The matrix $S$ is called the {\it Smith normal form} of $M$.
 \end{definition}

### 2023-10-30 article/paper_padic_spec.tex
commit by Simone

@@
 \newcommand{\OK}{\mathcal{O}_K}
+
+\newcommand{\GL}{\mathrm{GL}}
 
@@
 
-\begin{definition}[Smith normal form] \label{smith_nf}
+\begin{definition}[Smith Normal Form] \label{smith_nf}
   Let $M \in \allmat_{m,n}(K)$ be of rank $r$. There exist unique integers $a_1 \leq \cdots \leq a_r$, and
-  unique matrices $P \in GL_n(\OK)$ and $Q \in GL_m(\OK)$, such that
+  unique matrices $P \in \GL_n(\OK)$ and $Q \in \GL_m(\OK)$, such that
   $$
@@
   where ${\bf 0}_{m-r}$ is a null square matrix of size $m-r$.
-  The matrix $S$ is called the {\it Smith normal form} of $M$.
+  The matrix $S$ is called the {\it Smith Normal Form (SNF)} of $M$.
 \end{definition}
@@
   \end{enumerate}
-
 \end{remark}

### 2023-10-30 article/paper_padic_spec.tex
last modifs

@@
   where ${\bf 0}_{m-r}$ is a null square matrix of size $m-r$.
-  The matrix $S$ is called the {\it Smith Normal Form (SNF)} of $M$.
+  The matrix $S$ is called the \emph{Smith Normal Form (SNF)} of $M$, and the elements $p^{a_i}$ the
+  \emph{invariant factors}.
 \end{definition}
@@
 \begin{remark}
-  \begin{enumerate}%[label=\roman*.]
-  \item The coefficient of the Smith normal form are unique and called \textit{invariant factors}.
-  \item The valuation of the first coefficient of the Smith normal form of a matrix $M \in \mathcal{M}_n \left( \QQ_p \right) $ is the minimum of the valuations of the matrix $M$'s terms.
-  \item In particular, the the normal Smith form of matrix of $\mathcal{M}_n \left( \OK \right) $ have coefficients in $\ZZ_p$ .
-  \item The $r = \text{rank} M$ first diagonals coefficients of $S$ are exactly its non-zero coefficient.
-  \end{enumerate}
+  The valuation of the first coefficient\footnote{invariant factor?} of the SNF of a matrix
+  $M \in \allmat_{n,n} \left( \QQ_p \right) $ is the minimum of the valuations of the matrix
+  $M$'s terms (\simone{proof or reference}). In particular, the the SNF of matrix of $\mathcal{M}_n \left( \OK \right) $ have coefficients in $\ZZ_p$ .
+ The $r = \text{rank} M$ first diagonals coefficients of $S$ are exactly its non-zero coefficient.
 \end{remark}
@@
 
+\section{Other questions}
+\begin{itemize}
+\item The projection of a real polyhedron is a real polyhedron (thanks to Fourier-Motzkin elimination procedure). Is it the same for $K$-polyhedra?
+\item Annuli are semidefinite representable, we should remark/prove that they are not spectrahedra.
+\end{itemize}
+
 \printbibliography

### 2023-11-14 article/paper_padic_spec.tex
modification polyhedra

@@
 \newtheorem{proposition}{Proposition}
-\newtheorem{corollary}{corollary}
+\newtheorem{corollary}{Corollary}
 \newtheorem{algorithm}{Algorithm}
@@
 \newtheorem{example}{Example}
+\newtheorem{notation}{Notation}
 \usepackage{booktabs}
@@
 $\OK$ its ring of integers and $\pi$ a uniformizer.
-For $k \in \N$, we write $O(\pi^k)$ for $\pi^k \OK.$
+For $k \in \N$, we write $O(\pi^k)$ for $\pi^k \OK$.
 A typical example of $K$ as above is the field of $p$-adic numbers 
@@
 
-In this section, we define polyhedra over a (complete) discrete valuation field $K$ with valuation $\val$,
+In this section, we define polyhedra over a complete discrete valuation field $K$ with valuation $\val$ and a uniformizer $\pi$,
 and we discuss the associated linear optimization problem.
@@
 \begin{array}{rcll}
-  p^* & := & \inf_{x \in \R^n} & \val(\left\langle c, x \right\rangle) \\
+  p^* & := & \inf_{x \in K^n} & \val(\left\langle c, x \right\rangle) \\
   &    & \text{s.t.}         & A x + b \geq 0
@@
 
-\begin{definition}[Smith Normal Form] \label{smith_nf}
+\begin{definition}[Smith Normal Form]\label{smith_nf}
   Let $M \in \allmat_{m,n}(K)$ be of rank $r$. There exist unique integers $a_1 \leq \cdots \leq a_r$, and
-  unique matrices $P \in \GL_n(\OK)$ and $Q \in \GL_m(\OK)$, such that
+  matrices $P \in \GL_n(\OK)$ and $Q \in \GL_m(\OK)$, such that
   $$
-  S := QMP^{-1} = p^{a_1} \oplus p^{a_2} \oplus \cdots \oplus p^{a_r} \oplus {\bf 0}_{m-r}
+  S := QMP^{-1} = \pi^{a_1} \oplus \pi^{a_2} \oplus \cdots \oplus \pi^{a_r} \oplus {\bf 0}_{\min(m,n)-r}
   $$
-  where ${\bf 0}_{m-r}$ is a null square matrix of size $m-r$.
-  The matrix $S$ is called the \emph{Smith Normal Form (SNF)} of $M$, and the elements $p^{a_i}$ the
+  where ${\bf 0}_{\min(m,n)-r}$ is a null square matrix of size $\min(m,n)-r$.
+  The matrix $S$ is called the \emph{Smith Normal Form (SNF)} of $M$, and the elements $\pi^{a_i}$ the
   \emph{invariant factors}.
 \end{definition}
-
 \begin{remark}
   The valuation of the first coefficient\footnote{invariant factor?} of the SNF of a matrix
-  $M \in \allmat_{n,n} \left( \QQ_p \right) $ is the minimum of the valuations of the matrix
-  $M$'s terms (\simone{proof or reference}). In particular, the the SNF of matrix of $\mathcal{M}_n \left( \OK \right) $ have coefficients in $\ZZ_p$ .
- The $r = \text{rank} M$ first diagonals coefficients of $S$ are exactly its non-zero coefficient.
+  $M \in \allmat_{n,n} \left( K \right) $ is the minimum of the valuations of the matrix
+  $M$'s terms (\simone{proof or reference}). In particular, the the SNF of matrix of $\allmat_n \left( \OK \right) $ have coefficients in $\OK$.
 \end{remark}
 
-In order to be able to use the Smith normal form to resolve \ref{eqn:Proglinp} we need the following lemma :
+The most interesting aspect in the SNF regarding the resolution of \ref{LP} is that the transition matrices are invertible in $\OK$.
+Indeed, if $z \in K^n$ and $M \in \allmat_n(\OK)$ such that $z \geq 0$ then $Mz \geq 0$.
+The latter property is a direct consequence of $\OK$ being a ring and the converse is true if the matrix $M$ is invertible in $\OK$ \corentin{est-ce qu'il y a besoin de le prouver ?}.
+Therefore, for all matrix $M \in \allmat_n(K)$ with SNF $S$ and all $z \in K^n$ $Mz \geq 0$ if and only if $Sz \geq 0$.
 
-\begin{lemma}
-  Forall $p$-adic numbers $z \in \QQ_p ^n$ and matrix $M \in \mathcal{M}_{m,n}\left( \QQ_p  \right)  $ if $z\ge 0$ and $M\ge 0$ then $Mz\ge 0$.  
-\end{lemma}
-\begin{proof}
-  $\ZZ_p$ is a ring.
-\end{proof}
+That property applied to the matrix $A$ in \ref{LP} allow to reduce the problem to an equivalent simpler iteration of the \ref{LP} problem that will be called {\it diagonal linear programming problem} \corentin{or maybe reduced linear programming problem?}.
+This problem is the optimization problem:
+\begin{equation}
+  \tag{dLP}\label{dLP}
+\begin{array}{rcll}
+  p^* & := & \inf_{y \in K^n} & \val(\left\langle c', y \right\rangle) \\
+  &    & \text{s.t.}         & S y + b' \geq 0
+\end{array}
+\end{equation}
+with $c' \in K^n$ a fixed vector of size $n$, $b' \in K^m$ and $S$ a diagonal $m \times n$ matrix of the form $S = s_1 \oplus s_2 \oplus \ldots \oplus s_r \oplus { \bm 0}_{m-r} $ for $r={\rm rank} S$.
 
-If we put the matrix $A$ of \ref{eqn:Proglinp} in its normal Smith form, it comes that resolving \ref{eqn:Proglinp} is equivalent to resolve :
+The {\it associated diagonal linear programming problem} of a linear program is the iteration of the \ref{dLP} problem defined by $b' = Qb$, $c' = \left(P^{-1}\right)^T c$ and where $S$ is the Smith normal form of $A$ and $P \in GL_m\left( \OK \right)$ and $ Q \in GL_n\left( \OK \right)$ are such that $A = Q^{-1} S P$.
 
-\begin{equation}
-	\tag{PLp'}
-	\begin{matrix}
-		\text{Minimize } \val\left(\left<c',x \right>\right) \text{ subject to }\\
-		Sy + b' \ge 0
-	\end{matrix}
-	\label{eqn:Proglinp2}
-\end{equation}
-where $b' = Qb$, $c' = P^Tc$, $S$ is the Smith normal form of $A$ and $A = Q^{-1} S P$ for some $P \in \mathcal{G}L_m\left( \ZZ_p \right)$ and $ Q \in \mathcal{G}L_n\left( \ZZ_p \right)$.
+A vector $x^* \in K^n$ is {\it feasible solution} of \ref{LP} if $Ax^* + b \geq 0$.
+Similarly, a vector $y^* \in K^n$ is a feasible of \ref{dLP} if $Sy^*+b' \geq 0$.
+We will denote as $Adm$ \corentin{Probablement à changer mais je ne sais pas quel nom lui donner} the set of feasible solution of \ref{dLP}.
 
-\begin{remark}
+\begin{proposition}\label{prop:reduc}
 
@@
 	\begin{enumerate}
-		\item $x^*$ is a feasible solution of \ref{eqn:Proglinp} if and only if $y^* = P x^*$ is a feasible solution of \ref{eqn:Proglinp2}
-		\item \ref{eqn:Proglinp2} have feasible solutions if and only if the $m-r$ coefficients of $b'$ are non-zero, with $r$ the rank of $S$.
-		\item If at least one of the $n-r$ last coefficients of $c'$ is non-zero \ref{eqn:Proglinp2} is unbounded and does not have a soution.
+		\item $x^*$ is a feasible solution of \ref{LP} if and only if $y^* = P x^*$ is a feasible solution of the associated \ref{dLP} problem.
+		\item $x$ is a solution of \ref{LP} if and only if $y = P x$ is a solution of the associated \ref{dLP} and the the infimum is the same.
+		\item \ref{dLP} have feasible solutions if and only if the $m-r$ last coefficients of $b'$ have nonegative valuation, with $r$ the rank of $S$.
+		\item If at least one of the $n-r$ last coefficients of $c'$ is non-zero, if \ref{dLP} admits feasible solutions it is unbounded and does not have a solution.
+
   \end{enumerate}
+\end{proposition}
 
-\end{remark}
+\begin{proof}
 
-\begin{proposition}
-	\begin{itemize}~
+  First of all, 1. is a consequence of the fact that $Mx^*+b = MP^{-1}y^* +b\geq 0$ if and only if $Q(MP^{-1}y^* + b) = Sy^* + b' \geq 0$ because $Q \in GL_m(\OK)$.
 
-		\item[$\circ$] If not all the $m-r$ coefficients of $b'$ are zeros then there is no $y \in K ^n$ so that $A'y+b' \ge  0$.
-		\item[$\circ$] If not all the $n-r$ coefficients of $c'$ are zero then the problem is unbounded and does not have solution. \end{itemize} 
-\end{proposition}
-If one considers only the itération of the problem which have des solution one can reduce the problem by only taking acount the $r$ first coefficients of $y, b', c'$ and the submatrix of $S$ made with only $r$ first lines et columns of and which coefficients are exactly the nonzero invariants factors.
+  Then, 2. comes from the fact that for all $c \in K^n$ $\langle c, x\rangle = \langle c, P^{-1}Py \rangle = \langle \left(P^{-1}\right)^T c, y \rangle$.
+
+  A vector $y =  \left[\begin{smallmatrix} y_1 \\ \vdots \\ y_n \end{smallmatrix}\right] \in K^n$ is feasible solution of \ref{dLP} if and only if $\val(s_i y_i + b_i) >=0$ for all $i \in \{1...n\}$ \corentin{préciser les notations}.
+  However, $s_i =0$ for $n-r \leq i\leq n$. Therefore, \ref{dLP} have solution only if the $m-r$ last coefficient of b' are zero.
+
+  Conversely, if the $m-r$ last coefficient of $b'$ are zero, the vector $y \in K^n$ such that $y_i = -\frac{-b'_i}{s_i}$ if $1 \leq i \leq r$ and $y_i =0$ otherwise is a feasible solution.
+
+  Finally, let $y^*$ be a feasible solution of \ref{dLP}.
+Let us suppose there exists $r+1 \leq i \leq m$ such that $c'_i \neq  0$ and fix such $i$.
+Let us then consider the vector $e^i$ whose only non-zero coefficient is the $i-$th, which is $1$.
+Then $y^*+\lambda e^i$ is a feasible solution for all $\lambda \in K$ and $\langle c', y^* + \lambda e^i\rangle = \langle c' , y^* \rangle + \lambda c'_i$.
+In particular, for $\lambda = -\frac{\langle c', y^* \rangle}{c'_i}$ $\val \left( \langle c', y^* + \lambda e ^i \rangle\right) = \val (0) = + \infty$.
+
+The two first points of the proposition \ref{prop:reduc} show that we can resolving a linear program is equivalent to resolution the associated \ref{dLP} problem.
+Furthermore, if one considers only the iteration of \ref{dLP} which have solutions.
+By point 3.
+and 4.
+of proposition \ref{prop:reduc} one can reduce the problem by only taking acount only the $r$ first coefficients of $y, b', c'$ and the submatrix of $S$ made with only $r$ first lines et columns of and which coefficients are exactly the nonzero invariants factors.
 The set $Adm$ of the feasible solutions can then be written as the set of vectors $y \in \mathbb{Q}_{ p } ^n$ that verifies $\forall 1 \le i\le r \ s_i y_i + b'_i \in \OK$ i.e.
@@
 \begin{equation}
-	\forall 1 \le i\le r  \ y_i \in -\frac{b’_i}{s_i} + \frac{1}{s_i} \OK
+	\forall 1 \le i\le r  \ y_i \in -\frac{b`_i}{s_i} + \frac{1}{s_i} \OK
 \end{equation}
 
-Resolving \ref{eqn:Proglinp2} consists in minimizing $\val\left(\left<c',y \right>\right)$ over $Adm$.
-The image of $Adm$ by $y \mapsto \left<c',y \right>$ is $\sum_{i=1}^r -c'_i.\frac{b'_i}{s_i} + \sum_{i=1}^r\left( \frac{c'_i}{s_{i}} \OK \right)$ which can be rewritten in
-$$\left<c',Adm \right> = \lambda + p^{v} \OK$$
-with $\lambda = \sum\limits_{i=1}^r -c'_i.\frac{b'_i}{s_i}$ et $v = \min\limits_{1\le i\le r} \val \frac{c'_{i}}{s_{i}} $.
+Resolving \ref{dLP} consists in minimizing $\val\left(\left<c',y \right>\right)$ over $Adm$.
+The image of $Adm$ by $y \mapsto \left<c',y \right>$ is $\sum_{i=1}^r -c'_i.\frac{b'_i}{s_i} + \sum_{i=1}^r\left( \frac{c'_i}{s_{i}} \OK \right)$ which can be rewritten in $\left<c',Adm \right> = \lambda + \pi^{v} \OK$ with $\lambda = \sum_{i=1}^r -c'_i.\frac{b'_i}{s_i}$ and $v = \min\limits_{1\le i\le r} \val \frac{c'_{i}}{s_{i}} $.
 
-The result can be split depending on the valuation of $\lambda$.
+Finally, two cases can occur depending on $v$ and the valuation of $\lambda$.
 \begin{itemize}
 	\item If $\val( \lambda) < v$ the minimum of $y\mapsto \val\left(\left<c',y \right>\right)$ over $Adm$ is reached in any point of $Adm$ and is equal to $\val\left( \lambda\right)$.
-	\item If $\val\left( \lambda \right) \ge v$ then $\lambda \in p^{v} \OK$ and the minimum is $v $ and is reached in any points $y$ of $Adm$ that verifies 
-	$$\val\sum \limits_{\begin{array}{c} 1\le i\le r\\ \val\left(c'_{i}/{s_{i}} \right) = v  \end{array}   } y_{i} = 0.$$
+	\item If $\val\left( \lambda \right) \ge v$ then $\lambda \in \pi^{v} \OK$ and the minimum is $v $ and is reached in any points $y$ of $Adm$ that verifies 
+	\[\val \underset{ \begin{array}{c} 1\le i\le r\\ \val\left(c'_{i}/{s_{i}} \right) = v  \end{array}}{\sum} y_{i} = 0. \]
 
@@
 	To maximize the valuation of a linear map over a convex $p$-adic polyhedron instead of minimizing it (which is equuivalent to minimize the absolute value) the same reasoning can be aplied.
-The only differnece being that if $\val\left( \lambda\right) < v$ the problem is unbounded and then does not have any solution.
+The only difference being that if $\val\left( \lambda\right) < v$ the problem is unbounded and as such does not have any solution.
 \end{remark}
@@
 
-	A matrix is positive semidefinite if and only if its characteristic polynomial have coefficients in $\OK$ .
+	A matrix is positive semidefinite if and only if its characteristic polynomial have coefficients in $\OK$.
 

### 2023-11-22 article/paper_padic_spec.tex
commit by Simone
Brouillon de preuve de la stabilité des polyèdres par application linéaire.

@@
 
-\newtheorem{theorem}{Theorem}
-\newtheorem{lemma}{Lemma}
-\newtheorem{proposition}{Proposition}
-\newtheorem{corollary}{Corollary}
-\newtheorem{algorithm}{Algorithm}
-\newtheorem{conjecture}{Conjecture}
-\newtheorem{condition}{Condition}
-\newtheorem{definition}{Definition}
-\newtheorem{assumption}{Assumption}
-\newtheorem{remark}{Remark}
-\newtheorem{problem}{Problem}
-\newtheorem{example}{Example}
-\newtheorem{notation}{Notation}
+\newtheorem{theorem}{Theorem}[section]
+\newtheorem{lemma}[theorem]{Lemma}
+\newtheorem{proposition}[theorem]{Proposition}
+\newtheorem{corollary}[theorem]{Corollary}
+\newtheorem{algorithm}[theorem]{Algorithm}
+\newtheorem{conjecture}[theorem]{Conjecture}
+\newtheorem{condition}[theorem]{Condition}
+\newtheorem{definition}[theorem]{Definition}
+\newtheorem{assumption}[theorem]{Assumption}
+\newtheorem{remark}[theorem]{Remark}
+\newtheorem{problem}[theorem]{Problem}
+\newtheorem{example}[theorem]{Example}
+\newtheorem{notation}[theorem]{Notation}
 \usepackage{booktabs}
@@
 \newcommand{\sym}{\mathbb{S}} % matrices symétriques
+\newcommand{\PP}{\mathcal{P}}
+\newcommand{\Qc}{\mathcal{Q}}
 \renewcommand{\span}[1]{{\text{span}(#1)}} % simone's comments
@@
 \newcommand{\corentin}[1]{{\color{red} #1}} % corentin's comments
-\newcommand{\tristan}[1]{{\color{olive} #1}} % tristan's comments
+\newcommand{\tristan}[1]{{\color{red} #1}} % tristan's comments
 
@@
 
+\end{proof}
+
 The two first points of the proposition \ref{prop:reduc} show that we can resolving a linear program is equivalent to resolution the associated \ref{dLP} problem.
@@
 
+\begin{proposition}
+Let $\PP \subset K^n$ be a polyhedron and $f: K^n \rightarrow K^m$
+be a linear mapping. Then $f(\PP)$ is a polyhedron.
+\end{proposition}
+\begin{proof}
+Let us assume that 
+$\PP$ is defined by the set of conditions $\left\lbrace \val (l_i (x) ) \geq 0, \textrm{ for } i \in I \right\rbrace$ for some
+finite set $I \subset \N$ and all $l_i \in K[X]_1$ for $i \in I.$
+We further assume that $\PP$ is non-empty.
+
+Thanks to the Smith Normal Form (see Definition \ref{smith_nf}), $f$
+can be written $f=Q^{-1} \Delta P$
+with $P \in \GL_n(\OK),$ $Q \in \GL_m(\OK)$
+and $\Delta \in \allmat_{n,m}(K)$ of the form $\lambda_1 \oplus \cdots \oplus \lambda_r \oplus {\bf 0}_{\min(m,n)-r}$
+  where ${\bf 0}_{\min(m,n)-r}$ is a null square matrix of size $\min(m,n)-r$ for $\lambda_1,\dots,\lambda_r$ non-zero and $r \in \N.$
+
+We first prove the result when $f$ is in $\GL_n(\OK)$.
+In that case, $x \in f(P)$ if and only if for all
+$i \in I,$
+$\val (l_i (f^{-1}(x)) \geq 0$.
+The $l_i \circ f^{-1}$ are clearly in $K[x]_1$
+and $f(P)$ is a polyhedra.
+
+Similarly, if $f$ is of the form $K^n \rightarrow K^n$,
+$(x_1,\dots,x_n) \mapsto (\lambda_1 x_1,\dots,\lambda_n x_n)$
+for some $\lambda_i$'s in $K$,
+then it is clear that $f(P)$
+can be defined by $\val (\widetilde{l_i}(x)) \geq 0$, $i \in I$
+with the $\widetilde{l_i}$'s obtained from the $l_i$'s by an
+obvious change of variables.
+
+Now, we turn our attention to the $\Delta$ part of $f.$
+We first assume that $f$ is a projection 
+of the form $K^n \rightarrow K^{n+1},$
+$(x_1,\dots,x_{n-1},x_n)\mapsto (x_1,\dots,x_{n-1}).$
+
+Let us write the conditions defining $\PP$
+in matrix form:
+$\val(A X+B) \geq 0$
+with $A \in M_{q,n}(K)$, $B \in K^q$
+and $X=(x_1,\dots,x_n)^\intercal.$
+
+We can computer a Smith Normal Form
+of the $q \times (n-1)$ matrix defined by the 
+$n-1$ first columns of $A$
+to obtain a decomposition of the form:
+\[ Q_A A P_A^{-1} = \begin{bmatrix}
+\delta_1	& 		& 			&   &		 &  &a_1	\\
+			& \ddots& 			& 0	&		 &	&		\\
+			&		& \delta_l  &   & 		 &	&		\\
+			&		&			&0  & 		 &	& 		\\
+			&		&			&   & \ddots &	&		\\
+			&		&			&	&		 & 0&a_{n-1} \\
+			&		&			&	&		 &	&a_n 	\\
+			&		&			&	&		 &	&    	\\
+			&		&			&	&		 &	&a_q 	\\			
+\end{bmatrix},\]
+with $Q_A \in \GL_q(\OK)$ and $P_A \in \GL_n(\OK)$ such that $P_A(e_n)=e_n.$
+
+Multiplying on the left by $Q_A^{\pm 1}$ does not
+modify whether the valuation inequalities are satisfied.
+Moreover, thanks to our previous on the case when $f$ is an automorphism,
+$\PP$ can be written
+$\PP=P_A^{-1}(\PP_2)$ for some polyhedron $\PP_2 \in K^n$
+and we are reduced to proving that
+$f(\PP_2)$ is polyhedron for $f$ still the canonical projection
+$K^n \rightarrow K^{n-1}$ and $\PP_2$
+defined by the linear matrix inequality (for some $B_2 \in K^q$):
+\[  \begin{bmatrix}
+\delta_1	& 		& 			&   &		 &  &a_1	\\
+			& \ddots& 			& 0	&		 &	&		\\
+			&		& \delta_l  &   & 		 &	& \vdots\\
+			&		&			&0  & 		 &	& 		\\
+			&		&			&   & \ddots &	&		\\
+			&		&			&	&		 & 0&a_{n-1} \\
+			&		&			&	&		 &	&a_n 	\\
+			&		&			&	&		 &	& \vdots   	\\
+			&		&			&	&		 &	&a_q 	\\			
+\end{bmatrix} \begin{bmatrix} x_1 \\ \\ \\ \\ \\ \vdots \\ \\ \\ \\ x_n \\ \end{bmatrix} + B_2 \geq 0.\]
+
+We remark that 
+$a_s x_n + b_s \geq 0$
+if and only if $x_n = -a_s^{-1} b_s + O(\pi^{- \val(a_s)}).$
+This exactly corresponds to $x_n \in B(-a_s^{-1} b_s, 2^{\val(a_s)}).$
+Since the conditions have to be compatible (we have assumed
+$\PP$ not empty), and thanks to ultrametricity,  
+the intersection of these conditions for 
+$s \in \llbracket l+1,q \rrbracket$
+is then given by the smallest of these balls.
+Let us assume it is the one defined for $l=n.$
+The only condition on $x_n$
+is then $\val(a_nx_n +b_n) \geq 0.$
+
+Thanks to the above discussion on diagonal mapping,
+we can further assume that the $\delta_i$'s and $a_n$ are all $1$'s
+and are reduce to $\PP_2$ defined by the linear matrix inequality :
+\[  \begin{bmatrix}
+1	& 		& 			&   &		 &  &a_1	\\
+			& \ddots& 			& 0	&		 &	&		\\
+			&		& 1  &   & 		 &	& \\
+			&		&			&0  & 		 &	& 	\vdots	\\
+			&		&			&   & \ddots &	&		\\
+			&		&			&	&		 & 0&a_{n-1} \\
+			&		&			&	&		 &	&1 	\\
+
+\end{bmatrix} \begin{bmatrix} x_1 \\ \\  \\ \\ \vdots \\  \\ \\ x_n \\ \end{bmatrix} + \begin{bmatrix} b_1 \\ \\ \\  \\ \vdots  \\ \\ \\ b_n \\ \end{bmatrix}  \geq 0.\]
+Finally, we can also assume that, up to a permutation of the variables, $\val(a_1)= \min_{i=1}^{n-1} \val(a_i).$
+We distinguish two cases: $\val(a_1) \geq 0$ and $\val(a_1)<0.$
+
+Let us first assume that $\val(a_1) \geq 0$
+
+Let $x \in \PP_2$.
+Then $x_n=-b_n+O(1)$
+and $x_1+a_1 x_n+b_1=O(1).$
+Consequently, $x_1-a_1 b_n +b_1=O(1)+O(\pi^{\val(a_1)})=O(1).$
+Similarly, for all $i \in \llbracket 2,n-1 \rrbracket,$
+$x_i-a_ib_n+b_i=O(1)+O(\pi^{\val(a_i)})=O(1).$
+
+We define the polyhedron $\Qc \subset K^{n-1}$ by the following inequalities:
+ for all $i \in \llbracket 1,n-1 \rrbracket,$
+$\val(x_i-a_ib_n+b_i) \geq 0.$
+
+Then the previous computations prove that $f(\PP_2)\subset \Qc.$
+Conversely, let $(x_1,\dots,x_{n-1}) \in \Qc.$
+Then let $x_n := -b_n.$
+
+We check that for $i \in \llbracket 1,n-1 \rrbracket,$
+$x_i+a_ix_n+b_i=x_i-a_ib_n+b_i=O(1),$
+and $x_n+b_n=O(1)$. Hence $(x_1,\dots,x_n) \in \PP_2$
+which means that $(x_1,\dots,x_{n-1}) \in f(\PP_2).$
+Thus $f(\PP_2)= \Qc$ and $f(\PP_2)$ is a polyhedron.
+
+We now deal with the second case, with $\val(a_1)<0.$
+Let $x \in \PP_2$.
+Then $x_n=-b_n+O(1)$
+and $x_1+a_1 x_n+b_1=O(1).$
+Consequently, $x_1-a_1 b_n +b_1=O(1)+O(\pi^{\val(a_1)})=O(\pi^{\val(a_1)})).$
+Thus $a_1^{-1}x_1- b_n +a_1^{-1}b_1=O(1)$.
+%and $x_n=-a_1^{-1}(x_1+b_1)+O(1).$
+In addition, $x_n=-a_1^{-1}(x_1+b_1)+O(\pi^{-\val(a_1)}).$
+We plug this equality in 
+$x_i+a_i x_n+b_i=O(1)$ to get
+$x_i-a_1^{-1}a_i(x_1+b_1)+b_i=O(1)+O(\pi^{\val(a_i)-\val(a_1)})=O(1)$
+using that $\val(a_i) \geq \val (a_1).$
+
+We define the polyhedron $\Qc \subset K^{n-1}$ by the following inequalities:
+$\val(a_1^{-1}x_1- b_n +a_1^{-1}b_1) \geq 0$ and for all $i \in \llbracket 2,n-1 \rrbracket,$
+$\val(x_i-a_1^{-1}a_i(x_1+b_1)+b_i) \geq 0.$
+
+Then the previous computations prove that $f(\PP_2)\subset \Qc.$
+Conversely, let $(x_1,\dots,x_{n-1}) \in \Qc.$
+Let $x_n := -a_1^{-1}(x_1+b_1).$
+Then
+$x_1+a_1 x_n+b_1=0=O(1).$
+Let $i \in \llbracket 2,n-1 \rrbracket,$
+then $x_i+a_i x_n+b_i=x_i-a_1^{-1}a_i(x_1+b_1)+b_i=O(1)$
+since $(x_1,\dots,x_{n-1}) \in \Qc.$
+Finally, 
+$x_n+b_n=-a_1^{-1}(x_1+b_1)+b_n=O(1)$ thanks to the inequality satisfied by $x_1.$
+Hence $(x_1,\dots,x_n) \in \PP_2$
+which means that $(x_1,\dots,x_{n-1}) \in f(\PP_2).$
+Thus $f(\PP_2)= \Qc$ and $f(\PP_2)$ is a polyhedron,
+and it has been proved in both cases.
+
+Therefore, if $f$ is the projection 
+$(x_1,\dots,x_{n-1},x_n)\mapsto (x_1,\dots,x_{n-1})$ 
+and $\PP$ is a polyhedron in $K^n$,
+then $f(\PP)$ is a polyhedron.
+
+\tristan{Attention, à partir de maintenant,
+il faut ajouter à la définition qu'on peut
+fixer des points!
+Cela revient à ajouter des conditions
+$\val = + \infty.$}
+
+It is also clear that
+if $f$ is the immersion 
+$K^l \rightarrow K^n$
+$(x_1,\dots,x_l)\mapsto (x_1,\dots,x_l,0,\dots,0)$ 
+and $\PP$ is a polyhedron in $K^n$,
+then $f(\PP)$ is a polyhedron.
+
+We now prove that for
+$\Delta$ a Smith Normal Form
+and $\PP$ a polyhedron,
+$\Delta(\PP)$ is a polyhedron.
+Then $\Delta$ is the composition
+of the immersion 
+$K^l \rightarrow K^n$
+$(x_1,\dots,x_l)\mapsto (x_1,\dots,x_l,0,\dots,0),$ 
+ the diagonal invertible mapping
+$K^l \rightarrow K^l$,
+$(x_1,\dots,x_l)\mapsto (\delta_1,\dots,\delta_l x_l)$,
+and the projections
+$(x_1,\dots,x_{l+1})\mapsto (x_1,\dots,x_{l}),$
+ $(x_1,\dots,x_{l+2})\mapsto (x_1,\dots,x_{l+1}),$
+ $\dots,$
+ $(x_1,\dots,x_{n})\mapsto (x_1,\dots,x_{n-1}).$
+ Thus $\Delta(\PP)$ is a polyhedron thanks to the previous 
+ results on image of polyhedron.
+
+Finally, if $f: K^n \rightarrow K^m$
+is a linear mapping and
+$f=Q^{-1} \Delta P$ is its Smith Normal Form
+with $P \in \GL_n(\OK),$ $Q \in \GL_m(\OK)$
+and $\Delta \in \allmat_{n,m}(K)$,
+then
+$P(\PP)$ is a polyhedron,
+$\Delta (P(\PP))$ also,
+and finally $f(\PP)=Q^{-1} (\Delta (P(\PP)))$
+is a polyhedron.
+This concludes the proof.
+\end{proof}
+
 \printbibliography

### 2023-12-11 article/paper_padic_spec.tex
petites corrections prop 6.1

@@
 Let us assume that 
-$\PP$ is defined by the set of conditions $\left\lbrace \val (l_i (x) ) \geq 0, \textrm{ for } i \in I \right\rbrace$ for some
-finite set $I \subset \N$ and all $l_i \in K[X]_1$ for $i \in I.$
-We further assume that $\PP$ is non-empty.
+$\PP = \left\lbrace x \in K^n : \val (l_i (x) ) \geq 0, \textrm{ for } i \in I \right\rbrace$ for some
+finite set $I \subset \N$ and $l_i \in K[x]_1$, for $i \in I.$ We further assume that $\PP \neq \emptyset$.
 
@@
 The $l_i \circ f^{-1}$ are clearly in $K[x]_1$
-and $f(P)$ is a polyhedra.
+and $f(P)$ is a polyhedron.
 
@@
 
-We can computer a Smith Normal Form
+We can compute a Smith Normal Form
 of the $q \times (n-1)$ matrix defined by the 

### 2024-01-16 article/paper_padic_spec.tex
some changes def polyhedra

@@
 \newenvironment{proof}{\hbox{}\vspace{-0.5cm} {\bf Proof:}}{\hfill $\Box$ \\}
+
+\usepackage{amsmath}
+\usepackage{amssymb}
+\usepackage{amsfonts}
+\usepackage{mathrsfs} 
+\usepackage{graphicx}
+\usepackage{color}
+\usepackage{ulem}
+\usepackage{bm}
+
+\usepackage{cleveref}
 
@@
 \newtheorem{corollary}[theorem]{Corollary}
-\newtheorem{algorithm}[theorem]{Algorithm}
+\newtheorem{algorithm}{Algorithm}
 \newtheorem{conjecture}[theorem]{Conjecture}
-\newtheorem{condition}[theorem]{Condition}
-\newtheorem{definition}[theorem]{Definition}
-\newtheorem{assumption}[theorem]{Assumption}
+\newtheorem{condition}{Condition}
+\newtheorem{definition}{Definition}
+\newtheorem{assumption}{Assumption}
 \newtheorem{remark}[theorem]{Remark}
@@
 \parskip2mm
-
-\usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage{amsfonts}
-\usepackage{mathrsfs} 
-\usepackage{graphicx}
-\usepackage{color}
-\usepackage{ulem}
-\usepackage{bm}
-
-\usepackage{cleveref}
 
@@
 
-\author{Corentin Cornou$^{1}$, Simone Naldi$^2$ and Tristan Vaccon$^2$}
+\author{Corentin Cornou$^{1}$, Simone Naldi$^{2,3}$ and Tristan Vaccon$^{2}$}
 
 \footnotetext[1]{ENS Paris-Saclay, Université Paris-Saclay, France.}
-\footnotetext[2]{Université de Limoges, CNRS, XLIM, Limoges, France.}
+\footnotetext[2]{Université de Limoges, CNRS, XLIM, UMR 7252, F-87000 Limoges, France.}
+\footnotetext[3]{Sorbonne Université, CNRS, LIP6, Equipe PolSys, F-75005 Paris, France.}
 
@@
 
-Il faudra entre autre mentionner (et peut être motiver l'approche p-adique) :
-\begin{itemize}
-\item les questions ouvertes de complexité concernant la programmation semidefinie (pas clair si NP $\cap$ co-NP
-  dans le modele de Turing)
-\item les questions ouvertes géométriques (Conjecture de Lax)
-\end{itemize}
+%Il faudra entre autre mentionner (et peut être motiver l'approche p-adique) :
+%\begin{itemize}
+%\item les questions ouvertes de complexité concernant la programmation semidefinie (pas clair si NP $\cap$ co-NP
+%  dans le modele de Turing)
+%\item les questions ouvertes géométriques (Conjecture de Lax)
+%\end{itemize}
 
@@
 matrices. A matrix $M \in \sym_d(\R)$
-is called {\it positive semidefinite} ($M \succeq 0$) whenever the quadratic
+is called \emph{positive semidefinite} ($M \succeq 0$) whenever the quadratic
 form $x \mapsto x^TMx$ is nonnegative for all $x\in \R^n$. By the Spectral Theorem, $M \succeq 0$
@@
 equivalently, its pre-image $S = \{x \in \R^n : A(x) \succeq 0\}$ under the map $x \mapsto A(x)$, is called
-a {\it real spectrahedron}. As affine sections of $\sym_d^+(\R)$, real spectrahedra are closed convex sets,
+a \emph{real spectrahedron}. As affine sections of $\sym_d^+(\R)$, real spectrahedra are closed convex sets,
 but might have empty interior in $\calL$ (resp. in $\R^n$). Moreover, they are basic semialgebraic sets,
@@
 
-The optimization problem of miminizing a linear function over a real spectrahedron is called {\it semidefinite programming} (SDP).
+The optimization problem of miminizing a linear function over a real spectrahedron is called \emph{semidefinite programming} (SDP).
 Given $c \in \R^n$ and $A_0,A_1,\ldots,A_n \in \sym_d(\R)$, the corresponding semidefinite program is defined (in standard dual form) as
@@
 number of variables, bit size of the coefficients), in $\log(\frac{1}{\varepsilon})$ (where $\varepsilon$ is the
-precision) and $\log(\frac{1}{R})$, where $R$ is an {\it a priori} upper bound on the norm of the solution,
+precision) and $\log(\frac{1}{R})$, where $R$ is an {\it a priori} upper bound on the norm of a solution,
 cf. \cite[Sec.1.9]{deKlerk}. In exact arithmetic, the complexity status of SDP is essentially open but complexity
@@
 A more general class of convex semialgebraic sets are obtained by linear projections of real spectrahedra
-called {\it semidefinite representable sets} (or spectrahedral shadows): these are sets of the form
+called \emph{semidefinite representable sets} (or spectrahedral shadows): these are sets of the form
 $$
@@
 
-%\subsection{Polyhedra}
-
-In this section, we define polyhedra over a complete discrete valuation field $K$ with valuation $\val$ and a uniformizer $\pi$,
-and we discuss the associated linear optimization problem.
+In this section, we define polyhedra over a complete discrete valuation field $K$ with valuation $\val$ and a uniformizer $\pi$, and we discuss the associated linear optimization problem.
 
 \begin{definition}
-  A {\it polyhedron} is a subset $P \subset K^n$ of the form
-  $P = \{x \in K^n : \val(\ell_1(x))\geq0,\ldots,\val(\ell_n(x))\geq 0\}$,
-  for some $\ell_1,\ldots,\ell_d \in K[x]_1$. This will often be denoted with
-  the compact notation $\val(\ell_1 \oplus \cdots \oplus \ell_d) \geq 0$, where $\val$
-  and $\geq$ are applied entrywise.
+  \label{def_polyhedra}
+  A \emph{polyhedron} is a subset $P \subset K^n$ of the form
+  $$
+  P = \{x \in K^n : \val(\ell_1 \oplus \cdots \oplus \ell_d) \geq 0 \text{ and }
+  \val(m_1 \oplus \cdots \oplus m_e) = +\infty\},
+  $$
+  for some $\ell_1,\ldots,\ell_d,m_1,\ldots,m_e \in K[x]_1$, where $\val,\geq$ and $=$ are applied entrywise.
+  We always assume without loss of generality that $m_1,\ldots,m_e$ are $K$-linearly independent.
 \end{definition}
 
+We recall that that the smallest affine space of $K^n$ containing a set $P \subset K^n$ is called its
+\emph{affine hull}. The constraint $\val(m_1 \oplus \cdots \oplus m_e) = +\infty$ in \Cref{def_polyhedra}
+is equivalent to $m_1(x) = \cdots = m_e(x) = 0$ and defines the affine hull of $P$. The \emph{dimension}
+of $P$ is defined as $n-e$ (namely the dimension of its affine hull).
+
 \begin{example}
-  The closed unit ball $B_\infty(K^n)$ in $K^n$ for the supremum norm $||\cdot||_{\infty}$ is the
+  The \emph{closed unit ball} $\OK^n=B_\infty(K^n)$ in $K^n$ for the supremum norm $||\cdot||_{\infty}$ is the
   polyhedron defined as the set of $x=(x_1,\ldots,x_n) \in K^n$ such that $||x||_{\infty} =
   \max_i\{x_i\} \leq 1$, in other words, such that $\val(x_i) \geq 0$, for all $i=1, \ldots, n$.
-  In other words, $\OK^n = B_\infty(K^n)$ is the polyhedron in $K^n$ defined by the affine polynomials
-  $\ell_i(x)=x_i$, $i=1,\ldots, n$.
-%  $$
-%  \begin{pmatrix} x_1 &  & & \\
-%    & x_2 &0 &  \\
-%    &  0& \ddots & \\
-%    &  & & x_s/
-  %  \end{pmatrix} \ge 0.$$
+  In other words, $\OK^n$ is the polyhedron in $K^n$ defined by the affine polynomials
+  $\ell_i(x)=x_i$, $i=1,\ldots, n$, and $e=0$ (its affine hull is indeed the whole $K^n$).
 \end{example}
 
-%\subsection{linear programming}
-
-A {\it linear programming problem} (or simply {\it linear program}) is given by the following
+A \emph{linear programming problem} (or simply \emph{linear program}) is given by the following
 optimization problem:
@@
 \begin{remark}
-  The valuation of the first coefficient\footnote{invariant factor?} of the SNF of a matrix
-  $M \in \allmat_{n,n} \left( K \right) $ is the minimum of the valuations of the matrix
-  $M$'s terms (\simone{proof or reference}). In particular, the the SNF of matrix of $\allmat_n \left( \OK \right) $ have coefficients in $\OK$.
+  The valuation of the first invariant factor of the SNF of a matrix
+  $M \in \allmat_{n,n} \left( K \right)$ is the minimum of the valuations of the entries of
+  $M$. In particular, the SNF of $M \in \allmat_n \left( \OK \right)$ has entries in $\OK$.
 \end{remark}
@@
 
-That property applied to the matrix $A$ in \ref{LP} allow to reduce the problem to an equivalent simpler iteration of the \ref{LP} problem that will be called {\it diagonal linear programming problem} \corentin{or maybe reduced linear programming problem?}.
+That property applied to the matrix $A$ in \ref{LP} allow to reduce the problem to an equivalent simpler iteration of the \ref{LP} problem that will be called \emph{diagonal linear programming problem} \corentin{or maybe reduced linear programming problem?}.
 This problem is the optimization problem:
@@
 
-The {\it associated diagonal linear programming problem} of a linear program is the iteration of the \ref{dLP} problem defined by $b' = Qb$, $c' = \left(P^{-1}\right)^T c$ and where $S$ is the Smith normal form of $A$ and $P \in GL_m\left( \OK \right)$ and $ Q \in GL_n\left( \OK \right)$ are such that $A = Q^{-1} S P$.
+The \emph{associated diagonal linear programming problem} of a linear program is the iteration of the \ref{dLP} problem defined by $b' = Qb$, $c' = \left(P^{-1}\right)^T c$ and where $S$ is the Smith normal form of $A$ and $P \in GL_m\left( \OK \right)$ and $ Q \in GL_n\left( \OK \right)$ are such that $A = Q^{-1} S P$.
 
-A vector $x^* \in K^n$ is {\it feasible solution} of \ref{LP} if $Ax^* + b \geq 0$.
+A vector $x^* \in K^n$ is \emph{feasible solution} of \ref{LP} if $Ax^* + b \geq 0$.
 Similarly, a vector $y^* \in K^n$ is a feasible of \ref{dLP} if $Sy^*+b' \geq 0$.
@@
 \begin{definition}
-	We call {\it spectrahedron} the intersection of $\mathcal{M}_n^+\left( K \right) $ with an affine plan $\mathcal{L}$ of $\mathcal{M}_n\left( K \right) $.
+  We call \emph{spectrahedron} the intersection of $\mathcal{M}_n^+\left( K \right) $ with an affine plan $\mathcal{L}$ of $\mathcal{M}_n\left( K \right) $.
 \end{definition}
@@
 
-	We call {\it annulus} a set $A$ defined as $C = \{x \in K  | a\le \val\left(x\right) \le b\} $ for $a < b$ two nonnegative real numbers.
+	We call \emph{annulus} a set $A$ defined as $C = \{x \in K  | a\le \val\left(x\right) \le b\} $ for $a < b$ two nonnegative real numbers.
 \end{definition}

### 2024-01-16 article/paper_padic_spec.tex
other modifs

@@
 
-\newenvironment{proof}{\hbox{}\vspace{-0.5cm} {\bf Proof:}}{\hfill $\Box$ \\}
+\newenvironment{proof}{\hbox{}\vspace{-0.8cm} {\bf Proof:}}{\hfill $\Box$}
 
@@
   for some $\ell_1,\ldots,\ell_d,m_1,\ldots,m_e \in K[x]_1$, where $\val,\geq$ and $=$ are applied entrywise.
-  We always assume without loss of generality that $m_1,\ldots,m_e$ are $K$-linearly independent.
+  We always assume without loss of generality that $m_1,\ldots,m_e$ are affinely independent.
 \end{definition}
@@
   The valuation of the first invariant factor of the SNF of a matrix
-  $M \in \allmat_{n,n} \left( K \right)$ is the minimum of the valuations of the entries of
-  $M$. In particular, the SNF of $M \in \allmat_n \left( \OK \right)$ has entries in $\OK$.
+  $M \in \allmat_{n,n}(K)$ is the minimum of the valuations of the entries of
+  $M$. In particular, the SNF of $M \in \allmat_n(\OK)$ has entries in $\OK$.
 \end{remark}
@@
 
-The \emph{associated diagonal linear programming problem} of a linear program is the iteration of the \ref{dLP} problem defined by $b' = Qb$, $c' = \left(P^{-1}\right)^T c$ and where $S$ is the Smith normal form of $A$ and $P \in GL_m\left( \OK \right)$ and $ Q \in GL_n\left( \OK \right)$ are such that $A = Q^{-1} S P$.
+The \emph{associated diagonal linear programming problem} of a linear program is the iteration of the \ref{dLP} problem defined by $b' = Qb$, $c' = \left(P^{-1}\right)^T c$ and where $S$ is the Smith normal form of $A$ and $P \in GL_m(\OK)$ and $ Q \in GL_n(\OK)$ are such that $A = Q^{-1} S P$.
 
@@
 \newcommand\Mats{positive semidefinite matrices }
+
 \begin{definition}
-	We call ... any matrix $M \in \mathcal{M}_n\left( K \right) $ whose eigenvalues have nonegative valuation (in $\overline{K}$) .
+  We call a matrix $M \in \mathcal{M}_n(K)$ \emph{positive semidefinite} (in symbols $M \succeq 0$)
+  if all its eigenvalues have nonnegative valuation in $\overline{K}$.
+  We denote by $\mathcal{M}_n^+(K) \subset \mathcal{M}_n(K)$ the set of positive semidefinite matrices.
+  The characteristic polynomial of $M$ is denoted $\chi_M$.
+\end{definition}
 
-	We will denote as $ \mathcal{M}_n^+\left( K \right)$ the set of \mats and we will write $M \succeq 0$ if $M \in \mathcal{M}_n^+\left( K\right) $.
-\end{definition}
 \begin{theorem}
   \label{caracsdp}
-	Characterization of the \mats
+  $M \in \mathcal{M}_n^+(K)$ if and only if $\chi_M$ has coefficients in $\OK$.
+\end{theorem}
+\begin{proof}
+  \simone{preuve ?}
+\end{proof}
 
-	A matrix is positive semidefinite if and only if its characteristic polynomial have coefficients in $\OK$.
-
-\end{theorem}
-
-\begin{corollary}
-	$\mathcal{M}_n(\OK) \subset \mathcal{M}_n^+\left( K \right)$ 
+\begin{corollary}\label{cor_caracsdp}
+  $\mathcal{M}_n(\OK) \subset \mathcal{M}_n^+(K)$.
 \end{corollary}
-
 \begin{proof}
-$\OK$ is a ring therefore the characteristic polynomial of matrix whose coefficients are $p$-adic integers have coefficients ins $Pp$. We conclude by \ref{caracsdp} .
+$\OK$ is a ring therefore the characteristic polynomial of matrix whose coefficients are $p$-adic integers have coefficients ins $Pp$ \simone{je comprends pas}. We conclude by \Cref{caracsdp}.
 \end{proof}
@@
 \begin{remark}
-	In general, the reverse inclusion is false.
-For instance the characteristic polynomial of $M = \begin{pmatrix} 5 + \frac{3}{5} & \frac{4}{5} \\ \frac{4}{5} & -\frac{3}{5} \end{pmatrix} $ is $\chi_M = X^2  - 5 X - 4$.
+  The reverse inclusion of \Cref{cor_caracsdp} is false. For instance the characteristic polynomial of
+  $M = \left(\begin{smallmatrix} 5 + \frac{3}{5} & \frac{4}{5} \\ \frac{4}{5} & -\frac{3}{5} \end{smallmatrix}\right)$ is $\chi_M = X^2-5X-4$.
 However when seen as an element of $\mathbb{Q}_5$, $\chi_M \in \mathbb{Z}_5[X]$ then $M \in \mathcal{M}_2^+\left( \mathbb{Q}_5 \right)$ but no coefficient of $M$ is in $\mathbb{Z}_5 $
@@
 \begin{proposition}
-	The set $\mathcal{M}_n^+\left( K \right)$ is :
-	\begin{enumerate}%[label = \textit{\roman*}.]
-		\item open
-		\item closed
-		%\item a convex cone
-	\end{enumerate}
+	The set $\mathcal{M}_n^+(K)$ is both open and closed.
 \end{proposition}
-
-\textit{Preuve :}  
-Firstly, $\OK[X]$ is closed and open in $\mathbb{Q}_{ p }[X] $ equiped with the infinitiy norm $\|.\|_\infty : P = \sum_{k=1}^{n} a_k X^k \to \sup |a_k|_p$.
+\begin{proof}
+Firstly, $\OK[X]$ is closed and open in $\mathbb{Q}_{p}[X]$ equiped with the infinitiy norm $\|.\|_\infty : P = \sum_{k=1}^{n} a_k X^k \to \sup |a_k|_p$.
 $\OK$ is indeed the open unit ball for $\|\cdot \|_\infty$ which defines a discrete distance for which open balls are also closed.
-Furthermore, $\mathcal{M}^+_{n}\left(K \right)  = \chi^{-1}( \OK[X]) $ where $\chi$ is the function that maps its characteristic polynomial to a matrix which is continuous.
-
-%Le $iii$. est laissé en exercice au lecteur. 
-% Je ne parle plus de convexité dans le rapport mais on ne sait jamais
-%\input{convexemple.tex}
+Furthermore, $\mathcal{M}^+_{n}(K) = \chi^{-1}(\OK[X]) $ where $\chi$ is the function that maps its characteristic polynomial to a matrix which is continuous.
+\end{proof}
 
 \begin{definition}
-  We call \emph{spectrahedron} the intersection of $\mathcal{M}_n^+\left( K \right) $ with an affine plan $\mathcal{L}$ of $\mathcal{M}_n\left( K \right) $.
+  \label{def_spectrahedra}
+  Let $\mathcal{L} = A_0+\span{A_1,\ldots,A_n} \subset \mathcal{M}_n(K)$ be an affine space, for given
+  matrices $A_0,A_1,\ldots,A_n$.
+  The set $\mathcal{L} \cap \mathcal{M}_n^+(K)$ is called a \emph{spectrahedron} or equivalently
+  its canonical preimage in $K^n$:
+  $$
+  S = \{x \in K^n : A_0+x_1A_1+\cdots+x_nA_n \succeq 0\}.
+  $$
 \end{definition}
 
-\begin{remark}
-	As in the real case, the spectrahedron associated with the affine plan $\mathcal{L}$ will often be identified with its preimage in $K^s$ (i.e.
+Remark that \Cref{def_spectrahedra} is invariant under intersection: the intersection of two
+(canonical preimages of) spectrahedra is a (canonical image of a) spectrahedron.
+
+%\begin{remark}
+%	As in the real case, the spectrahedron associated with the affine plan $\mathcal{L}$ will often be identified with its preimage in $K^s$ (i.e.
 the set of vectors $x \in K ^s$ so that the linear matrix $A(x) = A_0 + x_1A_1 + \ldots + x_sA_s$ is positive semidefinite with $A_0,A_1,\ldots,A_s$ spanning $\mathcal{L}$).
-\end{remark}
-
-The latter allows gives us the following property :
+%\end{remark}
 \begin{proposition}
@@
 \begin{proof}
-	Same as in the real case (maybe modify it or add the link to real proof).
+  Let $\ell_i,m_j \in K[x]_1$, for $i=1,\ldots,d$ and $j=1,\ldots,e$, and let $P = Q \cap L \subset K^n$
+  be the polyhedron given in \Cref{def_polyhedra}, for $Q = \{x \in K^n : \val(\ell_i) \geq 0, i=1,\ldots,d\}$
+  and $L = \{x \in K^n : \val(m_j) = 0, j=1,\ldots,e\}$.
+  First, denote by $A(x) = \ell_1 \oplus \cdots \oplus \ell_d$, so that $Q$ is the (preimage of the)
+  spectrahedron defined by $A(x) \succeq 0$.
+  Next, remark that $L \subset K^n$ is the affine space defined by equations $m_1=\ldots=m_e=0$.
+
+  Let $\varphi_Q : K^n \to \mathcal{M}_n(K)$
 \end{proof}
@@
 
-	We call \emph{annulus} a set $A$ defined as $C = \{x \in K  | a\le \val\left(x\right) \le b\} $ for $a < b$ two nonnegative real numbers.
+	We call \emph{annulus} a set $A$ defined as $C = \{x \in K  | a\le \val(x) \le b\} $ for $a < b$ two nonnegative real numbers.
 \end{definition}
@@
 
-\textit{Preuve :}
+\begin{proof}
 Let $A$ be the annuli defined by $a<b \in R^*_+$.
@@
 
-Let us show that $x \in C$ if and only if  $\exists y \in K \left( x,y \right) \in \mathcal{S}$.
+Let us show that $x \in C$ if and only if  $\exists y \in K(x,y) \in \mathcal{S}$.
 
@@
 Reciprocally if $x \in C$ then $(x,x^{-1}) $ verifies \ref{eq:caracsdp}  .
+\end{proof}
 

### 2024-01-17 article/paper_padic_spec.tex
commit by Simone

@@
 \emph{affine hull}. The constraint $\val(m_1 \oplus \cdots \oplus m_e) = +\infty$ in \Cref{def_polyhedra}
-is equivalent to $m_1(x) = \cdots = m_e(x) = 0$ and defines the affine hull of $P$. The \emph{dimension}
-of $P$ is defined as $n-e$ (namely the dimension of its affine hull).
+is equivalent to $m_1(x) = \cdots = m_e(x) = 0$ and since the forms $m_i$ are affinely independent, it
+defines the affine hull of $P$. The \emph{dimension} of $P$ is defined as $n-e$ (namely the dimension of
+its affine hull).
 
@@
 That property applied to the matrix $A$ in \ref{LP} allow to reduce the problem to an equivalent simpler iteration of the \ref{LP} problem that will be called \emph{diagonal linear programming problem} \corentin{or maybe reduced linear programming problem?}.
-This problem is the optimization problem:
+This problem is the optimization problem: \simone{il me semble que tout ça n'est pas trop clair, par exemple quelle est la difference entre diagonal LP et associated diagonal LP plus en bas, est-ce qu'il y a vraiment besoin de tout ça, il faut simplifier la presentation}
 \begin{equation}

### 2024-01-17 article/paper_padic_spec.tex
commit by Simone

@@
 \newtheorem{theorem}{Theorem}[section]
-\newtheorem{lemma}[theorem]{Lemma}
-\newtheorem{proposition}[theorem]{Proposition}
-\newtheorem{corollary}[theorem]{Corollary}
+\newtheorem{lemma}{Lemma}
+\newtheorem{proposition}{Proposition}
+\newtheorem{corollary}{Corollary}
 \newtheorem{algorithm}{Algorithm}
-\newtheorem{conjecture}[theorem]{Conjecture}
+\newtheorem{conjecture}{Conjecture}
 \newtheorem{condition}{Condition}
@@
 \newtheorem{assumption}{Assumption}
-\newtheorem{remark}[theorem]{Remark}
-\newtheorem{problem}[theorem]{Problem}
-\newtheorem{example}[theorem]{Example}
-\newtheorem{notation}[theorem]{Notation}
+\newtheorem{remark}{Remark}
+\newtheorem{problem}{Problem}
+\newtheorem{example}{Example}
+\newtheorem{notation}{Notation}
 \usepackage{booktabs}
@@
 equivalently, its pre-image $S = \{x \in \R^n : A(x) \succeq 0\}$ under the map $x \mapsto A(x)$, is called
-a \emph{real spectrahedron}. As affine sections of $\sym_d^+(\R)$, real spectrahedra are closed convex sets,
-but might have empty interior in $\calL$ (resp. in $\R^n$). Moreover, they are basic semialgebraic sets,
-defined by sign conditions on the principal minors of the defining matrix as well as sign conditions on the
-coefficients of its characteristic polynomial (cf. \Cref{ell3}).
+a \emph{real spectrahedron}. As (linear preimage of) affine sections of $\sym_d^+(\R)$, real spectrahedra
+are closed convex sets, but might have empty interior in $\calL$ (resp. in $\R^n$).
+Moreover, they are basic semialgebraic sets, indeed they are defined by sign conditions on the principal
+minors of the defining matrix as well as sign conditions on the coefficients of its characteristic polynomial
+(cf. \Cref{ell3}).
 

### 2024-01-17 article/paper_padic_spec.tex
commit by Simone

@@
 \renewcommand{\span}[1]{{\text{span}(#1)}} % simone's comments
+\newcommand{\aff}[1]{{\text{aff}(#1)}} % simone's comments
+\newcommand{\relint}[1]{{\text{relint}(#1)}} % simone's comments
 \newcommand{\calL}{\mathcal{L}} % simone's comments
@@
   for some $\ell_1,\ldots,\ell_d,m_1,\ldots,m_e \in K[x]_1$, where $\val,\geq$ and $=$ are applied entrywise.
-  We always assume without loss of generality that $m_1,\ldots,m_e$ are affinely independent.
+  We assume without loss of generality that for every $i=1,\ldots,d$ there exists $x \in P$ such that
+  $\val(\ell_i(x))<+\infty$.
 \end{definition}
 
-We recall that that the smallest affine space of $K^n$ containing a set $P \subset K^n$ is called its
-\emph{affine hull}. The constraint $\val(m_1 \oplus \cdots \oplus m_e) = +\infty$ in \Cref{def_polyhedra}
-is equivalent to $m_1(x) = \cdots = m_e(x) = 0$ and since the forms $m_i$ are affinely independent, it
-defines the affine hull of $P$. The \emph{dimension} of $P$ is defined as $n-e$ (namely the dimension of
-its affine hull).
+We recall that that the smallest affine space of $K^n$ containing a set $S \subset K^n$ is called its
+\emph{affine hull} and denoted $\aff{S}$.
+The assumption on forms $\ell_i$ in \Cref{def_polyhedra} implies that the constraint
+$\val(m_1 \oplus \cdots \oplus m_e) = +\infty$ defines exactly the affine hull of $P$, in other words
+$\aff{P} = \{x \in K^n : m_j(x) = 0,
+j=1,\ldots,e\}$. The \emph{dimension} of $P$ is defined as the dimension of $\aff{P}$ (for $e=0$,
+$\aff{P}=K^n$ and $P$ has dimension $n$).
+The \emph{relative interior} of $P$ is defined as $\relint{P} = \{x \in P : \val(\ell_1 \oplus \cdots \oplus \ell_d)
+< +\infty\}$.
+Remark that \Cref{def_polyhedra} includes the case $d=0$ corresponding to affine spaces, as in the real case.
 
@@
 
-\begin{definition}[Smith Normal Form]\label{smith_nf}
+\begin{definition}[Smith Normal Form]\label{smith_nf} \simone{Je trouve que la SNF devrait être inclue dans les
+  préliminaires, car on l'utilise ailleurs, et laisser cette section pour polyèdre+LP}
   Let $M \in \allmat_{m,n}(K)$ be of rank $r$. There exist unique integers $a_1 \leq \cdots \leq a_r$, and
@@
   We call a matrix $M \in \mathcal{M}_n(K)$ \emph{positive semidefinite} (in symbols $M \succeq 0$)
-  if all its eigenvalues have nonnegative valuation in $\overline{K}$.
+  if all its eigenvalues have nonnegative valuation in an algebraic closure of $K$.
   We denote by $\mathcal{M}_n^+(K) \subset \mathcal{M}_n(K)$ the set of positive semidefinite matrices.
@@
 \begin{proof}
-$\OK$ is a ring therefore the characteristic polynomial of matrix whose coefficients are $p$-adic integers have coefficients ins $Pp$ \simone{je comprends pas}. We conclude by \Cref{caracsdp}.
+$\OK$ is a ring therefore the characteristic polynomial of matrix whose coefficients are $p$-adic integers have coefficients ins $Pp$ \simone{je comprends pas la fin de la phrase}.
+We conclude by \Cref{caracsdp}.
 \end{proof}
@@
   \label{def_spectrahedra}
-  Let $\mathcal{L} = A_0+\span{A_1,\ldots,A_n} \subset \mathcal{M}_n(K)$ be an affine space, for given
-  matrices $A_0,A_1,\ldots,A_n$.
-  The set $\mathcal{L} \cap \mathcal{M}_n^+(K)$ is called a \emph{spectrahedron} or equivalently
+  Let $\mathcal{L} = A_0+\span{A_1,\ldots,A_n} \subset \mathcal{M}_n(K)$ be an affine space, for some
+  $A_0,A_1,\ldots,A_n \in \mathcal{M}_n(K)$.
+  The set $\mathcal{L} \cap \mathcal{M}_n^+(K)$ or equivalently,
   its canonical preimage in $K^n$:
   $$
-  S = \{x \in K^n : A_0+x_1A_1+\cdots+x_nA_n \succeq 0\}.
+  S_A = \{x \in K^n : A_0+x_1A_1+\cdots+x_nA_n \succeq 0\},
   $$
+  is called a \emph{spectrahedron}.
 \end{definition}
 
-Remark that \Cref{def_spectrahedra} is invariant under intersection: the intersection of two
-(canonical preimages of) spectrahedra is a (canonical image of a) spectrahedron.
+\begin{remark}
+  The class of spectrahedra is closed under intersection. Indeed, for affine spaces $\mathcal{L}_1,\mathcal{L}_2$
+  one has $(\mathcal{L}_1 \cap \mathcal{M}_n^+(K)) \cap (\mathcal{L}_2 \cap \mathcal{M}_n^+(K)) =
+  (\mathcal{L}_1\cap\mathcal{L}_2) \cap \mathcal{M}_n^+(K)$. Now
+  assuming $\mathcal{L}_1 = A_0+\span{A_1,\ldots,A_n}$ and $\mathcal{L}_2 = B_0+\span{B_1,\ldots,B_n}$,
+  then 
+\end{remark}
 

### 2024-01-18 article/paper_padic_spec.tex
def pol

@@
 $\aff{P} = \{x \in K^n : m_j(x) = 0,
-j=1,\ldots,e\}$. The \emph{dimension} of $P$ is defined as the dimension of $\aff{P}$ (for $e=0$,
+j=1,\ldots,e\}$ (\simone{il nous faudrait une preuve}).
+The \emph{dimension} of $P$ is defined as the dimension of $\aff{P}$ (for $e=0$,
 $\aff{P}=K^n$ and $P$ has dimension $n$).
 The \emph{relative interior} of $P$ is defined as $\relint{P} = \{x \in P : \val(\ell_1 \oplus \cdots \oplus \ell_d)
-< +\infty\}$.
+< +\infty\}$ (\simone{pas clair si besoin de dimension et relint}).
 Remark that \Cref{def_polyhedra} includes the case $d=0$ corresponding to affine spaces, as in the real case.
@@
   $A_0,A_1,\ldots,A_n \in \mathcal{M}_n(K)$.
-  The set $\mathcal{L} \cap \mathcal{M}_n^+(K)$ or equivalently,
-  its canonical preimage in $K^n$:
-  $$
-  S_A = \{x \in K^n : A_0+x_1A_1+\cdots+x_nA_n \succeq 0\},
-  $$
-  is called a \emph{spectrahedron}.
+  The set $\mathcal{L} \cap \mathcal{M}_n^+(K)$ is called a \emph{spectrahedron}. Its 
+  its canonical preimage $S_A = \{x \in K^n : A_0+x_1A_1+\cdots+x_nA_n \succeq 0\}$
+  is also called spectrahedron.
 \end{definition}
@@
   assuming $\mathcal{L}_1 = A_0+\span{A_1,\ldots,A_n}$ and $\mathcal{L}_2 = B_0+\span{B_1,\ldots,B_n}$,
-  then 
+  then $S_A \cap S_B = S_{A \oplus B}$ (indeed both $A \succeq 0$ and $B \succeq 0$ if and only if
+  $A \oplus B \succeq 0$).
 \end{remark}
@@
   Let $\ell_i,m_j \in K[x]_1$, for $i=1,\ldots,d$ and $j=1,\ldots,e$, and let $P = Q \cap L \subset K^n$
-  be the polyhedron given in \Cref{def_polyhedra}, for $Q = \{x \in K^n : \val(\ell_i) \geq 0, i=1,\ldots,d\}$
+  be a polyhedron as in \Cref{def_polyhedra}, for $Q = \{x \in K^n : \val(\ell_i) \geq 0, i=1,\ldots,d\}$
   and $L = \{x \in K^n : \val(m_j) = 0, j=1,\ldots,e\}$.

### 2024-01-18 article/paper_padic_spec.tex
commit by Simone

@@
 Another example is the field of Laurent series
-$K=\QQ(\!(t)\!)$ equiped with $t$-adic valuation.
-In this case, $\OK = \QQ \llbracket t \rrbracket$.
+$K=\QQ(\!(t)\!)$ equiped with $t$-adic valuation,
+in which case $\OK = \QQ \llbracket t \rrbracket$.
 We refer to \cite{Serre:1979} for a
 general introduction to such fields
-and to X.~Caruso's course on $p$-adic computations \cite{caruso_computations_2017}
+and to Caruso's course on $p$-adic computations \cite{caruso_computations_2017}
 for an introduction to effective computations over $p$-adic numbers.
@@
 
-\section{Polyhedra and linear programming}
+\section{Polyhedra}
 
@@
 j=1,\ldots,e\}$ (\simone{il nous faudrait une preuve}).
-The \emph{dimension} of $P$ is defined as the dimension of $\aff{P}$ (for $e=0$,
-$\aff{P}=K^n$ and $P$ has dimension $n$).
-The \emph{relative interior} of $P$ is defined as $\relint{P} = \{x \in P : \val(\ell_1 \oplus \cdots \oplus \ell_d)
-< +\infty\}$ (\simone{pas clair si besoin de dimension et relint}).
+%The \emph{dimension} of $P$ is defined as the dimension of $\aff{P}$ (for $e=0$, $\aff{P}=K^n$ and $P$ has dimension $n$).
+The \emph{relative interior} of $P$ is defined as $\relint{P} = \{x \in P : \val(\ell_1 \oplus \cdots \oplus \ell_d) < +\infty\}$ (\simone{pas clair si besoin de dimension et relint}).
 Remark that \Cref{def_polyhedra} includes the case $d=0$ corresponding to affine spaces, as in the real case.
@@
 \begin{definition}
-  We call a matrix $M \in \mathcal{M}_n(K)$ \emph{positive semidefinite} (in symbols $M \succeq 0$)
+  We call a matrix $M \in \allmat_{d,d}(K)$ \emph{positive semidefinite} (in symbols $M \succeq 0$)
   if all its eigenvalues have nonnegative valuation in an algebraic closure of $K$.
-  We denote by $\mathcal{M}_n^+(K) \subset \mathcal{M}_n(K)$ the set of positive semidefinite matrices.
-  The characteristic polynomial of $M$ is denoted $\chi_M$.
+  We denote by $\allmat_{d,d}^+(K) \subset \allmat_{d,d}(K)$ the set of positive semidefinite matrices.
+  The characteristic polynomial of a matrix $M \in \allmat_{d,d}(K)$ is denoted $\chi_M \in K[T]$.
 \end{definition}
@@
   \label{caracsdp}
-  $M \in \mathcal{M}_n^+(K)$ if and only if $\chi_M$ has coefficients in $\OK$.
+  $M \in \allmat_{d,d}^+(K)$ if and only if $\chi_M \in \OK[T]$.
 \end{theorem}
@@
 \begin{corollary}\label{cor_caracsdp}
-  $\mathcal{M}_n(\OK) \subset \mathcal{M}_n^+(K)$.
+  $\allmat_{d,d}(\OK) \subset \allmat_{d,d}^+(K)$.
 \end{corollary}
 \begin{proof}
-$\OK$ is a ring therefore the characteristic polynomial of matrix whose coefficients are $p$-adic integers have coefficients ins $Pp$ \simone{je comprends pas la fin de la phrase}.
-We conclude by \Cref{caracsdp}.
+  $\OK$ is a ring therefore if $M \in \allmat_{d,d}(\OK)$, then $\chi_M \in \OK[T]$, thus we conclude
+  by \Cref{caracsdp}.
 \end{proof}
 
-\begin{remark}
-  The reverse inclusion of \Cref{cor_caracsdp} is false. For instance the characteristic polynomial of
-  $M = \left(\begin{smallmatrix} 5 + \frac{3}{5} & \frac{4}{5} \\ \frac{4}{5} & -\frac{3}{5} \end{smallmatrix}\right)$ is $\chi_M = X^2-5X-4$.
-However when seen as an element of $\mathbb{Q}_5$, $\chi_M \in \mathbb{Z}_5[X]$ then $M \in \mathcal{M}_2^+\left( \mathbb{Q}_5 \right)$ but no coefficient of $M$ is in $\mathbb{Z}_5 $
-\end{remark}
+\begin{example}
+  The reverse inclusion of \Cref{cor_caracsdp} is false in general. For instance the characteristic polynomial of
+  $M = (\begin{smallmatrix} 5 + {3}/{5} & {4}/{5} \\ {4}/{5} & -{3}/{5} \end{smallmatrix})$ is $\chi_M = T^2-5T-4$.
+However when seen as a matrix over $K=\mathbb{Q}_5$, then $\chi_M \in \mathbb{Z}_5[T] = \OK[T]$: then $M \in \allmat_{2,2}^+(\mathbb{Q}_5)$, nevertheless $M \not\in \allmat_{2,2}(\mathbb{Z}_5)$, hence $\allmat_{2,2}^+(\mathbb{Q}_5) \not\subset \allmat_{2,2}(\mathbb{Z}_5)$.
+\end{example}
 
 \begin{proposition}
-	The set $\mathcal{M}_n^+(K)$ is both open and closed.
+  The set $\allmat_{d,d}^+(K)$ is both open and closed.
 \end{proposition}
 \begin{proof}
-Firstly, $\OK[X]$ is closed and open in $\mathbb{Q}_{p}[X]$ equiped with the infinitiy norm $\|.\|_\infty : P = \sum_{k=1}^{n} a_k X^k \to \sup |a_k|_p$.
+Firstly, $\OK[X]$ is closed and open in $\mathbb{Q}_{p}[X]$ (\simone{attention p-adique}) equipped with the infinitiy norm $\|\cdot\|_\infty : P = \sum_{k=1}^{n} a_k X^k \to \sup |a_k|_p$ \simone{attention p-adique}.
 $\OK$ is indeed the open unit ball for $\|\cdot \|_\infty$ which defines a discrete distance for which open balls are also closed.
-Furthermore, $\mathcal{M}^+_{n}(K) = \chi^{-1}(\OK[X]) $ where $\chi$ is the function that maps its characteristic polynomial to a matrix which is continuous.
+Furthermore, $\allmat^+_{d,d}(K) = \chi^{-1}(\OK[X]) $ where $\chi$ is the function that maps its characteristic polynomial to a matrix which is continuous.
+\simone{mmm je dirais plutôt ``the function that maps a matrix to its characteristic polynomial'', n'est-ce pas ?}
 \end{proof}
+
+\simone{que peut-on dire de plus de l'ensemble $\allmat_{d,d}^+(K)$ ? normalement c'est un cône non ? peut être
+  à cause de \Cref{caracsdp} c'est un $\OK$-cône mais pas un $K$-cône ? ça serait un peu contre-intuitif, mais
+  bon, on est sur un corps abstrait.}
 
@@
   \label{def_spectrahedra}
-  Let $\mathcal{L} = A_0+\span{A_1,\ldots,A_n} \subset \mathcal{M}_n(K)$ be an affine space, for some
-  $A_0,A_1,\ldots,A_n \in \mathcal{M}_n(K)$.
-  The set $\mathcal{L} \cap \mathcal{M}_n^+(K)$ is called a \emph{spectrahedron}. Its 
-  its canonical preimage $S_A = \{x \in K^n : A_0+x_1A_1+\cdots+x_nA_n \succeq 0\}$
-  is also called spectrahedron.
+  Let $\mathcal{L} = A_0+\span{A_1,\ldots,A_n} \subset \allmat_{d,d}(K)$ be an affine space, for some
+  $A_0,A_1,\ldots,A_n \in \allmat_{d,d}(K)$.
+  The set $\mathcal{L} \cap \allmat_{d,d}^+(K)$ is called a \emph{spectrahedron}. The set 
+  $S_A = \{x \in K^n : A_0+x_1A_1+\cdots+x_nA_n \succeq 0\}$, that is the preimage of $\allmat_{d,d}^+(K)$
+  under the map $x \mapsto A_0+x_1A_1+\cdots+x_nA_n$, is also called spectrahedron.
 \end{definition}
@@
   The class of spectrahedra is closed under intersection. Indeed, for affine spaces $\mathcal{L}_1,\mathcal{L}_2$
-  one has $(\mathcal{L}_1 \cap \mathcal{M}_n^+(K)) \cap (\mathcal{L}_2 \cap \mathcal{M}_n^+(K)) =
-  (\mathcal{L}_1\cap\mathcal{L}_2) \cap \mathcal{M}_n^+(K)$. Now
+  one has $(\mathcal{L}_1 \cap \allmat_{d,d}^+(K)) \cap (\mathcal{L}_2 \cap \allmat_{d,d}^+(K)) =
+  (\mathcal{L}_1 \cap \mathcal{L}_2) \cap \allmat_{d,d}^+(K)$. Now
   assuming $\mathcal{L}_1 = A_0+\span{A_1,\ldots,A_n}$ and $\mathcal{L}_2 = B_0+\span{B_1,\ldots,B_n}$,
@@
   be a polyhedron as in \Cref{def_polyhedra}, for $Q = \{x \in K^n : \val(\ell_i) \geq 0, i=1,\ldots,d\}$
-  and $L = \{x \in K^n : \val(m_j) = 0, j=1,\ldots,e\}$.
-  First, denote by $A(x) = \ell_1 \oplus \cdots \oplus \ell_d$, so that $Q$ is the (preimage of the)
-  spectrahedron defined by $A(x) \succeq 0$.
+  and $L = \{x \in K^n : \val(m_j) = +\infty, j=1,\ldots,e\}$.
+  First, denote by $A(x) = \ell_1 \oplus \cdots \oplus \ell_d \in \allmat_{d,d}(K[x]_1)$,
+  so that $A = A_0+x_1A_1+\cdots+x_nA_n$ for some (diagonal) $A_i \in \allmat_{d,d}(K)$.
+  One has $Q=S_A$.
   Next, remark that $L \subset K^n$ is the affine space defined by equations $m_1=\ldots=m_e=0$.
+  Define $B = m_1 \oplus \cdots \oplus m_e \in \allmat_{e,e}(K[x]_1)$
 
@@
 \printbibliography
+
 \end{document}

### 2024-01-19 article/paper_padic_spec.tex
preuve poly spec

@@
 $\aff{P} = \{x \in K^n : m_j(x) = 0,
-j=1,\ldots,e\}$ (\simone{il nous faudrait une preuve}).
+j=1,\ldots,e\}$ \simone{(il nous faudrait une preuve, du genre: $\val(m(x))=+\infty$ pour tout $x \in P$ si et seulement si $m$ est une combinaison affine de $m_1,\ldots,m_e$.)}
 %The \emph{dimension} of $P$ is defined as the dimension of $\aff{P}$ (for $e=0$, $\aff{P}=K^n$ and $P$ has dimension $n$).
@@
 Remark that \Cref{def_polyhedra} includes the case $d=0$ corresponding to affine spaces, as in the real case.
+Moreover by definition the class of polyhedra is closed under intersection.
 
@@
   First, denote by $A(x) = \ell_1 \oplus \cdots \oplus \ell_d \in \allmat_{d,d}(K[x]_1)$,
-  so that $A = A_0+x_1A_1+\cdots+x_nA_n$ for some (diagonal) $A_i \in \allmat_{d,d}(K)$.
-  One has $Q=S_A$.
-  Next, remark that $L \subset K^n$ is the affine space defined by equations $m_1=\ldots=m_e=0$.
-  Define $B = m_1 \oplus \cdots \oplus m_e \in \allmat_{e,e}(K[x]_1)$
-
-  Let $\varphi_Q : K^n \to \mathcal{M}_n(K)$
+  so that $A(x) = A_0+x_1A_1+\cdots+x_nA_n$ for some (diagonal) $A_i \in \allmat_{d,d}(K)$.
+  We might assume that $A_0,A_1,\ldots,A_n$ are affinely independent, so that the mapping
+  $\varphi(x) = A(x)$ is injective. 
+  First, remark that $Q=S_A$ and thus $\varphi(Q) = \mathcal{L} \cap \allmat_{d,d}(K)$, with
+  $\mathcal{L} = A_0+\span{A_1,\ldots,A_n}$ is a spectrahedron.
+  Next, remark that $L \subset K^n$ is the affine space defined by equations $m_1=\ldots=m_e=0$,
+  hence $\varphi(L) \subset \allmat_{d,d}(K)$ is an affine space. Since $\varphi$ is injective,
+  one has $\varphi(P) = \varphi(Q \cap L) = \varphi(Q) \cap \varphi(L)$ which is the intersection
+  of a spectrahedron with an affine space, thus a spectrahedron.
+  %Define $B = m_1 \oplus \cdots \oplus m_e \in \allmat_{e,e}(K[x]_1)$
 \end{proof}

### 2024-01-25 article/paper_padic_spec.tex
preuve 4.1 (incomplète)

@@
 \begin{proof}
+  Both sense of the equivalence will be proven by contraposition.
+
+  Let $M \in \allmat_{d,d}(K)$ with characteristic polynomial $\chi_M = X^d + \sum_{i=0}^{d} a_i X_i$ for $a_0,...,a_{d-1} \in K$.
+  Firstly, suppose $\chi_M$ have a root $\rho$ of negative valuation {\it i.e.} $M \not \in \allmat_{d,d}^+(K)$.
+  It follows that $\val \chi_M (\rho) = \val \left(\rho^n \sum_{i=0}^{d} a_i \rho^i \right) = + \infty$ and $\val \rho^d = d \val \rho <0$.
+  The properties of the non-archimedean inequality followed by $\val $ implie that $\val \left( \sum_{i=0}^{d} a_i \rho^i\right) = \val \rho^n$ and $\val \left( \sum_{i=0}^{d} a_i \rho^i\right) \ge \min \limits_{i=0,..., d-1} \val \left(a_i \rho^i\right)$.
+Therefore, there exists $i \in \left\{0,...,d-1\right\}$ such that $\val( a_i \rho^i) \le \val\rho^n$ {\it i.e.} such that $\val (a_i) \le (n-i) \val \rho <0$.
+
+  We have proven the converse sense of the equivalence. To prove the direct sense we will need a brief intriduction to Newton's polygon.
+
+  Let suppose $\chi_M \not\in O_K[X]$.
+There exists $j \in \{0,...,d-1\}$ such that $\val (a_j)<0$.
+The polynomial $\chi_M$ being monic the point with abscissa $n$ of $\chi_M$'s Newton's Polygon is $(n,0)$.
+  Therefore, the point $(j, a_j)$ having negative ordinate implies that at least one of the slopes of $\chi_M$'s Newton's Polygon is positive so that $\chi_M$ has a root with negative valuation.
   \simone{preuve ?}
@@
 \begin{proof}
-Firstly, $\OK[X]$ is closed and open in $\mathbb{Q}_{p}[X]$ (\simone{attention p-adique}) equipped with the infinitiy norm $\|\cdot\|_\infty : P = \sum_{k=1}^{n} a_k X^k \to \sup |a_k|_p$ \simone{attention p-adique}.
-$\OK$ is indeed the open unit ball for $\|\cdot \|_\infty$ which defines a discrete distance for which open balls are also closed.
-Furthermore, $\allmat^+_{d,d}(K) = \chi^{-1}(\OK[X]) $ where $\chi$ is the function that maps its characteristic polynomial to a matrix which is continuous.
+Firstly, $\OK[X]$ is closed and open in $K[X]$ (\simone{attention p-adique}) equipped with the infinitiy norm $\|\cdot\|_\infty : P = \sum_{k=1}^{n} a_k X^k \to \sup |a_k|$ \simone{attention p-adique}.
+$\OK$ is indeed the open unit ball for $\|\cdot \|_\infty$ that induces a discrete distance for which open balls are also closed sets.
+Furthermore, $\allmat^+_{d,d}(K) = \chi^{-1}(\OK[X]) $ where $\chi$ is the function that maps a matrix to its characteristic polynomial which is continuous.
 \simone{mmm je dirais plutôt ``the function that maps a matrix to its characteristic polynomial'', n'est-ce pas ?}

### 2024-01-29 article/paper_padic_spec.tex
Ajout preuve caracterisation, modifs programmation lineaire et preuve couronne

--- 2024-01-19 article/paper_padic_spec.tex
@@
 Indeed, if $z \in K^n$ and $M \in \allmat_n(\OK)$ such that $z \geq 0$ then $Mz \geq 0$.
-The latter property is a direct consequence of $\OK$ being a ring and the converse is true if the matrix $M$ is invertible in $\OK$ \corentin{est-ce qu'il y a besoin de le prouver ?}.
+The latter property is a direct consequence of $\OK$ being a ring and the converse holds if the matrix $M$ is invertible in $\OK$.
 Therefore, for all matrix $M \in \allmat_n(K)$ with SNF $S$ and all $z \in K^n$ $Mz \geq 0$ if and only if $Sz \geq 0$.
@@
 \begin{equation}
-  \tag{dLP}\label{dLP}
+  \tag{DLP}\label{DLP}
 \begin{array}{rcll}
@@
 
-The \emph{associated diagonal linear programming problem} of a linear program is the iteration of the \ref{dLP} problem defined by $b' = Qb$, $c' = \left(P^{-1}\right)^T c$ and where $S$ is the Smith normal form of $A$ and $P \in GL_m(\OK)$ and $ Q \in GL_n(\OK)$ are such that $A = Q^{-1} S P$.
+%The \emph{associated diagonal linear programming problem} of a linear program is the iteration of the \ref{DLP} problem defined by $b' = Qb$, $c' = \left(P^{-1}\right)^T c$ and where $S$ is the Smith normal form of $A$ and $P \in GL_m(\OK)$ and $ Q \in GL_n(\OK)$ are such that $A = Q^{-1} S P$.
 
 A vector $x^* \in K^n$ is \emph{feasible solution} of \ref{LP} if $Ax^* + b \geq 0$.
-Similarly, a vector $y^* \in K^n$ is a feasible of \ref{dLP} if $Sy^*+b' \geq 0$.
-We will denote as $Adm$ \corentin{Probablement à changer mais je ne sais pas quel nom lui donner} the set of feasible solution of \ref{dLP}.
+Similarly, a vector $y^* \in K^n$ is a feasible of \ref{DLP} if $Sy^*+b' \geq 0$.
+We will denote as $Adm$ \corentin{Probablement à changer mais je ne sais pas quel nom lui donner} the set of feasible solution of \ref{DLP}.
 
+\begin{proposition} 
+  Let $A \in \allmat_{m,n}(K), b \in K^m, c\in K^n$ and let $S \in \allmat_{m,n}(K)$ be the Smith normal form of $A$ with transition matrices $P \in \GL_n(\OK)$ and $Q\in \GL(\OK)$ such that $A=Q^{-1}SP$.
+  We define $b':= Qb$ and $c':= (P^{-1})^Tc$. 
+   \begin{enumerate}
+    \item $x^* \in K^n$ is a feasible solution of the \ref{LP} problem of parameters $A, b$ and $c$ if and only if $y^* = P x^*$ is a feasible solution of the \ref{DLP} problem of parameters $S, b'$ ans $c'$.
+		\item $x \in K^n$ is a solution of the \ref{LP} problem of parameters $A, b$ and $c$ if and only if $y = P x$ is a solution of the \ref{DLP} problem of parameters $S,b'$ and $c'$ and $\langle c,x \rangle = \langle c',y \rangle$.
+   \end{enumerate}
+\end{proposition}
+\begin{proof}
+  First of all, 1. is a direct consequence of the fact that $Ax^*+b = AP^{-1}y^* +b\geq 0$ if and only if $Q(AP^{-1}y^* + b) = Sy^* + b' \geq 0$ because $Q \in GL_m(\OK)$.
+
+  Then, 2. comes from the fact that for all $c \in K^n$ $\langle c, x\rangle = \langle c, P^{-1}Py \rangle = \langle \left(P^{-1}\right)^T c, y \rangle$.
+\end{proof}
+
+The last proposition allows to only consider the resolution of the \ref{DLP} problem.
 \begin{proposition}\label{prop:reduc}
@@
 	\begin{enumerate}
-		\item $x^*$ is a feasible solution of \ref{LP} if and only if $y^* = P x^*$ is a feasible solution of the associated \ref{dLP} problem.
-		\item $x$ is a solution of \ref{LP} if and only if $y = P x$ is a solution of the associated \ref{dLP} and the the infimum is the same.
-		\item \ref{dLP} have feasible solutions if and only if the $m-r$ last coefficients of $b'$ have nonegative valuation, with $r$ the rank of $S$.
-		\item If at least one of the $n-r$ last coefficients of $c'$ is non-zero, if \ref{dLP} admits feasible solutions it is unbounded and does not have a solution.
+
+		\item \ref{DLP} have feasible solutions if and only if the $m-r$ last coefficients of $b'$ have nonegative valuation, with $r$ the rank of $S$.
+		\item If at least one of the $n-r$ last coefficients of $c'$ is non-zero, if \ref{DLP} admits feasible solutions it is unbounded and does not have a solution.
 
@@
 \begin{proof}
-
-  First of all, 1. is a consequence of the fact that $Mx^*+b = MP^{-1}y^* +b\geq 0$ if and only if $Q(MP^{-1}y^* + b) = Sy^* + b' \geq 0$ because $Q \in GL_m(\OK)$.
-
-  Then, 2. comes from the fact that for all $c \in K^n$ $\langle c, x\rangle = \langle c, P^{-1}Py \rangle = \langle \left(P^{-1}\right)^T c, y \rangle$.
-
-  A vector $y =  \left[\begin{smallmatrix} y_1 \\ \vdots \\ y_n \end{smallmatrix}\right] \in K^n$ is feasible solution of \ref{dLP} if and only if $\val(s_i y_i + b_i) >=0$ for all $i \in \{1...n\}$ \corentin{préciser les notations}.
-  However, $s_i =0$ for $n-r \leq i\leq n$. Therefore, \ref{dLP} have solution only if the $m-r$ last coefficient of b' are zero.
+  A vector $y =  \left[\begin{smallmatrix} y_1 \\ \vdots \\ y_n \end{smallmatrix}\right] \in K^n$ is feasible solution of \ref{DLP} if and only if $\val(s_i y_i + b_i) >=0$ for all $i = 1...n$ \corentin{préciser les notations}.
+  However, $s_i =0$ for $n-r \leq i\leq n$. Therefore, \ref{DLP} have solution only if the $m-r$ last coefficient of b' have nonnegative valuation.
 
@@
 
-  Finally, let $y^*$ be a feasible solution of \ref{dLP}.
+  Finally, let $y^*$ be a feasible solution of \ref{DLP}.
 Let us suppose there exists $r+1 \leq i \leq m$ such that $c'_i \neq  0$ and fix such $i$.
 Let us then consider the vector $e^i$ whose only non-zero coefficient is the $i-$th, which is $1$.
-Then $y^*+\lambda e^i$ is a feasible solution for all $\lambda \in K$ and $\langle c', y^* + \lambda e^i\rangle = \langle c' , y^* \rangle + \lambda c'_i$.
-In particular, for $\lambda = -\frac{\langle c', y^* \rangle}{c'_i}$ $\val \left( \langle c', y^* + \lambda e ^i \rangle\right) = \val (0) = + \infty$.
-
+Then $y^*+\alpha e^i$ is a feasible solution for all $\alpha \in K$ and $\langle c', y^* + \alpha e^i\rangle = \langle c' , y^* \rangle + \alpha c'_i$.
+In particular, for $\alpha = -\frac{\langle c', y^* \rangle}{c'_i}$, $\val \left( \langle c', y^* + \alpha e ^i \rangle\right) = \val (0) = + \infty$.
 \end{proof}
 
-The two first points of the proposition \ref{prop:reduc} show that we can resolving a linear program is equivalent to resolution the associated \ref{dLP} problem.
-Furthermore, if one considers only the iteration of \ref{dLP} which have solutions.
-By point 3.
-and 4.
-of proposition \ref{prop:reduc} one can reduce the problem by only taking acount only the $r$ first coefficients of $y, b', c'$ and the submatrix of $S$ made with only $r$ first lines et columns of and which coefficients are exactly the nonzero invariants factors.
-The set $Adm$ of the feasible solutions can then be written as the set of vectors $y \in \mathbb{Q}_{ p } ^n$ that verifies $\forall 1 \le i\le r \ s_i y_i + b'_i \in \OK$ i.e.
-that verifies :
+From now on, we will only consider the iterations of \ref{DLP} which have solutions, by \ref{prop:reduc}, we can then reduce the problem by only taking acount only the $r$ first coefficients of $y, b', c'$ and the submatrix of $S$ made with only $r$ first lines et columns of and whose coefficients are exactly the nonzero invariants factors.
+The set $Adm$ of the feasible solutions can then be written as the set of vectors $y \in K^n$ that verifies $ \ s_i y_i + b'_i \in \OK$ for $i=1,...,r$ {\it i.e.} $Adm = \left\{\left[\begin{smallmatrix} y_1\\ \vdots\\ y_n \end{smallmatrix}\right] \in K^n :\ y_i \in -\frac{b`_i}{s_i} + \frac{1}{s_i} \OK, 1\le i\le r\right\}$.
 
-\begin{equation}
-	\forall 1 \le i\le r  \ y_i \in -\frac{b`_i}{s_i} + \frac{1}{s_i} \OK
-\end{equation}
-
-Resolving \ref{dLP} consists in minimizing $\val\left(\left<c',y \right>\right)$ over $Adm$.
-The image of $Adm$ by $y \mapsto \left<c',y \right>$ is $\sum_{i=1}^r -c'_i.\frac{b'_i}{s_i} + \sum_{i=1}^r\left( \frac{c'_i}{s_{i}} \OK \right)$ which can be rewritten in $\left<c',Adm \right> = \lambda + \pi^{v} \OK$ with $\lambda = \sum_{i=1}^r -c'_i.\frac{b'_i}{s_i}$ and $v = \min\limits_{1\le i\le r} \val \frac{c'_{i}}{s_{i}} $.
-
+Resolving \ref{DLP} consists (by definition) in minimizing $y \mapsto \val\left(\left<c',y \right>\right)$ over $Adm$.
+The image of $Adm$ by $y \mapsto \left<c',y \right>$ is $\sum_{i=1}^r -c'_i.\frac{b'_i}{s_i} + \sum_{i=1}^r\left( \frac{c'_i}{s_{i}} \OK \right)$ which can be expressed as $\left<c',Adm \right> = \lambda + \pi^{v} \OK$ with $\lambda = \sum_{i=1}^r -c'_i.\frac{b'_i}{s_i}$ and $v = \min\limits_{1\le i\le r} \val \frac{c'_{i}}{s_{i}} $.
 Finally, two cases can occur depending on $v$ and the valuation of $\lambda$.
-\begin{itemize}
-	\item If $\val( \lambda) < v$ the minimum of $y\mapsto \val\left(\left<c',y \right>\right)$ over $Adm$ is reached in any point of $Adm$ and is equal to $\val\left( \lambda\right)$.
-	\item If $\val\left( \lambda \right) \ge v$ then $\lambda \in \pi^{v} \OK$ and the minimum is $v $ and is reached in any points $y$ of $Adm$ that verifies 
+If $\val( \lambda) < v$ the minimum of $y\mapsto \val\left(\left<c',y \right>\right)$ over $Adm$ is reached in any point of $Adm$ and is equal to $\val\left( \lambda\right)$.
+Whereas, if $\val\left( \lambda \right) \ge v$ then $\lambda \in \pi^{v} \OK$ and the minimum is $v $ and is reached in any points $y$ of $Adm$ that verifies
 	\[\val \underset{ \begin{array}{c} 1\le i\le r\\ \val\left(c'_{i}/{s_{i}} \right) = v  \end{array}}{\sum} y_{i} = 0. \]
 
-\end{itemize}
 \begin{remark}
@@
 \begin{proof}
-  \simone{preuve ?}
+  Both senses of the equivalence will be proven by contraposition.
+
+  Let $M \in \allmat_{d,d}(K)$ with characteristic polynomial $\chi_M = T^d + \sum_{i=0}^{d-1} a_i T^i$ for $a_0,...,a_{d-1} \in K$.
+  Firstly, suppose   $M \not \in \allmat_{d,d}^+(K)$ {\it i.e.} $\chi_M$ have a root $\rho$ of negative valuation.
+  It follows that $\val \chi_M (\rho) = \val \left(\rho^d+ \sum_{i=0}^{d-1} a_i \rho^i \right) = + \infty$ and $\val \rho^d = d \val \rho <0$.
+  The properties of the non-archimedean inequality followed by $\val $ implie that $\val \left( \sum_{i=0}^{d-1} a_i \rho^i\right) = \val \rho^d$ and $\val \left( \sum_{i=0}^{d-1} a_i \rho^i\right) \ge \min \limits_{i=0,..., d-1} \val \left(a_i \rho^i\right)$.
+Therefore, there exists $i \in \left\{0,...,d-1\right\}$ such that $\val( a_i \rho^i) \le \val\rho^d$ {\it i.e.} such that $\val (a_i) \le (d-i) \val \rho <0$.
+That is all the results we need to prove the result.
+
+  We have proven the converse sense of the equivalence.
+To prove the direct sense a brief introduction to Newton's polygon will be needed, we will only state the results we use in this proof and will redirect to \cite{gouvea_p-adic_2003} to further explanations.
+  The Newton polygon $\mathcal{P}$ of a polynomial $P = \sum_{n}^{i=0} a_i T^i \in K[T]$ is defined as the inferior convex hull of the set $\{(i, \val a_i ) | i\in \{0,...,d\} \}$ {\it i.e.} the largest convex function $\mathcal{P} : [0,n] \to \R$ such that $\mathcal{P}(i) \leq \val a_i$ for $i=1,...,n$.
+  This function is piecewise affine and its slopes are exactly the opposites of the valuations of the roots of $P$. These are all the results we will need for this proof.
+
+  Suppose $\chi_M \not\in \OK[T]$.
+There exists $j \in \{0,...,d-1\}$ such that $\val (a_j)<0$.
+The polynomial $\chi_M$ being monic the point with abscissa $n$ of $\chi_M$'s Newton's Polygon is $(n,0)$.
+  Therefore, the point $(j, \val a_j)$ having negative ordinate implies that at least one of the slopes of $\chi_M$'s Newton's Polygon is positive so that $\chi_M$ has a root with negative valuation.
 \end{proof}
@@
   The reverse inclusion of \Cref{cor_caracsdp} is false in general. For instance the characteristic polynomial of
-  $M = (\begin{smallmatrix} 5 + {3}/{5} & {4}/{5} \\ {4}/{5} & -{3}/{5} \end{smallmatrix})$ is $\chi_M = T^2-5T-4$.
+  $M = \left(\begin{smallmatrix} 5 + {3}/{5} & {4}/{5} \\ {4}/{5} & -{3}/{5} \end{smallmatrix}\right)$ is $\chi_M = T^2-5T-4$.
 However when seen as a matrix over $K=\mathbb{Q}_5$, then $\chi_M \in \mathbb{Z}_5[T] = \OK[T]$: then $M \in \allmat_{2,2}^+(\mathbb{Q}_5)$, nevertheless $M \not\in \allmat_{2,2}(\mathbb{Z}_5)$, hence $\allmat_{2,2}^+(\mathbb{Q}_5) \not\subset \allmat_{2,2}(\mathbb{Z}_5)$.
@@
 \begin{proof}
-Firstly, $\OK[X]$ is closed and open in $\mathbb{Q}_{p}[X]$ (\simone{attention p-adique}) equipped with the infinitiy norm $\|\cdot\|_\infty : P = \sum_{k=1}^{n} a_k X^k \to \sup |a_k|_p$ \simone{attention p-adique}.
-$\OK$ is indeed the open unit ball for $\|\cdot \|_\infty$ which defines a discrete distance for which open balls are also closed.
-Furthermore, $\allmat^+_{d,d}(K) = \chi^{-1}(\OK[X]) $ where $\chi$ is the function that maps its characteristic polynomial to a matrix which is continuous.
-\simone{mmm je dirais plutôt ``the function that maps a matrix to its characteristic polynomial'', n'est-ce pas ?}
+Firstly, $\OK[X]$ is closed and open in $K[X]$ equipped with the infinitiy norm $\|\cdot\|_\infty : P = \sum_{k=1}^{n} a_k X^k \to \sup |a_k|$.
+$\OK$ is indeed the open unit ball for $\|\cdot \|_\infty$ that induces a discrete distance for which open balls are also closed sets.
+Furthermore, $\allmat^+_{d,d}(K) = \chi^{-1}(\OK[X]) $ where $\chi$ is the function that maps a matrix to its characteristic polynomial which is continuous.
 \end{proof}
@@
   bon, on est sur un corps abstrait.}
+
+\begin{definition}
+  A \emph{cone} is subset $C$ of $K^d$ that is closed under multiplication by elements of $\OK$.   
+\end{definition}
+
+\begin{remark}
+  \corentin{Pas nécessairement très important, à voir}
+  If $C$ is a cone that is furthermore closed under addition (what shall be called a convex cone in the real case) then $C$ is a $\OK$-module.
+\end{remark}
+
+\begin{proposition}
+  The set $\allmat^+_{d,d}(K)$ is a cone.
+\end{proposition}
+\begin{proof}
+  The result is immediate following the definiton of $\allmat^+_{d,d}(K)$.
+\end{proof}
 
@@
 
+\corentin{ Une autre définition qu'il pourrait être intéressant d'explorer. Attention! Pas les mêmes propriétés.}
+\begin{definition}[Alternative definition]
+  Let $A_0, ..., A_n, B_0, ..., B_n \in M_{d,d}(K)$. 
+  We denote as $S^+_A$ the set $S_{A}^+ = \left\{ x \in K^n : A_0 + x_1 A_1+ ...+x_nA_n \succeq 0  \right\}$ and $S^-_B$ denotes the set $S^-_B = \left\{ x \in K^n : B_0 + x_1 B_1+ ...+x_nB_n \preceq 0\right\}$.
+  The set $S_A,B := S_A^+ \cup S_B^-$ is called a \emph{spectrahedron}.
+\end{definition}
+
 \subsection{Annuli (couronnes)}
@@
 Let $A$ be the annuli defined by $a<b \in R^*_+$.
+We consider for all $x,y \in K $ the spectrahedron $\mathcal{S}= \left\{(x,y) \in K  : M(x,y) := \pi^ax \oplus \pi^{-b}y \oplus \begin{bmatrix} \pi^{-1} & -\pi^{-1}x \\ \pi^{-1}y & - \pi^{-1}  \\ \end{bmatrix} \succeq 0\right\}$.
 
-We consider for all $x,y \in K $ the matrix  $$M(x,y) :=
-\begin{pmatrix} 
-	p^ax & 0 & 0 & 0 \\
-	0 & p^{-b}y & 0 & 0 \\
-	0 & 0 & p^{-1} & p^{-1}x \\
-	0 & 0 & p^{-1}y & - p^{-1}  \\
-\end{pmatrix} $$ and the associated spectrahedron $\mathcal{S}= \{(x,y) \in K  : M(x,y) \succeq 0\} $
+We will show that $x \in A$ if and only if  there exists $y\in K$ such that $(x,y) \in \mathcal{S}$.
 
-Let us show that $x \in C$ if and only if  $\exists y \in K(x,y) \in \mathcal{S}$.
+Let $x,y \in K$. By \ref{caracsdp}, $M(x,y)$ is positive semidefinite if and only if $(x,y)$ is a solution of \ref{eq:annulussyst}.
 
-Let $x,y$ be two $p$-adic numbers.
-$M(x,y)$ can be decomposed in three blocks : $p^ax$, $p^{-b}y $ and $M'(x,y) = \begin{pmatrix} p^{-1} & p^{-1}x \\ p^{-1} y & p^{-1}\end{pmatrix} $.
-Using \ref{caracsdp} we know that $M(x,y)$ is positive semidefinfite if and only if
-$
+\begin{equation}
+  \label[type]{eq:annulussyst}
 \begin{cases}
-  p^ax \ge 0 \\
-  p^{-b}y \ge 0\\
-  \text{Tr}M'\left( x,y \right) = 0 \ge 0\\
-  \text{det} M'(x,y ) = p^{-2}\left( xy-1 \right)  \ge 0 
+  \val(\pi^ax) \ge 0 \\
+  \val(\pi^{-b}y) \ge 0\\
+  \val(\pi^{-1}- \pi^{-1}) = +\infty \ge 0\\
+  \val(\pi^{-2}\left( xy-1 \right))  \ge 0 
 \end{cases}
-$ 
-that is if and only if 
-\begin{equation}
-	\label{eq:caracsdp} 
+\iff	
 \begin{cases} 
@@
 		\val\left(y\right)\ge -b\\
-		p^{-2} \left( xy-1 \right) \ge 0
+		\val\left( xy-1 \right) \ge 2
 	\end{cases}
@@
 
-Therefore $x \in C$ if and only if there exists $y \in K $ so that $(x, y)$ verifies \ref{eq:caracsdp}.
-Si $x, y$ verifies indeed \ref{caracsdp} then $\val\left(x\right)\ge a$, $\val\left(y\right)\ge -b$ and $p^{-2} \left( xy-1 \right) \ge 0$ implies that $\val\left(x\right)+\val\left(y\right)=\val\left(xy\right) = \val\left(-1\right) =0$ and therefore that $\val\left(x\right)=-\val\left(y\right)\le -(-b)  =b$, so $x \in $.
-Reciprocally if $x \in C$ then $(x,x^{-1}) $ verifies \ref{eq:caracsdp}  .
+Therefore, if $(x, y)$ verifies \ref{eq:annulussyst} then $\val\left(x\right)\ge a$, $\val\left(y\right)\ge -b$ and $ \left( xy-1 \right) \ge 2$.
+The last inequality implies that $\val\left(x\right)+\val\left(y\right)=\val\left(xy\right) = \val\left(-1\right) =0$ and therefore that $\val\left(x\right)=-\val\left(y\right)\le -(-b)  =b$, so $x \in C$.
+
+Reciprocally if $x \in C$ then $(x,x^{-1}) $ is a solution of \ref{eq:annulussyst} .
 \end{proof}

### 2024-02-01 article/paper_padic_spec.tex
ajout definition semialgebrique

@@
 
-The last proposition allows to only consider the resolution of the \ref{DLP} problem.
+The last proposition allows us to consider only the case of the \ref{DLP} problem to solve \ref{LP}.
 \begin{proposition}\label{prop:reduc}
-
-	We have then the following results
 		\begin{enumerate}
-
-		\item \ref{DLP} have feasible solutions if and only if the $m-r$ last coefficients of $b'$ have nonegative valuation, with $r$ the rank of $S$.
+		\item \ref{DLP} have feasible solutions if and only if the $m-r$ last coefficients of $b'$ have nonegative valuation, for $r$ the rank of $S$.
 		\item If at least one of the $n-r$ last coefficients of $c'$ is non-zero, if \ref{DLP} admits feasible solutions it is unbounded and does not have a solution.
@@
   Firstly, suppose   $M \not \in \allmat_{d,d}^+(K)$ {\it i.e.} $\chi_M$ have a root $\rho$ of negative valuation.
-  It follows that $\val \chi_M (\rho) = \val \left(\rho^d+ \sum_{i=0}^{d-1} a_i \rho^i \right) = + \infty$ and $\val \rho^d = d \val \rho <0$.
-  The properties of the non-archimedean inequality followed by $\val $ implie that $\val \left( \sum_{i=0}^{d-1} a_i \rho^i\right) = \val \rho^d$ and $\val \left( \sum_{i=0}^{d-1} a_i \rho^i\right) \ge \min \limits_{i=0,..., d-1} \val \left(a_i \rho^i\right)$.
+  It follows that $\val \chi_M (\rho) = \val (\rho^d+ \sum_{i=0}^{d-1} a_i \rho^i ) = + \infty$ and $\val \rho^d = d \val \rho <0$.
+  The properties of the non-archimedean inequality followed by $\val $ implie that $\val ( \sum_{i=0}^{d-1} a_i \rho^i) = \val \rho^d$ and $\val ( \sum_{i=0}^{d-1} a_i \rho^i) \ge \min_{i=0,..., d-1} \val \left(a_i \rho^i\right)$.
 Therefore, there exists $i \in \left\{0,...,d-1\right\}$ such that $\val( a_i \rho^i) \le \val\rho^d$ {\it i.e.} such that $\val (a_i) \le (d-i) \val \rho <0$.
@@
 \end{proof}
-
-\simone{que peut-on dire de plus de l'ensemble $\allmat_{d,d}^+(K)$ ? normalement c'est un cône non ? peut être
-  à cause de \Cref{caracsdp} c'est un $\OK$-cône mais pas un $K$-cône ? ça serait un peu contre-intuitif, mais
-  bon, on est sur un corps abstrait.}
 
@@
 
+\begin{definition}
+  A subset $S$ of $K^n$ is said \emph{semialgebraic} if it is defined by finite unions and intersections of sets defined by polynomial equalities of the form $\{ x \in K^n  : P( x) = 0 \}$ and of sets defined by polynomial inequalities of the form $\{ x\in K^n : \val P(x) \geq 0 \}$.
+\end{definition}
+
+\begin{proposition}
+  Spectrahedra are semialgebraic sets. 
+\end{proposition}
+
+\begin{proof}
+  Let $S$ be spectrahedron and $A$ a linear matrix such that $S={x \in K^n : A(x) \succeq 0}$. 
+  We denote as $p_i(x)$ the $i$-th coefficient of $\chi_{M(x)}$. The map $p_i	: x \to p_i(x)$ is polynomial and $x \in S$ if and only if $\val(p_i(x)) \geq 0$ for $i=0,...,d$.
+
+  Finally, by \ref{caracsdp}, $S = \{x \in K^n : \chi_{M(x)} \in \OK(T)\} = \bigcap\limits_{i=0}^d \{x \in K^n : \val(p_i(x)) \geq 0\}$.
+\end{proof}
+
 \corentin{ Une autre définition qu'il pourrait être intéressant d'explorer. Attention! Pas les mêmes propriétés.}
@@
 \begin{proof}
-Let $A$ be the annuli defined by $a<b \in R^*_+$.
+Let $A$ be the annulus defined by $a<b \in \R^*_+$.
 We consider for all $x,y \in K $ the spectrahedron $\mathcal{S}= \left\{(x,y) \in K  : M(x,y) := \pi^ax \oplus \pi^{-b}y \oplus \begin{bmatrix} \pi^{-1} & -\pi^{-1}x \\ \pi^{-1}y & - \pi^{-1}  \\ \end{bmatrix} \succeq 0\right\}$.
@@
 The last inequality implies that $\val\left(x\right)+\val\left(y\right)=\val\left(xy\right) = \val\left(-1\right) =0$ and therefore that $\val\left(x\right)=-\val\left(y\right)\le -(-b)  =b$, so $x \in C$.
-
 Reciprocally if $x \in C$ then $(x,x^{-1}) $ is a solution of \ref{eq:annulussyst} .

### 2024-02-15 article/paper_padic_spec.tex
proj poly in section poly

@@
 \newcommand{\OK}{\mathcal{O}_K}
+\def\diag{\mathrm{diag}}
 
@@
 
+\newpage
 \section{Preliminaries}
@@
 with coefficients in $K$ is denoted by $K[x]_{d}$. The vector space of matrices of
-size $p \times q$ with entries in $K$ is denoted by $\allmat_{p,q}(K)$. For the sake
+size $p \times q$ with entries in $K$ is $\allmat_{p,q}(K)$ and the general
+linear group in $\allmat_{n,n}(K)$ is $\GL_n(K)$.
+For the sake
 of ease of writing, block-diagonal matrices with blocks $B_1,\ldots,B_d$ are denoted by
-$B_1 \oplus \cdots \oplus B_d$.
+$\diag(B_1, \ldots, B_d)$.
+
+We recall the definition of Smith Normal Form, in our context.
+\begin{definition}[Smith Normal Form]\label{smith_nf}
+  Let $M \in \allmat_{m,n}(K)$ be of rank $r$. There exist unique integers $a_1 \leq \cdots \leq a_r$, and
+  matrices $P \in \GL_n(\OK)$ and $Q \in \GL_m(\OK)$, such that
+  $$
+  S := QMP^{-1} = \diag(\pi^{a_1}, \pi^{a_2}, \ldots, \pi^{a_r}, {\bf 0}_{\min(m,n)-r})
+  $$
+  where ${\bf 0}_{\min(m,n)-r}$ is a null square matrix of size $\min(m,n)-r$.
+  The matrix $S$ is called the \emph{Smith Normal Form (SNF)} of $M$, and the elements $\pi^{a_i}$ the
+  \emph{invariant factors}.
+\end{definition}
+\begin{remark}
+  The valuation of the first invariant factor of the SNF of a matrix
+  $M \in \allmat_{n,n}(K)$ is the minimum of the valuations of the entries of
+  $M$. In particular, the SNF of $M \in \allmat_{n,n}(\OK)$ has entries in $\OK$.
+\end{remark}
 
@@
   $$
-  P = \{x \in K^n : \val(\ell_1 \oplus \cdots \oplus \ell_d) \geq 0 \text{ and }
-  \val(m_1 \oplus \cdots \oplus m_e) = +\infty\},
+  P = \{x \in K^n : \val(\ell_i(x)) \geq 0, i=1,\ldots,d \text{ and }
+  \val(m_j(x)) = +\infty, j=1,\ldots,e\},
   $$
-  for some $\ell_1,\ldots,\ell_d,m_1,\ldots,m_e \in K[x]_1$, where $\val,\geq$ and $=$ are applied entrywise.
-  We assume without loss of generality that for every $i=1,\ldots,d$ there exists $x \in P$ such that
-  $\val(\ell_i(x))<+\infty$.
+  for some $\ell_1,\ldots,\ell_d,m_1,\ldots,m_e \in K[x]_1$.
 \end{definition}
 
-We recall that that the smallest affine space of $K^n$ containing a set $S \subset K^n$ is called its
-\emph{affine hull} and denoted $\aff{S}$.
-The assumption on forms $\ell_i$ in \Cref{def_polyhedra} implies that the constraint
-$\val(m_1 \oplus \cdots \oplus m_e) = +\infty$ defines exactly the affine hull of $P$, in other words
-$\aff{P} = \{x \in K^n : m_j(x) = 0,
-j=1,\ldots,e\}$ \simone{(il nous faudrait une preuve, du genre: $\val(m(x))=+\infty$ pour tout $x \in P$ si et seulement si $m$ est une combinaison affine de $m_1,\ldots,m_e$.)}
-%The \emph{dimension} of $P$ is defined as the dimension of $\aff{P}$ (for $e=0$, $\aff{P}=K^n$ and $P$ has dimension $n$).
+%%We recall that that the smallest affine space of $K^n$ containing a set $S \subset K^n$ is called its \emph{affine hull} and denoted $\aff{S}$.
+The assumption on forms $\ell_i$ in \Cref{def_polyhedra} implies that the constraint $\val(m_1 \oplus \cdots \oplus m_e) = +\infty$ defines exactly the affine hull of $P$, in other words $\aff{P} = \{x \in K^n : m_j(x) = 0, j=1,\ldots,e\}$ \simone{(il nous faudrait une preuve, du genre: $\val(m(x))=+\infty$ pour tout $x \in P$ si et seulement si $m$ est une combinaison affine de $m_1,\ldots,m_e$.)}
+%%The \emph{dimension} of $P$ is defined as the dimension of $\aff{P}$ (for $e=0$, $\aff{P}=K^n$ and $P$ has dimension $n$).
 The \emph{relative interior} of $P$ is defined as $\relint{P} = \{x \in P : \val(\ell_1 \oplus \cdots \oplus \ell_d) < +\infty\}$ (\simone{pas clair si besoin de dimension et relint}).
 Remark that \Cref{def_polyhedra} includes the case $d=0$ corresponding to affine spaces, as in the real case.
-Moreover by definition the class of polyhedra is closed under intersection.
+Moreover by definition the class of polyhedra is closed under intersection. Without loss of generality, one may
+assume in \Cref{def_polyhedra} that for every $i=1,\ldots,d$ there exists $x \in P$ such that
+$\val(\ell_i(x))<+\infty$.
 
@@
   In other words, $\OK^n$ is the polyhedron in $K^n$ defined by the affine polynomials
-  $\ell_i(x)=x_i$, $i=1,\ldots, n$, and $e=0$ (its affine hull is indeed the whole $K^n$).
+  $\ell_i(x)=x_i$, $i=1,\ldots, n$, and $e=0$. %%%%%(its affine hull is indeed the whole $K^n$).
 \end{example}
+
+\subsection{Projections of polyhedra}
+
+\begin{proposition}
+Let $\PP \subset K^n$ be a polyhedron and $f: K^n \rightarrow K^m$
+be a linear mapping. Then $f(\PP)$ is a polyhedron.
+\end{proposition}
+\begin{proof}
+Let us assume that 
+$\PP = \left\lbrace x \in K^n : \val (l_i (x) ) \geq 0, \textrm{ for } i \in I \right\rbrace$ for some
+finite set $I \subset \N$ and $l_i \in K[x]_1$, for $i \in I.$ We further assume that $\PP \neq \emptyset$.
+
+Thanks to the Smith Normal Form (see Definition \ref{smith_nf}), $f$
+can be written $f=Q^{-1} \Delta P$
+with $P \in \GL_n(\OK),$ $Q \in \GL_m(\OK)$
+and $\Delta \in \allmat_{n,m}(K)$ of the form $\lambda_1 \oplus \cdots \oplus \lambda_r \oplus {\bf 0}_{\min(m,n)-r}$
+  where ${\bf 0}_{\min(m,n)-r}$ is a null square matrix of size $\min(m,n)-r$ for $\lambda_1,\dots,\lambda_r$ non-zero and $r \in \N.$
+
+We first prove the result when $f$ is in $\GL_n(\OK)$.
+In that case, $x \in f(P)$ if and only if for all
+$i \in I,$
+$\val (l_i (f^{-1}(x)) \geq 0$.
+The $l_i \circ f^{-1}$ are clearly in $K[x]_1$
+and $f(P)$ is a polyhedron.
+
+Similarly, if $f$ is of the form $K^n \rightarrow K^n$,
+$(x_1,\dots,x_n) \mapsto (\lambda_1 x_1,\dots,\lambda_n x_n)$
+for some $\lambda_i$'s in $K$,
+then it is clear that $f(P)$
+can be defined by $\val (\widetilde{l_i}(x)) \geq 0$, $i \in I$
+with the $\widetilde{l_i}$'s obtained from the $l_i$'s by an
+obvious change of variables.
+
+Now, we turn our attention to the $\Delta$ part of $f.$
+We first assume that $f$ is a projection 
+of the form $K^n \rightarrow K^{n+1},$
+$(x_1,\dots,x_{n-1},x_n)\mapsto (x_1,\dots,x_{n-1}).$
+
+Let us write the conditions defining $\PP$
+in matrix form:
+$\val(A X+B) \geq 0$
+with $A \in M_{q,n}(K)$, $B \in K^q$
+and $X=(x_1,\dots,x_n)^\intercal.$
+
+We can compute a Smith Normal Form
+of the $q \times (n-1)$ matrix defined by the 
+$n-1$ first columns of $A$
+to obtain a decomposition of the form:
+\[ Q_A A P_A^{-1} = \begin{bmatrix}
+\delta_1	& 		& 			&   &		 &  &a_1	\\
+			& \ddots& 			& 0	&		 &	&		\\
+			&		& \delta_l  &   & 		 &	&		\\
+			&		&			&0  & 		 &	& 		\\
+			&		&			&   & \ddots &	&		\\
+			&		&			&	&		 & 0&a_{n-1} \\
+			&		&			&	&		 &	&a_n 	\\
+			&		&			&	&		 &	&    	\\
+			&		&			&	&		 &	&a_q 	\\			
+\end{bmatrix},\]
+with $Q_A \in \GL_q(\OK)$ and $P_A \in \GL_n(\OK)$ such that $P_A(e_n)=e_n.$
+
+Multiplying on the left by $Q_A^{\pm 1}$ does not
+modify whether the valuation inequalities are satisfied.
+Moreover, thanks to our previous on the case when $f$ is an automorphism,
+$\PP$ can be written
+$\PP=P_A^{-1}(\PP_2)$ for some polyhedron $\PP_2 \in K^n$
+and we are reduced to proving that
+$f(\PP_2)$ is polyhedron for $f$ still the canonical projection
+$K^n \rightarrow K^{n-1}$ and $\PP_2$
+defined by the linear matrix inequality (for some $B_2 \in K^q$):
+\[  \begin{bmatrix}
+\delta_1	& 		& 			&   &		 &  &a_1	\\
+			& \ddots& 			& 0	&		 &	&		\\
+			&		& \delta_l  &   & 		 &	& \vdots\\
+			&		&			&0  & 		 &	& 		\\
+			&		&			&   & \ddots &	&		\\
+			&		&			&	&		 & 0&a_{n-1} \\
+			&		&			&	&		 &	&a_n 	\\
+			&		&			&	&		 &	& \vdots   	\\
+			&		&			&	&		 &	&a_q 	\\			
+\end{bmatrix} \begin{bmatrix} x_1 \\ \\ \\ \\ \\ \vdots \\ \\ \\ \\ x_n \\ \end{bmatrix} + B_2 \geq 0.\]
+
+We remark that 
+$a_s x_n + b_s \geq 0$
+if and only if $x_n = -a_s^{-1} b_s + O(\pi^{- \val(a_s)}).$
+This exactly corresponds to $x_n \in B(-a_s^{-1} b_s, 2^{\val(a_s)}).$
+Since the conditions have to be compatible (we have assumed
+$\PP$ not empty), and thanks to ultrametricity,  
+the intersection of these conditions for 
+$s \in \llbracket l+1,q \rrbracket$
+is then given by the smallest of these balls.
+Let us assume it is the one defined for $l=n.$
+The only condition on $x_n$
+is then $\val(a_nx_n +b_n) \geq 0.$
+
+Thanks to the above discussion on diagonal mapping,
+we can further assume that the $\delta_i$'s and $a_n$ are all $1$'s
+and are reduce to $\PP_2$ defined by the linear matrix inequality :
+\[  \begin{bmatrix}
+1	& 		& 			&   &		 &  &a_1	\\
+			& \ddots& 			& 0	&		 &	&		\\
+			&		& 1  &   & 		 &	& \\
+			&		&			&0  & 		 &	& 	\vdots	\\
+			&		&			&   & \ddots &	&		\\
+			&		&			&	&		 & 0&a_{n-1} \\
+			&		&			&	&		 &	&1 	\\
+
+\end{bmatrix} \begin{bmatrix} x_1 \\ \\  \\ \\ \vdots \\  \\ \\ x_n \\ \end{bmatrix} + \begin{bmatrix} b_1 \\ \\ \\  \\ \vdots  \\ \\ \\ b_n \\ \end{bmatrix}  \geq 0.\]
+Finally, we can also assume that, up to a permutation of the variables, $\val(a_1)= \min_{i=1}^{n-1} \val(a_i).$
+We distinguish two cases: $\val(a_1) \geq 0$ and $\val(a_1)<0.$
+
+Let us first assume that $\val(a_1) \geq 0$
+
+Let $x \in \PP_2$.
+Then $x_n=-b_n+O(1)$
+and $x_1+a_1 x_n+b_1=O(1).$
+Consequently, $x_1-a_1 b_n +b_1=O(1)+O(\pi^{\val(a_1)})=O(1).$
+Similarly, for all $i \in \llbracket 2,n-1 \rrbracket,$
+$x_i-a_ib_n+b_i=O(1)+O(\pi^{\val(a_i)})=O(1).$
+
+We define the polyhedron $\Qc \subset K^{n-1}$ by the following inequalities:
+ for all $i \in \llbracket 1,n-1 \rrbracket,$
+$\val(x_i-a_ib_n+b_i) \geq 0.$
+
+Then the previous computations prove that $f(\PP_2)\subset \Qc.$
+Conversely, let $(x_1,\dots,x_{n-1}) \in \Qc.$
+Then let $x_n := -b_n.$
+
+We check that for $i \in \llbracket 1,n-1 \rrbracket,$
+$x_i+a_ix_n+b_i=x_i-a_ib_n+b_i=O(1),$
+and $x_n+b_n=O(1)$. Hence $(x_1,\dots,x_n) \in \PP_2$
+which means that $(x_1,\dots,x_{n-1}) \in f(\PP_2).$
+Thus $f(\PP_2)= \Qc$ and $f(\PP_2)$ is a polyhedron.
+
+We now deal with the second case, with $\val(a_1)<0.$
+Let $x \in \PP_2$.
+Then $x_n=-b_n+O(1)$
+and $x_1+a_1 x_n+b_1=O(1).$
+Consequently, $x_1-a_1 b_n +b_1=O(1)+O(\pi^{\val(a_1)})=O(\pi^{\val(a_1)})).$
+Thus $a_1^{-1}x_1- b_n +a_1^{-1}b_1=O(1)$.
+%and $x_n=-a_1^{-1}(x_1+b_1)+O(1).$
+In addition, $x_n=-a_1^{-1}(x_1+b_1)+O(\pi^{-\val(a_1)}).$
+We plug this equality in 
+$x_i+a_i x_n+b_i=O(1)$ to get
+$x_i-a_1^{-1}a_i(x_1+b_1)+b_i=O(1)+O(\pi^{\val(a_i)-\val(a_1)})=O(1)$
+using that $\val(a_i) \geq \val (a_1).$
+
+We define the polyhedron $\Qc \subset K^{n-1}$ by the following inequalities:
+$\val(a_1^{-1}x_1- b_n +a_1^{-1}b_1) \geq 0$ and for all $i \in \llbracket 2,n-1 \rrbracket,$
+$\val(x_i-a_1^{-1}a_i(x_1+b_1)+b_i) \geq 0.$
+
+Then the previous computations prove that $f(\PP_2)\subset \Qc.$
+Conversely, let $(x_1,\dots,x_{n-1}) \in \Qc.$
+Let $x_n := -a_1^{-1}(x_1+b_1).$
+Then
+$x_1+a_1 x_n+b_1=0=O(1).$
+Let $i \in \llbracket 2,n-1 \rrbracket,$
+then $x_i+a_i x_n+b_i=x_i-a_1^{-1}a_i(x_1+b_1)+b_i=O(1)$
+since $(x_1,\dots,x_{n-1}) \in \Qc.$
+Finally, 
+$x_n+b_n=-a_1^{-1}(x_1+b_1)+b_n=O(1)$ thanks to the inequality satisfied by $x_1.$
+Hence $(x_1,\dots,x_n) \in \PP_2$
+which means that $(x_1,\dots,x_{n-1}) \in f(\PP_2).$
+Thus $f(\PP_2)= \Qc$ and $f(\PP_2)$ is a polyhedron,
+and it has been proved in both cases.
+
+Therefore, if $f$ is the projection 
+$(x_1,\dots,x_{n-1},x_n)\mapsto (x_1,\dots,x_{n-1})$ 
+and $\PP$ is a polyhedron in $K^n$,
+then $f(\PP)$ is a polyhedron.
+
+\tristan{Attention, à partir de maintenant,
+il faut ajouter à la définition qu'on peut
+fixer des points!
+Cela revient à ajouter des conditions
+$\val = + \infty.$}
+
+It is also clear that
+if $f$ is the immersion 
+$K^l \rightarrow K^n$
+$(x_1,\dots,x_l)\mapsto (x_1,\dots,x_l,0,\dots,0)$ 
+and $\PP$ is a polyhedron in $K^n$,
+then $f(\PP)$ is a polyhedron.
+
+We now prove that for
+$\Delta$ a Smith Normal Form
+and $\PP$ a polyhedron,
+$\Delta(\PP)$ is a polyhedron.
+Then $\Delta$ is the composition
+of the immersion 
+$K^l \rightarrow K^n$
+$(x_1,\dots,x_l)\mapsto (x_1,\dots,x_l,0,\dots,0),$ 
+ the diagonal invertible mapping
+$K^l \rightarrow K^l$,
+$(x_1,\dots,x_l)\mapsto (\delta_1,\dots,\delta_l x_l)$,
+and the projections
+$(x_1,\dots,x_{l+1})\mapsto (x_1,\dots,x_{l}),$
+ $(x_1,\dots,x_{l+2})\mapsto (x_1,\dots,x_{l+1}),$
+ $\dots,$
+ $(x_1,\dots,x_{n})\mapsto (x_1,\dots,x_{n-1}).$
+ Thus $\Delta(\PP)$ is a polyhedron thanks to the previous 
+ results on image of polyhedron.
+
+Finally, if $f: K^n \rightarrow K^m$
+is a linear mapping and
+$f=Q^{-1} \Delta P$ is its Smith Normal Form
+with $P \in \GL_n(\OK),$ $Q \in \GL_m(\OK)$
+and $\Delta \in \allmat_{n,m}(K)$,
+then
+$P(\PP)$ is a polyhedron,
+$\Delta (P(\PP))$ also,
+and finally $f(\PP)=Q^{-1} (\Delta (P(\PP)))$
+is a polyhedron.
+This concludes the proof.
+\end{proof}
+
+\subsection{Linear programming}
 
@@
 and $\left\langle c, x \right\rangle := c_1x_1+\cdots +c_nx_n$.
+
 We present an algorithm for solving \eqref{LP} which consists in reducing the matrix $A$ in Smith normal form.
-We recall its definition below, in our context.
-
-\begin{definition}[Smith Normal Form]\label{smith_nf} \simone{Je trouve que la SNF devrait être inclue dans les
-  préliminaires, car on l'utilise ailleurs, et laisser cette section pour polyèdre+LP}
-  Let $M \in \allmat_{m,n}(K)$ be of rank $r$. There exist unique integers $a_1 \leq \cdots \leq a_r$, and
-  matrices $P \in \GL_n(\OK)$ and $Q \in \GL_m(\OK)$, such that
-  $$
-  S := QMP^{-1} = \pi^{a_1} \oplus \pi^{a_2} \oplus \cdots \oplus \pi^{a_r} \oplus {\bf 0}_{\min(m,n)-r}
-  $$
-  where ${\bf 0}_{\min(m,n)-r}$ is a null square matrix of size $\min(m,n)-r$.
-  The matrix $S$ is called the \emph{Smith Normal Form (SNF)} of $M$, and the elements $\pi^{a_i}$ the
-  \emph{invariant factors}.
-\end{definition}
-\begin{remark}
-  The valuation of the first invariant factor of the SNF of a matrix
-  $M \in \allmat_{n,n}(K)$ is the minimum of the valuations of the entries of
-  $M$. In particular, the SNF of $M \in \allmat_n(\OK)$ has entries in $\OK$.
-\end{remark}
-
 The most interesting aspect in the SNF regarding the resolution of \ref{LP} is that the transition matrices are invertible in $\OK$.
@@
 
-\begin{proposition}
-Let $\PP \subset K^n$ be a polyhedron and $f: K^n \rightarrow K^m$
-be a linear mapping. Then $f(\PP)$ is a polyhedron.
-\end{proposition}
-\begin{proof}
-Let us assume that 
-$\PP = \left\lbrace x \in K^n : \val (l_i (x) ) \geq 0, \textrm{ for } i \in I \right\rbrace$ for some
-finite set $I \subset \N$ and $l_i \in K[x]_1$, for $i \in I.$ We further assume that $\PP \neq \emptyset$.
-
-Thanks to the Smith Normal Form (see Definition \ref{smith_nf}), $f$
-can be written $f=Q^{-1} \Delta P$
-with $P \in \GL_n(\OK),$ $Q \in \GL_m(\OK)$
-and $\Delta \in \allmat_{n,m}(K)$ of the form $\lambda_1 \oplus \cdots \oplus \lambda_r \oplus {\bf 0}_{\min(m,n)-r}$
-  where ${\bf 0}_{\min(m,n)-r}$ is a null square matrix of size $\min(m,n)-r$ for $\lambda_1,\dots,\lambda_r$ non-zero and $r \in \N.$
-
-We first prove the result when $f$ is in $\GL_n(\OK)$.
-In that case, $x \in f(P)$ if and only if for all
-$i \in I,$
-$\val (l_i (f^{-1}(x)) \geq 0$.
-The $l_i \circ f^{-1}$ are clearly in $K[x]_1$
-and $f(P)$ is a polyhedron.
-
-Similarly, if $f$ is of the form $K^n \rightarrow K^n$,
-$(x_1,\dots,x_n) \mapsto (\lambda_1 x_1,\dots,\lambda_n x_n)$
-for some $\lambda_i$'s in $K$,
-then it is clear that $f(P)$
-can be defined by $\val (\widetilde{l_i}(x)) \geq 0$, $i \in I$
-with the $\widetilde{l_i}$'s obtained from the $l_i$'s by an
-obvious change of variables.
-
-Now, we turn our attention to the $\Delta$ part of $f.$
-We first assume that $f$ is a projection 
-of the form $K^n \rightarrow K^{n+1},$
-$(x_1,\dots,x_{n-1},x_n)\mapsto (x_1,\dots,x_{n-1}).$
-
-Let us write the conditions defining $\PP$
-in matrix form:
-$\val(A X+B) \geq 0$
-with $A \in M_{q,n}(K)$, $B \in K^q$
-and $X=(x_1,\dots,x_n)^\intercal.$
-
-We can compute a Smith Normal Form
-of the $q \times (n-1)$ matrix defined by the 
-$n-1$ first columns of $A$
-to obtain a decomposition of the form:
-\[ Q_A A P_A^{-1} = \begin{bmatrix}
-\delta_1	& 		& 			&   &		 &  &a_1	\\
-			& \ddots& 			& 0	&		 &	&		\\
-			&		& \delta_l  &   & 		 &	&		\\
-			&		&			&0  & 		 &	& 		\\
-			&		&			&   & \ddots &	&		\\
-			&		&			&	&		 & 0&a_{n-1} \\
-			&		&			&	&		 &	&a_n 	\\
-			&		&			&	&		 &	&    	\\
-			&		&			&	&		 &	&a_q 	\\			
-\end{bmatrix},\]
-with $Q_A \in \GL_q(\OK)$ and $P_A \in \GL_n(\OK)$ such that $P_A(e_n)=e_n.$
-
-Multiplying on the left by $Q_A^{\pm 1}$ does not
-modify whether the valuation inequalities are satisfied.
-Moreover, thanks to our previous on the case when $f$ is an automorphism,
-$\PP$ can be written
-$\PP=P_A^{-1}(\PP_2)$ for some polyhedron $\PP_2 \in K^n$
-and we are reduced to proving that
-$f(\PP_2)$ is polyhedron for $f$ still the canonical projection
-$K^n \rightarrow K^{n-1}$ and $\PP_2$
-defined by the linear matrix inequality (for some $B_2 \in K^q$):
-\[  \begin{bmatrix}
-\delta_1	& 		& 			&   &		 &  &a_1	\\
-			& \ddots& 			& 0	&		 &	&		\\
-			&		& \delta_l  &   & 		 &	& \vdots\\
-			&		&			&0  & 		 &	& 		\\
-			&		&			&   & \ddots &	&		\\
-			&		&			&	&		 & 0&a_{n-1} \\
-			&		&			&	&		 &	&a_n 	\\
-			&		&			&	&		 &	& \vdots   	\\
-			&		&			&	&		 &	&a_q 	\\			
-\end{bmatrix} \begin{bmatrix} x_1 \\ \\ \\ \\ \\ \vdots \\ \\ \\ \\ x_n \\ \end{bmatrix} + B_2 \geq 0.\]
-
-We remark that 
-$a_s x_n + b_s \geq 0$
-if and only if $x_n = -a_s^{-1} b_s + O(\pi^{- \val(a_s)}).$
-This exactly corresponds to $x_n \in B(-a_s^{-1} b_s, 2^{\val(a_s)}).$
-Since the conditions have to be compatible (we have assumed
-$\PP$ not empty), and thanks to ultrametricity,  
-the intersection of these conditions for 
-$s \in \llbracket l+1,q \rrbracket$
-is then given by the smallest of these balls.
-Let us assume it is the one defined for $l=n.$
-The only condition on $x_n$
-is then $\val(a_nx_n +b_n) \geq 0.$
-
-Thanks to the above discussion on diagonal mapping,
-we can further assume that the $\delta_i$'s and $a_n$ are all $1$'s
-and are reduce to $\PP_2$ defined by the linear matrix inequality :
-\[  \begin{bmatrix}
-1	& 		& 			&   &		 &  &a_1	\\
-			& \ddots& 			& 0	&		 &	&		\\
-			&		& 1  &   & 		 &	& \\
-			&		&			&0  & 		 &	& 	\vdots	\\
-			&		&			&   & \ddots &	&		\\
-			&		&			&	&		 & 0&a_{n-1} \\
-			&		&			&	&		 &	&1 	\\
-
-\end{bmatrix} \begin{bmatrix} x_1 \\ \\  \\ \\ \vdots \\  \\ \\ x_n \\ \end{bmatrix} + \begin{bmatrix} b_1 \\ \\ \\  \\ \vdots  \\ \\ \\ b_n \\ \end{bmatrix}  \geq 0.\]
-Finally, we can also assume that, up to a permutation of the variables, $\val(a_1)= \min_{i=1}^{n-1} \val(a_i).$
-We distinguish two cases: $\val(a_1) \geq 0$ and $\val(a_1)<0.$
-
-Let us first assume that $\val(a_1) \geq 0$
-
-Let $x \in \PP_2$.
-Then $x_n=-b_n+O(1)$
-and $x_1+a_1 x_n+b_1=O(1).$
-Consequently, $x_1-a_1 b_n +b_1=O(1)+O(\pi^{\val(a_1)})=O(1).$
-Similarly, for all $i \in \llbracket 2,n-1 \rrbracket,$
-$x_i-a_ib_n+b_i=O(1)+O(\pi^{\val(a_i)})=O(1).$
-
-We define the polyhedron $\Qc \subset K^{n-1}$ by the following inequalities:
- for all $i \in \llbracket 1,n-1 \rrbracket,$
-$\val(x_i-a_ib_n+b_i) \geq 0.$
-
-Then the previous computations prove that $f(\PP_2)\subset \Qc.$
-Conversely, let $(x_1,\dots,x_{n-1}) \in \Qc.$
-Then let $x_n := -b_n.$
-
-We check that for $i \in \llbracket 1,n-1 \rrbracket,$
-$x_i+a_ix_n+b_i=x_i-a_ib_n+b_i=O(1),$
-and $x_n+b_n=O(1)$. Hence $(x_1,\dots,x_n) \in \PP_2$
-which means that $(x_1,\dots,x_{n-1}) \in f(\PP_2).$
-Thus $f(\PP_2)= \Qc$ and $f(\PP_2)$ is a polyhedron.
-
-We now deal with the second case, with $\val(a_1)<0.$
-Let $x \in \PP_2$.
-Then $x_n=-b_n+O(1)$
-and $x_1+a_1 x_n+b_1=O(1).$
-Consequently, $x_1-a_1 b_n +b_1=O(1)+O(\pi^{\val(a_1)})=O(\pi^{\val(a_1)})).$
-Thus $a_1^{-1}x_1- b_n +a_1^{-1}b_1=O(1)$.
-%and $x_n=-a_1^{-1}(x_1+b_1)+O(1).$
-In addition, $x_n=-a_1^{-1}(x_1+b_1)+O(\pi^{-\val(a_1)}).$
-We plug this equality in 
-$x_i+a_i x_n+b_i=O(1)$ to get
-$x_i-a_1^{-1}a_i(x_1+b_1)+b_i=O(1)+O(\pi^{\val(a_i)-\val(a_1)})=O(1)$
-using that $\val(a_i) \geq \val (a_1).$
-
-We define the polyhedron $\Qc \subset K^{n-1}$ by the following inequalities:
-$\val(a_1^{-1}x_1- b_n +a_1^{-1}b_1) \geq 0$ and for all $i \in \llbracket 2,n-1 \rrbracket,$
-$\val(x_i-a_1^{-1}a_i(x_1+b_1)+b_i) \geq 0.$
-
-Then the previous computations prove that $f(\PP_2)\subset \Qc.$
-Conversely, let $(x_1,\dots,x_{n-1}) \in \Qc.$
-Let $x_n := -a_1^{-1}(x_1+b_1).$
-Then
-$x_1+a_1 x_n+b_1=0=O(1).$
-Let $i \in \llbracket 2,n-1 \rrbracket,$
-then $x_i+a_i x_n+b_i=x_i-a_1^{-1}a_i(x_1+b_1)+b_i=O(1)$
-since $(x_1,\dots,x_{n-1}) \in \Qc.$
-Finally, 
-$x_n+b_n=-a_1^{-1}(x_1+b_1)+b_n=O(1)$ thanks to the inequality satisfied by $x_1.$
-Hence $(x_1,\dots,x_n) \in \PP_2$
-which means that $(x_1,\dots,x_{n-1}) \in f(\PP_2).$
-Thus $f(\PP_2)= \Qc$ and $f(\PP_2)$ is a polyhedron,
-and it has been proved in both cases.
-
-Therefore, if $f$ is the projection 
-$(x_1,\dots,x_{n-1},x_n)\mapsto (x_1,\dots,x_{n-1})$ 
-and $\PP$ is a polyhedron in $K^n$,
-then $f(\PP)$ is a polyhedron.
-
-\tristan{Attention, à partir de maintenant,
-il faut ajouter à la définition qu'on peut
-fixer des points!
-Cela revient à ajouter des conditions
-$\val = + \infty.$}
-
-It is also clear that
-if $f$ is the immersion 
-$K^l \rightarrow K^n$
-$(x_1,\dots,x_l)\mapsto (x_1,\dots,x_l,0,\dots,0)$ 
-and $\PP$ is a polyhedron in $K^n$,
-then $f(\PP)$ is a polyhedron.
-
-We now prove that for
-$\Delta$ a Smith Normal Form
-and $\PP$ a polyhedron,
-$\Delta(\PP)$ is a polyhedron.
-Then $\Delta$ is the composition
-of the immersion 
-$K^l \rightarrow K^n$
-$(x_1,\dots,x_l)\mapsto (x_1,\dots,x_l,0,\dots,0),$ 
- the diagonal invertible mapping
-$K^l \rightarrow K^l$,
-$(x_1,\dots,x_l)\mapsto (\delta_1,\dots,\delta_l x_l)$,
-and the projections
-$(x_1,\dots,x_{l+1})\mapsto (x_1,\dots,x_{l}),$
- $(x_1,\dots,x_{l+2})\mapsto (x_1,\dots,x_{l+1}),$
- $\dots,$
- $(x_1,\dots,x_{n})\mapsto (x_1,\dots,x_{n-1}).$
- Thus $\Delta(\PP)$ is a polyhedron thanks to the previous 
- results on image of polyhedron.
-
-Finally, if $f: K^n \rightarrow K^m$
-is a linear mapping and
-$f=Q^{-1} \Delta P$ is its Smith Normal Form
-with $P \in \GL_n(\OK),$ $Q \in \GL_m(\OK)$
-and $\Delta \in \allmat_{n,m}(K)$,
-then
-$P(\PP)$ is a polyhedron,
-$\Delta (P(\PP))$ also,
-and finally $f(\PP)=Q^{-1} (\Delta (P(\PP)))$
-is a polyhedron.
-This concludes the proof.
-\end{proof}
-
 \printbibliography

### 2024-02-15 article/paper_padic_spec.tex
commit by Simone

@@
 
-In this section, we define polyhedra over a complete discrete valuation field $K$ with valuation $\val$ and a uniformizer $\pi$, and we discuss the associated linear optimization problem.
+In this section, we define polyhedra over a complete discrete valuation field $K$ with valuation $\val$ and a uniformizer $\pi$, and we prove that the class of polyhedra is closed under linear transformations, as in the real case.
+We end by presenting an algorithm for solving linear optimization problems over $K$.
 

### 2024-02-23 article/paper_padic_spec.tex
modif in annuli

@@
 
-\subsection{Annuli (couronnes)}
-\begin{definition}
-	Annulus
+\subsection{Annuli}
 
-	We call \emph{annulus} a set $A$ defined as $C = \{x \in K  | a\le \val(x) \le b\} $ for $a < b$ two nonnegative real numbers.
+$\R^*_+$ denotes the set of positive real numbers.
+
+\begin{definition}[Annulus]\label{def_annuli}
+  A set of the form $A = \{x \in K \,|\, a \le \val(x) \le b\}$ for $a,b \in \R^*_+$ is called \emph{annulus}.
 \end{definition}
@@
 \end{theorem} 
-
 \begin{proof}
-Let $A$ be the annulus defined by $a<b \in \R^*_+$.
-We consider for all $x,y \in K $ the spectrahedron $\mathcal{S}= \left\{(x,y) \in K  : M(x,y) := \pi^ax \oplus \pi^{-b}y \oplus \begin{bmatrix} \pi^{-1} & -\pi^{-1}x \\ \pi^{-1}y & - \pi^{-1}  \\ \end{bmatrix} \succeq 0\right\}$.
-
+  Let $A$ be as in \Cref{def_annuli}, for some $a,b \in \R^*_+$, assume $a<b$. Consider the spectrahedron
+  $\mathcal{S} \subset K^2$ defined by
+  $$
+  \mathcal{S}= \left\{(x,y) \in K^2 : M(x,y) := \diag\left(\pi^ax, \pi^{-b}y, \begin{bmatrix} \pi^{-1} & -\pi^{-1}x \\ \pi^{-1}y & - \pi^{-1}  \\ \end{bmatrix}\right) \succeq 0\right\}.
+  $$
 We will show that $x \in A$ if and only if  there exists $y\in K$ such that $(x,y) \in \mathcal{S}$.
-
-Let $x,y \in K$. By \ref{caracsdp}, $M(x,y)$ is positive semidefinite if and only if $(x,y)$ is a solution of \ref{eq:annulussyst}.
-
+Let $x,y \in K$. By \Cref{caracsdp}, $M(x,y) \succeq 0$ if and only if $(x,y)$ is a solution of
+\eqref{eq:annulussyst}:
 \begin{equation}
@@
 \end{equation}
-
-Therefore, if $(x, y)$ verifies \ref{eq:annulussyst} then $\val\left(x\right)\ge a$, $\val\left(y\right)\ge -b$ and $ \left( xy-1 \right) \ge 2$.
+Therefore, if $(x, y)$ verifies \eqref{eq:annulussyst} then $\val\left(x\right)\ge a$, $\val\left(y\right)\ge -b$ and $ \left( xy-1 \right) \ge 2$.
 The last inequality implies that $\val\left(x\right)+\val\left(y\right)=\val\left(xy\right) = \val\left(-1\right) =0$ and therefore that $\val\left(x\right)=-\val\left(y\right)\le -(-b)  =b$, so $x \in C$.
-Reciprocally if $x \in C$ then $(x,x^{-1}) $ is a solution of \ref{eq:annulussyst} .
+Reciprocally if $x \in C$ then $(x,x^{-1}) $ is a solution of \eqref{eq:annulussyst}.
 \end{proof}

### 2024-03-11 article/paper_padic_spec.tex
few modifs prop 1

@@
   $$
-  1-x_1^2 \geq 0, \,\,\, 1-x_2^2 \geq 0, \,\,\, 1-x_3^2 \geq 0 \,\,\, \text{ and } \,\,\, 1+2x_1x_2x_3-x_1^2-x_2^2-x_3^2 \geq 0
-  $$
-  \exend
+  1-x_1^2 \geq 0, \,\,\, 1-x_2^2 \geq 0, \,\,\, 1-x_3^2 \geq 0 \,\,\, \text{ and } \,\,\, 1+2x_1x_2x_3-x_1^2-x_2^2-x_3^2 \geq 0.$$ \exend
 \end{example}
@@
 
+{\bf normalement avec la nouvelle definition, ça devrait aller, peut être il faudrait
+  diviser la proposition en plusieures parties pour la rendre plus lisible}.
+
 \begin{proposition}
@@
 with $P \in \GL_n(\OK),$ $Q \in \GL_m(\OK)$
-and $\Delta \in \allmat_{n,m}(K)$ of the form $\lambda_1 \oplus \cdots \oplus \lambda_r \oplus {\bf 0}_{\min(m,n)-r}$
+and $\Delta \in \allmat_{n,m}(K)$ of the form $\diag(\lambda_1, \ldots, \lambda_r, {\bf 0}_{\min(m,n)-r})$
   where ${\bf 0}_{\min(m,n)-r}$ is a null square matrix of size $\min(m,n)-r$ for $\lambda_1,\dots,\lambda_r$ non-zero and $r \in \N.$
@@
 $i \in I,$
-$\val (l_i (f^{-1}(x)) \geq 0$.
+$\val(l_i (f^{-1}(x))) \geq 0$.
 The $l_i \circ f^{-1}$ are clearly in $K[x]_1$
@@
 
-Similarly, if $f$ is of the form $K^n \rightarrow K^n$,
-$(x_1,\dots,x_n) \mapsto (\lambda_1 x_1,\dots,\lambda_n x_n)$
-for some $\lambda_i$'s in $K$,
-then it is clear that $f(P)$
+Similarly, if $f:K^n \rightarrow K^n$ is of the form
+$f(x_1,\dots,x_n)=(\lambda_1 x_1,\dots,\lambda_n x_n)$
+for some $\lambda \in K$,
+then of course $f(P)$
 can be defined by $\val (\widetilde{l_i}(x)) \geq 0$, $i \in I$

### 2024-03-11 article/paper_padic_spec.tex
commit by Simone

@@
 
-{\bf normalement avec la nouvelle definition, ça devrait aller, peut être il faudrait
-  diviser la proposition en plusieures parties pour la rendre plus lisible}.
+{\color{blue} Normalement avec la nouvelle definition, ça devrait aller, il faut par contre
+  partir d'un polyedre defini aussi par des égalités. Peut être il faudrait aussi
+  diviser la proposition en plusieures parties pour la rendre plus lisible, par exemple une
+  première proposition avec la projection.}
 
@@
 finite set $I \subset \N$ and $l_i \in K[x]_1$, for $i \in I.$ We further assume that $\PP \neq \emptyset$.
+{\color{blue} mettre aussi les égalités dans $\PP$}.
 
@@
 We first assume that $f$ is a projection 
-of the form $K^n \rightarrow K^{n+1},$
+of the form $K^n \rightarrow K^{n-1},$
 $(x_1,\dots,x_{n-1},x_n)\mapsto (x_1,\dots,x_{n-1}).$
@@
 The latter property is a direct consequence of $\OK$ being a ring and the converse holds if the matrix $M$ is invertible in $\OK$.
-Therefore, for all matrix $M \in \allmat_n(K)$ with SNF $S$ and all $z \in K^n$ $Mz \geq 0$ if and only if $Sz \geq 0$.
+Therefore, for all matrix $M \in \allmat_n(K)$ with SNF $S$ and all $z \in K^n$, then $Mz \geq 0$ if and only if $Sz \geq 0$.
 
-That property applied to the matrix $A$ in \ref{LP} allow to reduce the problem to an equivalent simpler iteration of the \ref{LP} problem that will be called \emph{diagonal linear programming problem} \corentin{or maybe reduced linear programming problem?}.
-This problem is the optimization problem: \simone{il me semble que tout ça n'est pas trop clair, par exemple quelle est la difference entre diagonal LP et associated diagonal LP plus en bas, est-ce qu'il y a vraiment besoin de tout ça, il faut simplifier la presentation}
+That property applied to the matrix $A$ in \ref{LP} allows to reduce the problem to an equivalent simpler iteration of the problem in \eqref{LP}, that will be called \emph{diagonal linear programming problem}
+%%%\corentin{or maybe reduced linear programming problem?}:
+%%%\simone{il me semble que tout ça n'est pas trop clair, par exemple quelle est la difference entre diagonal LP et associated diagonal LP plus en bas, est-ce qu'il y a vraiment besoin de tout ça, il faut simplifier la presentation}
 \begin{equation}
-  \tag{DLP}\label{DLP}
+  \tag{dLP}\label{DLP}
 \begin{array}{rcll}
-  p^* & := & \inf_{y \in K^n} & \val(\left\langle c', y \right\rangle) \\
+  {p^*}' & := & \inf_{y \in K^n} & \val(\left\langle c', y \right\rangle) \\
   &    & \text{s.t.}         & S y + b' \geq 0
@@
 \end{equation}
-with $c' \in K^n$ a fixed vector of size $n$, $b' \in K^m$ and $S$ a diagonal $m \times n$ matrix of the form $S = s_1 \oplus s_2 \oplus \ldots \oplus s_r \oplus { \bm 0}_{m-r} $ for $r={\rm rank} S$.
+with $c' \in K^n$ a fixed vector of size $n$, $b' \in K^m$ and $S$ a diagonal $m \times n$ matrix of the form $S = \diag(s_1, s_2, \ldots, s_r, { \bm 0}_{m-r})$, with $r = {\rm rank}\, S$.
 
@@
 
-A vector $x^* \in K^n$ is \emph{feasible solution} of \ref{LP} if $Ax^* + b \geq 0$.
-Similarly, a vector $y^* \in K^n$ is a feasible of \ref{DLP} if $Sy^*+b' \geq 0$.
-We will denote as $Adm$ \corentin{Probablement à changer mais je ne sais pas quel nom lui donner} the set of feasible solution of \ref{DLP}.
+A vector $x \in K^n$ is \emph{feasible} for \eqref{LP} if $Ax + b \geq 0$.
+Similarly, a vector $y \in K^n$ is feasible for \eqref{DLP} if $Sy+b' \geq 0$.
+We denote the \emph{feasible set} of \eqref{LP} and \eqref{DLP} respectively by
+\begin{equation*}
+\begin{aligned}
+  \PP  &= \{x \in K^n : Ax + b \geq 0\} \\
+  \PP' &= \{y \in K^n : Sy + b' \geq 0\}.
+\end{aligned}
+\end{equation*}
+A feasible vector $x^* \in \PP$ is called a \emph{solution} to \eqref{LP} if $p^* = \left\langle c,x^*\right\rangle$
+(similarly for \eqref{DLP}).
+%%%$Adm$ \corentin{Probablement à changer mais je ne sais pas quel nom lui donner} the set of feasible solution of \ref{DLP}.
 
 \begin{proposition} 
-  Let $A \in \allmat_{m,n}(K), b \in K^m, c\in K^n$ and let $S \in \allmat_{m,n}(K)$ be the Smith normal form of $A$ with transition matrices $P \in \GL_n(\OK)$ and $Q\in \GL(\OK)$ such that $A=Q^{-1}SP$.
-  We define $b':= Qb$ and $c':= (P^{-1})^Tc$. 
+  Let $A \in \allmat_{m,n}(K), b \in K^m, c\in K^n$ and let $S \in \allmat_{m,n}(K)$ be the Smith normal form of $A$ with transition matrices $P \in \GL_n(\OK)$ and $Q\in \GL_m(\OK)$ such that $A=Q^{-1}SP$.
+  We define $b':= Qb$ and $c':= (P^{-1})^Tc$.  Then
    \begin{enumerate}
-    \item $x^* \in K^n$ is a feasible solution of the \ref{LP} problem of parameters $A, b$ and $c$ if and only if $y^* = P x^*$ is a feasible solution of the \ref{DLP} problem of parameters $S, b'$ ans $c'$.
+    \item $x^* \in K^n$ is feasible for \eqref{LP} if and only if $y^* = P x^* \in K^n$ is feasible for \eqref{DLP}.
     \item $x \in K^n$ is a solution of the \ref{LP} problem of parameters $A, b$ and $c$ if and only if $y = P x$ is a solution of the \ref{DLP} problem of parameters $S,b'$ and $c'$ and $\langle c,x \rangle = \langle c',y \rangle$.

### 2024-03-11 article/old_LP_section.tex
commit by Simone

--- 2024-03-11 article/paper_padic_spec.tex
@@
-\documentclass[a4paper,12pt]{article}
-
-\newenvironment{proof}{\hbox{}\vspace{-0.8cm} {\bf Proof:}}{\hfill $\Box$}
-
-\usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage{amsfonts}
-\usepackage{mathrsfs} 
-\usepackage{graphicx}
-\usepackage{color}
-\usepackage{ulem}
-\usepackage{bm}
-
-\usepackage{cleveref}
-
-\newtheorem{theorem}{Theorem}[section]
-\newtheorem{lemma}{Lemma}
-\newtheorem{proposition}{Proposition}
-\newtheorem{corollary}{Corollary}
-\newtheorem{algorithm}{Algorithm}
-\newtheorem{conjecture}{Conjecture}
-\newtheorem{condition}{Condition}
-\newtheorem{definition}{Definition}
-\newtheorem{assumption}{Assumption}
-\newtheorem{remark}{Remark}
-\newtheorem{problem}{Problem}
-\newtheorem{example}{Example}
-\newtheorem{notation}{Notation}
-\usepackage{booktabs}
-
-\textheight235mm
-\textwidth165mm
-\voffset-10mm
-\hoffset-12.5mm
-\parindent0cm
-\parskip2mm
-
-\usepackage{stmaryrd} %for double brackets
-
-%\usepackage{mathptmx}
-
-% updates
-
-\newcommand{\R}{\mathbb{R}} % real numbers
-\newcommand{\C}{\mathbb{C}} % complex numbers
-\newcommand{\N}{\mathbb{N}} % integers
-\newcommand{\allmat}{\mathbb{M}} % matrices
-\newcommand{\sym}{\mathbb{S}} % matrices symétriques
-\newcommand{\PP}{\mathcal{P}}
-\newcommand{\Qc}{\mathcal{Q}}
-\renewcommand{\span}[1]{{\text{span}(#1)}} % simone's comments
-\newcommand{\aff}[1]{{\text{aff}(#1)}} % simone's comments
-\newcommand{\relint}[1]{{\text{relint}(#1)}} % simone's comments
-\newcommand{\calL}{\mathcal{L}} % simone's comments
-
-\newcommand{\simone}[1]{{\color{blue} #1}} % simone's comments
-\newcommand{\corentin}[1]{{\color{red} #1}} % corentin's comments
-\newcommand{\tristan}[1]{{\color{red} #1}} % tristan's comments
-
-%p-adic commands
-\DeclareMathOperator{\val}{val}
-\def\QQ{\ensuremath{\mathbb{Q}}}
-\def\ZZ{\ensuremath{\mathbb{Z}}}
-\newcommand{\OK}{\mathcal{O}_K}
-\def\diag{\mathrm{diag}}
-
-\newcommand{\GL}{\mathrm{GL}}
-
-\newcommand{\exend}{\hfill $\blacksquare$}
-
-\usepackage{biblatex}
-\addbibresource{../rapport/bibstage.bib}
-
-\title{\bf Title}
-
-\begin{document}
-
-\author{Corentin Cornou$^{1}$, Simone Naldi$^{2,3}$ and Tristan Vaccon$^{2}$}
-
-\footnotetext[1]{ENS Paris-Saclay, Université Paris-Saclay, France.}
-\footnotetext[2]{Université de Limoges, CNRS, XLIM, UMR 7252, F-87000 Limoges, France.}
-\footnotetext[3]{Sorbonne Université, CNRS, LIP6, Equipe PolSys, F-75005 Paris, France.}
-
-\date{Draft of \today}
-
-\maketitle
-
-\begin{abstract}
-\end{abstract}
-
-\tableofcontents
-
-\section{Introduction}
-
-\subsection{Context and motivations}
-
-%Il faudra entre autre mentionner (et peut être motiver l'approche p-adique) :
-%\begin{itemize}
-%\item les questions ouvertes de complexité concernant la programmation semidefinie (pas clair si NP $\cap$ co-NP
-%  dans le modele de Turing)
-%\item les questions ouvertes géométriques (Conjecture de Lax)
-%\end{itemize}
-
-\subsection{Main results}
-
-\newpage
-\section{Preliminaries}
-
-\subsection{Notation}
-
-Throughout the paper, $K$ refers to a complete,
-discrete valuation field, $\val : K \twoheadrightarrow \ZZ \cup \{+\infty\}$ to its valuation,
-$\OK$ its ring of integers and $\pi$ a uniformizer.
-For $k \in \N$, we write $O(\pi^k)$ for $\pi^k \OK$.
-A typical example of $K$ as above is the field of $p$-adic numbers 
-$\QQ_p$ (equipped with the $p$-adic valuation). For this example, we 
-have $\OK = \ZZ_p$.
-Another example is the field of Laurent series
-$K=\QQ(\!(t)\!)$ equiped with $t$-adic valuation,
-in which case $\OK = \QQ \llbracket t \rrbracket$.
-We refer to \cite{Serre:1979} for a
-general introduction to such fields
-and to Caruso's course on $p$-adic computations \cite{caruso_computations_2017}
-for an introduction to effective computations over $p$-adic numbers.
-
-The $K$-vector space of polynomials of degree $\leq d$ on $x=(x_1,\ldots,x_n)$
-with coefficients in $K$ is denoted by $K[x]_{d}$. The vector space of matrices of
-size $p \times q$ with entries in $K$ is $\allmat_{p,q}(K)$ and the general
-linear group in $\allmat_{n,n}(K)$ is $\GL_n(K)$.
-For the sake
-of ease of writing, block-diagonal matrices with blocks $B_1,\ldots,B_d$ are denoted by
-$\diag(B_1, \ldots, B_d)$.
-
-We recall the definition of Smith Normal Form, in our context.
-\begin{definition}[Smith Normal Form]\label{smith_nf}
-  Let $M \in \allmat_{m,n}(K)$ be of rank $r$. There exist unique integers $a_1 \leq \cdots \leq a_r$, and
-  matrices $P \in \GL_n(\OK)$ and $Q \in \GL_m(\OK)$, such that
-  $$
-  S := QMP^{-1} = \diag(\pi^{a_1}, \pi^{a_2}, \ldots, \pi^{a_r}, {\bf 0}_{\min(m,n)-r})
-  $$
-  where ${\bf 0}_{\min(m,n)-r}$ is a null square matrix of size $\min(m,n)-r$.
-  The matrix $S$ is called the \emph{Smith Normal Form (SNF)} of $M$, and the elements $\pi^{a_i}$ the
-  \emph{invariant factors}.
-\end{definition}
-\begin{remark}
-  The valuation of the first invariant factor of the SNF of a matrix
-  $M \in \allmat_{n,n}(K)$ is the minimum of the valuations of the entries of
-  $M$. In particular, the SNF of $M \in \allmat_{n,n}(\OK)$ has entries in $\OK$.
-\end{remark}
-
-\subsection{Real spectrahedra}
-
-Let $\sym_d(\R) \subset \allmat_{d,d}(\R)$ be the vector space of $d \times d$ real symmetric
-matrices. A matrix $M \in \sym_d(\R)$
-is called \emph{positive semidefinite} ($M \succeq 0$) whenever the quadratic
-form $x \mapsto x^TMx$ is nonnegative for all $x\in \R^n$. By the Spectral Theorem, $M \succeq 0$
-if and only if the eigenvalues of $M$ are nonnegative, and this is equivalent to all the principal minors
-of $M$ being nonnegative. The set of positive semidefinite matrices, denoted $\sym_d^+(\R) \subset \sym_d(\R)$,
-is a closed convex cone with non-empty interior in $\sym_d(\R)$.
-
-Let $A_0,A_1,\ldots,A_n \in \sym_d(\R)$, and let $\calL = A_0+\span{A_1,\ldots,A_n}$ be the affine space
-containing $A_0$ and with direction the vector space spanned by $A_1,\ldots,A_n$ (which we assume linearly
-independent). The intersection $\calL \cap \sym_d^+(\R) = \left\{A(x) := A_0+\sum_i x_i A_i \in \sym_d(\R) :
-A(x) \succeq 0\right\}$, or
-equivalently, its pre-image $S = \{x \in \R^n : A(x) \succeq 0\}$ under the map $x \mapsto A(x)$, is called
-a \emph{real spectrahedron}. As (linear preimage of) affine sections of $\sym_d^+(\R)$, real spectrahedra
-are closed convex sets, but might have empty interior in $\calL$ (resp. in $\R^n$).
-Moreover, they are basic semialgebraic sets, indeed they are defined by sign conditions on the principal
-minors of the defining matrix as well as sign conditions on the coefficients of its characteristic polynomial
-(cf. \Cref{ell3}).
-
-\begin{example}\label{ell3}
-  Let $d=n=3$. The $3$-elliptope is the three-dimensional spectrahedron given by
-  $$
-  \mathcal{E}_3 :=
-  \left\{
-  x
-  \in \R^3 :
-  \begin{bmatrix}
-    1 & x_1 & x_2 \\
-    x_1 & 1 & x_3 \\
-    x_2 & x_3 & 1
-  \end{bmatrix}
-  \succeq 0
-  \right\}
-  =
-  \left\{
-  x
-  \in \R^3 :
-  \begin{array}{r}
-    3-x_1^2-x_2^2-x_3^2 \geq 0 \\
-    1+2x_1x_2x_3-x_1^2-x_2^2-x_3^2 \geq 0
-  \end{array}
-  \right\}.
-  $$
-  The polynomials on the right are the (non-constant) coefficients of the univariate polynomial
-  $p(t) = \det(A(x)+t I_3)$,
-  whose roots are the opposites of the eigenvalues of the defining matrix. Equivalently $\mathcal{E}_3$
-  is defined by positivity of the principal minors of the defining matrix:
-  $$
-  1-x_1^2 \geq 0, \,\,\, 1-x_2^2 \geq 0, \,\,\, 1-x_3^2 \geq 0 \,\,\, \text{ and } \,\,\, 1+2x_1x_2x_3-x_1^2-x_2^2-x_3^2 \geq 0.$$ \exend
-\end{example}
-
-The optimization problem of miminizing a linear function over a real spectrahedron is called \emph{semidefinite programming} (SDP).
-Given $c \in \R^n$ and $A_0,A_1,\ldots,A_n \in \sym_d(\R)$, the corresponding semidefinite program is defined (in standard dual form) as
-\begin{equation}
-  \label{SDP}
-\begin{array}{rcll}
-  p^* & := & \inf_{x \in \R^n} & \left\langle c, x \right\rangle \\
-  &    & \text{s.t.}         & A_0+\sum_{i=1}^n x_i A_i \succeq 0.
-\end{array}
-\end{equation}
-Real polyhedra (subsets of $\R^n$ defined by finitely many affine inequalities) are special cases of real
-spectrahedra, where the defining matrices $A_0, \ldots, A_n$ can be chosen diagonal, so that $A(x) =
-\ell_1(x) \oplus \cdots \oplus \ell_d(x)$. In other words, SDP is a generalization of Linear Programming (LP).
-
-In a fixed-precision model of computation, SDP is solvable in polynomial time in the input size (matrix size,
-number of variables, bit size of the coefficients), in $\log(\frac{1}{\varepsilon})$ (where $\varepsilon$ is the
-precision) and $\log(\frac{1}{R})$, where $R$ is an {\it a priori} upper bound on the norm of a solution,
-cf. \cite[Sec.1.9]{deKlerk}. In exact arithmetic, the complexity status of SDP is essentially open but complexity
-bounds are known based either on general quantifier elimination \cite{ramana1997exact,porkolab1997complexity}
-or by exploiting the determinantal structure of the constraints \cite{henrion2016exact}.
-
-A more general class of convex semialgebraic sets are obtained by linear projections of real spectrahedra
-called \emph{semidefinite representable sets} (or spectrahedral shadows): these are sets of the form
-$$
-P = \left\{x = \left[\begin{smallmatrix} x_1 \\ \vdots \\ x_n \end{smallmatrix}\right] \in \R^n : \exists\,y\in\R^p, \, A_0 + \sum_{i=1}^n x_i A_i + \sum_{j=1}^p y_j B_j \succeq 0\right\}
-$$
-
-\begin{example}
-\label{fermat_quartic}
-The basic closed semialgebraic set $P = \{(x_1,x_2) \in \R^2 : 1-x_1^4-x_2^4 \geq 0\}$ is not a spectrahedron
-but it is semidefinite representable:
-$$
-P = \left\{\begin{bmatrix} x_1 \\ x_2 \end{bmatrix} \in \R^2 :
-\exists\,
-\begin{bmatrix} y_1 \\ y_2 \end{bmatrix} \in \R^2, \,
-\begin{bmatrix}
-  1+y_1 & y_2 \\
-  y_2 & 1-y_1
-\end{bmatrix}
-\bigoplus
-\begin{bmatrix}
-  1 & x_1 \\
-  x_1 & y_1
-\end{bmatrix}
-\bigoplus
-\begin{bmatrix}
-  1 & x_2 \\
-  x_2 & y_2
-\end{bmatrix}
-\succeq 0
-\right\}
-$$
-\end{example}
-
-\section{Polyhedra}
-
-In this section, we define polyhedra over a complete discrete valuation field $K$ with valuation $\val$ and a uniformizer $\pi$, and we prove that the class of polyhedra is closed under linear transformations, as in the real case.
-We end by presenting an algorithm for solving linear optimization problems over $K$.
-
-\begin{definition}
-  \label{def_polyhedra}
-  A \emph{polyhedron} is a subset $P \subset K^n$ of the form
-  $$
-  P = \{x \in K^n : \val(\ell_i(x)) \geq 0, i=1,\ldots,d \text{ and }
-  \val(m_j(x)) = +\infty, j=1,\ldots,e\},
-  $$
-  for some $\ell_1,\ldots,\ell_d,m_1,\ldots,m_e \in K[x]_1$.
-\end{definition}
-
-%%We recall that that the smallest affine space of $K^n$ containing a set $S \subset K^n$ is called its \emph{affine hull} and denoted $\aff{S}$.
-The assumption on forms $\ell_i$ in \Cref{def_polyhedra} implies that the constraint $\val(m_1 \oplus \cdots \oplus m_e) = +\infty$ defines exactly the affine hull of $P$, in other words $\aff{P} = \{x \in K^n : m_j(x) = 0, j=1,\ldots,e\}$ \simone{(il nous faudrait une preuve, du genre: $\val(m(x))=+\infty$ pour tout $x \in P$ si et seulement si $m$ est une combinaison affine de $m_1,\ldots,m_e$.)}
-%%The \emph{dimension} of $P$ is defined as the dimension of $\aff{P}$ (for $e=0$, $\aff{P}=K^n$ and $P$ has dimension $n$).
-The \emph{relative interior} of $P$ is defined as $\relint{P} = \{x \in P : \val(\ell_1 \oplus \cdots \oplus \ell_d) < +\infty\}$ (\simone{pas clair si besoin de dimension et relint}).
-Remark that \Cref{def_polyhedra} includes the case $d=0$ corresponding to affine spaces, as in the real case.
-Moreover by definition the class of polyhedra is closed under intersection. Without loss of generality, one may
-assume in \Cref{def_polyhedra} that for every $i=1,\ldots,d$ there exists $x \in P$ such that
-$\val(\ell_i(x))<+\infty$.
-
-\begin{example}
-  The \emph{closed unit ball} $\OK^n=B_\infty(K^n)$ in $K^n$ for the supremum norm $||\cdot||_{\infty}$ is the
-  polyhedron defined as the set of $x=(x_1,\ldots,x_n) \in K^n$ such that $||x||_{\infty} =
-  \max_i\{x_i\} \leq 1$, in other words, such that $\val(x_i) \geq 0$, for all $i=1, \ldots, n$.
-  In other words, $\OK^n$ is the polyhedron in $K^n$ defined by the affine polynomials
-  $\ell_i(x)=x_i$, $i=1,\ldots, n$, and $e=0$. %%%%%(its affine hull is indeed the whole $K^n$).
-\end{example}
-
-\subsection{Projections of polyhedra}
-
-{\color{blue} Normalement avec la nouvelle definition, ça devrait aller, il faut par contre
-  partir d'un polyedre defini aussi par des égalités. Peut être il faudrait aussi
-  diviser la proposition en plusieures parties pour la rendre plus lisible, par exemple une
-  première proposition avec la projection.}
-
-\begin{proposition}
-Let $\PP \subset K^n$ be a polyhedron and $f: K^n \rightarrow K^m$
-be a linear mapping. Then $f(\PP)$ is a polyhedron.
-\end{proposition}
-\begin{proof}
-Let us assume that 
-$\PP = \left\lbrace x \in K^n : \val (l_i (x) ) \geq 0, \textrm{ for } i \in I \right\rbrace$ for some
-finite set $I \subset \N$ and $l_i \in K[x]_1$, for $i \in I.$ We further assume that $\PP \neq \emptyset$.
-{\color{blue} mettre aussi les égalités dans $\PP$}.
-
-Thanks to the Smith Normal Form (see Definition \ref{smith_nf}), $f$
-can be written $f=Q^{-1} \Delta P$
-with $P \in \GL_n(\OK),$ $Q \in \GL_m(\OK)$
-and $\Delta \in \allmat_{n,m}(K)$ of the form $\diag(\lambda_1, \ldots, \lambda_r, {\bf 0}_{\min(m,n)-r})$
-  where ${\bf 0}_{\min(m,n)-r}$ is a null square matrix of size $\min(m,n)-r$ for $\lambda_1,\dots,\lambda_r$ non-zero and $r \in \N.$
-
-We first prove the result when $f$ is in $\GL_n(\OK)$.
-In that case, $x \in f(P)$ if and only if for all
-$i \in I,$
-$\val(l_i (f^{-1}(x))) \geq 0$.
-The $l_i \circ f^{-1}$ are clearly in $K[x]_1$
-and $f(P)$ is a polyhedron.
-
-Similarly, if $f:K^n \rightarrow K^n$ is of the form
-$f(x_1,\dots,x_n)=(\lambda_1 x_1,\dots,\lambda_n x_n)$
-for some $\lambda \in K$,
-then of course $f(P)$
-can be defined by $\val (\widetilde{l_i}(x)) \geq 0$, $i \in I$
-with the $\widetilde{l_i}$'s obtained from the $l_i$'s by an
-obvious change of variables.
-
-Now, we turn our attention to the $\Delta$ part of $f.$
-We first assume that $f$ is a projection 
-of the form $K^n \rightarrow K^{n-1},$
-$(x_1,\dots,x_{n-1},x_n)\mapsto (x_1,\dots,x_{n-1}).$
-
-Let us write the conditions defining $\PP$
-in matrix form:
-$\val(A X+B) \geq 0$
-with $A \in M_{q,n}(K)$, $B \in K^q$
-and $X=(x_1,\dots,x_n)^\intercal.$
-
-We can compute a Smith Normal Form
-of the $q \times (n-1)$ matrix defined by the 
-$n-1$ first columns of $A$
-to obtain a decomposition of the form:
-\[ Q_A A P_A^{-1} = \begin{bmatrix}
-\delta_1	& 		& 			&   &		 &  &a_1	\\
-			& \ddots& 			& 0	&		 &	&		\\
-			&		& \delta_l  &   & 		 &	&		\\
-			&		&			&0  & 		 &	& 		\\
-			&		&			&   & \ddots &	&		\\
-			&		&			&	&		 & 0&a_{n-1} \\
-			&		&			&	&		 &	&a_n 	\\
-			&		&			&	&		 &	&    	\\
-			&		&			&	&		 &	&a_q 	\\			
-\end{bmatrix},\]
-with $Q_A \in \GL_q(\OK)$ and $P_A \in \GL_n(\OK)$ such that $P_A(e_n)=e_n.$
-
-Multiplying on the left by $Q_A^{\pm 1}$ does not
-modify whether the valuation inequalities are satisfied.
-Moreover, thanks to our previous on the case when $f$ is an automorphism,
-$\PP$ can be written
-$\PP=P_A^{-1}(\PP_2)$ for some polyhedron $\PP_2 \in K^n$
-and we are reduced to proving that
-$f(\PP_2)$ is polyhedron for $f$ still the canonical projection
-$K^n \rightarrow K^{n-1}$ and $\PP_2$
-defined by the linear matrix inequality (for some $B_2 \in K^q$):
-\[  \begin{bmatrix}
-\delta_1	& 		& 			&   &		 &  &a_1	\\
-			& \ddots& 			& 0	&		 &	&		\\
-			&		& \delta_l  &   & 		 &	& \vdots\\
-			&		&			&0  & 		 &	& 		\\
-			&		&			&   & \ddots &	&		\\
-			&		&			&	&		 & 0&a_{n-1} \\
-			&		&			&	&		 &	&a_n 	\\
-			&		&			&	&		 &	& \vdots   	\\
-			&		&			&	&		 &	&a_q 	\\			
-\end{bmatrix} \begin{bmatrix} x_1 \\ \\ \\ \\ \\ \vdots \\ \\ \\ \\ x_n \\ \end{bmatrix} + B_2 \geq 0.\]
-
-We remark that 
-$a_s x_n + b_s \geq 0$
-if and only if $x_n = -a_s^{-1} b_s + O(\pi^{- \val(a_s)}).$
-This exactly corresponds to $x_n \in B(-a_s^{-1} b_s, 2^{\val(a_s)}).$
-Since the conditions have to be compatible (we have assumed
-$\PP$ not empty), and thanks to ultrametricity,  
-the intersection of these conditions for 
-$s \in \llbracket l+1,q \rrbracket$
-is then given by the smallest of these balls.
-Let us assume it is the one defined for $l=n.$
-The only condition on $x_n$
-is then $\val(a_nx_n +b_n) \geq 0.$
-
-Thanks to the above discussion on diagonal mapping,
-we can further assume that the $\delta_i$'s and $a_n$ are all $1$'s
-and are reduce to $\PP_2$ defined by the linear matrix inequality :
-\[  \begin{bmatrix}
-1	& 		& 			&   &		 &  &a_1	\\
-			& \ddots& 			& 0	&		 &	&		\\
-			&		& 1  &   & 		 &	& \\
-			&		&			&0  & 		 &	& 	\vdots	\\
-			&		&			&   & \ddots &	&		\\
-			&		&			&	&		 & 0&a_{n-1} \\
-			&		&			&	&		 &	&1 	\\
-
-\end{bmatrix} \begin{bmatrix} x_1 \\ \\  \\ \\ \vdots \\  \\ \\ x_n \\ \end{bmatrix} + \begin{bmatrix} b_1 \\ \\ \\  \\ \vdots  \\ \\ \\ b_n \\ \end{bmatrix}  \geq 0.\]
-Finally, we can also assume that, up to a permutation of the variables, $\val(a_1)= \min_{i=1}^{n-1} \val(a_i).$
-We distinguish two cases: $\val(a_1) \geq 0$ and $\val(a_1)<0.$
-
-Let us first assume that $\val(a_1) \geq 0$
-
-Let $x \in \PP_2$.
-Then $x_n=-b_n+O(1)$
-and $x_1+a_1 x_n+b_1=O(1).$
-Consequently, $x_1-a_1 b_n +b_1=O(1)+O(\pi^{\val(a_1)})=O(1).$
-Similarly, for all $i \in \llbracket 2,n-1 \rrbracket,$
-$x_i-a_ib_n+b_i=O(1)+O(\pi^{\val(a_i)})=O(1).$
-
-We define the polyhedron $\Qc \subset K^{n-1}$ by the following inequalities:
- for all $i \in \llbracket 1,n-1 \rrbracket,$
-$\val(x_i-a_ib_n+b_i) \geq 0.$
-
-Then the previous computations prove that $f(\PP_2)\subset \Qc.$
-Conversely, let $(x_1,\dots,x_{n-1}) \in \Qc.$
-Then let $x_n := -b_n.$
-
-We check that for $i \in \llbracket 1,n-1 \rrbracket,$
-$x_i+a_ix_n+b_i=x_i-a_ib_n+b_i=O(1),$
-and $x_n+b_n=O(1)$. Hence $(x_1,\dots,x_n) \in \PP_2$
-which means that $(x_1,\dots,x_{n-1}) \in f(\PP_2).$
-Thus $f(\PP_2)= \Qc$ and $f(\PP_2)$ is a polyhedron.
-
-We now deal with the second case, with $\val(a_1)<0.$
-Let $x \in \PP_2$.
-Then $x_n=-b_n+O(1)$
-and $x_1+a_1 x_n+b_1=O(1).$
-Consequently, $x_1-a_1 b_n +b_1=O(1)+O(\pi^{\val(a_1)})=O(\pi^{\val(a_1)})).$
-Thus $a_1^{-1}x_1- b_n +a_1^{-1}b_1=O(1)$.
-%and $x_n=-a_1^{-1}(x_1+b_1)+O(1).$
-In addition, $x_n=-a_1^{-1}(x_1+b_1)+O(\pi^{-\val(a_1)}).$
-We plug this equality in 
-$x_i+a_i x_n+b_i=O(1)$ to get
-$x_i-a_1^{-1}a_i(x_1+b_1)+b_i=O(1)+O(\pi^{\val(a_i)-\val(a_1)})=O(1)$
-using that $\val(a_i) \geq \val (a_1).$
-
-We define the polyhedron $\Qc \subset K^{n-1}$ by the following inequalities:
-$\val(a_1^{-1}x_1- b_n +a_1^{-1}b_1) \geq 0$ and for all $i \in \llbracket 2,n-1 \rrbracket,$
-$\val(x_i-a_1^{-1}a_i(x_1+b_1)+b_i) \geq 0.$
-
-Then the previous computations prove that $f(\PP_2)\subset \Qc.$
-Conversely, let $(x_1,\dots,x_{n-1}) \in \Qc.$
-Let $x_n := -a_1^{-1}(x_1+b_1).$
-Then
-$x_1+a_1 x_n+b_1=0=O(1).$
-Let $i \in \llbracket 2,n-1 \rrbracket,$
-then $x_i+a_i x_n+b_i=x_i-a_1^{-1}a_i(x_1+b_1)+b_i=O(1)$
-since $(x_1,\dots,x_{n-1}) \in \Qc.$
-Finally, 
-$x_n+b_n=-a_1^{-1}(x_1+b_1)+b_n=O(1)$ thanks to the inequality satisfied by $x_1.$
-Hence $(x_1,\dots,x_n) \in \PP_2$
-which means that $(x_1,\dots,x_{n-1}) \in f(\PP_2).$
-Thus $f(\PP_2)= \Qc$ and $f(\PP_2)$ is a polyhedron,
-and it has been proved in both cases.
-
-Therefore, if $f$ is the projection 
-$(x_1,\dots,x_{n-1},x_n)\mapsto (x_1,\dots,x_{n-1})$ 
-and $\PP$ is a polyhedron in $K^n$,
-then $f(\PP)$ is a polyhedron.
-
-\tristan{Attention, à partir de maintenant,
-il faut ajouter à la définition qu'on peut
-fixer des points!
-Cela revient à ajouter des conditions
-$\val = + \infty.$}
-
-It is also clear that
-if $f$ is the immersion 
-$K^l \rightarrow K^n$
-$(x_1,\dots,x_l)\mapsto (x_1,\dots,x_l,0,\dots,0)$ 
-and $\PP$ is a polyhedron in $K^n$,
-then $f(\PP)$ is a polyhedron.
-
-We now prove that for
-$\Delta$ a Smith Normal Form
-and $\PP$ a polyhedron,
-$\Delta(\PP)$ is a polyhedron.
-Then $\Delta$ is the composition
-of the immersion 
-$K^l \rightarrow K^n$
-$(x_1,\dots,x_l)\mapsto (x_1,\dots,x_l,0,\dots,0),$ 
- the diagonal invertible mapping
-$K^l \rightarrow K^l$,
-$(x_1,\dots,x_l)\mapsto (\delta_1,\dots,\delta_l x_l)$,
-and the projections
-$(x_1,\dots,x_{l+1})\mapsto (x_1,\dots,x_{l}),$
- $(x_1,\dots,x_{l+2})\mapsto (x_1,\dots,x_{l+1}),$
- $\dots,$
- $(x_1,\dots,x_{n})\mapsto (x_1,\dots,x_{n-1}).$
- Thus $\Delta(\PP)$ is a polyhedron thanks to the previous 
- results on image of polyhedron.
-
-Finally, if $f: K^n \rightarrow K^m$
-is a linear mapping and
-$f=Q^{-1} \Delta P$ is its Smith Normal Form
-with $P \in \GL_n(\OK),$ $Q \in \GL_m(\OK)$
-and $\Delta \in \allmat_{n,m}(K)$,
-then
-$P(\PP)$ is a polyhedron,
-$\Delta (P(\PP))$ also,
-and finally $f(\PP)=Q^{-1} (\Delta (P(\PP)))$
-is a polyhedron.
-This concludes the proof.
-\end{proof}
-
 \subsection{Linear programming}
@@
 \end{remark}
-
-\section{Spectrahedra}
-
-\subsection{Definition}
-%\newcommand\mat{postive semidefinite matrix } 
-\newcommand\Mat{Positive semidefinite matrix }
-\newcommand\mats{positive semidefinite matrices }
-\newcommand\Mats{positive semidefinite matrices }
-
-\begin{definition}
-  We call a matrix $M \in \allmat_{d,d}(K)$ \emph{positive semidefinite} (in symbols $M \succeq 0$)
-  if all its eigenvalues have nonnegative valuation in an algebraic closure of $K$.
-  We denote by $\allmat_{d,d}^+(K) \subset \allmat_{d,d}(K)$ the set of positive semidefinite matrices.
-  The characteristic polynomial of a matrix $M \in \allmat_{d,d}(K)$ is denoted $\chi_M \in K[T]$.
-\end{definition}
-
-\begin{theorem}
-  \label{caracsdp}
-  $M \in \allmat_{d,d}^+(K)$ if and only if $\chi_M \in \OK[T]$.
-\end{theorem}
-\begin{proof}
-  Both senses of the equivalence will be proven by contraposition.
-
-  Let $M \in \allmat_{d,d}(K)$ with characteristic polynomial $\chi_M = T^d + \sum_{i=0}^{d-1} a_i T^i$ for $a_0,...,a_{d-1} \in K$.
-  Firstly, suppose   $M \not \in \allmat_{d,d}^+(K)$ {\it i.e.} $\chi_M$ have a root $\rho$ of negative valuation.
-  It follows that $\val \chi_M (\rho) = \val (\rho^d+ \sum_{i=0}^{d-1} a_i \rho^i ) = + \infty$ and $\val \rho^d = d \val \rho <0$.
-  The properties of the non-archimedean inequality followed by $\val $ implie that $\val ( \sum_{i=0}^{d-1} a_i \rho^i) = \val \rho^d$ and $\val ( \sum_{i=0}^{d-1} a_i \rho^i) \ge \min_{i=0,..., d-1} \val \left(a_i \rho^i\right)$.
-Therefore, there exists $i \in \left\{0,...,d-1\right\}$ such that $\val( a_i \rho^i) \le \val\rho^d$ {\it i.e.} such that $\val (a_i) \le (d-i) \val \rho <0$.
-That is all the results we need to prove the result.
-
-  We have proven the converse sense of the equivalence.
-To prove the direct sense a brief introduction to Newton's polygon will be needed, we will only state the results we use in this proof and will redirect to \cite{gouvea_p-adic_2003} to further explanations.
-  The Newton polygon $\mathcal{P}$ of a polynomial $P = \sum_{n}^{i=0} a_i T^i \in K[T]$ is defined as the inferior convex hull of the set $\{(i, \val a_i ) | i\in \{0,...,d\} \}$ {\it i.e.} the largest convex function $\mathcal{P} : [0,n] \to \R$ such that $\mathcal{P}(i) \leq \val a_i$ for $i=1,...,n$.
-  This function is piecewise affine and its slopes are exactly the opposites of the valuations of the roots of $P$. These are all the results we will need for this proof.
-
-  Suppose $\chi_M \not\in \OK[T]$.
-There exists $j \in \{0,...,d-1\}$ such that $\val (a_j)<0$.
-The polynomial $\chi_M$ being monic the point with abscissa $n$ of $\chi_M$'s Newton's Polygon is $(n,0)$.
-  Therefore, the point $(j, \val a_j)$ having negative ordinate implies that at least one of the slopes of $\chi_M$'s Newton's Polygon is positive so that $\chi_M$ has a root with negative valuation.
-\end{proof}
-
-\begin{corollary}\label{cor_caracsdp}
-  $\allmat_{d,d}(\OK) \subset \allmat_{d,d}^+(K)$.
-\end{corollary}
-\begin{proof}
-  $\OK$ is a ring therefore if $M \in \allmat_{d,d}(\OK)$, then $\chi_M \in \OK[T]$, thus we conclude
-  by \Cref{caracsdp}.
-\end{proof}
-
-\begin{example}
-  The reverse inclusion of \Cref{cor_caracsdp} is false in general. For instance the characteristic polynomial of
-  $M = \left(\begin{smallmatrix} 5 + {3}/{5} & {4}/{5} \\ {4}/{5} & -{3}/{5} \end{smallmatrix}\right)$ is $\chi_M = T^2-5T-4$.
-However when seen as a matrix over $K=\mathbb{Q}_5$, then $\chi_M \in \mathbb{Z}_5[T] = \OK[T]$: then $M \in \allmat_{2,2}^+(\mathbb{Q}_5)$, nevertheless $M \not\in \allmat_{2,2}(\mathbb{Z}_5)$, hence $\allmat_{2,2}^+(\mathbb{Q}_5) \not\subset \allmat_{2,2}(\mathbb{Z}_5)$.
-\end{example}
-
-\begin{proposition}
-  The set $\allmat_{d,d}^+(K)$ is both open and closed.
-\end{proposition}
-\begin{proof}
-Firstly, $\OK[X]$ is closed and open in $K[X]$ equipped with the infinitiy norm $\|\cdot\|_\infty : P = \sum_{k=1}^{n} a_k X^k \to \sup |a_k|$.
-$\OK$ is indeed the open unit ball for $\|\cdot \|_\infty$ that induces a discrete distance for which open balls are also closed sets.
-Furthermore, $\allmat^+_{d,d}(K) = \chi^{-1}(\OK[X]) $ where $\chi$ is the function that maps a matrix to its characteristic polynomial which is continuous.
-\end{proof}
-
-\begin{definition}
-  A \emph{cone} is subset $C$ of $K^d$ that is closed under multiplication by elements of $\OK$.   
-\end{definition}
-
-\begin{remark}
-  \corentin{Pas nécessairement très important, à voir}
-  If $C$ is a cone that is furthermore closed under addition (what shall be called a convex cone in the real case) then $C$ is a $\OK$-module.
-\end{remark}
-
-\begin{proposition}
-  The set $\allmat^+_{d,d}(K)$ is a cone.
-\end{proposition}
-\begin{proof}
-  The result is immediate following the definiton of $\allmat^+_{d,d}(K)$.
-\end{proof}
-
-\begin{definition}
-  \label{def_spectrahedra}
-  Let $\mathcal{L} = A_0+\span{A_1,\ldots,A_n} \subset \allmat_{d,d}(K)$ be an affine space, for some
-  $A_0,A_1,\ldots,A_n \in \allmat_{d,d}(K)$.
-  The set $\mathcal{L} \cap \allmat_{d,d}^+(K)$ is called a \emph{spectrahedron}. The set 
-  $S_A = \{x \in K^n : A_0+x_1A_1+\cdots+x_nA_n \succeq 0\}$, that is the preimage of $\allmat_{d,d}^+(K)$
-  under the map $x \mapsto A_0+x_1A_1+\cdots+x_nA_n$, is also called spectrahedron.
-\end{definition}
-
-\begin{remark}
-  The class of spectrahedra is closed under intersection. Indeed, for affine spaces $\mathcal{L}_1,\mathcal{L}_2$
-  one has $(\mathcal{L}_1 \cap \allmat_{d,d}^+(K)) \cap (\mathcal{L}_2 \cap \allmat_{d,d}^+(K)) =
-  (\mathcal{L}_1 \cap \mathcal{L}_2) \cap \allmat_{d,d}^+(K)$. Now
-  assuming $\mathcal{L}_1 = A_0+\span{A_1,\ldots,A_n}$ and $\mathcal{L}_2 = B_0+\span{B_1,\ldots,B_n}$,
-  then $S_A \cap S_B = S_{A \oplus B}$ (indeed both $A \succeq 0$ and $B \succeq 0$ if and only if
-  $A \oplus B \succeq 0$).
-\end{remark}
-
-%\begin{remark}
-%	As in the real case, the spectrahedron associated with the affine plan $\mathcal{L}$ will often be identified with its preimage in $K^s$ (i.e.
-the set of vectors $x \in K ^s$ so that the linear matrix $A(x) = A_0 + x_1A_1 + \ldots + x_sA_s$ is positive semidefinite with $A_0,A_1,\ldots,A_s$ spanning $\mathcal{L}$).
-%\end{remark}
-\begin{proposition}
-  A polyhedron is a spectrahedron.
-\end{proposition}
-\begin{proof}
-  Let $\ell_i,m_j \in K[x]_1$, for $i=1,\ldots,d$ and $j=1,\ldots,e$, and let $P = Q \cap L \subset K^n$
-  be a polyhedron as in \Cref{def_polyhedra}, for $Q = \{x \in K^n : \val(\ell_i) \geq 0, i=1,\ldots,d\}$
-  and $L = \{x \in K^n : \val(m_j) = +\infty, j=1,\ldots,e\}$.
-  First, denote by $A(x) = \ell_1 \oplus \cdots \oplus \ell_d \in \allmat_{d,d}(K[x]_1)$,
-  so that $A(x) = A_0+x_1A_1+\cdots+x_nA_n$ for some (diagonal) $A_i \in \allmat_{d,d}(K)$.
-  We might assume that $A_0,A_1,\ldots,A_n$ are affinely independent, so that the mapping
-  $\varphi(x) = A(x)$ is injective. 
-  First, remark that $Q=S_A$ and thus $\varphi(Q) = \mathcal{L} \cap \allmat_{d,d}(K)$, with
-  $\mathcal{L} = A_0+\span{A_1,\ldots,A_n}$ is a spectrahedron.
-  Next, remark that $L \subset K^n$ is the affine space defined by equations $m_1=\ldots=m_e=0$,
-  hence $\varphi(L) \subset \allmat_{d,d}(K)$ is an affine space. Since $\varphi$ is injective,
-  one has $\varphi(P) = \varphi(Q \cap L) = \varphi(Q) \cap \varphi(L)$ which is the intersection
-  of a spectrahedron with an affine space, thus a spectrahedron.
-  %Define $B = m_1 \oplus \cdots \oplus m_e \in \allmat_{e,e}(K[x]_1)$
-\end{proof}
-
-\begin{definition}
-  A subset $S$ of $K^n$ is said \emph{semialgebraic} if it is defined by finite unions and intersections of sets defined by polynomial equalities of the form $\{ x \in K^n  : P( x) = 0 \}$ and of sets defined by polynomial inequalities of the form $\{ x\in K^n : \val P(x) \geq 0 \}$.
-\end{definition}
-
-\begin{proposition}
-  Spectrahedra are semialgebraic sets. 
-\end{proposition}
-
-\begin{proof}
-  Let $S$ be spectrahedron and $A$ a linear matrix such that $S={x \in K^n : A(x) \succeq 0}$. 
-  We denote as $p_i(x)$ the $i$-th coefficient of $\chi_{M(x)}$. The map $p_i	: x \to p_i(x)$ is polynomial and $x \in S$ if and only if $\val(p_i(x)) \geq 0$ for $i=0,...,d$.
-
-  Finally, by \ref{caracsdp}, $S = \{x \in K^n : \chi_{M(x)} \in \OK(T)\} = \bigcap\limits_{i=0}^d \{x \in K^n : \val(p_i(x)) \geq 0\}$.
-\end{proof}
-
-\corentin{ Une autre définition qu'il pourrait être intéressant d'explorer. Attention! Pas les mêmes propriétés.}
-\begin{definition}[Alternative definition]
-  Let $A_0, ..., A_n, B_0, ..., B_n \in M_{d,d}(K)$. 
-  We denote as $S^+_A$ the set $S_{A}^+ = \left\{ x \in K^n : A_0 + x_1 A_1+ ...+x_nA_n \succeq 0  \right\}$ and $S^-_B$ denotes the set $S^-_B = \left\{ x \in K^n : B_0 + x_1 B_1+ ...+x_nB_n \preceq 0\right\}$.
-  The set $S_A,B := S_A^+ \cup S_B^-$ is called a \emph{spectrahedron}.
-\end{definition}
-
-\subsection{Annuli}
-
-$\R^*_+$ denotes the set of positive real numbers.
-
-\begin{definition}[Annulus]\label{def_annuli}
-  A set of the form $A = \{x \in K \,|\, a \le \val(x) \le b\}$ for $a,b \in \R^*_+$ is called \emph{annulus}.
-\end{definition}
-
-\begin{theorem}
-Annuli are spectrahedral shadows.
-\end{theorem} 
-\begin{proof}
-  Let $A$ be as in \Cref{def_annuli}, for some $a,b \in \R^*_+$, assume $a<b$. Consider the spectrahedron
-  $\mathcal{S} \subset K^2$ defined by
-  $$
-  \mathcal{S}= \left\{(x,y) \in K^2 : M(x,y) := \diag\left(\pi^ax, \pi^{-b}y, \begin{bmatrix} \pi^{-1} & -\pi^{-1}x \\ \pi^{-1}y & - \pi^{-1}  \\ \end{bmatrix}\right) \succeq 0\right\}.
-  $$
-We will show that $x \in A$ if and only if  there exists $y\in K$ such that $(x,y) \in \mathcal{S}$.
-Let $x,y \in K$. By \Cref{caracsdp}, $M(x,y) \succeq 0$ if and only if $(x,y)$ is a solution of
-\eqref{eq:annulussyst}:
-\begin{equation}
-  \label[type]{eq:annulussyst}
-\begin{cases}
-  \val(\pi^ax) \ge 0 \\
-  \val(\pi^{-b}y) \ge 0\\
-  \val(\pi^{-1}- \pi^{-1}) = +\infty \ge 0\\
-  \val(\pi^{-2}\left( xy-1 \right))  \ge 0 
-\end{cases}
-\iff	
-\begin{cases} 
-		\val\left(x\right)\ge a\\
-		\val\left(y\right)\ge -b\\
-		\val\left( xy-1 \right) \ge 2
-	\end{cases}
-\end{equation}
-Therefore, if $(x, y)$ verifies \eqref{eq:annulussyst} then $\val\left(x\right)\ge a$, $\val\left(y\right)\ge -b$ and $ \left( xy-1 \right) \ge 2$.
-The last inequality implies that $\val\left(x\right)+\val\left(y\right)=\val\left(xy\right) = \val\left(-1\right) =0$ and therefore that $\val\left(x\right)=-\val\left(y\right)\le -(-b)  =b$, so $x \in C$.
-Reciprocally if $x \in C$ then $(x,x^{-1}) $ is a solution of \eqref{eq:annulussyst}.
-\end{proof}
-
-\subsection{Polyhedrality}
-Cf. \cite{bhardwaj2015deciding}
-
-\section{Linear matrix inequalities}
-
-\section{Other questions}
-\begin{itemize}
-\item The projection of a real polyhedron is a real polyhedron (thanks to Fourier-Motzkin elimination procedure). Is it the same for $K$-polyhedra?
-\item Annuli are semidefinite representable, we should remark/prove that they are not spectrahedra.
-\end{itemize}
-
-\printbibliography
-
-\end{document}

### 2024-03-11 article/paper_padic_spec.tex
commit by Simone
modifs sec LP

@@
   $$
-  S := QMP^{-1} = \diag(\pi^{a_1}, \pi^{a_2}, \ldots, \pi^{a_r}, {\bf 0}_{\min(m,n)-r})
+  SNF(M) := QMP^{-1} = \diag(\pi^{a_1}, \pi^{a_2}, \ldots, \pi^{a_r}, {\bf 0}_{\min(m,n)-r})
   $$
   where ${\bf 0}_{\min(m,n)-r}$ is a null square matrix of size $\min(m,n)-r$.
-  The matrix $S$ is called the \emph{Smith Normal Form (SNF)} of $M$, and the elements $\pi^{a_i}$ the
+  The matrix $SNF(M)$ is called the \emph{Smith Normal Form (SNF)} of $M$, and the elements $\pi^{a_i}$ the
   \emph{invariant factors}.
@@
 \begin{remark}
-  The valuation of the first invariant factor of the SNF of a matrix
+  The valuation of the first invariant factor of $SNF(M)$ of a matrix
   $M \in \allmat_{n,n}(K)$ is the minimum of the valuations of the entries of
-  $M$. In particular, the SNF of $M \in \allmat_{n,n}(\OK)$ has entries in $\OK$.
+  $M$. In particular, $SNF(M) \in \allmat_{n,n}(\OK)$.
 \end{remark}
@@
 $\PP = \left\lbrace x \in K^n : \val (l_i (x) ) \geq 0, \textrm{ for } i \in I \right\rbrace$ for some
-finite set $I \subset \N$ and $l_i \in K[x]_1$, for $i \in I.$ We further assume that $\PP \neq \emptyset$.
-{\color{blue} mettre aussi les égalités dans $\PP$}.
+finite set $I \subset \N$ and $l_i \in K[x]_1$, for $i \in I$ ({\color{blue} mettre aussi les égalités dans $\PP$}).
+We further assume that $\PP \neq \emptyset$, and we identify $f$ with its matrix in $\allmat_{n,n}(K)$.
 
-Thanks to the Smith Normal Form (see Definition \ref{smith_nf}), $f$
+Thanks to Definition \ref{smith_nf}, (the matrix of) $f$
 can be written $f=Q^{-1} \Delta P$
 with $P \in \GL_n(\OK),$ $Q \in \GL_m(\OK)$
-and $\Delta \in \allmat_{n,m}(K)$ of the form $\diag(\lambda_1, \ldots, \lambda_r, {\bf 0}_{\min(m,n)-r})$
+and $\Delta = SNF(f)\in \allmat_{m,n}(K)$ of the form $\diag(\lambda_1, \ldots, \lambda_r, {\bf 0}_{\min(m,n)-r})$
   where ${\bf 0}_{\min(m,n)-r}$ is a null square matrix of size $\min(m,n)-r$ for $\lambda_1,\dots,\lambda_r$ non-zero and $r \in \N.$
@@
 
+%%%%% old section by Corentin
+%%%%%\input{old_LP_section.tex}
+
 \subsection{Linear programming}
 
-A \emph{linear programming problem} (or simply \emph{linear program}) is given by the following
-optimization problem:
+A \emph{linear programming problem} (or simply \emph{linear program}) \emph{with data $(A,b,c)$} is defined
+as:
 \begin{equation}
@@
 with $c \in K^n$ a fixed vector of size $n$ that represents the cost, $A \in \allmat_{m,n}(K)$, $b \in K^m$,
-and $\left\langle c, x \right\rangle := c_1x_1+\cdots +c_nx_n$.
+and $\left\langle c, x \right\rangle := c_1x_1+\cdots +c_nx_n$. When $A$ is a diagonal matrix, we often
+refer to \eqref{LP} as a \emph{diagonal} linear program. We denote the \emph{feasible set} of \eqref{LP} by
+\begin{equation*}
+\begin{aligned}
+  \PP  &= \{x \in K^n : Ax + b \geq 0\}.
+\end{aligned}
+\end{equation*}
+A vector $x \in K^n$ is called \emph{feasible} for \eqref{LP} if $x \in \PP$. A feasible vector $x^* \in \PP$
+is called a \emph{solution} to \eqref{LP} if $p^* = \left\langle c,x^*\right\rangle$.
 
-We present an algorithm for solving \eqref{LP} which consists in reducing the matrix $A$ in Smith normal form.
-The most interesting aspect in the SNF regarding the resolution of \ref{LP} is that the transition matrices are invertible in $\OK$.
-Indeed, if $z \in K^n$ and $M \in \allmat_n(\OK)$ such that $z \geq 0$ then $Mz \geq 0$.
-The latter property is a direct consequence of $\OK$ being a ring and the converse holds if the matrix $M$ is invertible in $\OK$.
-Therefore, for all matrix $M \in \allmat_n(K)$ with SNF $S$ and all $z \in K^n$, then $Mz \geq 0$ if and only if $Sz \geq 0$.
+In this section we present an algorithm for solving \eqref{LP} which consists in reducing the matrix $A$ in
+Smith Normal Form,
+thus reducing a general linear program to an iteration of diagonal linear programs.
+The most interesting aspect of the SNF regarding the resolution of \eqref{LP} is that the transition matrices are
+invertible in $\OK$, thus they preserve inequalities: indeed, if $z \in K^n$ and $M \in \allmat_n(\OK)$ such
+that $z \geq 0$, then $Mz \geq 0$.
+The latter property is a direct consequence of $\OK$ being a ring and the converse holds if the matrix $M$ is
+invertible in $\OK$. Therefore, for all matrix $M \in \allmat_{n,n}(K)$ with $S=SNF(M)$ and for all $z \in K^n$,
+then $Mz \geq 0$ if and only if $Sz \geq 0$.
 
-That property applied to the matrix $A$ in \ref{LP} allows to reduce the problem to an equivalent simpler iteration of the problem in \eqref{LP}, that will be called \emph{diagonal linear programming problem}
 %%%\corentin{or maybe reduced linear programming problem?}:
 %%%\simone{il me semble que tout ça n'est pas trop clair, par exemple quelle est la difference entre diagonal LP et associated diagonal LP plus en bas, est-ce qu'il y a vraiment besoin de tout ça, il faut simplifier la presentation}
-\begin{equation}
-  \tag{dLP}\label{DLP}
-\begin{array}{rcll}
-  {p^*}' & := & \inf_{y \in K^n} & \val(\left\langle c', y \right\rangle) \\
-  &    & \text{s.t.}         & S y + b' \geq 0
-\end{array}
-\end{equation}
-with $c' \in K^n$ a fixed vector of size $n$, $b' \in K^m$ and $S$ a diagonal $m \times n$ matrix of the form $S = \diag(s_1, s_2, \ldots, s_r, { \bm 0}_{m-r})$, with $r = {\rm rank}\, S$.
+%That property applied to the matrix $A$ in \ref{LP} allows to reduce the problem to an equivalent simpler iteration of the problem in \eqref{LP}, that will be called \emph{diagonal linear programming problem}
+%\begin{equation}
+%  \tag{dLP}\label{DLP}
+%\begin{array}{rcll}
+%  {p^*}' & := & \inf_{y \in K^n} & \val(\left\langle c', y \right\rangle) \\
+%  &    & \text{s.t.}         & S y + b' \geq 0
+%\end{array}
+%\end{equation}
+%with $c' \in K^n$ a fixed vector of size $n$, $b' \in K^m$ and $S$ a diagonal $m \times n$ matrix of the form $S = \diag(s_1, s_2, \ldots, s_r, { \bm 0}_{m-r})$, with $r = {\rm rank}\, S$.
 
@@
 
-A vector $x \in K^n$ is \emph{feasible} for \eqref{LP} if $Ax + b \geq 0$.
-Similarly, a vector $y \in K^n$ is feasible for \eqref{DLP} if $Sy+b' \geq 0$.
-We denote the \emph{feasible set} of \eqref{LP} and \eqref{DLP} respectively by
-\begin{equation*}
-\begin{aligned}
-  \PP  &= \{x \in K^n : Ax + b \geq 0\} \\
-  \PP' &= \{y \in K^n : Sy + b' \geq 0\}.
-\end{aligned}
-\end{equation*}
-A feasible vector $x^* \in \PP$ is called a \emph{solution} to \eqref{LP} if $p^* = \left\langle c,x^*\right\rangle$
-(similarly for \eqref{DLP}).
-%%%$Adm$ \corentin{Probablement à changer mais je ne sais pas quel nom lui donner} the set of feasible solution of \ref{DLP}.
-
-\begin{proposition} 
-  Let $A \in \allmat_{m,n}(K), b \in K^m, c\in K^n$ and let $S \in \allmat_{m,n}(K)$ be the Smith normal form of $A$ with transition matrices $P \in \GL_n(\OK)$ and $Q\in \GL_m(\OK)$ such that $A=Q^{-1}SP$.
-  We define $b':= Qb$ and $c':= (P^{-1})^Tc$.  Then
+\begin{proposition} \label{solsLP}
+  Let $A \in \allmat_{m,n}(K), b \in K^m, c\in K^n$ and let $S = SNF(A) = QAP^{-1} \in \allmat_{m,n}(K)$, with
+  transition matrices $P \in \GL_n(\OK)$ and $Q\in \GL_m(\OK)$. Define $b' = Qb$ and $c' = (P^{-1})^Tc$.
+  Then
    \begin{enumerate}
-    \item $x^* \in K^n$ is feasible for \eqref{LP} if and only if $y^* = P x^* \in K^n$ is feasible for \eqref{DLP}.
-    \item $x \in K^n$ is a solution of the \ref{LP} problem of parameters $A, b$ and $c$ if and only if $y = P x$ is a solution of the \ref{DLP} problem of parameters $S,b'$ and $c'$ and $\langle c,x \rangle = \langle c',y \rangle$.
+   \item \label{solsLP_item1}
+     $x \in K^n$ is feasible for \eqref{LP} with data $(A,b,c)$ if and only if $y = P x \in K^n$ is
+     feasible for \eqref{LP} with data $(S,b',c')$.
+   \item \label{solsLP_item2}
+     $x^* \in K^n$ is a solution to \eqref{LP} with data $(A,b,c)$ if and only if $y^* = P x^*$ is
+     a solution to \eqref{LP} with data $(S,b',c')$ and $\langle c,x^* \rangle = \langle c',y^* \rangle$.
    \end{enumerate}
@@
 \begin{proof}
-  First of all, 1. is a direct consequence of the fact that $Ax^*+b = AP^{-1}y^* +b\geq 0$ if and only if $Q(AP^{-1}y^* + b) = Sy^* + b' \geq 0$ because $Q \in GL_m(\OK)$.
-
-  Then, 2. comes from the fact that for all $c \in K^n$ $\langle c, x\rangle = \langle c, P^{-1}Py \rangle = \langle \left(P^{-1}\right)^T c, y \rangle$.
+  First of all, $Ax+b = AP^{-1}y +b \geq 0$ if and only if $Q(AP^{-1}y + b) = Sy + b' \geq 0$ because
+  $Q \in GL_m(\OK)$, which yields \Cref{solsLP_item1}. Next, for all $c \in K^n$, one has $\langle c,
+  x\rangle = \langle c, P^{-1}Px \rangle = \langle \left(P^{-1}\right)^T c, Px \rangle = \langle c',y\rangle$,
+  which proves \Cref{solsLP_item2}.
 \end{proof}
 
-The last proposition allows us to consider only the case of the \ref{DLP} problem to solve \ref{LP}.
+\Cref{solsLP} allows us to reduce \eqref{LP} to diagonal linear programs.
+
 \begin{proposition}\label{prop:reduc}
+  Let $(A,b,c), (S,b',c') \in \allmat_{m,n}(K) \times K^m \times K^n$ be as in \Cref{solsLP}, where
+  $S=SNF(A)$. Then
   \begin{enumerate}
-		\item \ref{DLP} have feasible solutions if and only if the $m-r$ last coefficients of $b'$ have nonegative valuation, for $r$ the rank of $S$.
-		\item If at least one of the $n-r$ last coefficients of $c'$ is non-zero, if \ref{DLP} admits feasible solutions it is unbounded and does not have a solution.
-
+  \item \label{prop:reduc_it1}
+    \eqref{LP} with data $(S,b',c')$ is feasible if and only if the $m-r$ last coefficients
+    of $b'$ have nonnegative valuation, for $r = \text{rank}\,S$.
+  \item \label{prop:reduc_it2}
+    Assume at least one of the $n-r$ last coefficients of $c'$ is non-zero. If \eqref{LP} with
+    data $(S,b',c')$ is feasible, then it is unbounded and does not admit solutions.
   \end{enumerate}
 \end{proposition}
+\begin{proof}
+  %%%%\corentin{préciser les notations}. 
+  A vector $y = (y_1, \ldots, y_n)^T \in K^n$ is feasible for \eqref{LP} with data $(S,b',c')$
+  if and only if $\val(s_i y_i + b_i) \geq 0$ for all $i = 1,\ldots,n$.
+  However $s_i = 0$ for $n-r \leq i\leq n$. Therefore, if \eqref{LP} with data $(S,b',c')$ is feasible,
+  necessarily the $m-r$ last coefficients of $b'$ have nonnegative valuation.
+  Conversely, if the $m-r$ last coefficients of $b'$ are zero, the vector $y \in K^n$ such that
+  $y_i = -\frac{-b'_i}{s_i}$ if $1 \leq i \leq r$, and $y_i =0$ otherwise, is feasible for \eqref{LP}
+  with data $(S,b',c')$.
 
-\begin{proof}
-  A vector $y =  \left[\begin{smallmatrix} y_1 \\ \vdots \\ y_n \end{smallmatrix}\right] \in K^n$ is feasible solution of \ref{DLP} if and only if $\val(s_i y_i + b_i) >=0$ for all $i = 1...n$ \corentin{préciser les notations}.
-  However, $s_i =0$ for $n-r \leq i\leq n$. Therefore, \ref{DLP} have solution only if the $m-r$ last coefficient of b' have nonnegative valuation.
-
-  Conversely, if the $m-r$ last coefficient of $b'$ are zero, the vector $y \in K^n$ such that $y_i = -\frac{-b'_i}{s_i}$ if $1 \leq i \leq r$ and $y_i =0$ otherwise is a feasible solution.
-
-  Finally, let $y^*$ be a feasible solution of \ref{DLP}.
-Let us suppose there exists $r+1 \leq i \leq m$ such that $c'_i \neq  0$ and fix such $i$.
-Let us then consider the vector $e^i$ whose only non-zero coefficient is the $i-$th, which is $1$.
-Then $y^*+\alpha e^i$ is a feasible solution for all $\alpha \in K$ and $\langle c', y^* + \alpha e^i\rangle = \langle c' , y^* \rangle + \alpha c'_i$.
-In particular, for $\alpha = -\frac{\langle c', y^* \rangle}{c'_i}$, $\val \left( \langle c', y^* + \alpha e ^i \rangle\right) = \val (0) = + \infty$.
+  Concerning \Cref{prop:reduc_it2}, let $y^*$ be feasible for \eqref{LP} with data $(S,b',c')$.
+  Let $i$ be such that $r+1 \leq i \leq n$ and $c'_i \neq 0$. Consider the vector $e^i$ whose only non-zero
+  coefficient is the $i-$th, which is $1$. Then $y^* + \alpha e^i$ is feasible for \eqref{LP} with data $(S,b',c')$,
+  for all $\alpha \in K$ and $\langle c', y^* + \alpha e^i\rangle = \langle c' , y^* \rangle + \alpha c'_i$.
+  In particular, for $\alpha = -\frac{\langle c', y^* \rangle}{c'_i}$, one has $\val \left( \langle c', y^* +
+  \alpha e ^i \rangle\right) = \val (0) = + \infty$. ({\color{blue} je ne comprends pas: il est non-borné
+    supérieurement, mais nous on cherche l'inf..., donc comment montrer qu'il n'y a pas de solutions ? il faudrait
+  une sequence avec limite valuation $-\infty$})
 \end{proof}
 
-From now on, we will only consider the iterations of \ref{DLP} which have solutions, by \ref{prop:reduc}, we can then reduce the problem by only taking acount only the $r$ first coefficients of $y, b', c'$ and the submatrix of $S$ made with only $r$ first lines et columns of and whose coefficients are exactly the nonzero invariants factors.
-The set $Adm$ of the feasible solutions can then be written as the set of vectors $y \in K^n$ that verifies $ \ s_i y_i + b'_i \in \OK$ for $i=1,...,r$ {\it i.e.} $Adm = \left\{\left[\begin{smallmatrix} y_1\\ \vdots\\ y_n \end{smallmatrix}\right] \in K^n :\ y_i \in -\frac{b`_i}{s_i} + \frac{1}{s_i} \OK, 1\le i\le r\right\}$.
+From now on, we will only consider iterations of diagonal linear programs which have solutions.
+By \Cref{prop:reduc} we can then reduce the problem by only taking account the first $r$ coefficients of
+$y, b', c'$ and the submatrix of $S$ made with only by the $r$ first rows and columns and whose coefficients
+are exactly the nonzero invariants factors.
 
-Resolving \ref{DLP} consists (by definition) in minimizing $y \mapsto \val\left(\left<c',y \right>\right)$ over $Adm$.
-The image of $Adm$ by $y \mapsto \left<c',y \right>$ is $\sum_{i=1}^r -c'_i.\frac{b'_i}{s_i} + \sum_{i=1}^r\left( \frac{c'_i}{s_{i}} \OK \right)$ which can be expressed as $\left<c',Adm \right> = \lambda + \pi^{v} \OK$ with $\lambda = \sum_{i=1}^r -c'_i.\frac{b'_i}{s_i}$ and $v = \min\limits_{1\le i\le r} \val \frac{c'_{i}}{s_{i}} $.
-Finally, two cases can occur depending on $v$ and the valuation of $\lambda$.
-If $\val( \lambda) < v$ the minimum of $y\mapsto \val\left(\left<c',y \right>\right)$ over $Adm$ is reached in any point of $Adm$ and is equal to $\val\left( \lambda\right)$.
-Whereas, if $\val\left( \lambda \right) \ge v$ then $\lambda \in \pi^{v} \OK$ and the minimum is $v $ and is reached in any points $y$ of $Adm$ that verifies
+The feasible set $\PP' = \{y \in K^n : Sy+b' \geq 0\}$ of the diagonal LP can be written as the set of vectors
+$y \in K^n$ that verifies $s_i y_i + b'_i \in \OK$ for $i=1,...,r$ {\it i.e.}:
+$$
+\PP' = \left\{\left[\begin{smallmatrix} y_1\\ \vdots\\ y_n \end{smallmatrix}\right] \in K^n :
+y_i \in -\frac{b`_i}{s_i} + \frac{1}{s_i} \OK, 1\le i\le r\right\}.
+$$
+
+Solving the diagonal LP consists (by definition) in minimizing the linear map $y \mapsto \val\left(\left\langle
+c',y \right\rangle\right)$ over $\PP'$. The image of $\PP'$ by $y \mapsto \left\langle c',y \right\rangle$ is
+$$
+\left\langle c',\PP' \right\rangle = \sum_{i=1}^r -c'_i \frac{b'_i}{s_i} + \sum_{i=1}^r\left( \frac{c'_i}{s_{i}} \OK \right) = \lambda + \pi^{v} \OK
+$$
+where $\lambda = \sum_{i=1}^r -c'_i \frac{b'_i}{s_i}$ and $v = \min\limits_{1\le i\le r} \val \frac{c'_{i}}{s_{i}} $.
+Finally, two cases can occur depending on $v$ and the valuation of $\lambda$:
+\begin{enumerate}
+\item
+  If $\val(\lambda) < v$, the minimum of $y\mapsto \val\left(\left\langle c',y \right\rangle\right)$ over $\PP'$
+  is reached at any point of $\PP'$, and is equal to $\val(\lambda)$.
+\item
+  If $\val(\lambda) \ge v$, then $\lambda \in \pi^{v} \OK$ and the minimum is $v$ and is reached at any points $y$
+  of $\PP'$ that verifies 
   \[\val \underset{ \begin{array}{c} 1\le i\le r\\ \val\left(c'_{i}/{s_{i}} \right) = v  \end{array}}{\sum} y_{i} = 0. \]
+\end{enumerate}
 

### 2024-11-08 article/paper_padic_spec.tex
feasible LP
commit by Simone

@@
   $$
-  where ${\bf 0}_{\min(m,n)-r}$ is a null square matrix of size $\min(m,n)-r$.
+  where ${\bf 0}_{t}$ is a null square matrix of size $t$.
   The matrix $SNF(M)$ is called the \emph{Smith Normal Form (SNF)} of $M$, and the elements $\pi^{a_i}$ the
@@
 \begin{bmatrix} y_1 \\ y_2 \end{bmatrix} \in \R^2, \,
+\diag\left(
 \begin{bmatrix}
@@
   y_2 & 1-y_1
-\end{bmatrix}
-\bigoplus
+\end{bmatrix},
 \begin{bmatrix}
@@
   x_1 & y_1
-\end{bmatrix}
-\bigoplus
+\end{bmatrix},
 \begin{bmatrix}
@@
 \end{bmatrix}
+\right)
 \succeq 0
@@
 \end{equation*}
-A vector $x \in K^n$ is called \emph{feasible} for \eqref{LP} if $x \in \PP$. A feasible vector $x^* \in \PP$
+A vector $x \in K^n$ is called \emph{feasible} for \eqref{LP} if $x \in \PP$ and the program \eqref{LP} is
+called \emph{feasible} if $\PP \neq \emptyset$. A feasible vector $x^* \in \PP$
 is called a \emph{solution} to \eqref{LP} if $p^* = \left\langle c,x^*\right\rangle$.

### 2024-11-08 article/paper_padic_spec.tex
commit by Simone
modif thm 4.1

@@
 
+Recall that the {\it Newton polygon} $\mathcal{P}$ of a polynomial $P = \sum_{i=0}^{n} a_i T^i \in K[T]$ is
+defined as the inferior convex hull of the set $\{(i, \val a_i) \,|\, i\in \{0,...,d\} \}$, {\it i.e.} the
+graph of the greatest convex function $\mathcal{P} : [0,n] \to \R$ such that $\mathcal{P}(i) \leq \val a_i$
+for $i=1,...,n$. This function is piecewise affine and its slopes are exactly the opposites of the valuations
+of the roots of $P$.
+  %%%These are all the results we will need for this proof.
+
 \begin{theorem}
@@
   Let $M \in \allmat_{d,d}(K)$ with characteristic polynomial $\chi_M = T^d + \sum_{i=0}^{d-1} a_i T^i$ for $a_0,...,a_{d-1} \in K$.
-  Firstly, suppose   $M \not \in \allmat_{d,d}^+(K)$ {\it i.e.} $\chi_M$ have a root $\rho$ of negative valuation.
-  It follows that $\val \chi_M (\rho) = \val (\rho^d+ \sum_{i=0}^{d-1} a_i \rho^i ) = + \infty$ and $\val \rho^d = d \val \rho <0$.
-  The properties of the non-archimedean inequality followed by $\val $ implie that $\val ( \sum_{i=0}^{d-1} a_i \rho^i) = \val \rho^d$ and $\val ( \sum_{i=0}^{d-1} a_i \rho^i) \ge \min_{i=0,..., d-1} \val \left(a_i \rho^i\right)$.
-Therefore, there exists $i \in \left\{0,...,d-1\right\}$ such that $\val( a_i \rho^i) \le \val\rho^d$ {\it i.e.} such that $\val (a_i) \le (d-i) \val \rho <0$.
-That is all the results we need to prove the result.
+  Firstly, suppose $M \not \in \allmat_{d,d}^+(K)$, {\it i.e.} $\chi_M$ has a root $\rho$ with $\val\,\rho<0$.
+  It follows that
+  $$
+  \val \chi_M (\rho) = \val \left(\rho^d+ \sum_{i=0}^{d-1} a_i \rho^i\right) = + \infty
+  $$ and $\val \rho^d = d \val \rho <0$.
+  The properties of the non-archimedean inequality and of the valuation imply that
+  $$
+  \min_{0 \leq i \leq d-1} \val \left(a_i \rho^i\right) \leq \val\left(\sum_{i=0}^{d-1} a_i \rho^i\right) = \val \rho^d
+  $$
+  %%%$\val ( \sum_{i=0}^{d-1} a_i \rho^i) = \val \rho^d$ and $\val ( \sum_{i=0}^{d-1} a_i \rho^i) \ge \min_{i=0,..., d-1} \val \left(a_i \rho^i\right)$.
+  Therefore, there exists $j \in \left\{0,...,d-1\right\}$ such that $\val(a_j \rho^j) \le \val\rho^d$,
+  {\it i.e.} such that $\val a_j \le (d-j) \val \rho <0$. This shows that $\chi_M \not\in \OK[T]$.
 
-  We have proven the converse sense of the equivalence.
-To prove the direct sense a brief introduction to Newton's polygon will be needed, we will only state the results we use in this proof and will redirect to \cite{gouvea_p-adic_2003} to further explanations.
-  The Newton polygon $\mathcal{P}$ of a polynomial $P = \sum_{n}^{i=0} a_i T^i \in K[T]$ is defined as the inferior convex hull of the set $\{(i, \val a_i ) | i\in \{0,...,d\} \}$ {\it i.e.} the largest convex function $\mathcal{P} : [0,n] \to \R$ such that $\mathcal{P}(i) \leq \val a_i$ for $i=1,...,n$.
-  This function is piecewise affine and its slopes are exactly the opposites of the valuations of the roots of $P$. These are all the results we will need for this proof.
+  %%We have proven the converse sense of the equivalence.
+  %%To prove the direct sense a brief introduction to Newton's polygon will be needed, we will only state the results we use in this proof and will redirect to \cite{gouvea_p-adic_2003} to further explanations.
 
-  Suppose $\chi_M \not\in \OK[T]$.
-There exists $j \in \{0,...,d-1\}$ such that $\val (a_j)<0$.
-The polynomial $\chi_M$ being monic the point with abscissa $n$ of $\chi_M$'s Newton's Polygon is $(n,0)$.
-  Therefore, the point $(j, \val a_j)$ having negative ordinate implies that at least one of the slopes of $\chi_M$'s Newton's Polygon is positive so that $\chi_M$ has a root with negative valuation.
+  Suppose now $\chi_M \not\in \OK[T]$.
+There exists $j \in \{0,...,d-1\}$ such that $\val a_j <0$.
+The polynomial $\chi_M$ being monic, the point with abscissa $n$ of the Newton polygon of $\chi_M$ is $(n,0)$.
+  Therefore, the point $(j, \val a_j)$ having negative ordinate implies that at least one of the slopes of
+  the Newton polygon of $\chi_M$ is positive, so that $\chi_M$ has a root with negative valuation.
 \end{proof}

### 2024-11-11 article/paper_padic_spec.tex
tentative title abstract

@@
 
-\title{\bf Title}
+%\title{\bf Title}
+%\title{\bf On polyhedra and spectrahedra over valuation fields}
+\title{\bf On semidefinite-representable sets over valuation fields}
 
@@
 \begin{abstract}
+  \noindent
+  Real polyhedra and real spectrahedra are respectively the feasible sets of linear programming
+  (LP) and semidefinite programming (SDP). This paper investigates versions of these sets and of
+  the related optimization problems with data over a field $K$ with valuation.
+  We showcase examples of non-polyhedral $K$-spectrahedra and of sets that are semidefinite
+  representable over $K$ but are not $K$-spectrahedra.
 \end{abstract}
@@
 
-\subsection{Context and motivations}
-
+%\subsection{Context and motivations}
 %Il faudra entre autre mentionner (et peut être motiver l'approche p-adique) :
@@
 %\end{itemize}
+%\subsection{Main results}
 
-\subsection{Main results}
-
-\newpage
+%\newpage
 \section{Preliminaries}
@@
 \begin{definition}
-  We call a matrix $M \in \allmat_{d,d}(K)$ \emph{positive semidefinite} (in symbols $M \succeq 0$)
+  We say that a matrix $M \in \allmat_{d,d}(K)$ is \emph{positive semidefinite} (in symbols $M \succeq 0$)
   if all its eigenvalues have nonnegative valuation in an algebraic closure of $K$.

### 2024-11-11 article/paper_padic_spec.tex
commit by Simone

@@
 \begin{definition}
-  We say that a matrix $M \in \allmat_{d,d}(K)$ is \emph{positive semidefinite} (in symbols $M \succeq 0$)
+  We say that a matrix $M \in \allmat_{d,d}(K)$ is \emph{positive semidefinite} ($M \succeq 0$)
   if all its eigenvalues have nonnegative valuation in an algebraic closure of $K$.
@@
 
+Testing positive semidefiniteness reduces to checking the coefficients of $\chi_M$.
 \begin{theorem}
@@
   Both senses of the equivalence will be proven by contraposition.
-
   Let $M \in \allmat_{d,d}(K)$ with characteristic polynomial $\chi_M = T^d + \sum_{i=0}^{d-1} a_i T^i$ for $a_0,...,a_{d-1} \in K$.

### 2024-11-11 article/paper_padic_spec.tex
commit by Simone

@@
 
-\newenvironment{proof}{\hbox{}\vspace{-0.8cm} {\bf Proof:}}{\hfill $\Box$}
+%%%\newenvironment{proof}{\hbox{}\vspace{-0.8cm} {\bf Proof:}}{\hfill $\Box$ \vspace{0.2cm}}
 
 \usepackage{amsmath}
+\usepackage{amsthm}
 \usepackage{amssymb}
@@
 \hoffset-12.5mm
-\parindent0cm
-\parskip2mm
+\parindent0.8cm
+\parskip0mm
 
@@
 %\title{\bf On polyhedra and spectrahedra over valuation fields}
-\title{\bf On semidefinite-representable sets over valuation fields}
+\title{\bf On semidefinite representable sets over valuation fields}
 
@@
   \noindent
-  Real polyhedra and real spectrahedra are respectively the feasible sets of linear programming
-  (LP) and semidefinite programming (SDP). This paper investigates versions of these sets and of
+  Real polyhedra and real spectrahedra (or their projections) are respectively the feasible sets
+  of linear programming (LP) and semidefinite programming (SDP). 
+  This paper investigates versions of these sets and of
   the related optimization problems with data over a field $K$ with valuation.
@@
 
-\subsection{Definition}
+\subsection{Positive semidefinite matrices}
 %\newcommand\mat{postive semidefinite matrix } 
@@
 
-Recall that the {\it Newton polygon} $\mathcal{P}$ of a polynomial $P = \sum_{i=0}^{n} a_i T^i \in K[T]$ is
-defined as the inferior convex hull of the set $\{(i, \val a_i) \,|\, i\in \{0,...,d\} \}$, {\it i.e.} the
-graph of the greatest convex function $\mathcal{P} : [0,n] \to \R$ such that $\mathcal{P}(i) \leq \val a_i$
-for $i=1,...,n$. This function is piecewise affine and its slopes are exactly the opposites of the valuations
+Recall that the {\it Newton polygon} $\mathcal{P}$ of a polynomial $P = \sum_{i=0}^{d} a_i T^i \in K[T]$ is
+defined as the inferior convex hull of the set $\{(i, \val a_i) \,|\, 0 \le i \le d\}$, {\it i.e.} the
+graph of the greatest convex function $\mathcal{P} : [0,d] \to \R$ such that $\mathcal{P}(i) \leq \val a_i$
+for $i=1,\ldots,d$. This function is piecewise affine and its slopes are exactly the opposites of the valuations
 of the roots of $P$.
-  %%%These are all the results we will need for this proof.
 
-Testing positive semidefiniteness reduces to checking the coefficients of $\chi_M$.
+The following result shows that testing positive semidefiniteness of matrices over
+valuation fields reduces to checking whether the coefficients of $\chi_M$ are integers.
+
 \begin{theorem}
@@
   Let $M \in \allmat_{d,d}(K)$ with characteristic polynomial $\chi_M = T^d + \sum_{i=0}^{d-1} a_i T^i$ for $a_0,...,a_{d-1} \in K$.
-  Firstly, suppose $M \not \in \allmat_{d,d}^+(K)$, {\it i.e.} $\chi_M$ has a root $\rho$ with $\val\,\rho<0$.
+  First suppose $M \not \in \allmat_{d,d}^+(K)$, thus $\chi_M$ has a root $\rho$ with $\val\,\rho<0$.
   It follows that
   $$
-  \val \chi_M (\rho) = \val \left(\rho^d+ \sum_{i=0}^{d-1} a_i \rho^i\right) = + \infty
+  + \infty = \val \chi_M (\rho) = \val \left(\rho^d+ \sum_{i=0}^{d-1} a_i \rho^i\right)
   $$ and $\val \rho^d = d \val \rho <0$.
@@
   $$
-  \min_{0 \leq i \leq d-1} \val \left(a_i \rho^i\right) \leq \val\left(\sum_{i=0}^{d-1} a_i \rho^i\right) = \val \rho^d
+  0> \val \rho^d = \val\left(\sum_{i=0}^{d-1} a_i \rho^i\right) \geq
+  \min_{0 \leq i \leq d-1} \val \left(a_i \rho^i\right)
   $$
@@
 
-  Suppose now $\chi_M \not\in \OK[T]$.
-There exists $j \in \{0,...,d-1\}$ such that $\val a_j <0$.
-The polynomial $\chi_M$ being monic, the point with abscissa $n$ of the Newton polygon of $\chi_M$ is $(n,0)$.
+  Suppose now $\chi_M \not\in \OK[T]$. There exists $j \in \{0,...,d-1\}$ such that $\val a_j <0$.
+  The polynomial $\chi_M$ being monic, the point with abscissa $d$ of the Newton polygon of $\chi_M$ is
+  $(d,\val(1)) = (d,0)$. 
   Therefore, the point $(j, \val a_j)$ having negative ordinate implies that at least one of the slopes of
@@
 \end{proof}
+
+As a consequence, matrices with integer coefficients are positive semidefinite.
 
@@
 
+The reverse inclusion of \Cref{cor_caracsdp} is false in general as we show in the next example.
+
 \begin{example}
-  The reverse inclusion of \Cref{cor_caracsdp} is false in general. For instance the characteristic polynomial of
-  $M = \left(\begin{smallmatrix} 5 + {3}/{5} & {4}/{5} \\ {4}/{5} & -{3}/{5} \end{smallmatrix}\right)$ is $\chi_M = T^2-5T-4$.
+  Let
+  $$
+  M = \begin{pmatrix} 5 + \frac{3}{5} & \frac{4}{5} \\ \frac{4}{5} & -\frac{3}{5} \end{pmatrix}.
+  $$
+  The characteristic polynomial of $M$
+  is $\chi_M = T^2-5T-4$.
 However when seen as a matrix over $K=\mathbb{Q}_5$, then $\chi_M \in \mathbb{Z}_5[T] = \OK[T]$: then $M \in \allmat_{2,2}^+(\mathbb{Q}_5)$, nevertheless $M \not\in \allmat_{2,2}(\mathbb{Z}_5)$, hence $\allmat_{2,2}^+(\mathbb{Q}_5) \not\subset \allmat_{2,2}(\mathbb{Z}_5)$.
@@
 \begin{proposition}
+  {\color{blue} [Peut être une hypothèse à rajouter, par exemple $K$ à valuation discrete]}
   The set $\allmat_{d,d}^+(K)$ is both open and closed.
@@
 \begin{definition}
-  A \emph{cone} is subset $C$ of $K^d$ that is closed under multiplication by elements of $\OK$.   
+  A \emph{cone} of $K^d$ is a subset that is closed under multiplication by elements of $\OK$.   
 \end{definition}
@@
 \end{proof}
+
+\subsection{Definition of spectrahedra}
 
@@
 
-\subsection{Polyhedrality}
-Cf. \cite{bhardwaj2015deciding}
+%\subsection{Polyhedrality}
+%Cf. \cite{bhardwaj2015deciding}
 
-\section{Linear matrix inequalities}
+%\section{Linear matrix inequalities}
 
-\section{Other questions}
-\begin{itemize}
-\item The projection of a real polyhedron is a real polyhedron (thanks to Fourier-Motzkin elimination procedure). Is it the same for $K$-polyhedra?
-\item Annuli are semidefinite representable, we should remark/prove that they are not spectrahedra.
-\end{itemize}
+%\section{Other questions}
+%\begin{itemize}
+%\item The projection of a real polyhedron is a real polyhedron (thanks to Fourier-Motzkin elimination procedure). Is it the same for $K$-polyhedra?
+%\item Annuli are semidefinite representable, we should remark/prove that they are not spectrahedra.
+%\end{itemize}
+
+\section*{Acknowledgments}
+
+The second author acknowledges support from the ANR Project ``HYPERSPACE'' (ANR-21-CE48-0006-01).
 

### 2024-11-11 article/paper_padic_spec.tex
changed notation matrices

@@
 with coefficients in $K$ is denoted by $K[x]_{d}$. The vector space of matrices of
-size $p \times q$ with entries in $K$ is $\allmat_{p,q}(K)$ and the general
-linear group in $\allmat_{n,n}(K)$ is $\GL_n(K)$.
+size $p \times q$ with entries in a ring $R$ is $R^{p \times q}$ and the general
+linear group in $R^{n \times n}$ is $\GL_n(R)$.
 For the sake
@@
 \begin{definition}[Smith Normal Form]\label{smith_nf}
-  Let $M \in \allmat_{m,n}(K)$ be of rank $r$. There exist unique integers $a_1 \leq \cdots \leq a_r$, and
+  Let $M \in K^{m \times n}$ be of rank $r$. There exist unique integers $a_1 \leq \cdots \leq a_r$, and
   matrices $P \in \GL_n(\OK)$ and $Q \in \GL_m(\OK)$, such that
@@
   The valuation of the first invariant factor of $SNF(M)$ of a matrix
-  $M \in \allmat_{n,n}(K)$ is the minimum of the valuations of the entries of
-  $M$. In particular, $SNF(M) \in \allmat_{n,n}(\OK)$.
+  $M \in K^{n \times n}$ is the minimum of the valuations of the entries of
+  $M$. In particular, $SNF(M) \in \OK^{n \times n}$.
 \end{remark}
@@
 
-Let $\sym_d(\R) \subset \allmat_{d,d}(\R)$ be the vector space of $d \times d$ real symmetric
+Let $\sym_d(\R) \subset \R^{d\times d}$ be the vector space of $d \times d$ real symmetric
 matrices. A matrix $M \in \sym_d(\R)$
@@
 Let $A_0,A_1,\ldots,A_n \in \sym_d(\R)$, and let $\calL = A_0+\span{A_1,\ldots,A_n}$ be the affine space
-containing $A_0$ and with direction the vector space spanned by $A_1,\ldots,A_n$ (which we assume linearly
-independent). The intersection $\calL \cap \sym_d^+(\R) = \left\{A(x) := A_0+\sum_i x_i A_i \in \sym_d(\R) :
-A(x) \succeq 0\right\}$, or
-equivalently, its pre-image $S = \{x \in \R^n : A(x) \succeq 0\}$ under the map $x \mapsto A(x)$, is called
+containing $A_0$ and with direction the vector space spanned by $A_1,\ldots,A_n$ (which we might assume
+to be linearly independent). The intersection
+$$
+\calL \cap \sym_d^+(\R) = \left\{A(x) := A_0+\sum_i x_i A_i \in \sym_d(\R) :
+A(x) \succeq 0\right\},
+$$
+or equivalently, its pre-image $S = \{x \in \R^n : A(x) \succeq 0\}$ under the map $x \mapsto A(x)$, is called
 a \emph{real spectrahedron}. As (linear preimage of) affine sections of $\sym_d^+(\R)$, real spectrahedra
@@
 finite set $I \subset \N$ and $l_i \in K[x]_1$, for $i \in I$ ({\color{blue} mettre aussi les égalités dans $\PP$}).
-We further assume that $\PP \neq \emptyset$, and we identify $f$ with its matrix in $\allmat_{n,n}(K)$.
+We further assume that $\PP \neq \emptyset$, and we identify $f$ with its matrix in $K^{n \times n}$.
 
@@
 with $P \in \GL_n(\OK),$ $Q \in \GL_m(\OK)$
-and $\Delta = SNF(f)\in \allmat_{m,n}(K)$ of the form $\diag(\lambda_1, \ldots, \lambda_r, {\bf 0}_{\min(m,n)-r})$
+and $\Delta = SNF(f)\in K^{m \times n}$ of the form $\diag(\lambda_1, \ldots, \lambda_r, {\bf 0}_{\min(m,n)-r})$
   where ${\bf 0}_{\min(m,n)-r}$ is a null square matrix of size $\min(m,n)-r$ for $\lambda_1,\dots,\lambda_r$ non-zero and $r \in \N.$
@@
 with $P \in \GL_n(\OK),$ $Q \in \GL_m(\OK)$
-and $\Delta \in \allmat_{n,m}(K)$,
+and $\Delta \in K^{m \times n}$,
 then
@@
 \end{equation}
-with $c \in K^n$ a fixed vector of size $n$ that represents the cost, $A \in \allmat_{m,n}(K)$, $b \in K^m$,
+with $c \in K^n$ a fixed vector of size $n$ that represents the cost, $A \in K^{m \times n}$, $b \in K^m$,
 and $\left\langle c, x \right\rangle := c_1x_1+\cdots +c_nx_n$. When $A$ is a diagonal matrix, we often
@@
 The most interesting aspect of the SNF regarding the resolution of \eqref{LP} is that the transition matrices are
-invertible in $\OK$, thus they preserve inequalities: indeed, if $z \in K^n$ and $M \in \allmat_n(\OK)$ such
+invertible in $\OK$, thus they preserve inequalities: indeed, if $z \in K^n$ and $M \in \OK^{n \times n}$ such
 that $z \geq 0$, then $Mz \geq 0$.
 The latter property is a direct consequence of $\OK$ being a ring and the converse holds if the matrix $M$ is
-invertible in $\OK$. Therefore, for all matrix $M \in \allmat_{n,n}(K)$ with $S=SNF(M)$ and for all $z \in K^n$,
+invertible in $\OK$. Therefore, for all matrix $M \in K^{n \times n}$ with $S=SNF(M)$ and for all $z \in K^n$,
 then $Mz \geq 0$ if and only if $Sz \geq 0$.
@@
 \begin{proposition} \label{solsLP}
-  Let $A \in \allmat_{m,n}(K), b \in K^m, c\in K^n$ and let $S = SNF(A) = QAP^{-1} \in \allmat_{m,n}(K)$, with
+  Let $A \in K^{m\times n}, b \in K^m, c\in K^n$ and let $S = SNF(A) = QAP^{-1} \in K^{m \times n}$, with
   transition matrices $P \in \GL_n(\OK)$ and $Q\in \GL_m(\OK)$. Define $b' = Qb$ and $c' = (P^{-1})^Tc$.
@@
 \begin{proposition}\label{prop:reduc}
-  Let $(A,b,c), (S,b',c') \in \allmat_{m,n}(K) \times K^m \times K^n$ be as in \Cref{solsLP}, where
+  Let $(A,b,c), (S,b',c') \in K^{m \times n} \times K^m \times K^n$ be as in \Cref{solsLP}, where
   $S=SNF(A)$. Then
@@
 \begin{definition}
-  We say that a matrix $M \in \allmat_{d,d}(K)$ is \emph{positive semidefinite} ($M \succeq 0$)
+  We say that a matrix $M \in K^{d \times d}$ is \emph{positive semidefinite} ($M \succeq 0$)
   if all its eigenvalues have nonnegative valuation in an algebraic closure of $K$.
-  We denote by $\allmat_{d,d}^+(K) \subset \allmat_{d,d}(K)$ the set of positive semidefinite matrices.
-  The characteristic polynomial of a matrix $M \in \allmat_{d,d}(K)$ is denoted $\chi_M \in K[T]$.
+  We denote by $K^{d \times d}_+ \subset K^{d\times d}$ the set of positive semidefinite matrices.
+  The characteristic polynomial of a matrix $M \in K^{d\times d}$ is denoted $\chi_M \in K[T]$.
 \end{definition}
@@
   \label{caracsdp}
-  $M \in \allmat_{d,d}^+(K)$ if and only if $\chi_M \in \OK[T]$.
+  $M \in K^{d\times d}_+$ if and only if $\chi_M \in \OK[T]$.
 \end{theorem}
@@
   Both senses of the equivalence will be proven by contraposition.
-  Let $M \in \allmat_{d,d}(K)$ with characteristic polynomial $\chi_M = T^d + \sum_{i=0}^{d-1} a_i T^i$ for $a_0,...,a_{d-1} \in K$.
-  First suppose $M \not \in \allmat_{d,d}^+(K)$, thus $\chi_M$ has a root $\rho$ with $\val\,\rho<0$.
+  Let $M \in K^{d\times d}$ with characteristic polynomial $\chi_M = T^d + \sum_{i=0}^{d-1} a_i T^i$ for $a_0,...,a_{d-1} \in K$.
+  First suppose $M \not \in K^{d\times d}_+$, thus $\chi_M$ has a root $\rho$ with $\val\,\rho<0$.
   It follows that
@@
 \begin{corollary}\label{cor_caracsdp}
-  $\allmat_{d,d}(\OK) \subset \allmat_{d,d}^+(K)$.
+  $\OK^{d\times d} \subset K^{d\times d}_+$.
 \end{corollary}
 \begin{proof}
-  $\OK$ is a ring therefore if $M \in \allmat_{d,d}(\OK)$, then $\chi_M \in \OK[T]$, thus we conclude
-  by \Cref{caracsdp}.
+  $\OK$ is a ring, therefore if $M \in \OK^{d \times d}$, then $\chi_M \in \OK[T]$.
 \end{proof}
@@
   $$
-  M = \begin{pmatrix} 5 + \frac{3}{5} & \frac{4}{5} \\ \frac{4}{5} & -\frac{3}{5} \end{pmatrix}.
+  M = \begin{bmatrix} 5 + \frac{3}{5} & \frac{4}{5} \\ \frac{4}{5} & -\frac{3}{5} \end{bmatrix}.
   $$
@@
   is $\chi_M = T^2-5T-4$.
-However when seen as a matrix over $K=\mathbb{Q}_5$, then $\chi_M \in \mathbb{Z}_5[T] = \OK[T]$: then $M \in \allmat_{2,2}^+(\mathbb{Q}_5)$, nevertheless $M \not\in \allmat_{2,2}(\mathbb{Z}_5)$, hence $\allmat_{2,2}^+(\mathbb{Q}_5) \not\subset \allmat_{2,2}(\mathbb{Z}_5)$.
+However when seen as a matrix over $K=\mathbb{Q}_5$, then $\chi_M \in \mathbb{Z}_5[T] = \OK[T]$: then $M \in (\mathbb{Q}_5)^{2 \times 2}_+$, nevertheless $M \not\in (\mathbb{Z}_5)^{2\times 2}$, hence
+  $(\mathbb{Q}_5)^{2 \times 2}_+ \not\subset (\mathbb{Z}_5)^{2 \times 2}$.
 \end{example}
@@
   {\color{blue} [Peut être une hypothèse à rajouter, par exemple $K$ à valuation discrete]}
-  The set $\allmat_{d,d}^+(K)$ is both open and closed.
+  The set $K^{d \times d}_+$ is both open and closed.
 \end{proposition}
@@
 $\OK$ is indeed the open unit ball for $\|\cdot \|_\infty$ that induces a discrete distance for which open balls are also closed sets.
-Furthermore, $\allmat^+_{d,d}(K) = \chi^{-1}(\OK[X]) $ where $\chi$ is the function that maps a matrix to its characteristic polynomial which is continuous.
+Furthermore, $K^{d\times d}_+ = \chi^{-1}(\OK[X]) $ where $\chi$ is the function that maps a matrix to its characteristic polynomial which is continuous.
 \end{proof}
@@
 \begin{proposition}
-  The set $\allmat^+_{d,d}(K)$ is a cone.
+  The set $K^{d \times d}_+$ is a cone.
 \end{proposition}
 \begin{proof}
-  The result is immediate following the definiton of $\allmat^+_{d,d}(K)$.
+  The result is immediate following the definiton of $K^{d \times d}_+$.
 \end{proof}
@@
   \label{def_spectrahedra}
-  Let $\mathcal{L} = A_0+\span{A_1,\ldots,A_n} \subset \allmat_{d,d}(K)$ be an affine space, for some
-  $A_0,A_1,\ldots,A_n \in \allmat_{d,d}(K)$.
-  The set $\mathcal{L} \cap \allmat_{d,d}^+(K)$ is called a \emph{spectrahedron}. The set 
-  $S_A = \{x \in K^n : A_0+x_1A_1+\cdots+x_nA_n \succeq 0\}$, that is the preimage of $\allmat_{d,d}^+(K)$
-  under the map $x \mapsto A_0+x_1A_1+\cdots+x_nA_n$, is also called spectrahedron.
+  A \emph{spectrahedron in $K^{d\times d}$} is a set of the form
+  $\mathcal{S} = \mathcal{L} \cap K^{d\times d}_+$,
+  where $\mathcal{L} = A_0+\span{A_1,\ldots,A_n} \subset K^{d \times d}$ is an affine space, for some
+  $A_0,A_1,\ldots,A_n \in K^{d\times d}$.
 \end{definition}
@@
 \begin{remark}
+  As in the real case, one often abuses of notation, saying that the preimage
+  $S = \varphi^{-1}(K^{d \times d}_+) = \{x \in K^n : A_0+x_1A_1+\cdots+x_nA_n \succeq 0\}$
+  of $K^{d \times d}_+$ under the map $\varphi(x) = A_0+x_1A_1+\cdots+x_nA_n$, is a \emph{spectrahedron
+  in $K^n$}.
+\end{remark}
+
+\begin{remark}
   The class of spectrahedra is closed under intersection. Indeed, for affine spaces $\mathcal{L}_1,\mathcal{L}_2$
-  one has $(\mathcal{L}_1 \cap \allmat_{d,d}^+(K)) \cap (\mathcal{L}_2 \cap \allmat_{d,d}^+(K)) =
-  (\mathcal{L}_1 \cap \mathcal{L}_2) \cap \allmat_{d,d}^+(K)$. Now
+  one has $(\mathcal{L}_1 \cap K^{d \times d}_+) \cap (\mathcal{L}_2 \cap K^{d \times d}_+) =
+  (\mathcal{L}_1 \cap \mathcal{L}_2) \cap K^{d \times d}_+$. Now
   assuming $\mathcal{L}_1 = A_0+\span{A_1,\ldots,A_n}$ and $\mathcal{L}_2 = B_0+\span{B_1,\ldots,B_n}$,
@@
   and $L = \{x \in K^n : \val(m_j) = +\infty, j=1,\ldots,e\}$.
-  First, denote by $A(x) = \ell_1 \oplus \cdots \oplus \ell_d \in \allmat_{d,d}(K[x]_1)$,
-  so that $A(x) = A_0+x_1A_1+\cdots+x_nA_n$ for some (diagonal) $A_i \in \allmat_{d,d}(K)$.
+  First, denote by $A(x) = \ell_1 \oplus \cdots \oplus \ell_d \in K[x]^{d\times d}_1$,
+  so that $A(x) = A_0+x_1A_1+\cdots+x_nA_n$ for some (diagonal) $A_i \in K^{d\times d}$.
   We might assume that $A_0,A_1,\ldots,A_n$ are affinely independent, so that the mapping
   $\varphi(x) = A(x)$ is injective. 
-  First, remark that $Q=S_A$ and thus $\varphi(Q) = \mathcal{L} \cap \allmat_{d,d}(K)$, with
+  First, remark that $Q=S_A$ and thus $\varphi(Q) = \mathcal{L} \cap K^{d\times d}$, with
   $\mathcal{L} = A_0+\span{A_1,\ldots,A_n}$ is a spectrahedron.
   Next, remark that $L \subset K^n$ is the affine space defined by equations $m_1=\ldots=m_e=0$,
-  hence $\varphi(L) \subset \allmat_{d,d}(K)$ is an affine space. Since $\varphi$ is injective,
+  hence $\varphi(L) \subset K^{d\times d}$ is an affine space. Since $\varphi$ is injective,
   one has $\varphi(P) = \varphi(Q \cap L) = \varphi(Q) \cap \varphi(L)$ which is the intersection
   of a spectrahedron with an affine space, thus a spectrahedron.
-  %Define $B = m_1 \oplus \cdots \oplus m_e \in \allmat_{e,e}(K[x]_1)$
+  %Define $B = m_1 \oplus \cdots \oplus m_e \in K[x]^{e\times e}_1$
 \end{proof}

### 2024-11-13 article/paper_padic_spec.tex
commit by Simone

@@
   the related optimization problems with data over a field $K$ with valuation.
+  DIRE CE QU'ON FAIT.
   We showcase examples of non-polyhedral $K$-spectrahedra and of sets that are semidefinite
@@
   As in the real case, one often abuses of notation, saying that the preimage
-  $S = \varphi^{-1}(K^{d \times d}_+) = \{x \in K^n : A_0+x_1A_1+\cdots+x_nA_n \succeq 0\}$
-  of $K^{d \times d}_+$ under the map $\varphi(x) = A_0+x_1A_1+\cdots+x_nA_n$, is a \emph{spectrahedron
-  in $K^n$}.
+  $S_A = \varphi_A^{-1}(K^{d \times d}_+) = \{x \in K^n : A_0+x_1A_1+\cdots+x_nA_n \succeq 0\}$
+  of $K^{d \times d}_+$ under the map $\varphi_A : K^n \to K^{d \times d}$, defined as
+  $\varphi_A(x) = A_0+x_1A_1+\cdots+x_nA_n$, is a \emph{spectrahedron
+  in $K^n$}. Remark that the map $\varphi_A$ is in general not injective, unless $A_1,\ldots,A_n$ are linearly
+  indepedent.
 \end{remark}
@@
 \begin{remark}
-  The class of spectrahedra is closed under intersection. Indeed, for affine spaces $\mathcal{L}_1,\mathcal{L}_2$
-  one has $(\mathcal{L}_1 \cap K^{d \times d}_+) \cap (\mathcal{L}_2 \cap K^{d \times d}_+) =
-  (\mathcal{L}_1 \cap \mathcal{L}_2) \cap K^{d \times d}_+$. Now
-  assuming $\mathcal{L}_1 = A_0+\span{A_1,\ldots,A_n}$ and $\mathcal{L}_2 = B_0+\span{B_1,\ldots,B_n}$,
-  then $S_A \cap S_B = S_{A \oplus B}$ (indeed both $A \succeq 0$ and $B \succeq 0$ if and only if
-  $A \oplus B \succeq 0$).
+  The class of spectrahedra in $K^{d \times d}$ (or in $K^n$) is closed under intersection: indeed one
+  has $(\mathcal{L}_1 \cap K^{d \times d}_+) \cap (\mathcal{L}_2 \cap K^{d \times d}_+) =
+  (\mathcal{L}_1 \cap \mathcal{L}_2) \cap K^{d \times d}_+$ and
+  $S_A \cap S_B = S_{\diag(A,B)}$, for two affine spaces $\mathcal{L}_1 = A_0+\span{A_1,\ldots,A_n}$
+  et $\mathcal{L}_2 = A_0+\span{B_1,\ldots,B_n}$.
 \end{remark}
@@
 %\end{remark}
+
 \begin{proposition}
-  A polyhedron is a spectrahedron.
+  A polyhedron in $K^{d \times d}$ is a spectrahedron in $K^{d \times d}$.
 \end{proposition}

### 2024-11-13 article/paper_padic_spec.tex
debut preuve poly-->spec

@@
   A \emph{spectrahedron in $K^{d\times d}$} is a set of the form
-  $\mathcal{S} = \mathcal{L} \cap K^{d\times d}_+$,
+  $$
+  \mathcal{S} = \mathcal{L} \cap K^{d\times d}_+ = \left\{X \in K^{d \times d} : \exists \, x \in K^n, X = A_0+\sum_{x_i A_i}, X \succeq 0\right\}
+  $$
   where $\mathcal{L} = A_0+\span{A_1,\ldots,A_n} \subset K^{d \times d}$ is an affine space, for some
@@
   $S_A = \varphi_A^{-1}(K^{d \times d}_+) = \{x \in K^n : A_0+x_1A_1+\cdots+x_nA_n \succeq 0\}$
-  of $K^{d \times d}_+$ under the map $\varphi_A : K^n \to K^{d \times d}$, defined as
+  of $K^{d \times d}_+$ under the map $\varphi_A : K^n \to \mathcal{L} \subset K^{d \times d}$, defined as
   $\varphi_A(x) = A_0+x_1A_1+\cdots+x_nA_n$, is a \emph{spectrahedron
@@
 \begin{proposition}
-  A polyhedron in $K^{d \times d}$ is a spectrahedron in $K^{d \times d}$.
+  %%% OLD STATEMENT
+  %%% A polyhedron is a spectrahedron.
+A polyhedron in $K^n$ is a spectrahedron in $K^n$.
 \end{proposition}
 \begin{proof}
-  Let $\ell_i,m_j \in K[x]_1$, for $i=1,\ldots,d$ and $j=1,\ldots,e$, and let $P = Q \cap L \subset K^n$
-  be a polyhedron as in \Cref{def_polyhedra}, for $Q = \{x \in K^n : \val(\ell_i) \geq 0, i=1,\ldots,d\}$
-  and $L = \{x \in K^n : \val(m_j) = +\infty, j=1,\ldots,e\}$.
-  First, denote by $A(x) = \ell_1 \oplus \cdots \oplus \ell_d \in K[x]^{d\times d}_1$,
-  so that $A(x) = A_0+x_1A_1+\cdots+x_nA_n$ for some (diagonal) $A_i \in K^{d\times d}$.
-  We might assume that $A_0,A_1,\ldots,A_n$ are affinely independent, so that the mapping
-  $\varphi(x) = A(x)$ is injective. 
-  First, remark that $Q=S_A$ and thus $\varphi(Q) = \mathcal{L} \cap K^{d\times d}$, with
-  $\mathcal{L} = A_0+\span{A_1,\ldots,A_n}$ is a spectrahedron.
-  Next, remark that $L \subset K^n$ is the affine space defined by equations $m_1=\ldots=m_e=0$,
-  hence $\varphi(L) \subset K^{d\times d}$ is an affine space. Since $\varphi$ is injective,
-  one has $\varphi(P) = \varphi(Q \cap L) = \varphi(Q) \cap \varphi(L)$ which is the intersection
-  of a spectrahedron with an affine space, thus a spectrahedron.
-  %Define $B = m_1 \oplus \cdots \oplus m_e \in K[x]^{e\times e}_1$
+  Let $P$ be a polyhedron in $K^n$. We show that there exist $d \in \mathbb{N}$ and
+  $A_0,A_1,\ldots,A_n \in K^{d \times d}$ such that $P = S_A$. Assume $P = L \cap M$ with
+  \begin{equation*}
+    \begin{aligned}
+    L &= \{x \in K^n : \val \ell_i(x) \geq 0, i=1, \ldots, d\} \\
+    M &= \{x \in K^n : \val m_j(x) = +\infty, j=1, \ldots, e\}
+    \end{aligned}
+  \end{equation*}
+  for some $d, e \in \mathbb{N}$. Let $\eta \leq n$ be the dimension of $M$ as vector subspace of
+  $K^n$, and let $y=(y_1, \ldots, y_\eta) \in K^{\eta}$ be variables on $M$, with $y = Tx$
+  for some $T \in K^{\eta \times n}$ with $\text{rank}(T) = \eta$. Let $A_0,A_1,\ldots,A_n \in K^{d \times d}$
+  be such that
+  $$
+  A_0+x_1A_1+\cdots+x_nA_n = \diag(\ell_1(x), \ldots, \ell_d(x)).
+  $$
+  One has that
+  $$
+  P = \{x \in \}
+  $$
+  {\bf à terminer -- Simone}  
+%%% OLD PROOF
+%  Let $\ell_i,m_j \in K[x]_1$, for $i=1,\ldots,d$ and $j=1,\ldots,e$, and let $P = Q \cap L \subset K^n$
+%  be a polyhedron as in \Cref{def_polyhedra}, for $Q = \{x \in K^n : \val(\ell_i) \geq 0, i=1,\ldots,d\}$
+%  and $L = \{x \in K^n : \val(m_j) = +\infty, j=1,\ldots,e\}$.
+%  First, denote by $A(x) = \ell_1 \oplus \cdots \oplus \ell_d \in K[x]^{d\times d}_1$,
+%  so that $A(x) = A_0+x_1A_1+\cdots+x_nA_n$ for some (diagonal) $A_i \in K^{d\times d}$.
+%  We might assume that $A_0,A_1,\ldots,A_n$ are affinely independent, so that the mapping
+%  $\varphi(x) = A(x)$ is injective. 
+%  First, remark that $Q=S_A$ and thus $\varphi(Q) = \mathcal{L} \cap K^{d\times d}$, with
+%  $\mathcal{L} = A_0+\span{A_1,\ldots,A_n}$ is a spectrahedron.
+%  Next, remark that $L \subset K^n$ is the affine space defined by equations $m_1=\ldots=m_e=0$,
+%  hence $\varphi(L) \subset K^{d\times d}$ is an affine space. Since $\varphi$ is injective,
+%  one has $\varphi(P) = \varphi(Q \cap L) = \varphi(Q) \cap \varphi(L)$ which is the intersection
+%  of a spectrahedron with an affine space, thus a spectrahedron.
+%  %Define $B = m_1 \oplus \cdots \oplus m_e \in K[x]^{e\times e}_1$
 \end{proof}

### 2024-11-13 article/paper_padic_spec.tex
Rework sections 3.1 and 3.2

@@
 
-{\color{blue} Normalement avec la nouvelle definition, ça devrait aller, il faut par contre
-  partir d'un polyedre defini aussi par des égalités. Peut être il faudrait aussi
-  diviser la proposition en plusieures parties pour la rendre plus lisible, par exemple une
-  première proposition avec la projection.}
+%{\color{blue} Normalement avec la nouvelle definition, ça devrait aller, il faut par contre
+%  partir d'un polyedre defini aussi par des égalités. Peut être il faudrait aussi
+%  diviser la proposition en plusieures parties pour la rendre plus lisible, par exemple une
+%  première proposition avec la projection.}
+
+In this section we show that the image of a polyhedron by a linear mappingA is a polyhedron. 
+We first prove the result in the cases of authomorphisms of $\OK^n$ and diagonal endomorphisms of $K^n$.
+Then we use these particular cases to prove the result for projections of the form $(x_1,\dots,x_n) \mapsto (x_1,\dots, x_{n-1})$
+and finally for the general case.
+
+\begin{remark}
+ First, let $f : K^n \to K^m$ be a linear map and $\PP \subset K^n$ be a polyhedron defined by 
+$\PP = \left\lbrace x \in K^n : \val (l_i (x) ) \geq 0, m_i(x)=0, \textrm{ for } i \in I, j \in J \right\rbrace$ 
+for some finite sets $I \subset \N$ and $J \subset \mathbb{N}$ and $m_j, l_i \in K[x]_1$, for $i \in I$  and $j \in J$.
+Then  $\PP = \PP_i \cap \PP_e$ where $\PP_i := \{x \in K^n : \val(l_i(x)) \ge 0, i = 1,\dots,d\}$
+and $\PP_e := \{x \in K^n : m_j(x) = 0, j = 1,\dots,e\}$.
+
+Thus, we have  $f(\PP) = f(\PP_i) \cap f(\PP_e)$.
+However, $\PP_e$ is either empty or an affine subspace of $K^n$ and therefore 
+$f(\PP_e)$ is either empty or an affine subspace of $K^m$, so it is a polyhedron.
+Hence, as the class of polyhedron is closed under intersection to prove that
+$f(\PP)$ is a polyhedron it is sufficient to prove that $f(\PP_i)$ is one.
+\end{remark}
+
+Therefore, we can only consider the image of polyhedron of the form 
+$\left\lbrace x \in K^n : \val (l_i (x) ) \geq 0 \textrm{ for } i \in I \right\rbrace$.
 
 \begin{proposition}
-Let $\PP \subset K^n$ be a polyhedron and $f: K^n \rightarrow K^m$
-be a linear mapping. Then $f(\PP)$ is a polyhedron.
+  Let $\PP \subset K^n$ be a polyhedron and $f : K^n \to K^n$ be a linear mapping.
+  If $f \in \GL_n(\OK)$ or if there exists $\lambda_1, \dots, \lambda_n \in K$ such that 
+  $(x_1,\dots,x_{n-1}, x_n) \mapsto (x_1,\dots, x_{n-1})$.
 \end{proposition}
+
 \begin{proof}
-Let us assume that 
-$\PP = \left\lbrace x \in K^n : \val (l_i (x) ) \geq 0, \textrm{ for } i \in I \right\rbrace$ for some
-finite set $I \subset \N$ and $l_i \in K[x]_1$, for $i \in I$ ({\color{blue} mettre aussi les égalités dans $\PP$}).
-We further assume that $\PP \neq \emptyset$, and we identify $f$ with its matrix in $K^{n \times n}$.
+We assume that $\PP \neq \emptyset$
+As discussed above we can assume that
+$\PP = \left\lbrace x \in K^n : \val (l_i (x) ) \geq 0,\textrm{ for } i \in I \right\rbrace$ for some
+finite set $I \subset \N$ and $l_i \in K[x]_1$, for $i \in I$ .
 
-Thanks to Definition \ref{smith_nf}, (the matrix of) $f$
-can be written $f=Q^{-1} \Delta P$
-with $P \in \GL_n(\OK),$ $Q \in \GL_m(\OK)$
-and $\Delta = SNF(f)\in K^{m \times n}$ of the form $\diag(\lambda_1, \ldots, \lambda_r, {\bf 0}_{\min(m,n)-r})$
-  where ${\bf 0}_{\min(m,n)-r}$ is a null square matrix of size $\min(m,n)-r$ for $\lambda_1,\dots,\lambda_r$ non-zero and $r \in \N.$
-
-We first prove the result when $f$ is in $\GL_n(\OK)$.
-In that case, $x \in f(P)$ if and only if for all
-$i \in I,$
+First, if $f \in \GL_n(\OK)$ then, $x \in f(P)$ if and only if for all $i \in I$, 
 $\val(l_i (f^{-1}(x))) \geq 0$.
@@
 $f(x_1,\dots,x_n)=(\lambda_1 x_1,\dots,\lambda_n x_n)$
-for some $\lambda \in K$,
+for some $\lambda_1,\ldots, \lambda_n \in K$,
 then of course $f(P)$
@@
 obvious change of variables.
+\end{proof}
 
-Now, we turn our attention to the $\Delta$ part of $f.$
-We first assume that $f$ is a projection 
-of the form $K^n \rightarrow K^{n-1},$
-$(x_1,\dots,x_{n-1},x_n)\mapsto (x_1,\dots,x_{n-1}).$
+The two above results allows us to demonstrate the following proposition, which we will use to prove the general case.
+
+\begin{proposition}
+      Let $\PP \subset K^n$ be a polyhedron and $p : K^n \to K^{n-1}$ be the projection $p : (x_1,\dots,x_{n-1},x_n) \mapsto (x_1, \dots, x_{n-1})$.
+       Then $p(\PP)$ is a spectrahedron.
+\end{proposition}
+
+  \begin{proof}
+
+We assume that $\PP \neq \emptyset$.
+As discussed above we can assume that
+  $\PP = \left\lbrace x \in K^n : \val (l_i (x) ) \geq 0,\textrm{ for } i \in I \right\rbrace$ for some
+finite set $I \subset \N$ and $l_i \in K[x]_1$, for $i \in I$ .
 
@@
 in matrix form:
-$\val(A X+B) \geq 0$
+$\val(A X+B) \geq 0$ and 
 with $A \in M_{q,n}(K)$, $B \in K^q$
-and $X=(x_1,\dots,x_n)^\intercal.$
+and $X=(x_1,\dots,x_n)^\intercal$.
 
@@
 $\PP$ can be written
-$\PP=P_A^{-1}(\PP_2)$ for some polyhedron $\PP_2 \in K^n$
+$\PP=P_A^{-1}(\PP_2)$ for some polyhedron $\PP_2 \subset K^n$
 and we are reduced to proving that
-$f(\PP_2)$ is polyhedron for $f$ still the canonical projection
+$f(\PP_2)$ is polyhedron for $p$ still the canonical projection
 $K^n \rightarrow K^{n-1}$ and $\PP_2$
@@
 
-Then the previous computations prove that $f(\PP_2)\subset \Qc.$
+Then the previous computations prove that $p(\PP_2)\subset \Qc.$
 Conversely, let $(x_1,\dots,x_{n-1}) \in \Qc.$
@@
 and $x_n+b_n=O(1)$. Hence $(x_1,\dots,x_n) \in \PP_2$
-which means that $(x_1,\dots,x_{n-1}) \in f(\PP_2).$
-Thus $f(\PP_2)= \Qc$ and $f(\PP_2)$ is a polyhedron.
+which means that $(x_1,\dots,x_{n-1}) \in p(\PP_2).$
+Thus $p(\PP_2)= \Qc$ and $p(\PP_2)$ is a polyhedron.
 
@@
 and $x_1+a_1 x_n+b_1=O(1).$
-Consequently, $x_1-a_1 b_n +b_1=O(1)+O(\pi^{\val(a_1)})=O(\pi^{\val(a_1)})).$
+Consequently, $x_1-a_1 b_n +b_1=O(1)+O(\pi^{\val(a_1)})=O(\pi^{\val(a_1)}).$
 Thus $a_1^{-1}x_1- b_n +a_1^{-1}b_1=O(1)$.
@@
 Hence $(x_1,\dots,x_n) \in \PP_2$
-which means that $(x_1,\dots,x_{n-1}) \in f(\PP_2).$
-Thus $f(\PP_2)= \Qc$ and $f(\PP_2)$ is a polyhedron,
+which means that $(x_1,\dots,x_{n-1}) \in p(\PP_2).$
+Thus $p(\PP_2)= \Qc$ and $p(\PP_2)$ is a polyhedron,
 and it has been proved in both cases.
 
-Therefore, if $f$ is the projection 
-$(x_1,\dots,x_{n-1},x_n)\mapsto (x_1,\dots,x_{n-1})$ 
-and $\PP$ is a polyhedron in $K^n$,
-then $f(\PP)$ is a polyhedron.
+Therefore,$p(\PP)$ is a polyhedron.
 
-\tristan{Attention, à partir de maintenant,
-il faut ajouter à la définition qu'on peut
-fixer des points!
-Cela revient à ajouter des conditions
-$\val = + \infty.$}
+\end{proof}
 
+We can finally prove that the image of polyhedron under a linear mapping is a polyhedron.
+\begin{proposition}
+Let $\PP \subset K^n$ be a polyhedron and $f: K^n \rightarrow K^m$
+be a linear mapping. Then $f(\PP)$ is a polyhedron.
+\end{proposition}
+
+\begin{proof}
+
+We assume that $\PP \neq \emptyset$, and we identify $f$ with its matrix in $\allmat_{n,n}(K)$.
+As seen above, we can assume that $\PP$ is of the form $\left\lbrace x \in K^n : \val (l_i (x) ) \geq 0, \textrm{ for } i \in I\right\rbrace$ for some
+finite sets $I \subset \N$ and $l_i \in K[x]_1$, for $i \in I$ .
+
+Thanks to Definition \ref{smith_nf}, (the matrix of) $f$
+can be written $f=Q^{-1} \Delta P$
+with $P \in \GL_n(\OK),$ $Q \in \GL_m(\OK)$
+and $\Delta = SNF(f)\in \allmat_{m,n}(K)$ of the form $\diag(\lambda_1, \ldots, \lambda_r, {\bf 0}_{\min(m,n)-r})$
+  where ${\bf 0}_{\min(m,n)-r}$ is a null square matrix of size $\min(m,n)-r$ for $\lambda_1,\dots,\lambda_r$ non-zero and $r \in \N.$
+
+  %Now, we turn our attention to the $\Delta$ part of $f$.
+We have previously proven that if $f \in \GL_n(\OK)$ then $f(\PP)$ is a polyhedron.
 It is also clear that
@@
 with $P \in \GL_n(\OK),$ $Q \in \GL_m(\OK)$
-and $\Delta \in K^{m \times n}$,
+and $\Delta \in \allmat_{n,m}(K)$,
 then
@@
 
-A \emph{linear programming problem} (or simply \emph{linear program}) \emph{with data $(A,b,c)$} is defined
+A \emph{linear programming problem} (or simply \emph{linear program}) \emph{with data $(A,b,c,D,e)$} is defined
 as:
@@
   p^* & := & \inf_{x \in K^n} & \val(\left\langle c, x \right\rangle) \\
-  &    & \text{s.t.}         & A x + b \geq 0
+  &    & \text{s.t.}         & A x + b \geq 0\\
+  & & & D x = e
 \end{array}
 \end{equation}
-with $c \in K^n$ a fixed vector of size $n$ that represents the cost, $A \in K^{m \times n}$, $b \in K^m$,
-and $\left\langle c, x \right\rangle := c_1x_1+\cdots +c_nx_n$. When $A$ is a diagonal matrix, we often
+with $c \in K^n$ a fixed vector of size $n$ that represents the cost, $A \in \allmat_{d,n}(K)$, $b \in K^d$, $D \in \allmat_{m,n}$, $e \in K^m$ 
+and $\left\langle c, x \right\rangle := c_1 x_1+\cdots +c_n x_n$. When $A$ is a diagonal matrix and $D = 0$, we often
 refer to \eqref{LP} as a \emph{diagonal} linear program. We denote the \emph{feasible set} of \eqref{LP} by
@@
 \begin{aligned}
-  \PP  &= \{x \in K^n : Ax + b \geq 0\}.
+  \PP  &= \{x \in K^n : Ax + b \geq 0, Dx = e\}.
 \end{aligned}
 \end{equation*}
-A vector $x \in K^n$ is called \emph{feasible} for \eqref{LP} if $x \in \PP$ and the program \eqref{LP} is
-called \emph{feasible} if $\PP \neq \emptyset$. A feasible vector $x^* \in \PP$
+A vector $x \in K^n$ is called \emph{feasible} for~\eqref{LP} if $x \in \PP$. A feasible vector $x^* \in \PP$
 is called a \emph{solution} to \eqref{LP} if $p^* = \left\langle c,x^*\right\rangle$.
 
-In this section we present an algorithm for solving \eqref{LP} which consists in reducing the matrix $A$ in
-Smith Normal Form,
-thus reducing a general linear program to an iteration of diagonal linear programs.
-The most interesting aspect of the SNF regarding the resolution of \eqref{LP} is that the transition matrices are
-invertible in $\OK$, thus they preserve inequalities: indeed, if $z \in K^n$ and $M \in \OK^{n \times n}$ such
-that $z \geq 0$, then $Mz \geq 0$.
-The latter property is a direct consequence of $\OK$ being a ring and the converse holds if the matrix $M$ is
-invertible in $\OK$. Therefore, for all matrix $M \in K^{n \times n}$ with $S=SNF(M)$ and for all $z \in K^n$,
+\begin{remark}
+The valuation $\val$ is discrete. Thus if \eqref{LP} admits feasible vectors, $p^*$ is either $- \infty$ or reached by a certain solution $x^*$.
+\end{remark}
+
+In this section we present an algorithm for solving \eqref{LP} which starts by eliminating the constraint forced by $D$ and $e$ by operating a substitution. Then it reduces the matrix $A$ to
+Smith Normal Form, thus reducing a general linear program to a diagonal linear program. The latter problem being easily solved by simple calulations in $K$.
+
+The first proposition we prove  allows to consider only iterations of~\eqref{LP} with data of the form $(A,b,c,0,0)$.
+
+\begin{proposition}\label{reducD}
+  Let $A \in \allmat_{d,n}(K), b \in K^d, c\in K^n$, $D \in \allmat_{m,n}$, $e \in K^m$ and let $J \in \allmat_{n,R}\left( K \right) $ be a matrix such that ${\rm Im } J = \ker D$ where $R$ denotes the dimension of $\ker D$.
+  Additionally, we assume the existence of $x_0 \in K^n$ that verifies $D x_0 =e$ as if
+  there are no such vector the problem~\ref{LP} with data $(A,b,c,D,e)$ is not solvable.
+
+  Let $x \in \{x \in K^n : Dx=e\} = x_0 + \ker D $ and let $y \in K^R$ denote the unique element of
+  $K^n$ such that $x = x_0 + J y$, then :
+  \begin{enumerate}
+    \item\label{reducD_item1} $x$ is feasible for~\eqref{LP} with data $(A,b,c,D,e)$ if and only if 
+      $y$ is feasible for~\eqref{LP} with data $(AJ,b+A x_0,J^T c,0,0)$.
+    \item\label{reducD_item2} $x$ is a solution for~\eqref{LP} with data $(A,b,c,D)$ if and only if 
+      $y$ is a solution for~\eqref{LP} with data $(AJ,b+A x_0,J^T c,0,0)$ and $\langle c,x^* \rangle = \langle J^T c,y^* \rangle$.
+  \end{enumerate}
+\end{proposition}
+
+\begin{proof}
+  %The existence and uniqueness of $y$ are granted by the fact that $x \in x_0 + \ker D =x_0+ {\rm Im } J$  and $\ker J = \{0\}$. 
+  First,  $Dx=e$ and $Ax + b \le 0$ if and only if $AJy + b+Ax_0 \le 0$, proving \Cref{reducD_item1}.
+  Next, for all $c \in K^n$, $\langle c,x\rangle = \langle c, Jy\rangle = \langle J^T c,y\rangle$, which proves \Cref{reducD_item2}.
+\end{proof}
+
+The most interesting aspect of the SNF regarding the resolution of~\eqref{LP} is that the transition matrices are
+invertible in $\OK$ and as such they preserve inequalities. %Indeed, for all $z \in K^n$ and $M \in \allmat_n(\OK)$ if $z \geq 0$, then $Mz \geq 0$.
+%The latter property is a direct consequence of $\OK$ being a ring and the converse holds if the matrix $M$ is
+%invertible in $\OK$. 
+Therefore, for all matrix $M \in \allmat_{n,n}(K)$ with $S=SNF(M)$ and for all $z \in K^n$,
 then $Mz \geq 0$ if and only if $Sz \geq 0$.
 
-%%%\corentin{or maybe reduced linear programming problem?}:
-%%%\simone{il me semble que tout ça n'est pas trop clair, par exemple quelle est la difference entre diagonal LP et associated diagonal LP plus en bas, est-ce qu'il y a vraiment besoin de tout ça, il faut simplifier la presentation}
-%That property applied to the matrix $A$ in \ref{LP} allows to reduce the problem to an equivalent simpler iteration of the problem in \eqref{LP}, that will be called \emph{diagonal linear programming problem}
-%\begin{equation}
-%  \tag{dLP}\label{DLP}
-%\begin{array}{rcll}
-%  {p^*}' & := & \inf_{y \in K^n} & \val(\left\langle c', y \right\rangle) \\
-%  &    & \text{s.t.}         & S y + b' \geq 0
-%\end{array}
-%\end{equation}
-%with $c' \in K^n$ a fixed vector of size $n$, $b' \in K^m$ and $S$ a diagonal $m \times n$ matrix of the form $S = \diag(s_1, s_2, \ldots, s_r, { \bm 0}_{m-r})$, with $r = {\rm rank}\, S$.
-
-%The \emph{associated diagonal linear programming problem} of a linear program is the iteration of the \ref{DLP} problem defined by $b' = Qb$, $c' = \left(P^{-1}\right)^T c$ and where $S$ is the Smith normal form of $A$ and $P \in GL_m(\OK)$ and $ Q \in GL_n(\OK)$ are such that $A = Q^{-1} S P$.
+\Cref{solsLP} allows us to reduce \eqref{LP} to diagonal linear programs.
 
 \begin{proposition} \label{solsLP}
-  Let $A \in K^{m\times n}, b \in K^m, c\in K^n$ and let $S = SNF(A) = QAP^{-1} \in K^{m \times n}$, with
-  transition matrices $P \in \GL_n(\OK)$ and $Q\in \GL_m(\OK)$. Define $b' = Qb$ and $c' = (P^{-1})^Tc$.
+  Let $A \in \allmat_{d,n}(K), b \in K^d, c\in K^n$ and let $S = SNF(A) = QAP^{-1} \in \allmat_{d,n}(K)$, with
+  transition matrices $P \in \GL_d(\OK)$ and $Q\in \GL_d(\OK)$. Define $b' = Qb$ and $c' = (P^{-1})^Tc$.
   Then
@@
    \item \label{solsLP_item1}
-     $x \in K^n$ is feasible for \eqref{LP} with data $(A,b,c)$ if and only if $y = P x \in K^n$ is
-     feasible for \eqref{LP} with data $(S,b',c')$.
+     $x \in K^n$ is feasible for \eqref{LP} with data $(A,b,c,0,0)$ if and only if $y = P x \in K^n$ is
+     feasible for \eqref{LP} with data $(S,b',c',0,0)$.
    \item \label{solsLP_item2}
-     $x^* \in K^n$ is a solution to \eqref{LP} with data $(A,b,c)$ if and only if $y^* = P x^*$ is
-     a solution to \eqref{LP} with data $(S,b',c')$ and $\langle c,x^* \rangle = \langle c',y^* \rangle$.
+     $x^* \in K^n$ is a solution to \eqref{LP} with data $(A,b,c,0,0)$ if and only if $y^* = P x^*$ is
+     a solution to \eqref{LP} with data $(S,b',c',0,0)$ and $\langle c,x^* \rangle = \langle c',y^* \rangle$.
    \end{enumerate}
@@
   First of all, $Ax+b = AP^{-1}y +b \geq 0$ if and only if $Q(AP^{-1}y + b) = Sy + b' \geq 0$ because
-  $Q \in GL_m(\OK)$, which yields \Cref{solsLP_item1}. Next, for all $c \in K^n$, one has $\langle c,
+  $Q \in GL_m(\OK)$, which yields \Cref{solsLP_item1}. Next, for all $c \in K^n$, we have $\langle c,
   x\rangle = \langle c, P^{-1}Px \rangle = \langle \left(P^{-1}\right)^T c, Px \rangle = \langle c',y\rangle$,
@@
 
-\Cref{solsLP} allows us to reduce \eqref{LP} to diagonal linear programs.
-
 \begin{proposition}\label{prop:reduc}
-  Let $(A,b,c), (S,b',c') \in K^{m \times n} \times K^m \times K^n$ be as in \Cref{solsLP}, where
+  Let $(A,b,c), (S,b',c') \in \allmat_{d,n}(K) \times K^d \times K^n$ be as in \Cref{solsLP}, where
   $S=SNF(A)$. Then
@@
   \item \label{prop:reduc_it1}
-    \eqref{LP} with data $(S,b',c')$ is feasible if and only if the $m-r$ last coefficients
-    of $b'$ have nonnegative valuation, for $r = \text{rank}\,S$.
+    \eqref{LP} with data $(S,b',c',0,0)$ is feasible if and only if the $d-r$ last coefficients
+    of $b'$ have nonnegative valuation, for $r = {\rm rank}\,S$.
   \item \label{prop:reduc_it2}
@@
   %%%%\corentin{préciser les notations}. 
-  A vector $y = (y_1, \ldots, y_n)^T \in K^n$ is feasible for \eqref{LP} with data $(S,b',c')$
+  A vector $y = (y_1, \ldots, y_n)^T \in K^n$ is feasible for \eqref{LP} with data $(S,b',c',0)$
   if and only if $\val(s_i y_i + b_i) \geq 0$ for all $i = 1,\ldots,n$.
-  However $s_i = 0$ for $n-r \leq i\leq n$. Therefore, if \eqref{LP} with data $(S,b',c')$ is feasible,
-  necessarily the $m-r$ last coefficients of $b'$ have nonnegative valuation.
-  Conversely, if the $m-r$ last coefficients of $b'$ are zero, the vector $y \in K^n$ such that
+  However $s_i = 0$ for $n-r \leq i\leq n$. Therefore, if \eqref{LP} with data $(S,b',c',0)$ is feasible,
+  necessarily the $d-r$ last coefficients of $b'$ have nonnegative valuation.
+  Conversely, if the $d-r$ last coefficients of $b'$ are zero, the vector $y \in K^n$ such that
   $y_i = -\frac{-b'_i}{s_i}$ if $1 \leq i \leq r$, and $y_i =0$ otherwise, is feasible for \eqref{LP}
-  with data $(S,b',c')$.
+  with data $(S,b',c',0,0)$.
 
-  Concerning \Cref{prop:reduc_it2}, let $y^*$ be feasible for \eqref{LP} with data $(S,b',c')$.
+  Concerning \Cref{prop:reduc_it2}, let $y^*$ be feasible for \eqref{LP} with data $(S,b',c',0,0)$.
   Let $i$ be such that $r+1 \leq i \leq n$ and $c'_i \neq 0$. Consider the vector $e^i$ whose only non-zero
-  coefficient is the $i-$th, which is $1$. Then $y^* + \alpha e^i$ is feasible for \eqref{LP} with data $(S,b',c')$,
+  coefficient is the $i-$th, which is $1$. Then $y^* + \alpha e^i$ is feasible for \eqref{LP} with data $(S,b',c',0,0)$,
   for all $\alpha \in K$ and $\langle c', y^* + \alpha e^i\rangle = \langle c' , y^* \rangle + \alpha c'_i$.
-  In particular, for $\alpha = -\frac{\langle c', y^* \rangle}{c'_i}$, one has $\val \left( \langle c', y^* +
-  \alpha e ^i \rangle\right) = \val (0) = + \infty$. ({\color{blue} je ne comprends pas: il est non-borné
-    supérieurement, mais nous on cherche l'inf..., donc comment montrer qu'il n'y a pas de solutions ? il faudrait
-  une sequence avec limite valuation $-\infty$})
+  In particular, for all $n \in \mathbb{N}$ if we set $\alpha = -\frac{\langle c', y^* \rangle + \pi^{-n}}{c'_i}$, we have $\val \left( \langle c', y^* + \alpha e ^i \rangle\right) = \val \pi^{-n} = -n$.
+Therefore, the problem is unbounded as $p^* = + \infty$.
 \end{proof}
@@
 
-Solving the diagonal LP consists (by definition) in minimizing the linear map $y \mapsto \val\left(\left\langle
+Solving the diagonal \Cref{LP} consists -by definition- in minimizing the linear map $y \mapsto \val\left(\left\langle
 c',y \right\rangle\right)$ over $\PP'$. The image of $\PP'$ by $y \mapsto \left\langle c',y \right\rangle$ is
-$$
+\[
 \left\langle c',\PP' \right\rangle = \sum_{i=1}^r -c'_i \frac{b'_i}{s_i} + \sum_{i=1}^r\left( \frac{c'_i}{s_{i}} \OK \right) = \lambda + \pi^{v} \OK
-$$
+\]
 where $\lambda = \sum_{i=1}^r -c'_i \frac{b'_i}{s_i}$ and $v = \min\limits_{1\le i\le r} \val \frac{c'_{i}}{s_{i}} $.
-Finally, two cases can occur depending on $v$ and the valuation of $\lambda$:
-\begin{enumerate}
-\item
+
+Two cases can occur depending on $v$ and the valuation of $\lambda$.
 If $\val(\lambda) < v$, the minimum of $y\mapsto \val\left(\left\langle c',y \right\rangle\right)$ over $\PP'$
   is reached at any point of $\PP'$, and is equal to $\val(\lambda)$.
-\item
-  If $\val(\lambda) \ge v$, then $\lambda \in \pi^{v} \OK$ and the minimum is $v$ and is reached at any points $y$
-  of $\PP'$ that verifies 
-  \[\val \underset{ \begin{array}{c} 1\le i\le r\\ \val\left(c'_{i}/{s_{i}} \right) = v  \end{array}}{\sum} y_{i} = 0. \]
-\end{enumerate}
+  Otherwise, if $\val(\lambda) \ge v$, then $\lambda \in \pi^{v} \OK$ and the minimum is $v$ and is reached at any points $y$
+  of $\PP'$ such that $\left<c',y \right> \in \pi^v$.
 
 \begin{remark}
-	To maximize the valuation of a linear map over a convex $p$-adic polyhedron instead of minimizing it (which is equuivalent to minimize the absolute value) the same reasoning can be aplied.
-The only difference being that if $\val\left( \lambda\right) < v$ the problem is unbounded and as such does not have any solution.
+	If $\val \lambda \ge v$ and $i_0 \in \{1,\ldots, n\} $ is such that $v = \val \frac{c_{i_0}'}{s_{i_0}²} $ 
+  then the vector $e^{i_0} \in K$ is a solution of \ref{LP}, 
+  where $e^{i_0}$ denotes the vector of $K^n$ whose only non-zero coefficient is the $i_0$-th which is $1$.
+\end{remark}
+
+\begin{remark}
+To maximize the valuation of a linear map over a polyhedron instead of minimizing it 
+(which is equivalent to minimize the absolute value) the same reasoning can be applied. 
+The only difference being that if $\val\left( \lambda\right) < v$ the problem is unbounded and 
+as such does not admit a solution. 
 \end{remark}

### 2024-11-19 article/paper_padic_spec.tex
section 4

@@
 
-\begin{proposition}
-  {\color{blue} [Peut être une hypothèse à rajouter, par exemple $K$ à valuation discrete]}
-  The set $K^{d \times d}_+$ is both open and closed.
-\end{proposition}
-\begin{proof}
-Firstly, $\OK[X]$ is closed and open in $K[X]$ equipped with the infinitiy norm $\|\cdot\|_\infty : P = \sum_{k=1}^{n} a_k X^k \to \sup |a_k|$.
-$\OK$ is indeed the open unit ball for $\|\cdot \|_\infty$ that induces a discrete distance for which open balls are also closed sets.
-Furthermore, $K^{d\times d}_+ = \chi^{-1}(\OK[X]) $ where $\chi$ is the function that maps a matrix to its characteristic polynomial which is continuous.
-\end{proof}
-
 \begin{definition}
@@
 
-\begin{remark}
-  \corentin{Pas nécessairement très important, à voir}
-  If $C$ is a cone that is furthermore closed under addition (what shall be called a convex cone in the real case) then $C$ is a $\OK$-module.
-\end{remark}
-
 \begin{proposition}
-  The set $K^{d \times d}_+$ is a cone.
+%  {\color{blue} [Peut être une hypothèse à rajouter, par exemple $K$ à valuation discrete]}
+  $K^{d \times d}_+$ is a cone.
+  If $\val$ is discrete, then it is both open and closed.
 \end{proposition}
 \begin{proof}
-  The result is immediate following the definiton of $K^{d \times d}_+$.
+  The fact that $K^{d \times d}_+$ is a cone is immediate from the definition.
+  Next, remark that $\OK[X]$ is closed and open in $K[X]$ equipped with the infinity norm
+  $$
+  \|\cdot\|_\infty : P = \sum_{k=1}^{n} a_k X^k \to
+  \max_{1 \leq k \leq n} |a_k|,
+  $$
+  {where $|\cdot|$ is any norm induced by $\val$}:
+  $\OK$ is indeed the open unit ball for $\|\cdot \|_\infty$ that induces a discrete distance for
+  which open balls are also closed sets.
+  Furthermore, $K^{d\times d}_+ = \chi^{-1}(\OK[X]) $ where $\chi$ is the function that maps a
+  matrix to its characteristic polynomial which is continuous.
+  Thus $K^{d\times d}_+$ is both open and closed, too.
 \end{proof}
+
+%\begin{remark}
+%  \corentin{Pas nécessairement très important, à voir}
+%  If $C$ is a cone that is furthermore closed under addition (what shall be called a convex cone in the real case) then $C$ is a $\OK$-module.
+%\end{remark}
 
@@
   $\varphi_A(x) = A_0+x_1A_1+\cdots+x_nA_n$, is a \emph{spectrahedron
-  in $K^n$}. Remark that the map $\varphi_A$ is in general not injective, unless $A_1,\ldots,A_n$ are linearly
-  indepedent.
+  in $K^n$}. Remark that the map $\varphi_A$ is onto $\mathcal{L}$ but not injective,
+  unless $A_1,\ldots,A_n$ are linearly indepedent.
 \end{remark}
 
-\begin{remark}
 The class of spectrahedra in $K^{d \times d}$ (or in $K^n$) is closed under intersection: indeed one
@@
 et $\mathcal{L}_2 = A_0+\span{B_1,\ldots,B_n}$.
-\end{remark}
+Moreover this class contains polyhedra in $K^n$.
 
@@
 \begin{proposition}
-  Spectrahedra are semialgebraic sets. 
+  Spectrahedra in $K^n$ are semialgebraic sets. 
 \end{proposition}
@@
 \begin{proof}
-  Let $S$ be spectrahedron and $A$ a linear matrix such that $S={x \in K^n : A(x) \succeq 0}$. 
-  We denote as $p_i(x)$ the $i$-th coefficient of $\chi_{M(x)}$. The map $p_i	: x \to p_i(x)$ is polynomial and $x \in S$ if and only if $\val(p_i(x)) \geq 0$ for $i=0,...,d$.
-
-  Finally, by \ref{caracsdp}, $S = \{x \in K^n : \chi_{M(x)} \in \OK(T)\} = \bigcap\limits_{i=0}^d \{x \in K^n : \val(p_i(x)) \geq 0\}$.
+  Let $S = S_A \subset K^n$ be spectrahedron, for some linear matrix $A(x) = A_0+\sum_{i=1}^n x_i A_i$. 
+  Denote by $p_i(x) \in K[x]$ the $i$-th coefficient of $\chi_{A(x)}$, $i=0,\ldots,d$.
+  By \Cref{caracsdp} one has:
+  $$
+  S = \left\{x \in K^n : \chi_{A(x)} \in \OK[T]\right\}
+  = \bigcap_{i=0}^d \{x \in K^n : \val(p_i(x)) \geq 0\}.
+  $$
 \end{proof}
 
-\corentin{ Une autre définition qu'il pourrait être intéressant d'explorer. Attention! Pas les mêmes propriétés.}
-\begin{definition}[Alternative definition]
-  Let $A_0, ..., A_n, B_0, ..., B_n \in M_{d,d}(K)$. 
+%\corentin{ Une autre définition qu'il pourrait être intéressant d'explorer. Attention! Pas les mêmes propriétés.}
+%\begin{definition}[Alternative definition]
+%  Let $A_0, ..., A_n, B_0, ..., B_n \in M_{d,d}(K)$.
 We denote as $S^+_A$ the set $S_{A}^+ = \left\{ x \in K^n : A_0 + x_1 A_1+ ...+x_nA_n \succeq 0  \right\}$ and $S^-_B$ denotes the set $S^-_B = \left\{ x \in K^n : B_0 + x_1 B_1+ ...+x_nB_n \preceq 0\right\}$.
 The set $S_A,B := S_A^+ \cup S_B^-$ is called a \emph{spectrahedron}.
-\end{definition}
+%\end{definition}
 

### 2024-11-19 article/paper_padic_spec.tex
commit by Simone

@@
   for some $d, e \in \mathbb{N}$. Let $\eta \leq n$ be the dimension of $M$ as vector subspace of
-  $K^n$, and let $y=(y_1, \ldots, y_\eta) \in K^{\eta}$ be variables on $M$, with $y = Tx$
-  for some $T \in K^{\eta \times n}$ with $\text{rank}(T) = \eta$. Let $A_0,A_1,\ldots,A_n \in K^{d \times d}$
+  $K^n$, and let $y = (y_1, \ldots, y_\eta)^T \in K^{\eta}$ be variables on $M$, with $Ty = x$
+  for some $T \in K^{n \times \eta}$ with $\text{rank}(T) = \eta$. Let $A_0,A_1,\ldots,A_n \in K^{d \times d}$
   be such that
@@
   $$
-  P = \{x \in \}
+  P = \{x \in K^n : x \in M, \}
   $$

### 2024-11-20 article/paper_padic_spec.tex
annuli-shadows

@@
 %\title{\bf On polyhedra and spectrahedra over valuation fields}
-\title{\bf On semidefinite representable sets over valuation fields}
+\title{\bf On semidefinite-representable sets over valuation fields}
 
@@
   Real polyhedra and real spectrahedra (or their projections) are respectively the feasible sets
-  of linear programming (LP) and semidefinite programming (SDP). 
-  This paper investigates versions of these sets and of
+  of linear programming (LP) and semidefinite programming (SDP) and form the family of
+  semidefinite-representable sets. This paper investigates versions of these sets and of
   the related optimization problems with data over a field $K$ with valuation.
-  DIRE CE QU'ON FAIT.
+  We prove that basic properties of semidefinite-representable sets generalize to this setting.
   We showcase examples of non-polyhedral $K$-spectrahedra and of sets that are semidefinite
@@
 A more general class of convex semialgebraic sets are obtained by linear projections of real spectrahedra
-called \emph{semidefinite representable sets} (or spectrahedral shadows): these are sets of the form
+called \emph{semidefinite representable sets}: these are sets of the form
 $$
-P = \left\{x = \left[\begin{smallmatrix} x_1 \\ \vdots \\ x_n \end{smallmatrix}\right] \in \R^n : \exists\,y\in\R^p, \, A_0 + \sum_{i=1}^n x_i A_i + \sum_{j=1}^p y_j B_j \succeq 0\right\}
+P = \left\{x = \left[\begin{smallmatrix} x_1 \\ \vdots \\ x_n \end{smallmatrix}\right] \in \R^n : \exists\,y\in\R^m, \, A_0 + \sum_{i=1}^n x_i A_i + \sum_{j=1}^m y_j B_j \succeq 0\right\}
 $$
+when $m>0$, the set $P$ is also called a \emph{spectrahedral shadow}.
 
@@
 
-$\R^*_+$ denotes the set of positive real numbers.
+Denote by $\R^*_+$ the set of positive real numbers.
 
 \begin{definition}[Annulus]\label{def_annuli}
-  A set of the form $A = \{x \in K \,|\, a \le \val(x) \le b\}$ for $a,b \in \R^*_+$ is called \emph{annulus}.
+  A set of the form $A = \{x \in K \,|\, a \le \val(x) \le b\}$, for $a,b \in \R^*_+$,
+  is called \emph{annulus}.
 \end{definition}
 
+\begin{definition}[Semidefinite-representable set]\label{def_annuli}
+  A set $S \subset K^n$ is called \emph{semide\-fi\-nite-re\-pre\-sen\-ta\-ble (SDR)} if there exist $m,d \in \N$ and
+  matrices $\{A_i,B_j : i = 0, \ldots, n, j = 1, \ldots, m\} \subset K^{d \times d}$ such that
+  $$
+  S = \left\{x \in K^n : \exists y \in K^m, A_0+\sum_{i=1}^n x_iA_i + \sum_{j=1}^m y_jB_j \succeq 0\right\}
+  $$
+  that is $S$ satisfies $x \in S$ if and only if there exists $y \in K^m$ such that
+  $(x,y) \in S_M \subset K^{n+m}$, for $M(x,y) = A_0+\sum_{i=1}^n x_iA_i + \sum_{j=1}^m y_jB_j$.
+  The integer $m$ is called the height of the representation.
+\end{definition}
+
+Of course spectrahedra are SDR sets with height $m=0$.
+In order to distinguish between spectrahedra and possibly non-spectrahedral semidefinite-representable sets
+we usually call \emph{spectrahedral shadows} the SDR sets with height $m>0$.
+
 \begin{theorem}
-Annuli are spectrahedral shadows.
+Annuli are spectrahedral shadows with height $m=1$.
 \end{theorem}
@@
   Let $A$ be as in \Cref{def_annuli}, for some $a,b \in \R^*_+$, assume $a<b$. Consider the spectrahedron
-  $\mathcal{S} \subset K^2$ defined by
+  $S_M \subset K^2$ defined by
   $$
-  \mathcal{S}= \left\{(x,y) \in K^2 : M(x,y) := \diag\left(\pi^ax, \pi^{-b}y, \begin{bmatrix} \pi^{-1} & -\pi^{-1}x \\ \pi^{-1}y & - \pi^{-1}  \\ \end{bmatrix}\right) \succeq 0\right\}.
+  S_M= \left\{(x,y) \in K^2 : M(x,y) := \diag\left(\pi^ax, \pi^{-b}y, \begin{bmatrix} \pi^{-1} & -\pi^{-1}x \\ \pi^{-1}y & - \pi^{-1}  \\ \end{bmatrix}\right) \succeq 0\right\}.
   $$

### 2024-11-20 article/paper_padic_spec.tex
commit by Simone

@@
   \end{equation*}
-  for some $d, e \in \mathbb{N}$. Let $\eta \leq n$ be the dimension of $M$ as vector subspace of
-  $K^n$, and let $y = (y_1, \ldots, y_\eta)^T \in K^{\eta}$ be variables on $M$, with $Ty = x$
-  for some $T \in K^{n \times \eta}$ with $\text{rank}(T) = \eta$. Let $A_0,A_1,\ldots,A_n \in K^{d \times d}$
+  for some $d, e \in \mathbb{N}$. Let $T : K^{\eta} \to K^n$ be a surjective linear map such that
+  $\text{im}(T) = M$, with $\eta = \dim(M)$.
+  Let $y = (y_1, \ldots, y_\eta)^T \in K^{\eta}$ be variables on $M$, so that $x \in M$ iff
+  $x = Ty$ for some $y \in K^{\eta}$. Let $A_0,A_1,\ldots,A_n \in K^{d \times d}$
   be such that
@@
   $$
-  P = \{x \in K^n : x \in M, \}
+  P = L \cap M = \{x \in K^n : x = Ty \in M, A_0+\sum_{i=1}^n x_iA_i \succeq 0\}.
   $$
-  {\bf à terminer -- Simone}  
 %%% OLD PROOF
@@
   $$
-We will show that $x \in A$ if and only if  there exists $y\in K$ such that $(x,y) \in \mathcal{S}$.
+We claim that $x \in A$ if and only if there exists $y \in K$ such that $(x,y) \in S_M$.
+
 Let $x,y \in K$. By \Cref{caracsdp}, $M(x,y) \succeq 0$ if and only if $(x,y)$ is a solution of

### 2024-11-20 article/paper_padic_spec.tex
commit by Simone

@@
 
-Recall that the {\it Newton polygon} $\mathcal{P}$ of a polynomial $P = \sum_{i=0}^{d} a_i T^i \in K[T]$ is
+Recall that the \emph{Newton polygon} $\mathcal{P}$ of a polynomial $P = \sum_{i=0}^{d} a_i T^i \in K[T]$ is
 defined as the inferior convex hull of the set $\{(i, \val a_i) \,|\, 0 \le i \le d\}$, {\it i.e.} the
@@
   $$
-  \mathcal{S} = \mathcal{L} \cap K^{d\times d}_+ = \left\{X \in K^{d \times d} : \exists \, x \in K^n, X = A_0+\sum_{x_i A_i}, X \succeq 0\right\}
+  \mathcal{S} = \mathcal{L} \cap K^{d\times d}_+ = \left\{X \in K^{d \times d} :
+  \exists \, x \in K^n, X = A_0 + \sum_{i=1}^n x_i A_i, X \succeq 0\right\}
   $$
@@
   in $K^n$}. Remark that the map $\varphi_A$ is onto $\mathcal{L}$ but not injective,
-  unless $A_1,\ldots,A_n$ are linearly indepedent.
+  unless $A_1,\ldots,A_n$ are linearly independent.
 \end{remark}
@@
 \begin{proof}
-  Let $P$ be a polyhedron in $K^n$. We show that there exist $d \in \mathbb{N}$ and
-  $A_0,A_1,\ldots,A_n \in K^{d \times d}$ such that $P = S_A$. Assume $P = L \cap M$ with
+  Let $P = L \cap M$ be a polyhedron in $K^n$, with
   \begin{equation*}
@@
   \end{equation*}
-  for some $d, e \in \mathbb{N}$. Let $T : K^{\eta} \to K^n$ be a surjective linear map such that
-  $\text{im}(T) = M$, with $\eta = \dim(M)$.
-  Let $y = (y_1, \ldots, y_\eta)^T \in K^{\eta}$ be variables on $M$, so that $x \in M$ iff
-  $x = Ty$ for some $y \in K^{\eta}$. Let $A_0,A_1,\ldots,A_n \in K^{d \times d}$
-  be such that
+  for some $d, e \in \mathbb{N}$.
+  %Let $T : K^{\eta} \to K^n$ be a surjective linear map such that
+  %$\text{im}(T) = M$, with $\eta = \dim(M)$.
+  %Let $y = (y_1, \ldots, y_\eta)^T \in K^{\eta}$ be variables on $M$, so that $x \in M$ iff
+  %$x = Ty$ for some $y \in K^{\eta}$.
+  Let $A_0,A_1,\ldots,A_n \in K^{d \times d}$ be such that
   $$
-  A_0+x_1A_1+\cdots+x_nA_n = \diag(\ell_1(x), \ldots, \ell_d(x)).
+  \varphi_A(x) := A_0+x_1A_1+\cdots+x_nA_n = \diag(\ell_1(x), \ldots, \ell_d(x)).
   $$
-  One has that
-  $$
-  P = L \cap M = \{x \in K^n : x = Ty \in M, A_0+\sum_{i=1}^n x_iA_i \succeq 0\}.
-  $$
+  One has $L = \varphi_A^{-1}(K^{d \times d}_+)$.
+  %and hence
+  %$$
+  %P = \{x \in K^n : x = Ty \in M, \varphi_A(x) \succeq 0\}.
+  %$$
+
+  \vspace{1cm}
+  In other words, we showed that there exist $d \in \mathbb{N}$ and
+  $A_0,A_1,\ldots,A_n \in K^{d \times d}$ such that $P = S_A$, as stated.
 %%% OLD PROOF

### 2024-11-20 article/paper_padic_spec.tex
end sec 4

@@
 
-\begin{remark}
-  As in the real case, one often abuses of notation, saying that the preimage
-  $S_A = \varphi_A^{-1}(K^{d \times d}_+) = \{x \in K^n : A_0+x_1A_1+\cdots+x_nA_n \succeq 0\}$
-  of $K^{d \times d}_+$ under the map $\varphi_A : K^n \to \mathcal{L} \subset K^{d \times d}$, defined as
-  $\varphi_A(x) = A_0+x_1A_1+\cdots+x_nA_n$, is a \emph{spectrahedron
-  in $K^n$}. Remark that the map $\varphi_A$ is onto $\mathcal{L}$ but not injective,
-  unless $A_1,\ldots,A_n$ are linearly independent.
+In the real case, one often abuses of the definition of spectrahedra, saying that the set
+$\{x \in \mathbb{R}^n : A_0+\sum_{i=1}^n x_iA_i \succeq 0\}$ is also a spectrahedron.
+Remark that this also yields that every affine subset of $\mathbb{R}^n$ is also
+a spectrahedron: indeed an affine equation $\ell(x) = 0$ is equivalent to the two inequalities
+$\ell(x) \geq 0 \leq -\ell(x)$. Over a valuation field it is necessary to give the following
+definition in order to include affine sets in the family of spectrahedra.
+
+\begin{definition}
+  \label{def_spectrahedra_Kn}
+  A \emph{spectrahedron in $K^n$} is any affine section of a set of the form
+  $$
+  S_A = \varphi_A^{-1}(K^{d \times d}_+) = \{x \in K^n : A_0+x_1A_1+\cdots+x_nA_n \succeq 0\}
+  $$
+  where $\varphi_A : K^n \to \mathcal{L} \subset K^{d \times d}$ is the map
+  $\varphi_A(x) = A_0+x_1A_1+\cdots+x_nA_n$.
 \end{remark}
+
+Remark that the map $\varphi_A$ in \Cref{def_spectrahedra_Kn} is onto $\mathcal{L}$ but not
+injective, unless $A_1,\ldots,A_n$ are linearly independent. Moreover $K^n$ (and thus every affine
+subset of $K^n$) is itself a spectrahedron, choosing $A_0 \succeq 0$ and $A_1=A_2=\cdots=A_n=0$.
 
@@
 has $(\mathcal{L}_1 \cap K^{d \times d}_+) \cap (\mathcal{L}_2 \cap K^{d \times d}_+) =
-(\mathcal{L}_1 \cap \mathcal{L}_2) \cap K^{d \times d}_+$ and
-$S_A \cap S_B = S_{\diag(A,B)}$, for two affine spaces $\mathcal{L}_1 = A_0+\span{A_1,\ldots,A_n}$
-et $\mathcal{L}_2 = A_0+\span{B_1,\ldots,B_n}$.
+(\mathcal{L}_1 \cap \mathcal{L}_2) \cap K^{d \times d}_+$
+, for two affine spaces
+$\mathcal{L}_1 = A_0+\span{A_1,\ldots,A_n}$ and $\mathcal{L}_2 = A_0+\span{B_1,\ldots,B_n}$,
+and
+$(L_1 \cap S_A) \cap (L_2 \cap S_B) = (L_1\cap L_2) \cap S_{\diag(A,B)}$ for
+two affine spaces $L_1,L_2 \subset K^n$.
 Moreover this class contains polyhedra in $K^n$.
 
-%\begin{remark}
-%	As in the real case, the spectrahedron associated with the affine plan $\mathcal{L}$ will often be identified with its preimage in $K^s$ (i.e.
-the set of vectors $x \in K ^s$ so that the linear matrix $A(x) = A_0 + x_1A_1 + \ldots + x_sA_s$ is positive semidefinite with $A_0,A_1,\ldots,A_s$ spanning $\mathcal{L}$).
-%\end{remark}
-
 \begin{proposition}
-  %%% OLD STATEMENT
-  %%% A polyhedron is a spectrahedron.
   A polyhedron in $K^n$ is a spectrahedron in $K^n$.
@@
 \begin{proof}
-  Let $P = L \cap M$ be a polyhedron in $K^n$, with
-  \begin{equation*}
-    \begin{aligned}
-    L &= \{x \in K^n : \val \ell_i(x) \geq 0, i=1, \ldots, d\} \\
-    M &= \{x \in K^n : \val m_j(x) = +\infty, j=1, \ldots, e\}
-    \end{aligned}
-  \end{equation*}
+  Assume $P = L \cap M$ be a polyhedron in $K^n$, with
+  $L = \{x \in K^n : \val \ell_i(x) \geq 0, i=1, \ldots, d\}$
+  and $M = \{x \in K^n : \val m_j(x) = +\infty, j=1, \ldots, e\}$,
   for some $d, e \in \mathbb{N}$.
-  %Let $T : K^{\eta} \to K^n$ be a surjective linear map such that
-  %$\text{im}(T) = M$, with $\eta = \dim(M)$.
-  %Let $y = (y_1, \ldots, y_\eta)^T \in K^{\eta}$ be variables on $M$, so that $x \in M$ iff
-  %$x = Ty$ for some $y \in K^{\eta}$.
   Let $A_0,A_1,\ldots,A_n \in K^{d \times d}$ be such that
@@
   $$
-  One has $L = \varphi_A^{-1}(K^{d \times d}_+)$.
-  %and hence
-  %$$
-  %P = \{x \in K^n : x = Ty \in M, \varphi_A(x) \succeq 0\}.
-  %$$
-
-  \vspace{1cm}
-  In other words, we showed that there exist $d \in \mathbb{N}$ and
-  $A_0,A_1,\ldots,A_n \in K^{d \times d}$ such that $P = S_A$, as stated.
+  One has $L = S_A = \varphi_A^{-1}(K^{d \times d}_+)$. Since $M \subset K^n$ is affine, 
+  $P$ is a spectrahedron in $K^n$.
+%  %and hence
+%  %$$
+%  %P = \{x \in K^n : x = Ty \in M, \varphi_A(x) \succeq 0\}.
+%  %$$
+%
+%  \vspace{1cm}
+%  In other words, we showed that there exist $d \in \mathbb{N}$ and
+%  $A_0,A_1,\ldots,A_n \in K^{d \times d}$ such that $P = S_A$, as stated.
 %%% OLD PROOF

### 2024-11-29 article/paper_padic_spec.tex
commit by Simone

@@
   $$
+  for some $d\in \mathbb{N}$,
   where $\varphi_A : K^n \to \mathcal{L} \subset K^{d \times d}$ is the map
-  $\varphi_A(x) = A_0+x_1A_1+\cdots+x_nA_n$.
-\end{remark}
+  $\varphi_A(x) = A_0+x_1A_1+\cdots+x_nA_n$, and $\mathcal{L} = A_0+\span{A_1,\ldots,A_n}$.
+\end{definition}
 
@@
 
-\subsection{Annuli}
+\subsection{Polyannuli}
 
@@
 
-\begin{definition}[Annulus]\label{def_annuli}
-  A set of the form $A = \{x \in K \,|\, a \le \val(x) \le b\}$, for $a,b \in \R^*_+$,
-  is called \emph{annulus}.
+\begin{definition}[Polyannulus]\label{def_annuli}
+  A set of the form $C = \{x \in K \,|\, a \le \val(x) \le b\}$, for $a,b \in \R^*_+$,
+  is called \emph{annulus}. A product $C_1 \times C_2 \times \cdots \times C_n \subset K^n$,
+  where each $C_i \subset K$ is an annulus, is called a \emph{polyannulus}.
 \end{definition}
@@
   $$
-  that is $S$ satisfies $x \in S$ if and only if there exists $y \in K^m$ such that
+  that is, $x \in S$ if and only if there exists $y \in K^m$ such that
   $(x,y) \in S_M \subset K^{n+m}$, for $M(x,y) = A_0+\sum_{i=1}^n x_iA_i + \sum_{j=1}^m y_jB_j$.
-  The integer $m$ is called the height of the representation.
+  The integer $m$ is called the \emph{height} of the representation and $d$ its \emph{degree}.
 \end{definition}
 
-Of course spectrahedra are SDR sets with height $m=0$.
-In order to distinguish between spectrahedra and possibly non-spectrahedral semidefinite-representable sets
+Of course a spectrahedron $S_A = \varphi_A^{-1}(K^{d \times d})$ is SDR with height $m=0$ and degree
+$d$. In order to distinguish between spectrahedra and possibly non-spectrahedral semidefinite-representable sets
 we usually call \emph{spectrahedral shadows} the SDR sets with height $m>0$.
@@
 \begin{theorem}
-Annuli are spectrahedral shadows with height $m=1$.
+Polyannuli in $K^n$ are spectrahedral shadows with height $m=n$ and degree $d=4n$.
 \end{theorem}
 \begin{proof}
-  Let $A$ be as in \Cref{def_annuli}, for some $a,b \in \R^*_+$, assume $a<b$. Consider the spectrahedron
+  Let $C = C_1 \times \cdots \times C_n \subset K^n$ be as in \Cref{def_annuli},
+  for some annuli $C_1,\ldots,C_n \subset K$. We claim that each $C_i$ is a spectrahedral
+  shadow of height $1$ and degree $4$. Assume $C_i = \{x \in K : a_i \leq \val(x) \leq b_i\}$
+  for some $a_i, b_i \in \R^*_+$ with $a_i < b_i$. Consider the spectrahedron
+
+  %%% ARRIVATO QUI
   $S_M \subset K^2$ defined by

### 2024-11-29 article/paper_padic_spec.tex
commit by Simone

@@
   for some annuli $C_1,\ldots,C_n \subset K$. We claim that each $C_i$ is a spectrahedral
-  shadow of height $1$ and degree $4$. Assume $C_i = \{x \in K : a_i \leq \val(x) \leq b_i\}$
+  shadow of height $1$ and degree $4$. Assume $C_i = \{x_i \in K : a_i \leq \val(x_i) \leq b_i\}$
   for some $a_i, b_i \in \R^*_+$ with $a_i < b_i$. Consider the spectrahedron
-
-  %%% ARRIVATO QUI
-  $S_M \subset K^2$ defined by
-  $$
-  S_M= \left\{(x,y) \in K^2 : M(x,y) := \diag\left(\pi^ax, \pi^{-b}y, \begin{bmatrix} \pi^{-1} & -\pi^{-1}x \\ \pi^{-1}y & - \pi^{-1}  \\ \end{bmatrix}\right) \succeq 0\right\}.
-  $$
-We claim that $x \in A$ if and only if there exists $y \in K$ such that $(x,y) \in S_M$.
-
-Let $x,y \in K$. By \Cref{caracsdp}, $M(x,y) \succeq 0$ if and only if $(x,y)$ is a solution of
-\eqref{eq:annulussyst}:
+  $S_{M^{(i)}} \subset K^2$ defined by
+  $$
+  S_{M^{(i)}} = \left\{(x_i,y_i) \in K^2 :
+  M^{(i)}(x_i,y_i) := \diag\left(\pi^a x_i, \pi^{-b} y_i,
+  \begin{bmatrix}
+    \pi^{-1} & -\pi^{-1} x_i  \\
+    \pi^{-1} y_i & - \pi^{-1} \\
+  \end{bmatrix}\right) \succeq 0
+  \right\}.
+  $$
+  We claim that $x_i \in C_i$ if and only if there exists $y_i \in K$ such that $(x_i,y_i) \in S_{M^{(i)}}$.
+  Indeed, by \Cref{caracsdp}, $M^{(i)}(x_i,y_i) \succeq 0$ if and only if $(x_i,y_i)$ is a solution of the system
+  of inequalities:
   \begin{equation}
@@
     \begin{cases}
-  \val(\pi^ax) \ge 0 \\
-  \val(\pi^{-b}y) \ge 0\\
+      \val(\pi^a x_i) \ge 0 \\
+  \val(\pi^{-b} y_i) \ge 0\\
   \val(\pi^{-1}- \pi^{-1}) = +\infty \ge 0\\
-  \val(\pi^{-2}\left( xy-1 \right))  \ge 0 
+  \val(\pi^{-2}\left( x_iy_i-1 \right))  \ge 0 
 \end{cases}
@@
 \begin{cases} 
-		\val\left(x\right)\ge a\\
-		\val\left(y\right)\ge -b\\
-		\val\left( xy-1 \right) \ge 2
+  \val\left(x_i\right)\ge a\\
+  \val\left(y_i\right)\ge -b\\
+  \val\left(x_iy_i-1 \right) \ge 2
 \end{cases}
 \end{equation}
-Therefore, if $(x, y)$ verifies \eqref{eq:annulussyst} then $\val\left(x\right)\ge a$, $\val\left(y\right)\ge -b$ and $ \left( xy-1 \right) \ge 2$.
-The last inequality implies that $\val\left(x\right)+\val\left(y\right)=\val\left(xy\right) = \val\left(-1\right) =0$ and therefore that $\val\left(x\right)=-\val\left(y\right)\le -(-b)  =b$, so $x \in C$.
-Reciprocally if $x \in C$ then $(x,x^{-1}) $ is a solution of \eqref{eq:annulussyst}.
+  %Therefore, if $(x, y)$ verifies \eqref{eq:annulussyst} then $\val\left(x\right)\ge a$, $\val\left(y\right)\ge -b$ and $ \left( xy-1 \right) \ge 2$.
+  The last inequality implies that $\val\left(x_i\right)+\val\left(y_i\right)=\val\left(x_iy_i\right) = \val\left(-1\right) =0$ and therefore that $\val\left(x_i\right)=-\val\left(y_i\right)\le -(-b) = b$, so $x_i \in C_i$.
+Reciprocally if $x_i \in C_i$ then $(x_i,x_i^{-1})$ is a solution of \eqref{eq:annulussyst}.
+This proves our claim.
+Finally, since $C = C_1 \times \cdots \times C_n$, one has
+\begin{equation*}
+  \begin{aligned}
+    C &=
+    \{x=(x_1,\ldots,x_n) \in K^n : \exists y = (y_1,\ldots,y_n) \in K^n, (x_i,y_i) \in S_{M^{(i)}}, i=1,\ldots,n\} \\
+    &= \{x \in K^n : \exists y \in K^n, (x,y) \in S_M\}
+  \end{aligned}
+\end{equation*}
+with $S_M = \diag\left(M^{(1)}, M^{(2)}, \ldots, M^{(n)}\right) \in K[x,y]^{4n \times 4n}.$
 \end{proof}

### 2024-11-29 article/paper_padic_spec.tex
commit by Simone

@@
 The $K$-vector space of polynomials of degree $\leq d$ on $x=(x_1,\ldots,x_n)$
-with coefficients in $K$ is denoted by $K[x]_{d}$. The vector space of matrices of
+with coefficients in $K$ is denoted by $K[x]_{d}$. The ring of matrices of
 size $p \times q$ with entries in a ring $R$ is $R^{p \times q}$ and the general

### 2024-12-01 article/paper_padic_spec.tex
caracterisation fo polyhedra and specatrahedron not polyhedral

@@
 This concludes the proof.
+\end{proof}
+
+\begin{proposition}[Caracterisation of polyhedron] \label{prop:carac}
+    Polyhedra are either empty or the image of polydiscs  under a linear mapping.
+\end{proposition}
+
+\begin{proof}
+    Let $\mathcal{P}$ be a polyhedron in $K^n$. Then $\mathcal{P} = \{x \in K^n : Ax+B \ge 0, Dx = e\}$ for some $A \in K^{d \times n}, b \in K ^d,  D\in  K^{m\times n}, e \in K^m$.
+
+    If $\mathcal{P}$ is nonempty then there exists $x_0 \in K^n$ such that $Dx_0=e$.
+Let $J \in K^{n \times R}$ such that $\textrm{Im} J = \ker D$ where $R$ denotes the dimension of $\ker D$.
+Then $\mathcal{P} = x_0 + J\mathcal{P}'$ where $A' := AJ$ $b' := Ax_0 + b$ and  $\mathcal{P'} := \{y \in K ^R: A'y + b' \ge 0 \}$.
+
+    Now let $S \in K^{n\times R}$ be the SNF of $A'$ and $Q \in \mathbf{GL}_n\left(\mathcal{O}_K\right)$ and $P \in \mathbf{GL}_R\left(\mathcal{O}_K\right)$ such that $A'= Q S P^{-1}$.
+    Then $\mathcal{P'} = \{y \in K^R : QSP^{-1}y + b' \ge  0\} = P\{z \in K^R : Sz + Q^{-1}b' \ge 0 \}$.
+    Let $b'':=Q^{-1}b$ then $P' = P \{z \in K^R : s_i z_i + b''_i \ge 0, i= 1\ldots R\}$.
+The set $\{z \in K^R : s_i z_i + b_i \ge 0\}$ is either empty or a polydisc (with eventually infinite radii) and $\mathcal{P} = x_0 + JP \{z \in K^R: s_i z_i + b_i \ge  0, i=1,\ldots,R\}$ which concludes the proof.
+
+\end{proof}
+
+\begin{corollary} \label{cor:caracdim1}
+   If $\mathcal{P}$ is a polyhedron in $K$ then $\mathcal{P}$ is either empty or a ball (eventually with infinite radius).
+\end{corollary}
+
+\begin{proof}
+    Let $\mathcal{P}$ be such polyhedron.
+We assume that $\mathcal{P} \neq \emptyset$.
+By \ref{prop:carac} there exist a polydisc $D = \{x \in K^n : \val s_i x_i - b_i \ge 0, i=1,\ldots,n \}$ for some $s_1,\ldots,s_n, b_1,\ldots,b_n \in K ^n$ and an affine map $f : K^n \to K$ such that $\mathcal{P} = f(D)$.
+    Let $a_0,a_1,\ldots,a_n \in K$ such that $f(x) = a_0 + a_1 x_1 + \ldots + a_n x_n$. We can assume, with no loss of generality, that the $a_i$'s are nonzero.
+
+If there exists $i_0 \in \{1,\ldots,n\}$ such that $s_{i_0} = 0$ then $\mathcal{P} = f(D) = K$ and $\mathcal{P}$ is a ball of infinite radius.
+Otherwise, we have $D = \{x \in K^n : x_i = \frac{b_i}{s_i} + O\left( \pi^{-val s_i} \right), i=1,\ldots,n \}$ and therefore for all $x \in  K$, $x \in P$ if and only if $x = a_0 + \sum_{i=1}^{n}( \frac{a_i b_i}{s_i} + O\left( \pi^{\val a_i - \val s_i} \right))= a_0  + \sum_{i=1}^{n} \frac{a_i b_i}{s_i} + O(\pi^d)$ where $d = \min \limits_{i = 1,\ldots,n} \val a_i - \val s_i$.
+Thus $\mathcal{P} = \{x \in K : \val (x - a_0 - \sum_{i=1}^{n} \frac{a_i b_i}{s_i}) \ge d \}$ is a ball.
+
 \end{proof}
@@
 %  %Define $B = m_1 \oplus \cdots \oplus m_e \in K[x]^{e\times e}_1$
+\end{proof}
+
+\begin{example}
+    The spectrahedron
+\[
+    \mathcal{S} = \left\{x \in K ; M(x) := \begin{bmatrix} 0 & x + \pi^{-1} \\ x & 0 \end{bmatrix} \succeq 0\right\}
+\] 
+    is not a polyhedron.
+\end{example}
+    \begin{proof}
+        By \ref{caracsdp} $S = \{x \in K, \val( x (x + \pi^{-1})) \ge 0\} = \{x \in K: \val x \ge 1\} \cup \{x \in K: \val (x - \pi^{-1}) \ge 1\}$which is not a ball.
+Therefore, by \ref{cor:caracdim1}, $S$ is not a polyhedron.
+
     \end{proof}

### 2024-12-10 article/paper_padic_spec.tex
Première version d'une preuve que si le corps résiduel est infini, les courrones de K ne peuvent pas être des spectraèdres.

@@
 \newtheorem{theorem}{Theorem}[section]
-\newtheorem{lemma}{Lemma}
-\newtheorem{proposition}{Proposition}
-\newtheorem{corollary}{Corollary}
-\newtheorem{algorithm}{Algorithm}
-\newtheorem{conjecture}{Conjecture}
-\newtheorem{condition}{Condition}
-\newtheorem{definition}{Definition}
-\newtheorem{assumption}{Assumption}
-\newtheorem{remark}{Remark}
-\newtheorem{problem}{Problem}
-\newtheorem{example}{Example}
-\newtheorem{notation}{Notation}
+\newtheorem{lemma}[theorem]{Lemma}
+\newtheorem{proposition}[theorem]{Proposition}
+\newtheorem{corollary}[theorem]{Corollary}
+\newtheorem{algorithm}[theorem]{Algorithm}
+\newtheorem{conjecture}[theorem]{Conjecture}
+\newtheorem{condition}[theorem]{Condition}
+\newtheorem{definition}[theorem]{Definition}
+\newtheorem{assumption}[theorem]{Assumption}
+\newtheorem{remark}[theorem]{Remark}
+\newtheorem{problem}[theorem]{Problem}
+\newtheorem{example}[theorem]{Example}
+\newtheorem{notation}[theorem]{Notation}
 \usepackage{booktabs}
@@
 discrete valuation field, $\val : K \twoheadrightarrow \ZZ \cup \{+\infty\}$ to its valuation,
-$\OK$ its ring of integers and $\pi$ a uniformizer.
+$\OK$ its ring of integers, $\kappa$ its residue field and $\pi$ a uniformizer.
 For $k \in \N$, we write $O(\pi^k)$ for $\pi^k \OK$.
@@
 
-\begin{definition}[Semidefinite-representable set]\label{def_annuli}
+\begin{definition}[Semidefinite-representable set]\label{def_semi_def_rep_set}
   A set $S \subset K^n$ is called \emph{semide\-fi\-nite-re\-pre\-sen\-ta\-ble (SDR)} if there exist $m,d \in \N$ and
@@
 
+\begin{proposition}
+If the residue field $\kappa$ is infinite, then
+no (non-trivial) annulus of $K$ can be a spectrahedron of $K.$
+\end{proposition}
+\begin{proof}
+By Definition \ref{def_spectrahedra_Kn}, a spectrahedron in $K$ 
+can be defined as the set $\{x \in K : A_0+x_1A_1 \succeq 0\}$
+for some integer $n$ and matrices $A_0$ and $A_1$ in $K^{n \times n}$.
+Thanks to Theorem \ref{caracsdp},
+this set corresponds to an intersection of the form
+$\cap_{i=0}^{n-1} \{ x \in K : \val(a_i(x)) \geq 0 \},$
+for some polynomials $a_i$'s, univariate over $K$.
+
+Following Julian Rüth's PhD thesis \cite{ruth_models_2015},
+the set $\{ x \in K : \val(a_i(x)) \geq 0 \}$
+is denoted by $\textrm{Disk}(a_i,0)$ and is called 
+a diskoid.
+By \cite[Lemma 4.44]{ruth_models_2015}, the intersection
+of two diskoids is either empty or a diskoid.
+Consequently, spectrahedra of $K$ are diskoids.
+
+By \cite[Lemma 4.43]{ruth_models_2015}, if $K$
+contains the roots of $\Phi$ then the diskoid
+$D=\textrm{Disk}(\Phi, \lambda)$ is the finite union
+of closed balls of equal radius centered at the roots of $f$ (and their common radius can be made explicit).
+
+Finally, if $\kappa$ is infinite, one can remark that the sphere
+$\{x \in K \,|\,  \val(x) =0\}$ is equal to the infinite disjoint union $\amalg_{l \in \kappa} B(b_l, \vert \pi \vert)$ for some 
+representatives $b_l \in O_K$ of the classes of $O_K / \pi O_K=\kappa.$
+It thus can not be covered by a finite amount of balls of radius $\vert \pi \vert$
+and if one take any ball of radius $1$ centered at a point of the sphere, then one gets the whole
+$B(0,1).$
+A direct generalization of this argument proves that
+if $\kappa$ is infinite, no (non trivial) annulus can be equal to
+a finite union of balls. Thus, no (non trivial) annulus can be a diskoid and finally, no (non trivial) annulus can be a spectrahedron.
+\end{proof}
+
 %\subsection{Polyhedrality}

### 2025-01-21 article/paper_padic_spec.tex
commit by Simone
footnote on rem 3.3

@@
 %%%\newenvironment{proof}{\hbox{}\vspace{-0.8cm} {\bf Proof:}}{\hfill $\Box$ \vspace{0.2cm}}
+
+\usepackage{geometry}
+\geometry{
+ a4paper,
+ %total={170mm,257mm},
+ left=35mm,
+ top=40mm,
+ bottom=20mm
+}
 
@@
 
-\tableofcontents
+%\tableofcontents
 
@@
 
-In this section we show that the image of a polyhedron by a linear mappingA is a polyhedron. 
+In this section we show that the image of a polyhedron by a linear mapping is a polyhedron. 
 We first prove the result in the cases of authomorphisms of $\OK^n$ and diagonal endomorphisms of $K^n$.
-Then we use these particular cases to prove the result for projections of the form $(x_1,\dots,x_n) \mapsto (x_1,\dots, x_{n-1})$
-and finally for the general case.
+Then we use these particular cases to prove the result for projections of the form
+$(x_1,\dots,x_n) \mapsto (x_1,\dots, x_{n-1})$ and finally for the general case.
 
 \begin{remark}
- First, let $f : K^n \to K^m$ be a linear map and $\PP \subset K^n$ be a polyhedron defined by 
+  First, let $f : K^n \to K^m$ be a linear map and let $\PP \subset K^n$ be a polyhedron defined by 
 $\PP = \left\lbrace x \in K^n : \val (l_i (x) ) \geq 0, m_i(x)=0, \textrm{ for } i \in I, j \in J \right\rbrace$ 
-for some finite sets $I \subset \N$ and $J \subset \mathbb{N}$ and $m_j, l_i \in K[x]_1$, for $i \in I$  and $j \in J$.
+  for some finite sets $I \subset \N$ and $J \subset \mathbb{N}$ and $m_j, l_i \in K[x]_1$, for $i \in I$  and
+  $j \in J$.
 Then  $\PP = \PP_i \cap \PP_e$ where $\PP_i := \{x \in K^n : \val(l_i(x)) \ge 0, i = 1,\dots,d\}$
@@
 
-Thus, we have  $f(\PP) = f(\PP_i) \cap f(\PP_e)$.
+Thus, we have\footnote{\simone{attention, ça est vrai si $f$ est injective, en général on a seulement
+$\subset$}}  $f(\PP) = f(\PP_i) \cap f(\PP_e)$.
 However, $\PP_e$ is either empty or an affine subspace of $K^n$ and therefore 

### 2025-03-17 article/paper_padic_spec.tex
commit by Simone

@@
 
-\author{Corentin Cornou$^{1}$, Simone Naldi$^{2,3}$ and Tristan Vaccon$^{2}$}
+\author{Corentin Cornou$^{1}$, Simone Naldi$^{2}$ and Tristan Vaccon$^{2}$}
 
@@
 \footnotetext[2]{Université de Limoges, CNRS, XLIM, UMR 7252, F-87000 Limoges, France.}
-\footnotetext[3]{Sorbonne Université, CNRS, LIP6, Equipe PolSys, F-75005 Paris, France.}
+%\footnotetext[3]{Sorbonne Université, CNRS, LIP6, Equipe PolSys, F-75005 Paris, France.}
 
@@
   Real polyhedra and real spectrahedra (or their projections) are respectively the feasible sets
-  of linear programming (LP) and semidefinite programming (SDP) and form the family of
+  of linear and semidefinite programming, and form the family of
   semidefinite-representable sets. This paper investigates versions of these sets and of
@@
 \section{Introduction}
+
+Linear programming
+
+A natural generalization of LP is {\it semidefinite programming}
+
+Contrary to the LP case, the complexity status of SDP is mostly open.
+
+Similar generalizations have been recently proposed in the context of tropical geometry \cite{iriarte2022polyhedral}.
 

### 2025-03-17 article/paper_padic_spec.tex
commit by Simone

@@
 
-Linear programming
-
-A natural generalization of LP is {\it semidefinite programming}
-
-Contrary to the LP case, the complexity status of SDP is mostly open.
-
+The study of polyhedra and of linear programming (LP) is at the heart of convex geometry and optimization,
+inasmuch as several optimization problems can be cast as, or relaxed to LP. An important generalization of LP
+is semidefinite programming (SDP), namely the problem of minimizing an affine polynomial over the set of
+positive semidefinite affine combinations of a given collection of real symmetric matrices.
+
+Contrary to the LP case, the complexity status of SDP is widely open.
+In a fixed-precision model of computation, SDP is solvable in polynomial time in the input size (matrix size,
+number of variables, bit size of the coefficients), in $\log(\frac{1}{\varepsilon})$ (where $\varepsilon$ is the
+precision) and $\log(\frac{1}{R})$, where $R$ is an {\it a priori} upper bound on the norm of a solution,
+cf. \cite[Sec.1.9]{deKlerk}. In exact arithmetic, the complexity status of SDP is essentially open but complexity
+bounds are known based either on general quantifier elimination \cite{ramana1997exact,porkolab1997complexity}
+or by exploiting the determinantal structure of the constraints \cite{henrion2016exact}.
+
+In this paper we 
 Similar generalizations have been recently proposed in the context of tropical geometry \cite{iriarte2022polyhedral}.
@@
 
-In a fixed-precision model of computation, SDP is solvable in polynomial time in the input size (matrix size,
-number of variables, bit size of the coefficients), in $\log(\frac{1}{\varepsilon})$ (where $\varepsilon$ is the
-precision) and $\log(\frac{1}{R})$, where $R$ is an {\it a priori} upper bound on the norm of a solution,
-cf. \cite[Sec.1.9]{deKlerk}. In exact arithmetic, the complexity status of SDP is essentially open but complexity
-bounds are known based either on general quantifier elimination \cite{ramana1997exact,porkolab1997complexity}
-or by exploiting the determinantal structure of the constraints \cite{henrion2016exact}.
+% IN INTRODUCTION
+%In a fixed-precision model of computation, SDP is solvable in polynomial time in the input size (matrix size,
+%number of variables, bit size of the coefficients), in $\log(\frac{1}{\varepsilon})$ (where $\varepsilon$ is the
+%precision) and $\log(\frac{1}{R})$, where $R$ is an {\it a priori} upper bound on the norm of a solution,
+%cf. \cite[Sec.1.9]{deKlerk}. In exact arithmetic, the complexity status of SDP is essentially open but complexity
+%bounds are known based either on general quantifier elimination \cite{ramana1997exact,porkolab1997complexity}
+%or by exploiting the determinantal structure of the constraints \cite{henrion2016exact}.
 

### 2025-03-17 article/paper_padic_spec.tex
commit by Simone

@@
 The study of polyhedra and of linear programming (LP) is at the heart of convex geometry and optimization,
-inasmuch as several optimization problems can be cast as, or relaxed to LP. An important generalization of LP
+inasmuch as several optimization problems can be cast as, or reduced to LP. An important generalization of LP
 is semidefinite programming (SDP), namely the problem of minimizing an affine polynomial over the set of
-positive semidefinite affine combinations of a given collection of real symmetric matrices.
+positive semidefinite affine combinations of a given collection of real symmetric matrices. The latter problem 
+has interested the community of polynomial optimization because of the relaxation method known as moment-SOS
+(or Lasserre) hierarchy \cite{henrion2020moment}.
 
@@
 
-In this section we show that the image of a polyhedron by a linear mapping is a polyhedron. 
+In this section we show that the image of a polyhedron by a linear mapping is a polyhedron,
+and discuss some consequences.
 We first prove the result in the cases of authomorphisms of $\OK^n$ and diagonal endomorphisms of $K^n$.
@@
 \begin{remark}
-  First, let $f : K^n \to K^m$ be a linear map and let $\PP \subset K^n$ be a polyhedron defined by 
-$\PP = \left\lbrace x \in K^n : \val (l_i (x) ) \geq 0, m_i(x)=0, \textrm{ for } i \in I, j \in J \right\rbrace$ 
-  for some finite sets $I \subset \N$ and $J \subset \mathbb{N}$ and $m_j, l_i \in K[x]_1$, for $i \in I$  and
-  $j \in J$.
-Then  $\PP = \PP_i \cap \PP_e$ where $\PP_i := \{x \in K^n : \val(l_i(x)) \ge 0, i = 1,\dots,d\}$
-and $\PP_e := \{x \in K^n : m_j(x) = 0, j = 1,\dots,e\}$.
-
-Thus, we have\footnote{\simone{attention, ça est vrai si $f$ est injective, en général on a seulement
-$\subset$}}  $f(\PP) = f(\PP_i) \cap f(\PP_e)$.
-However, $\PP_e$ is either empty or an affine subspace of $K^n$ and therefore 
-$f(\PP_e)$ is either empty or an affine subspace of $K^m$, so it is a polyhedron.
-Hence, as the class of polyhedron is closed under intersection to prove that
-$f(\PP)$ is a polyhedron it is sufficient to prove that $f(\PP_i)$ is one.
+  Let $f : K^n \to K^m$ be a linear map and let
+  $P = \{x \in K^n : \val(l_i(x)) \geq 0, m_i(x) = 0, 1 \leq i \leq d, 1 \leq j \leq e\}$.
+  Then $P = P_I \cap P_E$ where $P_I := \{x \in K^n : \val(l_i(x)) \geq 0, 1 \leq i \leq d\}$
+  and $P_E := \{x \in K^n : m_j(x) = 0, 1 \leq j \leq e\}$.
+
+  Thus we have\footnote{\simone{Est-ce vrai parce que $P_E$ est affine? Car en général il faut que
+    $f$ soit injective}} $f(P) = f(P_I) \cap f(P_E)$. However $P_E$ is either empty or an affine subspace of
+  $K^n$ and therefore $f(P_E)$ is either empty or an affine subspace of $K^m$, so it is a polyhedron.
+  Hence, as the class of polyhedra is closed under intersection, in order to prove that
+  $f(P)$ is a polyhedron, it is sufficient to prove that this holds for $f(P_I)$.
 \end{remark}
 
-Therefore, we can only consider the image of polyhedron of the form 
-$\left\lbrace x \in K^n : \val (l_i (x) ) \geq 0 \textrm{ for } i \in I \right\rbrace$.
+Therefore below we consider polyhedra of the form as in \Cref{def_polyhedra} with $e=0$.
 
@@
 
-\begin{proposition}[Caracterisation of polyhedron] \label{prop:carac}
+We recall that the Minkowski sum of two sets $A$ and $B$ is $A+B = \{a+b : a \in A, b \in B\}$.
+
+\begin{corollary}
+The Minkowski sum of two polyhedra in $K^n$ is a polyhedron in $K^n$.
+\end{corollary}
+\begin{proof}
+  Straightforward from the equality
+  $P_1 + P_2 = \{z \in K^n : x \in P_1, y \in P_2, x+y=z\}.$
+\end{proof}
+
+\begin{proposition}[Characterization of polyhedra] \label{prop:carac}
     Polyhedra are either empty or the image of polydiscs under a linear mapping.
 \end{proposition}
-
 \begin{proof}

### 2025-03-17 article/paper_padic_spec.tex
commit by Simone

@@
 
-  Thus we have\footnote{\simone{Est-ce vrai parce que $P_E$ est affine? Car en général il faut que
-    $f$ soit injective}} $f(P) = f(P_I) \cap f(P_E)$. However $P_E$ is either empty or an affine subspace of
+  Thus we have\footnote{\simone{Ça n'est pas vrai en général, il faut que $f$ soit injective.
+    Il faut peut être d'abord factoriser $f = g \circ h$ avec $h : K^n \to im(f)$ et
+    $g : im(f) \subset K^m$.}}
+  $f(P) = f(P_I) \cap f(P_E)$. However $P_E$ is either empty or an affine subspace of
   $K^n$ and therefore $f(P_E)$ is either empty or an affine subspace of $K^m$, so it is a polyhedron.

### 2025-03-17 article/paper_padic_spec.tex
commit by Simone

@@
 
-\begin{proposition}
-  Let $\PP \subset K^n$ be a polyhedron and $f : K^n \to K^n$ be a linear mapping.
+\begin{proposition}\simone{l'enoncé est incomplet}
+  Let $P \subset K^n$ be a polyhedron and let $f : K^n \to K^n$ be a linear mapping.
   If $f \in \GL_n(\OK)$ or if there exists $\lambda_1, \dots, \lambda_n \in K$ such that
@@
 
-The two above results allows us to demonstrate the following proposition, which we will use to prove the general case.
+The two above results\footnote{\simone{il y en an un}}
+allows us to demonstrate the following proposition, which we will use to prove the general case.
 

### 2025-03-17 article/paper_padic_spec.tex
ok sec 4.1 4.2

@@
   $$
-  M = \begin{bmatrix} 5 + \frac{3}{5} & \frac{4}{5} \\ \frac{4}{5} & -\frac{3}{5} \end{bmatrix}.
+  M = \begin{bmatrix} \frac{3}{5}+5 & \frac{4}{5} \\ \frac{4}{5} & -\frac{3}{5} \end{bmatrix}.
   $$
@@
 
+Spectrahedra form a strict generalization of polyhedra:
+
 \begin{example}
@@
   \[
-    \mathcal{S} = \left\{x \in K ; M(x) := \begin{bmatrix} 0 & x + \pi^{-1} \\ x & 0 \end{bmatrix} \succeq 0\right\}
+  S = \left\{x \in K : \begin{bmatrix} 0 & x + \pi^{-1} \\ x & 0 \end{bmatrix} \succeq 0\right\}
   \] 
@@
 \begin{proof}
-        By \ref{caracsdp} $S = \{x \in K, \val( x (x + \pi^{-1})) \ge 0\} = \{x \in K: \val x \ge 1\} \cup \{x \in K: \val (x - \pi^{-1}) \ge 1\}$which is not a ball.
-Therefore, by \ref{cor:caracdim1}, $S$ is not a polyhedron.
-
+  By \Cref{caracsdp}, one has $S = \{x \in K : \val(x(x + \pi^{-1})) \geq 0\} =
+  \{x \in K: \val x \ge 1\} \cup \{x \in K: \val (x - \pi^{-1}) \ge 1\}$ which is not a ball.
+  Therefore, by \Cref{cor:caracdim1}, $S$ is not a polyhedron.
 \end{proof}
@@
 \begin{proof}
-  Let $S = S_A \subset K^n$ be spectrahedron, for some linear matrix $A(x) = A_0+\sum_{i=1}^n x_i A_i$. 
-  Denote by $p_i(x) \in K[x]$ the $i$-th coefficient of $\chi_{A(x)}$, $i=0,\ldots,d$.
+  Let $S = S_A \subset K^n$ be spectrahedron, for some linear matrix $A = A_0+\sum_{i=1}^n x_i A_i$. 
+  Denote by $p_i \in K[x]$ the $i$-th coefficient of $\chi_{A}$, $i=0,\ldots,d$.
   By \Cref{caracsdp} one has:
   $$
-  S = \left\{x \in K^n : \chi_{A(x)} \in \OK[T]\right\}
+  S = \left\{x \in K^n : \chi_{A} \in \OK[T]\right\}
   = \bigcap_{i=0}^d \{x \in K^n : \val(p_i(x)) \geq 0\}.

### 2025-05-15 article/paper_padic_spec.tex
notation null and identity matrix

@@
 linear group in $R^{n \times n}$ is $\GL_n(R)$.
-For the sake
-of ease of writing, block-diagonal matrices with blocks $B_1,\ldots,B_d$ are denoted by
-$\diag(B_1, \ldots, B_d)$.
+For the sake of ease of writing, block-diagonal matrices with blocks
+$B_1,\ldots,B_d$ are denoted by $\diag(B_1, \ldots, B_d)$, the null square
+matrix of size $t$ by ${\bf 0}_{t}$, and the identity matrix by $I_t$.
 
@@
   $$
-  SNF(M) := QMP^{-1} = \diag(\pi^{a_1}, \pi^{a_2}, \ldots, \pi^{a_r}, {\bf 0}_{\min(m,n)-r})
-  $$
-  where ${\bf 0}_{t}$ is a null square matrix of size $t$.
+  SNF(M) := QMP^{-1} = \diag(\pi^{a_1}, \pi^{a_2}, \ldots, \pi^{a_r}, {\bf 0}_{\min(m,n)-r}).
+  $$
   The matrix $SNF(M)$ is called the \emph{Smith Normal Form (SNF)} of $M$, and the elements $\pi^{a_i}$ the
@@
 
-A \emph{linear programming problem} (or simply \emph{linear program}) \emph{with data $(A,b,c,D,e)$} is defined
+A \emph{linear programming problem} (or \emph{linear program}) \emph{with data $(A,b,c,D,e)$} is defined
 as:

### 2025-05-15 article/paper_padic_spec.tex
commit by Simone

@@
 \begin{array}{rcll}
-  p^* & := & \inf_{x \in K^n} & \val(\left\langle c, x \right\rangle) \\
+  p^* & := & \inf_{x \in K^n} & \val \left\langle c, x \right\rangle \\
   &    & \text{s.t.}         & A x + b \geq 0\\
@@
 \end{equation}
-with $c \in K^n$ a fixed vector of size $n$ that represents the cost, $A \in \allmat_{d,n}(K)$, $b \in K^d$, $D \in \allmat_{m,n}$, $e \in K^m$ 
-and $\left\langle c, x \right\rangle := c_1 x_1+\cdots +c_n x_n$. When $A$ is a diagonal matrix and $D = 0$, we often
-refer to \eqref{LP} as a \emph{diagonal} linear program. We denote the \emph{feasible set} of \eqref{LP} by
+with $c \in K^n$ a fixed vector of size $n$ that represents the cost,
+$A \in K^{d \times n}$, $b \in K^d$, $D \in K^{m\times n}$, $e \in K^m$ 
+and $\left\langle c, x \right\rangle := c_1 x_1+\cdots +c_n x_n$.
+When $A$ is a diagonal matrix and $D = 0$\footnote{\simone{pourquoi la contrainte $D=0$ ?}}, we often refer to \eqref{LP} as a \emph{diagonal} linear program.
+We denote the \emph{feasible set} of \eqref{LP} by
 \begin{equation*}
@@
 \end{equation*}
-A vector $x \in K^n$ is called \emph{feasible} for~\eqref{LP} if $x \in \PP$. A feasible vector $x^* \in \PP$
-is called a \emph{solution} to \eqref{LP} if $p^* = \left\langle c,x^*\right\rangle$.
+A vector $x \in K^n$ is called \emph{feasible} for~\eqref{LP} if $x \in \PP$.
+A feasible vector $x^* \in \PP$ is called a \emph{solution} to \eqref{LP} if $p^* = \val\left\langle c,x^*\right\rangle$, namely, if the infimum in \eqref{LP} is attained at $x^*$.
 

### 2025-05-15 article/paper_padic_spec.tex
stat prop 3.11

@@
 \begin{remark}
-The valuation $\val$ is discrete. Thus if \eqref{LP} admits feasible vectors, $p^*$ is either $- \infty$ or reached by a certain solution $x^*$.
+  Assume $\val$ is a discrete valuation. Then if \eqref{LP} admits feasible vectors,
+  $p^*$ is either $-\infty$ or attained at some solution $x^*$.
 \end{remark}
 
-In this section we present an algorithm for solving \eqref{LP} which starts by eliminating the constraint forced by $D$ and $e$ by operating a substitution. Then it reduces the matrix $A$ to
-Smith Normal Form, thus reducing a general linear program to a diagonal linear program. The latter problem being easily solved by simple calulations in $K$.
-
-The first proposition we prove  allows to consider only iterations of~\eqref{LP} with data of the form $(A,b,c,0,0)$.
+In this section we present an algorithm for solving \eqref{LP} which starts by
+eliminating the equality constraint defined by $D$ and $e$ by operating a substitution.
+Then the algorithm reduces the matrix $A$ to Smith Normal Form, thus reducing a general
+linear program to a diagonal linear program. The reduced problem is then easily solved
+by simple calulations in $K$\footnote{\simone{changer formulation}}.
+
+The first result allows us to consider only iterations of~\eqref{LP} with data of the
+form $(A,b,c,0,0)$. When $Dx=e$ has no solution, \eqref{LP} is infeasible, thus
+we only consider the case when $Dx=e$ has a solution.
 
 \begin{proposition}\label{reducD}
-  Let $A \in \allmat_{d,n}(K), b \in K^d, c\in K^n$, $D \in \allmat_{m,n}$, $e \in K^m$ and let $J \in \allmat_{n,R}\left( K \right) $ be a matrix such that ${\rm Im } J = \ker D$ where $R$ denotes the dimension of $\ker D$.
-  Additionally, we assume the existence of $x_0 \in K^n$ that verifies $D x_0 =e$ as if
-  there are no such vector the problem~\ref{LP} with data $(A,b,c,D,e)$ is not solvable.
-
-  Let $x \in \{x \in K^n : Dx=e\} = x_0 + \ker D $ and let $y \in K^R$ denote the unique element of
-  $K^n$ such that $x = x_0 + J y$, then :
+  Let $A \in K^{d \times n}, b \in K^d, c\in K^n$, $D \in K^{m\times n}$,
+  $e \in K^m$ and let $J \in K^{n \times R}$ be a matrix such that
+  ${\rm Im}\, J = \ker D$ and $R = \dim \ker D$.
+  Assume there exists $x_0 \in K^n$ such that $D x_0 = e$, and let
+  $x \in \{z \in K^n : Dz = e\} = x_0 + \ker D$.
+  Let $y \in K^R$ denote the unique element of $K^n$ such that
+  $x = x_0 + J y$. Then:
   \begin{enumerate}
-    \item\label{reducD_item1} $x$ is feasible for~\eqref{LP} with data $(A,b,c,D,e)$ if and only if 
+  \item\label{reducD_item1}
+    $x$ is feasible for~\eqref{LP} with data $(A,b,c,D,e)$ if and only if 
     $y$ is feasible for~\eqref{LP} with data $(AJ,b+A x_0,J^T c,0,0)$.
-    \item\label{reducD_item2} $x$ is a solution for~\eqref{LP} with data $(A,b,c,D)$ if and only if 
-      $y$ is a solution for~\eqref{LP} with data $(AJ,b+A x_0,J^T c,0,0)$ and $\langle c,x^* \rangle = \langle J^T c,y^* \rangle$.
+  \item\label{reducD_item2}
+    $x$ is a solution for~\eqref{LP} with data $(A,b,c,D,e)$ if and only if 
+    $y$ is a solution for~\eqref{LP} with data $(AJ,b+A x_0,J^T c,0,0)$ and
+    $\langle c,x^* \rangle = \langle J^T c,y^* \rangle$.
   \end{enumerate}

### 2025-05-15 article/paper_padic_spec.tex
SNF --> mathrm

@@
   $$
-  SNF(M) := QMP^{-1} = \diag(\pi^{a_1}, \pi^{a_2}, \ldots, \pi^{a_r}, {\bf 0}_{\min(m,n)-r}).
-  $$
-  The matrix $SNF(M)$ is called the \emph{Smith Normal Form (SNF)} of $M$, and the elements $\pi^{a_i}$ the
+  \mathrm{SNF}(M) := QMP^{-1} = \diag(\pi^{a_1}, \pi^{a_2}, \ldots, \pi^{a_r}, {\bf 0}_{\min(m,n)-r}).
+  $$
+  The matrix $\mathrm{SNF}(M)$ is called the \emph{Smith Normal Form (SNF)} of $M$, and the elements $\pi^{a_i}$ the
   \emph{invariant factors}.
@@
 \begin{remark}
-  The valuation of the first invariant factor of $SNF(M)$ of a matrix
+  The valuation of the first invariant factor of $\mathrm{SNF}(M)$ of a matrix
   $M \in K^{n \times n}$ is the minimum of the valuations of the entries of
-  $M$. In particular, $SNF(M) \in \OK^{n \times n}$.
+  $M$. In particular, $\mathrm{SNF}(M) \in \OK^{n \times n}$.
 \end{remark}
@@
 with $P \in \GL_n(\OK),$ $Q \in \GL_m(\OK)$
-and $\Delta = SNF(f)\in \allmat_{m,n}(K)$ of the form $\diag(\lambda_1, \ldots, \lambda_r, {\bf 0}_{\min(m,n)-r})$
+and $\Delta = \mathrm{SNF}(f)\in \allmat_{m,n}(K)$ of the form $\diag(\lambda_1, \ldots, \lambda_r, {\bf 0}_{\min(m,n)-r})$
   where ${\bf 0}_{\min(m,n)-r}$ is a null square matrix of size $\min(m,n)-r$ for $\lambda_1,\dots,\lambda_r$ non-zero and $r \in \N.$
@@
   $x \in \{z \in K^n : Dz = e\} = x_0 + \ker D$.
-  Let $y \in K^R$ denote the unique element of $K^n$ such that
+  Let $y \in K^R$ denote the unique\footnote{\simone{pas sur que ce soit unique,
+    la mappe $y\mapsto Jy$ est surjective sur $Im J=\ker D$, non pas injective, non ?
+    Il y a un seul élément de $\ker D$, mais il peut y avoir plusieurs fibres.
+    En tous cas, a-t-on a besoin de l'unicité dans la preuve ?}}
+  element of $K^n$ such that
   $x = x_0 + J y$. Then:
@@
 
-The most interesting aspect of the SNF regarding the resolution of~\eqref{LP} is that the transition matrices are
-invertible in $\OK$ and as such they preserve inequalities. %Indeed, for all $z \in K^n$ and $M \in \allmat_n(\OK)$ if $z \geq 0$, then $Mz \geq 0$.
-%The latter property is a direct consequence of $\OK$ being a ring and the converse holds if the matrix $M$ is
-%invertible in $\OK$. 
-Therefore, for all matrix $M \in \allmat_{n,n}(K)$ with $S=SNF(M)$ and for all $z \in K^n$,
+Concerning the usage of SNF in the resolution of \eqref{LP}, note that the transition matrices are invertible in $\OK$ and as such they preserve inequalities.
+%%%%Indeed, for all $z \in K^n$ and $M \in \allmat_n(\OK)$ if $z \geq 0$, then $Mz \geq 0$.
+The latter property is a direct consequence of $\OK$ being a ring and the converse holds if the matrix $M$ is invertible in $\OK$.
+Therefore, for all matrix $M \in K^{n\times n}$ with $S = \mathrm{SNF}(M)$
+and for all $z \in K^n$,
 then $Mz \geq 0$ if and only if $Sz \geq 0$.
@@
 \begin{proposition} \label{solsLP}
-  Let $A \in \allmat_{d,n}(K), b \in K^d, c\in K^n$ and let $S = SNF(A) = QAP^{-1} \in \allmat_{d,n}(K)$, with
+  Let $A \in \allmat_{d,n}(K), b \in K^d, c\in K^n$ and let $S = \mathrm{SNF}(A) = QAP^{-1} \in \allmat_{d,n}(K)$, with
   transition matrices $P \in \GL_d(\OK)$ and $Q\in \GL_d(\OK)$. Define $b' = Qb$ and $c' = (P^{-1})^Tc$.
@@
   Let $(A,b,c), (S,b',c') \in \allmat_{d,n}(K) \times K^d \times K^n$ be as in \Cref{solsLP}, where
-  $S=SNF(A)$. Then
+  $S=\mathrm{SNF}(A)$. Then
   \begin{enumerate}

### 2025-05-15 article/paper_padic_spec.tex
quelques footnote

@@
     $y$ is a solution for~\eqref{LP} with data $(AJ,b+A x_0,J^T c,0,0)$ and
-    $\langle c,x^* \rangle = \langle J^T c,y^* \rangle$.
+    $\langle c,x^* \rangle = \langle J^T c,y^* \rangle$\footnote{\simone{Est-ce que
+    c'est bien $\langle c,x^* \rangle = \langle J^T c,y^* \rangle$ ou plutôt la condition
+    plus faible $\val \langle c,x^* \rangle = \val \langle J^T c,y^* \rangle$ ?
+  Même question pour \Cref{solsLP}.}}.
   \end{enumerate}
@@
 
-Concerning the usage of SNF in the resolution of \eqref{LP}, note that the transition matrices are invertible in $\OK$ and as such they preserve inequalities.
+Concerning the usage of SNF in the resolution of \eqref{LP}, note that the transition matrices $P$ and $Q$ defining SNF$(M)$ in \Cref{smith_nf} are invertible in $\OK$ and as such they preserve inequalities.
 %%%%Indeed, for all $z \in K^n$ and $M \in \allmat_n(\OK)$ if $z \geq 0$, then $Mz \geq 0$.
 The latter property is a direct consequence of $\OK$ being a ring and the converse holds if the matrix $M$ is invertible in $\OK$.
-Therefore, for all matrix $M \in K^{n\times n}$ with $S = \mathrm{SNF}(M)$
-and for all $z \in K^n$,
-then $Mz \geq 0$ if and only if $Sz \geq 0$.
+Therefore, for all matrix $M \in K^{n\times n}$ and vector $z \in K^n$,
+then $Mz \geq 0$ if and only if $Sz \geq 0$, with $S = \mathrm{SNF}(M)$.
 
@@
 \begin{proposition} \label{solsLP}
-  Let $A \in \allmat_{d,n}(K), b \in K^d, c\in K^n$ and let $S = \mathrm{SNF}(A) = QAP^{-1} \in \allmat_{d,n}(K)$, with
-  transition matrices $P \in \GL_d(\OK)$ and $Q\in \GL_d(\OK)$. Define $b' = Qb$ and $c' = (P^{-1})^Tc$.
+  Let $A \in K^{d\times n}$, $b \in K^d$, $c\in K^n$ and let
+  $S = \mathrm{SNF}(A) = QAP^{-1} \in K^{d\times n}$, with
+  $P \in \GL_d(\OK)$ and $Q\in \GL_d(\OK)$.
+  Define $b' = Qb$ and $c' = (P^{-1})^Tc$.
   Then

### 2025-05-15 article/paper_padic_spec.tex
p*=+infty

@@
 \begin{proof}
-  First of all, $Ax+b = AP^{-1}y +b \geq 0$ if and only if $Q(AP^{-1}y + b) = Sy + b' \geq 0$ because
-  $Q \in GL_m(\OK)$, which yields \Cref{solsLP_item1}. Next, for all $c \in K^n$, we have $\langle c,
+  First, since $Q \in \GL_m(\OK)$, one has that $Ax+b = AP^{-1}y +b \geq 0$
+  if and only if $Q(AP^{-1}y + b) = Sy + b' \geq 0$; this yields \Cref{solsLP_item1}.
+  Next, for all $c \in K^n$, we have $\langle c,
   x\rangle = \langle c, P^{-1}Px \rangle = \langle \left(P^{-1}\right)^T c, Px \rangle = \langle c',y\rangle$,
@@
 \begin{proposition}\label{prop:reduc}
-  Let $(A,b,c), (S,b',c') \in \allmat_{d,n}(K) \times K^d \times K^n$ be as in \Cref{solsLP}, where
-  $S=\mathrm{SNF}(A)$. Then
+  Let $(A,b,c), (S,b',c') \in K^{d\times n} \times K^d \times K^n$ be as in \Cref{solsLP},
+  where $S = \mathrm{SNF}(A)$. Then
   \begin{enumerate}
@@
   In particular, for all $n \in \mathbb{N}$ if we set $\alpha = -\frac{\langle c', y^* \rangle + \pi^{-n}}{c'_i}$, we have $\val \left( \langle c', y^* + \alpha e ^i \rangle\right) = \val \pi^{-n} = -n$.
-Therefore, the problem is unbounded as $p^* = + \infty$.
-\end{proof}
-
-From now on, we will only consider iterations of diagonal linear programs which have solutions.
-By \Cref{prop:reduc} we can then reduce the problem by only taking account the first $r$ coefficients of
-$y, b', c'$ and the submatrix of $S$ made with only by the $r$ first rows and columns and whose coefficients
-are exactly the nonzero invariants factors.
+Therefore, the problem is unbounded as $p^* = -\infty$\footnote{\simone{avant c'était ``Therefore, the problem is unbounded as $p^* = +\infty$'' ce qui ne me paraît pas correct.}}.
+\end{proof}
+
+From now on, we only consider iterations of diagonal linear programs admitting a solution.
+By \Cref{prop:reduc} one can simplify the problem by only taking account the first $r$
+coefficients of $y, b', c'$ and the submatrix of $S$ made by the $r$ first rows and
+columns corresponding to the nonzero invariants factors.
 

### 2025-05-15 article/paper_padic_spec.tex
commit by Simone

@@
 By \ref{prop:carac} there exist a polydisc $D = \{x \in K^n : \val s_i x_i - b_i \ge 0, i=1,\ldots,n \}$ for some $s_1,\ldots,s_n, b_1,\ldots,b_n \in K ^n$ and an affine map $f : K^n \to K$ such that $\mathcal{P} = f(D)$.
-    Let $a_0,a_1,\ldots,a_n \in K$ such that $f(x) = a_0 + a_1 x_1 + \ldots + a_n x_n$. We can assume, with no loss of generality, that the $a_i$'s are nonzero.
+Let $a_0,a_1,\ldots,a_n \in K$ such that $f(x) = a_0 + a_1 x_1 + \ldots + a_n x_n$.
+We can assume, with no loss of generality, that the $a_i$'s are nonzero.
 
@@
 and $\left\langle c, x \right\rangle := c_1 x_1+\cdots +c_n x_n$.
-When $A$ is a diagonal matrix and $D = 0$\footnote{\simone{pourquoi la contrainte $D=0$ ?}}, we often refer to \eqref{LP} as a \emph{diagonal} linear program.
+When $A$ is a diagonal matrix\footnote{\simone{J'ai supprimé la contrainte ``and
+$D=0$'', car elle ne me semble pas nécessaire pour définir le ``diagonal LP''.}},
+we often refer to \eqref{LP} as a \emph{diagonal} linear program.
 We denote the \emph{feasible set} of \eqref{LP} by
@@
 Then the algorithm reduces the matrix $A$ to Smith Normal Form, thus reducing a general
-linear program to a diagonal linear program. The reduced problem is then easily solved
-by simple calulations in $K$\footnote{\simone{changer formulation}}.
+linear program to a diagonal linear program. The original problem is then easily solved
+by looking at valuations of input data of the reduced problem.
 
@@
   %%%%\corentin{préciser les notations}. 
-  A vector $y = (y_1, \ldots, y_n)^T \in K^n$ is feasible for \eqref{LP} with data $(S,b',c',0)$
-  if and only if $\val(s_i y_i + b_i) \geq 0$ for all $i = 1,\ldots,n$.
+  A vector $y = (y_1, \ldots, y_n)^T \in K^n$ is feasible for \eqref{LP} with data
+  $(S,b',c',0)$ if and only if $\val(s_i y_i + b_i) \geq 0$ for\footnote{\simone{Ce n'est pas plutôt $\val(s_i y_i + b'_i) \geq 0$ ? Car c'est $b'$ et non pas $b$.}} all $i = 1,\ldots,n$.
   However $s_i = 0$ for $n-r \leq i\leq n$. Therefore, if \eqref{LP} with data $(S,b',c',0)$ is feasible,
@@
 
-From now on, we only consider iterations of diagonal linear programs admitting a solution.
-By \Cref{prop:reduc} one can simplify the problem by only taking account the first $r$
-coefficients of $y, b', c'$ and the submatrix of $S$ made by the $r$ first rows and
-columns corresponding to the nonzero invariants factors.
+The previous results imply that we can consider iterations of diagonal linear programs admitting a solution.
+By \Cref{prop:reduc} one can simplify the problem by only taking account the first $r$ coefficients of $y, b', c'$ and the submatrix of $S$ made by the $r$ first rows and columns corresponding to the nonzero invariants factors.
 
@@
 \PP' = \left\{\left[\begin{smallmatrix} y_1\\ \vdots\\ y_n \end{smallmatrix}\right] \in K^n :
-y_i \in -\frac{b`_i}{s_i} + \frac{1}{s_i} \OK, 1\le i\le r\right\}.
-$$
-
-Solving the diagonal \Cref{LP} consists -by definition- in minimizing the linear map $y \mapsto \val\left(\left\langle
+y_i \in -\frac{b'_i}{s_i} + \frac{1}{s_i} \OK, 1\le i\le r\right\}.
+$$
+
+Solving the diagonal \eqref{LP} consists -- by definition -- in minimizing the linear map $y \mapsto \val\left(\left\langle
 c',y \right\rangle\right)$ over $\PP'$. The image of $\PP'$ by $y \mapsto \left\langle c',y \right\rangle$ is

### 2025-05-15 article/paper_padic_spec.tex
package algo
commit by Simone

@@
-\documentclass[a4paper,12pt]{article}
+\documentclass[a4paper,oneside,11pt]{article}
 
 %%%\newenvironment{proof}{\hbox{}\vspace{-0.8cm} {\bf Proof:}}{\hfill $\Box$ \vspace{0.2cm}}
-
-\usepackage{geometry}
-\geometry{
- a4paper,
- %total={170mm,257mm},
- left=35mm,
- top=40mm,
- bottom=20mm
-}
 
@@
 \usepackage{cleveref}
+
+% --------- ALGORITHMS ---------- <<:
+\usepackage[noend]{algpseudocode}      %%% this is for the algorithms
+\renewcommand{\algorithmicrequire}{\textbf{Input:}} % require --> input
+\renewcommand{\algorithmicensure}{\textbf{Output:}} % ensure --> output
+\algrenewcomment[1]{\hfill \(\triangleright\) \emph{\small #1}} % to italicize text in comments
+\algnewcommand{\CommentLine}[1]{\(\triangleright\) \emph{\small #1}} % whole line comment
+\algnewcommand{\InlineIf}[2]{ % single line if-then
+  \State \algorithmicif\ #1\ \algorithmicthen\ #2}
+\algnewcommand{\InlineIfElse}[3]{ % single line if-then-else
+  \State \algorithmicif\ #1\ \algorithmicthen\ #2\ \algorithmicelse\ #3}
+\algnewcommand{\InlineFor}[2]{\algorithmicfor\ #1\ \algorithmicdo\ #2} % single line for loop
+%% Change call to put a clickable link, and ensure no parentheses if
+%% no argument is given
+%% Original command from package for reference:
+%% \algnewcommand\Call[2]{\textproc{#1}\ifthenelse{\equal{#2}{}}{}{(#2)}}
+\algrenewcommand\Call[2]{\nameref{#1}\ifthenelse{\equal{#2}{}}{}{\ensuremath{(#2)}}}%
+\newcommand{\algoName}[1]{Algorithm \nameref{#1}}
+%% make sure the arguments of the algorithm are not stored in nameref
+\makeatletter
+\newcommand{\algoCaptionLabel}[2]{%
+     \NR@gettitle{\textproc{#1}}% % NR@gettitle to have nameref work fine with algos
+     \caption[\textproc{#1}]{\textproc{#1}\ifthenelse{\equal{#2}{}}{}{$(#2)$}}%
+     \label{algo:#1}
+     }%
+\makeatother
+%% to fix references to algo lines (problem is because of load order in siamonline cls)
+\makeatletter
+  \g@addto@macro\ALG@step{%
+    \addtocounter{ALG@line}{-1}%
+    \refstepcounter{ALG@line}%
+    \expandafter\@cref@getprefix\cref@currentlabel\@nil\cref@currentprefix%
+    \xdef\cref@currentprefix{\cref@currentprefix}}%
+  \g@addto@macro\ALG@beginalgorithmic{%
+    \def\cref@currentlabel{%
+      [line][\arabic{ALG@line}][\cref@currentprefix]\theALG@line}}%
+\makeatother
+%% to be able to use statex with some indentation, typically in an if statement
+%% from https://tex.stackexchange.com/questions/33979/include-a-line-break-in-algorithmic-while-maintaining-indentation/33995#33995
+\makeatletter
+\newcommand{\StateX}[1]{%
+  \setlength\@tempdima{\algorithmicindent}%
+  \Statex\hskip\dimexpr#1\@tempdima\relax}
+\makeatother
+% :>> ALGORITHMS
 
@@
 
-\textheight235mm
-\textwidth165mm
-\voffset-10mm
-\hoffset-12.5mm
+\usepackage{geometry}
+\geometry{
+ a4paper,
+ %total={170mm,257mm},
+ left=30mm,
+ right=30mm,
+ top=30mm,
+ bottom=30mm
+}
+
+%\textheight235mm
+%\textwidth165mm
+%\voffset-10mm
+%\hoffset-12.5mm
 \parindent0.8cm
@@
 (which is equivalent to minimize the absolute value) the same reasoning can be applied. 
-The only difference being that if $\val\left( \lambda\right) < v$ the problem is unbounded and 
-as such does not admit a solution. 
+The only difference being that if $\val\left( \lambda\right) < v$ the problem is unbounded
+and as such does not admit a solution. 
 \end{remark}

### 2025-05-15 article/paper_padic_spec.tex
commit by Simone

--- 2025-05-15 article/paper_padic_spec.tex
@@
 
+% --------- ALGORITHMS ---------- <<:
+\usepackage{algorithm,algorithmic}
+%\usepackage[noend]{algpseudocode}      %%% this is for the algorithms
+\renewcommand{\algorithmicrequire}{\textbf{Input:}} % require --> input
+\renewcommand{\algorithmicensure}{\textbf{Output:}} % ensure --> output
+% :>> ALGORITHMS
+
 \newtheorem{theorem}{Theorem}[section]
@@
 \newtheorem{corollary}[theorem]{Corollary}
-\newtheorem{algorithm}[theorem]{Algorithm}
+%\newtheorem{algorithm}[theorem]{Algorithm}
 \newtheorem{conjecture}[theorem]{Conjecture}
@@
 (which is equivalent to minimize the absolute value) the same reasoning can be applied. 
-The only difference being that if $\val\left( \lambda\right) < v$ the problem is unbounded and 
-as such does not admit a solution. 
+The only difference being that if $\val\left( \lambda\right) < v$ the problem is unbounded
+and as such does not admit a solution. 
 \end{remark}
+
+We formalize the algorithm described previously in \Cref{algo_LP}:
+
+\begin{algorithm}
+    \caption{SOLVELP($A,b,c,D,e$)}\label{algo_LP}
+    \begin{algorithmic}
+      \REQUIRE
+      $A \in K^{d\times n}$, $b \in K^d$, $D \in K^{m \times n}$ and $e \in K^m$
+      \ENSURE A feasibility type (INFEAS, FEAS) and a solution (if FEAS)
+      \vspace{0.1cm}
+      \hline
+      \vspace{0.1cm}
+      \STATE $\mathrm{SOLVELP} (f_i,w_i,o_j)$
+      \FOR{epochs = $1$ to $N$}
+      \WHILE{$(j\le m)$}
+      \STATE Randomly initialize $w_i=\{w_1,w_2,\dots,w_n\}$
+      \STATE input $o_j=\{o_1,o_2,\dots,o_m\}$ in the input layer
+      \STATE forward propagate $(f_i\cdot w_i)$ through layers until getting the predicted result $y$
+      \STATE compute $e=y-y^2$
+      \STATE back propagate $e$ from right to left through layers
+      \STATE update $w_i$
+      \ENDWHILE
+      \ENDFOR
+    \end{algorithmic}
+\end{algorithm}
 

### 2025-05-15 article/paper_padic_spec.tex
algo

@@
 and $\left\langle c, x \right\rangle := c_1 x_1+\cdots +c_n x_n$.
-When $A$ is a diagonal matrix\footnote{\simone{J'ai supprimé la contrainte ``and
-$D=0$'', car elle ne me semble pas nécessaire pour définir le ``diagonal LP''.}},
+When $A$ is a diagonal matrix\footnote{\simone{J'ai supprimé ``and
+$D=0$'', car cela ne me semble pas nécessaire pour définir le ``diagonal LP''.}},
 we often refer to \eqref{LP} as a \emph{diagonal} linear program.
@@
       \REQUIRE
-      $A \in K^{d\times n}$, $b \in K^d$, $D \in K^{m \times n}$ and $e \in K^m$
-      \ENSURE A feasibility type (INFEAS, FEAS) and a solution (if FEAS)
+      $A \in K^{d\times n}$, $b \in K^d$, $c \in K^n$, $D \in K^{m \times n}$ and $e \in K^m$
+      \ENSURE [TYPE, $x$], where:
+      \vspace{-0.25cm}
+      \begin{itemize}
+      \item[]
+        TYPE $=$ INFEAS and $x=[]$ if and only if \eqref{LP} is infeasible
+      \vspace{-0.25cm}
+      \item[]
+        TYPE $=$ UNBOUND and $x=[]$ if and only if \eqref{LP} is feasible and unbounded
+      \vspace{-0.25cm}
+      \item[]
+        TYPE $=$ FEAS if and only if \eqref{LP} is feasible and has a solution $x$
+      \end{itemize}
+      \vspace{-0.1cm}
+      \hrule
       \vspace{0.1cm}
-      \hline
-      \vspace{0.1cm}
-      \STATE $\mathrm{SOLVELP} (f_i,w_i,o_j)$
-      \FOR{epochs = $1$ to $N$}
-      \WHILE{$(j\le m)$}
-      \STATE Randomly initialize $w_i=\{w_1,w_2,\dots,w_n\}$
-      \STATE input $o_j=\{o_1,o_2,\dots,o_m\}$ in the input layer
-      \STATE forward propagate $(f_i\cdot w_i)$ through layers until getting the predicted result $y$
-      \STATE compute $e=y-y^2$
-      \STATE back propagate $e$ from right to left through layers
-      \STATE update $w_i$
-      \ENDWHILE
-      \ENDFOR
+      \IF{$Dx = e$ has no solution}
+      \RETURN [INFEAS, []]
+      \ENDIF
+      \IF{$D \neq {\bf 0}$}
+      \STATE $[\mathrm{STATUS}, y] \leftarrow $
+      \RETURN 
+      \ENDIF
+      %\FOR{epochs = $1$ to $N$}
+      %\WHILE{$(j\le m)$}
+      %\STATE Randomly initialize $w_i=\{w_1,w_2,\dots,w_n\}$
+      %\STATE input $o_j=\{o_1,o_2,\dots,o_m\}$ in the input layer
+      %\STATE forward propagate $(f_i\cdot w_i)$ through layers until getting the predicted result $y$
+      %\STATE compute $e=y-y^2$
+      %\STATE back propagate $e$ from right to left through layers
+      %\STATE update $w_i$
+      %\ENDWHILE
+      %\ENDFOR
     \end{algorithmic}

### 2025-05-16 article/paper_padic_spec.tex
commit by Simone

@@
 
-In this section we present an algorithm for solving \eqref{LP} which starts by
-eliminating the equality constraint defined by $D$ and $e$ by operating a substitution.
-Then the algorithm reduces the matrix $A$ to Smith Normal Form, thus reducing a general
-linear program to a diagonal linear program. The original problem is then easily solved
-by looking at valuations of input data of the reduced problem.
-
-The first result allows us to consider only iterations of~\eqref{LP} with data of the
-form $(A,b,c,0,0)$. When $Dx=e$ has no solution, \eqref{LP} is infeasible, thus
-we only consider the case when $Dx=e$ has a solution.
-
-\begin{proposition}\label{reducD}
-  Let $A \in K^{d \times n}, b \in K^d, c\in K^n$, $D \in K^{m\times n}$,
-  $e \in K^m$ and let $J \in K^{n \times R}$ be a matrix such that
-  ${\rm Im}\, J = \ker D$ and $R = \dim \ker D$.
-  Assume there exists $x_0 \in K^n$ such that $D x_0 = e$, and let
-  $x \in \{z \in K^n : Dz = e\} = x_0 + \ker D$.
-  Let $y \in K^R$ denote the unique\footnote{\simone{pas sur que ce soit unique,
-    la mappe $y\mapsto Jy$ est surjective sur $Im J=\ker D$, non pas injective, non ?
-    Il y a un seul élément de $\ker D$, mais il peut y avoir plusieurs fibres.
-    En tous cas, a-t-on a besoin de l'unicité dans la preuve ?}}
-  element of $K^n$ such that
-  $x = x_0 + J y$. Then:
-  \begin{enumerate}
-  \item\label{reducD_item1}
-    $x$ is feasible for~\eqref{LP} with data $(A,b,c,D,e)$ if and only if 
-    $y$ is feasible for~\eqref{LP} with data $(AJ,b+A x_0,J^T c,0,0)$.
-  \item\label{reducD_item2}
-    $x$ is a solution for~\eqref{LP} with data $(A,b,c,D,e)$ if and only if 
-    $y$ is a solution for~\eqref{LP} with data $(AJ,b+A x_0,J^T c,0,0)$ and
-    $\langle c,x^* \rangle = \langle J^T c,y^* \rangle$\footnote{\simone{Est-ce que
-    c'est bien $\langle c,x^* \rangle = \langle J^T c,y^* \rangle$ ou plutôt la condition
-    plus faible $\val \langle c,x^* \rangle = \val \langle J^T c,y^* \rangle$ ?
-  Même question pour \Cref{solsLP}.}}.
-  \end{enumerate}
-\end{proposition}
-
-\begin{proof}
-  %The existence and uniqueness of $y$ are granted by the fact that $x \in x_0 + \ker D =x_0+ {\rm Im } J$  and $\ker J = \{0\}$. 
-  First,  $Dx=e$ and $Ax + b \le 0$ if and only if $AJy + b+Ax_0 \le 0$, proving \Cref{reducD_item1}.
-  Next, for all $c \in K^n$, $\langle c,x\rangle = \langle c, Jy\rangle = \langle J^T c,y\rangle$, which proves \Cref{reducD_item2}.
-\end{proof}
-
-Concerning the usage of SNF in the resolution of \eqref{LP}, note that the transition matrices $P$ and $Q$ defining SNF$(M)$ in \Cref{smith_nf} are invertible in $\OK$ and as such they preserve inequalities.
-%%%%Indeed, for all $z \in K^n$ and $M \in \allmat_n(\OK)$ if $z \geq 0$, then $Mz \geq 0$.
-The latter property is a direct consequence of $\OK$ being a ring and the converse holds if the matrix $M$ is invertible in $\OK$.
-Therefore, for all matrix $M \in K^{n\times n}$ and vector $z \in K^n$,
-then $Mz \geq 0$ if and only if $Sz \geq 0$, with $S = \mathrm{SNF}(M)$.
-
-\Cref{solsLP} allows us to reduce \eqref{LP} to diagonal linear programs.
-
-\begin{proposition} \label{solsLP}
-  Let $A \in K^{d\times n}$, $b \in K^d$, $c\in K^n$ and let
-  $S = \mathrm{SNF}(A) = QAP^{-1} \in K^{d\times n}$, with
-  $P \in \GL_d(\OK)$ and $Q\in \GL_d(\OK)$.
-  Define $b' = Qb$ and $c' = (P^{-1})^Tc$.
-  Then
-   \begin{enumerate}
-   \item \label{solsLP_item1}
-     $x \in K^n$ is feasible for \eqref{LP} with data $(A,b,c,0,0)$ if and only if $y = P x \in K^n$ is
-     feasible for \eqref{LP} with data $(S,b',c',0,0)$.
-   \item \label{solsLP_item2}
-     $x^* \in K^n$ is a solution to \eqref{LP} with data $(A,b,c,0,0)$ if and only if $y^* = P x^*$ is
-     a solution to \eqref{LP} with data $(S,b',c',0,0)$ and $\langle c,x^* \rangle = \langle c',y^* \rangle$.
-   \end{enumerate}
-\end{proposition}
-\begin{proof}
-  First, since $Q \in \GL_m(\OK)$, one has that $Ax+b = AP^{-1}y +b \geq 0$
-  if and only if $Q(AP^{-1}y + b) = Sy + b' \geq 0$; this yields \Cref{solsLP_item1}.
-  Next, for all $c \in K^n$, we have $\langle c,
-  x\rangle = \langle c, P^{-1}Px \rangle = \langle \left(P^{-1}\right)^T c, Px \rangle = \langle c',y\rangle$,
-  which proves \Cref{solsLP_item2}.
-\end{proof}
-
-\begin{proposition}\label{prop:reduc}
-  Let $(A,b,c), (S,b',c') \in K^{d\times n} \times K^d \times K^n$ be as in \Cref{solsLP},
-  where $S = \mathrm{SNF}(A)$. Then
-  \begin{enumerate}
-  \item \label{prop:reduc_it1}
-    \eqref{LP} with data $(S,b',c',0,0)$ is feasible if and only if the $d-r$ last coefficients
-    of $b'$ have nonnegative valuation, for $r = {\rm rank}\,S$.
-  \item \label{prop:reduc_it2}
-    Assume at least one of the $n-r$ last coefficients of $c'$ is non-zero. If \eqref{LP} with
-    data $(S,b',c')$ is feasible, then it is unbounded and does not admit solutions.
-  \end{enumerate}
-\end{proposition}
-\begin{proof}
-  %%%%\corentin{préciser les notations}. 
-  A vector $y = (y_1, \ldots, y_n)^T \in K^n$ is feasible for \eqref{LP} with data
-  $(S,b',c',0)$ if and only if $\val(s_i y_i + b_i) \geq 0$ for\footnote{\simone{Ce n'est pas plutôt $\val(s_i y_i + b'_i) \geq 0$ ? Car c'est $b'$ et non pas $b$.}} all $i = 1,\ldots,n$.
-  However $s_i = 0$ for $n-r \leq i\leq n$. Therefore, if \eqref{LP} with data $(S,b',c',0)$ is feasible,
-  necessarily the $d-r$ last coefficients of $b'$ have nonnegative valuation.
-  Conversely, if the $d-r$ last coefficients of $b'$ are zero, the vector $y \in K^n$ such that
-  $y_i = -\frac{-b'_i}{s_i}$ if $1 \leq i \leq r$, and $y_i =0$ otherwise, is feasible for \eqref{LP}
-  with data $(S,b',c',0,0)$.
-
-  Concerning \Cref{prop:reduc_it2}, let $y^*$ be feasible for \eqref{LP} with data $(S,b',c',0,0)$.
-  Let $i$ be such that $r+1 \leq i \leq n$ and $c'_i \neq 0$. Consider the vector $e^i$ whose only non-zero
-  coefficient is the $i-$th, which is $1$. Then $y^* + \alpha e^i$ is feasible for \eqref{LP} with data $(S,b',c',0,0)$,
-  for all $\alpha \in K$ and $\langle c', y^* + \alpha e^i\rangle = \langle c' , y^* \rangle + \alpha c'_i$.
-  In particular, for all $n \in \mathbb{N}$ if we set $\alpha = -\frac{\langle c', y^* \rangle + \pi^{-n}}{c'_i}$, we have $\val \left( \langle c', y^* + \alpha e ^i \rangle\right) = \val \pi^{-n} = -n$.
-Therefore, the problem is unbounded as $p^* = -\infty$\footnote{\simone{avant c'était ``Therefore, the problem is unbounded as $p^* = +\infty$'' ce qui ne me paraît pas correct.}}.
-\end{proof}
-
-The previous results imply that we can consider iterations of diagonal linear programs admitting a solution.
-By \Cref{prop:reduc} one can simplify the problem by only taking account the first $r$ coefficients of $y, b', c'$ and the submatrix of $S$ made by the $r$ first rows and columns corresponding to the nonzero invariants factors.
-
-The feasible set $\PP' = \{y \in K^n : Sy+b' \geq 0\}$ of the diagonal LP can be written as the set of vectors
-$y \in K^n$ that verifies $s_i y_i + b'_i \in \OK$ for $i=1,...,r$ {\it i.e.}:
-$$
-\PP' = \left\{\left[\begin{smallmatrix} y_1\\ \vdots\\ y_n \end{smallmatrix}\right] \in K^n :
-y_i \in -\frac{b'_i}{s_i} + \frac{1}{s_i} \OK, 1\le i\le r\right\}.
-$$
-
-Solving the diagonal \eqref{LP} consists -- by definition -- in minimizing the linear map $y \mapsto \val\left(\left\langle
-c',y \right\rangle\right)$ over $\PP'$. The image of $\PP'$ by $y \mapsto \left\langle c',y \right\rangle$ is
-\[
-\left\langle c',\PP' \right\rangle = \sum_{i=1}^r -c'_i \frac{b'_i}{s_i} + \sum_{i=1}^r\left( \frac{c'_i}{s_{i}} \OK \right) = \lambda + \pi^{v} \OK
-\]
-where $\lambda = \sum_{i=1}^r -c'_i \frac{b'_i}{s_i}$ and $v = \min\limits_{1\le i\le r} \val \frac{c'_{i}}{s_{i}} $.
-
-Two cases can occur depending on $v$ and the valuation of $\lambda$.
-If $\val(\lambda) < v$, the minimum of $y\mapsto \val\left(\left\langle c',y \right\rangle\right)$ over $\PP'$
-  is reached at any point of $\PP'$, and is equal to $\val(\lambda)$.
-  Otherwise, if $\val(\lambda) \ge v$, then $\lambda \in \pi^{v} \OK$ and the minimum is $v$ and is reached at any points $y$
-  of $\PP'$ such that $\left<c',y \right> \in \pi^v$.
-
-\begin{remark}
-	If $\val \lambda \ge v$ and $i_0 \in \{1,\ldots, n\} $ is such that $v = \val \frac{c_{i_0}'}{s_{i_0}²} $ 
-  then the vector $e^{i_0} \in K$ is a solution of \ref{LP}, 
-  where $e^{i_0}$ denotes the vector of $K^n$ whose only non-zero coefficient is the $i_0$-th which is $1$.
-\end{remark}
-
-\begin{remark}
-To maximize the valuation of a linear map over a polyhedron instead of minimizing it 
-(which is equivalent to minimize the absolute value) the same reasoning can be applied. 
-The only difference being that if $\val\left( \lambda\right) < v$ the problem is unbounded
-and as such does not admit a solution. 
-\end{remark}
-
-We formalize the algorithm described previously in \Cref{algo_LP}:
+In this section we present an algorithm for solving Problem \eqref{LP}.
+The algorithm starts by eliminating the equality constraint defined by $D$ and $e$
+by variable substitution. Then the matrix $A$ is replaced by its Smith Normal Form,
+and the general linear program is consequently reduced to a diagonal linear program.
+The original \eqref{LP} is then easily solved by looking at valuations of input data
+in the reduced problem.
+
+We first give a formal description of our algorithm and then prove its correctness:
 
@@
 
+The first result allows us to consider only iterations of~\eqref{LP} with data of the
+form $(A,b,c,0,0)$. When $Dx=e$ has no solution, \eqref{LP} is infeasible, thus
+we only consider the case when $Dx=e$ has a solution.
+
+\begin{proposition}\label{reducD}
+  Let $A \in K^{d \times n}, b \in K^d, c\in K^n$, $D \in K^{m\times n}$,
+  $e \in K^m$ and let $J \in K^{n \times R}$ be a matrix such that
+  ${\rm Im}\, J = \ker D$ and $R = \dim \ker D$.
+  Assume there exists $x_0 \in K^n$ such that $D x_0 = e$, and let
+  $x \in \{z \in K^n : Dz = e\} = x_0 + \ker D$.
+  Let $y \in K^R$ denote the unique\footnote{\simone{pas sur que ce soit unique,
+    la mappe $y\mapsto Jy$ est surjective sur $Im J=\ker D$, non pas injective, non ?
+    Il y a un seul élément de $\ker D$, mais il peut y avoir plusieurs fibres.
+    En tous cas, a-t-on a besoin de l'unicité dans la preuve ?}}
+  element of $K^n$ such that
+  $x = x_0 + J y$. Then:
+  \begin{enumerate}
+  \item\label{reducD_item1}
+    $x$ is feasible for~\eqref{LP} with data $(A,b,c,D,e)$ if and only if 
+    $y$ is feasible for~\eqref{LP} with data $(AJ,b+A x_0,J^T c,0,0)$.
+  \item\label{reducD_item2}
+    $x$ is a solution for~\eqref{LP} with data $(A,b,c,D,e)$ if and only if 
+    $y$ is a solution for~\eqref{LP} with data $(AJ,b+A x_0,J^T c,0,0)$ and
+    $\langle c,x^* \rangle = \langle J^T c,y^* \rangle$\footnote{\simone{Est-ce que
+    c'est bien $\langle c,x^* \rangle = \langle J^T c,y^* \rangle$ ou plutôt la condition
+    plus faible $\val \langle c,x^* \rangle = \val \langle J^T c,y^* \rangle$ ?
+  Même question pour \Cref{solsLP}.}}.
+  \end{enumerate}
+\end{proposition}
+
+\begin{proof}
+  %The existence and uniqueness of $y$ are granted by the fact that $x \in x_0 + \ker D =x_0+ {\rm Im } J$  and $\ker J = \{0\}$. 
+  First,  $Dx=e$ and $Ax + b \le 0$ if and only if $AJy + b+Ax_0 \le 0$, proving \Cref{reducD_item1}.
+  Next, for all $c \in K^n$, $\langle c,x\rangle = \langle c, Jy\rangle = \langle J^T c,y\rangle$, which proves \Cref{reducD_item2}.
+\end{proof}
+
+Concerning the usage of SNF in the resolution of \eqref{LP}, note that the transition matrices $P$ and $Q$ defining SNF$(M)$ in \Cref{smith_nf} are invertible in $\OK$ and as such they preserve inequalities.
+%%%%Indeed, for all $z \in K^n$ and $M \in \allmat_n(\OK)$ if $z \geq 0$, then $Mz \geq 0$.
+The latter property is a direct consequence of $\OK$ being a ring and the converse holds if the matrix $M$ is invertible in $\OK$.
+Therefore, for all matrix $M \in K^{n\times n}$ and vector $z \in K^n$,
+then $Mz \geq 0$ if and only if $Sz \geq 0$, with $S = \mathrm{SNF}(M)$.
+
+\Cref{solsLP} allows us to reduce \eqref{LP} to diagonal linear programs.
+
+\begin{proposition} \label{solsLP}
+  Let $A \in K^{d\times n}$, $b \in K^d$, $c\in K^n$ and let
+  $S = \mathrm{SNF}(A) = QAP^{-1} \in K^{d\times n}$, with
+  $P \in \GL_d(\OK)$ and $Q\in \GL_d(\OK)$.
+  Define $b' = Qb$ and $c' = (P^{-1})^Tc$.
+  Then
+   \begin{enumerate}
+   \item \label{solsLP_item1}
+     $x \in K^n$ is feasible for \eqref{LP} with data $(A,b,c,0,0)$ if and only if $y = P x \in K^n$ is
+     feasible for \eqref{LP} with data $(S,b',c',0,0)$.
+   \item \label{solsLP_item2}
+     $x^* \in K^n$ is a solution to \eqref{LP} with data $(A,b,c,0,0)$ if and only if $y^* = P x^*$ is
+     a solution to \eqref{LP} with data $(S,b',c',0,0)$ and $\langle c,x^* \rangle = \langle c',y^* \rangle$.
+   \end{enumerate}
+\end{proposition}
+\begin{proof}
+  First, since $Q \in \GL_m(\OK)$, one has that $Ax+b = AP^{-1}y +b \geq 0$
+  if and only if $Q(AP^{-1}y + b) = Sy + b' \geq 0$; this yields \Cref{solsLP_item1}.
+  Next, for all $c \in K^n$, we have $\langle c,
+  x\rangle = \langle c, P^{-1}Px \rangle = \langle \left(P^{-1}\right)^T c, Px \rangle = \langle c',y\rangle$,
+  which proves \Cref{solsLP_item2}.
+\end{proof}
+
+\begin{proposition}\label{prop:reduc}
+  Let $(A,b,c), (S,b',c') \in K^{d\times n} \times K^d \times K^n$ be as in \Cref{solsLP},
+  where $S = \mathrm{SNF}(A)$. Then
+  \begin{enumerate}
+  \item \label{prop:reduc_it1}
+    \eqref{LP} with data $(S,b',c',0,0)$ is feasible if and only if the $d-r$ last coefficients
+    of $b'$ have nonnegative valuation, for $r = {\rm rank}\,S$.
+  \item \label{prop:reduc_it2}
+    Assume at least one of the $n-r$ last coefficients of $c'$ is non-zero. If \eqref{LP} with
+    data $(S,b',c')$ is feasible, then it is unbounded and does not admit solutions.
+  \end{enumerate}
+\end{proposition}
+\begin{proof}
+  %%%%\corentin{préciser les notations}. 
+  A vector $y = (y_1, \ldots, y_n)^T \in K^n$ is feasible for \eqref{LP} with data
+  $(S,b',c',0)$ if and only if $\val(s_i y_i + b_i) \geq 0$ for\footnote{\simone{Ce n'est pas plutôt $\val(s_i y_i + b'_i) \geq 0$ ? Car c'est $b'$ et non pas $b$.}} all $i = 1,\ldots,n$.
+  However $s_i = 0$ for $n-r \leq i\leq n$. Therefore, if \eqref{LP} with data $(S,b',c',0)$ is feasible,
+  necessarily the $d-r$ last coefficients of $b'$ have nonnegative valuation.
+  Conversely, if the $d-r$ last coefficients of $b'$ are zero, the vector $y \in K^n$ such that
+  $y_i = -\frac{-b'_i}{s_i}$ if $1 \leq i \leq r$, and $y_i =0$ otherwise, is feasible for \eqref{LP}
+  with data $(S,b',c',0,0)$.
+
+  Concerning \Cref{prop:reduc_it2}, let $y^*$ be feasible for \eqref{LP} with data $(S,b',c',0,0)$.
+  Let $i$ be such that $r+1 \leq i \leq n$ and $c'_i \neq 0$. Consider the vector $e^i$ whose only non-zero
+  coefficient is the $i-$th, which is $1$. Then $y^* + \alpha e^i$ is feasible for \eqref{LP} with data $(S,b',c',0,0)$,
+  for all $\alpha \in K$ and $\langle c', y^* + \alpha e^i\rangle = \langle c' , y^* \rangle + \alpha c'_i$.
+  In particular, for all $n \in \mathbb{N}$ if we set $\alpha = -\frac{\langle c', y^* \rangle + \pi^{-n}}{c'_i}$, we have $\val \left( \langle c', y^* + \alpha e ^i \rangle\right) = \val \pi^{-n} = -n$.
+Therefore, the problem is unbounded as $p^* = -\infty$\footnote{\simone{avant c'était ``Therefore, the problem is unbounded as $p^* = +\infty$'' ce qui ne me paraît pas correct.}}.
+\end{proof}
+
+The previous results imply that we can consider iterations of diagonal linear programs admitting a solution.
+By \Cref{prop:reduc} one can simplify the problem by only taking account the first $r$ coefficients of $y, b', c'$ and the submatrix of $S$ made by the $r$ first rows and columns corresponding to the nonzero invariants factors.
+
+The feasible set $\PP' = \{y \in K^n : Sy+b' \geq 0\}$ of the diagonal LP can be written as the set of vectors
+$y \in K^n$ that verifies $s_i y_i + b'_i \in \OK$ for $i=1,...,r$ {\it i.e.}:
+$$
+\PP' = \left\{\left[\begin{smallmatrix} y_1\\ \vdots\\ y_n \end{smallmatrix}\right] \in K^n :
+y_i \in -\frac{b'_i}{s_i} + \frac{1}{s_i} \OK, 1\le i\le r\right\}.
+$$
+
+Solving the diagonal \eqref{LP} consists -- by definition -- in minimizing the linear map $y \mapsto \val\left(\left\langle
+c',y \right\rangle\right)$ over $\PP'$. The image of $\PP'$ by $y \mapsto \left\langle c',y \right\rangle$ is
+\[
+\left\langle c',\PP' \right\rangle = \sum_{i=1}^r -c'_i \frac{b'_i}{s_i} + \sum_{i=1}^r\left( \frac{c'_i}{s_{i}} \OK \right) = \lambda + \pi^{v} \OK
+\]
+where $\lambda = \sum_{i=1}^r -c'_i \frac{b'_i}{s_i}$ and $v = \min\limits_{1\le i\le r} \val \frac{c'_{i}}{s_{i}} $.
+
+Two cases can occur depending on $v$ and the valuation of $\lambda$.
+If $\val(\lambda) < v$, the minimum of $y\mapsto \val\left(\left\langle c',y \right\rangle\right)$ over $\PP'$
+  is reached at any point of $\PP'$, and is equal to $\val(\lambda)$.
+  Otherwise, if $\val(\lambda) \ge v$, then $\lambda \in \pi^{v} \OK$ and the minimum is $v$ and is reached at any points $y$
+  of $\PP'$ such that $\left<c',y \right> \in \pi^v$.
+
+\begin{remark}
+	If $\val \lambda \ge v$ and $i_0 \in \{1,\ldots, n\} $ is such that $v = \val \frac{c_{i_0}'}{s_{i_0}²} $ 
+  then the vector $e^{i_0} \in K$ is a solution of \ref{LP}, 
+  where $e^{i_0}$ denotes the vector of $K^n$ whose only non-zero coefficient is the $i_0$-th which is $1$.
+\end{remark}
+
+\begin{remark}
+To maximize the valuation of a linear map over a polyhedron instead of minimizing it 
+(which is equivalent to minimize the absolute value) the same reasoning can be applied. 
+The only difference being that if $\val\left( \lambda\right) < v$ the problem is unbounded
+and as such does not admit a solution. 
+\end{remark}
+
 \section{Spectrahedra}

### 2025-05-16 article/paper_padic_spec.tex
commit by Simone

@@
 
-We first give a formal description of our algorithm and then prove its correctness:
+We first give a formal description of our algorithm:
 
@@
     \caption{SOLVELP($A,b,c,D,e$)}\label{algo_LP}
-    \begin{algorithmic}
+    \begin{algorithmic}[1]
       \REQUIRE
@@
 
-The first result allows us to consider only iterations of~\eqref{LP} with data of the
-form $(A,b,c,0,0)$. When $Dx=e$ has no solution, \eqref{LP} is infeasible, thus
-we only consider the case when $Dx=e$ has a solution.
+In order to prove correctness of \Cref{algo_LP}, we proceed step-by-step.
+When the system $Dx=e$ has no solution, \eqref{LP} is infeasible and
+thus from now on we only consider the case when $Dx=e$ has a solution.
+
+We first prove a reduction result, allowing to consider only iterations
+of~\eqref{LP} with data of the form $(A,b,c,0,0)$.
 
@@
   of $\PP'$ such that $\left<c',y \right> \in \pi^v$.
+
+  We conclude with a correctness theorem.
+
+  \begin{theorem} \Cref{algo_LP} is correct.
+  \end{theorem}
+  \begin{proof}
+  \end{proof}
 

### 2025-05-16 article/paper_padic_spec.tex
commit by Simone

@@
 \begin{remark}
-  Assume $\val$ is a discrete valuation. Then if \eqref{LP} admits feasible vectors,
+  Assume $\val$ is a discrete valuation. Then\footnote{\simone{Cela voudrait dire que
+    si la valuation n'est pas discrète, on pourrait avoir un problème LP qui est admissible
+    (c'est-à-dire l'ensemble admissible est non-vide) et où $p^* \in \ZZ$, mais $p^*$ n'est
+  pas atteint.}} if \eqref{LP} admits feasible vectors,
   $p^*$ is either $-\infty$ or attained at some solution $x^*$.

### 2025-05-16 article/paper_padic_spec.tex
commit by Simone

--- 2025-05-16 article/paper_padic_spec.tex
@@
 \begin{remark}
-  Assume $\val$ is a discrete valuation. Then if \eqref{LP} admits feasible vectors,
+  Assume $\val$ is a discrete valuation. Then\footnote{\simone{Cela voudrait dire que
+    si la valuation n'est pas discrète, on pourrait avoir un problème LP qui est admissible
+    (c'est-à-dire l'ensemble admissible est non-vide) et où $p^* \in \ZZ$, mais $p^*$ n'est
+  pas atteint. C'est ça ? A-t-on des exemples ?}} if \eqref{LP} admits feasible vectors,
   $p^*$ is either $-\infty$ or attained at some solution $x^*$.

### 2025-05-16 article/paper_padic_spec.tex
ok j'ai eliminé une footnote

@@
   $x \in \{z \in K^n : Dz = e\} = x_0 + \ker D$.
-  Let $y \in K^R$ denote the unique\footnote{\simone{pas sur que ce soit unique,
-    la mappe $y\mapsto Jy$ est surjective sur $Im J=\ker D$, non pas injective, non ?
-    Il y a un seul élément de $\ker D$, mais il peut y avoir plusieurs fibres.
-    En tous cas, a-t-on a besoin de l'unicité dans la preuve ?}}
-  element of $K^n$ such that
+  Let $y \in K^R$ denote the unique element of $K^n$ such that
   $x = x_0 + J y$. Then:

### 2025-05-16 article/paper_padic_spec.tex
commit by Simone

@@
     si la valuation n'est pas discrète, on pourrait avoir un problème LP qui est admissible
-    (c'est-à-dire l'ensemble admissible est non-vide) et où $p^* \in \ZZ$, mais $p^*$ n'est
+    (c'est-à-dire l'ensemble admissible est non-vide) et où $p^* \in \R$, mais $p^*$ n'est
   pas atteint. C'est ça ? A-t-on des exemples ?}} if \eqref{LP} admits feasible vectors,

### 2025-05-16 article/paper_padic_spec.tex
commit by Simone

@@
   %The existence and uniqueness of $y$ are granted by the fact that $x \in x_0 + \ker D =x_0+ {\rm Im } J$  and $\ker J = \{0\}$. 
-  First,  $Dx=e$ and $Ax + b \le 0$ if and only if $AJy + b+Ax_0 \le 0$, proving \Cref{reducD_item1}.
-  Next, for all $c \in K^n$, $\langle c,x\rangle = \langle c, Jy\rangle = \langle J^T c,y\rangle$, which proves \Cref{reducD_item2}.
+  First, if $D={\bf 0}$, then by the assumptions one must have $e=0$, and the problem
+  is already reduced (with $J=I_n$ and $x_0=0$).
+  Next, assume $D={\bf 0}$, then $Dx=e$ and $Ax + b \le 0$ if and only if
+  $AJy + b+Ax_0 \le 0$, proving \Cref{reducD_item1}. Finally, for all
+  $c \in K^n$, $\langle c,x\rangle = \langle c, Jy\rangle = \langle J^T c,y\rangle$, which proves \Cref{reducD_item2}.
 \end{proof}

### 2025-05-16 article/paper_padic_spec.tex
commit by Simone

@@
 
-Concerning the usage of SNF in the resolution of \eqref{LP}, note that the transition matrices $P$ and $Q$ defining SNF$(M)$ in \Cref{smith_nf} are invertible in $\OK$ and as such they preserve inequalities.
 %%%%Indeed, for all $z \in K^n$ and $M \in \allmat_n(\OK)$ if $z \geq 0$, then $Mz \geq 0$.
 The latter property is a direct consequence of $\OK$ being a ring and the converse holds if the matrix $M$ is invertible in $\OK$.
-Therefore, for all matrix $M \in K^{n\times n}$ and vector $z \in K^n$,
-then $Mz \geq 0$ if and only if $Sz \geq 0$, with $S = \mathrm{SNF}(M)$.
 
@@
 \begin{proof}
-  First, since $Q \in \GL_m(\OK)$, one has that $Ax+b = AP^{-1}y +b \geq 0$
-  if and only if $Q(AP^{-1}y + b) = Sy + b' \geq 0$; this yields \Cref{solsLP_item1}.
-  Next, for all $c \in K^n$, we have $\langle c,
-  x\rangle = \langle c, P^{-1}Px \rangle = \langle \left(P^{-1}\right)^T c, Px \rangle = \langle c',y\rangle$,
-  which proves \Cref{solsLP_item2}.
+  Note that the transition matrices $P$ and $Q$ defining SNF$(A)$ are invertible in $\OK$
+  and as such they preserve inequalities: $Mz \geq 0$ if and only if $Nz \geq 0$, with
+  $N = \mathrm{SNF}(M)$. Thus one has that $Ax+b = AP^{-1}y +b \geq 0$ if and only if
+  $Q(AP^{-1}y + b) = Sy + b' \geq 0$; this yields \Cref{solsLP_item1}.
+
+  Next, for all $c \in K^n$, we have $\langle c, x\rangle = \langle c, P^{-1}Px \rangle =
+  \langle \left(P^{-1}\right)^T c, Px \rangle = \langle c',y\rangle$, which proves
+  \Cref{solsLP_item2}.
 \end{proof}

### 2025-05-16 article/paper_padic_spec.tex
commit by Simone

@@
       \IF{$D \neq {\bf 0}$}
-      \STATE $[\mathrm{STATUS}, y] \leftarrow $
-      \RETURN 
+      \STATE find $J \in K^{n \times R}$, with $R = \dim\ker D$, such that $\text{Im}\, J = \ker D$
+      \STATE find $x_0$ such that $Dx_0=e$
+      \STATE $[\mathrm{STATUS}, y] \leftarrow \text{SOLVELP}(AJ,b+A x_0,J^T c,0,0)$
+      \RETURN $[\mathrm{STATUS}, y]$
       \ENDIF
@@
   is already reduced (with $J=I_n$ and $x_0=0$).
-  Next, assume $D={\bf 0}$, then $Dx=e$ and $Ax + b \le 0$ if and only if
+  Next, assume $D\neq{\bf 0}$, then $Dx=e$ and $Ax + b \le 0$ if and only if
   $AJy + b+Ax_0 \le 0$, proving \Cref{reducD_item1}. Finally, for all
@@
   $Q(AP^{-1}y + b) = Sy + b' \geq 0$; this yields \Cref{solsLP_item1}.
-
-  Next, for all $c \in K^n$, we have $\langle c, x\rangle = \langle c, P^{-1}Px \rangle =
-  \langle \left(P^{-1}\right)^T c, Px \rangle = \langle c',y\rangle$, which proves
+  Moreover, for all $c \in K^n$, we have $\langle c, x\rangle = \langle c, P^{-1}Px \rangle =
+  \langle (P^{-1})^T c, Px \rangle = \langle c',y\rangle$, which proves
   \Cref{solsLP_item2}.

### 2025-05-16 article/paper_padic_spec.tex
algo formal
commit by Simone

@@
 \begin{algorithm}
-    \caption{SOLVELP($A,b,c,D,e$)}\label{algo_LP}
+    \caption{\textbf{SOLVELP}($A,b,c,D,e$)}\label{algo_LP}
     \begin{algorithmic}[1]
@@
       \STATE find $x_0$ such that $Dx_0=e$
-      \STATE $[\mathrm{STATUS}, y] \leftarrow \text{SOLVELP}(AJ,b+A x_0,J^T c,0,0)$
-      \RETURN $[\mathrm{STATUS}, y]$
+      \RETURN $\textbf{SOLVELP}(AJ,b+A x_0,J^T c,0,0)$
       \ENDIF
-      %\FOR{epochs = $1$ to $N$}
-      %\WHILE{$(j\le m)$}
-      %\STATE Randomly initialize $w_i=\{w_1,w_2,\dots,w_n\}$
-      %\STATE input $o_j=\{o_1,o_2,\dots,o_m\}$ in the input layer
-      %\STATE forward propagate $(f_i\cdot w_i)$ through layers until getting the predicted result $y$
-      %\STATE compute $e=y-y^2$
-      %\STATE back propagate $e$ from right to left through layers
-      %\STATE update $w_i$
-      %\ENDWHILE
-      %\ENDFOR
+      \STATE $[Q,S,P] \leftarrow \textbf{SNF}(A)$
+      \IF{$S \neq A$}
+      \STATE $[\mathrm{STATUS}, y] \leftarrow \textbf{SOLVELP}(S,Qb,(P^{-1})^Tc,0,0)$
+      \RETURN $[\mathrm{STATUS}, P^{-1}y]$
+      \ELSE
+      \STATE
+      \ENDIF
     \end{algorithmic}
@@
 
-\begin{proposition}\label{reducD}
+\begin{lemma}\label{reducD}
   Let $A \in K^{d \times n}, b \in K^d, c\in K^n$, $D \in K^{m\times n}$,
@@
   \end{enumerate}
-\end{proposition}
-
+\end{lemma}
 \begin{proof}
@@
 
-\Cref{solsLP} allows us to reduce \eqref{LP} to diagonal linear programs.
-
-\begin{proposition} \label{solsLP}
+\Cref{solsLP} allows us to reduce Problem \eqref{LP} without linear equations
+to diagonal linear programs.
+
+\begin{lemma} \label{solsLP}
   Let $A \in K^{d\times n}$, $b \in K^d$, $c\in K^n$ and let
@@
    \end{enumerate}
-\end{proposition}
+\end{lemma}
 \begin{proof}
@@
 
-\begin{proposition}\label{prop:reduc}
-  Let $(A,b,c), (S,b',c') \in K^{d\times n} \times K^d \times K^n$ be as in \Cref{solsLP},
-  where $S = \mathrm{SNF}(A)$. Then
+Finally we show in \Cref{prop:reduc} that solving a diagonal \eqref{LP} amounts
+to checking the valuations of input data:
+
+\begin{lemma}\label{prop:reduc}
+  Let $(A,b,c), (S,b',c') \in K^{d\times n} \times K^d \times K^n$ be as in \Cref{solsLP}.
+  Then:
   \begin{enumerate}
@@
   \end{enumerate}
-\end{proposition}
+\end{lemma}
 \begin{proof}

### 2025-05-16 article/paper_padic_spec.tex
commit by Simone

@@
 \usepackage{graphicx}
-\usepackage{color}
+\usepackage{color,xcolor}
 \usepackage{ulem}
@@
 For the sake of ease of writing, block-diagonal matrices with blocks
-$B_1,\ldots,B_d$ are denoted by $\diag(B_1, \ldots, B_d)$, the null square
-matrix of size $t$ by ${\bf 0}_{t}$, and the identity matrix by $I_t$.
+$B_1,\ldots,B_d$ are denoted by $\diag(B_1, \ldots, B_d)$, the null matrix of
+size $p \times q$ by ${\bf 0}_{p,q}$, and the identity matrix by $I_t$.
 
@@
   $$
-  \mathrm{SNF}(M) := QMP^{-1} = \diag(\pi^{a_1}, \pi^{a_2}, \ldots, \pi^{a_r}, {\bf 0}_{\min(m,n)-r}).
+  \mathrm{SNF}(M) := QMP^{-1} = \diag(\pi^{a_1}, \pi^{a_2}, \ldots, \pi^{a_r}, {\bf 0}_{m-r,n-r}).
   $$
@@
 Real polyhedra (subsets of $\R^n$ defined by finitely many affine inequalities) are special cases of real
-spectrahedra, where the defining matrices $A_0, \ldots, A_n$ can be chosen diagonal, so that $A(x) =
-\ell_1(x) \oplus \cdots \oplus \ell_d(x)$. In other words, SDP is a generalization of Linear Programming (LP).
+spectrahedra, where the defining matrices $A_0, \ldots, A_n$ can be chosen diagonal, so that
+$A = \diag(\ell_1,\ldots, \ell_d)$. In other words, SDP is a generalization of Linear Programming (LP).
 
@@
 $D=0$'', car cela ne me semble pas nécessaire pour définir le ``diagonal LP''.}},
-we often refer to \eqref{LP} as a \emph{diagonal} linear program.
+we refer to \eqref{LP} as a \emph{diagonal} linear program.
 We denote the \emph{feasible set} of \eqref{LP} by
@@
       \STATE find $x_0$ such that $Dx_0=e$
-      \RETURN $\textbf{SOLVELP}(AJ,b+A x_0,J^T c,0,0)$
+      \RETURN $\textbf{SOLVELP}(AJ,b+A x_0,J^T c, {\bf 0},0)$ \hfill {\color{olive} \# \Cref{reducD}}
       \ENDIF
+      \IF{$A$ not in Smith Normal Form}
       \STATE $[Q,S,P] \leftarrow \textbf{SNF}(A)$
-      \IF{$S \neq A$}
-      \STATE $[\mathrm{STATUS}, y] \leftarrow \textbf{SOLVELP}(S,Qb,(P^{-1})^Tc,0,0)$
-      \RETURN $[\mathrm{STATUS}, P^{-1}y]$
+      \STATE $[\mathrm{STATUS}, y] \leftarrow \textbf{SOLVELP}(S,Qb,(P^{-1})^Tc,{\bf 0},0)$
+      \RETURN $[\mathrm{STATUS}, P^{-1}y]$ \hfill {\color{olive} \# \Cref{solsLP}}
       \ELSE
       \STATE
+      \STATE
+      \RETURN ... \hfill {\color{olive} \# \Cref{prop:reduc}}
       \ENDIF
@@
 We first prove a reduction result, allowing to consider only iterations
-of~\eqref{LP} with data of the form $(A,b,c,0,0)$.
+of~\eqref{LP} with data of the form $(A,b,c,{\bf 0},0)$.
 
@@
     $x$ is feasible for~\eqref{LP} with data $(A,b,c,D,e)$ if and only if 
-    $y$ is feasible for~\eqref{LP} with data $(AJ,b+A x_0,J^T c,0,0)$.
+    $y$ is feasible for~\eqref{LP} with data $(AJ,b+A x_0,J^T c,{\bf 0},0)$.
   \item\label{reducD_item2}
     $x$ is a solution for~\eqref{LP} with data $(A,b,c,D,e)$ if and only if 
-    $y$ is a solution for~\eqref{LP} with data $(AJ,b+A x_0,J^T c,0,0)$ and
+    $y$ is a solution for~\eqref{LP} with data $(AJ,b+A x_0,J^T c,{\bf 0},0)$ and
     $\langle c,x^* \rangle = \langle J^T c,y^* \rangle$\footnote{\simone{Est-ce que
@@
    \item \label{solsLP_item1}
-     $x \in K^n$ is feasible for \eqref{LP} with data $(A,b,c,0,0)$ if and only if $y = P x \in K^n$ is
-     feasible for \eqref{LP} with data $(S,b',c',0,0)$.
+     $x \in K^n$ is feasible for \eqref{LP} with data $(A,b,c,{\bf 0},0)$ if and only if $y = P x \in K^n$ is
+     feasible for \eqref{LP} with data $(S,b',c',{\bf 0},0)$.
    \item \label{solsLP_item2}
-     $x^* \in K^n$ is a solution to \eqref{LP} with data $(A,b,c,0,0)$ if and only if $y^* = P x^*$ is
-     a solution to \eqref{LP} with data $(S,b',c',0,0)$ and $\langle c,x^* \rangle = \langle c',y^* \rangle$.
+     $x^* \in K^n$ is a solution to \eqref{LP} with data $(A,b,c,{\bf 0},0)$ if and only if $y^* = P x^*$ is
+     a solution to \eqref{LP} with data $(S,b',c',{\bf 0},0)$ and $\langle c,x^* \rangle = \langle c',y^* \rangle$.
    \end{enumerate}
@@
 \begin{lemma}\label{prop:reduc}
-  Let $(A,b,c), (S,b',c') \in K^{d\times n} \times K^d \times K^n$ be as in \Cref{solsLP}.
+  Let $(S,b',c') \in K^{d\times n} \times K^d \times K^n$ be as in \Cref{solsLP}.
   Then:
@@
   \item \label{prop:reduc_it1}
-    \eqref{LP} with data $(S,b',c',0,0)$ is feasible if and only if the $d-r$ last coefficients
+    \eqref{LP} with data $(S,b',c',{\bf 0},0)$ is feasible if and only if the $d-r$ last coefficients
     of $b'$ have nonnegative valuation, for $r = {\rm rank}\,S$.
@@
   A vector $y = (y_1, \ldots, y_n)^T \in K^n$ is feasible for \eqref{LP} with data
-  $(S,b',c',0)$ if and only if $\val(s_i y_i + b_i) \geq 0$ for\footnote{\simone{Ce n'est pas plutôt $\val(s_i y_i + b'_i) \geq 0$ ? Car c'est $b'$ et non pas $b$.}} all $i = 1,\ldots,n$.
+  $(S,b',c',0)$ if and only if $\val(s_i y_i + b'_i) \geq 0$ for\footnote{\simone{J'ai mis
+    $\val(s_i y_i + b'_i) \geq 0$ au lieu de $\val(s_i y_i + b_i) \geq 0$ car c'est $b'$
+    et non pas $b$.}} all $i = 1,\ldots,n$.
   However $s_i = 0$ for $n-r \leq i\leq n$. Therefore, if \eqref{LP} with data $(S,b',c',0)$ is feasible,
@@
   $y_i = -\frac{-b'_i}{s_i}$ if $1 \leq i \leq r$, and $y_i =0$ otherwise, is feasible for \eqref{LP}
-  with data $(S,b',c',0,0)$.
-
-  Concerning \Cref{prop:reduc_it2}, let $y^*$ be feasible for \eqref{LP} with data $(S,b',c',0,0)$.
+  with data $(S,b',c',{\bf 0},0)$.
+
+  Concerning \Cref{prop:reduc_it2}, let $y^*$ be feasible for \eqref{LP} with data $(S,b',c',{\bf 0},0)$.
   Let $i$ be such that $r+1 \leq i \leq n$ and $c'_i \neq 0$. Consider the vector $e^i$ whose only non-zero
-  coefficient is the $i-$th, which is $1$. Then $y^* + \alpha e^i$ is feasible for \eqref{LP} with data $(S,b',c',0,0)$,
+  coefficient is the $i-$th, which is $1$. Then $y^* + \alpha e^i$ is feasible for \eqref{LP} with data $(S,b',c',{\bf 0},0)$,
   for all $\alpha \in K$ and $\langle c', y^* + \alpha e^i\rangle = \langle c' , y^* \rangle + \alpha c'_i$.

### 2025-05-16 article/paper_padic_spec.tex
commit by Simone

@@
       \ELSE
+      \IF{$\bigwedge_{i=r+1}^d \val(b_{i}) \geq 0$}
+      \STATE STATUS $\leftarrow$ FEAS
+      \STATE give solution in this case
+      \ENDIF
       \STATE
@@
   for all $\alpha \in K$ and $\langle c', y^* + \alpha e^i\rangle = \langle c' , y^* \rangle + \alpha c'_i$.
-  In particular, for all $n \in \mathbb{N}$ if we set $\alpha = -\frac{\langle c', y^* \rangle + \pi^{-n}}{c'_i}$, we have $\val \left( \langle c', y^* + \alpha e ^i \rangle\right) = \val \pi^{-n} = -n$.
+  In particular, for all $n \in \mathbb{N}$ if we set $\alpha_n = -({\langle c', y^* \rangle + \pi^{-n}})/{c'_i}$,
+  we have $\val \left(\langle c', y^* + \alpha_n e ^i \rangle\right) = \val \pi^{-n} = -n$.
   Therefore, the problem is unbounded as $p^* = -\infty$\footnote{\simone{avant c'était ``Therefore, the problem is unbounded as $p^* = +\infty$'' ce qui ne me paraît pas correct.}}.

### 2025-05-16 article/paper_padic_spec.tex
commit by Simone

@@
 
-In this section we present an algorithm for solving Problem \eqref{LP}.
+In this section we present \Cref{algo_LP}, \textbf{SOLVELPval}, for solving Problem \eqref{LP}.
 The algorithm starts by eliminating the equality constraint defined by $D$ and $e$
@@
 
-We first give a formal description of our algorithm:
-
 \begin{algorithm}
-    \caption{\textbf{SOLVELP}($A,b,c,D,e$)}\label{algo_LP}
+    \caption{\textbf{SOLVELPval}($A,b,c,D,e$)}\label{algo_LP}
     \begin{algorithmic}[1]
@@
       \STATE find $x_0$ such that $Dx_0=e$
-      \RETURN $\textbf{SOLVELP}(AJ,b+A x_0,J^T c, {\bf 0},0)$ \hfill {\color{olive} \# \Cref{reducD}}
+      \RETURN $\textbf{SOLVELPval}(AJ,b+A x_0,J^T c, {\bf 0},0)$ \hfill {\color{olive} \# \Cref{reducD}}
       \ENDIF
@@
       \STATE $[Q,S,P] \leftarrow \textbf{SNF}(A)$
-      \STATE $[\mathrm{STATUS}, y] \leftarrow \textbf{SOLVELP}(S,Qb,(P^{-1})^Tc,{\bf 0},0)$
+      \STATE $[\mathrm{STATUS}, y] \leftarrow \textbf{SOLVELPval}(S,Qb,(P^{-1})^Tc,{\bf 0},0)$
       \RETURN $[\mathrm{STATUS}, P^{-1}y]$ \hfill {\color{olive} \# \Cref{solsLP}}
       \ELSE
+      \STATE $r \leftarrow \text{rank}(A)$
       \IF{$\bigwedge_{i=r+1}^d \val(b_{i}) \geq 0$}
@@
       \STATE give solution in this case
-      \ENDIF
+      \ELSE
       \STATE
@@
       \RETURN ... \hfill {\color{olive} \# \Cref{prop:reduc}}
+      \ENDIF
       \ENDIF
@@
   Conversely, if the $d-r$ last coefficients of $b'$ are zero, the vector $y \in K^n$ such that
-  $y_i = -\frac{-b'_i}{s_i}$ if $1 \leq i \leq r$, and $y_i =0$ otherwise, is feasible for \eqref{LP}
+  $y_i = {-b'_i}/{s_i}$ if $1 \leq i \leq r$, and $y_i =0$ otherwise, is feasible for \eqref{LP}
   with data $(S,b',c',{\bf 0},0)$.

### 2025-05-17 article/paper_padic_spec.tex
correctness

@@
       \IF{$Dx = e$ has no solution}
-      \RETURN [INFEAS, []]
+      \RETURN [INFEAS, []] \label{step:linear_empty}
       \ENDIF
-      \IF{$D \neq {\bf 0}$}
+      \IF{$D \neq {\bf 0}$} \label{step:reducD:begin}
       \STATE find $J \in K^{n \times R}$, with $R = \dim\ker D$, such that $\text{Im}\, J = \ker D$
-      \STATE find $x_0$ such that $Dx_0=e$
-      \RETURN $\textbf{SOLVELPval}(AJ,b+A x_0,J^T c, {\bf 0},0)$ \hfill {\color{olive} \# \Cref{reducD}}
+      \STATE find $x_0$ such that $Dx_0=e$ \label{step:reducD:end}
+      \RETURN $\textbf{SOLVELPval}(AJ,b+A x_0,J^T c, {\bf 0},0)$ \label{step:reducD} \hfill {\color{olive} \# \Cref{reducD}}
       \ENDIF
@@
       \STATE STATUS $\leftarrow$ FEAS
-      \STATE give solution in this case
+      \STATE $\lambda \leftarrow \sum_{i=1}^r -c_i b_i / s_i$
+      \STATE $v \leftarrow $
+      \STATE 
       \ELSE
@@
   \begin{proof}
+    If the linear system $Dx=e$, Problem \eqref{LP} is infeasible
+    and \Cref{algo_LP} outputs correct answer at Step \ref{step:linear_empty}.
+    Else, by \Cref{reducD} the input problem can be reduced to a new linear
+    program with $D={\bf 0}$ and $e=0$, which is done on Steps
+    \ref{step:reducD:begin}-\ref{step:reducD:end},
+    and the correct output is given at Step \ref{step:reducD}.
   \end{proof}

### 2025-05-17 article/paper_padic_spec.tex
correctness

--- 2025-05-16 article/paper_padic_spec.tex
@@
       \IF{$Dx = e$ has no solution}
-      \RETURN [INFEAS, []]
+        \RETURN [INFEAS, []] \label{step:linear_empty}
       \ENDIF
-      \IF{$D \neq {\bf 0}$}
+      \IF{$D \neq {\bf 0}$} \label{step:reducD:begin}
         \STATE find $J \in K^{n \times R}$, with $R = \dim\ker D$, such that $\text{Im}\, J = \ker D$
-      \STATE find $x_0$ such that $Dx_0=e$
-      \RETURN $\textbf{SOLVELPval}(AJ,b+A x_0,J^T c, {\bf 0},0)$ \hfill {\color{olive} \# \Cref{reducD}}
+        \STATE find $x_0$ such that $Dx_0=e$ \label{step:reducD:end}
+        \RETURN $\textbf{SOLVELPval}(AJ,b+A x_0,J^T c, {\bf 0},0)$ \label{step:reducD} \hfill {\color{olive} \# \Cref{reducD}}
       \ENDIF
-      \IF{$A$ not in Smith Normal Form}
+      \IF{$A$ not in Smith Normal Form} \label{step:solsLP:begin}
         \STATE $[Q,S,P] \leftarrow \textbf{SNF}(A)$
-      \STATE $[\mathrm{STATUS}, y] \leftarrow \textbf{SOLVELPval}(S,Qb,(P^{-1})^Tc,{\bf 0},0)$
-      \RETURN $[\mathrm{STATUS}, P^{-1}y]$ \hfill {\color{olive} \# \Cref{solsLP}}
+        \STATE $[\mathrm{STATUS}, y] \leftarrow \textbf{SOLVELPval}(S,Qb,(P^{-1})^Tc,{\bf 0},0)$ \label{step:solsLP:end}
+        \RETURN $[\mathrm{STATUS}, P^{-1}y]$ \hfill {\color{olive} \# \Cref{solsLP}} \label{step:solsLP}
+      \ENDIF
+      \STATE $r \leftarrow \text{rank}(A)$ \label{step:core:begin}
+      \IF{$\bigwedge_{i=r+1}^d \val(b_{i}) \geq 0$}
+        \IF{$\bigvee_{i=r+1}^n c_i \neq 0$}
+        \RETURN [UNBOUND, []] \hfill {\color{olive} \# \Cref{prop:reduc}, item \ref{prop:reduc_it2}}
         \ELSE
-      \STATE $r \leftarrow \text{rank}(A)$
-      \IF{$\bigwedge_{i=r+1}^d \val(b_{i}) \geq 0$}
-      \STATE STATUS $\leftarrow$ FEAS
-      \STATE give solution in this case
+          %\STATE STATUS $\leftarrow$ FEAS
+          \STATE $\lambda \leftarrow -\sum_{i=1}^r c_i b_i / s_i$
+          \STATE $v \leftarrow \min_{1 \leq i \leq r} \val (c_i/s_i)$
+          \IF{$\val \lambda < v$}
+            \STATE choose $y \in K^n$ such that $y_i \in (-b_i+\OK)/s_i, i=1,\ldots,r$
+            \RETURN [FEAS, $y$]
           \ELSE
-      \STATE
-      \STATE
-      \RETURN ... \hfill {\color{olive} \# \Cref{prop:reduc}}
+            \STATE find $y \in K^n$ such that $y_i \in (-b_i+\OK)/s_i, i=1,\ldots,r$
+            and $\langle c,y\rangle = \pi^v\OK$
+            \RETURN [FEAS, $y$]
           \ENDIF
         \ENDIF 
+      \ENDIF
+        %\STATE
+        %\STATE
+        %\RETURN ... \hfill {\color{olive} \# \Cref{prop:reduc}}
+      %\ENDIF \label{step:core:end}
+      \RETURN [INFEAS, []]
     \end{algorithmic}
@@
 \]
-where $\lambda = \sum_{i=1}^r -c'_i \frac{b'_i}{s_i}$ and $v = \min\limits_{1\le i\le r} \val \frac{c'_{i}}{s_{i}} $.
+where $\lambda = -\sum_{i=1}^r c'_i \frac{b'_i}{s_i}$ and $v = \min\limits_{1\le i\le r} \val \frac{c'_{i}}{s_{i}} $.
 
 Two cases can occur depending on $v$ and the valuation of $\lambda$.
-If $\val(\lambda) < v$, the minimum of $y\mapsto \val\left(\left\langle c',y \right\rangle\right)$ over $\PP'$
-  is reached at any point of $\PP'$, and is equal to $\val(\lambda)$.
-  Otherwise, if $\val(\lambda) \ge v$, then $\lambda \in \pi^{v} \OK$ and the minimum is $v$ and is reached at any points $y$
-  of $\PP'$ such that $\left<c',y \right> \in \pi^v$.
-
-  We conclude with a correctness theorem.
+If $\val(\lambda) < v$, the minimum of $y\mapsto \val\left(\left\langle c',y \right\rangle\right)$ over $\PP'$ is reached at any point of $\PP'$, and is equal to $\val(\lambda)$.
+Otherwise, if $\val(\lambda) \ge v$, then $\lambda \in \pi^{v} \OK$ and the minimum is $v$ and is reached at any points $y$ of $\PP'$ such that\footnote{\simone{J'imagine que c'est plutôt
+$\left<c',y \right> \in \pi^v\OK$ ?}} $\left<c',y \right> \in \pi^v$.
+
+We conclude with a correctness theorem for \Cref{algo_LP}.
 
@@
   \begin{proof}
+    If the linear system $Dx=e$, Problem \eqref{LP} is infeasible
+    and \Cref{algo_LP} outputs correct answer at step \ref{step:linear_empty}.
+    Else, by \Cref{reducD} the input problem can be reduced to a new linear
+    program with $D={\bf 0}$ and $e=0$, which is done at steps
+    \ref{step:reducD:begin}-\ref{step:reducD:end},
+    and the correct output is given at step \ref{step:reducD}.
+    The reduction based on SNF from \Cref{solsLP} is performed at
+    steps \ref{step:solsLP:begin}-\ref{step:solsLP:end} and the output
+    is given at step \ref{step:solsLP}.
+
+    The core of \Cref{algo_LP} is on steps \ref{step:core:begin}-\ref{step:core:end}.
+
+    TO BE CONTINUED.
   \end{proof}
@@
 \begin{remark}
-	If $\val \lambda \ge v$ and $i_0 \in \{1,\ldots, n\} $ is such that $v = \val \frac{c_{i_0}'}{s_{i_0}²} $ 
-  then the vector $e^{i_0} \in K$ is a solution of \ref{LP}, 
-  where $e^{i_0}$ denotes the vector of $K^n$ whose only non-zero coefficient is the $i_0$-th which is $1$.
+  If $\val \lambda \ge v$ and $i_0 \in \{1,\ldots, n\} $ is such that
+  $v = \val \frac{c_{i_0}'}{s_{i_0}²} $ then the vector $e^{i_0} \in K$ is a solution of \ref{LP}, 
+  where $e^{i_0}$ denotes the vector of $K^n$ whose only non-zero coefficient is the $i_0$-th
+  which is $1$.
 \end{remark}

### 2025-05-18 article/paper_padic_spec.tex
commit by Simone

@@
           \ELSE
-            \STATE find $y \in K^n$ such that $y_i \in (-b_i+\OK)/s_i, i=1,\ldots,r$
-            and $\langle c,y\rangle = \pi^v\OK$
-            \RETURN [FEAS, $y$]
+          \STATE $i \leftarrow \min_{1 \leq i \leq r} \{i : v = \val (c_i/s_i)\}$
+          %find $y \in K^n$ such that $y_i \in (-b_i+\OK)/s_i, i=1,\ldots,r$
+          %and $\langle c,y\rangle = \pi^v\OK$
+            \RETURN [FEAS, ${\bf e}_i$]
           \ENDIF
@@
 
-The previous results imply that we can consider iterations of diagonal linear programs admitting a solution.
+%The previous results imply that we can consider iterations of diagonal linear programs admitting a solution.
 By \Cref{prop:reduc} one can simplify the problem by only taking account the first $r$ coefficients of $y, b', c'$ and the submatrix of $S$ made by the $r$ first rows and columns corresponding to the nonzero invariants factors.
 
+We conclude by the following Lemma:
+\begin{lemma}\label{solutions}
+  Let $(S,b',c') \in K^{d\times n} \times K^d \times K^n$ be as in \Cref{solsLP}.
+  Let $\lambda = -\sum_{i=1}^r c'_i \frac{b'_i}{s_i}$ and $v = \min\limits_{1\le i\le r} \val \frac{c'_{i}}{s_{i}}$.
+\end{lemma}
+\begin{proof}
 The feasible set $\PP' = \{y \in K^n : Sy+b' \geq 0\}$ of the diagonal LP can be written as the set of vectors
@@
 $\left<c',y \right> \in \pi^v\OK$ ?}} $\left<c',y \right> \in \pi^v$.
-
-We conclude with a correctness theorem for \Cref{algo_LP}.
+\end{proof}
+
+We are now able to state a correctness theorem for \Cref{algo_LP}.
 

### 2025-05-18 article/paper_padic_spec.tex
commit by Simone

@@
 
-We conclude by the following Lemma:
+We conclude by giving explicit solutions to the reduced \eqref{LP}:
+
 \begin{lemma}\label{solutions}
-  Let $(S,b',c') \in K^{d\times n} \times K^d \times K^n$ be as in \Cref{solsLP}.
-  Let $\lambda = -\sum_{i=1}^r c'_i \frac{b'_i}{s_i}$ and $v = \min\limits_{1\le i\le r} \val \frac{c'_{i}}{s_{i}}$.
+  Assume \eqref{LP} with data $(S,b',c',{\bf 0}, 0)$ be as in \Cref{solsLP} is feasible,
+  with feasible set $\PP' = \{y \in K^n : Sy+b' \geq 0\}$.
+  Let $\lambda = -\sum_{i=1}^r c'_i b'_i/s_i$ and $v = \min_{1\le i\le r} \val (c'_i/s_i)$.
+  If $\val \lambda < v$, the minimum is $\val \lambda$ and is attained on every $x \in \mathcal{P}'$;
+  if $\val \lambda \geq v$, the minimum is $v$ and is attained on ${\bf e}_i = (0,\ldots,0,1,0,\ldots,0}$.
 \end{lemma}

### 2025-05-18 article/paper_padic_spec.tex
commit by Simone

@@
   If $\val \lambda < v$, the minimum is $\val \lambda$ and is attained on every $x \in \mathcal{P}'$;
-  if $\val \lambda \geq v$, the minimum is $v$ and is attained on ${\bf e}_i = (0,\ldots,0,1,0,\ldots,0}$.
+  if $\val \lambda \geq v$, the minimum is $v$ and is attained on ${\bf e}_i = (0,\ldots,0,1,0,\ldots,0)$.
 \end{lemma}

### 2025-05-19 article/paper_padic_spec.tex
commit by Simone

--- 2025-05-18 article/paper_padic_spec.tex
@@
         \STATE $[\mathrm{STATUS}, y] \leftarrow \textbf{SOLVELPval}(S,Qb,(P^{-1})^Tc,{\bf 0},0)$ \label{step:solsLP:end}
-        \RETURN $[\mathrm{STATUS}, P^{-1}y]$ \hfill {\color{olive} \# \Cref{solsLP}} \label{step:solsLP}
+        \RETURN $[\mathrm{STATUS}, P^{-1}y]$ \hfill \color{olive} \# \Cref{solsLP} \label{step:solsLP}
       \ENDIF
@@
             \STATE choose $y \in K^n$ such that $y_i \in (-b_i+\OK)/s_i, i=1,\ldots,r$
-            \RETURN [FEAS, $y$]
+            \RETURN [FEAS, $y$] \hfill {\color{olive} \# \Cref{solutions}, item \ref{solutions:it1}}
           \ELSE
-          \STATE $i \leftarrow \min_{1 \leq i \leq r} \{i : v = \val (c_i/s_i)\}$
+          \STATE $j \leftarrow \min_{1 \leq i \leq r} \{i : v = \val (c_i/s_i)\}$
           %find $y \in K^n$ such that $y_i \in (-b_i+\OK)/s_i, i=1,\ldots,r$
           %and $\langle c,y\rangle = \pi^v\OK$
-            \RETURN [FEAS, ${\bf e}_i$]
+            \RETURN [FEAS, ${\bf e}_j$] \hfill {\color{olive} \# \Cref{solutions}, item \ref{solutions:it2}}
           \ENDIF
@@
       %\ENDIF \label{step:core:end}
-      \RETURN [INFEAS, []]
+      \RETURN [INFEAS, []] \label{step:core:end}
     \end{algorithmic}
@@
 
-We conclude by the following Lemma:
+We conclude by giving explicit solutions to the reduced \eqref{LP}:
+
 \begin{lemma}\label{solutions}
-  Let $(S,b',c') \in K^{d\times n} \times K^d \times K^n$ be as in \Cref{solsLP}.
-  Let $\lambda = -\sum_{i=1}^r c'_i \frac{b'_i}{s_i}$ and $v = \min\limits_{1\le i\le r} \val \frac{c'_{i}}{s_{i}}$.
+  Let $(S,b',c',{\bf 0}, 0)$ be as in \Cref{solsLP} and assume \eqref{LP} is feasible.
+  %%%$\PP' \neq \emptyset$.
+  %%%= \{y \in K^n : Sy+b' \geq 0\}
+  For $\lambda = -\sum_{i=1}^r c'_i b'_i/s_i$ and $v = \min_{1\le i\le r} \val (c'_i/s_i)$,
+  one has:
+  \begin{enumerate}
+  \item
+    if $\val \lambda < v$, the minimum is $\val \lambda$ and is attained on the whole feasible
+    set; \label{solutions:it1}
+  \item
+    if $\val \lambda \geq v$, the minimum is $v$ and is attained on
+    ${\bf e}_j \in K^n$, the vector with all $0$'s except with a $1$ on the $j$-th component,
+    with $j$ satisfying $\val (c'_j/s_j) = v$. \label{solutions:it2}
+  \end{enumerate}
+  %One has
+  %$$
+  %\langle c',\mathcal{P}'\rangle = \lambda + \pi^v\OK.
+  %$$
+  %If attained on every $x \in \mathcal{P}'$;
 \end{lemma}
 \begin{proof}
-The feasible set $\PP' = \{y \in K^n : Sy+b' \geq 0\}$ of the diagonal LP can be written as the set of vectors
-$y \in K^n$ that verifies $s_i y_i + b'_i \in \OK$ for $i=1,...,r$ {\it i.e.}:
+  The feasible set $\PP' = \{y \in K^n : Sy+b' \geq 0\}$ of the diagonal LP can be written
+  as the set of vectors $y \in K^n$ that verifies $s_i y_i + b'_i \in \OK$ for $i=1,...,r$.
+  In other words:
   $$
@@
   $$
-
-Solving the diagonal \eqref{LP} consists -- by definition -- in minimizing the linear map $y \mapsto \val\left(\left\langle
-c',y \right\rangle\right)$ over $\PP'$. The image of $\PP'$ by $y \mapsto \left\langle c',y \right\rangle$ is
+  The minimum in \eqref{LP} is the minimum of
+  $y \mapsto \val\left(\left\langle c',y \right\rangle\right)$ on $\PP'$.
+  The image of $\PP'$ by $y \mapsto \left\langle c',y \right\rangle$ is
   \[
-\left\langle c',\PP' \right\rangle = \sum_{i=1}^r -c'_i \frac{b'_i}{s_i} + \sum_{i=1}^r\left( \frac{c'_i}{s_{i}} \OK \right) = \lambda + \pi^{v} \OK
+  \left\langle c',\PP' \right\rangle = \sum_{i=1}^r -c'_i \frac{b'_i}{s_i} + \sum_{i=1}^r\left( \frac{c'_i}{s_{i}} \OK \right) = \lambda + \pi^{v} \OK.
   \]
-where $\lambda = -\sum_{i=1}^r c'_i \frac{b'_i}{s_i}$ and $v = \min\limits_{1\le i\le r} \val \frac{c'_{i}}{s_{i}} $.
-
   Two cases can occur depending on $v$ and the valuation of $\lambda$.
   If $\val(\lambda) < v$, the minimum of $y\mapsto \val\left(\left\langle c',y \right\rangle\right)$ over $\PP'$ is reached at any point of $\PP'$, and is equal to $\val(\lambda)$.
-Otherwise, if $\val(\lambda) \ge v$, then $\lambda \in \pi^{v} \OK$ and the minimum is $v$ and is reached at any points $y$ of $\PP'$ such that\footnote{\simone{J'imagine que c'est plutôt
-$\left<c',y \right> \in \pi^v\OK$ ?}} $\left<c',y \right> \in \pi^v$.
+  Otherwise, $\lambda \in \pi^{v} \OK$ and the minimum is $v$ and is reached at any points $y$ of $\PP'$ such that\footnote{\simone{J'imagine que c'est plutôt
+    $\left<c',y \right> \in \pi^v\OK$ ? Avant c'etait $\left<c',y \right> \in \pi^v$.}}
+  $\left<c',y \right> \in \pi^v\OK$.
 \end{proof}
@@
   \ref{step:reducD:begin}-\ref{step:reducD:end},
-  and the correct output is given at step \ref{step:reducD}.
+  and the correct recursion is given at step \ref{step:reducD}.
   The reduction based on SNF from \Cref{solsLP} is performed at
   steps \ref{step:solsLP:begin}-\ref{step:solsLP:end} and the output
-  is given at step \ref{step:solsLP}.
+  at step \ref{step:solsLP} is correct.
 

### 2025-05-19 article/paper_padic_spec.tex
commit by Simone
section LP

@@
       \STATE $r \leftarrow \text{rank}(A)$ \label{step:core:begin}
-      \IF{$\bigwedge_{i=r+1}^d \val(b_{i}) \geq 0$} 
+      \IF{$\bigwedge_{i=r+1}^d \val(b_{i}) \geq 0$} \label{step:condition}
         \IF{$\bigvee_{i=r+1}^n c_i \neq 0$}
-        \RETURN [UNBOUND, []] \hfill {\color{olive} \# \Cref{prop:reduc}, item \ref{prop:reduc_it2}}
+        \RETURN [UNBOUND, []] \hfill {\color{olive} \# \Cref{prop:reduc}, item \ref{prop:reduc_it2}} \label{step:unbound}
         \ELSE
@@
   The core of \Cref{algo_LP} is on steps \ref{step:core:begin}-\ref{step:core:end}.
-
-  TO BE CONTINUED.
-\end{proof}
-
-\begin{remark}
-  If $\val \lambda \ge v$ and $i_0 \in \{1,\ldots, n\} $ is such that
-  $v = \val \frac{c_{i_0}'}{s_{i_0}²} $ then the vector $e^{i_0} \in K$ is a solution of \ref{LP}, 
-  where $e^{i_0}$ denotes the vector of $K^n$ whose only non-zero coefficient is the $i_0$-th
-  which is $1$.
-\end{remark}
+  If $\val(b_i) \geq 0$, for all $i=1,\ldots,r+1$, with $r = \mathrm{rank}(A)$,
+  by \Cref{prop:reduc}, item \ref{prop:reduc_it1}, the problem \eqref{LP} is feasible.
+  Two cases can occur under this assumption:
+  either at least one of the $n-r$ last coefficients of $c'$ is non-zero,
+  in which case,
+  by \Cref{prop:reduc}, item \ref{prop:reduc_it2}, the problem is
+  unbounded and has no solution, thus the output on step \ref{step:unbound} is correct;
+  or all the $n-r$ last coefficients of $c'$ are null. In this case the solutions
+  are explicitely constructed according to \Cref{solutions}.
+
+  If the condition on step \ref{step:condition} is not satisfied, the problem
+  is infeasible by \Cref{prop:reduc} (step \ref{step:core:end}).
+\end{proof}
+
+%\begin{remark}
+%  If $\val \lambda \ge v$ and $i_0 \in \{1,\ldots, n\} $ is such that
+%  $v = \val \frac{c_{i_0}'}{s_{i_0}²} $ then the vector $e^{i_0} \in K$ is a solution of \ref{LP}, 
+%  where $e^{i_0}$ denotes the vector of $K^n$ whose only non-zero coefficient is the $i_0$-th
+%  which is $1$.
+%\end{remark}
 

### 2025-05-20 article/paper_padic_spec.tex
modif abstract

@@
   the related optimization problems with data over a field $K$ with valuation.
+  For $K$-polyhedra and linear programming over $K$ we give an algorithm based on computation
+  of Smith normal forms.
   We prove that basic properties of semidefinite-representable sets generalize to this setting.
-  We showcase examples of non-polyhedral $K$-spectrahedra and of sets that are semidefinite
-  representable over $K$ but are not $K$-spectrahedra.
+  In particular, we showcase examples of non-polyhedral $K$-spectrahedra and of sets that are
+  semidefinite representable over $K$ but are not $K$-spectrahedra.
 \end{abstract}

### 2025-05-22 article/paper_padic_spec.tex
modif abstract
commit by Simone

@@
 %\title{\bf On polyhedra and spectrahedra over valuation fields}
-\title{\bf On semidefinite-representable sets over valuation fields}
+\title{\Large \bf On semidefinite-representable sets over valuation fields}
 
@@
 Contrary to the LP case, the complexity status of SDP is widely open.
-In a fixed-precision model of computation, SDP is solvable in polynomial time in the input size (matrix size,
-number of variables, bit size of the coefficients), in $\log(\frac{1}{\varepsilon})$ (where $\varepsilon$ is the
-precision) and $\log(\frac{1}{R})$, where $R$ is an {\it a priori} upper bound on the norm of a solution,
-cf. \cite[Sec.1.9]{deKlerk}. In exact arithmetic, the complexity status of SDP is essentially open but complexity
-bounds are known based either on general quantifier elimination \cite{ramana1997exact,porkolab1997complexity}
-or by exploiting the determinantal structure of the constraints \cite{henrion2016exact}.
-
-In this paper we 
-Similar generalizations have been recently proposed in the context of tropical geometry \cite{iriarte2022polyhedral}.
+In a fixed-precision model of computation, SDP is solvable in polynomial time in the input size (matrix size, number of variables, bit size of the coefficients), in $\log(\frac{1}{\varepsilon})$ (where $\varepsilon$ is the precision) and $\log(\frac{1}{R})$, where $R$ is an {\it a priori} upper bound on the norm of a solution, cf.
+\cite[Sec.1.9]{deKlerk}.
+In exact arithmetic, the complexity status of SDP is essentially open but complexity bounds are known based either on general quantifier elimination \cite{ramana1997exact,porkolab1997complexity} or by exploiting the determinantal structure of the constraints \cite{henrion2016exact}.
+
+In this paper we consider the situation where input data are defined over fields $K$ with a prescribed valuation map $\val$ on $K$.
+The main example is the field of $p$-adic numbers with $p$-adic valuation.
+Similar generalizations have been recently proposed in the context of tropical geometry \cite{iriarte2022polyhedral} and tropical methods applied to non-archimedean semidefinite programming \cite{allamigeon2016solving}.
 

### 2025-05-23 article/paper_padic_spec.tex
commit by Simone

@@
 \usepackage{color,xcolor}
-\usepackage{ulem}
+%\usepackage{ulem}
 \usepackage{bm}
@@
 The main example is the field of $p$-adic numbers with $p$-adic valuation.
-Similar generalizations have been recently proposed in the context of tropical geometry \cite{iriarte2022polyhedral} and tropical methods applied to non-archimedean semidefinite programming \cite{allamigeon2016solving}.
+Similar generalizations have been recently proposed in the context of tropical geometry \cite{iriarte2022polyhedral} and tropical methods applied to non-archimedean semidefinite programming \cite{allamigeon2016solving,allamigeon_tropical_2020}.
 

### 2025-05-23 article/paper_padic_spec.tex
commit by Simone

@@
 The study of polyhedra and of linear programming (LP) is at the heart of convex geometry and optimization,
-inasmuch as several optimization problems can be cast as, or reduced to LP. An important generalization of LP
+inasmuch as several optimization problems can be cast as, or relaxed to LP. An important generalization of LP
 is semidefinite programming (SDP), namely the problem of minimizing an affine polynomial over the set of
 positive semidefinite affine combinations of a given collection of real symmetric matrices. The latter problem 
-has interested the community of polynomial optimization because of the relaxation method known as moment-SOS
-(or Lasserre) hierarchy \cite{henrion2020moment}.
+has interested the community of real algebraic geometry and polynomial optimization, mostly because of the
+relaxation method known as moment-SOS (or Lasserre) hierarchy \cite{henrion2020moment}.
 
@@
 The main example is the field of $p$-adic numbers with $p$-adic valuation.
+
+POLYHEDRA
+
+SPECTRAHEDRA
 Similar generalizations have been recently proposed in the context of tropical geometry \cite{iriarte2022polyhedral} and tropical methods applied to non-archimedean semidefinite programming \cite{allamigeon2016solving,allamigeon_tropical_2020}.

### 2025-05-23 article/paper_padic_spec.tex
commit by Simone

@@
 Contrary to the LP case, the complexity status of SDP is widely open.
-In a fixed-precision model of computation, SDP is solvable in polynomial time in the input size (matrix size, number of variables, bit size of the coefficients), in $\log(\frac{1}{\varepsilon})$ (where $\varepsilon$ is the precision) and $\log(\frac{1}{R})$, where $R$ is an {\it a priori} upper bound on the norm of a solution, cf.
-\cite[Sec.1.9]{deKlerk}.
-In exact arithmetic, the complexity status of SDP is essentially open but complexity bounds are known based either on general quantifier elimination \cite{ramana1997exact,porkolab1997complexity} or by exploiting the determinantal structure of the constraints \cite{henrion2016exact}.
+In a fixed-precision model of computation, SDP is solvable in polynomial time in the input size (matrix size, number of variables, bit size of the coefficients), in $\log(\frac{1}{\varepsilon})$ (where $\varepsilon$ is the precision) and $\log(\frac{R}{r})$, where $r,R$ are radii of balls respectively included in and containing the feasible set, cf.
+\cite{grotschel1981ellipsoid} or \cite[Thm.1.1]{de2016turing} (see also \cite[Sec.1.9]{deKlerk}).
+In exact arithmetic, complexity bounds are known based either on general quantifier elimination \cite{ramana1997exact,porkolab1997complexity} or by means of a dedicated application of the critical point method exploiting the determinantal structure of the constraints \cite{henrion2016exact,NALDI2018206}.
 

### 2025-05-23 article/paper_padic_spec.tex
some biblio / intro

@@
 \newcommand{\tristan}[1]{{\color{red} #1}} % tristan's comments
+\newcommand{\todo}[1]{{\color{blue}\bf \text{TODO: } #1}} % TODOs
 
@@
 Contrary to the LP case, the complexity status of SDP is widely open.
-In a fixed-precision model of computation, SDP is solvable in polynomial time in the input size (matrix size, number of variables, bit size of the coefficients), in $\log(\frac{1}{\varepsilon})$ (where $\varepsilon$ is the precision) and $\log(\frac{R}{r})$, where $r,R$ are radii of balls respectively included in and containing the feasible set, cf.
+A complexity analysis for the computation of an approximate solution of an SDP can be made based on the ellipsoid algorithm \cite{khachiyan1979polynomial,grotschel1981ellipsoid} or on interior-point methods \cite{de2016turing}; in this approximation model of computation, SDP is solvable in polynomial time in the input size (\emph{i.e.} matrix size, number of variables, bit size of the coefficients), $\log(\frac{1}{\varepsilon})$ (where $\varepsilon$ is the target precision) and $\log(\frac{R}{r})$, where $r,R$ are radii of balls respectively included in and containing the feasible set, cf.
 \cite{grotschel1981ellipsoid} or \cite[Thm.1.1]{de2016turing} (see also \cite[Sec.1.9]{deKlerk}).
-In exact arithmetic, complexity bounds are known based either on general quantifier elimination \cite{ramana1997exact,porkolab1997complexity} or by means of a dedicated application of the critical point method exploiting the determinantal structure of the constraints \cite{henrion2016exact,NALDI2018206}.
+
+Assuming the input data belongs to an effective field $K$ (\emph{e.g.} $K = \QQ$) then a solution can be described and computed as element of a vector space over some algebraic extension of $K$.
+In such exact model, complexity bounds are known based either on general quantifier elimination \cite{ramana1997exact,porkolab1997complexity} and explicit algorithms exist based on a dedicated application of the so-called critical point method, and exploiting the determinantal structure of the constraints \cite{henrion2016exact,NALDI2018206}.
+In the real numbers model of Blum, Shub and Smale \cite{blum2012complexity,blum1989theory}, the feasibility of SDP is in NP $\cap$ co-NP, whereas it is not known to be in NP in the Turing model \cite{ramana1997exact}.
 
@@
 The main example is the field of $p$-adic numbers with $p$-adic valuation.
+\todo{Give motivations for p-adic precision of LP/SDP.}
 

### 2025-05-23 article/paper_padic_spec.tex
encore intro

--- 2025-05-23 article/paper_padic_spec.tex
@@
 Contrary to the LP case, the complexity status of SDP is widely open.
-In a fixed-precision model of computation, SDP is solvable in polynomial time in the input size (matrix size, number of variables, bit size of the coefficients), in $\log(\frac{1}{\varepsilon})$ (where $\varepsilon$ is the precision) and $\log(\frac{R}{r})$, where $r,R$ are radii of balls respectively included in and containing the feasible set, cf.
+Ramana's construction \cite{ramana1997exact} implies a series of general results: in the Blum-Shub-Smale real numbers machines model \cite{blum1989theory}, the feasibility of SDP is in $\text{NP} \cap \text{co-NP}$, whereas it is not known to be in NP in the Turing model; checking boundedness, attainability and optimality can be polynomially reduced to the feasibility of SDP \cite{ramana1997exact}.
+
+Assuming the input data belongs to an effective field $K$ (\emph{e.g.} $K = \QQ$) then a solution can be described and computed as element of a vector space over some algebraic extension of $K$.
+For exact computation, complexity bounds are known based either on general quantifier elimination \cite{ramana1997exact,porkolab1997complexity} and explicit algorithms exist based on a dedicated application of the so-called critical point method, and exploiting the determinantal structure of the constraints \cite{henrion2016exact,NALDI2018206}.
+
+A complexity analysis for the computation of an approximate solution of an SDP can be made based on the ellipsoid algorithm \cite{khachiyan1979polynomial,grotschel1981ellipsoid} or on interior-point methods \cite{de2016turing}; in this approximation framework, SDP is solvable in polynomial time in the input size (\emph{i.e.} matrix size, number of variables, bit size of the coefficients), $\log(\frac{1}{\varepsilon})$ (where $\varepsilon$ is the target precision) and $\log(\frac{R}{r})$, where $r,R$ are radii of balls respectively included in and containing the feasible set, cf.
 \cite{grotschel1981ellipsoid} or \cite[Thm.1.1]{de2016turing} (see also \cite[Sec.1.9]{deKlerk}).
-In exact arithmetic, complexity bounds are known based either on general quantifier elimination \cite{ramana1997exact,porkolab1997complexity} or by means of a dedicated application of the critical point method exploiting the determinantal structure of the constraints \cite{henrion2016exact,NALDI2018206}.
 

### 2025-05-23 article/paper_padic_spec.tex
commit by Simone

@@
 
-The study of polyhedra and of linear programming (LP) is at the heart of convex geometry and optimization,
-inasmuch as several optimization problems can be cast as, or relaxed to LP. An important generalization of LP
-is semidefinite programming (SDP), namely the problem of minimizing an affine polynomial over the set of
-positive semidefinite affine combinations of a given collection of real symmetric matrices. The latter problem 
-has interested the community of real algebraic geometry and polynomial optimization, mostly because of the
-relaxation method known as moment-SOS (or Lasserre) hierarchy \cite{henrion2020moment}.
+The study of polyhedra and of linear programming (LP) is at the heart of convex geometry and optimization, inasmuch as several optimization problems can be cast as, or relaxed to LP.
+An important generalization of LP is semidefinite programming (SDP), namely the problem of minimizing a linear function over the set of positive semidefinite affine combinations of some real symmetric matrices.
+The latter problem has interested the community of real algebraic geometry and polynomial optimization, mostly because of the relaxation method known as moment-SOS (or Lasserre) hierarchy \cite{henrion2020moment}.
 

### 2025-06-04 article/paper_padic_spec.tex
titre
valuation field --> valued field

@@
 
-%\title{\bf Title}
-%\title{\bf On polyhedra and spectrahedra over valuation fields}
-\title{\Large \bf On semidefinite-representable sets over valuation fields}
+\title{\Large \bf On semidefinite-representable sets over valued fields}
 
@@
   semidefinite-representable sets. This paper investigates versions of these sets and of
-  the related optimization problems with data over a field $K$ with valuation.
+  the related optimization problems with data over a valued field $K$.
   For $K$-polyhedra and linear programming over $K$ we give an algorithm based on computation
@@
 Throughout the paper, $K$ refers to a complete,
-discrete valuation field, $\val : K \twoheadrightarrow \ZZ \cup \{+\infty\}$ to its valuation,
+discrete valued field, $\val : K \twoheadrightarrow \ZZ \cup \{+\infty\}$ to its valuation,
 $\OK$ its ring of integers, $\kappa$ its residue field and $\pi$ a uniformizer.
@@
 
-In this section, we define polyhedra over a complete discrete valuation field $K$ with valuation $\val$ and a uniformizer $\pi$, and we prove that the class of polyhedra is closed under linear transformations, as in the real case.
+In this section, we define polyhedra over a complete discrete valued field $K$ with valuation $\val$ and a uniformizer $\pi$, and we prove that the class of polyhedra is closed under linear transformations, as in the real case.
 We end by presenting an algorithm for solving linear optimization problems over $K$.
@@
 The following result shows that testing positive semidefiniteness of matrices over
-valuation fields reduces to checking whether the coefficients of $\chi_M$ are integers.
+valued fields reduces to checking whether the coefficients of $\chi_M$ are integers.
 
@@
 a spectrahedron: indeed an affine equation $\ell(x) = 0$ is equivalent to the two inequalities
-$\ell(x) \geq 0 \leq -\ell(x)$. Over a valuation field it is necessary to give the following
+$\ell(x) \geq 0 \leq -\ell(x)$. Over a valued field it is necessary to give the following
 definition in order to include affine sets in the family of spectrahedra.

### 2025-06-05 article/paper_padic_spec.tex
commit by Simone

@@
-\documentclass[a4paper,oneside,11pt]{article}
+\documentclass[a4paper,oneside,10pt]{article}
 
@@
 
-Contrary to the LP case, the complexity status of SDP is widely open.
+The main motivation for studying the effective aspects of SDP is the fact that, despite several properties of LP extend to SDP, the complexity status of SDP is, contrary to the LP case, widely open.
 Ramana's construction \cite{ramana1997exact} implies a series of general results: in the Blum-Shub-Smale real numbers machines model \cite{blum1989theory}, the feasibility of SDP is in $\text{NP} \cap \text{co-NP}$, whereas it is not known to be in NP in the Turing model; checking boundedness, attainability and optimality can be polynomially reduced to the feasibility of SDP \cite{ramana1997exact}.
-
 Assuming the input data belongs to an effective field $K$ (\emph{e.g.} $K = \QQ$) then a solution can be described and computed as element of a vector space over some algebraic extension of $K$.
 For exact computation, complexity bounds are known based either on general quantifier elimination \cite{ramana1997exact,porkolab1997complexity} and explicit algorithms exist based on a dedicated application of the so-called critical point method, and exploiting the determinantal structure of the constraints \cite{henrion2016exact,NALDI2018206}.
-
 A complexity analysis for the computation of an approximate solution of an SDP can be made based on the ellipsoid algorithm \cite{khachiyan1979polynomial,grotschel1981ellipsoid} or on interior-point methods \cite{de2016turing}; in this approximation framework, SDP is solvable in polynomial time in the input size (\emph{i.e.} matrix size, number of variables, bit size of the coefficients), $\log(\frac{1}{\varepsilon})$ (where $\varepsilon$ is the target precision) and $\log(\frac{R}{r})$, where $r,R$ are radii of balls respectively included in and containing the feasible set, cf.
@@
 
-In this paper we consider the situation where input data are defined over fields $K$ with a prescribed valuation map $\val$ on $K$.
-The main example is the field of $p$-adic numbers with $p$-adic valuation.
-\todo{Give motivations for p-adic precision of LP/SDP.}
-
-POLYHEDRA
-
-SPECTRAHEDRA
-Similar generalizations have been recently proposed in the context of tropical geometry \cite{iriarte2022polyhedral} and tropical methods applied to non-archimedean semidefinite programming \cite{allamigeon2016solving,allamigeon_tropical_2020}.
+In this paper we consider the situation where input data are defined over fields $K$ with a prescribed valuation map $\val$ on $K$. In this context a polyhedron is
+
+The prototype of valued field we target is the field of $p$-adic numbers with $p$-adic valuation.
+\todo{Give motivations for p-adic precision of LP/SDP.} Similar generalizations have been recently proposed in the context of tropical geometry \cite{iriarte2022polyhedral} and tropical methods applied to non-archimedean semidefinite programming \cite{allamigeon2016solving,allamigeon_tropical_2020}.
 
@@
 in which case $\OK = \QQ \llbracket t \rrbracket$.
-We refer to \cite{Serre:1979} for a
+We refer to \cite{Serre:1979,engler2005valued} for a
 general introduction to such fields
-and to Caruso's course on $p$-adic computations \cite{caruso_computations_2017}
+and to \cite{caruso_computations_2017}
 for an introduction to effective computations over $p$-adic numbers.

### 2025-06-05 article/paper_padic_spec.tex
commit by Simone

@@
 
-Throughout the paper, $K$ refers to a complete,
-discrete valued field, $\val : K \twoheadrightarrow \ZZ \cup \{+\infty\}$ to its valuation,
-$\OK$ its ring of integers, $\kappa$ its residue field and $\pi$ a uniformizer.
+Throughout the paper, $(K,\val)$ refers to a complete valued field, namely $K$ is a field
+and $\val : K \twoheadrightarrow \Gamma \cup \{+\infty\}$ is a valuation on $K$, $\Gamma$ an
+ordered abelian group. The valuation is often assumed to be discrete ({\it i.e.} $\Gamma=\ZZ$).
+The ring of integers of $K$ is
+$$
+\OK = \{x \in K : \val(x) \geq 0\},
+$$
+$\kappa = \OK/\mathfrak{m}_K$ its residue field, with
+$\mathfrak{m}_K = \{x \in K : \val(x) > 0\}$, and $\pi$ a uniformizer.
 For $k \in \N$, we write $O(\pi^k)$ for $\pi^k \OK$.
 A typical example of $K$ as above is the field of $p$-adic numbers 
-$\QQ_p$ (equipped with the $p$-adic valuation). For this example, we 
-have $\OK = \ZZ_p$.
-Another example is the field of Laurent series
+$\QQ_p$ equipped with the $p$-adic valuation. For this example, we 
+have $\OK = \ZZ_p$. Another example is the field of Laurent series
 $K=\QQ(\!(t)\!)$ equiped with $t$-adic valuation,

### 2025-06-05 article/paper_padic_spec.tex
commit by Simone

@@
 and $\val : K \twoheadrightarrow \Gamma \cup \{+\infty\}$ is a valuation on $K$, $\Gamma$ an
-ordered abelian group. The valuation is often assumed to be discrete ({\it i.e.} $\Gamma=\ZZ$).
-The ring of integers of $K$ is
+ordered abelian group. The valuation is often assumed to be discrete ({\it i.e.} $\Gamma=\ZZ$)
+with $\pi \in K$ a uniformizer. The ring of integers of $K$ is
 $$
@@
 $\kappa = \OK/\mathfrak{m}_K$ its residue field, with
-$\mathfrak{m}_K = \{x \in K : \val(x) > 0\}$, and $\pi$ a uniformizer.
-For $k \in \N$, we write $O(\pi^k)$ for $\pi^k \OK$.
+$\mathfrak{m}_K = \{x \in K : \val(x) > 0\}$.
+For $k \in \N$, we write $O(\pi^k)$ for $\pi^k \OK$\footnote{\simone{voir si on
+  utilise cette notation}}.
 A typical example of $K$ as above is the field of $p$-adic numbers 
@@
 \begin{definition}[Smith Normal Form]\label{smith_nf}
-  Let $M \in K^{m \times n}$ be of rank $r$. There exist unique integers $a_1 \leq \cdots \leq a_r$, and
+  Assume $(K,\val)$ is a discrete valued field with uniformizer $\pi$.
+  Let $M \in K^{m \times n}$ be of rank $r$. There exist unique integers
+  $a_1 \leq \cdots \leq a_r$, and
   matrices $P \in \GL_n(\OK)$ and $Q \in \GL_m(\OK)$, such that
@@
 
-\subsection{Linear programming}
+\section{Linear programming}
 
@@
 
-\begin{algorithm}
+\begin{algorithm}[!ht]
+    {\footnotesize
     \caption{\textbf{SOLVELPval}($A,b,c,D,e$)}\label{algo_LP}
     \begin{algorithmic}[1]
+    %%%\algsetup{linenosize=\tiny}
       \REQUIRE
@@
       \ENSURE [TYPE, $x$], where:
-      \vspace{-0.25cm}
+      \vspace{-0.1cm}
       \begin{itemize}
@@
         TYPE $=$ INFEAS and $x=[]$ if and only if \eqref{LP} is infeasible
-      \vspace{-0.25cm}
+        \vspace{-0.1cm}
       \item[]
         TYPE $=$ UNBOUND and $x=[]$ if and only if \eqref{LP} is feasible and unbounded
-      \vspace{-0.25cm}
+        \vspace{-0.1cm}
       \item[]
@@
     \end{algorithmic}
+  }
 \end{algorithm}

### 2025-06-10 article/paper_padic_spec.tex
commit by Simone

@@
 
-\subsection{Notation}
-
 Throughout the paper, $(K,\val)$ refers to a complete valued field, namely $K$ is a field
@@
 
-\subsection{Real spectrahedra}
-
 Let $\sym_d(\R) \subset \R^{d\times d}$ be the vector space of $d \times d$ real symmetric
-matrices. A matrix $M \in \sym_d(\R)$
-is called \emph{positive semidefinite} ($M \succeq 0$) whenever the quadratic
-form $x \mapsto x^TMx$ is nonnegative for all $x\in \R^n$. By the Spectral Theorem, $M \succeq 0$
-if and only if the eigenvalues of $M$ are nonnegative, and this is equivalent to all the principal minors
-of $M$ being nonnegative. The set of positive semidefinite matrices, denoted $\sym_d^+(\R) \subset \sym_d(\R)$,
-is a closed convex cone with non-empty interior in $\sym_d(\R)$.
+matrices.
+A matrix $M \in \sym_d(\R)$ is \emph{positive semidefinite} ($M \succeq 0$) whenever the quadratic form $x \mapsto x^TMx$ is nonnegative for all $x\in \R^n$.
+By the Spectral Theorem, $M \succeq 0$ if and only if the eigenvalues of $M$ are nonnegative, and this is equivalent to all the principal minors of $M$ being nonnegative.
+The set $\sym_d^+(\R) \subset \sym_d(\R)$ of positive semidefinite matrices is a closed convex cone with non-empty interior in $\sym_d(\R)$.
 

### 2025-06-18 article/paper_padic_spec.tex
Tentative de preuve du théorème sur la projection des polyèdres.

--- 2025-06-05 article/paper_padic_spec.tex
@@
-\documentclass[a4paper,oneside,10pt]{article}
+\documentclass[a4paper,oneside,11pt]{article}
 
@@
 \usepackage{color,xcolor}
-%\usepackage{ulem}
+\usepackage{ulem}
 \usepackage{bm}
+
+\usepackage{tikz}
+\usetikzlibrary{arrows.meta, positioning}
+
+\usepackage{hyperref}
 
@@
 \newcommand{\tristan}[1]{{\color{red} #1}} % tristan's comments
-\newcommand{\todo}[1]{{\color{blue}\bf \text{TODO: } #1}} % TODOs
 
@@
 
-\title{\Large \bf On semidefinite-representable sets over valued fields}
+%\title{\bf Title}
+%\title{\bf On polyhedra and spectrahedra over valuation fields}
+\title{\bf On semidefinite-representable sets over valuation fields}
 
@@
   semidefinite-representable sets. This paper investigates versions of these sets and of
-  the related optimization problems with data over a valued field $K$.
-  For $K$-polyhedra and linear programming over $K$ we give an algorithm based on computation
-  of Smith normal forms.
+  the related optimization problems with data over a field $K$ with valuation.
   We prove that basic properties of semidefinite-representable sets generalize to this setting.
-  In particular, we showcase examples of non-polyhedral $K$-spectrahedra and of sets that are
-  semidefinite representable over $K$ but are not $K$-spectrahedra.
+  We showcase examples of non-polyhedral $K$-spectrahedra and of sets that are semidefinite
+  representable over $K$ but are not $K$-spectrahedra.
 \end{abstract}
@@
 
-The study of polyhedra and of linear programming (LP) is at the heart of convex geometry and optimization, inasmuch as several optimization problems can be cast as, or relaxed to LP.
-An important generalization of LP is semidefinite programming (SDP), namely the problem of minimizing a linear function over the set of positive semidefinite affine combinations of some real symmetric matrices.
-The latter problem has interested the community of real algebraic geometry and polynomial optimization, mostly because of the relaxation method known as moment-SOS (or Lasserre) hierarchy \cite{henrion2020moment}.
-
-The main motivation for studying the effective aspects of SDP is the fact that, despite several properties of LP extend to SDP, the complexity status of SDP is, contrary to the LP case, widely open.
-Ramana's construction \cite{ramana1997exact} implies a series of general results: in the Blum-Shub-Smale real numbers machines model \cite{blum1989theory}, the feasibility of SDP is in $\text{NP} \cap \text{co-NP}$, whereas it is not known to be in NP in the Turing model; checking boundedness, attainability and optimality can be polynomially reduced to the feasibility of SDP \cite{ramana1997exact}.
-Assuming the input data belongs to an effective field $K$ (\emph{e.g.} $K = \QQ$) then a solution can be described and computed as element of a vector space over some algebraic extension of $K$.
-For exact computation, complexity bounds are known based either on general quantifier elimination \cite{ramana1997exact,porkolab1997complexity} and explicit algorithms exist based on a dedicated application of the so-called critical point method, and exploiting the determinantal structure of the constraints \cite{henrion2016exact,NALDI2018206}.
-A complexity analysis for the computation of an approximate solution of an SDP can be made based on the ellipsoid algorithm \cite{khachiyan1979polynomial,grotschel1981ellipsoid} or on interior-point methods \cite{de2016turing}; in this approximation framework, SDP is solvable in polynomial time in the input size (\emph{i.e.} matrix size, number of variables, bit size of the coefficients), $\log(\frac{1}{\varepsilon})$ (where $\varepsilon$ is the target precision) and $\log(\frac{R}{r})$, where $r,R$ are radii of balls respectively included in and containing the feasible set, cf.
-\cite{grotschel1981ellipsoid} or \cite[Thm.1.1]{de2016turing} (see also \cite[Sec.1.9]{deKlerk}).
-
-In this paper we consider the situation where input data are defined over fields $K$ with a prescribed valuation map $\val$ on $K$. In this context a polyhedron is
-
-The prototype of valued field we target is the field of $p$-adic numbers with $p$-adic valuation.
-\todo{Give motivations for p-adic precision of LP/SDP.} Similar generalizations have been recently proposed in the context of tropical geometry \cite{iriarte2022polyhedral} and tropical methods applied to non-archimedean semidefinite programming \cite{allamigeon2016solving,allamigeon_tropical_2020}.
+The study of polyhedra and of linear programming (LP) is at the heart of convex geometry and optimization,
+inasmuch as several optimization problems can be cast as, or reduced to LP. An important generalization of LP
+is semidefinite programming (SDP), namely the problem of minimizing an affine polynomial over the set of
+positive semidefinite affine combinations of a given collection of real symmetric matrices. The latter problem 
+has interested the community of polynomial optimization because of the relaxation method known as moment-SOS
+(or Lasserre) hierarchy \cite{henrion2020moment}.
+
+Contrary to the LP case, the complexity status of SDP is widely open.
+In a fixed-precision model of computation, SDP is solvable in polynomial time in the input size (matrix size,
+number of variables, bit size of the coefficients), in $\log(\frac{1}{\varepsilon})$ (where $\varepsilon$ is the
+precision) and $\log(\frac{1}{R})$, where $R$ is an {\it a priori} upper bound on the norm of a solution,
+cf. \cite[Sec.1.9]{deKlerk}. In exact arithmetic, the complexity status of SDP is essentially open but complexity
+bounds are known based either on general quantifier elimination \cite{ramana1997exact,porkolab1997complexity}
+or by exploiting the determinantal structure of the constraints \cite{henrion2016exact}.
+
+In this paper we 
+Similar generalizations have been recently proposed in the context of tropical geometry \cite{iriarte2022polyhedral}.
 
@@
 
-Throughout the paper, $(K,\val)$ refers to a complete valued field, namely $K$ is a field
-and $\val : K \twoheadrightarrow \Gamma \cup \{+\infty\}$ is a valuation on $K$, $\Gamma$ an
-ordered abelian group. The valuation is often assumed to be discrete ({\it i.e.} $\Gamma=\ZZ$).
-The ring of integers of $K$ is
-$$
-\OK = \{x \in K : \val(x) \geq 0\},
-$$
-$\kappa = \OK/\mathfrak{m}_K$ its residue field, with
-$\mathfrak{m}_K = \{x \in K : \val(x) > 0\}$, and $\pi$ a uniformizer.
+Throughout the paper, $K$ refers to a complete,
+discrete valuation field, $\val : K \twoheadrightarrow \ZZ \cup \{+\infty\}$ to its valuation,
+$\OK$ its ring of integers, $\kappa$ its residue field and $\pi$ a uniformizer.
 For $k \in \N$, we write $O(\pi^k)$ for $\pi^k \OK$.
 A typical example of $K$ as above is the field of $p$-adic numbers 
-$\QQ_p$ equipped with the $p$-adic valuation. For this example, we 
-have $\OK = \ZZ_p$. Another example is the field of Laurent series
+$\QQ_p$ (equipped with the $p$-adic valuation). For this example, we 
+have $\OK = \ZZ_p$.
+Another example is the field of Laurent series
 $K=\QQ(\!(t)\!)$ equiped with $t$-adic valuation,
 in which case $\OK = \QQ \llbracket t \rrbracket$.
-We refer to \cite{Serre:1979,engler2005valued} for a
+We refer to \cite{Serre:1979} for a
 general introduction to such fields
-and to \cite{caruso_computations_2017}
+and to Caruso's course on $p$-adic computations \cite{caruso_computations_2017}
 for an introduction to effective computations over $p$-adic numbers.
@@
 
-In this section, we define polyhedra over a complete discrete valued field $K$ with valuation $\val$ and a uniformizer $\pi$, and we prove that the class of polyhedra is closed under linear transformations, as in the real case.
+In this section, we define polyhedra over a complete discrete valuation field $K$ with valuation $\val$ and a uniformizer $\pi$, and we prove that the class of polyhedra is closed under linear transformations, as in the real case.
 We end by presenting an algorithm for solving linear optimization problems over $K$.
@@
 
-\subsection{Projections of polyhedra}
+\subsection{Projections and direct image of polyhedra}
 
@@
 
-In this section we show that the image of a polyhedron by a linear mapping is a polyhedron,
-and discuss some consequences.
-We first prove the result in the cases of authomorphisms of $\OK^n$ and diagonal endomorphisms of $K^n$.
-Then we use these particular cases to prove the result for projections of the form
-$(x_1,\dots,x_n) \mapsto (x_1,\dots, x_{n-1})$ and finally for the general case.
-
-\begin{remark}
-  Let $f : K^n \to K^m$ be a linear map and let
-  $P = \{x \in K^n : \val(l_i(x)) \geq 0, m_i(x) = 0, 1 \leq i \leq d, 1 \leq j \leq e\}$.
-  Then $P = P_I \cap P_E$ where $P_I := \{x \in K^n : \val(l_i(x)) \geq 0, 1 \leq i \leq d\}$
-  and $P_E := \{x \in K^n : m_j(x) = 0, 1 \leq j \leq e\}$.
-
-  Thus we have\footnote{\simone{Ça n'est pas vrai en général, il faut que $f$ soit injective.
-    Il faut peut être d'abord factoriser $f = g \circ h$ avec $h : K^n \to im(f)$ et
-    $g : im(f) \subset K^m$.}}
-  $f(P) = f(P_I) \cap f(P_E)$. However $P_E$ is either empty or an affine subspace of
-  $K^n$ and therefore $f(P_E)$ is either empty or an affine subspace of $K^m$, so it is a polyhedron.
-  Hence, as the class of polyhedra is closed under intersection, in order to prove that
-  $f(P)$ is a polyhedron, it is sufficient to prove that this holds for $f(P_I)$.
-\end{remark}
-
-Therefore below we consider polyhedra of the form as in \Cref{def_polyhedra} with $e=0$.
-
-\begin{proposition}\simone{l'enoncé est incomplet}
-  Let $P \subset K^n$ be a polyhedron and let $f : K^n \to K^n$ be a linear mapping.
-  If $f \in \GL_n(\OK)$ or if there exists $\lambda_1, \dots, \lambda_n \in K$ such that
-  $(x_1,\dots,x_{n-1}, x_n) \mapsto (x_1,\dots, x_{n-1})$.
-\end{proposition}
-
-\begin{proof}
-We assume that $\PP \neq \emptyset$
-As discussed above we can assume that
-$\PP = \left\lbrace x \in K^n : \val (l_i (x) ) \geq 0,\textrm{ for } i \in I \right\rbrace$ for some
-finite set $I \subset \N$ and $l_i \in K[x]_1$, for $i \in I$ .
-
-First, if $f \in \GL_n(\OK)$ then, $x \in f(P)$ if and only if for all $i \in I$, 
-$\val(l_i (f^{-1}(x))) \geq 0$.
-The $l_i \circ f^{-1}$ are clearly in $K[x]_1$
-and $f(P)$ is a polyhedron.
-
-Similarly, if $f:K^n \rightarrow K^n$ is of the form
-$f(x_1,\dots,x_n)=(\lambda_1 x_1,\dots,\lambda_n x_n)$
-for some $\lambda_1,\ldots, \lambda_n \in K$,
-then of course $f(P)$
-can be defined by $\val (\widetilde{l_i}(x)) \geq 0$, $i \in I$
-with the $\widetilde{l_i}$'s obtained from the $l_i$'s by an
-obvious change of variables.
-\end{proof}
-
-The two above results\footnote{\simone{il y en an un}}
-allows us to demonstrate the following proposition, which we will use to prove the general case.
-
-\begin{proposition}
-      Let $\PP \subset K^n$ be a polyhedron and $p : K^n \to K^{n-1}$ be the projection $p : (x_1,\dots,x_{n-1},x_n) \mapsto (x_1, \dots, x_{n-1})$.
-       Then $p(\PP)$ is a spectrahedron.
-\end{proposition}
-
-\begin{proof}
-
+In this section, we prove that the class of polyhedra is stable
+by applying affine maps:
+
+\begin{theorem}[DI] 
+Let $f : K^n \to K^m$ be an affine map and $\PP$ a polyhedron of $K^n.$
+Then $f(\PP)$ is a polyhedron. \label{theo:DI}
+\end{theorem}
+
+We prove the result by reducing to particular cases.
+The strategy to deduce the main theorem DI 
+is the following:
+\begin{figure}[htbp]
+\centering
+\begin{tikzpicture}[
+  node distance=1cm and 1cm,
+  box/.style={draw, rounded corners, minimum width=2.2cm, minimum height=1cm, align=center},
+  thickarrow/.style={->, >=Stealth, line width=1.2pt},
+]
+
+% Nodes
+\node[box] (DIdiag) {DI${}_{diag}$};
+\node[box, right=of DIdiag] (DIproj) {DI${}_{proj}$};
+\node[box, right=of DIproj] (DIl) {DI${}_{l}$};
+\node[box, right=of DIl] (DIi) {DI${}_{i}$};
+\node[box, right=of DIi] (DI) {DI};
+
+\node[box, above=of DIproj] (DIimm) {DI${}_{imm}$};
+\node[box, below=of DIproj] (DIaut) {DI${}_{aut}$};
+
+% Arrows
+\draw[thickarrow] (DIdiag) -- (DIproj);
+\draw[thickarrow] (DIproj) -- (DIl);
+\draw[thickarrow] (DIl) -- (DIi);
+\draw[thickarrow] (DIi) -- (DI);
+
+\draw[thickarrow] (DIimm) -- (DIl);
+\draw[thickarrow] (DIaut) -- (DIl);
+
+\end{tikzpicture}
+\caption{Strategy of proof of Theorem \ref{theo:DI}.}
+\label{fig:di-properties}
+\end{figure}
+
+We begin by the cases of linear maps in $GL_n(O_K)$.
+
+\begin{lemma}[DI${}_{aut}$]
+Let $f \in GL_n(O_K)$ and $\PP$ a polyhedron of $K^n$.
+Then $f(\PP)$ is a polyhedron. \label{lem:DIaut}
+If in addition, $\PP$ is defined only by inequalities,
+then so is $f(\PP)$.
+\end{lemma}
+\begin{proof}
+If $\PP$ is defined (in matrix form) by \[\left\lbrace X \in K^n,  AX+B \geq 0, CX+D=0 \right\rbrace\] and $U$ is the matrix of $f$ in the canonical basis of $K^n$, 
+let $\Qc$ be defined by \[\left\lbrace Y \in K^n,  AU^{-1} Y+B \geq 0, CU^{-1} Y+D=0 \right\rbrace.\]
+Then it is clear that $\Qc$ is a polyhedron and $f(\PP)=\Qc.$
+It is also clear that if $\PP$ is defined only by inequalities,
+then so is $f(\PP)$.
+\end{proof}
+
+If $f$ is diagonal, we can also conclude.
+
+\begin{lemma}[DI${}_{diag}$]
+Let $f : K^n \to K^n$ be a linear map and $\PP$ a polyhedron of $K^n$ defined only by inequalities. We assume that the matrix of $f$ in the canonical basis of $K^n$ is diagonal.
+Then $f(\PP)$ is a polyhedron. \label{lem:DIdiag}
+\end{lemma}
+\begin{proof}
+As in the proof of Lemma \ref{lem:DIaut} DI${}_{aut}$, an obvious change
+of variable is enough to conclude.
+\end{proof}
+
+We now treat the case where $f$ is a projection erasing the last coordinate.
+
+\begin{lemma}[DI${}_{proj}$]
+Let $f : K^n \to K^n, \: (x_1,\dots,x_{n-1},x_n) \mapsto (x_1,\dots,x_{n-1})$ and $\PP$ a polyhedron of $K^n$ defined only by inequalities. 
+Then $f(\PP)$ is a polyhedron defined only by inequalities. \label{lem:DIproj}
+\end{lemma}
+\begin{proof}
 We assume that $\PP \neq \emptyset$.
-As discussed above we can assume that
-  $\PP = \left\lbrace x \in K^n : \val (l_i (x) ) \geq 0,\textrm{ for } i \in I \right\rbrace$ for some
-finite set $I \subset \N$ and $l_i \in K[x]_1$, for $i \in I$ .
-
 Let us write the conditions defining $\PP$
 in matrix form:
-$\val(A X+B) \geq 0$ and 
+$\val(A X+B) \geq 0$ 
 with $A \in M_{q,n}(K)$, $B \in K^q$
@@
 modify whether the valuation inequalities are satisfied.
-Moreover, thanks to our previous on the case when $f$ is an automorphism,
+Moreover, thanks to Lemma \ref{lem:DIaut} DI${}_{aut}$,
 $\PP$ can be written
@@
 and we are reduced to proving that
-$f(\PP_2)$ is polyhedron for $p$ still the canonical projection
+$f(\PP_2)$ is polyhedron for $p$ still the projection
 $K^n \rightarrow K^{n-1}$ and $\PP_2$
-defined by the linear matrix inequality (for some $B_2 \in K^q$):
+defined by the following linear matrix inequality (for some $B_2 \in K^q$):
 \[  \begin{bmatrix}
@@
 if and only if $x_n = -a_s^{-1} b_s + O(\pi^{- \val(a_s)}).$
-This exactly corresponds to $x_n \in B(-a_s^{-1} b_s, 2^{\val(a_s)}).$
+This exactly corresponds to $x_n \in B(-a_s^{-1} b_s,\val(a_s)).$
 Since the conditions have to be compatible (we have assumed
@@
 
-Thanks to the above discussion on diagonal mapping,
+Thanks to Lemma \ref{lem:DIdiag} DI${}_{diag}$,
 we can further assume that the $\delta_i$'s and $a_n$ are all $1$'s
@@
 
-Let us first assume that $\val(a_1) \geq 0$
+Let us first assume that $\val(a_1) \geq 0$.
 
@@
  for all $i \in \llbracket 1,n-1 \rrbracket,$
-$\val(x_i-a_ib_n+b_i) \geq 0.$
+$\val(x_i-a_ib_n+b_i) \geq 0$.
 
@@
 
-Therefore,$p(\PP)$ is a polyhedron.
-
-\end{proof}
-
-We can finally prove that the image of polyhedron under a linear mapping is a polyhedron.
-\begin{proposition}
-Let $\PP \subset K^n$ be a polyhedron and $f: K^n \rightarrow K^m$
-be a linear mapping. Then $f(\PP)$ is a polyhedron.
+Therefore, $p(\PP)$ is a polyhedron (and inequalities are enough to define $p(\PP_2)$ as a polyhedron).
+\end{proof}
+
+\begin{lemma}[DI${}_{imm}$]
+Let $f : K^l \to K^n$ be the immersion $(x_1,\dots, x_l) \mapsto (x_1,\dots, x_l,0,\dots, 0)$ and $\PP$ a polyhedron of $K^l$
+Then $f(\PP)$ is a polyhedron. \label{lem:DIimm}
+\end{lemma}
+\begin{proof}
+Adding the equalities $x_{l+1}=0, \dots, x_n=0$ to the equations and inequations in
+$x_1,\dots, x_l$ defining $\PP$, the result is clear.
+\end{proof}
+
+We can now generalize to linear mappings and
+polyhedron defined only by inequalities.
+
+\begin{proposition}[DI${}_l$]
+Let $f : K^n \to K^m$ be a linear map and $\PP$ a polyhedron of $K^n$ defined only by inequalities.
+Then $f(\PP)$ is a polyhedron. \label{prop:DIl}
 \end{proposition}
-
-\begin{proof}
-
-We assume that $\PP \neq \emptyset$, and we identify $f$ with its matrix in $\allmat_{n,n}(K)$.
-As seen above, we can assume that $\PP$ is of the form $\left\lbrace x \in K^n : \val (l_i (x) ) \geq 0, \textrm{ for } i \in I\right\rbrace$ for some
+\begin{proof}
+We assume that $\PP \neq \emptyset$, and we identify $f$ with its matrix in $\allmat_{n,m}(K)$.
+We assume that $\PP$ is defined as $\left\lbrace x \in K^n : \val (l_i (x) ) \geq 0, \textrm{ for } i \in I\right\rbrace$ for some
 finite sets $I \subset \N$ and $l_i \in K[x]_1$, for $i \in I$ .
@@
 with $P \in \GL_n(\OK),$ $Q \in \GL_m(\OK)$
-and $\Delta = \mathrm{SNF}(f)\in \allmat_{m,n}(K)$ of the form $\diag(\lambda_1, \ldots, \lambda_r, {\bf 0}_{\min(m,n)-r})$
+and $\Delta = \mathrm{SNF}(f)\in \allmat_{n,m}(K)$ of the form $\diag(\lambda_1, \ldots, \lambda_r, {\bf 0}_{\min(m,n)-r})$
   where ${\bf 0}_{\min(m,n)-r}$ is a null square matrix of size $\min(m,n)-r$ for $\lambda_1,\dots,\lambda_r$ non-zero and $r \in \N.$
 
-  %Now, we turn our attention to the $\Delta$ part of $f$.
-We have previously proven that if $f \in \GL_n(\OK)$ then $f(\PP)$ is a polyhedron.
-It is also clear that
-if $f$ is the immersion 
-$K^l \rightarrow K^n$
-$(x_1,\dots,x_l)\mapsto (x_1,\dots,x_l,0,\dots,0)$ 
-and $\PP$ is a polyhedron in $K^n$,
-then $f(\PP)$ is a polyhedron.
-
-We now prove that for
-$\Delta$ a Smith Normal Form
-and $\PP$ a polyhedron,
-$\Delta(\PP)$ is a polyhedron.
-Then $\Delta$ is the composition
+By Lemma \ref{lem:DIaut} DI${}_{aut}$,
+$P(\PP)$ is a polyhedron defined only by inequalities.
+
+Let $\Qc= P(\PP)$
+We now prove that $\Delta (\Qc)$ is a polyhedron.
+One can write that $\Delta$ is the composition
 of the immersion 
-$K^l \rightarrow K^n$
-$(x_1,\dots,x_l)\mapsto (x_1,\dots,x_l,0,\dots,0),$ 
+$K^r \rightarrow K^n$
+$(x_1,\dots,x_r)\mapsto (x_1,\dots,x_r,0,\dots,0),$ 
  the diagonal invertible mapping
 $K^l \rightarrow K^l$,
-$(x_1,\dots,x_l)\mapsto (\delta_1,\dots,\delta_l x_l)$,
+$(x_1,\dots,x_r)\mapsto (\delta_1,\dots,\delta_r x_r)$,
 and the projections
-$(x_1,\dots,x_{l+1})\mapsto (x_1,\dots,x_{l}),$
- $(x_1,\dots,x_{l+2})\mapsto (x_1,\dots,x_{l+1}),$
+$(x_1,\dots,x_{r+1})\mapsto (x_1,\dots,x_{r}),$
+ $(x_1,\dots,x_{r+2})\mapsto (x_1,\dots,x_{r+1}),$
  $\dots,$
  $(x_1,\dots,x_{n})\mapsto (x_1,\dots,x_{n-1}).$
- Thus $\Delta(\PP)$ is a polyhedron thanks to the previous 
- results on image of polyhedron.
-
-Finally, if $f: K^n \rightarrow K^m$
-is a linear mapping and
-$f=Q^{-1} \Delta P$ is its Smith Normal Form
-with $P \in \GL_n(\OK),$ $Q \in \GL_m(\OK)$
-and $\Delta \in \allmat_{n,m}(K)$,
-then
-$P(\PP)$ is a polyhedron,
-$\Delta (P(\PP))$ also,
-and finally $f(\PP)=Q^{-1} (\Delta (P(\PP)))$
-is a polyhedron.
+ Thus, thanks to Lemmas \ref{lem:DIimm} DI${}_{imm}$, \ref{lem:DIproj} DI${}_{proj}$ and \ref{lem:DIaut} DI${}_{aut}$, $\Delta (\Qc)$ is a polyhedron.
+ One can note that it is only when applying the immersion as the last mapping in the composition chain that equalities are needed to define the last polyhedron.
+
+Finally, thanks to Lemma \ref{lem:DIaut} DI${}_{aut}$,
+$Q^{-1} \left( \Delta (\Qc) \right)$ is a polyhedron.
 This concludes the proof.
 \end{proof}
+
+We can generalize from linear mappings to affine mappings.
+\begin{proposition}[DI${}_i$]
+Let $f : K^n \to K^m$ be an affine map and $\PP$ a polyhedron of $K^n$ defined only by inequalities.
+Then $f(\PP)$ is a polyhedron. \label{prop:DIi}
+\end{proposition}
+\begin{proof}
+Let $P \in K^m$. One can see by immediate change of variables that $\Qc$ is a polyhedron of $K^m$ if and only if
+$\Qc+P$ is a polyhedron of $K^m$.
+Consequently, translating by $-f(O)$ in the codomain, one can reduce
+to the case of Proposition \ref{prop:DIl}   DI${}_l$.
+\end{proof}
+
+We can now conclude with the proof of the main result
+of this section.
+
+\begin{proof}[Proof of Theorem \ref{theo:DI} DI]
+Here, $f : K^n \to K^m$ is an affine map and $\PP$ a polyhedron of $K^n.$
+Let us write $\PP = \PP_I \cap \PP_E$
+with $\PP_I := \left\lbrace X \in K^n,  AX+B \geq 0 \right\rbrace$
+and $\PP_E := \left\lbrace X \in K^n,  CX+D=0 \right\rbrace = P + \overrightarrow{\PP_E}.$
+
+Then $f(\PP) = f_{\PP_E}(\PP_I).$
+
+By a translation of $-P$ in $K^n$, we can assume that
+$\PP_E$ is a linear vector space: we are reduced to proving that, if $\tilde{f}: \PP_E \to K^m$ is an affine map and $\PP_I$ is a polyhedron of the vector space $\PP_E$ defined only by inequalities, then  $\tilde{f}(\PP_I)$ is a polyhedron.
+This is the case thanks to Proposition \ref{prop:DIi} DI$_i$
+and the theorem is proven.
+\end{proof}
+
+%
+%In this section we show that the image of a polyhedron by a linear mapping is a polyhedron,
+%and discuss some consequences.
+%We first prove the result in the cases of authomorphisms of $\OK^n$ and diagonal endomorphisms of $K^n$.
+%Then we use these particular cases to prove the result for projections of the form
+%$(x_1,\dots,x_n) \mapsto (x_1,\dots, x_{n-1})$ and finally for the general case.
+%
+%\begin{remark}
+%  Let $f : K^n \to K^m$ be a linear map and let
+%  $P = \{x \in K^n : \val(l_i(x)) \geq 0, m_i(x) = 0, 1 \leq i \leq d, 1 \leq j \leq e\}$.
+%  Then $P = P_I \cap P_E$ where $P_I := \{x \in K^n : \val(l_i(x)) \geq 0, 1 \leq i \leq d\}$
+%  and $P_E := \{x \in K^n : m_j(x) = 0, 1 \leq j \leq e\}$.
+%
+%  Thus we have\footnote{\simone{Ça n'est pas vrai en général, il faut que $f$ soit injective.
+%    Il faut peut être d'abord factoriser $f = g \circ h$ avec $h : K^n \to im(f)$ et
+%    $g : im(f) \subset K^m$.}}
+%  $f(P) = f(P_I) \cap f(P_E)$. However $P_E$ is either empty or an affine subspace of
+%  $K^n$ and therefore $f(P_E)$ is either empty or an affine subspace of $K^m$, so it is a polyhedron.
+%  Hence, as the class of polyhedra is closed under intersection, in order to prove that
+%  $f(P)$ is a polyhedron, it is sufficient to prove that this holds for $f(P_I)$.
+%\end{remark}
+%
+%Therefore below we consider polyhedra of the form as in \Cref{def_polyhedra} with $e=0$.
+%
+%\begin{proposition}\simone{l'enoncé est incomplet}
+%  Let $P \subset K^n$ be a polyhedron and let $f : K^n \to K^n$ be a linear mapping.
+%  If $f \in \GL_n(\OK)$ or if there exists $\lambda_1, \dots, \lambda_n \in K$ such that
+%  $(x_1,\dots,x_{n-1}, x_n) \mapsto (x_1,\dots, x_{n-1})$.
+%\end{proposition}
+%
+%\begin{proof}
+%We assume that $\PP \neq \emptyset$
+%As discussed above we can assume that
+%$\PP = \left\lbrace x \in K^n : \val (l_i (x) ) \geq 0,\textrm{ for } i \in I \right\rbrace$ for some
+%finite set $I \subset \N$ and $l_i \in K[x]_1$, for $i \in I$ .
+%
+%First, if $f \in \GL_n(\OK)$ then, $x \in f(P)$ if and only if for all $i \in I$, 
+%$\val(l_i (f^{-1}(x))) \geq 0$.
+%The $l_i \circ f^{-1}$ are clearly in $K[x]_1$
+%and $f(P)$ is a polyhedron.
+%
+%Similarly, if $f:K^n \rightarrow K^n$ is of the form
+%$f(x_1,\dots,x_n)=(\lambda_1 x_1,\dots,\lambda_n x_n)$
+%for some $\lambda_1,\ldots, \lambda_n \in K$,
+%then of course $f(P)$
+%can be defined by $\val (\widetilde{l_i}(x)) \geq 0$, $i \in I$
+%with the $\widetilde{l_i}$'s obtained from the $l_i$'s by an
+%obvious change of variables.
+%\end{proof}
+%
+%The two above results\footnote{\simone{il y en an un}}
+%allows us to demonstrate the following proposition, which we will use to prove the general case. 
+%
+%\begin{proposition}
+%      Let $\PP \subset K^n$ be a polyhedron and $p : K^n \to K^{n-1}$ be the projection $p : (x_1,\dots,x_{n-1},x_n) \mapsto (x_1, \dots, x_{n-1})$.
+%       Then $p(\PP)$ is a spectrahedron.
+%\end{proposition}
+%
+%
+%\begin{proof}
+%      
+%We assume that $\PP \neq \emptyset$.
+%As discussed above we can assume that
+%  $\PP = \left\lbrace x \in K^n : \val (l_i (x) ) \geq 0,\textrm{ for } i \in I \right\rbrace$ for some
+%finite set $I \subset \N$ and $l_i \in K[x]_1$, for $i \in I$ .
+%
+%Let us write the conditions defining $\PP$
+%in matrix form:
+%$\val(A X+B) \geq 0$ and 
+%with $A \in M_{q,n}(K)$, $B \in K^q$
+%and $X=(x_1,\dots,x_n)^\intercal$. 
+%
+%
+%We can compute a Smith Normal Form
+%of the $q \times (n-1)$ matrix defined by the 
+%$n-1$ first columns of $A$
+%to obtain a decomposition of the form:
+%\[ Q_A A P_A^{-1} = \begin{bmatrix}
+%\delta_1	& 		& 			&   &		 &  &a_1	\\
+%			& \ddots& 			& 0	&		 &	&		\\
+%			&		& \delta_l  &   & 		 &	&		\\
+%			&		&			&0  & 		 &	& 		\\
+%			&		&			&   & \ddots &	&		\\
+%			&		&			&	&		 & 0&a_{n-1} \\
+%			&		&			&	&		 &	&a_n 	\\
+%			&		&			&	&		 &	&    	\\
+%			&		&			&	&		 &	&a_q 	\\			
+%\end{bmatrix},\]
+%with $Q_A \in \GL_q(\OK)$ and $P_A \in \GL_n(\OK)$ such that $P_A(e_n)=e_n.$
+%
+%Multiplying on the left by $Q_A^{\pm 1}$ does not
+%modify whether the valuation inequalities are satisfied.
+%Moreover, thanks to our previous on the case when $f$ is an automorphism,
+%$\PP$ can be written
+%$\PP=P_A^{-1}(\PP_2)$ for some polyhedron $\PP_2 \subset K^n$
+%and we are reduced to proving that
+%$f(\PP_2)$ is polyhedron for $p$ still the canonical projection
+%$K^n \rightarrow K^{n-1}$ and $\PP_2$
+%defined by the linear matrix inequality (for some $B_2 \in K^q$):
+%\[  \begin{bmatrix}
+%\delta_1	& 		& 			&   &		 &  &a_1	\\
+%			& \ddots& 			& 0	&		 &	&		\\
+%			&		& \delta_l  &   & 		 &	& \vdots\\
+%			&		&			&0  & 		 &	& 		\\
+%			&		&			&   & \ddots &	&		\\
+%			&		&			&	&		 & 0&a_{n-1} \\
+%			&		&			&	&		 &	&a_n 	\\
+%			&		&			&	&		 &	& \vdots   	\\
+%			&		&			&	&		 &	&a_q 	\\			
+%\end{bmatrix} \begin{bmatrix} x_1 \\ \\ \\ \\ \\ \vdots \\ \\ \\ \\ x_n \\ \end{bmatrix} + B_2 \geq 0.\]
+%
+%
+%
+%We remark that 
+%$a_s x_n + b_s \geq 0$
+%if and only if $x_n = -a_s^{-1} b_s + O(\pi^{- \val(a_s)}).$
+%This exactly corresponds to $x_n \in B(-a_s^{-1} b_s, 2^{\val(a_s)}).$
+%Since the conditions have to be compatible (we have assumed
+%$\PP$ not empty), and thanks to ultrametricity,  
+%the intersection of these conditions for 
+%$s \in \llbracket l+1,q \rrbracket$
+%is then given by the smallest of these balls.
+%Let us assume it is the one defined for $l=n.$
+%The only condition on $x_n$
+%is then $\val(a_nx_n +b_n) \geq 0.$
+%
+%Thanks to the above discussion on diagonal mapping,
+%we can further assume that the $\delta_i$'s and $a_n$ are all $1$'s
+%and are reduce to $\PP_2$ defined by the linear matrix inequality :
+%\[  \begin{bmatrix}
+%1	& 		& 			&   &		 &  &a_1	\\
+%			& \ddots& 			& 0	&		 &	&		\\
+%			&		& 1  &   & 		 &	& \\
+%			&		&			&0  & 		 &	& 	\vdots	\\
+%			&		&			&   & \ddots &	&		\\
+%			&		&			&	&		 & 0&a_{n-1} \\
+%			&		&			&	&		 &	&1 	\\
+%		
+%\end{bmatrix} \begin{bmatrix} x_1 \\ \\  \\ \\ \vdots \\  \\ \\ x_n \\ \end{bmatrix} + \begin{bmatrix} b_1 \\ \\ \\  \\ \vdots  \\ \\ \\ b_n \\ \end{bmatrix}  \geq 0.\]
+%Finally, we can also assume that, up to a permutation of the variables, $\val(a_1)= \min_{i=1}^{n-1} \val(a_i).$
+%We distinguish two cases: $\val(a_1) \geq 0$ and $\val(a_1)<0.$
+%
+%Let us first assume that $\val(a_1) \geq 0$
+%
+%Let $x \in \PP_2$.
+%Then $x_n=-b_n+O(1)$
+%and $x_1+a_1 x_n+b_1=O(1).$
+%Consequently, $x_1-a_1 b_n +b_1=O(1)+O(\pi^{\val(a_1)})=O(1).$
+%Similarly, for all $i \in \llbracket 2,n-1 \rrbracket,$
+%$x_i-a_ib_n+b_i=O(1)+O(\pi^{\val(a_i)})=O(1).$
+%
+%We define the polyhedron $\Qc \subset K^{n-1}$ by the following inequalities:
+% for all $i \in \llbracket 1,n-1 \rrbracket,$
+%$\val(x_i-a_ib_n+b_i) \geq 0.$
+%
+%Then the previous computations prove that $p(\PP_2)\subset \Qc.$
+%Conversely, let $(x_1,\dots,x_{n-1}) \in \Qc.$
+%Then let $x_n := -b_n.$
+%
+%We check that for $i \in \llbracket 1,n-1 \rrbracket,$
+%$x_i+a_ix_n+b_i=x_i-a_ib_n+b_i=O(1),$
+%and $x_n+b_n=O(1)$. Hence $(x_1,\dots,x_n) \in \PP_2$
+%which means that $(x_1,\dots,x_{n-1}) \in p(\PP_2).$
+%Thus $p(\PP_2)= \Qc$ and $p(\PP_2)$ is a polyhedron.
+%
+%We now deal with the second case, with $\val(a_1)<0.$
+%Let $x \in \PP_2$.
+%Then $x_n=-b_n+O(1)$
+%and $x_1+a_1 x_n+b_1=O(1).$
+%Consequently, $x_1-a_1 b_n +b_1=O(1)+O(\pi^{\val(a_1)})=O(\pi^{\val(a_1)}).$
+%Thus $a_1^{-1}x_1- b_n +a_1^{-1}b_1=O(1)$.
+%%and $x_n=-a_1^{-1}(x_1+b_1)+O(1).$
+%In addition, $x_n=-a_1^{-1}(x_1+b_1)+O(\pi^{-\val(a_1)}).$
+%We plug this equality in 
+%$x_i+a_i x_n+b_i=O(1)$ to get
+%$x_i-a_1^{-1}a_i(x_1+b_1)+b_i=O(1)+O(\pi^{\val(a_i)-\val(a_1)})=O(1)$
+%using that $\val(a_i) \geq \val (a_1).$
+%
+%We define the polyhedron $\Qc \subset K^{n-1}$ by the following inequalities:
+%$\val(a_1^{-1}x_1- b_n +a_1^{-1}b_1) \geq 0$ and for all $i \in \llbracket 2,n-1 \rrbracket,$
+%$\val(x_i-a_1^{-1}a_i(x_1+b_1)+b_i) \geq 0.$
+%
+%Then the previous computations prove that $p(\PP_2)\subset \Qc.$
+%Conversely, let $(x_1,\dots,x_{n-1}) \in \Qc.$
+%Let $x_n := -a_1^{-1}(x_1+b_1).$
+%Then
+%$x_1+a_1 x_n+b_1=0=O(1).$
+%Let $i \in \llbracket 2,n-1 \rrbracket,$
+%then $x_i+a_i x_n+b_i=x_i-a_1^{-1}a_i(x_1+b_1)+b_i=O(1)$
+%since $(x_1,\dots,x_{n-1}) \in \Qc.$
+%Finally, 
+%$x_n+b_n=-a_1^{-1}(x_1+b_1)+b_n=O(1)$ thanks to the inequality satisfied by $x_1.$
+%Hence $(x_1,\dots,x_n) \in \PP_2$
+%which means that $(x_1,\dots,x_{n-1}) \in p(\PP_2).$
+%Thus $p(\PP_2)= \Qc$ and $p(\PP_2)$ is a polyhedron,
+%and it has been proved in both cases.
+%
+%Therefore,$p(\PP)$ is a polyhedron.
+%
+%\end{proof}
+%
+%We can finally prove that the image of polyhedron under a linear mapping is a polyhedron.
+%\begin{proposition}
+%Let $\PP \subset K^n$ be a polyhedron and $f: K^n \rightarrow K^m$
+%be a linear mapping. Then $f(\PP)$ is a polyhedron.
+%\end{proposition}
+%
+%\begin{proof}
+%
+%We assume that $\PP \neq \emptyset$, and we identify $f$ with its matrix in $\allmat_{n,n}(K)$.
+%As seen above, we can assume that $\PP$ is of the form $\left\lbrace x \in K^n : \val (l_i (x) ) \geq 0, \textrm{ for } i \in I\right\rbrace$ for some
+%finite sets $I \subset \N$ and $l_i \in K[x]_1$, for $i \in I$ .
+%
+%Thanks to Definition \ref{smith_nf}, (the matrix of) $f$
+%can be written $f=Q^{-1} \Delta P$
+%with $P \in \GL_n(\OK),$ $Q \in \GL_m(\OK)$
+%and $\Delta = \mathrm{SNF}(f)\in \allmat_{m,n}(K)$ of the form $\diag(\lambda_1, \ldots, \lambda_r, {\bf 0}_{\min(m,n)-r})$
+%  where ${\bf 0}_{\min(m,n)-r}$ is a null square matrix of size $\min(m,n)-r$ for $\lambda_1,\dots,\lambda_r$ non-zero and $r \in \N.$
+%
+%  %Now, we turn our attention to the $\Delta$ part of $f$.
+%We have previously proven that if $f \in \GL_n(\OK)$ then $f(\PP)$ is a polyhedron.
+%It is also clear that
+%if $f$ is the immersion 
+%$K^l \rightarrow K^n$
+%$(x_1,\dots,x_l)\mapsto (x_1,\dots,x_l,0,\dots,0)$ 
+%and $\PP$ is a polyhedron in $K^n$,
+%then $f(\PP)$ is a polyhedron.
+%
+%
+%We now prove that for
+%$\Delta$ a Smith Normal Form
+%and $\PP$ a polyhedron,
+%$\Delta(\PP)$ is a polyhedron.
+%Then $\Delta$ is the composition
+%of the immersion 
+%$K^l \rightarrow K^n$
+%$(x_1,\dots,x_l)\mapsto (x_1,\dots,x_l,0,\dots,0),$ 
+% the diagonal invertible mapping
+%$K^l \rightarrow K^l$,
+%$(x_1,\dots,x_l)\mapsto (\delta_1,\dots,\delta_l x_l)$,
+%and the projections
+%$(x_1,\dots,x_{l+1})\mapsto (x_1,\dots,x_{l}),$
+% $(x_1,\dots,x_{l+2})\mapsto (x_1,\dots,x_{l+1}),$
+% $\dots,$
+% $(x_1,\dots,x_{n})\mapsto (x_1,\dots,x_{n-1}).$
+% Thus $\Delta(\PP)$ is a polyhedron thanks to the previous 
+% results on image of polyhedron.
+%
+%Finally, if $f: K^n \rightarrow K^m$
+%is a linear mapping and
+%$f=Q^{-1} \Delta P$ is its Smith Normal Form
+%with $P \in \GL_n(\OK),$ $Q \in \GL_m(\OK)$
+%and $\Delta \in \allmat_{n,m}(K)$,
+%then
+%$P(\PP)$ is a polyhedron,
+%$\Delta (P(\PP))$ also,
+%and finally $f(\PP)=Q^{-1} (\Delta (P(\PP)))$
+%is a polyhedron.
+%This concludes the proof.
+%\end{proof}
 
@@
 The following result shows that testing positive semidefiniteness of matrices over
-valued fields reduces to checking whether the coefficients of $\chi_M$ are integers.
+valuation fields reduces to checking whether the coefficients of $\chi_M$ are integers.
 
@@
 a spectrahedron: indeed an affine equation $\ell(x) = 0$ is equivalent to the two inequalities
-$\ell(x) \geq 0 \leq -\ell(x)$. Over a valued field it is necessary to give the following
+$\ell(x) \geq 0 \leq -\ell(x)$. Over a valuation field it is necessary to give the following
 definition in order to include affine sets in the family of spectrahedra.

### 2025-06-18 article/paper_padic_spec.tex

@@
 
-%\title{\bf Title}
-%\title{\bf On polyhedra and spectrahedra over valuation fields}
-\title{\bf On semidefinite-representable sets over valuation fields}
+\title{\Large \bf On semidefinite-representable sets over valued fields}
 
@@
   semidefinite-representable sets. This paper investigates versions of these sets and of
-  the related optimization problems with data over a field $K$ with valuation.
+  the related optimization problems with data over a valued field $K$.
+  For $K$-polyhedra and linear programming over $K$ we give an algorithm based on computation
+  of Smith normal forms.
   We prove that basic properties of semidefinite-representable sets generalize to this setting.
-  We showcase examples of non-polyhedral $K$-spectrahedra and of sets that are semidefinite
-  representable over $K$ but are not $K$-spectrahedra.
+  In particular, we showcase examples of non-polyhedral $K$-spectrahedra and of sets that are
+  semidefinite representable over $K$ but are not $K$-spectrahedra.
 \end{abstract}
@@
 
-The study of polyhedra and of linear programming (LP) is at the heart of convex geometry and optimization,
-inasmuch as several optimization problems can be cast as, or reduced to LP. An important generalization of LP
-is semidefinite programming (SDP), namely the problem of minimizing an affine polynomial over the set of
-positive semidefinite affine combinations of a given collection of real symmetric matrices. The latter problem 
-has interested the community of polynomial optimization because of the relaxation method known as moment-SOS
-(or Lasserre) hierarchy \cite{henrion2020moment}.
-
-Contrary to the LP case, the complexity status of SDP is widely open.
-In a fixed-precision model of computation, SDP is solvable in polynomial time in the input size (matrix size,
-number of variables, bit size of the coefficients), in $\log(\frac{1}{\varepsilon})$ (where $\varepsilon$ is the
-precision) and $\log(\frac{1}{R})$, where $R$ is an {\it a priori} upper bound on the norm of a solution,
-cf. \cite[Sec.1.9]{deKlerk}. In exact arithmetic, the complexity status of SDP is essentially open but complexity
-bounds are known based either on general quantifier elimination \cite{ramana1997exact,porkolab1997complexity}
-or by exploiting the determinantal structure of the constraints \cite{henrion2016exact}.
-
-In this paper we 
-Similar generalizations have been recently proposed in the context of tropical geometry \cite{iriarte2022polyhedral}.
+The study of polyhedra and of linear programming (LP) is at the heart of convex geometry and optimization, inasmuch as several optimization problems can be cast as, or relaxed to LP.
+An important generalization of LP is semidefinite programming (SDP), namely the problem of minimizing a linear function over the set of positive semidefinite affine combinations of some real symmetric matrices.
+The latter problem has interested the community of real algebraic geometry and polynomial optimization, mostly because of the relaxation method known as moment-SOS (or Lasserre) hierarchy \cite{henrion2020moment}.
+
+The main motivation for studying the effective aspects of SDP is the fact that, despite several properties of LP extend to SDP, the complexity status of SDP is, contrary to the LP case, widely open.
+Ramana's construction \cite{ramana1997exact} implies a series of general results: in the Blum-Shub-Smale real numbers machines model \cite{blum1989theory}, the feasibility of SDP is in $\text{NP} \cap \text{co-NP}$, whereas it is not known to be in NP in the Turing model; checking boundedness, attainability and optimality can be polynomially reduced to the feasibility of SDP \cite{ramana1997exact}.
+Assuming the input data belongs to an effective field $K$ (\emph{e.g.} $K = \QQ$) then a solution can be described and computed as element of a vector space over some algebraic extension of $K$.
+For exact computation, complexity bounds are known based either on general quantifier elimination \cite{ramana1997exact,porkolab1997complexity} and explicit algorithms exist based on a dedicated application of the so-called critical point method, and exploiting the determinantal structure of the constraints \cite{henrion2016exact,NALDI2018206}.
+A complexity analysis for the computation of an approximate solution of an SDP can be made based on the ellipsoid algorithm \cite{khachiyan1979polynomial,grotschel1981ellipsoid} or on interior-point methods \cite{de2016turing}; in this approximation framework, SDP is solvable in polynomial time in the input size (\emph{i.e.} matrix size, number of variables, bit size of the coefficients), $\log(\frac{1}{\varepsilon})$ (where $\varepsilon$ is the target precision) and $\log(\frac{R}{r})$, where $r,R$ are radii of balls respectively included in and containing the feasible set, cf.
+\cite{grotschel1981ellipsoid} or \cite[Thm.1.1]{de2016turing} (see also \cite[Sec.1.9]{deKlerk}).
+
+In this paper we consider the situation where input data are defined over fields $K$ with a prescribed valuation map $\val$ on $K$. In this context a polyhedron is
+
+The prototype of valued field we target is the field of $p$-adic numbers with $p$-adic valuation.
+\todo{Give motivations for p-adic precision of LP/SDP.} Similar generalizations have been recently proposed in the context of tropical geometry \cite{iriarte2022polyhedral} and tropical methods applied to non-archimedean semidefinite programming \cite{allamigeon2016solving,allamigeon_tropical_2020}.
 
@@
 
-\subsection{Notation}
-
-Throughout the paper, $K$ refers to a complete,
-discrete valuation field, $\val : K \twoheadrightarrow \ZZ \cup \{+\infty\}$ to its valuation,
-$\OK$ its ring of integers, $\kappa$ its residue field and $\pi$ a uniformizer.
-For $k \in \N$, we write $O(\pi^k)$ for $\pi^k \OK$.
+Throughout the paper, $(K,\val)$ refers to a complete valued field, namely $K$ is a field
+and $\val : K \twoheadrightarrow \Gamma \cup \{+\infty\}$ is a valuation on $K$, $\Gamma$ an
+ordered abelian group. The valuation is often assumed to be discrete ({\it i.e.} $\Gamma=\ZZ$)
+with $\pi \in K$ a uniformizer. The ring of integers of $K$ is
+$$
+\OK = \{x \in K : \val(x) \geq 0\},
+$$
+$\kappa = \OK/\mathfrak{m}_K$ its residue field, with
+$\mathfrak{m}_K = \{x \in K : \val(x) > 0\}$.
+For $k \in \N$, we write $O(\pi^k)$ for $\pi^k \OK$\footnote{\simone{voir si on
+  utilise cette notation}}.
 A typical example of $K$ as above is the field of $p$-adic numbers 
-$\QQ_p$ (equipped with the $p$-adic valuation). For this example, we 
-have $\OK = \ZZ_p$.
-Another example is the field of Laurent series
+$\QQ_p$ equipped with the $p$-adic valuation. For this example, we 
+have $\OK = \ZZ_p$. Another example is the field of Laurent series
 $K=\QQ(\!(t)\!)$ equiped with $t$-adic valuation,
 in which case $\OK = \QQ \llbracket t \rrbracket$.
-We refer to \cite{Serre:1979} for a
+We refer to \cite{Serre:1979,engler2005valued} for a
 general introduction to such fields
-and to Caruso's course on $p$-adic computations \cite{caruso_computations_2017}
+and to \cite{caruso_computations_2017}
 for an introduction to effective computations over $p$-adic numbers.

### 2025-10-06 article/paper_padic_spec.tex
commit by Simone

@@
 
-In this paper we consider the situation where input data are defined over fields $K$ with a prescribed valuation map $\val$ on $K$. In this context a polyhedron is
-
+In this paper we consider the situation where input data are defined over fields $K$ with a prescribed valuation map $\val$ on $K$.
+In this context a polyhedron is defined as a set of vectors such that some linear forms have nonnegative or infinite vluation ({\it cf.} \Cref{def_polyhedra}).
 The prototype of valued field we target is the field of $p$-adic numbers with $p$-adic valuation.
-\todo{Give motivations for p-adic precision of LP/SDP.} Similar generalizations have been recently proposed in the context of tropical geometry \cite{iriarte2022polyhedral} and tropical methods applied to non-archimedean semidefinite programming \cite{allamigeon2016solving,allamigeon_tropical_2020}.
+%%%\todo{Give motivations for p-adic precision of LP/SDP.}
+Similar generalizations have been recently proposed in the context of tropical geometry \cite{iriarte2022polyhedral} and tropical methods applied to non-archimedean semidefinite programming \cite{allamigeon2016solving,allamigeon_tropical_2020}.
 
@@
 $\mathfrak{m}_K = \{x \in K : \val(x) > 0\}$.
-For $k \in \N$, we write $O(\pi^k)$ for $\pi^k \OK$\footnote{\simone{voir si on
-  utilise cette notation}}.
+For $k \in \N$, we write $O(\pi^k)$ for $\pi^k \OK$.
 A typical example of $K$ as above is the field of $p$-adic numbers 

### 2025-10-06 article/paper_padic_spec.tex
commit by Simone

@@
 
+Let us now give a short introduction to classical ({\it i.e.} real) polyhedra and spectrahedra.
 Let $\sym_d(\R) \subset \R^{d\times d}$ be the vector space of $d \times d$ real symmetric
@@
 The optimization problem of miminizing a linear function over a real spectrahedron is called \emph{semidefinite programming} (SDP).
-Given $c \in \R^n$ and $A_0,A_1,\ldots,A_n \in \sym_d(\R)$, the corresponding semidefinite program is defined (in standard dual form) as
-\begin{equation}
-  \label{SDP}
-\begin{array}{rcll}
-  p^* & := & \inf_{x \in \R^n} & \left\langle c, x \right\rangle \\
-  &    & \text{s.t.}         & A_0+\sum_{i=1}^n x_i A_i \succeq 0.
-\end{array}
-\end{equation}
-Real polyhedra (subsets of $\R^n$ defined by finitely many affine inequalities) are special cases of real
+%Given $c \in \R^n$ and $A_0,A_1,\ldots,A_n \in \sym_d(\R)$, the corresponding semidefinite program is defined (in standard dual form) as
+%\begin{equation}
+%  \label{SDP}
+%\begin{array}{rcll}
+%  p^* & := & \inf_{x \in \R^n} & \left\langle c, x \right\rangle \\
+%  &    & \text{s.t.}         & A_0+\sum_{i=1}^n x_i A_i \succeq 0.
+%\end{array}
+%\end{equation}
+{\it Real polyhedra} (subsets of $\R^n$ defined by finitely many affine inequalities) are special cases of real
 spectrahedra, where the defining matrices $A_0, \ldots, A_n$ can be chosen diagonal, so that
@@
 $$
-P = \left\{x = \left[\begin{smallmatrix} x_1 \\ \vdots \\ x_n \end{smallmatrix}\right] \in \R^n : \exists\,y\in\R^m, \, A_0 + \sum_{i=1}^n x_i A_i + \sum_{j=1}^m y_j B_j \succeq 0\right\}
-$$
-when $m>0$, the set $P$ is also called a \emph{spectrahedral shadow}.
+P = \left\{x = \left[\begin{smallmatrix} x_1 \\ \vdots \\ x_n \end{smallmatrix}\right] \in \R^n : \exists\,y\in\R^m, \, A_0 + \sum_{i=1}^n x_i A_i + \sum_{j=1}^m y_j B_j \succeq 0\right\}.
+$$
+When $m>0$, the set $P$ is also called a \emph{spectrahedral shadow}.
 
@@
 \begin{proof}
-As in the proof of Lemma \ref{lem:DIaut} DI${}_{aut}$, an obvious change
-of variable is enough to conclude.
+As in the proof of Lemma \ref{lem:DIaut} DI${}_{aut}$, a trivial change
+of variables is enough to conclude.
 \end{proof}
@@
 and we are reduced to proving that
-$f(\PP_2)$ is polyhedron for $p$ still the projection
+$f(\PP_2)$ is a polyhedron for $p$ the projection
 $K^n \rightarrow K^{n-1}$ and $\PP_2$
@@
 we can further assume that the $\delta_i$'s and $a_n$ are all $1$'s
-and are reduce to $\PP_2$ defined by the linear matrix inequality :
+and are reduce to $\PP_2$ defined by the linear matrix inequality:
 \[  \begin{bmatrix}
@@
 \section*{Acknowledgments}
-
 The second author acknowledges support from the ANR Project ``HYPERSPACE'' (ANR-21-CE48-0006-01).

### 2025-10-06 article/paper_padic_spec.tex
commit by Simone

@@
 $$
-P = \left\{x = \left[\begin{smallmatrix} x_1 \\ \vdots \\ x_n \end{smallmatrix}\right] \in \R^n : \exists\,y\in\R^m, \, A_0 + \sum_{i=1}^n x_i A_i + \sum_{j=1}^m y_j B_j \succeq 0\right\}.
-$$
-When $m>0$, the set $P$ is also called a \emph{spectrahedral shadow}.
+\left\{x = \left[\begin{smallmatrix} x_1 \\ \vdots \\ x_n \end{smallmatrix}\right] \in \R^n : \exists\,y\in\R^m, \, A_0 + \sum_{i=1}^n x_i A_i + \sum_{j=1}^m y_j B_j \succeq 0\right\}.
+$$
+When $m>0$, the set is also called a \emph{spectrahedral shadow}.
 
@@
 \label{fermat_quartic}
-The basic closed semialgebraic set $P = \{(x_1,x_2) \in \R^2 : 1-x_1^4-x_2^4 \geq 0\}$ is not a spectrahedron
+The basic closed semialgebraic set $\mathcal{R} = \{(x_1,x_2) \in \R^2 : 1-x_1^4-x_2^4 \geq 0\}$ is not a spectrahedron
 but it is semidefinite representable:
 $$
-P = \left\{\begin{bmatrix} x_1 \\ x_2 \end{bmatrix} \in \R^2 :
+\mathcal{R} = \left\{\begin{bmatrix} x_1 \\ x_2 \end{bmatrix} \in \R^2 :
 \exists\,
@@
 and $\PP_E := \left\lbrace X \in K^n,  CX+D=0 \right\rbrace = P + \overrightarrow{\PP_E}.$ 
-
 Then $f(\PP) = f_{\PP_E}(\PP_I).$
@@
 
-    Now let $S \in K^{n\times R}$ be the SNF of $A'$ and $Q \in \mathbf{GL}_n\left(\mathcal{O}_K\right)$ and $P \in \mathbf{GL}_R\left(\mathcal{O}_K\right)$ such that $A'= Q S P^{-1}$.
+    Now let $S \in K^{n\times R}$ be the SNF of $A'$ and $Q \in \GL_n\left(\mathcal{O}_K\right)$ and $P \in \GL_R\left(\mathcal{O}_K\right)$ such that $A'= Q S P^{-1}$.
     Then $\mathcal{P'} = \{y \in K^R : QSP^{-1}y + b' \ge  0\} = P\{z \in K^R : Sz + Q^{-1}b' \ge 0 \}$.
@@
 and $\left\langle c, x \right\rangle := c_1 x_1+\cdots +c_n x_n$.
-When $A$ is a diagonal matrix\footnote{\simone{J'ai supprimé ``and
-$D=0$'', car cela ne me semble pas nécessaire pour définir le ``diagonal LP''.}},
+When $A$ is a diagonal matrix,
 we refer to \eqref{LP} as a \emph{diagonal} linear program.
@@
 \begin{remark}
-  Assume $\val$ is a discrete valuation. Then\footnote{\simone{Cela voudrait dire que
-    si la valuation n'est pas discrète, on pourrait avoir un problème LP qui est admissible
-    (c'est-à-dire l'ensemble admissible est non-vide) et où $p^* \in \R$, mais $p^*$ n'est
-  pas atteint. C'est ça ? A-t-on des exemples ?}} if \eqref{LP} admits feasible vectors,
+  Assume $\val$ is a discrete valuation. Then
+  if \eqref{LP} admits feasible vectors,
   $p^*$ is either $-\infty$ or attained at some solution $x^*$.
@@
     $y$ is a solution for~\eqref{LP} with data $(AJ,b+A x_0,J^T c,{\bf 0},0)$ and
-    $\langle c,x^* \rangle = \langle J^T c,y^* \rangle$\footnote{\simone{Est-ce que
-    c'est bien $\langle c,x^* \rangle = \langle J^T c,y^* \rangle$ ou plutôt la condition
-    plus faible $\val \langle c,x^* \rangle = \val \langle J^T c,y^* \rangle$ ?
-  Même question pour \Cref{solsLP}.}}.
+    $\langle c,x^* \rangle = \langle J^T c,y^* \rangle$.
   \end{enumerate}
@@
   A vector $y = (y_1, \ldots, y_n)^T \in K^n$ is feasible for \eqref{LP} with data
-  $(S,b',c',0)$ if and only if $\val(s_i y_i + b'_i) \geq 0$ for\footnote{\simone{J'ai mis
-    $\val(s_i y_i + b'_i) \geq 0$ au lieu de $\val(s_i y_i + b_i) \geq 0$ car c'est $b'$
-    et non pas $b$.}} all $i = 1,\ldots,n$.
+  $(S,b',c',0)$ if and only if $\val(s_i y_i + b'_i) \geq 0$ for all $i = 1,\ldots,n$.
   However $s_i = 0$ for $n-r \leq i\leq n$. Therefore, if \eqref{LP} with data $(S,b',c',0)$ is feasible,
@@
   we have $\val \left(\langle c', y^* + \alpha_n e ^i \rangle\right) = \val \pi^{-n} = -n$.
-  Therefore, the problem is unbounded as $p^* = -\infty$\footnote{\simone{avant c'était ``Therefore, the problem is unbounded as $p^* = +\infty$'' ce qui ne me paraît pas correct.}}.
+  Therefore, the problem is unbounded as $p^* = -\infty$.
 \end{proof}
@@
   If $\val(\lambda) < v$, the minimum of $y\mapsto \val\left(\left\langle c',y \right\rangle\right)$ over $\PP'$ is reached at any point of $\PP'$, and is equal to $\val(\lambda)$.
-  Otherwise, $\lambda \in \pi^{v} \OK$ and the minimum is $v$ and is reached at any points $y$ of $\PP'$ such that\footnote{\simone{J'imagine que c'est plutôt
-    $\left<c',y \right> \in \pi^v\OK$ ? Avant c'etait $\left<c',y \right> \in \pi^v$.}}
+  Otherwise, $\lambda \in \pi^{v} \OK$ and the minimum is $v$ and is reached at any points $y$ of $\PP'$ such that
   $\left<c',y \right> \in \pi^v\OK$.
@@
 
-Recall that the \emph{Newton polygon} $\mathcal{P}$ of a polynomial $P = \sum_{i=0}^{d} a_i T^i \in K[T]$ is
+Recall that the \emph{Newton polygon} of a polynomial $P = \sum_{i=0}^{d} a_i T^i \in K[T]$ is
 defined as the inferior convex hull of the set $\{(i, \val a_i) \,|\, 0 \le i \le d\}$, {\it i.e.} the
@@
   $$
-  S_A = \varphi_A^{-1}(K^{d \times d}_+) = \{x \in K^n : A_0+x_1A_1+\cdots+x_nA_n \succeq 0\}
+  \mathcal{S}_A = \varphi_A^{-1}(K^{d \times d}_+) = \{x \in K^n : A_0+x_1A_1+\cdots+x_nA_n \succeq 0\}
   $$
@@
 and
-$(L_1 \cap S_A) \cap (L_2 \cap S_B) = (L_1\cap L_2) \cap S_{\diag(A,B)}$ for
+$(L_1 \cap \mathcal{S}_A) \cap (L_2 \cap S_B) = (L_1\cap L_2) \cap S_{\diag(A,B)}$ for
 two affine spaces $L_1,L_2 \subset K^n$.
@@
   $$
-  One has $L = S_A = \varphi_A^{-1}(K^{d \times d}_+)$. Since $M \subset K^n$ is affine, 
+  One has $L = \mathcal{S}_A = \varphi_A^{-1}(K^{d \times d}_+)$. Since $M \subset K^n$ is affine, 
   $P$ is a spectrahedron in $K^n$.
@@
 %  In other words, we showed that there exist $d \in \mathbb{N}$ and
-%  $A_0,A_1,\ldots,A_n \in K^{d \times d}$ such that $P = S_A$, as stated.
+%  $A_0,A_1,\ldots,A_n \in K^{d \times d}$ such that $P = \mathcal{S}_A$, as stated.
 %%% OLD PROOF
@@
 %  $\varphi(x) = A(x)$ is injective. 
-%  First, remark that $Q=S_A$ and thus $\varphi(Q) = \mathcal{L} \cap K^{d\times d}$, with
+%  First, remark that $Q=\mathcal{S}_A$ and thus $\varphi(Q) = \mathcal{L} \cap K^{d\times d}$, with
 %  $\mathcal{L} = A_0+\span{A_1,\ldots,A_n}$ is a spectrahedron.
@@
   \[
-  S = \left\{x \in K : \begin{bmatrix} 0 & x + \pi^{-1} \\ x & 0 \end{bmatrix} \succeq 0\right\}
+  \mathcal{S} = \left\{x \in K : \begin{bmatrix} 0 & x + \pi^{-1} \\ x & 0 \end{bmatrix} \succeq 0\right\}
   \] 
@@
 \begin{proof}
-  By \Cref{caracsdp}, one has $S = \{x \in K : \val(x(x + \pi^{-1})) \geq 0\} =
+  By \Cref{caracsdp}, one has $\mathcal{S} = \{x \in K : \val(x(x + \pi^{-1})) \geq 0\} =
   \{x \in K: \val x \ge 1\} \cup \{x \in K: \val (x - \pi^{-1}) \ge 1\}$ which is not a ball.
-  Therefore, by \Cref{cor:caracdim1}, $S$ is not a polyhedron.
+  Therefore, by \Cref{cor:caracdim1}, $\mathcal{S}$ is not a polyhedron.
 \end{proof}
@@
 \end{proposition}
-
-\begin{proof}
-  Let $S = S_A \subset K^n$ be spectrahedron, for some linear matrix $A = A_0+\sum_{i=1}^n x_i A_i$. 
+\begin{proof}
+  Let $\mathcal{S}_A \subset K^n$ be a spectrahedron, for some linear matrix $A = A_0+\sum_{i=1}^n x_i A_i$. 
   Denote by $p_i \in K[x]$ the $i$-th coefficient of $\chi_{A}$, $i=0,\ldots,d$.
@@
   $$
-  S = \left\{x \in K^n : \chi_{A} \in \OK[T]\right\}
+  \mathcal{S}_A = \left\{x \in K^n : \chi_{A} \in \OK[T]\right\}
   = \bigcap_{i=0}^d \{x \in K^n : \val(p_i(x)) \geq 0\}.
@@
 \begin{definition}[Polyannulus]\label{def_annuli}
-  A set of the form $C = \{x \in K \,|\, a \le \val(x) \le b\}$, for $a,b \in \R^*_+$,
-  is called \emph{annulus}. A product $C_1 \times C_2 \times \cdots \times C_n \subset K^n$,
+  A set of the form $\mathcal{C} = \{x \in K \,|\, a \le \val(x) \le b\}$, for $a,b \in \R^*_+$,
+  is called \emph{annulus}. A product $\mathcal{C}_1 \times \mathcal{C}_2 \times \cdots \times \mathcal{C}_n \subset K^n$,
   where each $C_i \subset K$ is an annulus, is called a \emph{polyannulus}.
@@
 \begin{definition}[Semidefinite-representable set]\label{def_semi_def_rep_set}
-  A set $S \subset K^n$ is called \emph{semide\-fi\-nite-re\-pre\-sen\-ta\-ble (SDR)} if there exist $m,d \in \N$ and
+  A set $\mathcal{R} \subset K^n$ is called
+  \emph{semide\-fi\-nite-re\-pre\-sen\-ta\-ble (SDR)} if there exist $m,d \in \N$ and
   matrices $\{A_i,B_j : i = 0, \ldots, n, j = 1, \ldots, m\} \subset K^{d \times d}$ such that
   $$
-  S = \left\{x \in K^n : \exists y \in K^m, A_0+\sum_{i=1}^n x_iA_i + \sum_{j=1}^m y_jB_j \succeq 0\right\}
-  $$
-  that is, $x \in S$ if and only if there exists $y \in K^m$ such that
-  $(x,y) \in S_M \subset K^{n+m}$, for $M(x,y) = A_0+\sum_{i=1}^n x_iA_i + \sum_{j=1}^m y_jB_j$.
+  \mathcal{R} = \left\{x \in K^n : \exists y \in K^m, A_0+\sum_{i=1}^n x_iA_i + \sum_{j=1}^m y_jB_j \succeq 0\right\}
+  $$
+  that is, $x \in \mathcal{R}$ if and only if there exists $y \in K^m$ such that
+  $(x,y) \in S_M \subset K^{n+m}$, for some pencil $M(x,y) = A_0+\sum_{i=1}^n x_iA_i + \sum_{j=1}^m y_jB_j$.
   The integer $m$ is called the \emph{height} of the representation and $d$ its \emph{degree}.
@@
 
-Of course a spectrahedron $S_A = \varphi_A^{-1}(K^{d \times d})$ is SDR with height $m=0$ and degree
+Of course a spectrahedron $\mathcal{S}_A = \varphi_A^{-1}(K^{d \times d})$ is SDR with height $m=0$ and degree
 $d$. In order to distinguish between spectrahedra and possibly non-spectrahedral semidefinite-representable sets
@@
 \begin{proof}
-  Let $C = C_1 \times \cdots \times C_n \subset K^n$ be as in \Cref{def_annuli},
-  for some annuli $C_1,\ldots,C_n \subset K$. We claim that each $C_i$ is a spectrahedral
-  shadow of height $1$ and degree $4$. Assume $C_i = \{x_i \in K : a_i \leq \val(x_i) \leq b_i\}$
+  Let $\mathcal{C} = \mathcal{C}_1 \times \cdots \times \mathcal{C}_n \subset K^n$ be as in \Cref{def_annuli},
+  for some annuli $\mathcal{C}_1,\ldots,\mathcal{C}_n \subset K$. We claim that each $\mathcal{C}_i$ is a spectrahedral
+  shadow of height $1$ and degree $4$. Assume $\mathcal{C}_i = \{x_i \in K : a_i \leq \val(x_i) \leq b_i\}$
   for some $a_i, b_i \in \R^*_+$ with $a_i < b_i$. Consider the spectrahedron
-  $S_{M^{(i)}} \subset K^2$ defined by
-  $$
-  S_{M^{(i)}} = \left\{(x_i,y_i) \in K^2 :
+  $\mathcal{S}_{M^{(i)}} \subset K^2$ defined by
+  $$
+  \mathcal{S}_{M^{(i)}} = \left\{(x_i,y_i) \in K^2 :
   M^{(i)}(x_i,y_i) := \diag\left(\pi^a x_i, \pi^{-b} y_i,
@@
   $$
-  We claim that $x_i \in C_i$ if and only if there exists $y_i \in K$ such that $(x_i,y_i) \in S_{M^{(i)}}$.
+  We claim that $x_i \in \mathcal{C}_i$ if and only if there exists $y_i \in K$ such that $(x_i,y_i) \in
+  \mathcal{S}_{M^{(i)}}$.
   Indeed, by \Cref{caracsdp}, $M^{(i)}(x_i,y_i) \succeq 0$ if and only if $(x_i,y_i)$ is a solution of the system
@@
   %Therefore, if $(x, y)$ verifies \eqref{eq:annulussyst} then $\val\left(x\right)\ge a$, $\val\left(y\right)\ge -b$ and $ \left( xy-1 \right) \ge 2$.
-  The last inequality implies that $\val\left(x_i\right)+\val\left(y_i\right)=\val\left(x_iy_i\right) = \val\left(-1\right) =0$ and therefore that $\val\left(x_i\right)=-\val\left(y_i\right)\le -(-b) = b$, so $x_i \in C_i$.
-Reciprocally if $x_i \in C_i$ then $(x_i,x_i^{-1})$ is a solution of \eqref{eq:annulussyst}.
+  The last inequality implies that $\val\left(x_i\right)+\val\left(y_i\right)=\val\left(x_iy_i\right) = \val\left(-1\right) =0$ and therefore that $\val\left(x_i\right)=-\val\left(y_i\right)\le -(-b) = b$, so $x_i \in \mathcal{C}_i$.
+Reciprocally if $x_i \in \mathcal{C}_i$ then $(x_i,x_i^{-1})$ is a solution of \eqref{eq:annulussyst}.
 This proves our claim.
-Finally, since $C = C_1 \times \cdots \times C_n$, one has
+Finally, since $\mathcal{C} = \mathcal{C}_1 \times \cdots \times \mathcal{C}_n$, one has
 \begin{equation*}
   \begin{aligned}
-    C &=
-    \{x=(x_1,\ldots,x_n) \in K^n : \exists y = (y_1,\ldots,y_n) \in K^n, (x_i,y_i) \in S_{M^{(i)}}, i=1,\ldots,n\} \\
-    &= \{x \in K^n : \exists y \in K^n, (x,y) \in S_M\}
+    \mathcal{C} &=
+    \{x=(x_1,\ldots,x_n) \in K^n : \exists y = (y_1,\ldots,y_n) \in K^n, (x_i,y_i) \in
+    \mathcal{S}_{M^{(i)}}, i=1,\ldots,n\} \\
+    &= \{x \in K^n : \exists y \in K^n, (x,y) \in \mathcal{S}_M\}
   \end{aligned}
 \end{equation*}
-with $S_M = \diag\left(M^{(1)}, M^{(2)}, \ldots, M^{(n)}\right) \in K[x,y]^{4n \times 4n}.$
-\end{proof}
+with $\mathcal{S}_M = \diag\left(M^{(1)}, M^{(2)}, \ldots, M^{(n)}\right) \in K[x,y]^{4n \times 4n}.$
+\end{proof}
+
+We conclude proving that, in general, annuli are not spectrahedral.
 
 \begin{proposition}
-If the residue field $\kappa$ is infinite, then
-no (non-trivial) annulus of $K$ can be a spectrahedron of $K.$
+If the residue field $\kappa$ is infinite, then no (non-trivial) annulus of $K$ can be a spectrahedron of $K.$
 \end{proposition}

### 2025-10-06 article/paper_padic_spec.tex
commit by Simone

@@
  %total={170mm,257mm},
- left=30mm,
- right=30mm,
- top=30mm,
- bottom=30mm
+ left=33mm,
+ right=33mm,
+ top=35mm,
+ bottom=35mm
 }
@@
   \label{def_polyhedra}
-  A \emph{polyhedron} is a subset $P \subset K^n$ of the form
-  $$
-  P = \{x \in K^n : \val(\ell_i(x)) \geq 0, i=1,\ldots,d \text{ and }
+  A \emph{polyhedron} is a subset $\PP \subset K^n$ of the form
+  $$
+  \PP = \{x \in K^n : \val(\ell_i(x)) \geq 0, i=1,\ldots,d \text{ and }
   \val(m_j(x)) = +\infty, j=1,\ldots,e\},
@@
 \begin{theorem}[DI] 
-Let $f : K^n \to K^m$ be an affine map and $\PP$ a polyhedron of $K^n.$
+Let $f : K^n \to K^m$ be an affine map and $\PP$ a polyhedron in $K^n.$
 Then $f(\PP)$ is a polyhedron. \label{theo:DI}
@@
 The strategy to deduce the main theorem DI 
-is the following:
-\begin{figure}[htbp]
+is given in \Cref{fig:di-properties}.
+
+\begin{figure}[!ht] 
 \centering
@@
 ]
-
 % Nodes
@@
 \node[box, right=of DIi] (DI) {DI};
-
 \node[box, above=of DIproj] (DIimm) {DI${}_{imm}$};
 \node[box, below=of DIproj] (DIaut) {DI${}_{aut}$};
-
 % Arrows
@@
 \draw[thickarrow] (DIi) -- (DI);
-
 \draw[thickarrow] (DIimm) -- (DIl);
 \draw[thickarrow] (DIaut) -- (DIl);
-
 \end{tikzpicture}
@@
 
-We begin by the cases of linear maps in $GL_n(O_K)$.
+We begin with the case of linear maps in $\GL_n(O_K)$.
 
 \begin{lemma}[DI${}_{aut}$]
-Let $f \in GL_n(O_K)$ and $\PP$ a polyhedron of $K^n$.
+Let $f \in GL_n(O_K)$ and $\PP$ a polyhedron in $K^n$.
 Then $f(\PP)$ is a polyhedron. \label{lem:DIaut}
@@
 \begin{lemma}[DI${}_{diag}$]
-Let $f : K^n \to K^n$ be a linear map and $\PP$ a polyhedron of $K^n$ defined only by inequalities. We assume that the matrix of $f$ in the canonical basis of $K^n$ is diagonal.
+Let $f : K^n \to K^n$ be a linear map and $\PP$ a polyhedron in $K^n$ defined only by inequalities. We assume that the matrix of $f$ in the canonical basis of $K^n$ is diagonal.
 Then $f(\PP)$ is a polyhedron. \label{lem:DIdiag}
@@
 \begin{lemma}[DI${}_{proj}$]
-Let $f : K^n \to K^n, \: (x_1,\dots,x_{n-1},x_n) \mapsto (x_1,\dots,x_{n-1})$ and $\PP$ a polyhedron of $K^n$ defined only by inequalities. 
+Let $f : K^n \to K^n, \: (x_1,\dots,x_{n-1},x_n) \mapsto (x_1,\dots,x_{n-1})$ and $\PP$ a polyhedron in $K^n$ defined only by inequalities. 
 Then $f(\PP)$ is a polyhedron defined only by inequalities. \label{lem:DIproj}
@@
 \begin{lemma}[DI${}_{imm}$]
-Let $f : K^l \to K^n$ be the immersion $(x_1,\dots, x_l) \mapsto (x_1,\dots, x_l,0,\dots, 0)$ and $\PP$ a polyhedron of $K^l$
-Then $f(\PP)$ is a polyhedron. \label{lem:DIimm}
+  Let $f : K^l \to K^n$ be the immersion $(x_1,\dots, x_l) \mapsto (x_1,\dots, x_l,0,\dots, 0)$ and $\PP$
+  a polyhedron in $K^l$. Then $f(\PP)$ is a polyhedron. \label{lem:DIimm}
 \end{lemma}
@@
 \begin{proposition}[DI${}_l$]
-Let $f : K^n \to K^m$ be a linear map and $\PP$ a polyhedron of $K^n$ defined only by inequalities.
+Let $f : K^n \to K^m$ be a linear map and $\PP$ a polyhedron in $K^n$ defined only by inequalities.
 Then $f(\PP)$ is a polyhedron. \label{prop:DIl}
@@
 \begin{proposition}[DI${}_i$]
-Let $f : K^n \to K^m$ be an affine map and $\PP$ a polyhedron of $K^n$ defined only by inequalities.
+Let $f : K^n \to K^m$ be an affine map and $\PP$ a polyhedron in $K^n$ defined only by inequalities.
 Then $f(\PP)$ is a polyhedron. \label{prop:DIi}
@@
 \begin{proof}
-Let $P \in K^m$. One can see by immediate change of variables that $\Qc$ is a polyhedron of $K^m$ if and only if
-$\Qc+P$ is a polyhedron of $K^m$.
+Let $P \in K^m$. One can see by immediate change of variables that $\Qc$ is a polyhedron in $K^m$ if and only if
+$\Qc+P$ is a polyhedron in $K^m$.
 Consequently, translating by $-f(O)$ in the codomain, one can reduce
@@
 \begin{proof}[Proof of Theorem \ref{theo:DI} DI]
-Here, $f : K^n \to K^m$ is an affine map and $\PP$ a polyhedron of $K^n.$
+Here, $f : K^n \to K^m$ is an affine map and $\PP$ a polyhedron in $K^n.$
 Let us write $\PP = \PP_I \cap \PP_E$
@@
 By a translation of $-P$ in $K^n$, we can assume that
-$\PP_E$ is a linear vector space: we are reduced to proving that, if $\tilde{f}: \PP_E \to K^m$ is an affine map and $\PP_I$ is a polyhedron of the vector space $\PP_E$ defined only by inequalities, then  $\tilde{f}(\PP_I)$ is a polyhedron.
+$\PP_E$ is a linear vector space: we are reduced to proving that, if $\tilde{f}: \PP_E \to K^m$ is an affine map and $\PP_I$ is a polyhedron in the vector space $\PP_E$ defined only by inequalities, then  $\tilde{f}(\PP_I)$ is a polyhedron.
 This is the case thanks to Proposition \ref{prop:DIi} DI$_i$
@@
 \begin{proposition}[Characterization of polyhedra] \label{prop:carac}
-    Polyhedra are either empty or the image of polydiscs under a linear mapping.
+    Non-empty polyhedra are image of polydiscs under a linear mapping.
 \end{proposition}
 \begin{proof}
-    Let $\mathcal{P}$ be a polyhedron in $K^n$. Then $\mathcal{P} = \{x \in K^n : Ax+B \ge 0, Dx = e\}$ for some $A \in K^{d \times n}, b \in K ^d,  D\in  K^{m\times n}, e \in K^m$.
-
-    If $\mathcal{P}$ is nonempty then there exists $x_0 \in K^n$ such that $Dx_0=e$.
+    Let $\PP$ be a polyhedron in $K^n$. Then $\PP = \{x \in K^n : Ax+B \ge 0, Dx = e\}$ for some $A \in K^{d \times n}, b \in K ^d,  D\in  K^{m\times n}, e \in K^m$.
+
+    If $\PP$ is nonempty then there exists $x_0 \in K^n$ such that $Dx_0=e$.
 Let $J \in K^{n \times R}$ such that $\textrm{Im} J = \ker D$ where $R$ denotes the dimension of $\ker D$.
-Then $\mathcal{P} = x_0 + J\mathcal{P}'$ where $A' := AJ$ $b' := Ax_0 + b$ and  $\mathcal{P'} := \{y \in K ^R: A'y + b' \ge 0 \}$.
+Then $\PP = x_0 + J\PP'$ where $A' := AJ$ $b' := Ax_0 + b$ and
+    $\PP' := \{y \in K ^R: A'y + b' \ge 0 \}$.
 
     Now let $S \in K^{n\times R}$ be the SNF of $A'$ and $Q \in \GL_n\left(\mathcal{O}_K\right)$ and $P \in \GL_R\left(\mathcal{O}_K\right)$ such that $A'= Q S P^{-1}$.
-    Then $\mathcal{P'} = \{y \in K^R : QSP^{-1}y + b' \ge  0\} = P\{z \in K^R : Sz + Q^{-1}b' \ge 0 \}$.
+    Then $\PP' = \{y \in K^R : QSP^{-1}y + b' \ge  0\} = P\{z \in K^R : Sz + Q^{-1}b' \ge 0 \}$.
     Let $b'':=Q^{-1}b$ then $P' = P \{z \in K^R : s_i z_i + b''_i \ge 0, i= 1\ldots R\}$.
-The set $\{z \in K^R : s_i z_i + b_i \ge 0\}$ is either empty or a polydisc (with eventually infinite radii) and $\mathcal{P} = x_0 + JP \{z \in K^R: s_i z_i + b_i \ge  0, i=1,\ldots,R\}$ which concludes the proof.
+The set $\{z \in K^R : s_i z_i + b_i \ge 0\}$ is either empty or a polydisc (possibly with infinite radii) and $\PP = x_0 + JP \{z \in K^R: s_i z_i + b_i \ge  0, i=1,\ldots,R\}$ which concludes the proof.
 
@@
 \begin{corollary} \label{cor:caracdim1}
-   If $\mathcal{P}$ is a polyhedron in $K$ then $\mathcal{P}$ is either empty or a ball (eventually with infinite radius).
+   If $\PP$ is a polyhedron in $K$ then $\PP$ is either empty or a ball (possibly with infinite radius).
 \end{corollary}
@@
 \begin{proof}
-    Let $\mathcal{P}$ be such polyhedron.
-We assume that $\mathcal{P} \neq \emptyset$.
-By \ref{prop:carac} there exist a polydisc $D = \{x \in K^n : \val s_i x_i - b_i \ge 0, i=1,\ldots,n \}$ for some $s_1,\ldots,s_n, b_1,\ldots,b_n \in K ^n$ and an affine map $f : K^n \to K$ such that $\mathcal{P} = f(D)$.
+    Let $\PP$ be such polyhedron.
+We assume that $\PP \neq \emptyset$.
+By \ref{prop:carac} there exist a polydisc $D = \{x \in K^n : \val s_i x_i - b_i \ge 0, i=1,\ldots,n \}$ for some $s_1,\ldots,s_n, b_1,\ldots,b_n \in K ^n$ and an affine map $f : K^n \to K$ such that $\PP = f(D)$.
 Let $a_0,a_1,\ldots,a_n \in K$ such that $f(x) = a_0 + a_1 x_1 + \ldots + a_n x_n$.
@@
 
-If there exists $i_0 \in \{1,\ldots,n\}$ such that $s_{i_0} = 0$ then $\mathcal{P} = f(D) = K$ and $\mathcal{P}$ is a ball of infinite radius.
+If there exists $i_0 \in \{1,\ldots,n\}$ such that $s_{i_0} = 0$ then $\PP = f(D) = K$ and $\PP$ is a ball of infinite radius.
 Otherwise, we have $D = \{x \in K^n : x_i = \frac{b_i}{s_i} + O\left( \pi^{-val s_i} \right), i=1,\ldots,n \}$ and therefore for all $x \in  K$, $x \in P$ if and only if $x = a_0 + \sum_{i=1}^{n}( \frac{a_i b_i}{s_i} + O\left( \pi^{\val a_i - \val s_i} \right))= a_0  + \sum_{i=1}^{n} \frac{a_i b_i}{s_i} + O(\pi^d)$ where $d = \min \limits_{i = 1,\ldots,n} \val a_i - \val s_i$.
-Thus $\mathcal{P} = \{x \in K : \val (x - a_0 - \sum_{i=1}^{n} \frac{a_i b_i}{s_i}) \ge d \}$ is a ball.
+Thus $\PP = \{x \in K : \val (x - a_0 - \sum_{i=1}^{n} \frac{a_i b_i}{s_i}) \ge d \}$ is a ball.
 
@@
 \end{equation*}
+Note that $\PP$ is a polyhedron.
 A vector $x \in K^n$ is called \emph{feasible} for~\eqref{LP} if $x \in \PP$.
@@
   %$$
-  %\langle c',\mathcal{P}'\rangle = \lambda + \pi^v\OK.
+  %\langle c',\PP'\rangle = \lambda + \pi^v\OK.
   %$$
-  %If attained on every $x \in \mathcal{P}'$;
+  %If attained on every $x \in \PP'$;
 \end{lemma}
@@
 defined as the inferior convex hull of the set $\{(i, \val a_i) \,|\, 0 \le i \le d\}$, {\it i.e.} the
-graph of the greatest convex function $\mathcal{P} : [0,d] \to \R$ such that $\mathcal{P}(i) \leq \val a_i$
+graph of the greatest convex function $\PP : [0,d] \to \R$ such that $\PP(i) \leq \val a_i$
 for $i=1,\ldots,d$. This function is piecewise affine and its slopes are exactly the opposites of the valuations
@@
 \begin{definition}
-  A subset $S$ of $K^n$ is said \emph{semialgebraic} if it is defined by finite unions and intersections of sets defined by polynomial equalities of the form $\{ x \in K^n  : P( x) = 0 \}$ and of sets defined by polynomial inequalities of the form $\{ x\in K^n : \val P(x) \geq 0 \}$.
+  A subset $S$ of $K^n$ is said \emph{semialgebraic} if it is defined by finite unions and intersections
+  of sets defined by equalities of the form $\{x \in K^n  : p(x) = 0\}$
+  and of sets defined by inequalities of the form $\{ x\in K^n : \val p(x) \geq 0\}$, for polynomials
+  $p \in K[x]$.
 \end{definition}

### 2025-10-10 article/paper_padic_spec.tex
Correction de quelques typos.

@@
 In this paper we consider the situation where input data are defined over fields $K$ with a prescribed valuation map $\val$ on $K$.
-In this context a polyhedron is defined as a set of vectors such that some linear forms have nonnegative or infinite vluation ({\it cf.} \Cref{def_polyhedra}).
+In this context a polyhedron is defined as a set of vectors such that some linear forms have nonnegative or infinite valuation ({\it cf.} \Cref{def_polyhedra}).
 The prototype of valued field we target is the field of $p$-adic numbers with $p$-adic valuation.
@@
 ordered abelian group. The valuation is often assumed to be discrete ({\it i.e.} $\Gamma=\ZZ$)
-with $\pi \in K$ a uniformizer. The ring of integers of $K$ is
+with $\pi \in K$ a uniformizer. The valuation ring of $K$ is
 $$
@@
 $\kappa = \OK/\mathfrak{m}_K$ its residue field, with
-$\mathfrak{m}_K = \{x \in K : \val(x) > 0\}$.
+$\mathfrak{m}_K = \{x \in K : \val(x) > 0\}$. An element of $\OK$ is called integral (at $\val$).
 For $k \in \N$, we write $O(\pi^k)$ for $\pi^k \OK$.
@@
 $B_1,\ldots,B_d$ are denoted by $\diag(B_1, \ldots, B_d)$, the null matrix of
-size $p \times q$ by ${\bf 0}_{p,q}$, and the identity matrix by $I_t$.
+size $p \times q$ by ${\bf 0}_{p,q}$, and the identity matrix of size $t \times t$ by $I_t$.
 
@@
   polyhedron defined as the set of $x=(x_1,\ldots,x_n) \in K^n$ such that $||x||_{\infty} =
-  \max_i\{x_i\} \leq 1$, in other words, such that $\val(x_i) \geq 0$, for all $i=1, \ldots, n$.
-  In other words, $\OK^n$ is the polyhedron in $K^n$ defined by the affine polynomials
+  \max_i\{\vert x_i \vert\} \leq 1$, in other words, such that $\val(x_i) \geq 0$, for all $i=1, \ldots, n$.
+  As such, $\OK^n$ is the polyhedron in $K^n$ defined by the affine polynomials
   $\ell_i(x)=x_i$, $i=1,\ldots, n$, and $e=0$. %%%%%(its affine hull is indeed the whole $K^n$).
@@
 \begin{lemma}[DI${}_{proj}$]
-Let $f : K^n \to K^n, \: (x_1,\dots,x_{n-1},x_n) \mapsto (x_1,\dots,x_{n-1})$ and $\PP$ a polyhedron in $K^n$ defined only by inequalities. 
+Let $f : K^n \to K^{n-1}, \: (x_1,\dots,x_{n-1},x_n) \mapsto (x_1,\dots,x_{n-1})$ and $\PP$ a polyhedron in $K^n$ defined only by inequalities. 
 Then $f(\PP)$ is a polyhedron defined only by inequalities. \label{lem:DIproj}
@@
 $K^l \rightarrow K^l$,
-$(x_1,\dots,x_r)\mapsto (\delta_1,\dots,\delta_r x_r)$,
+$(x_1,\dots,x_r)\mapsto (\delta_1 x_1,\dots,\delta_r x_r)$,
 and the projections
@@
 Let $a_0,a_1,\ldots,a_n \in K$ such that $f(x) = a_0 + a_1 x_1 + \ldots + a_n x_n$.
-We can assume, with no loss of generality, that the $a_i$'s are nonzero.
+We can assume, without loss of generality, that the $a_i$'s are nonzero.
 
@@
 \begin{proof}
-  If the linear system $Dx=e$, Problem \eqref{LP} is infeasible
-  and \Cref{algo_LP} outputs correct answer at step \ref{step:linear_empty}.
+  If the linear system $Dx=e$ has no solution, Problem \eqref{LP} is infeasible
+  and \Cref{algo_LP} outputs the correct answer at step \ref{step:linear_empty}.
   Else, by \Cref{reducD} the input problem can be reduced to a new linear
@@
 Recall that the \emph{Newton polygon} of a polynomial $P = \sum_{i=0}^{d} a_i T^i \in K[T]$ is
-defined as the inferior convex hull of the set $\{(i, \val a_i) \,|\, 0 \le i \le d\}$, {\it i.e.} the
+defined as the lower convex hull of the set $\{(i, \val a_i) \,|\, 0 \le i \le d\}$, {\it i.e.} the
 graph of the greatest convex function $\PP : [0,d] \to \R$ such that $\PP(i) \leq \val a_i$
@@
 The following result shows that testing positive semidefiniteness of matrices over
-valued fields reduces to checking whether the coefficients of $\chi_M$ are integers.
+valued fields reduces to checking whether the coefficients of $\chi_M$ are integral.
 
@@
 
-As a consequence, matrices with integer coefficients are positive semidefinite.
+As a consequence, matrices with integral coefficients are positive semidefinite.
 
@@
   is $\chi_M = T^2-5T-4$.
-However when seen as a matrix over $K=\mathbb{Q}_5$, then $\chi_M \in \mathbb{Z}_5[T] = \OK[T]$: then $M \in (\mathbb{Q}_5)^{2 \times 2}_+$, nevertheless $M \not\in (\mathbb{Z}_5)^{2\times 2}$, hence
+However when seen as a matrix over $K=\mathbb{Q}_5$, then $\chi_M \in \mathbb{Z}_5[T] = \OK[T]$.
+As such $M \in (\mathbb{Q}_5)^{2 \times 2}_+$, while nevertheless $M \not\in (\mathbb{Z}_5)^{2\times 2}$, and hence
   $(\mathbb{Q}_5)^{2 \times 2}_+ \not\subset (\mathbb{Z}_5)^{2 \times 2}$.
@@
 
-In the real case, one often abuses of the definition of spectrahedra, saying that the set
+In the real case, one often abuses the definition of spectrahedra, saying that the set
 $\{x \in \mathbb{R}^n : A_0+\sum_{i=1}^n x_iA_i \succeq 0\}$ is also a spectrahedron.
-Remark that this also yields that every affine subset of $\mathbb{R}^n$ is also
+Remark that this yields that every affine subset of $\mathbb{R}^n$ is also
 a spectrahedron: indeed an affine equation $\ell(x) = 0$ is equivalent to the two inequalities
@@
 two affine spaces $L_1,L_2 \subset K^n$.
-Moreover this class contains polyhedra in $K^n$.
+Moreover this class contains the polyhedra in $K^n$.
 
@@
   A set of the form $\mathcal{C} = \{x \in K \,|\, a \le \val(x) \le b\}$, for $a,b \in \R^*_+$,
-  is called \emph{annulus}. A product $\mathcal{C}_1 \times \mathcal{C}_2 \times \cdots \times \mathcal{C}_n \subset K^n$,
+  is called an \emph{annulus}. A product $\mathcal{C}_1 \times \mathcal{C}_2 \times \cdots \times \mathcal{C}_n \subset K^n$,
   where each $C_i \subset K$ is an annulus, is called a \emph{polyannulus}.
@@
   \mathcal{S}_{M^{(i)}} = \left\{(x_i,y_i) \in K^2 :
-  M^{(i)}(x_i,y_i) := \diag\left(\pi^a x_i, \pi^{-b} y_i,
+  M^{(i)}(x_i,y_i) := \diag\left(\pi^{-a} x_i, \pi^{b} y_i,
   \begin{bmatrix}
@@
     \begin{cases}
-      \val(\pi^a x_i) \ge 0 \\
-  \val(\pi^{-b} y_i) \ge 0\\
+      \val(\pi^{-a} x_i) \ge 0 \\
+  \val(\pi^{b} y_i) \ge 0\\
   \val(\pi^{-1}- \pi^{-1}) = +\infty \ge 0\\
@@
 
-We conclude proving that, in general, annuli are not spectrahedral.
+We conclude proving that, in general, annuli are not spectrahedra.
 

### 2025-12-09 issac2026/main.tex
commit by Simone

--- 2025-10-06 article/paper_padic_spec.tex
@@
-\documentclass[a4paper,oneside,10pt]{article}
-
-%%%\newenvironment{proof}{\hbox{}\vspace{-0.8cm} {\bf Proof:}}{\hfill $\Box$ \vspace{0.2cm}}
+\documentclass[sigconf]{acmart}
 
@@
 
-\newtheorem{theorem}{Theorem}[section]
-\newtheorem{lemma}[theorem]{Lemma}
-\newtheorem{proposition}[theorem]{Proposition}
-\newtheorem{corollary}[theorem]{Corollary}
-%\newtheorem{algorithm}[theorem]{Algorithm}
-\newtheorem{conjecture}[theorem]{Conjecture}
-\newtheorem{condition}[theorem]{Condition}
-\newtheorem{definition}[theorem]{Definition}
-\newtheorem{assumption}[theorem]{Assumption}
-\newtheorem{remark}[theorem]{Remark}
-\newtheorem{problem}[theorem]{Problem}
-\newtheorem{example}[theorem]{Example}
-\newtheorem{notation}[theorem]{Notation}
-\usepackage{booktabs}
-
-\usepackage{geometry}
-\geometry{
- a4paper,
- %total={170mm,257mm},
- left=33mm,
- right=33mm,
- top=35mm,
- bottom=35mm
-}
-
-%\textheight235mm
-%\textwidth165mm
-%\voffset-10mm
-%\hoffset-12.5mm
-\parindent0.8cm
-\parskip0mm
-
 \usepackage{stmaryrd} %for double brackets
-
-%\usepackage{mathptmx}
-
-% updates
 
@@
 
-\usepackage{biblatex}
-\addbibresource{../rapport/bibstage.bib}
+%\usepackage{biblatex}
+%\addbibresource{../rapport/bibstage.bib}
 
-\title{\Large \bf On semidefinite-representable sets over valued fields}
+\title{On semidefinite-representable sets over valued fields}
 
-\begin{document}
+\author{Simone Naldi}
+\affiliation{
+    \institution{Université de Limoges, CNRS, XLIM}
+    \city{Limoges}
+    \country{France}
+}
 
-\author{Corentin Cornou$^{1}$, Simone Naldi$^{2}$ and Tristan Vaccon$^{2}$}
+\author{Tristan Vaccon}
+\affiliation{
+    \institution{Université de Limoges, CNRS, XLIM}
+    \city{Limoges}
+    \country{France}
+}
 
-\footnotetext[1]{ENS Paris-Saclay, Université Paris-Saclay, France.}
-\footnotetext[2]{Université de Limoges, CNRS, XLIM, UMR 7252, F-87000 Limoges, France.}
-%\footnotetext[3]{Sorbonne Université, CNRS, LIP6, Equipe PolSys, F-75005 Paris, France.}
+\author{Corentin Cornou}
+\affiliation{
+    \institution{}
+    \city{}
+    \country{France}
+}
 
-\date{Draft of \today}
+\copyrightyear{2026}
+\acmYear{2026}
+\setcopyright{cc}
+\setcctype{by}
+\acmConference[ISSAC '26]{International Symposium on Symbolic and Algebraic Computation}{Date}{Place}
+\acmBooktitle{International Symposium on Symbolic and Algebraic Computation (ISSAC '26), date, place}\acmDOI{}
+\acmISBN{}
 
-\maketitle
+%\begin{CCSXML}
+%<ccs2012>
+%   <concept>
+%       <concept_id>10010147.10010148.10010149.10010150</concept_id>
+%       <concept_desc>Computing methodologies~Algebraic algorithms</concept_desc>
+%       <concept_significance>500</concept_significance>
+%       </concept>
+% </ccs2012>
+%\end{CCSXML}
+
+%\ccsdesc[500]{Computing methodologies~Algebraic algorithms}
+
+\keywords{keywords}
 
 \begin{abstract}
-  \noindent
   Real polyhedra and real spectrahedra (or their projections) are respectively the feasible sets
@@
 
-%\tableofcontents
+\begin{document}
+\maketitle
 
-\section{Introduction}
-
-The study of polyhedra and of linear programming (LP) is at the heart of convex geometry and optimization, inasmuch as several optimization problems can be cast as, or relaxed to LP.
-An important generalization of LP is semidefinite programming (SDP), namely the problem of minimizing a linear function over the set of positive semidefinite affine combinations of some real symmetric matrices.
-The latter problem has interested the community of real algebraic geometry and polynomial optimization, mostly because of the relaxation method known as moment-SOS (or Lasserre) hierarchy \cite{henrion2020moment}.
-
-The main motivation for studying the effective aspects of SDP is the fact that, despite several properties of LP extend to SDP, the complexity status of SDP is, contrary to the LP case, widely open.
-Ramana's construction \cite{ramana1997exact} implies a series of general results: in the Blum-Shub-Smale real numbers machines model \cite{blum1989theory}, the feasibility of SDP is in $\text{NP} \cap \text{co-NP}$, whereas it is not known to be in NP in the Turing model; checking boundedness, attainability and optimality can be polynomially reduced to the feasibility of SDP \cite{ramana1997exact}.
-Assuming the input data belongs to an effective field $K$ (\emph{e.g.} $K = \QQ$) then a solution can be described and computed as element of a vector space over some algebraic extension of $K$.
-For exact computation, complexity bounds are known based either on general quantifier elimination \cite{ramana1997exact,porkolab1997complexity} and explicit algorithms exist based on a dedicated application of the so-called critical point method, and exploiting the determinantal structure of the constraints \cite{henrion2016exact,NALDI2018206}.
-A complexity analysis for the computation of an approximate solution of an SDP can be made based on the ellipsoid algorithm \cite{khachiyan1979polynomial,grotschel1981ellipsoid} or on interior-point methods \cite{de2016turing}; in this approximation framework, SDP is solvable in polynomial time in the input size (\emph{i.e.} matrix size, number of variables, bit size of the coefficients), $\log(\frac{1}{\varepsilon})$ (where $\varepsilon$ is the target precision) and $\log(\frac{R}{r})$, where $r,R$ are radii of balls respectively included in and containing the feasible set, cf.
-\cite{grotschel1981ellipsoid} or \cite[Thm.1.1]{de2016turing} (see also \cite[Sec.1.9]{deKlerk}).
-
-In this paper we consider the situation where input data are defined over fields $K$ with a prescribed valuation map $\val$ on $K$.
-In this context a polyhedron is defined as a set of vectors such that some linear forms have nonnegative or infinite vluation ({\it cf.} \Cref{def_polyhedra}).
-The prototype of valued field we target is the field of $p$-adic numbers with $p$-adic valuation.
-%%%\todo{Give motivations for p-adic precision of LP/SDP.}
-Similar generalizations have been recently proposed in the context of tropical geometry \cite{iriarte2022polyhedral} and tropical methods applied to non-archimedean semidefinite programming \cite{allamigeon2016solving,allamigeon_tropical_2020}.
-
-%\subsection{Context and motivations}
-%Il faudra entre autre mentionner (et peut être motiver l'approche p-adique) :
-%\begin{itemize}
-%\item les questions ouvertes de complexité concernant la programmation semidefinie (pas clair si NP $\cap$ co-NP
-%  dans le modele de Turing)
-%\item les questions ouvertes géométriques (Conjecture de Lax)
-%\end{itemize}
-%\subsection{Main results}
-
-%\newpage
-\section{Preliminaries}
-
-Throughout the paper, $(K,\val)$ refers to a complete valued field, namely $K$ is a field
-and $\val : K \twoheadrightarrow \Gamma \cup \{+\infty\}$ is a valuation on $K$, $\Gamma$ an
-ordered abelian group. The valuation is often assumed to be discrete ({\it i.e.} $\Gamma=\ZZ$)
-with $\pi \in K$ a uniformizer. The ring of integers of $K$ is
-$$
-\OK = \{x \in K : \val(x) \geq 0\},
-$$
-$\kappa = \OK/\mathfrak{m}_K$ its residue field, with
-$\mathfrak{m}_K = \{x \in K : \val(x) > 0\}$.
-For $k \in \N$, we write $O(\pi^k)$ for $\pi^k \OK$.
-A typical example of $K$ as above is the field of $p$-adic numbers 
-$\QQ_p$ equipped with the $p$-adic valuation. For this example, we 
-have $\OK = \ZZ_p$. Another example is the field of Laurent series
-$K=\QQ(\!(t)\!)$ equiped with $t$-adic valuation,
-in which case $\OK = \QQ \llbracket t \rrbracket$.
-We refer to \cite{Serre:1979,engler2005valued} for a
-general introduction to such fields
-and to \cite{caruso_computations_2017}
-for an introduction to effective computations over $p$-adic numbers.
-
-The $K$-vector space of polynomials of degree $\leq d$ on $x=(x_1,\ldots,x_n)$
-with coefficients in $K$ is denoted by $K[x]_{d}$. The ring of matrices of
-size $p \times q$ with entries in a ring $R$ is $R^{p \times q}$ and the general
-linear group in $R^{n \times n}$ is $\GL_n(R)$.
-For the sake of ease of writing, block-diagonal matrices with blocks
-$B_1,\ldots,B_d$ are denoted by $\diag(B_1, \ldots, B_d)$, the null matrix of
-size $p \times q$ by ${\bf 0}_{p,q}$, and the identity matrix by $I_t$.
-
-We recall the definition of Smith Normal Form, in our context.
-\begin{definition}[Smith Normal Form]\label{smith_nf}
-  Assume $(K,\val)$ is a discrete valued field with uniformizer $\pi$.
-  Let $M \in K^{m \times n}$ be of rank $r$. There exist unique integers
-  $a_1 \leq \cdots \leq a_r$, and
-  matrices $P \in \GL_n(\OK)$ and $Q \in \GL_m(\OK)$, such that
-  $$
-  \mathrm{SNF}(M) := QMP^{-1} = \diag(\pi^{a_1}, \pi^{a_2}, \ldots, \pi^{a_r}, {\bf 0}_{m-r,n-r}).
-  $$
-  The matrix $\mathrm{SNF}(M)$ is called the \emph{Smith Normal Form (SNF)} of $M$, and the elements $\pi^{a_i}$ the
-  \emph{invariant factors}.
-\end{definition}
-\begin{remark}
-  The valuation of the first invariant factor of $\mathrm{SNF}(M)$ of a matrix
-  $M \in K^{n \times n}$ is the minimum of the valuations of the entries of
-  $M$. In particular, $\mathrm{SNF}(M) \in \OK^{n \times n}$.
-\end{remark}
-
-Let us now give a short introduction to classical ({\it i.e.} real) polyhedra and spectrahedra.
-Let $\sym_d(\R) \subset \R^{d\times d}$ be the vector space of $d \times d$ real symmetric
-matrices.
-A matrix $M \in \sym_d(\R)$ is \emph{positive semidefinite} ($M \succeq 0$) whenever the quadratic form $x \mapsto x^TMx$ is nonnegative for all $x\in \R^n$.
-By the Spectral Theorem, $M \succeq 0$ if and only if the eigenvalues of $M$ are nonnegative, and this is equivalent to all the principal minors of $M$ being nonnegative.
-The set $\sym_d^+(\R) \subset \sym_d(\R)$ of positive semidefinite matrices is a closed convex cone with non-empty interior in $\sym_d(\R)$.
-
-Let $A_0,A_1,\ldots,A_n \in \sym_d(\R)$, and let $\calL = A_0+\span{A_1,\ldots,A_n}$ be the affine space
-containing $A_0$ and with direction the vector space spanned by $A_1,\ldots,A_n$ (which we might assume
-to be linearly independent). The intersection
-$$
-\calL \cap \sym_d^+(\R) = \left\{A(x) := A_0+\sum_i x_i A_i \in \sym_d(\R) :
-A(x) \succeq 0\right\},
-$$
-or equivalently, its pre-image $S = \{x \in \R^n : A(x) \succeq 0\}$ under the map $x \mapsto A(x)$, is called
-a \emph{real spectrahedron}. As (linear preimage of) affine sections of $\sym_d^+(\R)$, real spectrahedra
-are closed convex sets, but might have empty interior in $\calL$ (resp. in $\R^n$).
-Moreover, they are basic semialgebraic sets, indeed they are defined by sign conditions on the principal
-minors of the defining matrix as well as sign conditions on the coefficients of its characteristic polynomial
-(cf. \Cref{ell3}).
-
-\begin{example}\label{ell3}
-  Let $d=n=3$. The $3$-elliptope is the three-dimensional spectrahedron given by
-  $$
-  \mathcal{E}_3 :=
-  \left\{
-  x
-  \in \R^3 :
-  \begin{bmatrix}
-    1 & x_1 & x_2 \\
-    x_1 & 1 & x_3 \\
-    x_2 & x_3 & 1
-  \end{bmatrix}
-  \succeq 0
-  \right\}
-  =
-  \left\{
-  x
-  \in \R^3 :
-  \begin{array}{r}
-    3-x_1^2-x_2^2-x_3^2 \geq 0 \\
-    1+2x_1x_2x_3-x_1^2-x_2^2-x_3^2 \geq 0
-  \end{array}
-  \right\}.
-  $$
-  The polynomials on the right are the (non-constant) coefficients of the univariate polynomial
-  $p(t) = \det(A(x)+t I_3)$,
-  whose roots are the opposites of the eigenvalues of the defining matrix. Equivalently $\mathcal{E}_3$
-  is defined by positivity of the principal minors of the defining matrix:
-  $$
-  1-x_1^2 \geq 0, \,\,\, 1-x_2^2 \geq 0, \,\,\, 1-x_3^2 \geq 0 \,\,\, \text{ and } \,\,\, 1+2x_1x_2x_3-x_1^2-x_2^2-x_3^2 \geq 0.$$ \exend
-\end{example}
-
-The optimization problem of miminizing a linear function over a real spectrahedron is called \emph{semidefinite programming} (SDP).
-%Given $c \in \R^n$ and $A_0,A_1,\ldots,A_n \in \sym_d(\R)$, the corresponding semidefinite program is defined (in standard dual form) as
-%\begin{equation}
-%  \label{SDP}
-%\begin{array}{rcll}
-%  p^* & := & \inf_{x \in \R^n} & \left\langle c, x \right\rangle \\
-%  &    & \text{s.t.}         & A_0+\sum_{i=1}^n x_i A_i \succeq 0.
-%\end{array}
-%\end{equation}
-{\it Real polyhedra} (subsets of $\R^n$ defined by finitely many affine inequalities) are special cases of real
-spectrahedra, where the defining matrices $A_0, \ldots, A_n$ can be chosen diagonal, so that
-$A = \diag(\ell_1,\ldots, \ell_d)$. In other words, SDP is a generalization of Linear Programming (LP).
-
-% IN INTRODUCTION
-%In a fixed-precision model of computation, SDP is solvable in polynomial time in the input size (matrix size,
-%number of variables, bit size of the coefficients), in $\log(\frac{1}{\varepsilon})$ (where $\varepsilon$ is the
-%precision) and $\log(\frac{1}{R})$, where $R$ is an {\it a priori} upper bound on the norm of a solution,
-%cf. \cite[Sec.1.9]{deKlerk}. In exact arithmetic, the complexity status of SDP is essentially open but complexity
-%bounds are known based either on general quantifier elimination \cite{ramana1997exact,porkolab1997complexity}
-%or by exploiting the determinantal structure of the constraints \cite{henrion2016exact}.
-
-A more general class of convex semialgebraic sets are obtained by linear projections of real spectrahedra
-called \emph{semidefinite representable sets}: these are sets of the form
-$$
-\left\{x = \left[\begin{smallmatrix} x_1 \\ \vdots \\ x_n \end{smallmatrix}\right] \in \R^n : \exists\,y\in\R^m, \, A_0 + \sum_{i=1}^n x_i A_i + \sum_{j=1}^m y_j B_j \succeq 0\right\}.
-$$
-When $m>0$, the set is also called a \emph{spectrahedral shadow}.
-
-\begin{example}
-\label{fermat_quartic}
-The basic closed semialgebraic set $\mathcal{R} = \{(x_1,x_2) \in \R^2 : 1-x_1^4-x_2^4 \geq 0\}$ is not a spectrahedron
-but it is semidefinite representable:
-$$
-\mathcal{R} = \left\{\begin{bmatrix} x_1 \\ x_2 \end{bmatrix} \in \R^2 :
-\exists\,
-\begin{bmatrix} y_1 \\ y_2 \end{bmatrix} \in \R^2, \,
-\diag\left(
-\begin{bmatrix}
-  1+y_1 & y_2 \\
-  y_2 & 1-y_1
-\end{bmatrix},
-\begin{bmatrix}
-  1 & x_1 \\
-  x_1 & y_1
-\end{bmatrix},
-\begin{bmatrix}
-  1 & x_2 \\
-  x_2 & y_2
-\end{bmatrix}
-\right)
-\succeq 0
-\right\}
-$$
-\end{example}
-
-\section{Polyhedra}
-
-In this section, we define polyhedra over a complete discrete valued field $K$ with valuation $\val$ and a uniformizer $\pi$, and we prove that the class of polyhedra is closed under linear transformations, as in the real case.
-We end by presenting an algorithm for solving linear optimization problems over $K$.
-
-\begin{definition}
-  \label{def_polyhedra}
-  A \emph{polyhedron} is a subset $\PP \subset K^n$ of the form
-  $$
-  \PP = \{x \in K^n : \val(\ell_i(x)) \geq 0, i=1,\ldots,d \text{ and }
-  \val(m_j(x)) = +\infty, j=1,\ldots,e\},
-  $$
-  for some $\ell_1,\ldots,\ell_d,m_1,\ldots,m_e \in K[x]_1$.
-\end{definition}
-
-%%We recall that that the smallest affine space of $K^n$ containing a set $S \subset K^n$ is called its \emph{affine hull} and denoted $\aff{S}$.
-The assumption on forms $\ell_i$ in \Cref{def_polyhedra} implies that the constraint $\val(m_1 \oplus \cdots \oplus m_e) = +\infty$ defines exactly the affine hull of $P$, in other words $\aff{P} = \{x \in K^n : m_j(x) = 0, j=1,\ldots,e\}$ \simone{(il nous faudrait une preuve, du genre: $\val(m(x))=+\infty$ pour tout $x \in P$ si et seulement si $m$ est une combinaison affine de $m_1,\ldots,m_e$.)}
-%%The \emph{dimension} of $P$ is defined as the dimension of $\aff{P}$ (for $e=0$, $\aff{P}=K^n$ and $P$ has dimension $n$).
-The \emph{relative interior} of $P$ is defined as $\relint{P} = \{x \in P : \val(\ell_1 \oplus \cdots \oplus \ell_d) < +\infty\}$ (\simone{pas clair si besoin de dimension et relint}).
-Remark that \Cref{def_polyhedra} includes the case $d=0$ corresponding to affine spaces, as in the real case.
-Moreover by definition the class of polyhedra is closed under intersection. Without loss of generality, one may
-assume in \Cref{def_polyhedra} that for every $i=1,\ldots,d$ there exists $x \in P$ such that
-$\val(\ell_i(x))<+\infty$.
-
-\begin{example}
-  The \emph{closed unit ball} $\OK^n=B_\infty(K^n)$ in $K^n$ for the supremum norm $||\cdot||_{\infty}$ is the
-  polyhedron defined as the set of $x=(x_1,\ldots,x_n) \in K^n$ such that $||x||_{\infty} =
-  \max_i\{x_i\} \leq 1$, in other words, such that $\val(x_i) \geq 0$, for all $i=1, \ldots, n$.
-  In other words, $\OK^n$ is the polyhedron in $K^n$ defined by the affine polynomials
-  $\ell_i(x)=x_i$, $i=1,\ldots, n$, and $e=0$. %%%%%(its affine hull is indeed the whole $K^n$).
-\end{example}
-
-\subsection{Projections and direct image of polyhedra}
-
-%{\color{blue} Normalement avec la nouvelle definition, ça devrait aller, il faut par contre
-%  partir d'un polyedre defini aussi par des égalités. Peut être il faudrait aussi
-%  diviser la proposition en plusieures parties pour la rendre plus lisible, par exemple une
-%  première proposition avec la projection.}
-
-In this section, we prove that the class of polyhedra is stable
-by applying affine maps:
-
-\begin{theorem}[DI] 
-Let $f : K^n \to K^m$ be an affine map and $\PP$ a polyhedron in $K^n.$
-Then $f(\PP)$ is a polyhedron. \label{theo:DI}
-\end{theorem}
-
-We prove the result by reducing to particular cases.
-The strategy to deduce the main theorem DI 
-is given in \Cref{fig:di-properties}.
-
-\begin{figure}[!ht] 
-\centering
-\begin{tikzpicture}[
-  node distance=1cm and 1cm,
-  box/.style={draw, rounded corners, minimum width=2.2cm, minimum height=1cm, align=center},
-  thickarrow/.style={->, >=Stealth, line width=1.2pt},
-]
-% Nodes
-\node[box] (DIdiag) {DI${}_{diag}$};
-\node[box, right=of DIdiag] (DIproj) {DI${}_{proj}$};
-\node[box, right=of DIproj] (DIl) {DI${}_{l}$};
-\node[box, right=of DIl] (DIi) {DI${}_{i}$};
-\node[box, right=of DIi] (DI) {DI};
-\node[box, above=of DIproj] (DIimm) {DI${}_{imm}$};
-\node[box, below=of DIproj] (DIaut) {DI${}_{aut}$};
-% Arrows
-\draw[thickarrow] (DIdiag) -- (DIproj);
-\draw[thickarrow] (DIproj) -- (DIl);
-\draw[thickarrow] (DIl) -- (DIi);
-\draw[thickarrow] (DIi) -- (DI);
-\draw[thickarrow] (DIimm) -- (DIl);
-\draw[thickarrow] (DIaut) -- (DIl);
-\end{tikzpicture}
-\caption{Strategy of proof of Theorem \ref{theo:DI}.}
-\label{fig:di-properties}
-\end{figure}
-
-We begin with the case of linear maps in $\GL_n(O_K)$.
-
-\begin{lemma}[DI${}_{aut}$]
-Let $f \in GL_n(O_K)$ and $\PP$ a polyhedron in $K^n$.
-Then $f(\PP)$ is a polyhedron. \label{lem:DIaut}
-If in addition, $\PP$ is defined only by inequalities,
-then so is $f(\PP)$.
-\end{lemma}
-\begin{proof}
-If $\PP$ is defined (in matrix form) by \[\left\lbrace X \in K^n,  AX+B \geq 0, CX+D=0 \right\rbrace\] and $U$ is the matrix of $f$ in the canonical basis of $K^n$, 
-let $\Qc$ be defined by \[\left\lbrace Y \in K^n,  AU^{-1} Y+B \geq 0, CU^{-1} Y+D=0 \right\rbrace.\]
-Then it is clear that $\Qc$ is a polyhedron and $f(\PP)=\Qc.$
-It is also clear that if $\PP$ is defined only by inequalities,
-then so is $f(\PP)$.
-\end{proof}
-
-If $f$ is diagonal, we can also conclude.
-
-\begin{lemma}[DI${}_{diag}$]
-Let $f : K^n \to K^n$ be a linear map and $\PP$ a polyhedron in $K^n$ defined only by inequalities. We assume that the matrix of $f$ in the canonical basis of $K^n$ is diagonal.
-Then $f(\PP)$ is a polyhedron. \label{lem:DIdiag}
-\end{lemma}
-\begin{proof}
-As in the proof of Lemma \ref{lem:DIaut} DI${}_{aut}$, a trivial change
-of variables is enough to conclude.
-\end{proof}
-
-We now treat the case where $f$ is a projection erasing the last coordinate.
-
-\begin{lemma}[DI${}_{proj}$]
-Let $f : K^n \to K^n, \: (x_1,\dots,x_{n-1},x_n) \mapsto (x_1,\dots,x_{n-1})$ and $\PP$ a polyhedron in $K^n$ defined only by inequalities. 
-Then $f(\PP)$ is a polyhedron defined only by inequalities. \label{lem:DIproj}
-\end{lemma}
-\begin{proof}
-We assume that $\PP \neq \emptyset$.
-Let us write the conditions defining $\PP$
-in matrix form:
-$\val(A X+B) \geq 0$ 
-with $A \in M_{q,n}(K)$, $B \in K^q$
-and $X=(x_1,\dots,x_n)^\intercal$.
-
-We can compute a Smith Normal Form
-of the $q \times (n-1)$ matrix defined by the 
-$n-1$ first columns of $A$
-to obtain a decomposition of the form:
-\[ Q_A A P_A^{-1} = \begin{bmatrix}
-\delta_1	& 		& 			&   &		 &  &a_1	\\
-			& \ddots& 			& 0	&		 &	&		\\
-			&		& \delta_l  &   & 		 &	&		\\
-			&		&			&0  & 		 &	& 		\\
-			&		&			&   & \ddots &	&		\\
-			&		&			&	&		 & 0&a_{n-1} \\
-			&		&			&	&		 &	&a_n 	\\
-			&		&			&	&		 &	&    	\\
-			&		&			&	&		 &	&a_q 	\\			
-\end{bmatrix},\]
-with $Q_A \in \GL_q(\OK)$ and $P_A \in \GL_n(\OK)$ such that $P_A(e_n)=e_n.$
-
-Multiplying on the left by $Q_A^{\pm 1}$ does not
-modify whether the valuation inequalities are satisfied.
-Moreover, thanks to Lemma \ref{lem:DIaut} DI${}_{aut}$,
-$\PP$ can be written
-$\PP=P_A^{-1}(\PP_2)$ for some polyhedron $\PP_2 \subset K^n$
-and we are reduced to proving that
-$f(\PP_2)$ is a polyhedron for $p$ the projection
-$K^n \rightarrow K^{n-1}$ and $\PP_2$
-defined by the following linear matrix inequality (for some $B_2 \in K^q$):
-\[  \begin{bmatrix}
-\delta_1	& 		& 			&   &		 &  &a_1	\\
-			& \ddots& 			& 0	&		 &	&		\\
-			&		& \delta_l  &   & 		 &	& \vdots\\
-			&		&			&0  & 		 &	& 		\\
-			&		&			&   & \ddots &	&		\\
-			&		&			&	&		 & 0&a_{n-1} \\
-			&		&			&	&		 &	&a_n 	\\
-			&		&			&	&		 &	& \vdots   	\\
-			&		&			&	&		 &	&a_q 	\\			
-\end{bmatrix} \begin{bmatrix} x_1 \\ \\ \\ \\ \\ \vdots \\ \\ \\ \\ x_n \\ \end{bmatrix} + B_2 \geq 0.\]
-
-We remark that 
-$a_s x_n + b_s \geq 0$
-if and only if $x_n = -a_s^{-1} b_s + O(\pi^{- \val(a_s)}).$
-This exactly corresponds to $x_n \in B(-a_s^{-1} b_s,\val(a_s)).$
-Since the conditions have to be compatible (we have assumed
-$\PP$ not empty), and thanks to ultrametricity,  
-the intersection of these conditions for 
-$s \in \llbracket l+1,q \rrbracket$
-is then given by the smallest of these balls.
-Let us assume it is the one defined for $l=n.$
-The only condition on $x_n$
-is then $\val(a_nx_n +b_n) \geq 0.$
-
-Thanks to Lemma \ref{lem:DIdiag} DI${}_{diag}$,
-we can further assume that the $\delta_i$'s and $a_n$ are all $1$'s
-and are reduce to $\PP_2$ defined by the linear matrix inequality:
-\[  \begin{bmatrix}
-1	& 		& 			&   &		 &  &a_1	\\
-			& \ddots& 			& 0	&		 &	&		\\
-			&		& 1  &   & 		 &	& \\
-			&		&			&0  & 		 &	& 	\vdots	\\
-			&		&			&   & \ddots &	&		\\
-			&		&			&	&		 & 0&a_{n-1} \\
-			&		&			&	&		 &	&1 	\\
-
-\end{bmatrix} \begin{bmatrix} x_1 \\ \\  \\ \\ \vdots \\  \\ \\ x_n \\ \end{bmatrix} + \begin{bmatrix} b_1 \\ \\ \\  \\ \vdots  \\ \\ \\ b_n \\ \end{bmatrix}  \geq 0.\]
-Finally, we can also assume that, up to a permutation of the variables, $\val(a_1)= \min_{i=1}^{n-1} \val(a_i).$
-We distinguish two cases: $\val(a_1) \geq 0$ and $\val(a_1)<0.$
-
-Let us first assume that $\val(a_1) \geq 0$.
-
-Let $x \in \PP_2$.
-Then $x_n=-b_n+O(1)$
-and $x_1+a_1 x_n+b_1=O(1).$
-Consequently, $x_1-a_1 b_n +b_1=O(1)+O(\pi^{\val(a_1)})=O(1).$
-Similarly, for all $i \in \llbracket 2,n-1 \rrbracket,$
-$x_i-a_ib_n+b_i=O(1)+O(\pi^{\val(a_i)})=O(1).$
-
-We define the polyhedron $\Qc \subset K^{n-1}$ by the following inequalities:
- for all $i \in \llbracket 1,n-1 \rrbracket,$
-$\val(x_i-a_ib_n+b_i) \geq 0$.
-
-Then the previous computations prove that $p(\PP_2)\subset \Qc.$
-Conversely, let $(x_1,\dots,x_{n-1}) \in \Qc.$
-Then let $x_n := -b_n.$
-
-We check that for $i \in \llbracket 1,n-1 \rrbracket,$
-$x_i+a_ix_n+b_i=x_i-a_ib_n+b_i=O(1),$
-and $x_n+b_n=O(1)$. Hence $(x_1,\dots,x_n) \in \PP_2$
-which means that $(x_1,\dots,x_{n-1}) \in p(\PP_2).$
-Thus $p(\PP_2)= \Qc$ and $p(\PP_2)$ is a polyhedron.
-
-We now deal with the second case, with $\val(a_1)<0.$
-Let $x \in \PP_2$.
-Then $x_n=-b_n+O(1)$
-and $x_1+a_1 x_n+b_1=O(1).$
-Consequently, $x_1-a_1 b_n +b_1=O(1)+O(\pi^{\val(a_1)})=O(\pi^{\val(a_1)}).$
-Thus $a_1^{-1}x_1- b_n +a_1^{-1}b_1=O(1)$.
-%and $x_n=-a_1^{-1}(x_1+b_1)+O(1).$
-In addition, $x_n=-a_1^{-1}(x_1+b_1)+O(\pi^{-\val(a_1)}).$
-We plug this equality in 
-$x_i+a_i x_n+b_i=O(1)$ to get
-$x_i-a_1^{-1}a_i(x_1+b_1)+b_i=O(1)+O(\pi^{\val(a_i)-\val(a_1)})=O(1)$
-using that $\val(a_i) \geq \val (a_1).$
-
-We define the polyhedron $\Qc \subset K^{n-1}$ by the following inequalities:
-$\val(a_1^{-1}x_1- b_n +a_1^{-1}b_1) \geq 0$ and for all $i \in \llbracket 2,n-1 \rrbracket,$
-$\val(x_i-a_1^{-1}a_i(x_1+b_1)+b_i) \geq 0.$
-
-Then the previous computations prove that $p(\PP_2)\subset \Qc.$
-Conversely, let $(x_1,\dots,x_{n-1}) \in \Qc.$
-Let $x_n := -a_1^{-1}(x_1+b_1).$
-Then
-$x_1+a_1 x_n+b_1=0=O(1).$
-Let $i \in \llbracket 2,n-1 \rrbracket,$
-then $x_i+a_i x_n+b_i=x_i-a_1^{-1}a_i(x_1+b_1)+b_i=O(1)$
-since $(x_1,\dots,x_{n-1}) \in \Qc.$
-Finally, 
-$x_n+b_n=-a_1^{-1}(x_1+b_1)+b_n=O(1)$ thanks to the inequality satisfied by $x_1.$
-Hence $(x_1,\dots,x_n) \in \PP_2$
-which means that $(x_1,\dots,x_{n-1}) \in p(\PP_2).$
-Thus $p(\PP_2)= \Qc$ and $p(\PP_2)$ is a polyhedron,
-and it has been proved in both cases.
-
-Therefore, $p(\PP)$ is a polyhedron (and inequalities are enough to define $p(\PP_2)$ as a polyhedron).
-\end{proof}
-
-\begin{lemma}[DI${}_{imm}$]
-  Let $f : K^l \to K^n$ be the immersion $(x_1,\dots, x_l) \mapsto (x_1,\dots, x_l,0,\dots, 0)$ and $\PP$
-  a polyhedron in $K^l$. Then $f(\PP)$ is a polyhedron. \label{lem:DIimm}
-\end{lemma}
-\begin{proof}
-Adding the equalities $x_{l+1}=0, \dots, x_n=0$ to the equations and inequations in
-$x_1,\dots, x_l$ defining $\PP$, the result is clear.
-\end{proof}
-
-We can now generalize to linear mappings and
-polyhedron defined only by inequalities.
-
-\begin{proposition}[DI${}_l$]
-Let $f : K^n \to K^m$ be a linear map and $\PP$ a polyhedron in $K^n$ defined only by inequalities.
-Then $f(\PP)$ is a polyhedron. \label{prop:DIl}
-\end{proposition}
-\begin{proof}
-We assume that $\PP \neq \emptyset$, and we identify $f$ with its matrix in $\allmat_{n,m}(K)$.
-We assume that $\PP$ is defined as $\left\lbrace x \in K^n : \val (l_i (x) ) \geq 0, \textrm{ for } i \in I\right\rbrace$ for some
-finite sets $I \subset \N$ and $l_i \in K[x]_1$, for $i \in I$ .
-
-Thanks to Definition \ref{smith_nf}, (the matrix of) $f$
-can be written $f=Q^{-1} \Delta P$
-with $P \in \GL_n(\OK),$ $Q \in \GL_m(\OK)$
-and $\Delta = \mathrm{SNF}(f)\in \allmat_{n,m}(K)$ of the form $\diag(\lambda_1, \ldots, \lambda_r, {\bf 0}_{\min(m,n)-r})$
-  where ${\bf 0}_{\min(m,n)-r}$ is a null square matrix of size $\min(m,n)-r$ for $\lambda_1,\dots,\lambda_r$ non-zero and $r \in \N.$
-
-By Lemma \ref{lem:DIaut} DI${}_{aut}$,
-$P(\PP)$ is a polyhedron defined only by inequalities.
-
-Let $\Qc= P(\PP)$
-We now prove that $\Delta (\Qc)$ is a polyhedron.
-One can write that $\Delta$ is the composition
-of the immersion 
-$K^r \rightarrow K^n$
-$(x_1,\dots,x_r)\mapsto (x_1,\dots,x_r,0,\dots,0),$ 
- the diagonal invertible mapping
-$K^l \rightarrow K^l$,
-$(x_1,\dots,x_r)\mapsto (\delta_1,\dots,\delta_r x_r)$,
-and the projections
-$(x_1,\dots,x_{r+1})\mapsto (x_1,\dots,x_{r}),$
- $(x_1,\dots,x_{r+2})\mapsto (x_1,\dots,x_{r+1}),$
- $\dots,$
- $(x_1,\dots,x_{n})\mapsto (x_1,\dots,x_{n-1}).$
- Thus, thanks to Lemmas \ref{lem:DIimm} DI${}_{imm}$, \ref{lem:DIproj} DI${}_{proj}$ and \ref{lem:DIaut} DI${}_{aut}$, $\Delta (\Qc)$ is a polyhedron.
- One can note that it is only when applying the immersion as the last mapping in the composition chain that equalities are needed to define the last polyhedron.
-
-Finally, thanks to Lemma \ref{lem:DIaut} DI${}_{aut}$,
-$Q^{-1} \left( \Delta (\Qc) \right)$ is a polyhedron.
-This concludes the proof.
-\end{proof}
-
-We can generalize from linear mappings to affine mappings.
-\begin{proposition}[DI${}_i$]
-Let $f : K^n \to K^m$ be an affine map and $\PP$ a polyhedron in $K^n$ defined only by inequalities.
-Then $f(\PP)$ is a polyhedron. \label{prop:DIi}
-\end{proposition}
-\begin{proof}
-Let $P \in K^m$. One can see by immediate change of variables that $\Qc$ is a polyhedron in $K^m$ if and only if
-$\Qc+P$ is a polyhedron in $K^m$.
-Consequently, translating by $-f(O)$ in the codomain, one can reduce
-to the case of Proposition \ref{prop:DIl}   DI${}_l$.
-\end{proof}
-
-We can now conclude with the proof of the main result
-of this section.
-
-\begin{proof}[Proof of Theorem \ref{theo:DI} DI]
-Here, $f : K^n \to K^m$ is an affine map and $\PP$ a polyhedron in $K^n.$
-Let us write $\PP = \PP_I \cap \PP_E$
-with $\PP_I := \left\lbrace X \in K^n,  AX+B \geq 0 \right\rbrace$
-and $\PP_E := \left\lbrace X \in K^n,  CX+D=0 \right\rbrace = P + \overrightarrow{\PP_E}.$ 
-Then $f(\PP) = f_{\PP_E}(\PP_I).$
-
-By a translation of $-P$ in $K^n$, we can assume that
-$\PP_E$ is a linear vector space: we are reduced to proving that, if $\tilde{f}: \PP_E \to K^m$ is an affine map and $\PP_I$ is a polyhedron in the vector space $\PP_E$ defined only by inequalities, then  $\tilde{f}(\PP_I)$ is a polyhedron.
-This is the case thanks to Proposition \ref{prop:DIi} DI$_i$
-and the theorem is proven.
-\end{proof}
-
-%
-%In this section we show that the image of a polyhedron by a linear mapping is a polyhedron,
-%and discuss some consequences.
-%We first prove the result in the cases of authomorphisms of $\OK^n$ and diagonal endomorphisms of $K^n$.
-%Then we use these particular cases to prove the result for projections of the form
-%$(x_1,\dots,x_n) \mapsto (x_1,\dots, x_{n-1})$ and finally for the general case.
-%
-%\begin{remark}
-%  Let $f : K^n \to K^m$ be a linear map and let
-%  $P = \{x \in K^n : \val(l_i(x)) \geq 0, m_i(x) = 0, 1 \leq i \leq d, 1 \leq j \leq e\}$.
-%  Then $P = P_I \cap P_E$ where $P_I := \{x \in K^n : \val(l_i(x)) \geq 0, 1 \leq i \leq d\}$
-%  and $P_E := \{x \in K^n : m_j(x) = 0, 1 \leq j \leq e\}$.
-%
-%  Thus we have\footnote{\simone{Ça n'est pas vrai en général, il faut que $f$ soit injective.
-%    Il faut peut être d'abord factoriser $f = g \circ h$ avec $h : K^n \to im(f)$ et
-%    $g : im(f) \subset K^m$.}}
-%  $f(P) = f(P_I) \cap f(P_E)$. However $P_E$ is either empty or an affine subspace of
-%  $K^n$ and therefore $f(P_E)$ is either empty or an affine subspace of $K^m$, so it is a polyhedron.
-%  Hence, as the class of polyhedra is closed under intersection, in order to prove that
-%  $f(P)$ is a polyhedron, it is sufficient to prove that this holds for $f(P_I)$.
-%\end{remark}
-%
-%Therefore below we consider polyhedra of the form as in \Cref{def_polyhedra} with $e=0$.
-%
-%\begin{proposition}\simone{l'enoncé est incomplet}
-%  Let $P \subset K^n$ be a polyhedron and let $f : K^n \to K^n$ be a linear mapping.
-%  If $f \in \GL_n(\OK)$ or if there exists $\lambda_1, \dots, \lambda_n \in K$ such that
-%  $(x_1,\dots,x_{n-1}, x_n) \mapsto (x_1,\dots, x_{n-1})$.
-%\end{proposition}
-%
-%\begin{proof}
-%We assume that $\PP \neq \emptyset$
-%As discussed above we can assume that
-%$\PP = \left\lbrace x \in K^n : \val (l_i (x) ) \geq 0,\textrm{ for } i \in I \right\rbrace$ for some
-%finite set $I \subset \N$ and $l_i \in K[x]_1$, for $i \in I$ .
-%
-%First, if $f \in \GL_n(\OK)$ then, $x \in f(P)$ if and only if for all $i \in I$, 
-%$\val(l_i (f^{-1}(x))) \geq 0$.
-%The $l_i \circ f^{-1}$ are clearly in $K[x]_1$
-%and $f(P)$ is a polyhedron.
-%
-%Similarly, if $f:K^n \rightarrow K^n$ is of the form
-%$f(x_1,\dots,x_n)=(\lambda_1 x_1,\dots,\lambda_n x_n)$
-%for some $\lambda_1,\ldots, \lambda_n \in K$,
-%then of course $f(P)$
-%can be defined by $\val (\widetilde{l_i}(x)) \geq 0$, $i \in I$
-%with the $\widetilde{l_i}$'s obtained from the $l_i$'s by an
-%obvious change of variables.
-%\end{proof}
-%
-%The two above results\footnote{\simone{il y en an un}}
-%allows us to demonstrate the following proposition, which we will use to prove the general case. 
-%
-%\begin{proposition}
-%      Let $\PP \subset K^n$ be a polyhedron and $p : K^n \to K^{n-1}$ be the projection $p : (x_1,\dots,x_{n-1},x_n) \mapsto (x_1, \dots, x_{n-1})$.
-%       Then $p(\PP)$ is a spectrahedron.
-%\end{proposition}
-%
-%
-%\begin{proof}
-%      
-%We assume that $\PP \neq \emptyset$.
-%As discussed above we can assume that
-%  $\PP = \left\lbrace x \in K^n : \val (l_i (x) ) \geq 0,\textrm{ for } i \in I \right\rbrace$ for some
-%finite set $I \subset \N$ and $l_i \in K[x]_1$, for $i \in I$ .
-%
-%Let us write the conditions defining $\PP$
-%in matrix form:
-%$\val(A X+B) \geq 0$ and 
-%with $A \in M_{q,n}(K)$, $B \in K^q$
-%and $X=(x_1,\dots,x_n)^\intercal$. 
-%
-%
-%We can compute a Smith Normal Form
-%of the $q \times (n-1)$ matrix defined by the 
-%$n-1$ first columns of $A$
-%to obtain a decomposition of the form:
-%\[ Q_A A P_A^{-1} = \begin{bmatrix}
-%\delta_1	& 		& 			&   &		 &  &a_1	\\
-%			& \ddots& 			& 0	&		 &	&		\\
-%			&		& \delta_l  &   & 		 &	&		\\
-%			&		&			&0  & 		 &	& 		\\
-%			&		&			&   & \ddots &	&		\\
-%			&		&			&	&		 & 0&a_{n-1} \\
-%			&		&			&	&		 &	&a_n 	\\
-%			&		&			&	&		 &	&    	\\
-%			&		&			&	&		 &	&a_q 	\\			
-%\end{bmatrix},\]
-%with $Q_A \in \GL_q(\OK)$ and $P_A \in \GL_n(\OK)$ such that $P_A(e_n)=e_n.$
-%
-%Multiplying on the left by $Q_A^{\pm 1}$ does not
-%modify whether the valuation inequalities are satisfied.
-%Moreover, thanks to our previous on the case when $f$ is an automorphism,
-%$\PP$ can be written
-%$\PP=P_A^{-1}(\PP_2)$ for some polyhedron $\PP_2 \subset K^n$
-%and we are reduced to proving that
-%$f(\PP_2)$ is polyhedron for $p$ still the canonical projection
-%$K^n \rightarrow K^{n-1}$ and $\PP_2$
-%defined by the linear matrix inequality (for some $B_2 \in K^q$):
-%\[  \begin{bmatrix}
-%\delta_1	& 		& 			&   &		 &  &a_1	\\
-%			& \ddots& 			& 0	&		 &	&		\\
-%			&		& \delta_l  &   & 		 &	& \vdots\\
-%			&		&			&0  & 		 &	& 		\\
-%			&		&			&   & \ddots &	&		\\
-%			&		&			&	&		 & 0&a_{n-1} \\
-%			&		&			&	&		 &	&a_n 	\\
-%			&		&			&	&		 &	& \vdots   	\\
-%			&		&			&	&		 &	&a_q 	\\			
-%\end{bmatrix} \begin{bmatrix} x_1 \\ \\ \\ \\ \\ \vdots \\ \\ \\ \\ x_n \\ \end{bmatrix} + B_2 \geq 0.\]
-%
-%
-%
-%We remark that 
-%$a_s x_n + b_s \geq 0$
-%if and only if $x_n = -a_s^{-1} b_s + O(\pi^{- \val(a_s)}).$
-%This exactly corresponds to $x_n \in B(-a_s^{-1} b_s, 2^{\val(a_s)}).$
-%Since the conditions have to be compatible (we have assumed
-%$\PP$ not empty), and thanks to ultrametricity,  
-%the intersection of these conditions for 
-%$s \in \llbracket l+1,q \rrbracket$
-%is then given by the smallest of these balls.
-%Let us assume it is the one defined for $l=n.$
-%The only condition on $x_n$
-%is then $\val(a_nx_n +b_n) \geq 0.$
-%
-%Thanks to the above discussion on diagonal mapping,
-%we can further assume that the $\delta_i$'s and $a_n$ are all $1$'s
-%and are reduce to $\PP_2$ defined by the linear matrix inequality :
-%\[  \begin{bmatrix}
-%1	& 		& 			&   &		 &  &a_1	\\
-%			& \ddots& 			& 0	&		 &	&		\\
-%			&		& 1  &   & 		 &	& \\
-%			&		&			&0  & 		 &	& 	\vdots	\\
-%			&		&			&   & \ddots &	&		\\
-%			&		&			&	&		 & 0&a_{n-1} \\
-%			&		&			&	&		 &	&1 	\\
-%		
-%\end{bmatrix} \begin{bmatrix} x_1 \\ \\  \\ \\ \vdots \\  \\ \\ x_n \\ \end{bmatrix} + \begin{bmatrix} b_1 \\ \\ \\  \\ \vdots  \\ \\ \\ b_n \\ \end{bmatrix}  \geq 0.\]
-%Finally, we can also assume that, up to a permutation of the variables, $\val(a_1)= \min_{i=1}^{n-1} \val(a_i).$
-%We distinguish two cases: $\val(a_1) \geq 0$ and $\val(a_1)<0.$
-%
-%Let us first assume that $\val(a_1) \geq 0$
-%
-%Let $x \in \PP_2$.
-%Then $x_n=-b_n+O(1)$
-%and $x_1+a_1 x_n+b_1=O(1).$
-%Consequently, $x_1-a_1 b_n +b_1=O(1)+O(\pi^{\val(a_1)})=O(1).$
-%Similarly, for all $i \in \llbracket 2,n-1 \rrbracket,$
-%$x_i-a_ib_n+b_i=O(1)+O(\pi^{\val(a_i)})=O(1).$
-%
-%We define the polyhedron $\Qc \subset K^{n-1}$ by the following inequalities:
-% for all $i \in \llbracket 1,n-1 \rrbracket,$
-%$\val(x_i-a_ib_n+b_i) \geq 0.$
-%
-%Then the previous computations prove that $p(\PP_2)\subset \Qc.$
-%Conversely, let $(x_1,\dots,x_{n-1}) \in \Qc.$
-%Then let $x_n := -b_n.$
-%
-%We check that for $i \in \llbracket 1,n-1 \rrbracket,$
-%$x_i+a_ix_n+b_i=x_i-a_ib_n+b_i=O(1),$
-%and $x_n+b_n=O(1)$. Hence $(x_1,\dots,x_n) \in \PP_2$
-%which means that $(x_1,\dots,x_{n-1}) \in p(\PP_2).$
-%Thus $p(\PP_2)= \Qc$ and $p(\PP_2)$ is a polyhedron.
-%
-%We now deal with the second case, with $\val(a_1)<0.$
-%Let $x \in \PP_2$.
-%Then $x_n=-b_n+O(1)$
-%and $x_1+a_1 x_n+b_1=O(1).$
-%Consequently, $x_1-a_1 b_n +b_1=O(1)+O(\pi^{\val(a_1)})=O(\pi^{\val(a_1)}).$
-%Thus $a_1^{-1}x_1- b_n +a_1^{-1}b_1=O(1)$.
-%%and $x_n=-a_1^{-1}(x_1+b_1)+O(1).$
-%In addition, $x_n=-a_1^{-1}(x_1+b_1)+O(\pi^{-\val(a_1)}).$
-%We plug this equality in 
-%$x_i+a_i x_n+b_i=O(1)$ to get
-%$x_i-a_1^{-1}a_i(x_1+b_1)+b_i=O(1)+O(\pi^{\val(a_i)-\val(a_1)})=O(1)$
-%using that $\val(a_i) \geq \val (a_1).$
-%
-%We define the polyhedron $\Qc \subset K^{n-1}$ by the following inequalities:
-%$\val(a_1^{-1}x_1- b_n +a_1^{-1}b_1) \geq 0$ and for all $i \in \llbracket 2,n-1 \rrbracket,$
-%$\val(x_i-a_1^{-1}a_i(x_1+b_1)+b_i) \geq 0.$
-%
-%Then the previous computations prove that $p(\PP_2)\subset \Qc.$
-%Conversely, let $(x_1,\dots,x_{n-1}) \in \Qc.$
-%Let $x_n := -a_1^{-1}(x_1+b_1).$
-%Then
-%$x_1+a_1 x_n+b_1=0=O(1).$
-%Let $i \in \llbracket 2,n-1 \rrbracket,$
-%then $x_i+a_i x_n+b_i=x_i-a_1^{-1}a_i(x_1+b_1)+b_i=O(1)$
-%since $(x_1,\dots,x_{n-1}) \in \Qc.$
-%Finally, 
-%$x_n+b_n=-a_1^{-1}(x_1+b_1)+b_n=O(1)$ thanks to the inequality satisfied by $x_1.$
-%Hence $(x_1,\dots,x_n) \in \PP_2$
-%which means that $(x_1,\dots,x_{n-1}) \in p(\PP_2).$
-%Thus $p(\PP_2)= \Qc$ and $p(\PP_2)$ is a polyhedron,
-%and it has been proved in both cases.
-%
-%Therefore,$p(\PP)$ is a polyhedron.
-%
-%\end{proof}
-%
-%We can finally prove that the image of polyhedron under a linear mapping is a polyhedron.
-%\begin{proposition}
-%Let $\PP \subset K^n$ be a polyhedron and $f: K^n \rightarrow K^m$
-%be a linear mapping. Then $f(\PP)$ is a polyhedron.
-%\end{proposition}
-%
-%\begin{proof}
-%
-%We assume that $\PP \neq \emptyset$, and we identify $f$ with its matrix in $\allmat_{n,n}(K)$.
-%As seen above, we can assume that $\PP$ is of the form $\left\lbrace x \in K^n : \val (l_i (x) ) \geq 0, \textrm{ for } i \in I\right\rbrace$ for some
-%finite sets $I \subset \N$ and $l_i \in K[x]_1$, for $i \in I$ .
-%
-%Thanks to Definition \ref{smith_nf}, (the matrix of) $f$
-%can be written $f=Q^{-1} \Delta P$
-%with $P \in \GL_n(\OK),$ $Q \in \GL_m(\OK)$
-%and $\Delta = \mathrm{SNF}(f)\in \allmat_{m,n}(K)$ of the form $\diag(\lambda_1, \ldots, \lambda_r, {\bf 0}_{\min(m,n)-r})$
-%  where ${\bf 0}_{\min(m,n)-r}$ is a null square matrix of size $\min(m,n)-r$ for $\lambda_1,\dots,\lambda_r$ non-zero and $r \in \N.$
-%
-%  %Now, we turn our attention to the $\Delta$ part of $f$.
-%We have previously proven that if $f \in \GL_n(\OK)$ then $f(\PP)$ is a polyhedron.
-%It is also clear that
-%if $f$ is the immersion 
-%$K^l \rightarrow K^n$
-%$(x_1,\dots,x_l)\mapsto (x_1,\dots,x_l,0,\dots,0)$ 
-%and $\PP$ is a polyhedron in $K^n$,
-%then $f(\PP)$ is a polyhedron.
-%
-%
-%We now prove that for
-%$\Delta$ a Smith Normal Form
-%and $\PP$ a polyhedron,
-%$\Delta(\PP)$ is a polyhedron.
-%Then $\Delta$ is the composition
-%of the immersion 
-%$K^l \rightarrow K^n$
-%$(x_1,\dots,x_l)\mapsto (x_1,\dots,x_l,0,\dots,0),$ 
-% the diagonal invertible mapping
-%$K^l \rightarrow K^l$,
-%$(x_1,\dots,x_l)\mapsto (\delta_1,\dots,\delta_l x_l)$,
-%and the projections
-%$(x_1,\dots,x_{l+1})\mapsto (x_1,\dots,x_{l}),$
-% $(x_1,\dots,x_{l+2})\mapsto (x_1,\dots,x_{l+1}),$
-% $\dots,$
-% $(x_1,\dots,x_{n})\mapsto (x_1,\dots,x_{n-1}).$
-% Thus $\Delta(\PP)$ is a polyhedron thanks to the previous 
-% results on image of polyhedron.
-%
-%Finally, if $f: K^n \rightarrow K^m$
-%is a linear mapping and
-%$f=Q^{-1} \Delta P$ is its Smith Normal Form
-%with $P \in \GL_n(\OK),$ $Q \in \GL_m(\OK)$
-%and $\Delta \in \allmat_{n,m}(K)$,
-%then
-%$P(\PP)$ is a polyhedron,
-%$\Delta (P(\PP))$ also,
-%and finally $f(\PP)=Q^{-1} (\Delta (P(\PP)))$
-%is a polyhedron.
-%This concludes the proof.
-%\end{proof}
-
-We recall that the Minkowski sum of two sets $A$ and $B$ is $A+B = \{a+b : a \in A, b \in B\}$.
-
-\begin{corollary}
-The Minkowski sum of two polyhedra in $K^n$ is a polyhedron in $K^n$.
-\end{corollary}
-\begin{proof}
-  Straightforward from the equality
-  $P_1 + P_2 = \{z \in K^n : x \in P_1, y \in P_2, x+y=z\}.$
-\end{proof}
-
-\begin{proposition}[Characterization of polyhedra] \label{prop:carac}
-    Non-empty polyhedra are image of polydiscs under a linear mapping.
-\end{proposition}
-\begin{proof}
-    Let $\PP$ be a polyhedron in $K^n$. Then $\PP = \{x \in K^n : Ax+B \ge 0, Dx = e\}$ for some $A \in K^{d \times n}, b \in K ^d,  D\in  K^{m\times n}, e \in K^m$.
-
-    If $\PP$ is nonempty then there exists $x_0 \in K^n$ such that $Dx_0=e$.
-Let $J \in K^{n \times R}$ such that $\textrm{Im} J = \ker D$ where $R$ denotes the dimension of $\ker D$.
-Then $\PP = x_0 + J\PP'$ where $A' := AJ$ $b' := Ax_0 + b$ and
-    $\PP' := \{y \in K ^R: A'y + b' \ge 0 \}$.
-
-    Now let $S \in K^{n\times R}$ be the SNF of $A'$ and $Q \in \GL_n\left(\mathcal{O}_K\right)$ and $P \in \GL_R\left(\mathcal{O}_K\right)$ such that $A'= Q S P^{-1}$.
-    Then $\PP' = \{y \in K^R : QSP^{-1}y + b' \ge  0\} = P\{z \in K^R : Sz + Q^{-1}b' \ge 0 \}$.
-    Let $b'':=Q^{-1}b$ then $P' = P \{z \in K^R : s_i z_i + b''_i \ge 0, i= 1\ldots R\}$.
-The set $\{z \in K^R : s_i z_i + b_i \ge 0\}$ is either empty or a polydisc (possibly with infinite radii) and $\PP = x_0 + JP \{z \in K^R: s_i z_i + b_i \ge  0, i=1,\ldots,R\}$ which concludes the proof.
-
-\end{proof}
-
-\begin{corollary} \label{cor:caracdim1}
-   If $\PP$ is a polyhedron in $K$ then $\PP$ is either empty or a ball (possibly with infinite radius).
-\end{corollary}
-
-\begin{proof}
-    Let $\PP$ be such polyhedron.
-We assume that $\PP \neq \emptyset$.
-By \ref{prop:carac} there exist a polydisc $D = \{x \in K^n : \val s_i x_i - b_i \ge 0, i=1,\ldots,n \}$ for some $s_1,\ldots,s_n, b_1,\ldots,b_n \in K ^n$ and an affine map $f : K^n \to K$ such that $\PP = f(D)$.
-Let $a_0,a_1,\ldots,a_n \in K$ such that $f(x) = a_0 + a_1 x_1 + \ldots + a_n x_n$.
-We can assume, with no loss of generality, that the $a_i$'s are nonzero.
-
-If there exists $i_0 \in \{1,\ldots,n\}$ such that $s_{i_0} = 0$ then $\PP = f(D) = K$ and $\PP$ is a ball of infinite radius.
-Otherwise, we have $D = \{x \in K^n : x_i = \frac{b_i}{s_i} + O\left( \pi^{-val s_i} \right), i=1,\ldots,n \}$ and therefore for all $x \in  K$, $x \in P$ if and only if $x = a_0 + \sum_{i=1}^{n}( \frac{a_i b_i}{s_i} + O\left( \pi^{\val a_i - \val s_i} \right))= a_0  + \sum_{i=1}^{n} \frac{a_i b_i}{s_i} + O(\pi^d)$ where $d = \min \limits_{i = 1,\ldots,n} \val a_i - \val s_i$.
-Thus $\PP = \{x \in K : \val (x - a_0 - \sum_{i=1}^{n} \frac{a_i b_i}{s_i}) \ge d \}$ is a ball.
-
-\end{proof}
-
-%%%%% old section by Corentin
-%%%%%\input{old_LP_section.tex}
-
-\section{Linear programming}
-
-A \emph{linear programming problem} (or \emph{linear program}) \emph{with data $(A,b,c,D,e)$} is defined
-as:
-\begin{equation}
-  \tag{LP}\label{LP}
-\begin{array}{rcll}
-  p^* & := & \inf_{x \in K^n} & \val \left\langle c, x \right\rangle \\
-  &    & \text{s.t.}         & A x + b \geq 0\\
-  & & & D x = e
-\end{array}
-\end{equation}
-with $c \in K^n$ a fixed vector of size $n$ that represents the cost,
-$A \in K^{d \times n}$, $b \in K^d$, $D \in K^{m\times n}$, $e \in K^m$ 
-and $\left\langle c, x \right\rangle := c_1 x_1+\cdots +c_n x_n$.
-When $A$ is a diagonal matrix,
-we refer to \eqref{LP} as a \emph{diagonal} linear program.
-We denote the \emph{feasible set} of \eqref{LP} by
-\begin{equation*}
-\begin{aligned}
-  \PP  &= \{x \in K^n : Ax + b \geq 0, Dx = e\}.
-\end{aligned}
-\end{equation*}
-Note that $\PP$ is a polyhedron.
-A vector $x \in K^n$ is called \emph{feasible} for~\eqref{LP} if $x \in \PP$.
-A feasible vector $x^* \in \PP$ is called a \emph{solution} to \eqref{LP} if $p^* = \val\left\langle c,x^*\right\rangle$, namely, if the infimum in \eqref{LP} is attained at $x^*$.
-
-\begin{remark}
-  Assume $\val$ is a discrete valuation. Then
-  if \eqref{LP} admits feasible vectors,
-  $p^*$ is either $-\infty$ or attained at some solution $x^*$.
-\end{remark}
-
-In this section we present \Cref{algo_LP}, \textbf{SOLVELPval}, for solving Problem \eqref{LP}.
-The algorithm starts by eliminating the equality constraint defined by $D$ and $e$
-by variable substitution. Then the matrix $A$ is replaced by its Smith Normal Form,
-and the general linear program is consequently reduced to a diagonal linear program.
-The original \eqref{LP} is then easily solved by looking at valuations of input data
-in the reduced problem.
-
-\begin{algorithm}[!ht]
-    {\footnotesize
-    \caption{\textbf{SOLVELPval}($A,b,c,D,e$)}\label{algo_LP}
-    \begin{algorithmic}[1]
-    %%%\algsetup{linenosize=\tiny}
-      \REQUIRE
-      $A \in K^{d\times n}$, $b \in K^d$, $c \in K^n$, $D \in K^{m \times n}$ and $e \in K^m$
-      \ENSURE [TYPE, $x$], where:
-      \vspace{-0.1cm}
-      \begin{itemize}
-      \item[]
-        TYPE $=$ INFEAS and $x=[]$ if and only if \eqref{LP} is infeasible
-        \vspace{-0.1cm}
-      \item[]
-        TYPE $=$ UNBOUND and $x=[]$ if and only if \eqref{LP} is feasible and unbounded
-        \vspace{-0.1cm}
-      \item[]
-        TYPE $=$ FEAS if and only if \eqref{LP} is feasible and has a solution $x$
-      \end{itemize}
-      \vspace{-0.1cm}
-      \hrule
-      \vspace{0.1cm}
-      \IF{$Dx = e$ has no solution}
-      \RETURN [INFEAS, []] \label{step:linear_empty}
-      \ENDIF
-      \IF{$D \neq {\bf 0}$} \label{step:reducD:begin}
-      \STATE find $J \in K^{n \times R}$, with $R = \dim\ker D$, such that $\text{Im}\, J = \ker D$
-      \STATE find $x_0$ such that $Dx_0=e$ \label{step:reducD:end}
-      \RETURN $\textbf{SOLVELPval}(AJ,b+A x_0,J^T c, {\bf 0},0)$ \label{step:reducD} \hfill {\color{olive} \# \Cref{reducD}}
-      \ENDIF
-      \IF{$A$ not in Smith Normal Form} \label{step:solsLP:begin}
-      \STATE $[Q,S,P] \leftarrow \textbf{SNF}(A)$
-      \STATE $[\mathrm{STATUS}, y] \leftarrow \textbf{SOLVELPval}(S,Qb,(P^{-1})^Tc,{\bf 0},0)$ \label{step:solsLP:end}
-      \RETURN $[\mathrm{STATUS}, P^{-1}y]$ \hfill \color{olive} \# \Cref{solsLP} \label{step:solsLP}
-      \ENDIF
-      \STATE $r \leftarrow \text{rank}(A)$ \label{step:core:begin}
-      \IF{$\bigwedge_{i=r+1}^d \val(b_{i}) \geq 0$} \label{step:condition}
-      \IF{$\bigvee_{i=r+1}^n c_i \neq 0$}
-      \RETURN [UNBOUND, []] \hfill {\color{olive} \# \Cref{prop:reduc}, item \ref{prop:reduc_it2}} \label{step:unbound}
-      \ELSE
-          %\STATE STATUS $\leftarrow$ FEAS
-      \STATE $\lambda \leftarrow -\sum_{i=1}^r c_i b_i / s_i$
-      \STATE $v \leftarrow \min_{1 \leq i \leq r} \val (c_i/s_i)$
-      \IF{$\val \lambda < v$}
-      \STATE choose $y \in K^n$ such that $y_i \in (-b_i+\OK)/s_i, i=1,\ldots,r$
-      \RETURN [FEAS, $y$] \hfill {\color{olive} \# \Cref{solutions}, item \ref{solutions:it1}}
-      \ELSE
-      \STATE $j \leftarrow \min_{1 \leq i \leq r} \{i : v = \val (c_i/s_i)\}$
-      %find $y \in K^n$ such that $y_i \in (-b_i+\OK)/s_i, i=1,\ldots,r$
-      %and $\langle c,y\rangle = \pi^v\OK$
-      \RETURN [FEAS, ${\bf e}_j$] \hfill {\color{olive} \# \Cref{solutions}, item \ref{solutions:it2}}
-      \ENDIF
-      \ENDIF 
-      \ENDIF 
-      %\STATE
-      %\STATE
-      %\RETURN ... \hfill {\color{olive} \# \Cref{prop:reduc}}
-      %\ENDIF \label{step:core:end}
-      \RETURN [INFEAS, []] \label{step:core:end}
-    \end{algorithmic}
-  }
-\end{algorithm}
-
-In order to prove correctness of \Cref{algo_LP}, we proceed step-by-step.
-When the system $Dx=e$ has no solution, \eqref{LP} is infeasible and
-thus from now on we only consider the case when $Dx=e$ has a solution.
-
-We first prove a reduction result, allowing to consider only iterations
-of~\eqref{LP} with data of the form $(A,b,c,{\bf 0},0)$.
-
-\begin{lemma}\label{reducD}
-  Let $A \in K^{d \times n}, b \in K^d, c\in K^n$, $D \in K^{m\times n}$,
-  $e \in K^m$ and let $J \in K^{n \times R}$ be a matrix such that
-  ${\rm Im}\, J = \ker D$ and $R = \dim \ker D$.
-  Assume there exists $x_0 \in K^n$ such that $D x_0 = e$, and let
-  $x \in \{z \in K^n : Dz = e\} = x_0 + \ker D$.
-  Let $y \in K^R$ denote the unique element of $K^n$ such that
-  $x = x_0 + J y$. Then:
-  \begin{enumerate}
-  \item\label{reducD_item1}
-    $x$ is feasible for~\eqref{LP} with data $(A,b,c,D,e)$ if and only if 
-    $y$ is feasible for~\eqref{LP} with data $(AJ,b+A x_0,J^T c,{\bf 0},0)$.
-  \item\label{reducD_item2}
-    $x$ is a solution for~\eqref{LP} with data $(A,b,c,D,e)$ if and only if 
-    $y$ is a solution for~\eqref{LP} with data $(AJ,b+A x_0,J^T c,{\bf 0},0)$ and
-    $\langle c,x^* \rangle = \langle J^T c,y^* \rangle$.
-  \end{enumerate}
-\end{lemma}
-\begin{proof}
-  %The existence and uniqueness of $y$ are granted by the fact that $x \in x_0 + \ker D =x_0+ {\rm Im } J$  and $\ker J = \{0\}$. 
-  First, if $D={\bf 0}$, then by the assumptions one must have $e=0$, and the problem
-  is already reduced (with $J=I_n$ and $x_0=0$).
-  Next, assume $D\neq{\bf 0}$, then $Dx=e$ and $Ax + b \le 0$ if and only if
-  $AJy + b+Ax_0 \le 0$, proving \Cref{reducD_item1}. Finally, for all
-  $c \in K^n$, $\langle c,x\rangle = \langle c, Jy\rangle = \langle J^T c,y\rangle$, which proves \Cref{reducD_item2}.
-\end{proof}
-
-%%%%Indeed, for all $z \in K^n$ and $M \in \allmat_n(\OK)$ if $z \geq 0$, then $Mz \geq 0$.
-The latter property is a direct consequence of $\OK$ being a ring and the converse holds if the matrix $M$ is invertible in $\OK$.
-
-\Cref{solsLP} allows us to reduce Problem \eqref{LP} without linear equations
-to diagonal linear programs.
-
-\begin{lemma} \label{solsLP}
-  Let $A \in K^{d\times n}$, $b \in K^d$, $c\in K^n$ and let
-  $S = \mathrm{SNF}(A) = QAP^{-1} \in K^{d\times n}$, with
-  $P \in \GL_d(\OK)$ and $Q\in \GL_d(\OK)$.
-  Define $b' = Qb$ and $c' = (P^{-1})^Tc$.
-  Then
-   \begin{enumerate}
-   \item \label{solsLP_item1}
-     $x \in K^n$ is feasible for \eqref{LP} with data $(A,b,c,{\bf 0},0)$ if and only if $y = P x \in K^n$ is
-     feasible for \eqref{LP} with data $(S,b',c',{\bf 0},0)$.
-   \item \label{solsLP_item2}
-     $x^* \in K^n$ is a solution to \eqref{LP} with data $(A,b,c,{\bf 0},0)$ if and only if $y^* = P x^*$ is
-     a solution to \eqref{LP} with data $(S,b',c',{\bf 0},0)$ and $\langle c,x^* \rangle = \langle c',y^* \rangle$.
-   \end{enumerate}
-\end{lemma}
-\begin{proof}
-  Note that the transition matrices $P$ and $Q$ defining SNF$(A)$ are invertible in $\OK$
-  and as such they preserve inequalities: $Mz \geq 0$ if and only if $Nz \geq 0$, with
-  $N = \mathrm{SNF}(M)$. Thus one has that $Ax+b = AP^{-1}y +b \geq 0$ if and only if
-  $Q(AP^{-1}y + b) = Sy + b' \geq 0$; this yields \Cref{solsLP_item1}.
-  Moreover, for all $c \in K^n$, we have $\langle c, x\rangle = \langle c, P^{-1}Px \rangle =
-  \langle (P^{-1})^T c, Px \rangle = \langle c',y\rangle$, which proves
-  \Cref{solsLP_item2}.
-\end{proof}
-
-Finally we show in \Cref{prop:reduc} that solving a diagonal \eqref{LP} amounts
-to checking the valuations of input data:
-
-\begin{lemma}\label{prop:reduc}
-  Let $(S,b',c') \in K^{d\times n} \times K^d \times K^n$ be as in \Cref{solsLP}.
-  Then:
-  \begin{enumerate}
-  \item \label{prop:reduc_it1}
-    \eqref{LP} with data $(S,b',c',{\bf 0},0)$ is feasible if and only if the $d-r$ last coefficients
-    of $b'$ have nonnegative valuation, for $r = {\rm rank}\,S$.
-  \item \label{prop:reduc_it2}
-    Assume at least one of the $n-r$ last coefficients of $c'$ is non-zero. If \eqref{LP} with
-    data $(S,b',c')$ is feasible, then it is unbounded and does not admit solutions.
-  \end{enumerate}
-\end{lemma}
-\begin{proof}
-  %%%%\corentin{préciser les notations}. 
-  A vector $y = (y_1, \ldots, y_n)^T \in K^n$ is feasible for \eqref{LP} with data
-  $(S,b',c',0)$ if and only if $\val(s_i y_i + b'_i) \geq 0$ for all $i = 1,\ldots,n$.
-  However $s_i = 0$ for $n-r \leq i\leq n$. Therefore, if \eqref{LP} with data $(S,b',c',0)$ is feasible,
-  necessarily the $d-r$ last coefficients of $b'$ have nonnegative valuation.
-  Conversely, if the $d-r$ last coefficients of $b'$ are zero, the vector $y \in K^n$ such that
-  $y_i = {-b'_i}/{s_i}$ if $1 \leq i \leq r$, and $y_i =0$ otherwise, is feasible for \eqref{LP}
-  with data $(S,b',c',{\bf 0},0)$.
-
-  Concerning \Cref{prop:reduc_it2}, let $y^*$ be feasible for \eqref{LP} with data $(S,b',c',{\bf 0},0)$.
-  Let $i$ be such that $r+1 \leq i \leq n$ and $c'_i \neq 0$. Consider the vector $e^i$ whose only non-zero
-  coefficient is the $i-$th, which is $1$. Then $y^* + \alpha e^i$ is feasible for \eqref{LP} with data $(S,b',c',{\bf 0},0)$,
-  for all $\alpha \in K$ and $\langle c', y^* + \alpha e^i\rangle = \langle c' , y^* \rangle + \alpha c'_i$.
-  In particular, for all $n \in \mathbb{N}$ if we set $\alpha_n = -({\langle c', y^* \rangle + \pi^{-n}})/{c'_i}$,
-  we have $\val \left(\langle c', y^* + \alpha_n e ^i \rangle\right) = \val \pi^{-n} = -n$.
-  Therefore, the problem is unbounded as $p^* = -\infty$.
-\end{proof}
-
-%The previous results imply that we can consider iterations of diagonal linear programs admitting a solution.
-By \Cref{prop:reduc} one can simplify the problem by only taking account the first $r$ coefficients of $y, b', c'$ and the submatrix of $S$ made by the $r$ first rows and columns corresponding to the nonzero invariants factors.
-
-We conclude by giving explicit solutions to the reduced \eqref{LP}:
-
-\begin{lemma}\label{solutions}
-  Let $(S,b',c',{\bf 0}, 0)$ be as in \Cref{solsLP} and assume \eqref{LP} is feasible.
-  %%%$\PP' \neq \emptyset$.
-  %%%= \{y \in K^n : Sy+b' \geq 0\}
-  For $\lambda = -\sum_{i=1}^r c'_i b'_i/s_i$ and $v = \min_{1\le i\le r} \val (c'_i/s_i)$,
-  one has:
-  \begin{enumerate}
-  \item
-    if $\val \lambda < v$, the minimum is $\val \lambda$ and is attained on the whole feasible
-    set; \label{solutions:it1}
-  \item
-    if $\val \lambda \geq v$, the minimum is $v$ and is attained on
-    ${\bf e}_j \in K^n$, the vector with all $0$'s except with a $1$ on the $j$-th component,
-    with $j$ satisfying $\val (c'_j/s_j) = v$. \label{solutions:it2}
-  \end{enumerate}
-  %One has
-  %$$
-  %\langle c',\PP'\rangle = \lambda + \pi^v\OK.
-  %$$
-  %If attained on every $x \in \PP'$;
-\end{lemma}
-\begin{proof}
-  The feasible set $\PP' = \{y \in K^n : Sy+b' \geq 0\}$ of the diagonal LP can be written
-  as the set of vectors $y \in K^n$ that verifies $s_i y_i + b'_i \in \OK$ for $i=1,...,r$.
-  In other words:
-  $$
-  \PP' = \left\{\left[\begin{smallmatrix} y_1\\ \vdots\\ y_n \end{smallmatrix}\right] \in K^n :
-  y_i \in -\frac{b'_i}{s_i} + \frac{1}{s_i} \OK, 1\le i\le r\right\}.
-  $$
-  The minimum in \eqref{LP} is the minimum of
-  $y \mapsto \val\left(\left\langle c',y \right\rangle\right)$ on $\PP'$.
-  The image of $\PP'$ by $y \mapsto \left\langle c',y \right\rangle$ is
-  \[
-  \left\langle c',\PP' \right\rangle = \sum_{i=1}^r -c'_i \frac{b'_i}{s_i} + \sum_{i=1}^r\left( \frac{c'_i}{s_{i}} \OK \right) = \lambda + \pi^{v} \OK.
-  \]
-  Two cases can occur depending on $v$ and the valuation of $\lambda$.
-  If $\val(\lambda) < v$, the minimum of $y\mapsto \val\left(\left\langle c',y \right\rangle\right)$ over $\PP'$ is reached at any point of $\PP'$, and is equal to $\val(\lambda)$.
-  Otherwise, $\lambda \in \pi^{v} \OK$ and the minimum is $v$ and is reached at any points $y$ of $\PP'$ such that
-  $\left<c',y \right> \in \pi^v\OK$.
-\end{proof}
-
-We are now able to state a correctness theorem for \Cref{algo_LP}.
-
-\begin{theorem} \Cref{algo_LP} is correct.
-\end{theorem}
-\begin{proof}
-  If the linear system $Dx=e$, Problem \eqref{LP} is infeasible
-  and \Cref{algo_LP} outputs correct answer at step \ref{step:linear_empty}.
-  Else, by \Cref{reducD} the input problem can be reduced to a new linear
-  program with $D={\bf 0}$ and $e=0$, which is done at steps
-  \ref{step:reducD:begin}-\ref{step:reducD:end},
-  and the correct recursion is given at step \ref{step:reducD}.
-  The reduction based on SNF from \Cref{solsLP} is performed at
-  steps \ref{step:solsLP:begin}-\ref{step:solsLP:end} and the output
-  at step \ref{step:solsLP} is correct.
-
-  The core of \Cref{algo_LP} is on steps \ref{step:core:begin}-\ref{step:core:end}.
-  If $\val(b_i) \geq 0$, for all $i=1,\ldots,r+1$, with $r = \mathrm{rank}(A)$,
-  by \Cref{prop:reduc}, item \ref{prop:reduc_it1}, the problem \eqref{LP} is feasible.
-  Two cases can occur under this assumption:
-  either at least one of the $n-r$ last coefficients of $c'$ is non-zero,
-  in which case,
-  by \Cref{prop:reduc}, item \ref{prop:reduc_it2}, the problem is
-  unbounded and has no solution, thus the output on step \ref{step:unbound} is correct;
-  or all the $n-r$ last coefficients of $c'$ are null. In this case the solutions
-  are explicitely constructed according to \Cref{solutions}.
-
-  If the condition on step \ref{step:condition} is not satisfied, the problem
-  is infeasible by \Cref{prop:reduc} (step \ref{step:core:end}).
-\end{proof}
-
-%\begin{remark}
-%  If $\val \lambda \ge v$ and $i_0 \in \{1,\ldots, n\} $ is such that
-%  $v = \val \frac{c_{i_0}'}{s_{i_0}²} $ then the vector $e^{i_0} \in K$ is a solution of \ref{LP}, 
-%  where $e^{i_0}$ denotes the vector of $K^n$ whose only non-zero coefficient is the $i_0$-th
-%  which is $1$.
-%\end{remark}
-
-\begin{remark}
-  To maximize the valuation of a linear map over a polyhedron instead of minimizing it 
-  (which is equivalent to minimize the absolute value) the same reasoning can be applied. 
-  The only difference being that if $\val\left( \lambda\right) < v$ the problem is unbounded
-  and as such does not admit a solution. 
-\end{remark}
-
-\section{Spectrahedra}
-
-\subsection{Positive semidefinite matrices}
-%\newcommand\mat{postive semidefinite matrix } 
-\newcommand\Mat{Positive semidefinite matrix }
-\newcommand\mats{positive semidefinite matrices }
-\newcommand\Mats{positive semidefinite matrices }
-
-\begin{definition}
-  We say that a matrix $M \in K^{d \times d}$ is \emph{positive semidefinite} ($M \succeq 0$)
-  if all its eigenvalues have nonnegative valuation in an algebraic closure of $K$.
-  We denote by $K^{d \times d}_+ \subset K^{d\times d}$ the set of positive semidefinite matrices.
-  The characteristic polynomial of a matrix $M \in K^{d\times d}$ is denoted $\chi_M \in K[T]$.
-\end{definition}
-
-Recall that the \emph{Newton polygon} of a polynomial $P = \sum_{i=0}^{d} a_i T^i \in K[T]$ is
-defined as the inferior convex hull of the set $\{(i, \val a_i) \,|\, 0 \le i \le d\}$, {\it i.e.} the
-graph of the greatest convex function $\PP : [0,d] \to \R$ such that $\PP(i) \leq \val a_i$
-for $i=1,\ldots,d$. This function is piecewise affine and its slopes are exactly the opposites of the valuations
-of the roots of $P$.
-
-The following result shows that testing positive semidefiniteness of matrices over
-valued fields reduces to checking whether the coefficients of $\chi_M$ are integers.
-
-\begin{theorem}
-  \label{caracsdp}
-  $M \in K^{d\times d}_+$ if and only if $\chi_M \in \OK[T]$.
-\end{theorem}
-\begin{proof}
-  Both senses of the equivalence will be proven by contraposition.
-  Let $M \in K^{d\times d}$ with characteristic polynomial $\chi_M = T^d + \sum_{i=0}^{d-1} a_i T^i$ for $a_0,...,a_{d-1} \in K$.
-  First suppose $M \not \in K^{d\times d}_+$, thus $\chi_M$ has a root $\rho$ with $\val\,\rho<0$.
-  It follows that
-  $$
-  + \infty = \val \chi_M (\rho) = \val \left(\rho^d+ \sum_{i=0}^{d-1} a_i \rho^i\right)
-  $$ and $\val \rho^d = d \val \rho <0$.
-  The properties of the non-archimedean inequality and of the valuation imply that
-  $$
-  0> \val \rho^d = \val\left(\sum_{i=0}^{d-1} a_i \rho^i\right) \geq
-  \min_{0 \leq i \leq d-1} \val \left(a_i \rho^i\right)
-  $$
-  %%%$\val ( \sum_{i=0}^{d-1} a_i \rho^i) = \val \rho^d$ and $\val ( \sum_{i=0}^{d-1} a_i \rho^i) \ge \min_{i=0,..., d-1} \val \left(a_i \rho^i\right)$.
-  Therefore, there exists $j \in \left\{0,...,d-1\right\}$ such that $\val(a_j \rho^j) \le \val\rho^d$,
-  {\it i.e.} such that $\val a_j \le (d-j) \val \rho <0$. This shows that $\chi_M \not\in \OK[T]$.
-
-  %%We have proven the converse sense of the equivalence.
-  %%To prove the direct sense a brief introduction to Newton's polygon will be needed, we will only state the results we use in this proof and will redirect to \cite{gouvea_p-adic_2003} to further explanations.
-
-  Suppose now $\chi_M \not\in \OK[T]$. There exists $j \in \{0,...,d-1\}$ such that $\val a_j <0$.
-  The polynomial $\chi_M$ being monic, the point with abscissa $d$ of the Newton polygon of $\chi_M$ is
-  $(d,\val(1)) = (d,0)$. 
-  Therefore, the point $(j, \val a_j)$ having negative ordinate implies that at least one of the slopes of
-  the Newton polygon of $\chi_M$ is positive, so that $\chi_M$ has a root with negative valuation.
-\end{proof}
-
-As a consequence, matrices with integer coefficients are positive semidefinite.
-
-\begin{corollary}\label{cor_caracsdp}
-  $\OK^{d\times d} \subset K^{d\times d}_+$.
-\end{corollary}
-\begin{proof}
-  $\OK$ is a ring, therefore if $M \in \OK^{d \times d}$, then $\chi_M \in \OK[T]$.
-\end{proof}
-
-The reverse inclusion of \Cref{cor_caracsdp} is false in general as we show in the next example.
-
-\begin{example}
-  Let
-  $$
-  M = \begin{bmatrix} \frac{3}{5}+5 & \frac{4}{5} \\ \frac{4}{5} & -\frac{3}{5} \end{bmatrix}.
-  $$
-  The characteristic polynomial of $M$
-  is $\chi_M = T^2-5T-4$.
-However when seen as a matrix over $K=\mathbb{Q}_5$, then $\chi_M \in \mathbb{Z}_5[T] = \OK[T]$: then $M \in (\mathbb{Q}_5)^{2 \times 2}_+$, nevertheless $M \not\in (\mathbb{Z}_5)^{2\times 2}$, hence
-  $(\mathbb{Q}_5)^{2 \times 2}_+ \not\subset (\mathbb{Z}_5)^{2 \times 2}$.
-\end{example}
-
-\begin{definition}
-  A \emph{cone} of $K^d$ is a subset that is closed under multiplication by elements of $\OK$.   
-\end{definition}
-
-\begin{proposition}
-%  {\color{blue} [Peut être une hypothèse à rajouter, par exemple $K$ à valuation discrete]}
-  $K^{d \times d}_+$ is a cone.
-  If $\val$ is discrete, then it is both open and closed.
-\end{proposition}
-\begin{proof}
-  The fact that $K^{d \times d}_+$ is a cone is immediate from the definition.
-  Next, remark that $\OK[X]$ is closed and open in $K[X]$ equipped with the infinity norm
-  $$
-  \|\cdot\|_\infty : P = \sum_{k=1}^{n} a_k X^k \to
-  \max_{1 \leq k \leq n} |a_k|,
-  $$
-  {where $|\cdot|$ is any norm induced by $\val$}:
-  $\OK$ is indeed the open unit ball for $\|\cdot \|_\infty$ that induces a discrete distance for
-  which open balls are also closed sets.
-  Furthermore, $K^{d\times d}_+ = \chi^{-1}(\OK[X]) $ where $\chi$ is the function that maps a
-  matrix to its characteristic polynomial which is continuous.
-  Thus $K^{d\times d}_+$ is both open and closed, too.
-\end{proof}
-
-%\begin{remark}
-%  \corentin{Pas nécessairement très important, à voir}
-%  If $C$ is a cone that is furthermore closed under addition (what shall be called a convex cone in the real case) then $C$ is a $\OK$-module.
-%\end{remark}
-
-\subsection{Definition of spectrahedra}
-
-\begin{definition}
-  \label{def_spectrahedra}
-  A \emph{spectrahedron in $K^{d\times d}$} is a set of the form
-  $$
-  \mathcal{S} = \mathcal{L} \cap K^{d\times d}_+ = \left\{X \in K^{d \times d} :
-  \exists \, x \in K^n, X = A_0 + \sum_{i=1}^n x_i A_i, X \succeq 0\right\}
-  $$
-  where $\mathcal{L} = A_0+\span{A_1,\ldots,A_n} \subset K^{d \times d}$ is an affine space, for some
-  $A_0,A_1,\ldots,A_n \in K^{d\times d}$.
-\end{definition}
-
-In the real case, one often abuses of the definition of spectrahedra, saying that the set
-$\{x \in \mathbb{R}^n : A_0+\sum_{i=1}^n x_iA_i \succeq 0\}$ is also a spectrahedron.
-Remark that this also yields that every affine subset of $\mathbb{R}^n$ is also
-a spectrahedron: indeed an affine equation $\ell(x) = 0$ is equivalent to the two inequalities
-$\ell(x) \geq 0 \leq -\ell(x)$. Over a valued field it is necessary to give the following
-definition in order to include affine sets in the family of spectrahedra.
-
-\begin{definition}
-  \label{def_spectrahedra_Kn}
-  A \emph{spectrahedron in $K^n$} is any affine section of a set of the form
-  $$
-  \mathcal{S}_A = \varphi_A^{-1}(K^{d \times d}_+) = \{x \in K^n : A_0+x_1A_1+\cdots+x_nA_n \succeq 0\}
-  $$
-  for some $d\in \mathbb{N}$,
-  where $\varphi_A : K^n \to \mathcal{L} \subset K^{d \times d}$ is the map
-  $\varphi_A(x) = A_0+x_1A_1+\cdots+x_nA_n$, and $\mathcal{L} = A_0+\span{A_1,\ldots,A_n}$.
-\end{definition}
-
-Remark that the map $\varphi_A$ in \Cref{def_spectrahedra_Kn} is onto $\mathcal{L}$ but not
-injective, unless $A_1,\ldots,A_n$ are linearly independent. Moreover $K^n$ (and thus every affine
-subset of $K^n$) is itself a spectrahedron, choosing $A_0 \succeq 0$ and $A_1=A_2=\cdots=A_n=0$.
-
-The class of spectrahedra in $K^{d \times d}$ (or in $K^n$) is closed under intersection: indeed one
-has $(\mathcal{L}_1 \cap K^{d \times d}_+) \cap (\mathcal{L}_2 \cap K^{d \times d}_+) =
-(\mathcal{L}_1 \cap \mathcal{L}_2) \cap K^{d \times d}_+$
-, for two affine spaces
-$\mathcal{L}_1 = A_0+\span{A_1,\ldots,A_n}$ and $\mathcal{L}_2 = A_0+\span{B_1,\ldots,B_n}$,
-and
-$(L_1 \cap \mathcal{S}_A) \cap (L_2 \cap S_B) = (L_1\cap L_2) \cap S_{\diag(A,B)}$ for
-two affine spaces $L_1,L_2 \subset K^n$.
-Moreover this class contains polyhedra in $K^n$.
-
-\begin{proposition}
-  A polyhedron in $K^n$ is a spectrahedron in $K^n$.
-\end{proposition}
-\begin{proof}
-  Assume $P = L \cap M$ be a polyhedron in $K^n$, with
-  $L = \{x \in K^n : \val \ell_i(x) \geq 0, i=1, \ldots, d\}$
-  and $M = \{x \in K^n : \val m_j(x) = +\infty, j=1, \ldots, e\}$,
-  for some $d, e \in \mathbb{N}$.
-  Let $A_0,A_1,\ldots,A_n \in K^{d \times d}$ be such that
-  $$
-  \varphi_A(x) := A_0+x_1A_1+\cdots+x_nA_n = \diag(\ell_1(x), \ldots, \ell_d(x)).
-  $$
-  One has $L = \mathcal{S}_A = \varphi_A^{-1}(K^{d \times d}_+)$. Since $M \subset K^n$ is affine, 
-  $P$ is a spectrahedron in $K^n$.
-%  %and hence
-%  %$$
-%  %P = \{x \in K^n : x = Ty \in M, \varphi_A(x) \succeq 0\}.
-%  %$$
-%
-%  \vspace{1cm}
-%  In other words, we showed that there exist $d \in \mathbb{N}$ and
-%  $A_0,A_1,\ldots,A_n \in K^{d \times d}$ such that $P = \mathcal{S}_A$, as stated.
-%%% OLD PROOF
-%  Let $\ell_i,m_j \in K[x]_1$, for $i=1,\ldots,d$ and $j=1,\ldots,e$, and let $P = Q \cap L \subset K^n$
-%  be a polyhedron as in \Cref{def_polyhedra}, for $Q = \{x \in K^n : \val(\ell_i) \geq 0, i=1,\ldots,d\}$
-%  and $L = \{x \in K^n : \val(m_j) = +\infty, j=1,\ldots,e\}$.
-%  First, denote by $A(x) = \ell_1 \oplus \cdots \oplus \ell_d \in K[x]^{d\times d}_1$,
-%  so that $A(x) = A_0+x_1A_1+\cdots+x_nA_n$ for some (diagonal) $A_i \in K^{d\times d}$.
-%  We might assume that $A_0,A_1,\ldots,A_n$ are affinely independent, so that the mapping
-%  $\varphi(x) = A(x)$ is injective. 
-%  First, remark that $Q=\mathcal{S}_A$ and thus $\varphi(Q) = \mathcal{L} \cap K^{d\times d}$, with
-%  $\mathcal{L} = A_0+\span{A_1,\ldots,A_n}$ is a spectrahedron.
-%  Next, remark that $L \subset K^n$ is the affine space defined by equations $m_1=\ldots=m_e=0$,
-%  hence $\varphi(L) \subset K^{d\times d}$ is an affine space. Since $\varphi$ is injective,
-%  one has $\varphi(P) = \varphi(Q \cap L) = \varphi(Q) \cap \varphi(L)$ which is the intersection
-%  of a spectrahedron with an affine space, thus a spectrahedron.
-%  %Define $B = m_1 \oplus \cdots \oplus m_e \in K[x]^{e\times e}_1$
-\end{proof}
-
-Spectrahedra form a strict generalization of polyhedra:
-
-\begin{example}
-  The spectrahedron
-  \[
-  \mathcal{S} = \left\{x \in K : \begin{bmatrix} 0 & x + \pi^{-1} \\ x & 0 \end{bmatrix} \succeq 0\right\}
-  \] 
-  is not a polyhedron.
-\end{example}
-\begin{proof}
-  By \Cref{caracsdp}, one has $\mathcal{S} = \{x \in K : \val(x(x + \pi^{-1})) \geq 0\} =
-  \{x \in K: \val x \ge 1\} \cup \{x \in K: \val (x - \pi^{-1}) \ge 1\}$ which is not a ball.
-  Therefore, by \Cref{cor:caracdim1}, $\mathcal{S}$ is not a polyhedron.
-\end{proof}
-
-\begin{definition}
-  A subset $S$ of $K^n$ is said \emph{semialgebraic} if it is defined by finite unions and intersections
-  of sets defined by equalities of the form $\{x \in K^n  : p(x) = 0\}$
-  and of sets defined by inequalities of the form $\{ x\in K^n : \val p(x) \geq 0\}$, for polynomials
-  $p \in K[x]$.
-\end{definition}
-
-\begin{proposition}
-  Spectrahedra in $K^n$ are semialgebraic sets. 
-\end{proposition}
-\begin{proof}
-  Let $\mathcal{S}_A \subset K^n$ be a spectrahedron, for some linear matrix $A = A_0+\sum_{i=1}^n x_i A_i$. 
-  Denote by $p_i \in K[x]$ the $i$-th coefficient of $\chi_{A}$, $i=0,\ldots,d$.
-  By \Cref{caracsdp} one has:
-  $$
-  \mathcal{S}_A = \left\{x \in K^n : \chi_{A} \in \OK[T]\right\}
-  = \bigcap_{i=0}^d \{x \in K^n : \val(p_i(x)) \geq 0\}.
-  $$
-\end{proof}
-
-%\corentin{ Une autre définition qu'il pourrait être intéressant d'explorer. Attention! Pas les mêmes propriétés.}
-%\begin{definition}[Alternative definition]
-%  Let $A_0, ..., A_n, B_0, ..., B_n \in M_{d,d}(K)$.
-We denote as $S^+_A$ the set $S_{A}^+ = \left\{ x \in K^n : A_0 + x_1 A_1+ ...+x_nA_n \succeq 0  \right\}$ and $S^-_B$ denotes the set $S^-_B = \left\{ x \in K^n : B_0 + x_1 B_1+ ...+x_nB_n \preceq 0\right\}$.
-The set $S_A,B := S_A^+ \cup S_B^-$ is called a \emph{spectrahedron}.
-%\end{definition}
-
-\subsection{Polyannuli}
-
-Denote by $\R^*_+$ the set of positive real numbers.
-
-\begin{definition}[Polyannulus]\label{def_annuli}
-  A set of the form $\mathcal{C} = \{x \in K \,|\, a \le \val(x) \le b\}$, for $a,b \in \R^*_+$,
-  is called \emph{annulus}. A product $\mathcal{C}_1 \times \mathcal{C}_2 \times \cdots \times \mathcal{C}_n \subset K^n$,
-  where each $C_i \subset K$ is an annulus, is called a \emph{polyannulus}.
-\end{definition}
-
-\begin{definition}[Semidefinite-representable set]\label{def_semi_def_rep_set}
-  A set $\mathcal{R} \subset K^n$ is called
-  \emph{semide\-fi\-nite-re\-pre\-sen\-ta\-ble (SDR)} if there exist $m,d \in \N$ and
-  matrices $\{A_i,B_j : i = 0, \ldots, n, j = 1, \ldots, m\} \subset K^{d \times d}$ such that
-  $$
-  \mathcal{R} = \left\{x \in K^n : \exists y \in K^m, A_0+\sum_{i=1}^n x_iA_i + \sum_{j=1}^m y_jB_j \succeq 0\right\}
-  $$
-  that is, $x \in \mathcal{R}$ if and only if there exists $y \in K^m$ such that
-  $(x,y) \in S_M \subset K^{n+m}$, for some pencil $M(x,y) = A_0+\sum_{i=1}^n x_iA_i + \sum_{j=1}^m y_jB_j$.
-  The integer $m$ is called the \emph{height} of the representation and $d$ its \emph{degree}.
-\end{definition}
-
-Of course a spectrahedron $\mathcal{S}_A = \varphi_A^{-1}(K^{d \times d})$ is SDR with height $m=0$ and degree
-$d$. In order to distinguish between spectrahedra and possibly non-spectrahedral semidefinite-representable sets
-we usually call \emph{spectrahedral shadows} the SDR sets with height $m>0$.
-
-\begin{theorem}
-Polyannuli in $K^n$ are spectrahedral shadows with height $m=n$ and degree $d=4n$.
-\end{theorem}
-\begin{proof}
-  Let $\mathcal{C} = \mathcal{C}_1 \times \cdots \times \mathcal{C}_n \subset K^n$ be as in \Cref{def_annuli},
-  for some annuli $\mathcal{C}_1,\ldots,\mathcal{C}_n \subset K$. We claim that each $\mathcal{C}_i$ is a spectrahedral
-  shadow of height $1$ and degree $4$. Assume $\mathcal{C}_i = \{x_i \in K : a_i \leq \val(x_i) \leq b_i\}$
-  for some $a_i, b_i \in \R^*_+$ with $a_i < b_i$. Consider the spectrahedron
-  $\mathcal{S}_{M^{(i)}} \subset K^2$ defined by
-  $$
-  \mathcal{S}_{M^{(i)}} = \left\{(x_i,y_i) \in K^2 :
-  M^{(i)}(x_i,y_i) := \diag\left(\pi^a x_i, \pi^{-b} y_i,
-  \begin{bmatrix}
-    \pi^{-1} & -\pi^{-1} x_i  \\
-    \pi^{-1} y_i & - \pi^{-1} \\
-  \end{bmatrix}\right) \succeq 0
-  \right\}.
-  $$
-  We claim that $x_i \in \mathcal{C}_i$ if and only if there exists $y_i \in K$ such that $(x_i,y_i) \in
-  \mathcal{S}_{M^{(i)}}$.
-  Indeed, by \Cref{caracsdp}, $M^{(i)}(x_i,y_i) \succeq 0$ if and only if $(x_i,y_i)$ is a solution of the system
-  of inequalities:
-  \begin{equation}
-    \label[type]{eq:annulussyst}
-    \begin{cases}
-      \val(\pi^a x_i) \ge 0 \\
-  \val(\pi^{-b} y_i) \ge 0\\
-  \val(\pi^{-1}- \pi^{-1}) = +\infty \ge 0\\
-  \val(\pi^{-2}\left( x_iy_i-1 \right))  \ge 0 
-\end{cases}
-\iff	
-\begin{cases} 
-  \val\left(x_i\right)\ge a\\
-  \val\left(y_i\right)\ge -b\\
-  \val\left(x_iy_i-1 \right) \ge 2
-\end{cases}
-\end{equation} 
-  %Therefore, if $(x, y)$ verifies \eqref{eq:annulussyst} then $\val\left(x\right)\ge a$, $\val\left(y\right)\ge -b$ and $ \left( xy-1 \right) \ge 2$.
-  The last inequality implies that $\val\left(x_i\right)+\val\left(y_i\right)=\val\left(x_iy_i\right) = \val\left(-1\right) =0$ and therefore that $\val\left(x_i\right)=-\val\left(y_i\right)\le -(-b) = b$, so $x_i \in \mathcal{C}_i$.
-Reciprocally if $x_i \in \mathcal{C}_i$ then $(x_i,x_i^{-1})$ is a solution of \eqref{eq:annulussyst}.
-This proves our claim.
-Finally, since $\mathcal{C} = \mathcal{C}_1 \times \cdots \times \mathcal{C}_n$, one has
-\begin{equation*}
-  \begin{aligned}
-    \mathcal{C} &=
-    \{x=(x_1,\ldots,x_n) \in K^n : \exists y = (y_1,\ldots,y_n) \in K^n, (x_i,y_i) \in
-    \mathcal{S}_{M^{(i)}}, i=1,\ldots,n\} \\
-    &= \{x \in K^n : \exists y \in K^n, (x,y) \in \mathcal{S}_M\}
-  \end{aligned}
-\end{equation*}
-with $\mathcal{S}_M = \diag\left(M^{(1)}, M^{(2)}, \ldots, M^{(n)}\right) \in K[x,y]^{4n \times 4n}.$
-\end{proof}
-
-We conclude proving that, in general, annuli are not spectrahedral.
-
-\begin{proposition}
-If the residue field $\kappa$ is infinite, then no (non-trivial) annulus of $K$ can be a spectrahedron of $K.$
-\end{proposition}
-\begin{proof}
-By Definition \ref{def_spectrahedra_Kn}, a spectrahedron in $K$ 
-can be defined as the set $\{x \in K : A_0+x_1A_1 \succeq 0\}$
-for some integer $n$ and matrices $A_0$ and $A_1$ in $K^{n \times n}$.
-Thanks to Theorem \ref{caracsdp},
-this set corresponds to an intersection of the form
-$\cap_{i=0}^{n-1} \{ x \in K : \val(a_i(x)) \geq 0 \},$
-for some polynomials $a_i$'s, univariate over $K$.
-
-Following Julian Rüth's PhD thesis \cite{ruth_models_2015},
-the set $\{ x \in K : \val(a_i(x)) \geq 0 \}$
-is denoted by $\textrm{Disk}(a_i,0)$ and is called 
-a diskoid.
-By \cite[Lemma 4.44]{ruth_models_2015}, the intersection
-of two diskoids is either empty or a diskoid.
-Consequently, spectrahedra of $K$ are diskoids.
-
-By \cite[Lemma 4.43]{ruth_models_2015}, if $K$
-contains the roots of $\Phi$ then the diskoid
-$D=\textrm{Disk}(\Phi, \lambda)$ is the finite union
-of closed balls of equal radius centered at the roots of $f$ (and their common radius can be made explicit).
-
-Finally, if $\kappa$ is infinite, one can remark that the sphere
-$\{x \in K \,|\,  \val(x) =0\}$ is equal to the infinite disjoint union $\amalg_{l \in \kappa} B(b_l, \vert \pi \vert)$ for some 
-representatives $b_l \in O_K$ of the classes of $O_K / \pi O_K=\kappa.$
-It thus can not be covered by a finite amount of balls of radius $\vert \pi \vert$
-and if one take any ball of radius $1$ centered at a point of the sphere, then one gets the whole
-$B(0,1).$
-A direct generalization of this argument proves that
-if $\kappa$ is infinite, no (non trivial) annulus can be equal to
-a finite union of balls. Thus, no (non trivial) annulus can be a diskoid and finally, no (non trivial) annulus can be a spectrahedron.
-\end{proof}
-
-%\subsection{Polyhedrality}
-%Cf. \cite{bhardwaj2015deciding}
-
-%\section{Linear matrix inequalities}
-
-%\section{Other questions}
-%\begin{itemize}
-%\item The projection of a real polyhedron is a real polyhedron (thanks to Fourier-Motzkin elimination procedure). Is it the same for $K$-polyhedra?
-%\item Annuli are semidefinite representable, we should remark/prove that they are not spectrahedra.
-%\end{itemize}
-
-\section*{Acknowledgments}
-The second author acknowledges support from the ANR Project ``HYPERSPACE'' (ANR-21-CE48-0006-01).
-
-\printbibliography
+\bibliographystyle{ACM-Reference-Format}
+\bibliography{refs}
 

### 2025-12-10 issac2026/main.tex
commit by Simone

--- 2025-10-10 article/paper_padic_spec.tex
@@
 \usepackage{amsthm}
-\usepackage{amssymb}
+%\usepackage{amssymb} %%% ça ne fait pas compiler en acmart
 \usepackage{amsfonts}
@@
 
-\usepackage{biblatex}
-\addbibresource{../rapport/bibstage.bib}
-
-\title{\Large \bf On semidefinite-representable sets over valued fields}
-
-\begin{document}
-
-\author{Corentin Cornou$^{1}$, Simone Naldi$^{2}$ and Tristan Vaccon$^{2}$}
-
-\footnotetext[1]{ENS Paris-Saclay, Université Paris-Saclay, France.}
-\footnotetext[2]{Université de Limoges, CNRS, XLIM, UMR 7252, F-87000 Limoges, France.}
-%\footnotetext[3]{Sorbonne Université, CNRS, LIP6, Equipe PolSys, F-75005 Paris, France.}
-
-\date{Draft of \today}
-
-\maketitle
+%\usepackage{biblatex}
+%\addbibresource{../rapport/bibstage.bib}
+
+\title{On semidefinite-representable sets over valued fields}
+
+\author{Simone Naldi}
+\affiliation{
+    \institution{Université de Limoges, CNRS, XLIM}
+    \city{Limoges}
+    \country{France}
+}
+
+\author{Tristan Vaccon}
+\affiliation{
+    \institution{Université de Limoges, CNRS, XLIM}
+    \city{Limoges}
+    \country{France}
+}
+
+\author{Corentin Cornou}
+\affiliation{
+    \institution{}
+    \city{}
+    \country{France}
+}
+
+%\copyrightyear{2026}
+%\acmYear{2026}
+%\setcopyright{cc}
+%\setcctype{by}
+%\acmConference[ISSAC '26]{International Symposium on Symbolic and Algebraic Computation}{Date}{Place}
+%\acmBooktitle{International Symposium on Symbolic and Algebraic Computation (ISSAC '26), date, place}\acmDOI{}
+%\acmISBN{}
+
+%\begin{CCSXML}
+%<ccs2012>
+%   <concept>
+%       <concept_id>10010147.10010148.10010149.10010150</concept_id>
+%       <concept_desc>Computing methodologies~Algebraic algorithms</concept_desc>
+%       <concept_significance>500</concept_significance>
+%       </concept>
+% </ccs2012>
+%\end{CCSXML}
+
+%\ccsdesc[500]{Computing methodologies~Algebraic algorithms}
+
+\keywords{keywords}
 
 \begin{abstract}
-  \noindent
   Real polyhedra and real spectrahedra (or their projections) are respectively the feasible sets
@@
 
-%\tableofcontents
+\begin{document}
+\maketitle
 
@@
 
-\printbibliography
+\bibliographystyle{ACM-Reference-Format}
+\bibliography{refs}
 

### 2025-12-10 issac2026/main.tex
commit by Simone

@@
 \usepackage{hyperref}
-
 \usepackage{cleveref}
@@
 
+\newtheorem{theorem}{Theorem}[section]
+\newtheorem{lemma}[theorem]{Lemma}
+\newtheorem{proposition}[theorem]{Proposition}
+\newtheorem{corollary}[theorem]{Corollary}
+%\newtheorem{algorithm}[theorem]{Algorithm}
+\newtheorem{conjecture}[theorem]{Conjecture}
+\newtheorem{condition}[theorem]{Condition}
+\newtheorem{definition}[theorem]{Definition}
+\newtheorem{assumption}[theorem]{Assumption}
+\newtheorem{remark}[theorem]{Remark}
+\newtheorem{problem}[theorem]{Problem}
+\newtheorem{example}[theorem]{Example}
+\newtheorem{notation}[theorem]{Notation}
+
 %p-adic commands
@@
 
+%\usepackage[natbib=true]{biblatex}
 %\usepackage{biblatex}
@@
 \centering
+\scalebox{0.5}{
 \begin{tikzpicture}[
@@
   box/.style={draw, rounded corners, minimum width=2.2cm, minimum height=1cm, align=center},
-  thickarrow/.style={->, >=Stealth, line width=1.2pt},
+  thickarrow/.style={->, >=Stealth, line width=1.2pt}
 ]
@@
 \end{tikzpicture}
+}
 \caption{Strategy of proof of Theorem \ref{theo:DI}.}

### 2025-12-12 issac_biblatex_tentative/paper_CNV.tex
commit by Simone

--- 2025-12-10 issac2026/main.tex
@@
-\documentclass[sigconf]{acmart}
+%%
+%% This is file `sample-sigconf-biblatex.tex',
+%% generated with the docstrip utility.
+%%
+%% The original source files were:
+%%
+%% samples.dtx  (with options: `all,proceedings,sigconf-biblatex')
+%% 
+%% IMPORTANT NOTICE:
+%% 
+%% For the copyright see the source file.
+%% 
+%% Any modified versions of this file must be renamed
+%% with new filenames distinct from sample-sigconf-biblatex.tex.
+%% 
+%% For distribution of the original source see the terms
+%% for copying and modification in the file samples.dtx.
+%% 
+%% This generated file may be distributed as long as the
+%% original source files, as listed above, are part of the
+%% same distribution. (The sources need not necessarily be
+%% in the same archive or directory.)
+%%
+%%
+%% Commands for TeXCount
+%TC:macro \cite [option:text,text]
+%TC:macro \citep [option:text,text]
+%TC:macro \citet [option:text,text]
+%TC:envir table 0 1
+%TC:envir table* 0 1
+%TC:envir tabular [ignore] word
+%TC:envir displaymath 0 word
+%TC:envir math 0 word
+%TC:envir comment 0 0
+%%
+%% The first command in your LaTeX source must be the \documentclass
+%% command.
+%%
+%% For submission and review of your manuscript please change the
+%% command to \documentclass[manuscript, screen, review]{acmart}.
+%%
+%% When submitting camera ready or to TAPS, please change the command
+%% to \documentclass[sigconf]{acmart} or whichever template is required
+%% for your publication.
+%%
+%%
+\documentclass[sigconf,natbib=false]{acmart}
+%%
+%% \BibTeX command to typeset BibTeX logo in the docs
+\AtBeginDocument{%
+  \providecommand\BibTeX{{%
+    Bib\TeX}}}
+
+%% Rights management information.  This information is sent to you
+%% when you complete the rights form.  These commands have SAMPLE
+%% values in them; it is your responsibility as an author to replace
+%% the commands and values with those provided to you when you
+%% complete the rights form.
+\setcopyright{acmlicensed}
+\copyrightyear{2018}
+\acmYear{2018}
+\acmDOI{XXXXXXX.XXXXXXX}
+%% These commands are for a PROCEEDINGS abstract or paper.
+\acmConference[Conference acronym 'XX]{Make sure to enter the correct
+  conference title from your rights confirmation email}{June 03--05,
+  2018}{Woodstock, NY}
+%%
+%%  Uncomment \acmBooktitle if the title of the proceedings is different
+%%  from ``Proceedings of ...''!
+%%
+%%\acmBooktitle{Woodstock '18: ACM Symposium on Neural Gaze Detection,
+%%  June 03--05, 2018, Woodstock, NY}
+\acmISBN{978-1-4503-XXXX-X/2018/06}
+
+%%
+%% Submission ID.
+%% Use this when submitting an article to a sponsored event. You'll
+%% receive a unique submission ID from the organizers
+%% of the event, and this ID should be used as the parameter to this command.
+%%\acmSubmissionID{123-A56-BU3}
+
+%%
+%% For managing citations, it is recommended to use bibliography
+%% files in BibTeX format.
+%%
+%% You can then either use BibTeX with the ACM-Reference-Format style,
+%% or BibLaTeX with the acmnumeric or acmauthoryear sytles, that include
+%% support for advanced citation of software artefact from the
+%% biblatex-software package, also separately available on CTAN.
+%%
+%% Look at the sample-*-biblatex.tex files for templates showcasing
+%% the biblatex styles.
+%%
+
+%%
+%% The majority of ACM publications use numbered citations and
+%% references, obtained by selecting the acmnumeric BibLaTeX style.
+%% The acmauthoryear BibLaTeX style switches to the "author year" style.
+%%
+%% If you are preparing content for an event
+%% sponsored by ACM SIGGRAPH, you must use the acmauthoryear style of
+%% citations and references.
+%%
+%% Bibliography style
+\RequirePackage[
+  datamodel=acmdatamodel,
+  style=acmnumeric,
+  ]{biblatex}
+
+%% Declare bibliography sources (one \addbibresource command per source)
+\addbibresource{refs.bib}
 
@@
 
-%\usepackage[natbib=true]{biblatex}
-%\usepackage{biblatex}
-%\addbibresource{../rapport/bibstage.bib}
-
+%%
+%% end of the preamble, start of the body of the document source.
+\begin{document}
+
+%%
+%% The "title" command has an optional parameter,
+%% allowing the author to define a "short title" to be used in page headers.
 \title{On semidefinite-representable sets over valued fields}
+
+\author{Corentin Cornou}
+\affiliation{
+    \institution{ENS}
+    \city{Paris}
+    \country{France}
+}
 
@@
 
-\author{Corentin Cornou}
-\affiliation{
-    \institution{}
-    \city{}
-    \country{France}
-}
-
-%\copyrightyear{2026}
-%\acmYear{2026}
-%\setcopyright{cc}
-%\setcctype{by}
-%\acmConference[ISSAC '26]{International Symposium on Symbolic and Algebraic Computation}{Date}{Place}
-%\acmBooktitle{International Symposium on Symbolic and Algebraic Computation (ISSAC '26), date, place}\acmDOI{}
-%\acmISBN{}
-
-%\begin{CCSXML}
-%<ccs2012>
-%   <concept>
-%       <concept_id>10010147.10010148.10010149.10010150</concept_id>
-%       <concept_desc>Computing methodologies~Algebraic algorithms</concept_desc>
-%       <concept_significance>500</concept_significance>
-%       </concept>
-% </ccs2012>
-%\end{CCSXML}
-
-%\ccsdesc[500]{Computing methodologies~Algebraic algorithms}
-
-\keywords{keywords}
-
+%%
+%% By default, the full list of authors will be used in the page
+%% headers. Often, this list is too long, and will overlap
+%% other information printed in the page headers. This command allows
+%% the author to define a more concise list
+%% of authors' names for this purpose.
+\renewcommand{\shortauthors}{Cornou et al.}
+
+%%
+%% The abstract is a short summary of the work to be presented in the
+%% article.
 \begin{abstract}
@@
 
-\begin{document}
+%%
+%% The code below is generated by the tool at http://dl.acm.org/ccs.cfm.
+%% Please copy and paste the code instead of the example below.
+%%
+\begin{CCSXML}
+<ccs2012>
+ <concept>
+  <concept_id>00000000.0000000.0000000</concept_id>
+  <concept_desc>Do Not Use This Code, Generate the Correct Terms for Your Paper</concept_desc>
+  <concept_significance>500</concept_significance>
+ </concept>
+ <concept>
+  <concept_id>00000000.00000000.00000000</concept_id>
+  <concept_desc>Do Not Use This Code, Generate the Correct Terms for Your Paper</concept_desc>
+  <concept_significance>300</concept_significance>
+ </concept>
+ <concept>
+  <concept_id>00000000.00000000.00000000</concept_id>
+  <concept_desc>Do Not Use This Code, Generate the Correct Terms for Your Paper</concept_desc>
+  <concept_significance>100</concept_significance>
+ </concept>
+ <concept>
+  <concept_id>00000000.00000000.00000000</concept_id>
+  <concept_desc>Do Not Use This Code, Generate the Correct Terms for Your Paper</concept_desc>
+  <concept_significance>100</concept_significance>
+ </concept>
+</ccs2012>
+\end{CCSXML}
+
+\ccsdesc[500]{Do Not Use This Code~Generate the Correct Terms for Your Paper}
+\ccsdesc[300]{Do Not Use This Code~Generate the Correct Terms for Your Paper}
+\ccsdesc{Do Not Use This Code~Generate the Correct Terms for Your Paper}
+\ccsdesc[100]{Do Not Use This Code~Generate the Correct Terms for Your Paper}
+
+%%
+%% Keywords. The author(s) should pick words that accurately describe
+%% the work being presented. Separate the keywords with commas.
+\keywords{Do, Not, Use, This, Code, Put, the, Correct, Terms, for,
+  Your, Paper}
+
+\received{20 February 2007}
+\received[revised]{12 March 2009}
+\received[accepted]{5 June 2009}
+
+%%
+%% This command processes the author and affiliation and title
+%% information and builds the first part of the formatted document.
 \maketitle
@@
 
-\bibliographystyle{ACM-Reference-Format}
-\bibliography{refs}
+\printbibliography
 
 \end{document}
+\endinput
+%%
+%% End of file `sample-sigconf-biblatex.tex'.

### 2025-12-22 issac_biblatex_tentative/paper_CNV.tex
modifs in section 2

@@
 \setcopyright{acmlicensed}
-\copyrightyear{2018}
-\acmYear{2018}
+\copyrightyear{2026}
+\acmYear{2026}
 \acmDOI{XXXXXXX.XXXXXXX}
 %% These commands are for a PROCEEDINGS abstract or paper.
-\acmConference[Conference acronym 'XX]{Make sure to enter the correct
-  conference title from your rights confirmation email}{June 03--05,
-  2018}{Woodstock, NY}
+\acmConference[ISSAC 2026]{the International Symposium
+on Symbolic and Algebraic Computation}{July 13--17,
+  2026}{Oldenburg, Germany}
 %%
@@
   datamodel=acmdatamodel,
-  style=acmnumeric,
-  ]{biblatex}
+  style=acmnumeric]{biblatex}
 
@@
 \begin{abstract}
-  Real polyhedra and real spectrahedra (or their projections) are respectively the feasible sets
-  of linear and semidefinite programming, and form the family of
-  semidefinite-representable sets. This paper investigates versions of these sets and of
+  Polyhedra and spectrahedra over the real numbers or, more generally,
+  their images through linear maps, are respectively the feasible sets
+  of linear and semidefinite
+  programming, and form the family of semidefinite-representable sets.
+  This paper investigates versions of these sets and of
   the related optimization problems with data over a valued field $K$.
-  For $K$-polyhedra and linear programming over $K$ we give an algorithm based on computation
-  of Smith normal forms.
-  We prove that basic properties of semidefinite-representable sets generalize to this setting.
-  In particular, we showcase examples of non-polyhedral $K$-spectrahedra and of sets that are
-  semidefinite representable over $K$ but are not $K$-spectrahedra.
+  For $K$-polyhedra and linear programming over $K$ we give an algorithm
+  based on computation of Smith normal forms.
+  We prove that basic properties of semidefinite-representable sets generalize
+  to the valued setting.
+  In particular, we showcase examples of non-polyhedral $K$-spectrahedra and
+  of sets that are semidefinite representable over $K$ but are not $K$-spectrahedra.
 \end{abstract}
@@
 
-The study of polyhedra and of linear programming (LP) is at the heart of convex geometry and optimization, inasmuch as several optimization problems can be cast as, or relaxed to LP.
-An important generalization of LP is semidefinite programming (SDP), namely the problem of minimizing a linear function over the set of positive semidefinite affine combinations of some real symmetric matrices.
-The latter problem has interested the community of real algebraic geometry and polynomial optimization, mostly because of the relaxation method known as moment-SOS (or Lasserre) hierarchy \cite{henrion2020moment}.
-
-The main motivation for studying the effective aspects of SDP is the fact that, despite several properties of LP extend to SDP, the complexity status of SDP is, contrary to the LP case, widely open.
+The study of real polyhedra and of linear programming (LP) is at
+the heart of convex geometry and optimization, inasmuch as several
+optimization problems can be cast as, or relaxed to LP.
+An important generalization of LP is semidefinite programming (SDP),
+namely the problem of minimizing a linear function over the set of
+positive semidefinite affine combinations of some real symmetric matrices.
+The latter problem has interested the community of real algebraic
+geometry and polynomial optimization, mostly because of the relaxation
+method known as moment-SOS (or Lasserre) hierarchy \cite{henrion2020moment}.
+
+The main motivation for studying the effective aspects of SDP is the fact
+that, despite several properties of LP extend to SDP, the complexity status of SDP is, contrary to the LP case, widely open.
 Ramana's construction \cite{ramana1997exact} implies a series of general results: in the Blum-Shub-Smale real numbers machines model \cite{blum1989theory}, the feasibility of SDP is in $\text{NP} \cap \text{co-NP}$, whereas it is not known to be in NP in the Turing model; checking boundedness, attainability and optimality can be polynomially reduced to the feasibility of SDP \cite{ramana1997exact}.
@@
 For exact computation, complexity bounds are known based either on general quantifier elimination \cite{ramana1997exact,porkolab1997complexity} and explicit algorithms exist based on a dedicated application of the so-called critical point method, and exploiting the determinantal structure of the constraints \cite{henrion2016exact,NALDI2018206}.
-A complexity analysis for the computation of an approximate solution of an SDP can be made based on the ellipsoid algorithm \cite{khachiyan1979polynomial,grotschel1981ellipsoid} or on interior-point methods \cite{de2016turing}; in this approximation framework, SDP is solvable in polynomial time in the input size (\emph{i.e.} matrix size, number of variables, bit size of the coefficients), $\log(\frac{1}{\varepsilon})$ (where $\varepsilon$ is the target precision) and $\log(\frac{R}{r})$, where $r,R$ are radii of balls respectively included in and containing the feasible set, cf.
+%%% CE PARAGRAPHE ME PARAIT MOINS PRIORITAIRE
+% A complexity analysis for the computation of an approximate solution of an SDP can be made based on the ellipsoid algorithm \cite{khachiyan1979polynomial,grotschel1981ellipsoid} or on interior-point methods \cite{de2016turing}; in this approximation framework, SDP is solvable in polynomial time in the input size (\emph{i.e.} matrix size, number of variables, bit size of the coefficients), $\log(\frac{1}{\varepsilon})$ (where $\varepsilon$ is the target precision) and $\log(\frac{R}{r})$, where $r,R$ are radii of balls respectively included in and containing the feasible set, cf.
 \cite{grotschel1981ellipsoid} or \cite[Thm.1.1]{de2016turing} (see also \cite[Sec.1.9]{deKlerk}).
@@
 
+\paragraph{Outline.}
 %\subsection{Context and motivations}
@@
 
-Throughout the paper, $(K,\val)$ refers to a complete valued field, namely $K$ is a field
+Throughout the paper, $(K,\val)$ refers to a complete valued field, {\it i.e.} $K$ is a field
 and $\val : K \twoheadrightarrow \Gamma \cup \{+\infty\}$ is a valuation on $K$, $\Gamma$ an
-ordered abelian group. The valuation is often assumed to be discrete ({\it i.e.} $\Gamma=\ZZ$)
-with $\pi \in K$ a uniformizer. The valuation ring of $K$ is
+ordered abelian group. The valuation is often assumed to be discrete ($\Gamma=\ZZ$)
+with uniformizer $\pi \in K$. The valuation ring of $K$ is
 $$
@@
 $$
-$\kappa = \OK/\mathfrak{m}_K$ its residue field, with
-$\mathfrak{m}_K = \{x \in K : \val(x) > 0\}$. An element of $\OK$ is called integral (at $\val$).
+and $\kappa = \OK/\mathfrak{m}_K$ its residue field, with
+$\mathfrak{m}_K = \{x \in K : \val(x) > 0\}$.
+An element of $\OK$ is called integral (at\footnote{Je comprends pas, c'est bien integral
+à la valuation?} $\val$).
 For $k \in \N$, we write $O(\pi^k)$ for $\pi^k \OK$.
@@
 
-The $K$-vector space of polynomials of degree $\leq d$ on $x=(x_1,\ldots,x_n)$
+The $K$-vector space of polynomials of degree $\leq d$ on variables
+$x=(x_1,\ldots,x_n)$
 with coefficients in $K$ is denoted by $K[x]_{d}$. The ring of matrices of
@@
 $B_1,\ldots,B_d$ are denoted by $\diag(B_1, \ldots, B_d)$, the null matrix of
-size $p \times q$ by ${\bf 0}_{p,q}$, and the identity matrix of size $t \times t$ by $I_t$.
+size $p \times q$ by ${\bf 0}_{p,q}$, and the $t \times t$ identity matrix by $I_t$.
 
 We recall the definition of Smith Normal Form, in our context.
+
 \begin{definition}[Smith Normal Form]\label{smith_nf}
@@
 
-Let us now give a short introduction to classical ({\it i.e.} real) polyhedra and spectrahedra.
+Let us now give a short introduction to classical ({\it i.e.} real) polyhedra and
+spectrahedra.
 Let $\sym_d(\R) \subset \R^{d\times d}$ be the vector space of $d \times d$ real symmetric
@@
 \begin{example}\label{ell3}
-  Let $d=n=3$. The $3$-elliptope is the three-dimensional spectrahedron given by
-  $$
-  \mathcal{E}_3 :=
+  Let $d=n=3$. The $3$-elliptope is the three-di\-men\-sio\-nal spectrahedron
+  $\mathcal{E}_3$ given by
+  $$
   \left\{
@@
   \in \R^3 :
-  \begin{bmatrix}
+  \left[
+  \begin{smallmatrix}
     1 & x_1 & x_2 \\
@@
     x_2 & x_3 & 1
-  \end{bmatrix}
+  \end{smallmatrix}
+  \right]
   \succeq 0
@@
   \in \R^3 :
-  \begin{array}{r}
-    3-x_1^2-x_2^2-x_3^2 \geq 0 \\
-    1+2x_1x_2x_3-x_1^2-x_2^2-x_3^2 \geq 0
+  \begin{array}{l}
+    {\footnotesize 3-\sum x_i^2 \geq 0} \\
+    {\footnotesize 1+2x_1x_2x_3-\sum x_i^2 \geq 0}
   \end{array}
@@
   $$
-  The polynomials on the right are the (non-constant) coefficients of the univariate polynomial
-  $p(t) = \det(A(x)+t I_3)$,
-  whose roots are the opposites of the eigenvalues of the defining matrix. Equivalently $\mathcal{E}_3$
+  The polynomials on the right are the (non-constant) coefficients of the
+  univariate polynomial $p(t) = \det(A(x)+t I_3)$. Equivalently $\mathcal{E}_3$
   is defined by positivity of the principal minors of the defining matrix:
   $$
-  1-x_1^2 \geq 0, \,\,\, 1-x_2^2 \geq 0, \,\,\, 1-x_3^2 \geq 0 \,\,\, \text{ and } \,\,\, 1+2x_1x_2x_3-x_1^2-x_2^2-x_3^2 \geq 0.$$ \exend
+  1-x_i^2 \geq 0, \, i=1,2,3, \,\,\, \text{ and } \,\,\,
+  1+2x_1x_2x_3-x_1^2-x_2^2-x_3^2 \geq 0
+  \vspace{-0.3cm}
+  $$
+  \exend
 \end{example}
@@
 spectrahedra, where the defining matrices $A_0, \ldots, A_n$ can be chosen diagonal, so that
-$A = \diag(\ell_1,\ldots, \ell_d)$. In other words, SDP is a generalization of Linear Programming (LP).
+$A = \diag(\ell_1,\ldots, \ell_d)$ for some affine functions $\ell_i$. In other words, SDP generalizes LP.
 
@@
 \label{fermat_quartic}
-The basic closed semialgebraic set $\mathcal{R} = \{(x_1,x_2) \in \R^2 : 1-x_1^4-x_2^4 \geq 0\}$ is not a spectrahedron
-but it is semidefinite representable:
-$$
-\mathcal{R} = \left\{\begin{bmatrix} x_1 \\ x_2 \end{bmatrix} \in \R^2 :
+The basic closed semialgebraic set $\mathcal{R} = \{(x_1,x_2) \in \R^2 : 1-x_1^4-x_2^4 \geq 0\}$ is not a spectrahedron but it is semidefinite representable with representation:
+$$
+%%\mathcal{R} =
+\left\{\begin{bmatrix} x_1 \\ x_2 \end{bmatrix} \in \R^2 :
 \exists\,
 \begin{bmatrix} y_1 \\ y_2 \end{bmatrix} \in \R^2, \,
+%\left[
+%  \begin{smallmatrix}
+%    1+y_1 & y_2   &   0 &   0 & 0 & 0 \\
+%      y_2 & 1-y_1 &   0 &   0 & 0 & 0 \\
+%        0 &     0 &   1 & x_1 & 0 & 0 \\
+%        0 &     0 & x_1 & y_1 & 0 & 0 \\
+%        0 &     0 &   0 &   0 & 1 & x_2 \\
+%        0 &     0 &   0 &   0 & x_2 & y_2
+%  \end{smallmatrix}
+%  \right]
 \diag\left(
-\begin{bmatrix}
+\left[
+\begin{smallmatrix}
   1+y_1 & y_2 \\
   y_2 & 1-y_1
-\end{bmatrix},
-\begin{bmatrix}
+\end{smallmatrix}
+\right],
+\left[
+\begin{smallmatrix}
   1 & x_1 \\
   x_1 & y_1
-\end{bmatrix},
-\begin{bmatrix}
+\end{smallmatrix}
+\right],
+\left[
+\begin{smallmatrix}
   1 & x_2 \\
   x_2 & y_2
-\end{bmatrix}
+\end{smallmatrix}
+\right]
 \right)

### 2025-12-23 issac_biblatex_tentative/paper_CNV.tex
commit by Simone

@@
   $$
-  \mathrm{SNF}(M) := QMP^{-1} = \diag(\pi^{a_1}, \pi^{a_2}, \ldots, \pi^{a_r}, {\bf 0}_{m-r,n-r}).
+  \mathrm{SNF}(M) \coloneq QMP^{-1} = \diag(\pi^{a_1}, \pi^{a_2}, \ldots, \pi^{a_r}, {\bf 0}_{m-r,n-r}).
   $$
@@
 $$
-\calL \cap \sym_d^+(\R) = \left\{A(x) := A_0+\sum_i x_i A_i \in \sym_d(\R) :
+\calL \cap \sym_d^+(\R) = \left\{A(x) \coloneq A_0+\sum_i x_i A_i \in \sym_d(\R) :
 A(x) \succeq 0\right\},
@@
 %\begin{array}{rcll}
-%  p^* & := & \inf_{x \in \R^n} & \left\langle c, x \right\rangle \\
+%  p^* & \coloneq & \inf_{x \in \R^n} & \left\langle c, x \right\rangle \\
 %  &    & \text{s.t.}         & A_0+\sum_{i=1}^n x_i A_i \succeq 0.
@@
   $$
-  \PP = \{x \in K^n : \val(\ell_i(x)) \geq 0, i=1,\ldots,d \text{ and }
-  \val(m_j(x)) = +\infty, j=1,\ldots,e\},
+  \PP =
+  \left\{
+  x \in K^n :
+  \begin{array}{ll}
+    \val(\ell_i(x)) \geq 0 & i=1,\ldots,d \\
+    \val(m_j(x)) = +\infty & j=1,\ldots,e
+  \end{array}
+    \right\},
   $$
@@
   The \emph{closed unit ball} $\OK^n=B_\infty(K^n)$ in $K^n$ for the supremum norm $||\cdot||_{\infty}$ is the
-  polyhedron defined as the set of $x=(x_1,\ldots,x_n) \in K^n$ such that $||x||_{\infty} =
+  polyhedron defined as the set of $x=(x_1,\ldots,x_n) \in K^n$ such that $||x||_{\infty} \coloneq
   \max_i\{\vert x_i \vert\} \leq 1$, in other words, such that $\val(x_i) \geq 0$, for all $i=1, \ldots, n$.
@@
 Conversely, let $(x_1,\dots,x_{n-1}) \in \Qc.$
-Then let $x_n := -b_n.$
+Then let $x_n \coloneq -b_n.$
 
@@
 Conversely, let $(x_1,\dots,x_{n-1}) \in \Qc.$
-Let $x_n := -a_1^{-1}(x_1+b_1).$
+Let $x_n \coloneq -a_1^{-1}(x_1+b_1).$
 Then
@@
 Let us write $\PP = \PP_I \cap \PP_E$
-with $\PP_I := \left\lbrace X \in K^n,  AX+B \geq 0 \right\rbrace$
-and $\PP_E := \left\lbrace X \in K^n,  CX+D=0 \right\rbrace = P + \overrightarrow{\PP_E}.$ 
+with $\PP_I \coloneq \left\lbrace X \in K^n,  AX+B \geq 0 \right\rbrace$
+and $\PP_E \coloneq \left\lbrace X \in K^n,  CX+D=0 \right\rbrace = P + \overrightarrow{\PP_E}.$ 
 Then $f(\PP) = f_{\PP_E}(\PP_I).$
@@
 %  $P = \{x \in K^n : \val(l_i(x)) \geq 0, m_i(x) = 0, 1 \leq i \leq d, 1 \leq j \leq e\}$.
-%  Then $P = P_I \cap P_E$ where $P_I := \{x \in K^n : \val(l_i(x)) \geq 0, 1 \leq i \leq d\}$
-%  and $P_E := \{x \in K^n : m_j(x) = 0, 1 \leq j \leq e\}$.
+%  Then $P = P_I \cap P_E$ where $P_I \coloneq \{x \in K^n : \val(l_i(x)) \geq 0, 1 \leq i \leq d\}$
+%  and $P_E \coloneq \{x \in K^n : m_j(x) = 0, 1 \leq j \leq e\}$.
 %
@@
 %Conversely, let $(x_1,\dots,x_{n-1}) \in \Qc.$
-%Then let $x_n := -b_n.$
+%Then let $x_n \coloneq -b_n.$
 %
@@
 %Conversely, let $(x_1,\dots,x_{n-1}) \in \Qc.$
-%Let $x_n := -a_1^{-1}(x_1+b_1).$
+%Let $x_n \coloneq -a_1^{-1}(x_1+b_1).$
 %Then
@@
 Let $J \in K^{n \times R}$ such that $\textrm{Im} J = \ker D$ where $R$ denotes the dimension of $\ker D$.
-Then $\PP = x_0 + J\PP'$ where $A' := AJ$ $b' := Ax_0 + b$ and
-    $\PP' := \{y \in K ^R: A'y + b' \ge 0 \}$.
+Then $\PP = x_0 + J\PP'$ where $A' \coloneq AJ$ $b' \coloneq Ax_0 + b$ and
+    $\PP' \coloneq \{y \in K ^R: A'y + b' \ge 0 \}$.
 
@@
     Then $\PP' = \{y \in K^R : QSP^{-1}y + b' \ge  0\} = P\{z \in K^R : Sz + Q^{-1}b' \ge 0 \}$.
-    Let $b'':=Q^{-1}b$ then $P' = P \{z \in K^R : s_i z_i + b''_i \ge 0, i= 1\ldots R\}$.
+    Let $b'' \coloneq Q^{-1}b$ then $P' = P \{z \in K^R : s_i z_i + b''_i \ge 0, i= 1\ldots R\}$.
 The set $\{z \in K^R : s_i z_i + b_i \ge 0\}$ is either empty or a polydisc (possibly with infinite radii) and $\PP = x_0 + JP \{z \in K^R: s_i z_i + b_i \ge  0, i=1,\ldots,R\}$ which concludes the proof.
@@
 \begin{array}{rcll}
-  p^* & := & \inf_{x \in K^n} & \val \left\langle c, x \right\rangle \\
+  p^* & \coloneq & \inf_{x \in K^n} & \val \left\langle c, x \right\rangle \\
   &    & \text{s.t.}         & A x + b \geq 0\\
@@
 $A \in K^{d \times n}$, $b \in K^d$, $D \in K^{m\times n}$, $e \in K^m$ 
-and $\left\langle c, x \right\rangle := c_1 x_1+\cdots +c_n x_n$.
+and $\left\langle c, x \right\rangle \coloneq c_1 x_1+\cdots +c_n x_n$.
 When $A$ is a diagonal matrix,
@@
   $$
-  \varphi_A(x) := A_0+x_1A_1+\cdots+x_nA_n = \diag(\ell_1(x), \ldots, \ell_d(x)).
+  \varphi_A(x) \coloneq A_0+x_1A_1+\cdots+x_nA_n = \diag(\ell_1(x), \ldots, \ell_d(x)).
   $$
@@
 We denote as $S^+_A$ the set $S_{A}^+ = \left\{ x \in K^n : A_0 + x_1 A_1+ ...+x_nA_n \succeq 0  \right\}$ and $S^-_B$ denotes the set $S^-_B = \left\{ x \in K^n : B_0 + x_1 B_1+ ...+x_nB_n \preceq 0\right\}$.
-The set $S_A,B := S_A^+ \cup S_B^-$ is called a \emph{spectrahedron}.
+The set $S_A,B \coloneq S_A^+ \cup S_B^-$ is called a \emph{spectrahedron}.
 %\end{definition}
@@
   \mathcal{S}_{M^{(i)}} = \left\{(x_i,y_i) \in K^2 :
-  M^{(i)}(x_i,y_i) := \diag\left(\pi^{-a} x_i, \pi^{b} y_i,
+  M^{(i)}(x_i,y_i) \coloneq \diag\left(\pi^{-a} x_i, \pi^{b} y_i,
   \begin{bmatrix}

### 2025-12-23 issac_biblatex_tentative/paper_CNV.tex
commit by Simone

@@
 \label{fermat_quartic}
-The basic closed semialgebraic set $\mathcal{R} = \{(x_1,x_2) \in \R^2 : 1-x_1^4-x_2^4 \geq 0\}$ is not a spectrahedron but it is semidefinite representable with representation:
+The basic closed semialgebraic set $\mathcal{R} = \{(x_1,x_2) \in \R^2 : 1-x_1^4-x_2^4 \geq 0\}$ is not a spectrahedron but it is a spectrahedral shadow with semidefinite representation
 $$
 %%\mathcal{R} =
-\left\{\begin{bmatrix} x_1 \\ x_2 \end{bmatrix} \in \R^2 :
-\exists\,
-\begin{bmatrix} y_1 \\ y_2 \end{bmatrix} \in \R^2, \,
+\left\{x \in \R^2 :
+%%\begin{bmatrix} x_1 \\ x_2 \end{bmatrix} \in \R^2 :
+\exists\, y \in \R^2,
+%%\begin{bmatrix} y_1 \\ y_2 \end{bmatrix} \in \R^2, \,
 %\left[
@@
 In this section, we prove that the class of polyhedra is stable
-by applying affine maps:
-
-\begin{theorem}[DI] 
+under application of affine maps:
+
+\begin{theorem}[direct image (DI)] 
 Let $f : K^n \to K^m$ be an affine map and $\PP$ a polyhedron in $K^n.$
@@
 \centering
-\scalebox{0.5}{
+\scalebox{0.55}{
 \begin{tikzpicture}[
@@
 We begin with the case of linear maps in $\GL_n(O_K)$.
+We often fix a linear basis $e_1,\ldots,e_n$ of $K^n$ which we call canonical\footnote{j'ai rajouté ça}.
 
@@
 \begin{proof}
-If $\PP$ is defined (in matrix form) by \[\left\lbrace X \in K^n,  AX+B \geq 0, CX+D=0 \right\rbrace\] and $U$ is the matrix of $f$ in the canonical basis of $K^n$, 
-let $\Qc$ be defined by \[\left\lbrace Y \in K^n,  AU^{-1} Y+B \geq 0, CU^{-1} Y+D=0 \right\rbrace.\]
-Then it is clear that $\Qc$ is a polyhedron and $f(\PP)=\Qc.$
+  If $\PP$ is defined (in matrix form) by
+  \[
+  \PP=\left\lbrace x \in K^n,  Ax+B \geq 0, Cx+D=0 \right\rbrace
+  \] and $U$ is the matrix of
+  $f$ in the canonical basis of $K^n$, 
+  let
+  \[\Qc=\left\lbrace y \in K^n,  AU^{-1} y+B \geq 0, CU^{-1} y+D=0 \right\rbrace.\]
+  Then it follow that $\Qc$ is a polyhedron and $f(\PP)=\Qc.$
   It is also clear that if $\PP$ is defined only by inequalities,
@@
 \begin{lemma}[DI${}_{diag}$]
-Let $f : K^n \to K^n$ be a linear map and $\PP$ a polyhedron in $K^n$ defined only by inequalities. We assume that the matrix of $f$ in the canonical basis of $K^n$ is diagonal.
-Then $f(\PP)$ is a polyhedron. \label{lem:DIdiag}
+  Let $f : K^n \to K^n$ be a linear map and $\PP$ a polyhedron in $K^n$ defined only by inequalities.
+  If the matrix of $f$ in the canonical basis of $K^n$ is diagonal,
+  then $f(\PP)$ is a polyhedron. \label{lem:DIdiag}
 \end{lemma}
 \begin{proof}
-As in the proof of Lemma \ref{lem:DIaut} DI${}_{aut}$, a trivial change
+As in Lemma \ref{lem:DIaut}, a change
 of variables is enough to conclude.
@@
 
-We now treat the case where $f$ is a projection erasing the last coordinate.
+We assume now $f$ is a projection erasing the last coordinate.
 
 \begin{lemma}[DI${}_{proj}$]
-Let $f : K^n \to K^{n-1}, \: (x_1,\dots,x_{n-1},x_n) \mapsto (x_1,\dots,x_{n-1})$ and $\PP$ a polyhedron in $K^n$ defined only by inequalities. 
+  Let $f : K^n \to K^{n-1}, \: (x_1,\dots,x_{n-1},x_n) \mapsto (x_1,\dots,x_{n-1})$, and let
+  $\PP$ be a polyhedron in $K^n$ defined only by inequalities. 
   Then $f(\PP)$ is a polyhedron defined only by inequalities. \label{lem:DIproj}
@@
 in matrix form:
-$\val(A X+B) \geq 0$ 
-with $A \in M_{q,n}(K)$, $B \in K^q$
-and $X=(x_1,\dots,x_n)^\intercal$.
-
-We can compute a Smith Normal Form
-of the $q \times (n-1)$ matrix defined by the 
+$\val(A x+B) \geq 0$ 
+with $A \in M_{q,n}(K)$, $B \in K^q$,
+and $x=(x_1,\dots,x_n)$ a column vector.
+
+We can compute a Smith Normal Form SNF($A'$)
+of the $q \times (n-1)$ matrix $A'$ defined by the 
 $n-1$ first columns of $A$
+\[
+\mathrm{SNF}(A') = \diag(\delta_1,\ldots,\delta_r,{\bf 0}_{q-r,n-1-r})
+\]
+
 to obtain a decomposition of the form:
-\[ Q_A A P_A^{-1} = \begin{bmatrix}
-\delta_1	& 		& 			&   &		 &  &a_1	\\
-			& \ddots& 			& 0	&		 &	&		\\
-			&		& \delta_l  &   & 		 &	&		\\
-			&		&			&0  & 		 &	& 		\\
-			&		&			&   & \ddots &	&		\\
-			&		&			&	&		 & 0&a_{n-1} \\
-			&		&			&	&		 &	&a_n 	\\
-			&		&			&	&		 &	&    	\\
-			&		&			&	&		 &	&a_q 	\\			
-\end{bmatrix},\]
+\[
+Q_A A P_A^{-1} =
+\begin{bmatrix}
+  &                  & & a_1 \\
+  & \mathrm{SNF}(A') & & \vdots \\
+  &                  & & a_{n-1} \\
+  &                  & &
+\end{bmatrix}
+%\begin{bmatrix}
+%  \delta_1	& 		& 			&   &		 &  &a_1	\\
+%  & \ddots& 			& 0	&		 &	&		\\
+%  &		& \delta_l  &   & 		 &	&		\\
+%  &		&			&0  & 		 &	& 		\\
+%  &		&			&   & \ddots &	&		\\
+%  &		&			&	&		 & 0&a_{n-1} \\
+%  &		&			&	&		 &	&a_n 	\\
+%  &		&			&	&		 &	&    	\\
+%  &		&			&	&		 &	&a_q 	\\			
+%\end{bmatrix},
+\]
 with $Q_A \in \GL_q(\OK)$ and $P_A \in \GL_n(\OK)$ such that $P_A(e_n)=e_n.$

### 2025-12-23 issac_biblatex_tentative/paper_CNV.tex
commit by Simone

@@
 \begin{bmatrix}
-  &                  & & a_1 \\
-  & \mathrm{SNF}(A') & & \vdots \\
-  &                  & & a_{n-1} \\
-  &                  & &
+ \mathrm{SNF}(A') & a
 \end{bmatrix}
@@
 \]
-with $Q_A \in \GL_q(\OK)$ and $P_A \in \GL_n(\OK)$ such that $P_A(e_n)=e_n.$
+with $Q_A \in \GL_q(\OK)$ and $P_A \in \GL_n(\OK)$ such that $P_A(e_n)=e_n$,
+and $a = (a_1,\ldots,a_q)^\intercal$
 
@@
 modify whether the valuation inequalities are satisfied.
-Moreover, thanks to Lemma \ref{lem:DIaut} DI${}_{aut}$,
-$\PP$ can be written
+Moreover, thanks to Lemma \ref{lem:DIaut},
+$\PP$ can be written as
 $\PP=P_A^{-1}(\PP_2)$ for some polyhedron $\PP_2 \subset K^n$
 and we are reduced to proving that
-$f(\PP_2)$ is a polyhedron for $p$ the projection
-$K^n \rightarrow K^{n-1}$ and $\PP_2$
+$f(\PP_2)$ is a polyhedron for $\PP_2$
 defined by the following linear matrix inequality (for some $B_2 \in K^q$):
-\[  \begin{bmatrix}
-\delta_1	& 		& 			&   &		 &  &a_1	\\
-			& \ddots& 			& 0	&		 &	&		\\
-			&		& \delta_l  &   & 		 &	& \vdots\\
-			&		&			&0  & 		 &	& 		\\
-			&		&			&   & \ddots &	&		\\
-			&		&			&	&		 & 0&a_{n-1} \\
-			&		&			&	&		 &	&a_n 	\\
-			&		&			&	&		 &	& \vdots   	\\
-			&		&			&	&		 &	&a_q 	\\			
-\end{bmatrix} \begin{bmatrix} x_1 \\ \\ \\ \\ \\ \vdots \\ \\ \\ \\ x_n \\ \end{bmatrix} + B_2 \geq 0.\]
-
+\[
+Q_A A P_A^{-1}
+%\begin{bmatrix}
+%\delta_1	& 		& 			&   &		 &  &a_1	\\
+%			& \ddots& 			& 0	&		 &	&		\\
+%			&		& \delta_l  &   & 		 &	& \vdots\\
+%			&		&			&0  & 		 &	& 		\\
+%			&		&			&   & \ddots &	&		\\
+%			&		&			&	&		 & 0&a_{n-1} \\
+%			&		&			&	&		 &	&a_n 	\\
+%			&		&			&	&		 &	& \vdots \\
+%			&		&			&	&		 &	&a_q 	\\
+%\end{bmatrix}
+\left[
+  \begin{smallmatrix}
+    x_1 \\ \vdots \\ x_n
+  \end{smallmatrix}
+  \right]
++ B_2 \geq 0.
+\]
 We remark that 
@@
 Since the conditions have to be compatible (we have assumed
-$\PP$ not empty), and thanks to ultrametricity,  
+$\PP\neq\emptyset$), and thanks to ultrametricity,  
 the intersection of these conditions for 
@@
 
-Thanks to Lemma \ref{lem:DIdiag} DI${}_{diag}$,
+Thanks to Lemma \ref{lem:DIdiag},
 we can further assume that the $\delta_i$'s and $a_n$ are all $1$'s
 and are reduce to $\PP_2$ defined by the linear matrix inequality:
-\[  \begin{bmatrix}
-1	& 		& 			&   &		 &  &a_1	\\
-			& \ddots& 			& 0	&		 &	&		\\
-			&		& 1  &   & 		 &	& \\
-			&		&			&0  & 		 &	& 	\vdots	\\
-			&		&			&   & \ddots &	&		\\
-			&		&			&	&		 & 0&a_{n-1} \\
-			&		&			&	&		 &	&1 	\\
-
-\end{bmatrix} \begin{bmatrix} x_1 \\ \\  \\ \\ \vdots \\  \\ \\ x_n \\ \end{bmatrix} + \begin{bmatrix} b_1 \\ \\ \\  \\ \vdots  \\ \\ \\ b_n \\ \end{bmatrix}  \geq 0.\]
+\[
+\begin{bmatrix}
+  \diag(I_\ell,{\bf 0}_{n-1-\ell,n-1-\ell}) & a \\
+       {\bf 0}_{1,n-1} & 1 
+\end{bmatrix}
+\left[
+  \begin{smallmatrix}
+    x_1 \\ \vdots \\ x_n
+  \end{smallmatrix}
+  \right]
++
+\left[
+  \begin{smallmatrix}
+    b_1 \\ \vdots \\ b_n
+  \end{smallmatrix}
+  \right]
+%\begin{bmatrix}
+%1	& 		& 			&   &		 &  &a_1	\\
+%			& \ddots& 			& 0	&		 &	&		\\
+%			&		& 1  &   & 		 &	& \\
+%			&		&			&0  & 		 &	& 	\vdots	\\
+%			&		&			&   & \ddots &	&		\\
+%			&		&			&	&		 & 0&a_{n-1} \\
+%			&		&			&	&		 &	&1 	\\
+%\end{bmatrix} \begin{bmatrix} x_1 \\ \\  \\ \\ \vdots \\  \\ \\ x_n \\ \end{bmatrix} + \begin{bmatrix} b_1 \\ \\ \\  \\ \vdots  \\ \\ \\ b_n \\ \end{bmatrix}
+\geq 0.\]
 Finally, we can also assume that, up to a permutation of the variables, $\val(a_1)= \min_{i=1}^{n-1} \val(a_i).$
@@
 
-Then the previous computations prove that $p(\PP_2)\subset \Qc.$
+Then the previous computations prove that $f(\PP_2)\subset \Qc.$
 Conversely, let $(x_1,\dots,x_{n-1}) \in \Qc.$
@@
 and $x_n+b_n=O(1)$. Hence $(x_1,\dots,x_n) \in \PP_2$
-which means that $(x_1,\dots,x_{n-1}) \in p(\PP_2).$
-Thus $p(\PP_2)= \Qc$ and $p(\PP_2)$ is a polyhedron.
+which means that $(x_1,\dots,x_{n-1}) \in f(\PP_2).$
+Thus $f(\PP_2)= \Qc$ and $f(\PP_2)$ is a polyhedron.
 
@@
 Hence $(x_1,\dots,x_n) \in \PP_2$
-which means that $(x_1,\dots,x_{n-1}) \in p(\PP_2).$
-Thus $p(\PP_2)= \Qc$ and $p(\PP_2)$ is a polyhedron,
+which means that $(x_1,\dots,x_{n-1}) \in f(\PP_2).$
+Thus $f(\PP_2)= \Qc$ and $f(\PP_2)$ is a polyhedron,
 and it has been proved in both cases.
 
-Therefore, $p(\PP)$ is a polyhedron (and inequalities are enough to define $p(\PP_2)$ as a polyhedron).
+Therefore, $f(\PP)$ is a polyhedron (and inequalities are enough to define $f(\PP_2)$ as a
+polyhedron\footnote{$f(\PP_2)$ ou bien $f(\PP)$ ?}).
 \end{proof}
@@
 \begin{lemma}[DI${}_{imm}$]
-  Let $f : K^l \to K^n$ be the immersion $(x_1,\dots, x_l) \mapsto (x_1,\dots, x_l,0,\dots, 0)$ and $\PP$
+  Let $f : K^l \to K^n$ be the immersion defined by
+  $(x_1,\dots, x_l) \mapsto (x_1,\dots, x_l,0,\dots, 0)$ and let $\PP$ be
   a polyhedron in $K^l$. Then $f(\PP)$ is a polyhedron. \label{lem:DIimm}
@@
 
-We can now generalize to linear mappings and
-polyhedron defined only by inequalities.
+We can now generalize to linear mappings and polyhedra defined only by inequalities.
 
@@
 \begin{proof}
-We assume that $\PP \neq \emptyset$, and we identify $f$ with its matrix in $\allmat_{n,m}(K)$.
-We assume that $\PP$ is defined as $\left\lbrace x \in K^n : \val (l_i (x) ) \geq 0, \textrm{ for } i \in I\right\rbrace$ for some
-finite sets $I \subset \N$ and $l_i \in K[x]_1$, for $i \in I$ .
-
-Thanks to Definition \ref{smith_nf}, (the matrix of) $f$
-can be written $f=Q^{-1} \Delta P$
+  We identify $f$ with its matrix in $\allmat_{n,m}(K)$, and we
+  assume that $\PP \neq \emptyset$ and that it is defined as
+$$
+\PP = \left\lbrace x \in K^n : \val (l_i (x) ) \geq 0, \textrm{ for } i \in I\right\rbrace
+$$
+for some finite set $I \subset \N$ and $l_i \in K[x]_1$, for $i \in I$ .
+
+Thanks to Definition \ref{smith_nf}, (the matrix of) $f$ can be written $f = Q^{-1} \Delta P$
 with $P \in \GL_n(\OK),$ $Q \in \GL_m(\OK)$

### 2025-12-23 issac_biblatex_tentative/paper_CNV.tex
end sec 3

@@
 with $P \in \GL_n(\OK),$ $Q \in \GL_m(\OK)$
-and $\Delta = \mathrm{SNF}(f)\in \allmat_{n,m}(K)$ of the form $\diag(\lambda_1, \ldots, \lambda_r, {\bf 0}_{\min(m,n)-r})$
-  where ${\bf 0}_{\min(m,n)-r}$ is a null square matrix of size $\min(m,n)-r$ for $\lambda_1,\dots,\lambda_r$ non-zero and $r \in \N.$
-
-By Lemma \ref{lem:DIaut} DI${}_{aut}$,
-$P(\PP)$ is a polyhedron defined only by inequalities.
-
-Let $\Qc= P(\PP)$
+and
+$$
+\Delta = \diag(\lambda_1, \ldots, \lambda_r, {\bf 0}_{\min(m,n)-r}) \in \mathrm{SNF}(f)\in \allmat_{n,m}(K)
+$$
+where ${\bf 0}_{\min(m,n)-r}$ is a null square matrix of size $\min(m,n)-r$ for
+$\lambda_1,\dots,\lambda_r$ non-zero and $r \in \N.$
+
+By Lemma \ref{lem:DIaut}, $\Qc = P(\PP)$ is a polyhedron defined only by inequalities.
 We now prove that $\Delta (\Qc)$ is a polyhedron.
@@
  the diagonal invertible mapping
-$K^l \rightarrow K^l$,
+$K^r \rightarrow K^r$,
 $(x_1,\dots,x_r)\mapsto (\delta_1 x_1,\dots,\delta_r x_r)$,
 and the projections
-$(x_1,\dots,x_{r+1})\mapsto (x_1,\dots,x_{r}),$
- $(x_1,\dots,x_{r+2})\mapsto (x_1,\dots,x_{r+1}),$
- $\dots,$
- $(x_1,\dots,x_{n})\mapsto (x_1,\dots,x_{n-1}).$
- Thus, thanks to Lemmas \ref{lem:DIimm} DI${}_{imm}$, \ref{lem:DIproj} DI${}_{proj}$ and \ref{lem:DIaut} DI${}_{aut}$, $\Delta (\Qc)$ is a polyhedron.
- One can note that it is only when applying the immersion as the last mapping in the composition chain that equalities are needed to define the last polyhedron.
-
-Finally, thanks to Lemma \ref{lem:DIaut} DI${}_{aut}$,
+\begin{equation*}
+  \begin{aligned}
+    (x_1,\dots,x_{r+1}) &\mapsto (x_1,\dots,x_{r})   \\
+    & \,\,\,\, \vdots \\
+    (x_1,\dots,x_{n}) &\mapsto (x_1,\dots,x_{n-1}).
+  \end{aligned}
+\end{equation*}
+%$(x_1,\dots,x_{r+1})\mapsto (x_1,\dots,x_{r}),$
+%$(x_1,\dots,x_{r+2})\mapsto (x_1,\dots,x_{r+1}),$
+%$\dots,$
+%$(x_1,\dots,x_{n})\mapsto (x_1,\dots,x_{n-1}).$
+Thus, thanks to Lemmas \ref{lem:DIimm}, \ref{lem:DIproj} and \ref{lem:DIaut},
+$\Delta (\Qc)$ is a polyhedron. One can note that it is only when applying the
+immersion as the last mapping in the composition chain that equalities are
+needed to define the last polyhedron.
+
+Finally, thanks to Lemma \ref{lem:DIaut},
 $Q^{-1} \left( \Delta (\Qc) \right)$ is a polyhedron.
@@
 \begin{proof}
-Let $P \in K^m$. One can see by immediate change of variables that $\Qc$ is a polyhedron in $K^m$ if and only if
-$\Qc+P$ is a polyhedron in $K^m$.
-Consequently, translating by $-f(O)$ in the codomain, one can reduce
-to the case of Proposition \ref{prop:DIl}   DI${}_l$.
+  Let $v \in K^m$. One can see by immediate change
+  of variables that $\Qc$ is a polyhedron in $K^m$ if and only if
+  $\Qc+v$ is a polyhedron in $K^m$.
+  Consequently, translating by $-f(O)$ in the codomain\footnote{Qu'est-ce q'est $O$ ? C'est $v$ ?},
+  one can reduce to the case of Proposition \ref{prop:DIl}.
 \end{proof}
@@
 
-\begin{proof}[Proof of Theorem \ref{theo:DI} DI]
-Here, $f : K^n \to K^m$ is an affine map and $\PP$ a polyhedron in $K^n.$
+\begin{proof}[Proof of Theorem \ref{theo:DI}]
+Recall that here $f : K^n \to K^m$ is an affine map and $\PP \subset K^n$ is a polyhedron.
 Let us write $\PP = \PP_I \cap \PP_E$
-with $\PP_I \coloneq \left\lbrace X \in K^n,  AX+B \geq 0 \right\rbrace$
-and $\PP_E \coloneq \left\lbrace X \in K^n,  CX+D=0 \right\rbrace = P + \overrightarrow{\PP_E}.$ 
-Then $f(\PP) = f_{\PP_E}(\PP_I).$
-
-By a translation of $-P$ in $K^n$, we can assume that
-$\PP_E$ is a linear vector space: we are reduced to proving that, if $\tilde{f}: \PP_E \to K^m$ is an affine map and $\PP_I$ is a polyhedron in the vector space $\PP_E$ defined only by inequalities, then  $\tilde{f}(\PP_I)$ is a polyhedron.
-This is the case thanks to Proposition \ref{prop:DIi} DI$_i$
+with $\PP_I \coloneq \left\lbrace x \in K^n,  Ax+B \geq 0 \right\rbrace$
+and $\PP_E \coloneq \left\lbrace x \in K^n,  Cx+D=0 \right\rbrace = v + \overrightarrow{\PP_E}.$
+\footnote{c'est quoi le overrightarrow sur $\PP_E$ ?}
+Then\footnote{je comprends pas la notation $f_{\PP_E}$.}
+$f(\PP) = f_{\PP_E}(\PP_I).$
+
+By a translation of $-v$ in $K^n$, we can assume that
+$\PP_E$ is a linear vector space: we are reduced to proving that, if
+$\tilde{f}: \PP_E \to K^m$ is an affine map and $\PP_I$ is a polyhedron in the vector space $\PP_E$ defined only by inequalities, then  $\tilde{f}(\PP_I)$ is a polyhedron.
+This is the case thanks to Proposition \ref{prop:DIi}
 and the theorem is proven.
@@
 \begin{proposition}[Characterization of polyhedra] \label{prop:carac}
-    Non-empty polyhedra are image of polydiscs under a linear mapping.
+    A non-empty polyhedron is the image of a polydisc under a linear mapping.
 \end{proposition}
@@
 
-If there exists $i_0 \in \{1,\ldots,n\}$ such that $s_{i_0} = 0$ then $\PP = f(D) = K$ and $\PP$ is a ball of infinite radius.
-Otherwise, we have $D = \{x \in K^n : x_i = \frac{b_i}{s_i} + O\left( \pi^{-val s_i} \right), i=1,\ldots,n \}$ and therefore for all $x \in  K$, $x \in P$ if and only if $x = a_0 + \sum_{i=1}^{n}( \frac{a_i b_i}{s_i} + O\left( \pi^{\val a_i - \val s_i} \right))= a_0  + \sum_{i=1}^{n} \frac{a_i b_i}{s_i} + O(\pi^d)$ where $d = \min \limits_{i = 1,\ldots,n} \val a_i - \val s_i$.
-Thus $\PP = \{x \in K : \val (x - a_0 - \sum_{i=1}^{n} \frac{a_i b_i}{s_i}) \ge d \}$ is a ball.
-
+    If there exists $i_0 \in \{1,\ldots,n\}$ such that $s_{i_0} = 0$ then $\PP = f(D) = K$ and $\PP$ is a ball of infinite radius. Otherwise, we have
+    $$
+    D = \left\{x \in K^n : x_i = \frac{b_i}{s_i} + O\left( \pi^{-val s_i} \right), i=1,\ldots,n\right\}
+    $$
+    and therefore for all $x \in K$, one has $x \in P$ if and only if
+    $$
+    x = a_0 + \sum_{i=1}^{n}\left(\frac{a_i b_i}{s_i} + O( \pi^{\val a_i - \val s_i}) \right)
+    = a_0  + \sum_{i=1}^{n} \frac{a_i b_i}{s_i} + O(\pi^d)
+    $$
+    where $d = \min \limits_{i = 1,\ldots,n} \val a_i - \val s_i$. Thus
+    $\PP$ is the ball described by
+    $$
+    \PP = \{x \in K : \val (x - a_0 - \sum_{i=1}^{n} \frac{a_i b_i}{s_i}) \ge d \}.
+    $$
 \end{proof}
